### 2022-01-26 tex/draft.tex
Initial commit

\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{physics}
\usepackage{bm}

\usepackage{url,hyperref,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}
\usepackage{cleveref}
% \usepackage[font={bold,it}]{caption}

% Define better ref abbreviations
\usepackage[displaymath]{lineno}

\renewcommand{\d}{\mathrm{d}}
\renewcommand{\k}{\mathrm{K}}
\newcommand{\ca}{\mathrm{Ca}}
\newcommand{\na}{\mathrm{Na}}
\newcommand{\leak}{\mathrm{L}}
\newcommand{\dstar}{d^\star}
\newcommand{\gstar}{g^\star}
\newcommand{\gbar}{\bar g}
\newcommand{\delt}{\Delta t}
\newcommand{\taus}{\tau_s}
\newcommand{\dn}{\delta_n}
\newcommand{\taud}{\tau_d}

\linenumbers

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Olenik {et~al.}} %use et al only if is more than 1 author
\def\Authors{Mark Olenik\,$^{1,*}$, and Conor Houghton\,$^{2}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$School of Biological Sciences, Faculty of Life Sciences, University of Bristol, Bristol, United Kingdom \\
$^{2}$School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, Faculty of Engineering, University of Bristol, Bristol, United Kingdom}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Mark Olenik}

\def\corrEmail{m.olenik@bristol.ac.uk}

\begin{document}

\onecolumn
\firstpage{1}

\title[Scalar Poincaré map for bursting]{A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression.}

\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}

\maketitle

\begin{abstract}
\section{}
Short-term synaptic plasticity is found in many areas of the central
nervous system.  In the inhibitory half-centre central pattern
generators involved in locomotion, synaptic depression is believed to
act as a burst termination mechanism, allowing networks to generate
anti-phase bursting patterns of varying periods.  To better understand
burst generation in these central patter generators, we study a
minimal network of two neurons coupled through depressing synapses.
Depending on the strength of the synaptic conductance between the two
neurons, this network can produce symmetric $n-n$ anti-phase bursts,
where neurons fire $n$ spikes in alternation, with the period of such
solutions increasing with the strength of the synaptic conductance.
Relying on the timescale disparity in the model, we reduce the
eight-dimensional network equations to a fully-explicit scalar
Poincaré burst map.  This map tracks the state of synaptic depression
from one burst to the next and captures the complex bursting dynamics
of the network.  Fixed points of this map are associated with stable
burst solutions of the full network model, and are created through
fold bifurcations of maps.  We derive conditions that describe
period-increment bifurcations between stable $n-n$ and $(n+1)-(n+1)$
bursts, producing a full bifurcation diagram of the burst cycle
period.  Predictions of the Poincaré map fit excellently with
numerical simulations of the full network model and allow the study of
parameter sensitivity for rhythm generation.

\tiny
 \keyFont{ \section{Keywords:} Synaptic depression, Poincaré map, Dynamical system, Neuronal bursting, Central pattern generator}

\end{abstract}

\section{Introduction}
% DEPRESSION
Short-term synaptic plasticity may have a role in burst activity in
central pattern generators (CPGs).  Short-term synaptic depression is
commonly found in neuronal networks involved in the generation of
rhythmic movements, such as in the pyloric CPG of the spiny
lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of
the chick embryo~\citep{donovan1998}.  Synaptic depression modulates
the strength of synapses in response to changes to the presynaptic
firing frequency.  At a high neuronal firing frequency, depression
weakens the strength of synapses and therefore reduces the magnitude
of the postsynaptic response.  At low firing frequency, it allows
sufficient time for the synapse to recover from depression between
spikes, leading to a stronger postsynaptic response.  In reciprocal
networks, synaptic depression has been shown to act as a ``switch'',
giving rise to a wide range of network dynamics such as synchronous
and multi-stable rhythms, as well as fine tuning the frequency of
network oscillations~\citep{nadim2000, nadim1999, bose2011}.

% Brown
~\citet{brown1911} pioneered the idea that synaptic depression acts as
a burst termination mechanism in reciprocally inhibitory CPGs involved
in rhythm generation of locomotion. When one side is firing during a
burst the other, antagonistic side, is prevented from firing by
synaptic inhibition. However, the weakening of inhibition as a result
of synaptic depression eventually releases the antagonistic side so
that it starts firing, terminating the burst on the side that had
originally been firing.  This rhythmogenesis hypothesis has been
considered one of a handful of standard mechanisms for generating
locomotion rhythms in
vertebrates~\citep{reiss1962,perkel1974,friesen1994}. It has been
proposed as an explaination of the antiphase burst rhythm in
struggling in \textit{Xenopus} tadpoles~\citep{li2007}.

~\citet{bose2011} investigated burst generation in a generic
half-centre CPG that consists of two identical, tonically active
Morris-Lecar~\citep{morris1981} neurons coupled through inhibitory
depressing synapses.  Numerical simulations showed that when the
reciprocal synaptic conductance between the two neurons is varied, the
network produces symmetric $n-n$ anti-phase bursts, with stronger
synaptic coupling leading to longer bursts.  They used methods from
geometric singular perturbation theory to separate the timescales of
the fast membrane, and the slow synaptic dynamics of the network to
derive one-dimensional conditions necessary for the existence of
stable $n-n$ solutions (for $n\leq 2$). According to these conditions
the type of firing pattern largely depends on the slow depression
dynamics of the synapses between the two neurons, and can therefore be
predicted by knowing the strengths of the synaptic conductances of the
two synapses.
Thus, the scalar conditions derived in~\citet{bose2011} provide a
method to numerically identify the type of stable $n-n$ pattern for
any given value of the coupling strength.  However, they do not
predict the exact period of such solutions.
Furthermore, while they provide good arguments for the validity of
their reduction assumptions and the resulting scalar conditions, they
do not verify them numerically.

Here we extend the previous analysis by providing a Poincaré map of
the slow depression dynamics.  This allows us not only to predict the
types of stable $n-n$ solutions the full network can produce, (for any
$n$), but also to study how varying the coupling strength affects the
period of such solutions.  To do this, we build on, and numerically
test, the assumptions on the fast-slow timescale disparity made
in~\cite{bose2011}.  We reduce the two-cell model to a scalar
Poincaré map that tracks the evolution of the depression from the
beginning of one burst to the beginning of the next burst.  Stable
fixed points of our map are associated with stable $n-n$ burst
solutions.  Our map construction is motivated by the burst length map
of a T-type calcium current, utilised by~\citet{matveev2007}, which
approximates the anti-phase bursting dynamics of a network of two
coupled Morris-Lecar neurons.  In contrast to our model, the network
described in the~\cite{matveev2007} paper does not contain short-term synaptic
depression, and burst termination is instead accomplished through the
dynamics of a slow T-type calcium current.

% MAIN RESULTS AND CONCLUSIONS
The Poincaré map derived here replicates the results from numerical
simulations of the full two-cell ODE system: Given the strength of
maximum conductance between the two neurons, fixed points of our map
predict the type and period of $n-n$ patterns, the switch between
burst solutions of different periods, as well as the occurrence of
co-existent solutions.  In addition to proving the existence and
stability of fixed points, our map shows that fixed points are created
via a fold bifurcation of maps.  We also derive algebraic conditions
that predict the period increment bifurcations that allow the switch
between $n-n$ and $(n+1)-(n+1)$ solutions.  Because our map is fully
explicit, it lays the framework for studying the effects of other
model parameter on network dynamics without the need to run expensive
numerical integrations of the ODEs.

% PAPER STRUCTURE.
This paper is organised as follows.  First, we introduce the network
of two neurons, and describe the properties of single cell and synapse
dynamics.  We use numerical simulations of the network to provide an
intuition for the range of possible burst dynamics the system can
produce.  Next, we state and justify the simplifying assumptions that
are necessary for the map construction.  Finally, we analytically
derive the first return map of the depression variable as well as the
conditions that are required for stable solutions to bifurcate between
$n-n$ and $(n+1)-(n+1)$ solutions.  We end this work with a
discussion.

\section{Materials and Methods}
We consider a pair of identical Morris-Lecar neurons~\citep{morris1981}, with parameters adapted from~\cite{bose2011}.
The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
\begin{align}
    ~\label{eq:cell-modelA}
     \dot v_{i}&= f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}),\\
    ~\label{eq:cell-modelB}
     \dot w_{i} &=h(v_i,w_i).
   \end{align}
Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.
Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
\begin{equation}
 ~\label{eq:memcur}
  f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})-g_{\leak}(v_{i}-v_{\leak}) + I.
\end{equation}
The currents include a constant current $I$, and three ionic currents:
an instantaneous calcium current, a potassium current, and a leak current, with respective reversal potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances $g_{\ca}$, $g_{\k}$, and $g_{\leak}$.
The function $h(v_{i}, w_{i})$ models the kinetics of the potassium gating variable $w_{i}$, and is given by
\begin{equation}
  h(v_{i}, w_{i})=\frac{w_{\infty}(v_{i})-w_{i}}{\tau_{w}}~\label{eq:h}.
\end{equation}
The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the \textbf{Supplementary Material S1}.

The dynamics of the synaptic interactions between the neurons are governed by a synaptic gating variable $s_{i}$ and a depression variable $d_{i}$:
\begin{linenomath}
  \begin{align}
    \dot s_{i} &= -s_{i}/\tau_{s}~\label{eq:dot-s},\\
    \dot d_{i} &= (1-d_{i})/\tau_{d}~\label{eq:dot-d}.
  \end{align}
\end{linenomath}
Variable $d_{i}$ describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
Our model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
In between spikes $s_{i}$ decays with time constant $\tau_{s}$, while $d_{i}$ recovers with time constant $\tau_{d}$.
Because synaptic depression occurs on a much slower timescale than synaptic inhibition, we assume $\tau_{d}\gg\tau_{s}$.
At spike time when the voltage $v_{i}$ crosses a synaptic threshold $v_{\theta}$, the synaptic variable $s_{i}$ is reset to the current value of $d_{i}$, and $d_{i}$ is scaled down by the depression strength parameter $\lambda$, where $0<\lambda<1$.
This results in the following discontinuous reset rule on spike time:
\begin{linenomath}
  \begin{align}
    s_{i} &\leftarrow d_{i}~\label{eq:s-reset},\\
    d_{i} &\leftarrow \lambda d_{i}~\label{eq:d-reset}.
  \end{align}
\end{linenomath}
The equations for the depression model were adapted from the~\citet{bose2001} model.
These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by~\citet{tsodyks1997}.
The original equations in~\cite{bose2001} include an exponential decay of $d_{i}$ throughout the active phase of the action potential, that is $\dot d_{i}=-d_{i}/\tau_{\beta}$ for $v_{i}>v_{\theta}$.
To simplify the mathematical analysis we have reduced these dynamics to a single-reset event at spike time according to \cref{eq:d-reset}.
This simplification is natural given an approximately constant duration of the active phase of an action potential, and it will become evident from our results that this simplification does not qualitatively change the dynamics of the network compared to the original equations, where depression dynamics are described by an exponential decay.

When the cells are uncoupled ($\gbar=0$), the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
The two curves intersect along the middle branch of $v_{\infty}$, creating an unstable fixed point $p_{f}=(v_{f},w_{f})$ with a surrounding stable limit cycle of period $T$ (\cref{fig:nullclines}A).
Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.

The two-cell network model is numerically integrated using an adaptive step-size integrator for stiff differential equations implemented with XPPAUT~\citep{ermentrout2002} and controlled through the Python packages SciPy~\citep{scipy2020} and PyXPP~\citep{pyxpp}.
The following mathematical analysis is performed on the equations of a single cell.
Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.

\section{Results}
\subsection{Anti-phase burst solutions}
Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism~\citep{brown1911} and is known to produce $n-n$ anti-phase burst solutions of varying period.
Such $n-n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
\Cref{fig:depression-traces}A shows the timecourse of a typical $4-4$ burst.
While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
Therefore, at any given moment one cell is spiking while the other is inhibited.
Consistent with~\citet{bose2011} we will refer to the currently firing cell as ``free'' and we will call the inhibited cell ``quiet''.
Additionally, we will distinguish between two phases of a $n-n$ solution:
We will refer to the burst duration of a cell as the ``free phase'', which is the time between the first spike and the last spike in a burst. And we will call the remaining duration of a cycle, when a cell is not spiking, the ``quiet phase''.

% TODO: Add mention of gstar. Once critical conductance is crossed, cell is released.
With each action potential of the free cell, short-term depression leads to a step-wise decrease of $d$, and consequently of $s$ (\cref{fig:depression-traces}B).
If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\gbar s$ will eventually become sufficiently small to allow for the quiet cell to be released and start firing, thus inhibiting the previously free cell.
While a cell is quiet its depression variable can recover.
Once the quiet cell becomes free again its synaptic inhibition will be sufficient to terminate the burst of the previously free cell and commence a new cycle.
As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\gbar$ determines the type of $n-n$ solution.
Increasing $\gbar$ produces higher $n-n$ burst solutions with more spikes per burst and a longer cycle period.
\Cref{fig:burst-sols} shows numerically stable $n-n$ solutions for varying values of $\gbar$.
For small values of $\gbar$ the network produces anti-phase spiking $1-1$ solutions.
As $\gbar$ is increased the network generates solutions of increasing $n$, that is $2-2$, $3-3$, and $4-4$.
When $\gbar$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
Depending on the initial conditions either of the two cells can become the suppressed cell, which is why the suppressed solution is numerically bistable.

Branches of numerically stable $n-n$ solutions and their associated limit cycle period for varying values of $\gbar$ are depicted in \cref{fig:bif-diagram}A (see  \textbf{Supplementary Material S2} for algorithm description).
Not only do higher $n-n$ solutions branches require stronger coupling $\gbar$, but also within $n-n$ branches the period increases with $\gbar$.
In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2-2$ and $3-3$ solution branches.
Branches of higher $n-n$ burst solutions occur on increasingly smaller intervals of $\gbar$, for instance is the $\gbar$ interval of the $5-5$ branch shorter than that of the $4-4$ branch and so on.
The interval between the $5-5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n-n$ solutions, such as $11-11$ bursts, but also other non-symmetric $n-m$ solutions as well irregular, non-periodic solutions. However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n-n$ solutions.

\subsection{Mathematical analysis of two-cell network}
~\label{sec:assumptions}
% Summary of assumptions
The goal of the following mathematical analysis is to reduce the complexity of the eight-dimensional system to some easily tractable quantity.
As we will see later this quantity is the value of the depression variable $d$ of either of the two cells.
We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the free phase, and then during the quiet phase.
This construction will require two assumptions about the membrane and synaptic dynamics.
The first assumption states that during a burst the free cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
The second assumption states that once the inhibitory conductance acting on the quiet cell drops below a critical threshold, the cell is immediately released and fires.
The second assumption is necessary to predict the release time of the quiet cell, which allows us to model the recovery of $d$ during the quiet phase.
In other words, the second assumption requires that the release of the quiet cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the quiet cell.
Both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n-n$ solutions.
However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.

% Assumption 1: Free phase
Our first assumption about the model states that the free cell fires at its uncoupled period $T$, that is, during the free phase of a burst we have $ISI=T$.
Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
We can further numerically confirm this observation by capturing the $ISI$s of the stable solutions from the bifurcation diagram in \cref{fig:bif-diagram}A.
In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the quiet phase of the burst.
$IBI$s lie on multiple branches, each branch associated with a stable $n-n$ solution, and are monotonically increasing with $\gbar$.
In contrast, $ISI$s are calculated from the spikes within the free phase and do not vary significantly with $\gbar$, but are approximately $ISI\approx T$, affirming our first assumption.
Assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the free phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
Assuming $ISI=T$ seems reasonable given that inhibition acting on the quiet cell decays exponentially to zero on a much shorter timescale than the duration of the $ISI$, and therefore, once the quiet cell is released its trajectory quickly approaches the spiking limit cycle.

% Assumption 2: Release
Our second assumption states that the quiet cell is released and spikes as soon as inhibition from the free cell drops below a constant threshold.
We will now define such a ``release condition'' by exploiting the discrepancy in timescales between the fast membrane dynamics, and the slower synaptic dynamics.
Let us first consider the dynamics of a single Morris-Lecar neuron.
We fix the synaptic variable that acts on the cell by setting $s=1$, which also makes the applied synaptic conductance $\gbar s$ constant.
Recall from \cref{fig:nullclines}A that in case of a single uncoupled cell ($\gbar s=0$), the $v$- and $w$-nullclines intersect at some unstable fixed point $p_{f}=(v_{f},w_{f})$, while trajectories revolve around a stable spiking limit cycle.
Increasing $\gbar s$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point $p_{f}$ down the sigmoid $w_{\infty}$ in the $(v-w)$-plane (\cref{fig:nullclines-coupled}).
When $\gbar s$ is large enough, the fixed point $p_{f}$ becomes stable, attracting all previously periodic trajectories.
There exists a unique value $\gbar s=g^{\star}$ when $p_{f}$ changes stability and the stable limit cycle vanishes.
Thus, when a constant inhibitory conductance is applied, $\gbar s<g^{\star}$ acts as a necessary condition for a cell to spike.
In contrast, when $\gbar s>g^{\star}$ inhibition is strong enough to prevent a cell from spiking~\citep{bose2011}.

% NOTE
% In our parameter range the bifurcations occur via subcritical Hopf (bose2011 p.47)

Now let us analyse the nullclines of the quiet cell when the two cells are coupled via synaptic inhibition with depression.
Let $\gbar s$ here denote the total synaptic conductance which acts on the quiet cell and is produced by the free cell, and let $p_{f}$ be the fixed point associated with the quiet cell.
At the start of the burst of the free cell we have $\gbar s > g^{\star}$ and $p_{f}$ is stable.
When the free cell spikes, $\gbar s$ peaks (\cref{eq:s-reset}), and the $v$-nullcline with the ensuing stable $p_f$ move down the $w$-nullcline.
Then in between spikes $\gbar s$ decays exponentially (\cref{eq:dot-s}) causing the $v$-nullcline and $p_{f}$ to move up the $w$-nullcline while attracting trajectories of the quiet cell.
Once depression causes the synaptic conductance to become small enough to satisfy $\gbar s<g^{\star}$ and the quiet cell is released, fixed point $p_{f}$ becomes unstable allowing the quiet cell to fire.
If the trajectory of the quiet cell remains sufficiently close to the stable $p_{f}$ at the time when it changes stability, then $\gbar s < g^{\star}$ acts as a release condition that is not only necessary, but also sufficient for firing of the quiet cell.
In this case the release of the quiet cell occurs precisely when
\begin{equation}
 ~\label{eq:release}
  \gbar s=g^{\star}
\end{equation}
is satisfied.

Whether the $(v,w)$-trajectory of the quiet cell can remain close enough to $p_{f}$ to make \cref{eq:release} sufficient for firing depends largely on the coupling strength $\gbar$ and the timescale disparity between membrane dynamics and synaptic dynamics~\citep{bose2011}.
It is straightforward to test our assumption of a release condition by numerically integrating the full system of ODEs and calculating the time interval between the first spike of the quiet cell and the time when $\gbar s$ first crosses $g^{\star}$.
We will call this time interval the ``release delay''.
If our assumption holds, we would expect an approximately zero release delay.
\Cref{fig:release-delay} shows the numerically computed graph of the release delay for varying $\gbar$.
The graph shows three distinct branches, next to each branch we also plot the timecourse of a corresponding sample solution of the total synaptic conductance $\gbar s$ of both cells.
For the rightmost branch where $\gbar>0.592$ $\si{mS/cm^{2}}$ the release delay is approximately zero.
Here the first spike of the quiet cell can be accurately predicted by the release condition in \cref{eq:release}.
The leftmost and middle branches for $\gbar<0.592$ $\si{mS/cm^{2}}$  show a release delay greater than zero, the quiet cell does not immediately fire when the release condition is first satisfied, and \cref{eq:release} does not accurately predict the release of the quiet cell.
The leftmost and middle branches contain $1-1$ and $2-2$ solutions respectively.
In both cases the coupling $\gbar$ is not sufficiently strong to allow trajectories of the quiet cell to be close enough to $p_{f}$ to guarantee spiking once $\gbar$ crosses $g^{\star}$.
Note that in the middle branch $\gbar s $ crosses $g^{\star}$ twice, and only after the second crossing does the quiet cell fire.
The following map construction relies on the assumption that the release condition in \cref{eq:release} can accurately predict the release time of the quiet cell.
Given our model parameters this is only possible for sufficiently large $\gbar>0.592 $ $\si{mS/cm^{2}}$.
For completeness, however, we will also consider values $\gbar < 0.592$ $\si{mS/cm^{2}}$ in the following analysis, bearing in mind that in this parameter range our map will not be accurate.

In summary: For $\gbar>0.592$ $\si{mS/cm^{2}}$ the release condition is sufficient to predict when the quiet cell is released.
Due to the symmetry of $n-n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
The release time therefore uniquely determines the type of $n-n$ solution.
Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the quiet cell.
Instead, the solution of the synaptic variable $s$ of the free cell is sufficient to predict when $\gbar s=g^{*}$ is satisfied.
Finally, $s$ is solely determined by the evolution of the depression variable $d$ of the free cell.
Constructing a solution of $d$ during the free phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n-n$ solutions.

\subsection{Construction of the scalar Poincaré map}
In this section we construct the scalar Poincaré map $\Pi_{n}:d^{\star}\mapsto d^{\star}$.
Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n-n$ burst.
The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
To simplify the map construction we will assume that a free cell fires exactly $n$ times before it becomes quiet.
Later we will relax this assumption.
We will construct $\Pi_{n}$ by evolving $d$ first during the free phase and then during the quiet phase of the $n-n$ limit cycle.
First, let us give explicit definitions of the free and quiet phases.
A schematic illustration of both phases is given in \cref{fig:free-quiet1}.

Suppose that at $t=0$ cell 1 becomes free with some initial $d(0)$. 
Cell 1 then fires $n$ spikes at the uncoupled period $T$.
Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
After $n$ spikes the total conductance $\gbar s(t)$ acting on the quiet cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}, that is at some time $t=(n-1)T+\delt$ we have $\gbar s(t)=g^{\star}$.
Cell 2 is then released and prevents cell 1 from further spiking.
Here $\delt$ is the \emph{inter-burst-interval}, or the time between the last spike of cell 1 and the first spike of cell 2~\citep{bose2011}.
Once released, cell 2 also fires $n$ spikes until cell 1 becomes free once again at the cycle period.
Let $P_n$ denote the full cycle period of a $n-n$ solution:
\begin{equation}
 ~\label{eq:P}
  P_n = 2(n-1)T + 2\delt.
\end{equation}
We can now define the free and quiet phases of cell 1 explicitly. The free phase is the time interval between the first and last spikes of the burst, that is for time $0<t<(n-1)T$.
During the free phase of cell 1, the quiet cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\gbar s > g^{\star}$.
The quiet phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T < t < 2(n-1)T + 2\delt$.

Note that only the quiet phase depends on $\delt$, and $\delt$ will play a central role in the construction of $\Pi_{n}$.
From \cref{eq:P} $\delt$ can be be computed as
\begin{equation}
 ~\label{eq:delta-t-P}
  \delt = \frac{1}{2}P_n - (n-1)T.
\end{equation}
\noindent
We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n-n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\delt$ as a function of $\gbar$ (\cref{fig:delta-t}).
Each continuous branch of $\delt$ is monotonically increasing and corresponds to a $n-n$ burst:
Stronger coupling $\gbar$ increases the total synaptic conductance $\gbar s$ that acts on the quiet cell, thus delaying its release.
It is easy to see that for any $n$-branch we have $\delt<T$:
Once $\delt$ crosses $T$, the free cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1)-(n+1)$ burst.

Distinguishing between the free and quiet phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
As can be seen from \cref{fig:free-quiet1}C, during the free phase $d$ depresses at spike times and recovers in the $ISI$s.
In contrast, during the quiet phase $d$ only recovers and does not depress.
Given the initial $d^{\star}=d(0)$ at the beginning of the cycle and the number of spikes in the free phase $n$, we can now construct the burst map $\Pi_{n}$.
The map
\begin{equation}
  \Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star}\big))
\end{equation}
\noindent
is a composition of two maps.
Map
\begin{equation}
  F_{n}:d^{\star}\mapsto \delt
\end{equation}
models the evolution of $d$ in the free phase.
$F_{n}$ takes an initial value $d^{\star}$ and calculates the inter-burst-interval $\delt$.
Map
\begin{equation}
  Q_{n}:\delt \mapsto d^{\star}
\end{equation}
models the recovery of $d$ in the quiet phase.
Given some $\delt$ map $Q_n$ computes $\dstar$ at the start of the next cycle.

Our aim in the following analysis is to elucidate the properties of $\Pi_{n}$ and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of $\Pi_{n}$ are created.
To that effect it will be useful to include not only positive, but also negative values of $d^{\star}$ to the domain of $\Pi_{n}$.
But it is important to add that values $d^{\star}<0$ are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
Because $\Pi_{n}$ maps first from $d^{\star}$ to $\delt$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n-n$ solutions with partially overlapping bursts.
As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n-n$ solutions of the full system of ODEs only exist for $\Delta t>0$.

We start the construction of $\Pi_n$ by first considering the free phase and building the map $F_n$.
At each spike time $t_{k}$, variable $d$ depresses with the reset $d(t_{k})\leftarrow \lambda d(t_{k}^{-})$ (\cref{eq:d-reset}).
For the duration of the subsequent $ISI$, the recovery of $d$ is described by the solution to \cref{eq:dot-d}:
\begin{equation}
  d(t) = 1 - (1-\lambda d_{k})e^{-t/\tau_{d}}~\label{eq:d-sol},
\end{equation}
where the variable $d_{k}=d(t^{-}_{k})$ is the level of depression at spike time $t_{k}$.
By substituting $t=T$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the free phase:
\begin{equation}
  d_{k+1} = \lambda\rho d_{k} + (1-\rho),~\label{eq:map-d}
\end{equation}
where to keep the notation simple we let $\rho=\exp(-T/\tau_{d})$.
Since $0<\lambda, \rho<1$, the map~\eqref{eq:map-d} is increasing and contracting, with a fixed point at
\begin{equation}
 ~\label{eq:dsup}
  d_{s}=\frac{1-\rho}{1-\lambda\rho},
\end{equation}
where $0<d_{s}<1$.
The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
Using the release condition in \cref{eq:release} allows us to derive the value of the the minimum coupling strength that will produce the full suppressed solution, denoted as $\gbar_{s}$.
Solving \cref{eq:dot-s} for $s(t)$ with $t=T$ and setting the initial value $s(0)=d_{s}$ gives
\begin{equation}
\gbar_{s} d_{s}e^{-T/\tau_{s}}=g^{\star}.
\end{equation}
By further substituting the definition of $d_{s}$ in~\eqref{eq:dsup} and rearranging, we can write $\gbar_{s}$ as a function of the depression strength $\lambda$:
\begin{equation}
  \label{eq:gs}
  \gbar_{s}(\lambda) = g^{\star}e^{T/\tau_{s}}\frac{1-\lambda \rho}{1-\rho}.
\end{equation}
Note that the above dependence of $\gbar_{s}$ on $\lambda$ is linear and monotonically decreasing.
Increasing $\lambda$ reduces the strength of the depression of the free cell.
This in turn allows the free cell to fully suppress the quiet cell at smaller values of $\gbar$.

Solving~\eqref{eq:map-d} gives us the linear map $\delta_{n}:d^{\star}\mapsto d_{n}$, that for some initial $d^{\star}$ computes the depression at the $n$th spike time, $d_{n}=d(t_{n}^{-})$:
\begin{equation}
 ~\label{eq:delta-map}
  \delta_{n}(d^{\star}) = (\lambda \rho)^{n-1} d^{\star} + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}.
\end{equation}
Since $\lambda < 1$, function $\delta_{n}$ is a linearly increasing function of $d^{\star}$ with a fixed point at $d_{s}$ for all $n$.
Having identified $d$ after $n$ spikes, we can now use the release condition $\gbar s = g^{\star}$ (\cref{eq:release}) to find $\delt$.
At the last spike of the free phase at time $t_{n}=(n-1)T$ the synapse variable $s$ is reset according to \cref{eq:s-reset}:
\begin{equation}
  s(t_{n})\leftarrow \dn(\dstar).
\end{equation}
After the last spike $s$ decays exponentially according to the solution of \cref{eq:dot-s}, where setting the initial condition $s(0)=\dn(\dstar)$ yields:
\begin{equation}
~\label{eq:s-sol}
  s(\delt)=\dn(\dstar)e^{-\Delta t/\tau_{s}}.
\end{equation}
Substituting $s(\delt)$ into $s$ of the release condition (\cref{eq:release}) gives then
\begin{equation}
 ~\label{eq:release2}
  \gbar \dn(\dstar) e^{-\delt/\tau_{s}}=g^{\star}.
\end{equation}
Our assumption of the release condition guarantees that the quiet cell 2 spikes and becomes free when $\gbar s - g^{\star}$ crosses zero.
Solving \cref{eq:release2} for $\delt$ allows us to compute the inter-spike-interval as a function of $\dstar$, which defines our map $F_n$:
\begin{equation}
 ~\label{eq:Fn-map}
  F_{n}(d^{\star}):=\tau_{s}\ln{\left(\frac{\gbar }{g^{\star}} \delta_{n}(d^{\star})\right)}= \delt.
\end{equation}

\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\gbar$.
Larger values of $d^{\star}$ and $\gbar$, respectively, cause stronger inhibition of the quiet cell, and therefore prolong its release time and the associated $\delt$.
Map $F_{n}$ is defined on $d^{\star}>d_{a}$, where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(\dstar)=0$ in \cref{eq:delta-map} for $\dstar$, which yields
\begin{equation}
  d_{a}(n)=-\frac{(1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}}{ (\lambda \rho)^{n-1} }\leq 0~\label{eq:da}.
\end{equation}

We now turn to the construction of map $Q_{n}$, which describes the recovery of the depression variable during the quiet phase.
As we have identified earlier, the recovery in the quiet phase of a $n-n$ solution is of duration $2\delt +(n-1)T$.
Substituting that into the solution for $d(t)$ (\cref{eq:d-sol}) with the initial condition $d(0)=\dn(\dstar)$ yields the map $Q_{n}$:
\begin{equation}
 ~\label{eq:Qn-map}
  Q_{n}(\delt):=1- (1- \lambda \dn(\dstar))e^{-(2\Delta t+(n-1)T)/\tau_{d}}.
\end{equation}
Given $\delt$, we can find $\dn(\dstar)$ by rearranging the release condition in \cref{eq:release2}:
\begin{equation}
 ~\label{eq:dn}
  \dn(\dstar) = \frac{g^{\star}}{\gbar} e^{\delt/\tau_{s}}.
\end{equation}
Map $Q_{n}$ is shown in \cref{fig:FQ-map}B for various values $n$.
Note that $Q_{n}$ is monotonically increasing as larger values $\delt$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
All curves $Q_{n}$ intersect at some $\delt = \tau_{s}\ln{\left[\gbar/(g^{\star}\lambda)\right]}$ where
\begin{equation}
     ~\label{eq:Qn-intersect}
      Q_{n}\left[\tau_{s}\ln{\left(\frac{\gbar}{g^{\star}\lambda}\right)}\right]=1.
    \end{equation}
As we will show in the next section, all fixed points of the full map $\Pi_{n}$ occur for $d^{\star}<1$.
We will therefore restrict the domain of $Q_{n}$ to $(-\infty, \ln{\left[\gbar/(g^{\star}\lambda)\right]}\tau_{s})$ and the codomain to $(-\infty, 1)$.
Additionally, while values $\delt>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t=T$, and we will address this concern in the last part of our map analysis.

Having found $F_{n}$ and $Q_{n}$, we can now construct the full map $\Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star})\big)$:
\begin{equation}
 ~\label{eq:Pn-map}
  \Pi_{n}(d^{\star})= 1-
\frac{\rho^{n-1}{g^{\star}}^{\tau}}{{\gbar}^{\tau}}\delta_{n}^{-\tau}(d^{\star})\big(1-\lambda\delta_{n}(d^{\star})\big),
\end{equation}
where we substituted $\tau = 2\tau_{s}/\tau_{d}$.
Since $d$ is the slowest variable of the system and $\tau_{d}\gg \tau_{s}$, we will also assume $\tau<1$.
\Cref{fig:Pn-map}A depicts $\Pi_{n}$ for various $n$.
Intersections of $\Pi_{n}$ with the diagonal are fixed points of the map.
\Cref{fig:Pn-map}B shows $\Pi_{2}$ with $n=2$.
Varying the synaptic strength $\gbar$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
For $\gbar<0.03$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
As $\gbar$ is increased to $\gbar \approx 0.03$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
When $\gbar > 0.03$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.

From \cref{eq:Pn-map} it is evident that $\Pi_{n}$ is monotonically increasing with respect to $\gbar$ and also $\dstar$:
\begin{align}
  \label{eq:non-degen1}
  \dv{\Pi_{n}}{\gbar}&>0,\\[0.5ex]
  \label{eq:dPidd}
  \dv{\Pi_{n}}{\dstar}&>0,
\end{align}
and in the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
Just as $F_{n}$, curves $\Pi_{n}$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
\begin{equation}
  \lim_{\gbar \to \infty}\Pi_{n} = 1\text{ for all }n,
\end{equation}
fixed points of $\Pi_{n}$ lie in $(d_{a}, 1)$.

% \subsection{Existence and stability of fixed points of $\mathit{\Pi_{n}}$}
\subsection{Existence and stability of fixed points}
We introduce the fixed point notation $\dstar_{f}$ with $\Pi_{n}(\dstar_{f})=\dstar_{f}$.
The existence of fixed points $\dstar_{f}$ for $\gbar$ sufficiently large can be shown from the strict monotonicity of $\Pi_{n}$ with respect to $\gbar$ and $\dstar$ (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of $\Pi_{n}$ is monotonically decreasing,
\begin{equation}
  \label{eq:non-degen2}
  \left(\frac{\mathrm{d}}{\mathrm{d}\dstar}\right)^2 \Pi_{n}<0.
\end{equation}
In the limit $\dstar \to d_{a}$ the value of $\Pi_n$ decreases without bound for any $\gbar>0$.
In the limit $\gbar \to 0$, $\Pi_n$ also decreases without bound, but as $\gbar \to \infty$ values of $\Pi_n$ approach $1$.
It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some $\gbar$ large enough $\Pi_n$ intersects the diagonal.
Moreover, because $\Pi_n$ and its slope are monotonic with respect to $\dstar$, there exists some critical fixed point $(\dstar_b, \gbar_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
\begin{align}
  \Pi_{n}(\dstar_{b}; \gbar_{b}) &=\dstar_{b},\\
  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b})&=1.
\end{align}
Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(\dstar_{b}, \gbar_{b})$ map $\Pi_{n}$ has the topological normal form described by the graph of
\begin{equation}
  \label{eq:normal-form}
  x\mapsto \beta+x-x^{2},
\end{equation}
with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.

\subsection{Fold bifurcations}
Fixed points of $\Pi_n$ satisfy the fixed point equation
\begin{equation}
  \label{eq:Phi}
  \Phi_n(\dstar; \gbar)=0,
\end{equation}
where
\begin{equation}
 ~\label{eq:Phi-def}
  \Phi_{n}(d^{\star}, \gbar):=\Pi_{n}(d^{\star}, \gbar)-d^{\star}.
\end{equation}
As we have already shown, for $\gbar > \gbar_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
Solving \cref{eq:Phi} explicitly for $\dstar$ it not trivial, but solving for $\gbar$ is straightforward and given by $\gbar = G_n(\dstar)$, where
\begin{equation}
 ~\label{eq:g}
  G_{n}(d^{\star}) := g^{\star} \left(\frac{\rho^{n-1}\delta_{n}^{-\tau}(d^{\star})(1-\lambda\delta_{n}(d^{\star}))}{1-d^{\star}}\right)^{1/\tau}.
\end{equation}
Plotting $d^{\star}$ against $\gbar$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
Note the typical quadratic shape of a fold bifurcation of maps.
It is also evident that the fold bifurcations occur for increasingly smaller $\gbar$ as $n$ is increased.
Moreover, we can observe that unstable fixed points have negative values of $d^{\star}$ for $n>1$.

\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(\dstar_{b}(n), \gbar_{b}(n)\big)$, which is the global minimum of $G_{n}(\dstar_f)$:
\begin{align}
  \dstar_{b}(n) &= \operatorname{argmin} G_{n}(\dstar_{f}),\\
  \gbar_{b}(n)  &= \min{G_{n}(\dstar_{f})}.
\end{align}
Function $G_{n}$ is strictly monotonic on the respective intervals of $\dstar_f$ that correspond to the stable and unstable fixed points, that is
\begin{align}
  \dv{G_n}{\dstar_f}& < 0, \text{ for } \dstar_f>\dstar_b(n) \text{ stable},\\[0.5ex]
  \dv{G_n}{\dstar_f}& > 0, \text{ for } \dstar_f<\dstar_b(n) \text{ unstable},
\end{align}
which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $\dstar_f$.
Because we are primarily interested in the stable fixed points, we define the stable fixed point function $\dstar_f=\phi_n(\gbar)$ as
\begin{equation}
  \label{eq:phi}
  \phi_{n}(\gbar):= G_{n}^{-1}(\dstar_{f}) \text{ for } \dstar_{f}>\dstar_{b}(n).
\end{equation}
Function $\phi_n(\gbar)$ is also monotonic, and is therefore straightforward to compute numerically via root-finding.
Here we use the Python package Pynverse~\citep{pynverse} for that purpose.

Having found the stable fixed points $\dstar_f$ as a function of the coupling strength $\gbar$, we can now compute the associated cycle period.
Recall that the period is given by \cref{eq:P}, which we can be written as a function of $\gbar$:
\begin{equation}
  \label{eq:period}
  P_n(\gbar) = 2(n-1)T + 2F_n\big(\underbrace{\phi_n(\gbar)}_{\dstar_f}, \gbar\big),
\end{equation}
where map $F_n$ (\cref{eq:Fn-map}) calculates the inter-burst-interval $\delt$ given a stable fixed point $\dstar_f=\phi_n(\gbar)$.
We plot the predicted period $P_n(\gbar)$ versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
For $n>1$ our map $\Pi_n$ accurately predicts the period.
When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for $n=1$ (see \cref{fig:release-delay}), since here $\gbar$ is not sufficiently strong to guarantee the validity of our release condition (\cref{eq:release}).

It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\gbar$.
This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\gbar), \gbar)=0$ in \cref{eq:Phi}. For $\dstar_f=\phi_n(\gbar)>d_b(n)$ we get:
\begin{equation}
  \label{eq:dstardg}
  \dv{\phi_n}{\gbar} = -\frac{\pdv*{\Phi_n}{\gbar}}{\pdv*{\Phi_n}{\dstar}} =
  \frac{\pdv*{\Pi_n}{\gbar}}{1-\pdv*{\Pi_n}{\dstar}}>0.
\end{equation}
The inequality follows from $\pdv*{\Pi_n}{\gbar}>0$ and the fact that $\pdv*{\Pi_n}{\dstar}<1$ for $\dstar>d_b(n)$.
\Cref{eq:dstardg} allows us to explain why the period $P_n$ increases with $\gbar$, as seen in \cref{fig:folds}B.
Differentiating $P_n$ gives:
\begin{equation}
  \label{eq:dPdg}
  \dv{P_{n}}{\gbar} = 2\grad F_n(\dstar_f, \gbar) \cdot
                      \begin{bmatrix}\pdv*{\phi_n}{\gbar}\\[0.5ex] 1\end{bmatrix}>0,
\end{equation}
where the partial derivatives of $F_n(\dstar_f, \gbar)$ are:
\begin{align}
  \pdv{F_n}{\dstar_f} &= \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar_f)}>0,\\[0.5ex]
  \pdv{F_n}{\gbar}  &= \frac{\taus}{\gbar}>0.
\end{align}
\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation:
Increasing the coupling strength between the neurons leads to overall stronger inhibition of the quiet cell, which delays its release and leads to a longer cycle period.
The latter allows more time for the synapse to depress in the free phase and recover in the quiet phase, resulting in overall larger values of $\dstar_f$, that is weaker depression at the burst onset.

While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the free phase contains exactly $n$ spikes.
As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n-n$ bursts exists only on certain parameter intervals of $\gbar$.
In the last sub-section we will analyse the mechanisms that guide how the stable $n-n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\gbar$ where such solutions exist.

% TODO: Need to find a better sub-section title that doesn't include 'period increment'
\subsection{Period increment bifurcations with co-existent attractors}
Let $\gbar_+(n)$ and $\gbar_-(n)$ denote the left and right parameter borders on $\gbar$ where stable $n-n$ solutions exist.
That is, as $\gbar$ is increased stable $n-n$ solutions are created at $\gbar_+(n)$ and destroyed at $\gbar_-(n)$.
When $\gbar$ is reduced beyond $\gbar_+(n)$, $n-n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\gbar$ is increased beyond $\gbar_-(n)$, $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
Let us briefly recap our observations regarding $\gbar_+(n)$ and $\gbar_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
For $n>1$ there are the following relations:
\begin{align}
  \gbar_+(n) &< \gbar_-(n)\label{eq:easy1},\\
  \gbar_+(n) &< \gbar_+(n+1)\text{ and } \gbar_-(n)<\gbar_-(n+1)\label{eq:easy2},\\
  \gbar_+(n+1) &< \gbar_-(n)\label{eq:coexistence},\\
  \gbar_-(n+1) - \gbar_+(n+1) &< \gbar_-(n) - \gbar_-(n)\label{eq:robustness}.
\end{align}
\Cref{eq:easy1,eq:easy2} are self-explanatory.
\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n-n$ and $(n+1)-(n+1)$ solutions.
\Cref{eq:robustness} implies that the parameter interval on $\gbar$ of $n-n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
All of the above relations are reminiscent of the period increment bifurcations with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g. see][]{gardini2012,tramontana2012,avrutin2011,gardini2012}.
While our maps $\Pi_n$ are fully continuous, the above observation suggests that
a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
We will explore what such a map might look like in the discussion.

Let us now find algebraic equations that will allow us to calculate the critical parameters $\gbar_+(n)$ and $\gbar_-(n)$ associated with the period increment bifurcations.
% BUG: Maybe don't call it period-increment here?
Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\gbar$:
\begin{equation}
  \dv{P_{n}}{\gbar}=2\dv{F_n(\phi_n(\gbar), \gbar)}{\gbar}>0,
\end{equation}
that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the quiet cell, and $\delt$ becomes larger.
Once $\delt=T$, the free cell can produce another spike and the solution bifurcates into a $(n+1)-(n+1)$ solution.
Note, however, that at $\gbar_+(n)$ the bifurcation into a $(n-1)-(n-1)$ does not occur when $\delt=0$.
Here the mechanism is different: A sufficient reduction of $\gbar$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the quiet cell to be released one spike earlier.

Using the above reasoning we can now formulate the conditions for both bifurcations at $\gbar_+(n)$ and $\gbar_-(n)$.
As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $\dstar_f=\phi_n(\gbar)$ (\cref{eq:phi}).
At the right bifurcation border $\gbar_-(n)$ we have $\delt=T$, and after substituting our $F_{n}$-map (\cref{eq:Fn-map}) this translates into
\begin{equation}
  F_n(\phi_n(\gbar), \gbar) = T,
\end{equation}
which lets us define a function
\begin{equation}
  \label{eq:R}
  R_{n}(\gbar):=F_n(\phi_n(\gbar), \gbar)-T,
\end{equation}
whose root is the desired right bifurcation border $\gbar_-(n)$.
In case of the left bifurcation border at $\gbar_+(n)$ the release condition is satisfied just before the free cell has produced its $n$th spike, and after the depression variable has been reset $n-1$ times, which gives the condition
\begin{equation}
  \gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} = \gstar,
\end{equation}
and can be rewritten as a function
\begin{equation}
  \label{eq:L}
  L_{n}(\gbar):=\gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} -\gstar,
\end{equation}
whose root is $\gbar_+(n)$.
Both $R_{n}$ and $L_{n}$ are increasing with respect to $\gbar$, which makes finding their roots numerically straightforward.

\Cref{fig:final-bif} shows the period $P_n(\gbar)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\gbar \in [\gbar_+(n),\gbar_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
Note that the width of $n-n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
That is, bursts with more spikes occur on increasingly smaller intervals of $\gbar$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
We also note the occurrence of bi-stability between pairs of $n-n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in \cref{eq:coexistence}.

As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate for $n>1$.
Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be $\gbar \approx 0.592\si{mS/cm^2}$ in \cref{fig:release-delay}.
The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\gbar_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
However, even for branches of large $n-n$ solutions there is a mismatch between the bifurcation borders.
Presumably our assumptions on the time scales of $w$ and $s$ dynamics do not hold here, and can only be captured by more complex approximations.
Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.

\section{Discussion}
% PROBLEM SUMMARY
Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming~\citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
Mathematical modelling can shed light on the underlying mechanisms that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.

% MAIN RESULTS
To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression.
When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n-n$ burst patterns.
Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n-n$ solutions respectively.
Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons.
Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n-n$ burst solutions of the full two-cell system of ODEs.
The results from our one-dimensional map match excellently with numerical simulation of the full network.
Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.

% FURTHER METHOD IDEAS
We have studied $n-n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes.
It is conceivable that our map construction can be extended to also capture such $m-n$ solutions.
Remember, in the case of symmetrical coupling with $n-n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other.
To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$.
While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}.
Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons.
As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses. 
In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.

In tadpoles, struggling is believed to be initiated by an increase in the firing frequency of reciprocally inhibitory commisural interneurons, which has been hypothesised to lead to stronger synaptic depression of inhibition and result in the iconic anti-phase bursting \citep{li2007}.
It would therefore be interesting to study how varying the cell intrinsic firing period $T$ could affect the network rhythm.
While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying $T$.
Recall that $T$ is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters.
This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult.
A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting in this scenario.

% LIMITATION: SPIKE MAP
Our simulations of the network showed that $n-n$ solutions lose robustness as their period is increased.
That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
We were able to replicate this finding by numerically finding the respective left and right borders of stable $n-n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
We have also noted the resemblance of our bifurcation diagram to one where such $n-n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}.
Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations.
It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.

% FLOW SYSTEM BIFURCATION
In addition to stable $n-n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n-n$ solutions.
While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.
However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
% Should be possible to use averaging to reduce the system.

% BIOLOGICAL IMPORTANCE OF DEPRESSION
We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.
This result is in line with the idea that one role of synaptic depression in the nervous system may be to allow a finite size neuronal network to participate in different tasks by producing a large number of rhythms~\citep{bose2011, jalil2004, li2007}.
To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength, which can occur through the process of learning.
Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.

\section*{Conflict of Interest Statement}
The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

\section*{Author Contributions}
MO and CH contributed to conception and design of the study.
MO performed numerical computation and analysis.
All authors contributed to manuscript writing and revision.

\section*{Funding}
This work was supported by the Wellcome Trust Doctoral Training Programme in Neural Dynamics, Grant no. 099699/Z/12/Z.

\section*{Acknowledgements}
The first author thanks the Wellcome Trust for financial support of his Ph.D. study.
We thank Alan Champneys for sharing his insights on non-continuous maps during the course of this research.
We are also grateful to Alan Roberts and Stephen R. Soffe for their comments on earlier versions of the manuscript.

\section*{Data Availability Statement}
The datasets generated for this study are available on request to the corresponding author.

% \bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities
\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles

\bibliography{bibliography.bib}

\section*{Figure captions}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/nullclines-uncoupled.pdf}
  \caption{Periodic solution of relaxation-oscillator model neuron. $\bm{\mathrm{(A)}}$ Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue, $v_\infty$) and $w$-nullcline (orange, $w_\infty$). Unstable fixed point $p_{f}$ is indicated by an orange dot. $\bm{\mathrm{(B)}}$ Corresponding voltage trace $v(t)$ of an action potential.~\label{fig:nullclines}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/depression-traces.pdf}
  \caption{Solution profiles of a $4-4$ burst. $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange). $\bm{\mathrm{(B)}}$ Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell 1.~\label{fig:depression-traces}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/burst-sols.pdf}
  \caption{Voltage traces of both cells of numerically stable solutions for increasing values of the coupling strength $\gbar$ (increasing top to bottom).~\label{fig:burst-sols}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/bif-diagram.pdf}
  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for increasing coupling strength $\gbar$. $\bm{\mathrm{(A)}}$ Period of stable solutions. Dashed lines show the interval between the $5-5$ and the suppressed solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals of $\gbar$. $\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in $\mathrm{(A)}$. Long $ISI$s are associated with the quiet phase of a burst, short $ISI$s with the free phase. During the free phase, $ISI$s are of approximately constant duration $T$.\label{fig:bif-diagram}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/nullclines-coupled.pdf}
  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar s$. For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange point). Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until $p_{f}$ changes stability (half orange,  half blue point) at some critical total conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
  \caption{Numerically computed values of the release delay for varying $\gbar$. Each of the three branches (A, B, C) also shows the timecourse of the total synaptic conductance $\gbar s$ of a sample stable solution of both cells (blue and orange), as well as the release conductance $g^{\star}$ (dashed green line). $\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution. Here the quiet cell only spikes after a significant release delay. $\bm{\mathrm{(B)}}$ Branch with a long release delay associated with a subset of $2-2$ solutions. Here the release condition is briefly satisfied after the first spike of cell 1. This does not cause firing of cell 2, which only occurs after the second spike of cell 1. $\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is approximately zero and the release condition is sufficient for firing of cell 2.
   ~\label{fig:release-delay}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/free-quiet.pdf}
  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution. $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).  The grey patches depict inter-burst-intervals $\delt$. $\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$. $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/delta-t.pdf}
  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$. Each continuous branch is associated with a stable $n-n$ burst solution. Increasing $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx T$.~\label{fig:delta-t}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/FQ-map.pdf}
  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/Pn-map.pdf}
  \caption{Map $\Pi_{n}:d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$ at $\gbar=0.6$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$. The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{fig/folds.pdf}
  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves) and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$. $\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the corresponding solution period from numerical integration of the system of ODEs (orange).~\label{fig:folds}}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
\end{figure}

\end{document}

### 2022-01-26 tex/supplemental.tex
Initial commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when producing your supplementary material for your Frontiers article.                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 2.5 Generated 2018/06/15 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%

\documentclass[utf8]{frontiers_suppmat} % for all articles
\usepackage{url,hyperref,lineno,microtype}
\usepackage[onehalfspacing]{setspace}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{xr}
\externaldocument{draft}

\renewcommand{\d}{\mathrm{d}}
\renewcommand{\k}{\mathrm{K}}
\newcommand{\ca}{\mathrm{Ca}}
\newcommand{\na}{\mathrm{Na}}
\newcommand{\leak}{\mathrm{L}}
\newcommand{\dstar}{d^\star}
\newcommand{\gstar}{g^\star}
\newcommand{\gbar}{\bar g}
\newcommand{\delt}{\Delta t}
\newcommand{\taus}{\tau_s}
\newcommand{\dn}{\delta_n}
\newcommand{\taud}{\tau_d}

% Leave a blank line between paragraphs instead of using \\

\begin{document}
\onecolumn
\firstpage{1}

\title[Supplementary Material]{{\helveticaitalic{Supplementary Material}}}

\maketitle

\section{Model equations and parameters}
The asymptotic functions $m_{\infty}$ and $w_{\infty}$ for the calcium and potassium conductances, respectively, are given by
\begin{align}
  m_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{A})/v_{B}\right)}\right),\\
  w_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{C})/v_{D}\right)}\right).
\end{align}
Model parameters were adapted from~\cite{bose2011} and are given in \cref{tab:pars}:
\begin{table}[h]
  \caption{Default parameters for coupled Morris-Lecar model.~\label{tab:pars}}
  \centering
  \begin{tabular}{ll}
    Parameter & value\\
    \hline
              & \\
    $g_{\leak}$ & 0.15 \si{mS/cm^2}\\
    $g_{\ca}$ & 0.3 \si{mS/cm^2}\\
    $g_{\k}$ & 0.6 \si{mS/cm^2}\\
    $v_{\leak}$ & -50 mV\\
    $v_{\ca}$ & 100 mV\\
    $v_{\k}$ & -70 mV\\
    $v_{A}$ & 1 mV\\
    $v_{B}$ & 14.5 mV\\
    $v_{C}$ & 4 mV\\
    $v_{D}$ & 15 mV\\
    $I$ & 6 \si{\mu A/cm^2}\\
    $\tau$$_{w}$ & 100 ms\\
    $\tau$$_{d}$ & 1000 ms\\
    $\tau$$_{s}$ & 100 ms\\
    $v_{\theta}$ & 0 mV\\
    $v_{s}$ & -80 mV\\
    $\lambda$ & 0.5\\
    $T$ & 217 ms\\
    $\gstar$ & 0.03804 \si{mS/cm^2}\\
  \end{tabular}
\end{table}

\section{Computing bifurcation diagram numerically}\label{appendix2}
The bifurcation diagram of stable $n-n$ solutions of the two-cell network in \cref{fig:bif-diagram} is obtained numerically as follows:
We initialise the coupling strength at parameter values associated with one type of $n-n$ solution, that is we choose the values $\bar g = 0.4, 0.7, 0.8, 0.9, 0.98$ for the $1-1$, $2-2$, $3-3$, $4-4$, and $5-5$ solutions respectively.
For each $\bar g$ the system is then numerically integrated sufficiently long for any transients to fully subside.
We then identify one period of the solution by finding the first return of the depression variable $d_{1}$.
That is, we choose some value $d_{k}$ at a spike time $t_{k}$, and by iterating from spike to spike find some subsequent value $d_{k+1}$ at spike time such that $|d_{k+1}-d_{k}|<\epsilon$.
If a periodic solution of type $n-n$ is found in such way, $\bar g$ is step-wise increased/decreased, and the above algorithm is repeated.
Otherwise, the set of all previously found solutions and the corresponding values $\bar g$ are returned.

Note that applying conventional methods of numerical continuation is not straightforward for our model, as the discontinuous resets in \cref{eq:s-reset} and~\eqref{eq:d-reset} make the root finding challenging~\citep[e.g. see][ for continuation methods]{kuznetsov2004}.

% \bibliographystyle{frontiersinSCNS_ENG_HUMS} %  for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
\bibliography{bibliography.bib}

\end{document}

### 2022-01-26 tex/supplementary_derivations.tex
Initial commit

\documentclass[12pt,authoryear]{elsarticle}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{soul}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[textsize=tiny]{todonotes}
\usepackage{soul}
\usepackage{appendix}
\usepackage{physics}

% Define better ref abbreviations
\usepackage{cleveref}
\usepackage{sectsty}
\sectionfont{\fontsize{13}{15}\selectfont\centering}
\subsectionfont{\normalfont\fontsize{12}{15}\selectfont\textit}

\renewcommand{\d}{\mathrm{d}}
\newcommand{\dstar}{d^\star}
\newcommand{\gstar}{g^\star}
\newcommand{\gbar}{\bar g}
\newcommand{\phin}{\phi_n}
\newcommand{\Phin}{\Phi_n}
\newcommand{\delt}{\Delta t}
\newcommand{\taus}{\tau_s}
\newcommand{\dn}{\delta_n}
\renewcommand{\P}{\Pi_n}
\newcommand{\F}{F_n}
\newcommand{\Q}{Q_n}

\journal{Journal of Theoretical Biology}

% This removes the horizontal lines around abstract
\makeatletter
  \long\def\pprintMaketitle{\clearpage
  \iflongmktitle\if@twocolumn\let\columnwidth=\textwidth\fi\fi
  \resetTitleCounters
  \def\baselinestretch{1}%
  \printFirstPageNotes
  \begin{center}%
 \thispagestyle{pprintTitle}%
   \def\baselinestretch{1}%
    \Large\@title\par\vskip18pt
    \normalsize\elsauthors\par\vskip10pt
    \footnotesize\itshape\elsaddress\par\vskip36pt
    % \hrule\vskip12pt
    % \ifvoid\absbox\else\unvbox\absbox\par\vskip10pt\fi
    % \ifvoid\keybox\else\unvbox\keybox\par\vskip10pt\fi
    % \hrule\vskip12pt
    \end{center}%
  \gdef\thefootnote{\arabic{footnote}}%
  }
\makeatother

\begin{document}

\begin{frontmatter}

\title{A scalar Poincaré map for struggling in \textit{Xenopus} tadpoles: Supplemental Information}

\author{Mark Olenik$^{1}$}
\ead{mark.olenik@gmail.com}
\address{$^{1}$School of Biological Sciences, University of Bristol, Bristol BS81TQ, United Kingdom}
\author{Conor Houghton$^{2}$\corref{mycorrespondingauthor}}
\address{$^{2}$School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, University of Bristol, Bristol BS81UB, United Kingdom}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{conor.houghton@bristol.ac.uk}

\end{frontmatter}

\section{Explicit map $\Pi_{n}$}

\begin{align}
  \rho &= e^{-T/\tau_{d}}
\end{align}

\noindent
Predicted period from $\Pi_{n}$:
\begin{equation}
 ~\label{eq:P}
  P=2(\Delta t + (n-1)T),
\end{equation}

\noindent
Map $\psi(d_{k})$ computes the value of $d$ at the next spike:
\begin{equation}
  \psi(d_{k}):= \lambda\rho d_{k} + (1-\rho)~\label{eq:map-d},
\end{equation}

\noindent
Value of $d$ at cycle start associated with suppressed solution:
\begin{equation}
 ~\label{eq:dsup}
  d_{s}=\frac{1-\rho}{1-\lambda\rho},
\end{equation}

\noindent
Left domain boundary of $\Pi_{n}$
\begin{equation}
  d_{a}(n)=-\frac{(1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}}{ (\lambda \rho)^{n-1} }\leq 0~\label{eq:da}.
\end{equation}
Release condition:
\begin{equation}
 ~\label{eq:release}
  \bar gs=g^{\star}
\end{equation}

\subsection{Map $\delta_{n}$}
This equation predicts $d$ after $n$ spikes:
\begin{equation}
 ~\label{eq:delta-map}
  \delta_{n}(d^{\star}) = {(\lambda \rho)}^{n-1} d^{\star} + (1-\rho)\sum_{i=0}^{n-2}{(\lambda \rho)}^{i}.
\end{equation}
Map $\delta_{n}(\dstar)$ has a root for $\dstar=d_{a}$, where
\begin{equation}
  d_{a}(n)=-\frac{(1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}}{ (\lambda \rho)^{n-1} }\leq 0.
\end{equation}
The fixed point is $\dstar=d_{s}$ and given by:
\begin{equation}
  d_{s}=\frac{1-\rho}{1-\lambda\rho}.
\end{equation}
Derivative computes as
\begin{equation}
  \dv{\dn}{\dstar} = {(\lambda\rho)}^{n-1}.
\end{equation}

\subsection{Map $F_{n}$}
\begin{equation}
 ~\label{eq:Fn-map}
  F_{n}:=\tau_{s}\ln{\left(\frac{\bar g }{g^{\star}} \delta_{n}(d^{\star})\right)}= \Delta t.
\end{equation}
Since for $\dstar>d_{a}$ we have $\delta_{n}(\dstar)>0$, map $F_{n}$ is also defined only for $\dstar>d_{a}$.
Partial derivatives are
\begin{align}
  \pdv{\F}{\dstar} &= \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar)}>0\\
  \nonumber\\
  \pdv{\F}{\gbar}  &= \frac{\taus}{\gbar}>0
\end{align}

\subsection{Map $Q_{n}$}
\begin{equation}
 ~\label{eq:Qn-map}
  Q_{n}(\Delta t):=1- (1- \lambda d_{n})e^{-(2\Delta t+(n-1)T)/\tau_{d}}.
\end{equation}

with
\begin{equation}
 ~\label{eq:dn}
  d_{n} = \frac{g^{\star}}{\bar g} e^{\Delta t/\tau_{s}}.
\end{equation}

\subsection{Map $\Pi_{n}$}
\begin{align}
  \Pi_{n}(d^{\star})&= 1-
\frac{\rho^{n-1}{g^{\star}}^{\tau}}{{\bar g}^{\tau}}\delta_{n}^{-\tau}(d^{\star})\Big(1-\lambda\delta_{n}(d^{\star})\Big)\\
  \nonumber\\
  \frac{\mathrm{d}\Pi_{n}}{\mathrm{d}d^{\star}} &= \frac{\rho^{n-1}{g^{\star}}^{\tau}}{\bar g^{\tau}}\Big(\tau \delta_{n}^{-(\tau+1)}(d^{\star})+\lambda(1-\tau) \delta_{n}^{-\tau}(d^{\star})\Big)\\
  \nonumber\\
  \frac{\mathrm{d}\Pi_{n}}{\mathrm{d}\bar g} &= \tau\frac{\rho^{n-1}{g^{\star}}^{\tau}}{\bar g^{\tau+1}}\delta_{n}^{-\tau}(d^{\star})\Big(1-\lambda\delta_{n}(d^{\star})\Big)
\end{align}

\noindent
Implicit function for fix points of $\Pi_{n}$, satisfied at $(d^{\star}_{f}, \bar g_{f})$:
\begin{align}
  \Phi_{n}(d^{\star}; \bar g):&=\Pi_{n}(d^{\star}; \bar g)-d^{\star}=0,\\
  \nonumber\\
  \frac{\partial \Phi_{n}}{\partial d^{\star}} &= \frac{\mathrm{d} \Pi_{n}}{\mathrm{d}d^{\star}} - 1 \neq 0 \quad (< 0?)\\
  \nonumber\\
  \frac{\mathrm{d}\Phi_{n}}{\mathrm{d}\bar g} &= \frac{\mathrm{d}\Pi_{n}}{\mathrm{d}\bar g} > 0
\end{align}

\noindent
Fixed points, essentially the inverse of $d_{f}^{\star}=\phi_{n}(\bar g_{f})$. For a fixed point $d_{f}^{\star}$ compute corresponding $\bar g_{f}$:
\begin{equation}
  \bar g_{f} = G_{n}(d^{\star}_{f}) := g^{\star} \left(\frac{\rho^{n-1}\delta_{n}^{-\tau}(d^{\star}_{f})(1-\lambda\delta_{n}(d^{\star}_{f}))}{1-d^{\star}_{f}}\right)^{1/\tau}.
\end{equation}

\section*{Existence and stability of fixed points of $\Pi_{n}$}
As $\gbar$ is increased maps $\Pi_{n}$ move up the plane, colliding the diagonal tangentially, which creates two fixed points, one stable and one unstable.
We will show below that these fixed points are created by a fold bifurcation of maps, and that they exist for a sufficiently large coupling strength $\gbar>\gbar_{b}(n)$, where $\gbar_{b}(n)$ is the critical value of the parameter where the fold bifurcation occurs for each map $\Pi_{n}$.

Fixed points of $\Pi_{n}$ satisfy the fixed point equation
\begin{equation}
  \Phi_{n}(\dstar; \gbar)= \Pi_{n}(\dstar; \gbar) - \dstar = 0.
\end{equation}
It is straightforward to show that the slope of $\Phi_{n}$ with respect to $\dstar$ is monotonically decreasing,
\begin{equation}\label{eq:non-degen1}
  \frac{\d^{2}\Phi_{n}}{\d{(d^{\star})}^{2}}<0,
\end{equation}
and because in the limit of the left domain boundary $\dstar \to d_{a}$ the slope is positive,
\begin{equation}
  \lim_{\dstar \to d_{a}}\dv{\Phin}{\dstar} = \infty,
\end{equation}
it follows that for $\dstar$ large enough $\Phin$ has zero slope and a
global maximum.
Moreover, since $\Phin$ is monotonic with respect to $\gbar$,
\begin{equation}\label{eq:non-degen2}
  \frac{\d \Phi_{n}}{\d \gbar}>0,
\end{equation}
for $\gbar$ sufficiently large the maximum of $\Phin$ will align tangentially with the abscissa at some critical fixed point $(\dstar_{b}, \gbar_{b})$.
For $\gbar > \gbar_{b}$ two roots of $\Phin$ arise with slopes of opposite signs, respectively.
Thus at $(\dstar_{b}, \gbar_{b})$ we have
\begin{align}
  \Phi_{n}(\dstar_{b}; \gbar_{b}) &=0,\\
  \frac{\d}{\d \dstar}\Phi_{n}(\dstar_{b}; \gbar_{b})&=0,
\end{align}
or equivalently
\begin{align}
  \Pi_{n}(\dstar_{b}; \gbar_{b}) &=\dstar_{b},\\
  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b})&=1.
\end{align}
Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(\dstar_{b}, \gbar_{b})$ map $\Pi_{n}$ has the topological normal form described by the graph of
\begin{equation}
x\mapsto \beta+x-x^{2},
\end{equation}
with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.

\section*{Why \boldmath{$\dstar_{f}$} increases with \boldmath{$\gbar$}}
As we have shown for $\gbar>\gbar_{b}(n)$ there exists a local relationship $\dstar_{f}=\phi_{n}(\gbar)$.
We can compute the slope of $\phi_{n}(\gbar)$ using implicit differentiation:
\begin{equation}
  \dv{\phin}{\gbar} = -\frac{\pdv*{\Phin}{\gbar}}{\pdv*{\Phin}{\dstar}}=
  -\frac{\pdv*{\P}{\gbar}}{\pdv*{\P}{\dstar}-1}
\end{equation}
As we have seen in the fold bifurcation plot, the slope of $\phin(\gbar)$ is positive for the unstable, and negative for the stable fixed points, respectively.
Both inequalities follow from normal form of the fold bifurcation:
\begin{equation}
x\mapsto \beta+x-x^{2},
\end{equation}
with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.

% NOTE: It's also trivial to prove the slopes without using the normal form. The nominator is always positive, the denominator is negative for the stable since the slope of Phi is mon. decreasing, and the stable fp is larger than the unstable, and at the fold bif the slope of Phi is zero.
% TODO: Ask Conor whether the normal form derivation is sufficient here.

\section*{Why slope of period decreases with \boldmath{$\gbar$}}
\emph{NOTE: Will leave this out, since the decrease of the slope of the period isn't really interesting, what's interesting is how it changes with $n$, and that is hard to show.}

Recall that the period from the map is computed by
\begin{align}
  P_{n}(n)&= (n-1)T + \delt\\
          &= (n-1)T + F_{n}\big(\phin^{-}(\gbar), \gbar\big)
\end{align}
We will show below that
\begin{equation}
  \dv[2]{P_{n}}{\gbar} < 0
\end{equation}
We can calculate the derivative as
\begin{align}
  \dv{P_{n}}{\gbar} &= \dv{F_{n}(\phin(\gbar), \gbar)}{\gbar} \\[0.5ex]
                    &= \grad F_{n} \cdot \dv{\gbar}\begin{bmatrix}\phin^{-}\\[0.5ex] \gbar\end{bmatrix}\\[0.5ex]
                    &= \pdv{\F}{\dstar}\dv{\phin^{-}}{\gbar} + \pdv{\F}{\gbar}\\[0.5ex]
                    &>0
\end{align}
The last inequality follows from the fact that all terms are positive, as we've shown somewhere earlier.
Then the second derivative is given by
\begin{align}
  \dv[2]{P_{n}}{\gbar}&=\dv{\gbar}\Big(\dv{F_{n}(\phin(\gbar), \gbar)}{\gbar} \Big)\\[0.5ex]
                      &=\dv{\gbar}\Big(\grad F_{n} \cdot \begin{bmatrix}\dv*{\phin}{\gbar}\\1 \end{bmatrix}\Big)\\[0.5ex]
                      &= \dv{\gbar}\grad F_{n} \cdot \begin{bmatrix}\dv*{\phin}{\gbar}\\ 1\end{bmatrix} + \grad F_{n}\cdot \begin{bmatrix}\dv*[2]{\phin}{\gbar}\\0\end{bmatrix}\\[0.5ex]
  &=\dv[2]{F_{n}}{\gbar} + \pdv{F_{n}}{\dstar}\dv[2]{\phin}{\gbar}\\[0.5ex]
  &< 0
\end{align}
The last inequality follow from the following
\begin{align}
  \pdv{\gbar}\dv{F_{n}}{\gbar}<0\\[0.5ex]
  \pdv{F_{n}}{\dstar}>0
\end{align}
and the fact that
\begin{equation}
  \dv[2]{\phin}{\gbar}<0
\end{equation}
The latter inequality is easy to show but also follows from the fold bifurcation, i.e. $\dv*{(2\sqrt(\beta)^{-1})}{\beta}<0$.

\section*{Why slope of period decreases with \boldmath{$n$}}

\section*{Period adding/subtracting bifurcations}
So far we have assumed that both neurons produce exactly $n$ spikes in a burst, irrespective of the coupling strength.
As we have seen in the numerical bifurcation diagram branches of stable $n-n$ solutions exist on increasingly smaller intervals of $\gbar$ with increasing $n$.
We can once again use the release condition to derive the exact values of $\gbar$ where these bifurcations occur.
There are two bifurcations for each branch, on the left there's period subtraction, on the right period-adding.

We've already briefly touched on the period-adding bifurcation.
Remember, we have shown
\begin{equation}
  \dv{P_{n}}{\gbar}=\dv{\delt}{\gbar}>0,
\end{equation}
that is, as the coupling strength increases, it takes longer for the total synaptic conductance to cross the release conductance, which delay the release of the quiet cell, thus $\delt$ becomes larger.
Once $\delt=T$, the free cell can produce another spike, thus we have period-adding (ref), and the solution bifurcates into a stable $(n+1)-(n+1)$.
Note that on the left side the period-subtraction bifurcation into a $(n-1)-(n-1)$ does not occur when $\delt=0$.
Here the mechanism is different: A sufficient reduction of $\gbar$ causes the total synaptic conductance to drop below the release conductance in the previous $ISI$, which allows the quiet cell to be released one spike earlier.

Using the above reasoning we can now formulate the conditions for both period-adding and -subtracting bifurcations.
We will only restrict ourselves to the analysis of the stable fixed points.
In case of period adding, we have $\delt=T$, and after substituting our $F_{n}$-map this translates into
\begin{equation}
   R_{n}(\gbar):=\underbrace{\taus \ln\big[\frac{\gbar}{\gstar}\delta_{n}\big(\phi_{n}^{-}(\gbar)\big)\big]}_{F_{n}\big(\phi_{n}^{-}(\gbar)\big)} -T =0.
\end{equation}
In case of period subtraction, the release condition is satisfied exactly at the $n$th spike time, which translates into
\begin{equation}
  L_{n}(\gbar):=\gbar \delta_{n-1}\big(\phi_{n}^{-}(\gbar)\big)e^{-T/\taus} -\gstar = 0.
\end{equation}
Finding the roots of $L_{n}$ and $R_{n}$ gives us the desired period adding and subtracting bifurcations, respectively.

It is easy to show that the period increment and decrement bifurcations for each $n$ are unique, since both $R_{n}$ and $L_{n}$ are monotonous with respect to $\gbar$:
\begin{align}
  \dv{\gbar}R_{n}(\gbar) = \dv{\gbar}F_{n}(\phin(\gbar), \gbar) = \grad F_{n} \cdot \begin{bmatrix}\dv*{\phin^{-}}{\gbar}\\ 1\end{bmatrix} > 0.
\end{align}

\section*{Computing bifurcation diagram numerically}
The bifurcation diagram of stable $n-n$ solutions of the two-cell network in \cref{fig:bif-diagram} is obtained numerically as follows:
We initialise the coupling strength at parameter values associated with one type of $n-n$ solution, that is we choose the values $\bar g = 0.4, 0.7, 0.8, 0.9, 0.98$ for the $1-1$, $2-2$, $3-3$, $4-4$, and $5-5$ solutions respectively.
For each $\bar g$ the system is then numerically integrated sufficiently long for any transients to fully subside.
We then identify one period of the solution by finding the first return of the depression variable $d_{1}$.
That is, we choose some value $d_{k}$ at a spike time $t_{k}$, and by iterating from spike to spike find some subsequent value $d_{k+1}$ at spike time such that $|d_{k+1}-d_{k}|<\epsilon$.
If a periodic solution of type $n-n$ is found in such way, $\bar g$ is step-wise increased/decreased, and the above algorithm is repeated.
Otherwise, the set of all previously found solutions and the corresponding values $\bar g$ are returned.

Note that applying conventional methods of numerical continuation is not straightforward for our model, as the discontinuous resets in \cref{eq:s-reset} and~\eqref{eq:d-reset} make the root finding challenging~\citep[e.g. see][ for continuation methods]{kuznetsov2004}.

\bibliographystyle{model5-names}
\bibliography{bibliography.bib}
\end{document}

### 2022-01-26 scripts/compute_bifdat.py

@@ -1,0 +1,45 @@
+"""Script to numerically compute bifurcation diagram."""
+
+import argparse
+import pickle
+
+import pandas as pd
+
+from poincare_map import ode
+
+
+def compute_bif_diagram(xppfile: str, echo: bool = True) -> pd.DataFrame:
+    nsteps = 100
+    p0s = [0.3, 0.4, 0.5, 0.52, 0.56]
+    parsteps = [0.01, 0.01, 0.005, 0.001, 0.001]
+    totals = [5000, 8000, 10000, 15000, 15000]
+    curves = []
+    for p0, step, total in zip(p0s, parsteps, totals):
+        if echo:
+            print(f"Initialising parameter at {p0}")
+        left = ode.cont(
+            xppfile, g=p0, parstep=-step, nsteps=nsteps, total=total
+        )
+        right = ode.cont(
+            xppfile, g=p0, parstep=step, nsteps=nsteps, total=total
+        )
+        if (left is not None) and (right is not None):
+            curve = (
+                left.iloc[::-1].append(right.iloc[1:]).reset_index(drop=True)
+            )
+            curves.append(curve)
+        else:
+            curves.append(None)
+    return pd.concat(curves)
+
+
+if __name__ == "__main__":
+    parser = argparse.ArgumentParser()
+    parser.add_argument("--output", help="Output file", type=str)
+    parser.add_argument(
+        "--xppfile", help="XPP ODE file", default="mlml.ode", type=str
+    )
+    args = parser.parse_args()
+
+    dat = compute_bif_diagram(args.xppfile)
+    pickle.dump(dat, open(args.output, "wb"))

### 2022-01-26 scripts/makefig.py

@@ -1,0 +1,1685 @@
+import itertools
+import multiprocessing
+import os
+import pickle
+import string
+import warnings
+from os import path
+
+import matplotlib
+import pandas as pd
+import pyxpp.pyxpp as xpp
+import scipy as sp
+from matplotlib import patches
+from matplotlib import pyplot as plt
+from matplotlib.backends.backend_pgf import FigureCanvasPgf
+from matplotlib.gridspec import GridSpec
+from matplotlib.lines import Line2D
+from pandas import DataFrame
+from scipy.misc import derivative
+from pathlib import Path
+
+from poincare_map import helpers
+from poincare_map import model
+from poincare_map import ode
+
+import numpy as np
+
+warnings.filterwarnings("ignore", category=DeprecationWarning)
+# Ignore devide by zero
+np.seterr(divide='ignore')
+np.seterr(all='ignore')
+
+rcp = matplotlib.rcParamsDefault
+plt.ioff()
+matplotlib.use('pgf')
+
+
+DATDIR = Path('data')
+FIGDIR = Path('figures/')
+if not os.path.isdir(DATDIR):
+    os.mkdir(DATDIR)
+if not os.path.isdir(FIGDIR):
+    os.mkdir(DATDIR)
+
+XPPFILE = 'mlml.ode'
+CENTER_TITLE_SIZE = 11
+FIGWIDTH = 3.85
+FIGSIZE = (FIGWIDTH, FIGWIDTH)
+FIG2by1 = (FIGWIDTH*1.4, (FIGWIDTH*1.4)/2)
+
+EQSIZE = 15                     # Font size of equaitons.
+
+rcp['figure.max_open_warning'] = 0
+rcp['axes.unicode_minus'] = False
+rcp['text.usetex'] = True
+rcp['pgf.rcfonts'] = False
+rcp['pgf.texsystem'] = 'pdflatex'
+rcp['xtick.labelsize'] = 'small'
+rcp['ytick.labelsize'] = 'small'
+rcp['axes.labelsize'] = 'x-large'
+rcp['axes.titlesize'] = 'xx-large'
+rcp['figure.titlesize'] = 'large'
+rcp['font.size'] = 9
+# Use latex preamble.
[…]

### 2022-01-26 scripts/plot_bifdiagram.py

@@ -1,0 +1,104 @@
+import pickle
+
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import pyxpp.pyxpp as xpp
+from poincare_map import model
+
+rcp = matplotlib.rcParamsDefault
+matplotlib.rcParams.update(rcp)
+plt.ioff()
+matplotlib.use('pgf')
+
+
+EQSIZE = 15                     # Font size of equations.
+CENTER_TITLE_SIZE = 11
+FIGWIDTH = 3.85
+FIGSIZE = (FIGWIDTH, FIGWIDTH)
+FIG2by1 = (FIGWIDTH*1.4, (FIGWIDTH*1.4)/2)
+
+rcp['figure.max_open_warning'] = 0
+rcp['axes.unicode_minus'] = False
+rcp['text.usetex'] = True
+rcp['pgf.rcfonts'] = False
+rcp['pgf.texsystem'] = 'lualatex'
+rcp['xtick.labelsize'] = 'small'
+rcp['ytick.labelsize'] = 'small'
+rcp['axes.labelsize'] = 'x-large'
+rcp['axes.titlesize'] = 'xx-large'
+rcp['figure.titlesize'] = 'large'
+rcp['font.size'] = 9
+# Use latex preamble.
+rcp['pgf.preamble'] = r'\usepackage{amsmath} \usepackage{siunitx}'
+
+matplotlib.rcParams.update(rcp)
+
+XPPFILE = 'mlml.ode'
+p = xpp.read_pars(XPPFILE)
+
+
+pars = model.Pars(p['g'], p['gstar'], p['lambda'])
+
+from poincare_map import ode
+# Find initial solution.
+sol = ode.run(XPPFILE, g=0., total=5000)
+lc = ode.find_lc(sol, norm=True)
+
+# lc = ode.find_lc(sol, norm=False)
+lc = ode.find_lc(sol, norm=True)
+fig, axs = plt.subplots(nrows=2)
+axs[0].plot(lc["t"], lc["v1"])
+axs[1].plot(lc["t"], lc["d1"])
+fig.savefig("tmp.pdf")
+
+
+#*
+
+# Load data
+df = pickle.load(open('data/bif-diagram.pkl', 'rb'))
+
+
+## Plot
+fig, axs = plt.subplots(ncols=2, tight_layout=True,
+                        figsize=FIG2by1)
+
+# A: Period diagram
+ax = axs[0]
+nmax = max(df['n'])
+for n in range(nmax+1)[1:]:
[…]

### 2022-01-26 scripts/plot_tauk.py

@@ -1,0 +1,203 @@
+from poincare_map import ode
+from poincare_map import helpers
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+from matplotlib.figure import Figure
+import intersect
+import tqdm
+from typing import Tuple
+import pandas as pd
+
+plt.ioff()
+
+rcp = matplotlib.rcParamsDefault
+rcp["axes.spines.right"] = False
+rcp["axes.spines.top"] = False
+matplotlib.rcParams.update(rcp)
+
+GSTAR = 0.0036
+T = 375
+
+xppfile = "odes/ml.ode"
+vnull, wnull = ode.nullclines(xppfile, gtot=GSTAR)
+v_fp, w_fp = intersect.intersection(vnull[:, 0], vnull[:, 1], wnull[:, 0], wnull[:, 1])
+v_fp = v_fp[0]
+w_fp = w_fp[0]
+
+
+def roots(x, y) -> np.ndarray:
+    return intersect.intersection(x, y, x, np.zeros(len(x)))[0]
+
+
+def calc(
+    xppfile: str,
+    v0: float = v_fp,
+    w0: float = w_fp,
+    gstar: float = GSTAR,
+    g: float = 0.5,
+    tauk: float = 100,
+    total: float = 400,  # big enough even for large g?
+    **kwargs,
+) -> pd.DataFrame:
+    """Compute solution given initial conditiosn"""
+    s0 = gstar / g
+    ics = np.array([v0, w0, s0])
+    sol = ode.run(xppfile, ics=ics, g=g, tauk=tauk, total=total, **kwargs)
+    return sol
+
+
+
+def nth_ISI(sol: pd.DataFrame, n: int = 0) -> float:
+    """Compute nth ISI."""
+    x0s = roots(sol.t, sol.v)
+    spikes = x0s[::2]
+    ISIs = np.diff(spikes)
+    return ISIs[n]
+
+
+#* spikes
+
+signs = np.sign(sol.v)
+roots = np.where(signs + np.roll(signs, 1) == 0)[0]
+
+id1 = helpers.spikes(sol.v)
+
+
+
+fig, ax = plt.subplots()
+ax.plot(sol.t, sol.v)
[…]

### 2022-01-26 src/poincare_map/helpers.py

@@ -1,0 +1,152 @@
+import numpy as np
+from typing import List, Optional, Tuple
+from matplotlib import pyplot as plt
+import matplotlib.lines as mlines
+import matplotlib.patches as mpatches
+
+
+def roots(x: np.ndarray) -> np.ndarray:
+    """Find roots using sign changes."""
+    signs = np.sign(x)
+    roots = np.where(signs + np.roll(signs, -1) == 0)[0]
+    return roots
+
+
+def spikes(x: np.ndarray) -> np.ndarray:
+    """Find spike indices using roots with positive slope."""
+
+    id1 = roots(x)
+    if len(id1) > 0:
+        grad1 = np.gradient(x)
+        return id1[grad1[id1]>0]
+    else:
+        return np.array([])
+
+
+def events(x: np.ndarray, down: bool = True) -> np.ndarray:
+    """Find indices of events where the slope of array changes its sign."""
+    grad = np.gradient(x)
+    signs = np.sign(grad)
+    direction = signs > 0 if down else signs < 0
+    sign_changes = np.where((signs + np.roll(signs, -1) == 0) & direction)[0]
+    return sign_changes
+
+
+def find_lc(x: np.ndarray, thresh: float = 1e-3) -> Optional[Tuple[int, int]]:
+    """Return start and end index of limit cycle solution."""
+    idxs = events(x)
+
+    def first_return(idxs, thresh=thresh):
+        """Compute indices of limit cycle via first periodic return."""
+
+        # Go backwards because of transients.
+        back_cross = idxs[::-1]
+        # Find crossing where norm function is small enough.
+        for _, idx in enumerate(back_cross[1:]):
+            err = abs(x[idx] - x[idxs[-1]])
+            if err < thresh:
+                return idx
+        # No section return found.
+        return None
+
+    start = first_return(idxs, thresh=thresh)
+    end = idxs[-1]
+    if start is not None:
+        return (start, end)
+    else:
+        return None
+
+
+def shift_sol(sol, shift):
+    """Shift solution by some time."""
+    P = sol[-1, 0]
+    dt = sol[1, 0] - sol[0, 0]
+    roll_by = int(shift / float(dt))
+    shifted_sol = np.roll(sol, roll_by, axis=0)
+    # Recompute time.
+    shifted_sol[:, 0] = np.linspace(0.0, P, len(shifted_sol))
[…]

### 2022-01-26 src/poincare_map/model.py

@@ -1,0 +1,473 @@
+"""Poincare map definition with methods.
+
+Module containing the most important model parameters and derived
+quantities and functions.
+"""
+
+from typing import NamedTuple, Sequence, Optional, Tuple
+
+import numpy as np
+from scipy import optimize
+from pandas import DataFrame
+from pynverse import inversefunc
+
+
+class Pars(NamedTuple):
+    """Map parameters."""
+
+    g: float = 0
+    gstar: float = 0.0036
+    period: float = 375  # Spiking period.
+    tauk: float = 100
+
+
+    @property
+    def rho(self):
+        return np.exp(-self.period / self.taud)
+
+    @property
+    def d_sup(self):
+        return (1 - self.rho) / (1 - self.Lambda * self.rho)
+
+    @property
+    def g_sup(self):
+        return self.gstar * np.exp(self.period / self.taus) / self.d_sup
+
+    @property
+    def tau(self):
+        return 2 * self.taus / self.taud
+
+
+## Convenience functions
+
+
+def alpha(pars: Pars, n: int) -> float:
+    return pow(pars.Lambda * pars.rho, n - 1)
+
+
+def beta(pars: Pars, n: int) -> float:
+    return (1 - pars.rho) * sum(
+        [pow(pars.Lambda * pars.rho, k) for k in range(int(n - 1))]
+    )
+
+
+def L2delt(pars: Pars, L: float) -> float:
+    """Get delta-t from burst length L."""
+    if L < 0:
+        return L
+    else:
+        return L % pars.period
+
+
+def L2n(pars: Pars, L: float) -> int:
+    """Get number of spikes in burst of length L."""
+    if L < 0:
+        return 0
+    else:
+        return int(L // pars.period + 1)
+
+
+def d2n(pars: Pars, d: float) -> int:
+    """Just a convenience function to find n from d."""
+    L = F_map(pars, d)
+    return L2n(pars, L)
+
+
+def d_n(pars: Pars, delt: float) -> float:
+    """Value of d at last (nth) spike time."""
+    return pars.gstar / pars.g * np.exp(delt / pars.taus)
+
+
+def d_a(pars: Pars, n: int) -> float:
+    """Leftmost bound of Pn-map domain."""
+    return -beta(pars, n) / alpha(pars, n)
+
+
[…]

### 2022-01-26 src/poincare_map/ode.py

@@ -1,0 +1,206 @@
+"""Utilities for numerical integration of XPPAUT ODEs."""
+
+import pandas as pd
+from typing import List, Optional, Tuple, Dict
+import multiprocessing
+from functools import partial
+import numpy as np
+import pyxpp.pyxpp as xpp
+from poincare_map import helpers
+
+
+def run(xppfile: str, **kwargs) -> pd.DataFrame:
+    """Run XPP ODEs and wrap result in a Pandas dataframe."""
+
+    dat = xpp.run(xppfile, **kwargs)
+    allvars = np.append("t", xpp.read_vars(xppfile))
+    return pd.DataFrame(dat, columns=allvars)
+
+
+def par_run(xppfile: str, nrand: int = 5, **kwargs) -> List[pd.DataFrame]:
+    """Randomise ICs and integrate system multiple times."""
+
+    with multiprocessing.get_context("fork").Pool() as pool:
+        futures = []
+        for idx in range(nrand):
+            ics = randics(seed=idx)
+            runfun = partial(run, uid=idx, ics=ics, **kwargs)
+            future = pool.apply_async(runfun, [xppfile])
+            futures.append(future)
+        lcs = [future.get() for future in futures]
+    return lcs
+
+
+def nullclines(xppfile: str, gtot=0, **kwargs) -> Tuple[np.ndarray, np.ndarray]:
+    """Compute nullclines."""
+
+    # NOTE You can't modify the plot parameters (xhi, xlo etc).
+    # That must be written directly into the xpp file.
+    vnull, wnull = xpp.nullclines(xppfile, g=0.0, gtot=gtot, **kwargs)
+    return vnull, wnull
+
+
+def randics(seed=0):
+    """Randomise initial conditions."""
+
+    np.random.seed(seed)
+    # FIXME: The dimensions etc should reflect the odes, fixex for now.
+    # You have to initialise auxilliary variables as well (xpp).
+    ics = np.concatenate(
+        (np.random.uniform(-50.0, 40.0, 2), np.random.uniform(0.0, 1.0, 8))
+    )
+    return ics
+
+
+# def spikes(sol: pd.DataFrame) -> Tuple[np.ndarray, np.ndarray]:
+#     """Find spike indices of both cells using depression variable."""
+
+#     id1 = helpers.events(sol.d1)
+#     id2 = helpers.events(sol.d2)
+#     return (id1, id2)
+
[…]

### 2022-02-04 tex/manuscript.tex
Rename to manuscript
Split latex document into subfiles

--- 2022-01-26 tex/draft.tex
@@
-\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and
+\documentclass[utf8, draft]{frontiersFPHY} % for Physics and Applied Maths
+% \documentclass[utf8]{frontiersFPHY} % for Physics and Applied Maths
 \usepackage{graphicx}
@@
 \usepackage{bm}
+\usepackage{subfiles}
 
 \usepackage{url,hyperref,microtype,subcaption}
-\usepackage[onehalfspacing]{setspace}
+% \usepackage[onehalfspacing]{setspace}
 \usepackage{cleveref}
@@
 
+\graphicspath{{../figures/}}
+
 % Define better ref abbreviations
-\usepackage[displaymath]{lineno}
+\usepackage{lineno}
 
+% Define some convenience commands
 \renewcommand{\d}{\mathrm{d}}
@@
   \section{}
-Short-term synaptic plasticity is found in many areas of the central
-nervous system.  In the inhibitory half-centre central pattern
-generators involved in locomotion, synaptic depression is believed to
-act as a burst termination mechanism, allowing networks to generate
-anti-phase bursting patterns of varying periods.  To better understand
-burst generation in these central patter generators, we study a
-minimal network of two neurons coupled through depressing synapses.
-Depending on the strength of the synaptic conductance between the two
-neurons, this network can produce symmetric $n-n$ anti-phase bursts,
-where neurons fire $n$ spikes in alternation, with the period of such
-solutions increasing with the strength of the synaptic conductance.
-Relying on the timescale disparity in the model, we reduce the
-eight-dimensional network equations to a fully-explicit scalar
-Poincaré burst map.  This map tracks the state of synaptic depression
-from one burst to the next and captures the complex bursting dynamics
-of the network.  Fixed points of this map are associated with stable
-burst solutions of the full network model, and are created through
-fold bifurcations of maps.  We derive conditions that describe
-period-increment bifurcations between stable $n-n$ and $(n+1)-(n+1)$
-bursts, producing a full bifurcation diagram of the burst cycle
-period.  Predictions of the Poincaré map fit excellently with
-numerical simulations of the full network model and allow the study of
-parameter sensitivity for rhythm generation.
+  Short-term synaptic plasticity is found in many areas of the central nervous system.  In
+  the inhibitory half-centre central pattern generators involved in locomotion, synaptic
+  depression is believed to act as a burst termination mechanism, allowing networks to
+  generate anti-phase bursting patterns of varying periods.  To better understand burst
+  generation in these central patter generators, we study a minimal network of two neurons
+  coupled through depressing synapses.  Depending on the strength of the synaptic
+  conductance between the two neurons, this network can produce symmetric $n-n$ anti-phase
+  bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions
+  increasing with the strength of the synaptic conductance.  Relying on the timescale
+  disparity in the model, we reduce the eight-dimensional network equations to a
+  fully-explicit scalar Poincaré burst map.  This map tracks the state of synaptic
+  depression from one burst to the next and captures the complex bursting dynamics of the
+  network.  Fixed points of this map are associated with stable burst solutions of the
+  full network model, and are created through fold bifurcations of maps.  We derive
+  conditions that describe period-increment bifurcations between stable $n-n$ and
+  $(n+1)-(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
+  Predictions of the Poincaré map fit excellently with numerical simulations of the full
+  network model and allow the study of parameter sensitivity for rhythm generation.
 
@@
 \section{Introduction}
-% DEPRESSION
-Short-term synaptic plasticity may have a role in burst activity in
-central pattern generators (CPGs).  Short-term synaptic depression is
-commonly found in neuronal networks involved in the generation of
-rhythmic movements, such as in the pyloric CPG of the spiny
-lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of
-the chick embryo~\citep{donovan1998}.  Synaptic depression modulates
-the strength of synapses in response to changes to the presynaptic
-firing frequency.  At a high neuronal firing frequency, depression
-weakens the strength of synapses and therefore reduces the magnitude
-of the postsynaptic response.  At low firing frequency, it allows
-sufficient time for the synapse to recover from depression between
-spikes, leading to a stronger postsynaptic response.  In reciprocal
-networks, synaptic depression has been shown to act as a ``switch'',
-giving rise to a wide range of network dynamics such as synchronous
-and multi-stable rhythms, as well as fine tuning the frequency of
-network oscillations~\citep{nadim2000, nadim1999, bose2011}.
-
-% Brown
-~\citet{brown1911} pioneered the idea that synaptic depression acts as
-a burst termination mechanism in reciprocally inhibitory CPGs involved
-in rhythm generation of locomotion. When one side is firing during a
-burst the other, antagonistic side, is prevented from firing by
-synaptic inhibition. However, the weakening of inhibition as a result
-of synaptic depression eventually releases the antagonistic side so
-that it starts firing, terminating the burst on the side that had
-originally been firing.  This rhythmogenesis hypothesis has been
-considered one of a handful of standard mechanisms for generating
-locomotion rhythms in
-vertebrates~\citep{reiss1962,perkel1974,friesen1994}. It has been
-proposed as an explaination of the antiphase burst rhythm in
-struggling in \textit{Xenopus} tadpoles~\citep{li2007}.
-
-~\citet{bose2011} investigated burst generation in a generic
-half-centre CPG that consists of two identical, tonically active
-Morris-Lecar~\citep{morris1981} neurons coupled through inhibitory
-depressing synapses.  Numerical simulations showed that when the
-reciprocal synaptic conductance between the two neurons is varied, the
-network produces symmetric $n-n$ anti-phase bursts, with stronger
-synaptic coupling leading to longer bursts.  They used methods from
-geometric singular perturbation theory to separate the timescales of
-the fast membrane, and the slow synaptic dynamics of the network to
-derive one-dimensional conditions necessary for the existence of
-stable $n-n$ solutions (for $n\leq 2$). According to these conditions
-the type of firing pattern largely depends on the slow depression
-dynamics of the synapses between the two neurons, and can therefore be
-predicted by knowing the strengths of the synaptic conductances of the
-two synapses.
-Thus, the scalar conditions derived in~\citet{bose2011} provide a
-method to numerically identify the type of stable $n-n$ pattern for
-any given value of the coupling strength.  However, they do not
-predict the exact period of such solutions.
-Furthermore, while they provide good arguments for the validity of
-their reduction assumptions and the resulting scalar conditions, they
-do not verify them numerically.
-
-Here we extend the previous analysis by providing a Poincaré map of
-the slow depression dynamics.  This allows us not only to predict the
-types of stable $n-n$ solutions the full network can produce, (for any
-$n$), but also to study how varying the coupling strength affects the
-period of such solutions.  To do this, we build on, and numerically
-test, the assumptions on the fast-slow timescale disparity made
-in~\cite{bose2011}.  We reduce the two-cell model to a scalar
-Poincaré map that tracks the evolution of the depression from the
-beginning of one burst to the beginning of the next burst.  Stable
-fixed points of our map are associated with stable $n-n$ burst
-solutions.  Our map construction is motivated by the burst length map
-of a T-type calcium current, utilised by~\citet{matveev2007}, which
-approximates the anti-phase bursting dynamics of a network of two
-coupled Morris-Lecar neurons.  In contrast to our model, the network
-described in the~\cite{matveev2007} paper does not contain short-term synaptic
-depression, and burst termination is instead accomplished through the
-dynamics of a slow T-type calcium current.
-
-% MAIN RESULTS AND CONCLUSIONS
-The Poincaré map derived here replicates the results from numerical
-simulations of the full two-cell ODE system: Given the strength of
-maximum conductance between the two neurons, fixed points of our map
-predict the type and period of $n-n$ patterns, the switch between
-burst solutions of different periods, as well as the occurrence of
-co-existent solutions.  In addition to proving the existence and
-stability of fixed points, our map shows that fixed points are created
-via a fold bifurcation of maps.  We also derive algebraic conditions
-that predict the period increment bifurcations that allow the switch
-between $n-n$ and $(n+1)-(n+1)$ solutions.  Because our map is fully
-explicit, it lays the framework for studying the effects of other
-model parameter on network dynamics without the need to run expensive
-numerical integrations of the ODEs.
-
-% PAPER STRUCTURE.
-This paper is organised as follows.  First, we introduce the network
-of two neurons, and describe the properties of single cell and synapse
-dynamics.  We use numerical simulations of the network to provide an
-intuition for the range of possible burst dynamics the system can
-produce.  Next, we state and justify the simplifying assumptions that
-are necessary for the map construction.  Finally, we analytically
-derive the first return map of the depression variable as well as the
-conditions that are required for stable solutions to bifurcate between
-$n-n$ and $(n+1)-(n+1)$ solutions.  We end this work with a
-discussion.
-
 \section{Materials and Methods}
-We consider a pair of identical Morris-Lecar neurons~\citep{morris1981}, with parameters adapted from~\cite{bose2011}.
-The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
-The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
-The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
-\begin{align}
-    ~\label{eq:cell-modelA}
-     \dot v_{i}&= f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}),\\
-    ~\label{eq:cell-modelB}
-     \dot w_{i} &=h(v_i,w_i).
-   \end{align}
-Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.
-Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
-\begin{equation}
- ~\label{eq:memcur}
-  f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})-g_{\leak}(v_{i}-v_{\leak}) + I.
-\end{equation}
-The currents include a constant current $I$, and three ionic currents:
-an instantaneous calcium current, a potassium current, and a leak current, with respective reversal potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances $g_{\ca}$, $g_{\k}$, and $g_{\leak}$.
-The function $h(v_{i}, w_{i})$ models the kinetics of the potassium gating variable $w_{i}$, and is given by
-\begin{equation}
-  h(v_{i}, w_{i})=\frac{w_{\infty}(v_{i})-w_{i}}{\tau_{w}}~\label{eq:h}.
-\end{equation}
-The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the \textbf{Supplementary Material S1}.
-
-The dynamics of the synaptic interactions between the neurons are governed by a synaptic gating variable $s_{i}$ and a depression variable $d_{i}$:
-\begin{linenomath}
-  \begin{align}
-    \dot s_{i} &= -s_{i}/\tau_{s}~\label{eq:dot-s},\\
-    \dot d_{i} &= (1-d_{i})/\tau_{d}~\label{eq:dot-d}.
-  \end{align}
-\end{linenomath}
-Variable $d_{i}$ describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
-Our model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
-In between spikes $s_{i}$ decays with time constant $\tau_{s}$, while $d_{i}$ recovers with time constant $\tau_{d}$.
-Because synaptic depression occurs on a much slower timescale than synaptic inhibition, we assume $\tau_{d}\gg\tau_{s}$.
-At spike time when the voltage $v_{i}$ crosses a synaptic threshold $v_{\theta}$, the synaptic variable $s_{i}$ is reset to the current value of $d_{i}$, and $d_{i}$ is scaled down by the depression strength parameter $\lambda$, where $0<\lambda<1$.
-This results in the following discontinuous reset rule on spike time:
-\begin{linenomath}
-  \begin{align}
-    s_{i} &\leftarrow d_{i}~\label{eq:s-reset},\\
-    d_{i} &\leftarrow \lambda d_{i}~\label{eq:d-reset}.
-  \end{align}
-\end{linenomath}
-The equations for the depression model were adapted from the~\citet{bose2001} model.
-These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by~\citet{tsodyks1997}.
-The original equations in~\cite{bose2001} include an exponential decay of $d_{i}$ throughout the active phase of the action potential, that is $\dot d_{i}=-d_{i}/\tau_{\beta}$ for $v_{i}>v_{\theta}$.
-To simplify the mathematical analysis we have reduced these dynamics to a single-reset event at spike time according to \cref{eq:d-reset}.
-This simplification is natural given an approximately constant duration of the active phase of an action potential, and it will become evident from our results that this simplification does not qualitatively change the dynamics of the network compared to the original equations, where depression dynamics are described by an exponential decay.
-
-When the cells are uncoupled ($\gbar=0$), the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
-The two curves intersect along the middle branch of $v_{\infty}$, creating an unstable fixed point $p_{f}=(v_{f},w_{f})$ with a surrounding stable limit cycle of period $T$ (\cref{fig:nullclines}A).
-Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
-The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
-During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
-Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
-During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
-
-The two-cell network model is numerically integrated using an adaptive step-size integrator for stiff differential equations implemented with XPPAUT~\citep{ermentrout2002} and controlled through the Python packages SciPy~\citep{scipy2020} and PyXPP~\citep{pyxpp}.
-The following mathematical analysis is performed on the equations of a single cell.
-Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
+\subfile{sections/methods.tex}
 
 \section{Results}
-\subsection{Anti-phase burst solutions}
-Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism~\citep{brown1911} and is known to produce $n-n$ anti-phase burst solutions of varying period.
-Such $n-n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
-\Cref{fig:depression-traces}A shows the timecourse of a typical $4-4$ burst.
-While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
-Therefore, at any given moment one cell is spiking while the other is inhibited.
-Consistent with~\citet{bose2011} we will refer to the currently firing cell as ``free'' and we will call the inhibited cell ``quiet''.
-Additionally, we will distinguish between two phases of a $n-n$ solution:
-We will refer to the burst duration of a cell as the ``free phase'', which is the time between the first spike and the last spike in a burst.
-And we will call the remaining duration of a cycle, when a cell is not spiking, the ``quiet phase''.
-
-% TODO: Add mention of gstar. Once critical conductance is crossed, cell is released.
-With each action potential of the free cell, short-term depression leads to a step-wise decrease of $d$, and consequently of $s$ (\cref{fig:depression-traces}B).
-If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\gbar s$ will eventually become sufficiently small to allow for the quiet cell to be released and start firing, thus inhibiting the previously free cell.
-While a cell is quiet its depression variable can recover.
-Once the quiet cell becomes free again its synaptic inhibition will be sufficient to terminate the burst of the previously free cell and commence a new cycle.
-As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\gbar$ determines the type of $n-n$ solution.
-Increasing $\gbar$ produces higher $n-n$ burst solutions with more spikes per burst and a longer cycle period.
-\Cref{fig:burst-sols} shows numerically stable $n-n$ solutions for varying values of $\gbar$.
-For small values of $\gbar$ the network produces anti-phase spiking $1-1$ solutions.
-As $\gbar$ is increased the network generates solutions of increasing $n$, that is $2-2$, $3-3$, and $4-4$.
-When $\gbar$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
-Depending on the initial conditions either of the two cells can become the suppressed cell, which is why the suppressed solution is numerically bistable.
-
-Branches of numerically stable $n-n$ solutions and their associated limit cycle period for varying values of $\gbar$ are depicted in \cref{fig:bif-diagram}A (see  \textbf{Supplementary Material S2} for algorithm description).
-Not only do higher $n-n$ solutions branches require stronger coupling $\gbar$, but also within $n-n$ branches the period increases with $\gbar$.
-In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2-2$ and $3-3$ solution branches.
-Branches of higher $n-n$ burst solutions occur on increasingly smaller intervals of $\gbar$, for instance is the $\gbar$ interval of the $5-5$ branch shorter than that of the $4-4$ branch and so on.
-The interval between the $5-5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n-n$ solutions, such as $11-11$ bursts, but also other non-symmetric $n-m$ solutions as well irregular, non-periodic solutions.
-However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n-n$ solutions.
-
-\subsection{Mathematical analysis of two-cell network}
-~\label{sec:assumptions}
-% Summary of assumptions
-The goal of the following mathematical analysis is to reduce the complexity of the eight-dimensional system to some easily tractable quantity.
-As we will see later this quantity is the value of the depression variable $d$ of either of the two cells.
-We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the free phase, and then during the quiet phase.
-This construction will require two assumptions about the membrane and synaptic dynamics.
-The first assumption states that during a burst the free cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
-The second assumption states that once the inhibitory conductance acting on the quiet cell drops below a critical threshold, the cell is immediately released and fires.
-The second assumption is necessary to predict the release time of the quiet cell, which allows us to model the recovery of $d$ during the quiet phase.
-In other words, the second assumption requires that the release of the quiet cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the quiet cell.
-Both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
-Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n-n$ solutions.
-However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.
-
-% Assumption 1: Free phase
-Our first assumption about the model states that the free cell fires at its uncoupled period $T$, that is, during the free phase of a burst we have $ISI=T$.
-Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
-We can further numerically confirm this observation by capturing the $ISI$s of the stable solutions from the bifurcation diagram in \cref{fig:bif-diagram}A.
-In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the quiet phase of the burst.
-$IBI$s lie on multiple branches, each branch associated with a stable $n-n$ solution, and are monotonically increasing with $\gbar$.
-In contrast, $ISI$s are calculated from the spikes within the free phase and do not vary significantly with $\gbar$, but are approximately $ISI\approx T$, affirming our first assumption.
-Assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the free phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
-Assuming $ISI=T$ seems reasonable given that inhibition acting on the quiet cell decays exponentially to zero on a much shorter timescale than the duration of the $ISI$, and therefore, once the quiet cell is released its trajectory quickly approaches the spiking limit cycle.
-
-% Assumption 2: Release
-Our second assumption states that the quiet cell is released and spikes as soon as inhibition from the free cell drops below a constant threshold.
-We will now define such a ``release condition'' by exploiting the discrepancy in timescales between the fast membrane dynamics, and the slower synaptic dynamics.
-Let us first consider the dynamics of a single Morris-Lecar neuron.
-We fix the synaptic variable that acts on the cell by setting $s=1$, which also makes the applied synaptic conductance $\gbar s$ constant.
-Recall from \cref{fig:nullclines}A that in case of a single uncoupled cell ($\gbar s=0$), the $v$- and $w$-nullclines intersect at some unstable fixed point $p_{f}=(v_{f},w_{f})$, while trajectories revolve around a stable spiking limit cycle.
-Increasing $\gbar s$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point $p_{f}$ down the sigmoid $w_{\infty}$ in the $(v-w)$-plane (\cref{fig:nullclines-coupled}).
-When $\gbar s$ is large enough, the fixed point $p_{f}$ becomes stable, attracting all previously periodic trajectories.
-There exists a unique value $\gbar s=g^{\star}$ when $p_{f}$ changes stability and the stable limit cycle vanishes.
-Thus, when a constant inhibitory conductance is applied, $\gbar s<g^{\star}$ acts as a necessary condition for a cell to spike.
-In contrast, when $\gbar s>g^{\star}$ inhibition is strong enough to prevent a cell from spiking~\citep{bose2011}.
-
-% NOTE
-% In our parameter range the bifurcations occur via subcritical Hopf (bose2011 p.47)
-
-Now let us analyse the nullclines of the quiet cell when the two cells are coupled via synaptic inhibition with depression.
-Let $\gbar s$ here denote the total synaptic conductance which acts on the quiet cell and is produced by the free cell, and let $p_{f}$ be the fixed point associated with the quiet cell.
-At the start of the burst of the free cell we have $\gbar s > g^{\star}$ and $p_{f}$ is stable.
-When the free cell spikes, $\gbar s$ peaks (\cref{eq:s-reset}), and the $v$-nullcline with the ensuing stable $p_f$ move down the $w$-nullcline.
-Then in between spikes $\gbar s$ decays exponentially (\cref{eq:dot-s}) causing the $v$-nullcline and $p_{f}$ to move up the $w$-nullcline while attracting trajectories of the quiet cell.
-Once depression causes the synaptic conductance to become small enough to satisfy $\gbar s<g^{\star}$ and the quiet cell is released, fixed point $p_{f}$ becomes unstable allowing the quiet cell to fire.
-If the trajectory of the quiet cell remains sufficiently close to the stable $p_{f}$ at the time when it changes stability, then $\gbar s < g^{\star}$ acts as a release condition that is not only necessary, but also sufficient for firing of the quiet cell.
-In this case the release of the quiet cell occurs precisely when
-\begin{equation}
- ~\label{eq:release}
-  \gbar s=g^{\star}
-\end{equation}
-is satisfied.
-
-Whether the $(v,w)$-trajectory of the quiet cell can remain close enough to $p_{f}$ to make \cref{eq:release} sufficient for firing depends largely on the coupling strength $\gbar$ and the timescale disparity between membrane dynamics and synaptic dynamics~\citep{bose2011}.
-It is straightforward to test our assumption of a release condition by numerically integrating the full system of ODEs and calculating the time interval between the first spike of the quiet cell and the time when $\gbar s$ first crosses $g^{\star}$.
-We will call this time interval the ``release delay''.
-If our assumption holds, we would expect an approximately zero release delay.
-\Cref{fig:release-delay} shows the numerically computed graph of the release delay for varying $\gbar$.
-The graph shows three distinct branches, next to each branch we also plot the timecourse of a corresponding sample solution of the total synaptic conductance $\gbar s$ of both cells.
-For the rightmost branch where $\gbar>0.592$ $\si{mS/cm^{2}}$ the release delay is approximately zero.
-Here the first spike of the quiet cell can be accurately predicted by the release condition in \cref{eq:release}.
-The leftmost and middle branches for $\gbar<0.592$ $\si{mS/cm^{2}}$  show a release delay greater than zero, the quiet cell does not immediately fire when the release condition is first satisfied, and \cref{eq:release} does not accurately predict the release of the quiet cell.
-The leftmost and middle branches contain $1-1$ and $2-2$ solutions respectively.
-In both cases the coupling $\gbar$ is not sufficiently strong to allow trajectories of the quiet cell to be close enough to $p_{f}$ to guarantee spiking once $\gbar$ crosses $g^{\star}$.
-Note that in the middle branch $\gbar s $ crosses $g^{\star}$ twice, and only after the second crossing does the quiet cell fire.
-The following map construction relies on the assumption that the release condition in \cref{eq:release} can accurately predict the release time of the quiet cell.
-Given our model parameters this is only possible for sufficiently large $\gbar>0.592 $ $\si{mS/cm^{2}}$.
-For completeness, however, we will also consider values $\gbar < 0.592$ $\si{mS/cm^{2}}$ in the following analysis, bearing in mind that in this parameter range our map will not be accurate.
-
-In summary: For $\gbar>0.592$ $\si{mS/cm^{2}}$ the release condition is sufficient to predict when the quiet cell is released.
-Due to the symmetry of $n-n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
-The release time therefore uniquely determines the type of $n-n$ solution.
-Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the quiet cell.
-Instead, the solution of the synaptic variable $s$ of the free cell is sufficient to predict when $\gbar s=g^{*}$ is satisfied.
-Finally, $s$ is solely determined by the evolution of the depression variable $d$ of the free cell.
-Constructing a solution of $d$ during the free phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
-However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
-In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n-n$ solutions.
-
-\subsection{Construction of the scalar Poincaré map}
-In this section we construct the scalar Poincaré map $\Pi_{n}:d^{\star}\mapsto d^{\star}$.
-Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n-n$ burst.
-The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
-To simplify the map construction we will assume that a free cell fires exactly $n$ times before it becomes quiet.
-Later we will relax this assumption.
-We will construct $\Pi_{n}$ by evolving $d$ first during the free phase and then during the quiet phase of the $n-n$ limit cycle.
-First, let us give explicit definitions of the free and quiet phases.
-A schematic illustration of both phases is given in \cref{fig:free-quiet1}.
-
-Suppose that at $t=0$ cell 1 becomes free with some initial $d(0)$. 
-Cell 1 then fires $n$ spikes at the uncoupled period $T$.
-Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
-After $n$ spikes the total conductance $\gbar s(t)$ acting on the quiet cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}, that is at some time $t=(n-1)T+\delt$ we have $\gbar s(t)=g^{\star}$.
-Cell 2 is then released and prevents cell 1 from further spiking.
-Here $\delt$ is the \emph{inter-burst-interval}, or the time between the last spike of cell 1 and the first spike of cell 2~\citep{bose2011}.
-Once released, cell 2 also fires $n$ spikes until cell 1 becomes free once again at the cycle period.
-Let $P_n$ denote the full cycle period of a $n-n$ solution:
-\begin{equation}
- ~\label{eq:P}
-  P_n = 2(n-1)T + 2\delt.
-\end{equation}
-We can now define the free and quiet phases of cell 1 explicitly. The free phase is the time interval between the first and last spikes of the burst, that is for time $0<t<(n-1)T$.
-During the free phase of cell 1, the quiet cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\gbar s > g^{\star}$.
-The quiet phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T < t < 2(n-1)T + 2\delt$.
-
-Note that only the quiet phase depends on $\delt$, and $\delt$ will play a central role in the construction of $\Pi_{n}$.
-From \cref{eq:P} $\delt$ can be be computed as
-\begin{equation}
- ~\label{eq:delta-t-P}
-  \delt = \frac{1}{2}P_n - (n-1)T.
-\end{equation}
-\noindent
-We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n-n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\delt$ as a function of $\gbar$ (\cref{fig:delta-t}).
-Each continuous branch of $\delt$ is monotonically increasing and corresponds to a $n-n$ burst:
-Stronger coupling $\gbar$ increases the total synaptic conductance $\gbar s$ that acts on the quiet cell, thus delaying its release.
-It is easy to see that for any $n$-branch we have $\delt<T$:
-Once $\delt$ crosses $T$, the free cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1)-(n+1)$ burst.
-
-Distinguishing between the free and quiet phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
-As can be seen from \cref{fig:free-quiet1}C, during the free phase $d$ depresses at spike times and recovers in the $ISI$s.
-In contrast, during the quiet phase $d$ only recovers and does not depress.
-Given the initial $d^{\star}=d(0)$ at the beginning of the cycle and the number of spikes in the free phase $n$, we can now construct the burst map $\Pi_{n}$.
-The map
-\begin{equation}
-  \Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star}\big))
-\end{equation}
-\noindent
-is a composition of two maps.
-Map
-\begin{equation}
-  F_{n}:d^{\star}\mapsto \delt
-\end{equation}
-models the evolution of $d$ in the free phase.
-$F_{n}$ takes an initial value $d^{\star}$ and calculates the inter-burst-interval $\delt$.
-Map
-\begin{equation}
-  Q_{n}:\delt \mapsto d^{\star}
-\end{equation}
-models the recovery of $d$ in the quiet phase.
-Given some $\delt$ map $Q_n$ computes $\dstar$ at the start of the next cycle.
-
-Our aim in the following analysis is to elucidate the properties of $\Pi_{n}$ and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of $\Pi_{n}$ are created.
-To that effect it will be useful to include not only positive, but also negative values of $d^{\star}$ to the domain of $\Pi_{n}$.
-But it is important to add that values $d^{\star}<0$ are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
-Because $\Pi_{n}$ maps first from $d^{\star}$ to $\delt$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n-n$ solutions with partially overlapping bursts.
-As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n-n$ solutions of the full system of ODEs only exist for $\Delta t>0$.
-
-We start the construction of $\Pi_n$ by first considering the free phase and building the map $F_n$.
-At each spike time $t_{k}$, variable $d$ depresses with the reset $d(t_{k})\leftarrow \lambda d(t_{k}^{-})$ (\cref{eq:d-reset}).
-For the duration of the subsequent $ISI$, the recovery of $d$ is described by the solution to \cref{eq:dot-d}:
-\begin{equation}
-  d(t) = 1 - (1-\lambda d_{k})e^{-t/\tau_{d}}~\label{eq:d-sol},
-\end{equation}
-where the variable $d_{k}=d(t^{-}_{k})$ is the level of depression at spike time $t_{k}$.
-By substituting $t=T$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the free phase:
-\begin{equation}
-  d_{k+1} = \lambda\rho d_{k} + (1-\rho),~\label{eq:map-d}
-\end{equation}
-where to keep the notation simple we let $\rho=\exp(-T/\tau_{d})$.
-Since $0<\lambda, \rho<1$, the map~\eqref{eq:map-d} is increasing and contracting, with a fixed point at
-\begin{equation}
- ~\label{eq:dsup}
-  d_{s}=\frac{1-\rho}{1-\lambda\rho},
-\end{equation}
-where $0<d_{s}<1$.
-The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
-Using the release condition in \cref{eq:release} allows us to derive the value of the the minimum coupling strength that will produce the full suppressed solution, denoted as $\gbar_{s}$.
-Solving \cref{eq:dot-s} for $s(t)$ with $t=T$ and setting the initial value $s(0)=d_{s}$ gives
-\begin{equation}
-\gbar_{s} d_{s}e^{-T/\tau_{s}}=g^{\star}.
-\end{equation}
-By further substituting the definition of $d_{s}$ in~\eqref{eq:dsup} and rearranging, we can write $\gbar_{s}$ as a function of the depression strength $\lambda$:
-\begin{equation}
-  \label{eq:gs}
-  \gbar_{s}(\lambda) = g^{\star}e^{T/\tau_{s}}\frac{1-\lambda \rho}{1-\rho}.
-\end{equation}
-Note that the above dependence of $\gbar_{s}$ on $\lambda$ is linear and monotonically decreasing.
-Increasing $\lambda$ reduces the strength of the depression of the free cell.
-This in turn allows the free cell to fully suppress the quiet cell at smaller values of $\gbar$.
-
-Solving~\eqref{eq:map-d} gives us the linear map $\delta_{n}:d^{\star}\mapsto d_{n}$, that for some initial $d^{\star}$ computes the depression at the $n$th spike time, $d_{n}=d(t_{n}^{-})$:
-\begin{equation}
- ~\label{eq:delta-map}
-  \delta_{n}(d^{\star}) = (\lambda \rho)^{n-1} d^{\star} + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}.
-\end{equation}
-Since $\lambda < 1$, function $\delta_{n}$ is a linearly increasing function of $d^{\star}$ with a fixed point at $d_{s}$ for all $n$.
-Having identified $d$ after $n$ spikes, we can now use the release condition $\gbar s = g^{\star}$ (\cref{eq:release}) to find $\delt$.
-At the last spike of the free phase at time $t_{n}=(n-1)T$ the synapse variable $s$ is reset according to \cref{eq:s-reset}:
-\begin{equation}
-  s(t_{n})\leftarrow \dn(\dstar).
-\end{equation}
-After the last spike $s$ decays exponentially according to the solution of \cref{eq:dot-s}, where setting the initial condition $s(0)=\dn(\dstar)$ yields:
-\begin{equation}
-~\label{eq:s-sol}
-  s(\delt)=\dn(\dstar)e^{-\Delta t/\tau_{s}}.
-\end{equation}
-Substituting $s(\delt)$ into $s$ of the release condition (\cref{eq:release}) gives then
-\begin{equation}
- ~\label{eq:release2}
-  \gbar \dn(\dstar) e^{-\delt/\tau_{s}}=g^{\star}.
-\end{equation}
-Our assumption of the release condition guarantees that the quiet cell 2 spikes and becomes free when $\gbar s - g^{\star}$ crosses zero.
-Solving \cref{eq:release2} for $\delt$ allows us to compute the inter-spike-interval as a function of $\dstar$, which defines our map $F_n$:
-\begin{equation}
- ~\label{eq:Fn-map}
-  F_{n}(d^{\star}):=\tau_{s}\ln{\left(\frac{\gbar }{g^{\star}} \delta_{n}(d^{\star})\right)}= \delt.
-\end{equation}
-
-\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\gbar$.
-Larger values of $d^{\star}$ and $\gbar$, respectively, cause stronger inhibition of the quiet cell, and therefore prolong its release time and the associated $\delt$.
-Map $F_{n}$ is defined on $d^{\star}>d_{a}$, where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(\dstar)=0$ in \cref{eq:delta-map} for $\dstar$, which yields
-\begin{equation}
-  d_{a}(n)=-\frac{(1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}}{ (\lambda \rho)^{n-1} }\leq 0~\label{eq:da}.
-\end{equation}
-
-We now turn to the construction of map $Q_{n}$, which describes the recovery of the depression variable during the quiet phase.
-As we have identified earlier, the recovery in the quiet phase of a $n-n$ solution is of duration $2\delt +(n-1)T$.
-Substituting that into the solution for $d(t)$ (\cref{eq:d-sol}) with the initial condition $d(0)=\dn(\dstar)$ yields the map $Q_{n}$:
-\begin{equation}
- ~\label{eq:Qn-map}
-  Q_{n}(\delt):=1- (1- \lambda \dn(\dstar))e^{-(2\Delta t+(n-1)T)/\tau_{d}}.
-\end{equation}
-Given $\delt$, we can find $\dn(\dstar)$ by rearranging the release condition in \cref{eq:release2}:
-\begin{equation}
- ~\label{eq:dn}
-  \dn(\dstar) = \frac{g^{\star}}{\gbar} e^{\delt/\tau_{s}}.
-\end{equation}
-Map $Q_{n}$ is shown in \cref{fig:FQ-map}B for various values $n$.
-Note that $Q_{n}$ is monotonically increasing as larger values $\delt$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
-All curves $Q_{n}$ intersect at some $\delt = \tau_{s}\ln{\left[\gbar/(g^{\star}\lambda)\right]}$ where
-\begin{equation}
-     ~\label{eq:Qn-intersect}
-      Q_{n}\left[\tau_{s}\ln{\left(\frac{\gbar}{g^{\star}\lambda}\right)}\right]=1.
-    \end{equation}
-As we will show in the next section, all fixed points of the full map $\Pi_{n}$ occur for $d^{\star}<1$.
-We will therefore restrict the domain of $Q_{n}$ to $(-\infty, \ln{\left[\gbar/(g^{\star}\lambda)\right]}\tau_{s})$ and the codomain to $(-\infty, 1)$.
-Additionally, while values $\delt>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t=T$, and we will address this concern in the last part of our map analysis.
-
-Having found $F_{n}$ and $Q_{n}$, we can now construct the full map $\Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star})\big)$:
-\begin{equation}
- ~\label{eq:Pn-map}
-  \Pi_{n}(d^{\star})= 1-
-\frac{\rho^{n-1}{g^{\star}}^{\tau}}{{\gbar}^{\tau}}\delta_{n}^{-\tau}(d^{\star})\big(1-\lambda\delta_{n}(d^{\star})\big),
-\end{equation}
-where we substituted $\tau = 2\tau_{s}/\tau_{d}$.
-Since $d$ is the slowest variable of the system and $\tau_{d}\gg \tau_{s}$, we will also assume $\tau<1$.
-\Cref{fig:Pn-map}A depicts $\Pi_{n}$ for various $n$.
-Intersections of $\Pi_{n}$ with the diagonal are fixed points of the map.
-\Cref{fig:Pn-map}B shows $\Pi_{2}$ with $n=2$.
-Varying the synaptic strength $\gbar$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
-For $\gbar<0.03$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
-As $\gbar$ is increased to $\gbar \approx 0.03$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
-When $\gbar > 0.03$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
-
-From \cref{eq:Pn-map} it is evident that $\Pi_{n}$ is monotonically increasing with respect to $\gbar$ and also $\dstar$:
-\begin{align}
-  \label{eq:non-degen1}
-  \dv{\Pi_{n}}{\gbar}&>0,\\[0.5ex]
-  \label{eq:dPidd}
-  \dv{\Pi_{n}}{\dstar}&>0,
-\end{align}
-and in the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
-Just as $F_{n}$, curves $\Pi_{n}$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
-\begin{equation}
-  \lim_{\gbar \to \infty}\Pi_{n} = 1\text{ for all }n,
-\end{equation}
-fixed points of $\Pi_{n}$ lie in $(d_{a}, 1)$.
-
-% \subsection{Existence and stability of fixed points of $\mathit{\Pi_{n}}$}
-\subsection{Existence and stability of fixed points}
-We introduce the fixed point notation $\dstar_{f}$ with $\Pi_{n}(\dstar_{f})=\dstar_{f}$.
-The existence of fixed points $\dstar_{f}$ for $\gbar$ sufficiently large can be shown from the strict monotonicity of $\Pi_{n}$ with respect to $\gbar$ and $\dstar$ (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of $\Pi_{n}$ is monotonically decreasing,
-\begin{equation}
-  \label{eq:non-degen2}
-  \left(\frac{\mathrm{d}}{\mathrm{d}\dstar}\right)^2 \Pi_{n}<0.
-\end{equation}
-In the limit $\dstar \to d_{a}$ the value of $\Pi_n$ decreases without bound for any $\gbar>0$.
-In the limit $\gbar \to 0$, $\Pi_n$ also decreases without bound, but as $\gbar \to \infty$ values of $\Pi_n$ approach $1$.
-It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some $\gbar$ large enough $\Pi_n$ intersects the diagonal.
-Moreover, because $\Pi_n$ and its slope are monotonic with respect to $\dstar$, there exists some critical fixed point $(\dstar_b, \gbar_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
-\begin{align}
-  \Pi_{n}(\dstar_{b}; \gbar_{b}) &=\dstar_{b},\\
-  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b})&=1.
-\end{align}
-Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(\dstar_{b}, \gbar_{b})$ map $\Pi_{n}$ has the topological normal form described by the graph of
-\begin{equation}
-  \label{eq:normal-form}
-  x\mapsto \beta+x-x^{2},
-\end{equation}
-with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.
-
-\subsection{Fold bifurcations}
-Fixed points of $\Pi_n$ satisfy the fixed point equation
-\begin{equation}
-  \label{eq:Phi}
-  \Phi_n(\dstar; \gbar)=0,
-\end{equation}
-where
-\begin{equation}
- ~\label{eq:Phi-def}
-  \Phi_{n}(d^{\star}, \gbar):=\Pi_{n}(d^{\star}, \gbar)-d^{\star}.
-\end{equation}
-As we have already shown, for $\gbar > \gbar_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
-Solving \cref{eq:Phi} explicitly for $\dstar$ it not trivial, but solving for $\gbar$ is straightforward and given by $\gbar = G_n(\dstar)$, where
-\begin{equation}
- ~\label{eq:g}
-  G_{n}(d^{\star}) := g^{\star} \left(\frac{\rho^{n-1}\delta_{n}^{-\tau}(d^{\star})(1-\lambda\delta_{n}(d^{\star}))}{1-d^{\star}}\right)^{1/\tau}.
-\end{equation}
-Plotting $d^{\star}$ against $\gbar$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
-Note the typical quadratic shape of a fold bifurcation of maps.
-It is also evident that the fold bifurcations occur for increasingly smaller $\gbar$ as $n$ is increased.
-Moreover, we can observe that unstable fixed points have negative values of $d^{\star}$ for $n>1$.
-
-\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(\dstar_{b}(n), \gbar_{b}(n)\big)$, which is the global minimum of $G_{n}(\dstar_f)$:
-\begin{align}
-  \dstar_{b}(n) &= \operatorname{argmin} G_{n}(\dstar_{f}),\\
-  \gbar_{b}(n)  &= \min{G_{n}(\dstar_{f})}.
-\end{align}
-Function $G_{n}$ is strictly monotonic on the respective intervals of $\dstar_f$ that correspond to the stable and unstable fixed points, that is
-\begin{align}
-  \dv{G_n}{\dstar_f}& < 0, \text{ for } \dstar_f>\dstar_b(n) \text{ stable},\\[0.5ex]
-  \dv{G_n}{\dstar_f}& > 0, \text{ for } \dstar_f<\dstar_b(n) \text{ unstable},
-\end{align}
-which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $\dstar_f$.
-Because we are primarily interested in the stable fixed points, we define the stable fixed point function $\dstar_f=\phi_n(\gbar)$ as
-\begin{equation}
-  \label{eq:phi}
-  \phi_{n}(\gbar):= G_{n}^{-1}(\dstar_{f}) \text{ for } \dstar_{f}>\dstar_{b}(n).
-\end{equation}
-Function $\phi_n(\gbar)$ is also monotonic, and is therefore straightforward to compute numerically via root-finding.
-Here we use the Python package Pynverse~\citep{pynverse} for that purpose.
-
-Having found the stable fixed points $\dstar_f$ as a function of the coupling strength $\gbar$, we can now compute the associated cycle period.
-Recall that the period is given by \cref{eq:P}, which we can be written as a function of $\gbar$:
-\begin{equation}
-  \label{eq:period}
-  P_n(\gbar) = 2(n-1)T + 2F_n\big(\underbrace{\phi_n(\gbar)}_{\dstar_f}, \gbar\big),
-\end{equation}
-where map $F_n$ (\cref{eq:Fn-map}) calculates the inter-burst-interval $\delt$ given a stable fixed point $\dstar_f=\phi_n(\gbar)$.
-We plot the predicted period $P_n(\gbar)$ versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
-For $n>1$ our map $\Pi_n$ accurately predicts the period.
-When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for $n=1$ (see \cref{fig:release-delay}), since here $\gbar$ is not sufficiently strong to guarantee the validity of our release condition (\cref{eq:release}).
-
-It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\gbar$.
-This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\gbar), \gbar)=0$ in \cref{eq:Phi}.
-For $\dstar_f=\phi_n(\gbar)>d_b(n)$ we get:
-\begin{equation}
-  \label{eq:dstardg}
-  \dv{\phi_n}{\gbar} = -\frac{\pdv*{\Phi_n}{\gbar}}{\pdv*{\Phi_n}{\dstar}} =
-  \frac{\pdv*{\Pi_n}{\gbar}}{1-\pdv*{\Pi_n}{\dstar}}>0.
-\end{equation}
-The inequality follows from $\pdv*{\Pi_n}{\gbar}>0$ and the fact that $\pdv*{\Pi_n}{\dstar}<1$ for $\dstar>d_b(n)$.
-\Cref{eq:dstardg} allows us to explain why the period $P_n$ increases with $\gbar$, as seen in \cref{fig:folds}B.
-Differentiating $P_n$ gives:
-\begin{equation}
-  \label{eq:dPdg}
-  \dv{P_{n}}{\gbar} = 2\grad F_n(\dstar_f, \gbar) \cdot
-                      \begin{bmatrix}\pdv*{\phi_n}{\gbar}\\[0.5ex] 1\end{bmatrix}>0,
-\end{equation}
-where the partial derivatives of $F_n(\dstar_f, \gbar)$ are:
-\begin{align}
-  \pdv{F_n}{\dstar_f} &= \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar_f)}>0,\\[0.5ex]
-  \pdv{F_n}{\gbar}  &= \frac{\taus}{\gbar}>0.
-\end{align}
-\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation:
-Increasing the coupling strength between the neurons leads to overall stronger inhibition of the quiet cell, which delays its release and leads to a longer cycle period.
-The latter allows more time for the synapse to depress in the free phase and recover in the quiet phase, resulting in overall larger values of $\dstar_f$, that is weaker depression at the burst onset.
-
-While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the free phase contains exactly $n$ spikes.
-As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n-n$ bursts exists only on certain parameter intervals of $\gbar$.
-In the last sub-section we will analyse the mechanisms that guide how the stable $n-n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\gbar$ where such solutions exist.
-
-% TODO: Need to find a better sub-section title that doesn't include 'period increment'
-\subsection{Period increment bifurcations with co-existent attractors}
-Let $\gbar_+(n)$ and $\gbar_-(n)$ denote the left and right parameter borders on $\gbar$ where stable $n-n$ solutions exist.
-That is, as $\gbar$ is increased stable $n-n$ solutions are created at $\gbar_+(n)$ and destroyed at $\gbar_-(n)$.
-When $\gbar$ is reduced beyond $\gbar_+(n)$, $n-n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\gbar$ is increased beyond $\gbar_-(n)$, $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
-Let us briefly recap our observations regarding $\gbar_+(n)$ and $\gbar_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
-For $n>1$ there are the following relations:
-\begin{align}
-  \gbar_+(n) &< \gbar_-(n)\label{eq:easy1},\\
-  \gbar_+(n) &< \gbar_+(n+1)\text{ and } \gbar_-(n)<\gbar_-(n+1)\label{eq:easy2},\\
-  \gbar_+(n+1) &< \gbar_-(n)\label{eq:coexistence},\\
-  \gbar_-(n+1) - \gbar_+(n+1) &< \gbar_-(n) - \gbar_-(n)\label{eq:robustness}.
-\end{align}
-\Cref{eq:easy1,eq:easy2} are self-explanatory.
-\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n-n$ and $(n+1)-(n+1)$ solutions.
-\Cref{eq:robustness} implies that the parameter interval on $\gbar$ of $n-n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
-All of the above relations are reminiscent of the period increment bifurcations with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
-see][]{gardini2012,tramontana2012,avrutin2011,gardini2012}.
-While our maps $\Pi_n$ are fully continuous, the above observation suggests that
-a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
-We will explore what such a map might look like in the discussion.
-
-Let us now find algebraic equations that will allow us to calculate the critical parameters $\gbar_+(n)$ and $\gbar_-(n)$ associated with the period increment bifurcations.
-% BUG: Maybe don't call it period-increment here?
-Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\gbar$:
-\begin{equation}
-  \dv{P_{n}}{\gbar}=2\dv{F_n(\phi_n(\gbar), \gbar)}{\gbar}>0,
-\end{equation}
-that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the quiet cell, and $\delt$ becomes larger.
-Once $\delt=T$, the free cell can produce another spike and the solution bifurcates into a $(n+1)-(n+1)$ solution.
-Note, however, that at $\gbar_+(n)$ the bifurcation into a $(n-1)-(n-1)$ does not occur when $\delt=0$.
-Here the mechanism is different: A sufficient reduction of $\gbar$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the quiet cell to be released one spike earlier.
-
-Using the above reasoning we can now formulate the conditions for both bifurcations at $\gbar_+(n)$ and $\gbar_-(n)$.
-As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $\dstar_f=\phi_n(\gbar)$ (\cref{eq:phi}).
-At the right bifurcation border $\gbar_-(n)$ we have $\delt=T$, and after substituting our $F_{n}$-map (\cref{eq:Fn-map}) this translates into
-\begin{equation}
-  F_n(\phi_n(\gbar), \gbar) = T,
-\end{equation}
-which lets us define a function
-\begin{equation}
-  \label{eq:R}
-  R_{n}(\gbar):=F_n(\phi_n(\gbar), \gbar)-T,
-\end{equation}
-whose root is the desired right bifurcation border $\gbar_-(n)$.
-In case of the left bifurcation border at $\gbar_+(n)$ the release condition is satisfied just before the free cell has produced its $n$th spike, and after the depression variable has been reset $n-1$ times, which gives the condition
-\begin{equation}
-  \gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} = \gstar,
-\end{equation}
-and can be rewritten as a function
-\begin{equation}
-  \label{eq:L}
-  L_{n}(\gbar):=\gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} -\gstar,
-\end{equation}
-whose root is $\gbar_+(n)$.
-Both $R_{n}$ and $L_{n}$ are increasing with respect to $\gbar$, which makes finding their roots numerically straightforward.
-
-\Cref{fig:final-bif} shows the period $P_n(\gbar)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\gbar \in [\gbar_+(n),\gbar_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
-Note that the width of $n-n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
-That is, bursts with more spikes occur on increasingly smaller intervals of $\gbar$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
-We also note the occurrence of bi-stability between pairs of $n-n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in \cref{eq:coexistence}.
-
-As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate for $n>1$.
-Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be $\gbar \approx 0.592\si{mS/cm^2}$ in \cref{fig:release-delay}.
-The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\gbar_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
-However, even for branches of large $n-n$ solutions there is a mismatch between the bifurcation borders.
-Presumably our assumptions on the time scales of $w$ and $s$ dynamics do not hold here, and can only be captured by more complex approximations.
-Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.
+\subfile{sections/results.tex}
 
 \section{Discussion}
-% PROBLEM SUMMARY
-Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming~\citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
-In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
-Mathematical modelling can shed light on the underlying mechanisms that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.
-
-% MAIN RESULTS
-To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression.
-When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n-n$ burst patterns.
-Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
-This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n-n$ solutions respectively.
-Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons.
-Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n-n$ burst solutions of the full two-cell system of ODEs.
-The results from our one-dimensional map match excellently with numerical simulation of the full network.
-Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.
-
-% FURTHER METHOD IDEAS
-We have studied $n-n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
-However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes.
-It is conceivable that our map construction can be extended to also capture such $m-n$ solutions.
-Remember, in the case of symmetrical coupling with $n-n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
-To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other.
-To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$.
-While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}.
-Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons.
-As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses.
-In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.
-
-In tadpoles, struggling is believed to be initiated by an increase in the firing frequency of reciprocally inhibitory commisural interneurons, which has been hypothesised to lead to stronger synaptic depression of inhibition and result in the iconic anti-phase bursting \citep{li2007}.
-It would therefore be interesting to study how varying the cell intrinsic firing period $T$ could affect the network rhythm.
-While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying $T$.
-Recall that $T$ is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters.
-This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult.
-A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting in this scenario.
-
-% LIMITATION: SPIKE MAP
-Our simulations of the network showed that $n-n$ solutions lose robustness as their period is increased.
-That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
-We were able to replicate this finding by numerically finding the respective left and right borders of stable $n-n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
-We have also noted the resemblance of our bifurcation diagram to one where such $n-n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
-It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}.
-Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
-The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
-In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations.
-It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
-In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.
-
-% FLOW SYSTEM BIFURCATION
-In addition to stable $n-n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n-n$ solutions.
-While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.
-However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
-SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
-% Should be possible to use averaging to reduce the system.
-
-% BIOLOGICAL IMPORTANCE OF DEPRESSION
-We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.
-This result is in line with the idea that one role of synaptic depression in the nervous system may be to allow a finite size neuronal network to participate in different tasks by producing a large number of rhythms~\citep{bose2011, jalil2004, li2007}.
-To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength, which can occur through the process of learning.
-Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.
+\subfile{sections/discussion.tex}
 
@@
 
-% \bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities
 \bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
-
 \bibliography{bibliography.bib}

### 2022-02-04 tex/sections/discussion.tex
Split latex document into subfiles

--- 2022-01-26 tex/draft.tex
@@
-\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and
-\usepackage{graphicx}
-\usepackage{amssymb}
-\usepackage{siunitx}
-\usepackage{amsmath}
-\usepackage{soul}
-\usepackage{physics}
-\usepackage{bm}
-
-\usepackage{url,hyperref,microtype,subcaption}
-\usepackage[onehalfspacing]{setspace}
-\usepackage{cleveref}
-% \usepackage[font={bold,it}]{caption}
-
-% Define better ref abbreviations
-\usepackage[displaymath]{lineno}
-
-\renewcommand{\d}{\mathrm{d}}
-\renewcommand{\k}{\mathrm{K}}
-\newcommand{\ca}{\mathrm{Ca}}
-\newcommand{\na}{\mathrm{Na}}
-\newcommand{\leak}{\mathrm{L}}
-\newcommand{\dstar}{d^\star}
-\newcommand{\gstar}{g^\star}
-\newcommand{\gbar}{\bar g}
-\newcommand{\delt}{\Delta t}
-\newcommand{\taus}{\tau_s}
-\newcommand{\dn}{\delta_n}
-\newcommand{\taud}{\tau_d}
-
-\linenumbers
-
-\def\keyFont{\fontsize{8}{11}\helveticabold }
-\def\firstAuthorLast{Olenik {et~al.}} %use et al only if is more than 1 author
-\def\Authors{Mark Olenik\,$^{1,*}$, and Conor Houghton\,$^{2}$}
-% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
-% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
-\def\Address{$^{1}$School of Biological Sciences, Faculty of Life Sciences, University of Bristol, Bristol, United Kingdom \\
-$^{2}$School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, Faculty of Engineering, University of Bristol, Bristol, United Kingdom}
-% The Corresponding Author should be marked with an asterisk
-% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
-\def\corrAuthor{Mark Olenik}
-
-\def\corrEmail{m.olenik@bristol.ac.uk}
+\documentclass[../manuscript.tex]{subfiles}
+\graphicspath{{../figures/}}
 
@@
 
-\onecolumn
-\firstpage{1}
-
-\title[Scalar Poincaré map for bursting]{A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression.}
-
-\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
-\address{} %This field will be automatically populated
-\correspondance{} %This field will be automatically populated
-
-\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
-%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
-
-\maketitle
-
-\begin{abstract}
-\section{}
-Short-term synaptic plasticity is found in many areas of the central
-nervous system.  In the inhibitory half-centre central pattern
-generators involved in locomotion, synaptic depression is believed to
-act as a burst termination mechanism, allowing networks to generate
-anti-phase bursting patterns of varying periods.  To better understand
-burst generation in these central patter generators, we study a
-minimal network of two neurons coupled through depressing synapses.
-Depending on the strength of the synaptic conductance between the two
-neurons, this network can produce symmetric $n-n$ anti-phase bursts,
-where neurons fire $n$ spikes in alternation, with the period of such
-solutions increasing with the strength of the synaptic conductance.
-Relying on the timescale disparity in the model, we reduce the
-eight-dimensional network equations to a fully-explicit scalar
-Poincaré burst map.  This map tracks the state of synaptic depression
-from one burst to the next and captures the complex bursting dynamics
-of the network.  Fixed points of this map are associated with stable
-burst solutions of the full network model, and are created through
-fold bifurcations of maps.  We derive conditions that describe
-period-increment bifurcations between stable $n-n$ and $(n+1)-(n+1)$
-bursts, producing a full bifurcation diagram of the burst cycle
-period.  Predictions of the Poincaré map fit excellently with
-numerical simulations of the full network model and allow the study of
-parameter sensitivity for rhythm generation.
-
-\tiny
- \keyFont{ \section{Keywords:} Synaptic depression, Poincaré map, Dynamical system, Neuronal bursting, Central pattern generator}
-
-\end{abstract}
-
-\section{Introduction}
-% DEPRESSION
-Short-term synaptic plasticity may have a role in burst activity in
-central pattern generators (CPGs).  Short-term synaptic depression is
-commonly found in neuronal networks involved in the generation of
-rhythmic movements, such as in the pyloric CPG of the spiny
-lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of
-the chick embryo~\citep{donovan1998}.  Synaptic depression modulates
-the strength of synapses in response to changes to the presynaptic
-firing frequency.  At a high neuronal firing frequency, depression
-weakens the strength of synapses and therefore reduces the magnitude
-of the postsynaptic response.  At low firing frequency, it allows
-sufficient time for the synapse to recover from depression between
-spikes, leading to a stronger postsynaptic response.  In reciprocal
-networks, synaptic depression has been shown to act as a ``switch'',
-giving rise to a wide range of network dynamics such as synchronous
-and multi-stable rhythms, as well as fine tuning the frequency of
-network oscillations~\citep{nadim2000, nadim1999, bose2011}.
-
-% Brown
-~\citet{brown1911} pioneered the idea that synaptic depression acts as
-a burst termination mechanism in reciprocally inhibitory CPGs involved
-in rhythm generation of locomotion. When one side is firing during a
-burst the other, antagonistic side, is prevented from firing by
-synaptic inhibition. However, the weakening of inhibition as a result
-of synaptic depression eventually releases the antagonistic side so
-that it starts firing, terminating the burst on the side that had
-originally been firing.  This rhythmogenesis hypothesis has been
-considered one of a handful of standard mechanisms for generating
-locomotion rhythms in
-vertebrates~\citep{reiss1962,perkel1974,friesen1994}. It has been
-proposed as an explaination of the antiphase burst rhythm in
-struggling in \textit{Xenopus} tadpoles~\citep{li2007}.
-
-~\citet{bose2011} investigated burst generation in a generic
-half-centre CPG that consists of two identical, tonically active
-Morris-Lecar~\citep{morris1981} neurons coupled through inhibitory
-depressing synapses.  Numerical simulations showed that when the
-reciprocal synaptic conductance between the two neurons is varied, the
-network produces symmetric $n-n$ anti-phase bursts, with stronger
-synaptic coupling leading to longer bursts.  They used methods from
-geometric singular perturbation theory to separate the timescales of
-the fast membrane, and the slow synaptic dynamics of the network to
-derive one-dimensional conditions necessary for the existence of
-stable $n-n$ solutions (for $n\leq 2$). According to these conditions
-the type of firing pattern largely depends on the slow depression
-dynamics of the synapses between the two neurons, and can therefore be
-predicted by knowing the strengths of the synaptic conductances of the
-two synapses.
-Thus, the scalar conditions derived in~\citet{bose2011} provide a
-method to numerically identify the type of stable $n-n$ pattern for
-any given value of the coupling strength.  However, they do not
-predict the exact period of such solutions.
-Furthermore, while they provide good arguments for the validity of
-their reduction assumptions and the resulting scalar conditions, they
-do not verify them numerically.
-
-Here we extend the previous analysis by providing a Poincaré map of
-the slow depression dynamics.  This allows us not only to predict the
-types of stable $n-n$ solutions the full network can produce, (for any
-$n$), but also to study how varying the coupling strength affects the
-period of such solutions.  To do this, we build on, and numerically
-test, the assumptions on the fast-slow timescale disparity made
-in~\cite{bose2011}.  We reduce the two-cell model to a scalar
-Poincaré map that tracks the evolution of the depression from the
-beginning of one burst to the beginning of the next burst.  Stable
-fixed points of our map are associated with stable $n-n$ burst
-solutions.  Our map construction is motivated by the burst length map
-of a T-type calcium current, utilised by~\citet{matveev2007}, which
-approximates the anti-phase bursting dynamics of a network of two
-coupled Morris-Lecar neurons.  In contrast to our model, the network
-described in the~\cite{matveev2007} paper does not contain short-term synaptic
-depression, and burst termination is instead accomplished through the
-dynamics of a slow T-type calcium current.
-
-% MAIN RESULTS AND CONCLUSIONS
-The Poincaré map derived here replicates the results from numerical
-simulations of the full two-cell ODE system: Given the strength of
-maximum conductance between the two neurons, fixed points of our map
-predict the type and period of $n-n$ patterns, the switch between
-burst solutions of different periods, as well as the occurrence of
-co-existent solutions.  In addition to proving the existence and
-stability of fixed points, our map shows that fixed points are created
-via a fold bifurcation of maps.  We also derive algebraic conditions
-that predict the period increment bifurcations that allow the switch
-between $n-n$ and $(n+1)-(n+1)$ solutions.  Because our map is fully
-explicit, it lays the framework for studying the effects of other
-model parameter on network dynamics without the need to run expensive
-numerical integrations of the ODEs.
-
-% PAPER STRUCTURE.
-This paper is organised as follows.  First, we introduce the network
-of two neurons, and describe the properties of single cell and synapse
-dynamics.  We use numerical simulations of the network to provide an
-intuition for the range of possible burst dynamics the system can
-produce.  Next, we state and justify the simplifying assumptions that
-are necessary for the map construction.  Finally, we analytically
-derive the first return map of the depression variable as well as the
-conditions that are required for stable solutions to bifurcate between
-$n-n$ and $(n+1)-(n+1)$ solutions.  We end this work with a
-discussion.
-
-\section{Materials and Methods}
-We consider a pair of identical Morris-Lecar neurons~\citep{morris1981}, with parameters adapted from~\cite{bose2011}.
-The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
-The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
-The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
-\begin{align}
-    ~\label{eq:cell-modelA}
-     \dot v_{i}&= f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}),\\
-    ~\label{eq:cell-modelB}
-     \dot w_{i} &=h(v_i,w_i).
-   \end{align}
-Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.
-Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
-\begin{equation}
- ~\label{eq:memcur}
-  f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})-g_{\leak}(v_{i}-v_{\leak}) + I.
-\end{equation}
-The currents include a constant current $I$, and three ionic currents:
-an instantaneous calcium current, a potassium current, and a leak current, with respective reversal potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances $g_{\ca}$, $g_{\k}$, and $g_{\leak}$.
-The function $h(v_{i}, w_{i})$ models the kinetics of the potassium gating variable $w_{i}$, and is given by
-\begin{equation}
-  h(v_{i}, w_{i})=\frac{w_{\infty}(v_{i})-w_{i}}{\tau_{w}}~\label{eq:h}.
-\end{equation}
-The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the \textbf{Supplementary Material S1}.
-
-The dynamics of the synaptic interactions between the neurons are governed by a synaptic gating variable $s_{i}$ and a depression variable $d_{i}$:
-\begin{linenomath}
-  \begin{align}
-    \dot s_{i} &= -s_{i}/\tau_{s}~\label{eq:dot-s},\\
-    \dot d_{i} &= (1-d_{i})/\tau_{d}~\label{eq:dot-d}.
-  \end{align}
-\end{linenomath}
-Variable $d_{i}$ describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
-Our model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
-In between spikes $s_{i}$ decays with time constant $\tau_{s}$, while $d_{i}$ recovers with time constant $\tau_{d}$.
-Because synaptic depression occurs on a much slower timescale than synaptic inhibition, we assume $\tau_{d}\gg\tau_{s}$.
-At spike time when the voltage $v_{i}$ crosses a synaptic threshold $v_{\theta}$, the synaptic variable $s_{i}$ is reset to the current value of $d_{i}$, and $d_{i}$ is scaled down by the depression strength parameter $\lambda$, where $0<\lambda<1$.
-This results in the following discontinuous reset rule on spike time:
-\begin{linenomath}
-  \begin{align}
-    s_{i} &\leftarrow d_{i}~\label{eq:s-reset},\\
-    d_{i} &\leftarrow \lambda d_{i}~\label{eq:d-reset}.
-  \end{align}
-\end{linenomath}
-The equations for the depression model were adapted from the~\citet{bose2001} model.
-These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by~\citet{tsodyks1997}.
-The original equations in~\cite{bose2001} include an exponential decay of $d_{i}$ throughout the active phase of the action potential, that is $\dot d_{i}=-d_{i}/\tau_{\beta}$ for $v_{i}>v_{\theta}$.
-To simplify the mathematical analysis we have reduced these dynamics to a single-reset event at spike time according to \cref{eq:d-reset}.
-This simplification is natural given an approximately constant duration of the active phase of an action potential, and it will become evident from our results that this simplification does not qualitatively change the dynamics of the network compared to the original equations, where depression dynamics are described by an exponential decay.
-
-When the cells are uncoupled ($\gbar=0$), the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
-The two curves intersect along the middle branch of $v_{\infty}$, creating an unstable fixed point $p_{f}=(v_{f},w_{f})$ with a surrounding stable limit cycle of period $T$ (\cref{fig:nullclines}A).
-Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
-The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
-During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
-Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
-During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
-
-The two-cell network model is numerically integrated using an adaptive step-size integrator for stiff differential equations implemented with XPPAUT~\citep{ermentrout2002} and controlled through the Python packages SciPy~\citep{scipy2020} and PyXPP~\citep{pyxpp}.
-The following mathematical analysis is performed on the equations of a single cell.
-Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
-
-\section{Results}
-\subsection{Anti-phase burst solutions}
-Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism~\citep{brown1911} and is known to produce $n-n$ anti-phase burst solutions of varying period.
-Such $n-n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
-\Cref{fig:depression-traces}A shows the timecourse of a typical $4-4$ burst.
-While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
-Therefore, at any given moment one cell is spiking while the other is inhibited.
-Consistent with~\citet{bose2011} we will refer to the currently firing cell as ``free'' and we will call the inhibited cell ``quiet''.
-Additionally, we will distinguish between two phases of a $n-n$ solution:
-We will refer to the burst duration of a cell as the ``free phase'', which is the time between the first spike and the last spike in a burst.
-And we will call the remaining duration of a cycle, when a cell is not spiking, the ``quiet phase''.
-
-% TODO: Add mention of gstar. Once critical conductance is crossed, cell is released.
-With each action potential of the free cell, short-term depression leads to a step-wise decrease of $d$, and consequently of $s$ (\cref{fig:depression-traces}B).
-If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\gbar s$ will eventually become sufficiently small to allow for the quiet cell to be released and start firing, thus inhibiting the previously free cell.
-While a cell is quiet its depression variable can recover.
-Once the quiet cell becomes free again its synaptic inhibition will be sufficient to terminate the burst of the previously free cell and commence a new cycle.
-As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\gbar$ determines the type of $n-n$ solution.
-Increasing $\gbar$ produces higher $n-n$ burst solutions with more spikes per burst and a longer cycle period.
-\Cref{fig:burst-sols} shows numerically stable $n-n$ solutions for varying values of $\gbar$.
-For small values of $\gbar$ the network produces anti-phase spiking $1-1$ solutions.
-As $\gbar$ is increased the network generates solutions of increasing $n$, that is $2-2$, $3-3$, and $4-4$.
-When $\gbar$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
-Depending on the initial conditions either of the two cells can become the suppressed cell, which is why the suppressed solution is numerically bistable.
-
-Branches of numerically stable $n-n$ solutions and their associated limit cycle period for varying values of $\gbar$ are depicted in \cref{fig:bif-diagram}A (see  \textbf{Supplementary Material S2} for algorithm description).
-Not only do higher $n-n$ solutions branches require stronger coupling $\gbar$, but also within $n-n$ branches the period increases with $\gbar$.
-In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2-2$ and $3-3$ solution branches.
-Branches of higher $n-n$ burst solutions occur on increasingly smaller intervals of $\gbar$, for instance is the $\gbar$ interval of the $5-5$ branch shorter than that of the $4-4$ branch and so on.
-The interval between the $5-5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n-n$ solutions, such as $11-11$ bursts, but also other non-symmetric $n-m$ solutions as well irregular, non-periodic solutions.
-However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n-n$ solutions.
-
-\subsection{Mathematical analysis of two-cell network}
-~\label{sec:assumptions}
-% Summary of assumptions
-The goal of the following mathematical analysis is to reduce the complexity of the eight-dimensional system to some easily tractable quantity.
-As we will see later this quantity is the value of the depression variable $d$ of either of the two cells.
-We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the free phase, and then during the quiet phase.
-This construction will require two assumptions about the membrane and synaptic dynamics.
-The first assumption states that during a burst the free cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
-The second assumption states that once the inhibitory conductance acting on the quiet cell drops below a critical threshold, the cell is immediately released and fires.
-The second assumption is necessary to predict the release time of the quiet cell, which allows us to model the recovery of $d$ during the quiet phase.
-In other words, the second assumption requires that the release of the quiet cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the quiet cell.
-Both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
-Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n-n$ solutions.
-However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.
-
-% Assumption 1: Free phase
-Our first assumption about the model states that the free cell fires at its uncoupled period $T$, that is, during the free phase of a burst we have $ISI=T$.
-Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
-We can further numerically confirm this observation by capturing the $ISI$s of the stable solutions from the bifurcation diagram in \cref{fig:bif-diagram}A.
-In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the quiet phase of the burst.
-$IBI$s lie on multiple branches, each branch associated with a stable $n-n$ solution, and are monotonically increasing with $\gbar$.
-In contrast, $ISI$s are calculated from the spikes within the free phase and do not vary significantly with $\gbar$, but are approximately $ISI\approx T$, affirming our first assumption.
-Assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the free phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
-Assuming $ISI=T$ seems reasonable given that inhibition acting on the quiet cell decays exponentially to zero on a much shorter timescale than the duration of the $ISI$, and therefore, once the quiet cell is released its trajectory quickly approaches the spiking limit cycle.
-
-% Assumption 2: Release
-Our second assumption states that the quiet cell is released and spikes as soon as inhibition from the free cell drops below a constant threshold.
-We will now define such a ``release condition'' by exploiting the discrepancy in timescales between the fast membrane dynamics, and the slower synaptic dynamics.
-Let us first consider the dynamics of a single Morris-Lecar neuron.
-We fix the synaptic variable that acts on the cell by setting $s=1$, which also makes the applied synaptic conductance $\gbar s$ constant.
-Recall from \cref{fig:nullclines}A that in case of a single uncoupled cell ($\gbar s=0$), the $v$- and $w$-nullclines intersect at some unstable fixed point $p_{f}=(v_{f},w_{f})$, while trajectories revolve around a stable spiking limit cycle.
-Increasing $\gbar s$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point $p_{f}$ down the sigmoid $w_{\infty}$ in the $(v-w)$-plane (\cref{fig:nullclines-coupled}).
-When $\gbar s$ is large enough, the fixed point $p_{f}$ becomes stable, attracting all previously periodic trajectories.
-There exists a unique value $\gbar s=g^{\star}$ when $p_{f}$ changes stability and the stable limit cycle vanishes.
-Thus, when a constant inhibitory conductance is applied, $\gbar s<g^{\star}$ acts as a necessary condition for a cell to spike.
-In contrast, when $\gbar s>g^{\star}$ inhibition is strong enough to prevent a cell from spiking~\citep{bose2011}.
-
-% NOTE
-% In our parameter range the bifurcations occur via subcritical Hopf (bose2011 p.47)
-
-Now let us analyse the nullclines of the quiet cell when the two cells are coupled via synaptic inhibition with depression.
-Let $\gbar s$ here denote the total synaptic conductance which acts on the quiet cell and is produced by the free cell, and let $p_{f}$ be the fixed point associated with the quiet cell.
-At the start of the burst of the free cell we have $\gbar s > g^{\star}$ and $p_{f}$ is stable.
-When the free cell spikes, $\gbar s$ peaks (\cref{eq:s-reset}), and the $v$-nullcline with the ensuing stable $p_f$ move down the $w$-nullcline.
-Then in between spikes $\gbar s$ decays exponentially (\cref{eq:dot-s}) causing the $v$-nullcline and $p_{f}$ to move up the $w$-nullcline while attracting trajectories of the quiet cell.
-Once depression causes the synaptic conductance to become small enough to satisfy $\gbar s<g^{\star}$ and the quiet cell is released, fixed point $p_{f}$ becomes unstable allowing the quiet cell to fire.
-If the trajectory of the quiet cell remains sufficiently close to the stable $p_{f}$ at the time when it changes stability, then $\gbar s < g^{\star}$ acts as a release condition that is not only necessary, but also sufficient for firing of the quiet cell.
-In this case the release of the quiet cell occurs precisely when
-\begin{equation}
- ~\label{eq:release}
-  \gbar s=g^{\star}
-\end{equation}
-is satisfied.
-
-Whether the $(v,w)$-trajectory of the quiet cell can remain close enough to $p_{f}$ to make \cref{eq:release} sufficient for firing depends largely on the coupling strength $\gbar$ and the timescale disparity between membrane dynamics and synaptic dynamics~\citep{bose2011}.
-It is straightforward to test our assumption of a release condition by numerically integrating the full system of ODEs and calculating the time interval between the first spike of the quiet cell and the time when $\gbar s$ first crosses $g^{\star}$.
-We will call this time interval the ``release delay''.
-If our assumption holds, we would expect an approximately zero release delay.
-\Cref{fig:release-delay} shows the numerically computed graph of the release delay for varying $\gbar$.
-The graph shows three distinct branches, next to each branch we also plot the timecourse of a corresponding sample solution of the total synaptic conductance $\gbar s$ of both cells.
-For the rightmost branch where $\gbar>0.592$ $\si{mS/cm^{2}}$ the release delay is approximately zero.
-Here the first spike of the quiet cell can be accurately predicted by the release condition in \cref{eq:release}.
-The leftmost and middle branches for $\gbar<0.592$ $\si{mS/cm^{2}}$  show a release delay greater than zero, the quiet cell does not immediately fire when the release condition is first satisfied, and \cref{eq:release} does not accurately predict the release of the quiet cell.
-The leftmost and middle branches contain $1-1$ and $2-2$ solutions respectively.
-In both cases the coupling $\gbar$ is not sufficiently strong to allow trajectories of the quiet cell to be close enough to $p_{f}$ to guarantee spiking once $\gbar$ crosses $g^{\star}$.
-Note that in the middle branch $\gbar s $ crosses $g^{\star}$ twice, and only after the second crossing does the quiet cell fire.
-The following map construction relies on the assumption that the release condition in \cref{eq:release} can accurately predict the release time of the quiet cell.
-Given our model parameters this is only possible for sufficiently large $\gbar>0.592 $ $\si{mS/cm^{2}}$.
-For completeness, however, we will also consider values $\gbar < 0.592$ $\si{mS/cm^{2}}$ in the following analysis, bearing in mind that in this parameter range our map will not be accurate.
-
-In summary: For $\gbar>0.592$ $\si{mS/cm^{2}}$ the release condition is sufficient to predict when the quiet cell is released.
-Due to the symmetry of $n-n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
-The release time therefore uniquely determines the type of $n-n$ solution.
-Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the quiet cell.
-Instead, the solution of the synaptic variable $s$ of the free cell is sufficient to predict when $\gbar s=g^{*}$ is satisfied.
-Finally, $s$ is solely determined by the evolution of the depression variable $d$ of the free cell.
-Constructing a solution of $d$ during the free phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
-However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
-In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n-n$ solutions.
-
-\subsection{Construction of the scalar Poincaré map}
-In this section we construct the scalar Poincaré map $\Pi_{n}:d^{\star}\mapsto d^{\star}$.
-Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n-n$ burst.
-The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
-To simplify the map construction we will assume that a free cell fires exactly $n$ times before it becomes quiet.
-Later we will relax this assumption.
-We will construct $\Pi_{n}$ by evolving $d$ first during the free phase and then during the quiet phase of the $n-n$ limit cycle.
-First, let us give explicit definitions of the free and quiet phases.
-A schematic illustration of both phases is given in \cref{fig:free-quiet1}.
-
-Suppose that at $t=0$ cell 1 becomes free with some initial $d(0)$. 
-Cell 1 then fires $n$ spikes at the uncoupled period $T$.
-Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
-After $n$ spikes the total conductance $\gbar s(t)$ acting on the quiet cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}, that is at some time $t=(n-1)T+\delt$ we have $\gbar s(t)=g^{\star}$.
-Cell 2 is then released and prevents cell 1 from further spiking.
-Here $\delt$ is the \emph{inter-burst-interval}, or the time between the last spike of cell 1 and the first spike of cell 2~\citep{bose2011}.
-Once released, cell 2 also fires $n$ spikes until cell 1 becomes free once again at the cycle period.
-Let $P_n$ denote the full cycle period of a $n-n$ solution:
-\begin{equation}
- ~\label{eq:P}
-  P_n = 2(n-1)T + 2\delt.
-\end{equation}
-We can now define the free and quiet phases of cell 1 explicitly. The free phase is the time interval between the first and last spikes of the burst, that is for time $0<t<(n-1)T$.
-During the free phase of cell 1, the quiet cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\gbar s > g^{\star}$.
-The quiet phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T < t < 2(n-1)T + 2\delt$.
-
-Note that only the quiet phase depends on $\delt$, and $\delt$ will play a central role in the construction of $\Pi_{n}$.
-From \cref{eq:P} $\delt$ can be be computed as
-\begin{equation}
- ~\label{eq:delta-t-P}
-  \delt = \frac{1}{2}P_n - (n-1)T.
-\end{equation}
-\noindent
-We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n-n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\delt$ as a function of $\gbar$ (\cref{fig:delta-t}).
-Each continuous branch of $\delt$ is monotonically increasing and corresponds to a $n-n$ burst:
-Stronger coupling $\gbar$ increases the total synaptic conductance $\gbar s$ that acts on the quiet cell, thus delaying its release.
-It is easy to see that for any $n$-branch we have $\delt<T$:
-Once $\delt$ crosses $T$, the free cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1)-(n+1)$ burst.
-
-Distinguishing between the free and quiet phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
-As can be seen from \cref{fig:free-quiet1}C, during the free phase $d$ depresses at spike times and recovers in the $ISI$s.
-In contrast, during the quiet phase $d$ only recovers and does not depress.
-Given the initial $d^{\star}=d(0)$ at the beginning of the cycle and the number of spikes in the free phase $n$, we can now construct the burst map $\Pi_{n}$.
-The map
-\begin{equation}
-  \Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star}\big))
-\end{equation}
-\noindent
-is a composition of two maps.
-Map
-\begin{equation}
-  F_{n}:d^{\star}\mapsto \delt
-\end{equation}
-models the evolution of $d$ in the free phase.
-$F_{n}$ takes an initial value $d^{\star}$ and calculates the inter-burst-interval $\delt$.
-Map
-\begin{equation}
-  Q_{n}:\delt \mapsto d^{\star}
-\end{equation}
-models the recovery of $d$ in the quiet phase.
-Given some $\delt$ map $Q_n$ computes $\dstar$ at the start of the next cycle.
-
-Our aim in the following analysis is to elucidate the properties of $\Pi_{n}$ and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of $\Pi_{n}$ are created.
-To that effect it will be useful to include not only positive, but also negative values of $d^{\star}$ to the domain of $\Pi_{n}$.
-But it is important to add that values $d^{\star}<0$ are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
-Because $\Pi_{n}$ maps first from $d^{\star}$ to $\delt$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n-n$ solutions with partially overlapping bursts.
-As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n-n$ solutions of the full system of ODEs only exist for $\Delta t>0$.
-
-We start the construction of $\Pi_n$ by first considering the free phase and building the map $F_n$.
-At each spike time $t_{k}$, variable $d$ depresses with the reset $d(t_{k})\leftarrow \lambda d(t_{k}^{-})$ (\cref{eq:d-reset}).
-For the duration of the subsequent $ISI$, the recovery of $d$ is described by the solution to \cref{eq:dot-d}:
-\begin{equation}
-  d(t) = 1 - (1-\lambda d_{k})e^{-t/\tau_{d}}~\label{eq:d-sol},
-\end{equation}
-where the variable $d_{k}=d(t^{-}_{k})$ is the level of depression at spike time $t_{k}$.
-By substituting $t=T$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the free phase:
-\begin{equation}
-  d_{k+1} = \lambda\rho d_{k} + (1-\rho),~\label{eq:map-d}
-\end{equation}
-where to keep the notation simple we let $\rho=\exp(-T/\tau_{d})$.
-Since $0<\lambda, \rho<1$, the map~\eqref{eq:map-d} is increasing and contracting, with a fixed point at
-\begin{equation}
- ~\label{eq:dsup}
-  d_{s}=\frac{1-\rho}{1-\lambda\rho},
-\end{equation}
-where $0<d_{s}<1$.
-The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
-Using the release condition in \cref{eq:release} allows us to derive the value of the the minimum coupling strength that will produce the full suppressed solution, denoted as $\gbar_{s}$.
-Solving \cref{eq:dot-s} for $s(t)$ with $t=T$ and setting the initial value $s(0)=d_{s}$ gives
-\begin{equation}
-\gbar_{s} d_{s}e^{-T/\tau_{s}}=g^{\star}.
-\end{equation}
-By further substituting the definition of $d_{s}$ in~\eqref{eq:dsup} and rearranging, we can write $\gbar_{s}$ as a function of the depression strength $\lambda$:
-\begin{equation}
-  \label{eq:gs}
-  \gbar_{s}(\lambda) = g^{\star}e^{T/\tau_{s}}\frac{1-\lambda \rho}{1-\rho}.
-\end{equation}
-Note that the above dependence of $\gbar_{s}$ on $\lambda$ is linear and monotonically decreasing.
-Increasing $\lambda$ reduces the strength of the depression of the free cell.
-This in turn allows the free cell to fully suppress the quiet cell at smaller values of $\gbar$.
-
-Solving~\eqref{eq:map-d} gives us the linear map $\delta_{n}:d^{\star}\mapsto d_{n}$, that for some initial $d^{\star}$ computes the depression at the $n$th spike time, $d_{n}=d(t_{n}^{-})$:
-\begin{equation}
- ~\label{eq:delta-map}
-  \delta_{n}(d^{\star}) = (\lambda \rho)^{n-1} d^{\star} + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}.
-\end{equation}
-Since $\lambda < 1$, function $\delta_{n}$ is a linearly increasing function of $d^{\star}$ with a fixed point at $d_{s}$ for all $n$.
-Having identified $d$ after $n$ spikes, we can now use the release condition $\gbar s = g^{\star}$ (\cref{eq:release}) to find $\delt$.
-At the last spike of the free phase at time $t_{n}=(n-1)T$ the synapse variable $s$ is reset according to \cref{eq:s-reset}:
-\begin{equation}
-  s(t_{n})\leftarrow \dn(\dstar).
-\end{equation}
-After the last spike $s$ decays exponentially according to the solution of \cref{eq:dot-s}, where setting the initial condition $s(0)=\dn(\dstar)$ yields:
-\begin{equation}
-~\label{eq:s-sol}
-  s(\delt)=\dn(\dstar)e^{-\Delta t/\tau_{s}}.
-\end{equation}
-Substituting $s(\delt)$ into $s$ of the release condition (\cref{eq:release}) gives then
-\begin{equation}
- ~\label{eq:release2}
-  \gbar \dn(\dstar) e^{-\delt/\tau_{s}}=g^{\star}.
-\end{equation}
-Our assumption of the release condition guarantees that the quiet cell 2 spikes and becomes free when $\gbar s - g^{\star}$ crosses zero.
-Solving \cref{eq:release2} for $\delt$ allows us to compute the inter-spike-interval as a function of $\dstar$, which defines our map $F_n$:
-\begin{equation}
- ~\label{eq:Fn-map}
-  F_{n}(d^{\star}):=\tau_{s}\ln{\left(\frac{\gbar }{g^{\star}} \delta_{n}(d^{\star})\right)}= \delt.
-\end{equation}
-
-\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\gbar$.
-Larger values of $d^{\star}$ and $\gbar$, respectively, cause stronger inhibition of the quiet cell, and therefore prolong its release time and the associated $\delt$.
-Map $F_{n}$ is defined on $d^{\star}>d_{a}$, where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(\dstar)=0$ in \cref{eq:delta-map} for $\dstar$, which yields
-\begin{equation}
-  d_{a}(n)=-\frac{(1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}}{ (\lambda \rho)^{n-1} }\leq 0~\label{eq:da}.
-\end{equation}
-
-We now turn to the construction of map $Q_{n}$, which describes the recovery of the depression variable during the quiet phase.
-As we have identified earlier, the recovery in the quiet phase of a $n-n$ solution is of duration $2\delt +(n-1)T$.
-Substituting that into the solution for $d(t)$ (\cref{eq:d-sol}) with the initial condition $d(0)=\dn(\dstar)$ yields the map $Q_{n}$:
-\begin{equation}
- ~\label{eq:Qn-map}
-  Q_{n}(\delt):=1- (1- \lambda \dn(\dstar))e^{-(2\Delta t+(n-1)T)/\tau_{d}}.
-\end{equation}
-Given $\delt$, we can find $\dn(\dstar)$ by rearranging the release condition in \cref{eq:release2}:
-\begin{equation}
- ~\label{eq:dn}
-  \dn(\dstar) = \frac{g^{\star}}{\gbar} e^{\delt/\tau_{s}}.
-\end{equation}
-Map $Q_{n}$ is shown in \cref{fig:FQ-map}B for various values $n$.
-Note that $Q_{n}$ is monotonically increasing as larger values $\delt$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
-All curves $Q_{n}$ intersect at some $\delt = \tau_{s}\ln{\left[\gbar/(g^{\star}\lambda)\right]}$ where
-\begin{equation}
-     ~\label{eq:Qn-intersect}
-      Q_{n}\left[\tau_{s}\ln{\left(\frac{\gbar}{g^{\star}\lambda}\right)}\right]=1.
-    \end{equation}
-As we will show in the next section, all fixed points of the full map $\Pi_{n}$ occur for $d^{\star}<1$.
-We will therefore restrict the domain of $Q_{n}$ to $(-\infty, \ln{\left[\gbar/(g^{\star}\lambda)\right]}\tau_{s})$ and the codomain to $(-\infty, 1)$.
-Additionally, while values $\delt>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t=T$, and we will address this concern in the last part of our map analysis.
-
-Having found $F_{n}$ and $Q_{n}$, we can now construct the full map $\Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star})\big)$:
-\begin{equation}
- ~\label{eq:Pn-map}
-  \Pi_{n}(d^{\star})= 1-
-\frac{\rho^{n-1}{g^{\star}}^{\tau}}{{\gbar}^{\tau}}\delta_{n}^{-\tau}(d^{\star})\big(1-\lambda\delta_{n}(d^{\star})\big),
-\end{equation}
-where we substituted $\tau = 2\tau_{s}/\tau_{d}$.
-Since $d$ is the slowest variable of the system and $\tau_{d}\gg \tau_{s}$, we will also assume $\tau<1$.
-\Cref{fig:Pn-map}A depicts $\Pi_{n}$ for various $n$.
-Intersections of $\Pi_{n}$ with the diagonal are fixed points of the map.
-\Cref{fig:Pn-map}B shows $\Pi_{2}$ with $n=2$.
-Varying the synaptic strength $\gbar$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
-For $\gbar<0.03$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
-As $\gbar$ is increased to $\gbar \approx 0.03$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
-When $\gbar > 0.03$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
-
-From \cref{eq:Pn-map} it is evident that $\Pi_{n}$ is monotonically increasing with respect to $\gbar$ and also $\dstar$:
-\begin{align}
-  \label{eq:non-degen1}
-  \dv{\Pi_{n}}{\gbar}&>0,\\[0.5ex]
-  \label{eq:dPidd}
-  \dv{\Pi_{n}}{\dstar}&>0,
-\end{align}
-and in the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
-Just as $F_{n}$, curves $\Pi_{n}$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
-\begin{equation}
-  \lim_{\gbar \to \infty}\Pi_{n} = 1\text{ for all }n,
-\end{equation}
-fixed points of $\Pi_{n}$ lie in $(d_{a}, 1)$.
-
-% \subsection{Existence and stability of fixed points of $\mathit{\Pi_{n}}$}
-\subsection{Existence and stability of fixed points}
-We introduce the fixed point notation $\dstar_{f}$ with $\Pi_{n}(\dstar_{f})=\dstar_{f}$.
-The existence of fixed points $\dstar_{f}$ for $\gbar$ sufficiently large can be shown from the strict monotonicity of $\Pi_{n}$ with respect to $\gbar$ and $\dstar$ (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of $\Pi_{n}$ is monotonically decreasing,
-\begin{equation}
-  \label{eq:non-degen2}
-  \left(\frac{\mathrm{d}}{\mathrm{d}\dstar}\right)^2 \Pi_{n}<0.
-\end{equation}
-In the limit $\dstar \to d_{a}$ the value of $\Pi_n$ decreases without bound for any $\gbar>0$.
-In the limit $\gbar \to 0$, $\Pi_n$ also decreases without bound, but as $\gbar \to \infty$ values of $\Pi_n$ approach $1$.
-It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some $\gbar$ large enough $\Pi_n$ intersects the diagonal.
-Moreover, because $\Pi_n$ and its slope are monotonic with respect to $\dstar$, there exists some critical fixed point $(\dstar_b, \gbar_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
-\begin{align}
-  \Pi_{n}(\dstar_{b}; \gbar_{b}) &=\dstar_{b},\\
-  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b})&=1.
-\end{align}
-Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(\dstar_{b}, \gbar_{b})$ map $\Pi_{n}$ has the topological normal form described by the graph of
-\begin{equation}
-  \label{eq:normal-form}
-  x\mapsto \beta+x-x^{2},
-\end{equation}
-with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.
-
-\subsection{Fold bifurcations}
-Fixed points of $\Pi_n$ satisfy the fixed point equation
-\begin{equation}
-  \label{eq:Phi}
-  \Phi_n(\dstar; \gbar)=0,
-\end{equation}
-where
-\begin{equation}
- ~\label{eq:Phi-def}
-  \Phi_{n}(d^{\star}, \gbar):=\Pi_{n}(d^{\star}, \gbar)-d^{\star}.
-\end{equation}
-As we have already shown, for $\gbar > \gbar_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
-Solving \cref{eq:Phi} explicitly for $\dstar$ it not trivial, but solving for $\gbar$ is straightforward and given by $\gbar = G_n(\dstar)$, where
-\begin{equation}
- ~\label{eq:g}
-  G_{n}(d^{\star}) := g^{\star} \left(\frac{\rho^{n-1}\delta_{n}^{-\tau}(d^{\star})(1-\lambda\delta_{n}(d^{\star}))}{1-d^{\star}}\right)^{1/\tau}.
-\end{equation}
-Plotting $d^{\star}$ against $\gbar$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
-Note the typical quadratic shape of a fold bifurcation of maps.
-It is also evident that the fold bifurcations occur for increasingly smaller $\gbar$ as $n$ is increased.
-Moreover, we can observe that unstable fixed points have negative values of $d^{\star}$ for $n>1$.
-
-\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(\dstar_{b}(n), \gbar_{b}(n)\big)$, which is the global minimum of $G_{n}(\dstar_f)$:
-\begin{align}
-  \dstar_{b}(n) &= \operatorname{argmin} G_{n}(\dstar_{f}),\\
-  \gbar_{b}(n)  &= \min{G_{n}(\dstar_{f})}.
-\end{align}
-Function $G_{n}$ is strictly monotonic on the respective intervals of $\dstar_f$ that correspond to the stable and unstable fixed points, that is
-\begin{align}
-  \dv{G_n}{\dstar_f}& < 0, \text{ for } \dstar_f>\dstar_b(n) \text{ stable},\\[0.5ex]
-  \dv{G_n}{\dstar_f}& > 0, \text{ for } \dstar_f<\dstar_b(n) \text{ unstable},
-\end{align}
-which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $\dstar_f$.
-Because we are primarily interested in the stable fixed points, we define the stable fixed point function $\dstar_f=\phi_n(\gbar)$ as
-\begin{equation}
-  \label{eq:phi}
-  \phi_{n}(\gbar):= G_{n}^{-1}(\dstar_{f}) \text{ for } \dstar_{f}>\dstar_{b}(n).
-\end{equation}
-Function $\phi_n(\gbar)$ is also monotonic, and is therefore straightforward to compute numerically via root-finding.
-Here we use the Python package Pynverse~\citep{pynverse} for that purpose.
-
-Having found the stable fixed points $\dstar_f$ as a function of the coupling strength $\gbar$, we can now compute the associated cycle period.
-Recall that the period is given by \cref{eq:P}, which we can be written as a function of $\gbar$:
-\begin{equation}
-  \label{eq:period}
-  P_n(\gbar) = 2(n-1)T + 2F_n\big(\underbrace{\phi_n(\gbar)}_{\dstar_f}, \gbar\big),
-\end{equation}
-where map $F_n$ (\cref{eq:Fn-map}) calculates the inter-burst-interval $\delt$ given a stable fixed point $\dstar_f=\phi_n(\gbar)$.
-We plot the predicted period $P_n(\gbar)$ versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
-For $n>1$ our map $\Pi_n$ accurately predicts the period.
-When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for $n=1$ (see \cref{fig:release-delay}), since here $\gbar$ is not sufficiently strong to guarantee the validity of our release condition (\cref{eq:release}).
-
-It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\gbar$.
-This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\gbar), \gbar)=0$ in \cref{eq:Phi}.
-For $\dstar_f=\phi_n(\gbar)>d_b(n)$ we get:
-\begin{equation}
-  \label{eq:dstardg}
-  \dv{\phi_n}{\gbar} = -\frac{\pdv*{\Phi_n}{\gbar}}{\pdv*{\Phi_n}{\dstar}} =
-  \frac{\pdv*{\Pi_n}{\gbar}}{1-\pdv*{\Pi_n}{\dstar}}>0.
-\end{equation}
-The inequality follows from $\pdv*{\Pi_n}{\gbar}>0$ and the fact that $\pdv*{\Pi_n}{\dstar}<1$ for $\dstar>d_b(n)$.
-\Cref{eq:dstardg} allows us to explain why the period $P_n$ increases with $\gbar$, as seen in \cref{fig:folds}B.
-Differentiating $P_n$ gives:
-\begin{equation}
-  \label{eq:dPdg}
-  \dv{P_{n}}{\gbar} = 2\grad F_n(\dstar_f, \gbar) \cdot
-                      \begin{bmatrix}\pdv*{\phi_n}{\gbar}\\[0.5ex] 1\end{bmatrix}>0,
-\end{equation}
-where the partial derivatives of $F_n(\dstar_f, \gbar)$ are:
-\begin{align}
-  \pdv{F_n}{\dstar_f} &= \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar_f)}>0,\\[0.5ex]
-  \pdv{F_n}{\gbar}  &= \frac{\taus}{\gbar}>0.
-\end{align}
-\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation:
-Increasing the coupling strength between the neurons leads to overall stronger inhibition of the quiet cell, which delays its release and leads to a longer cycle period.
-The latter allows more time for the synapse to depress in the free phase and recover in the quiet phase, resulting in overall larger values of $\dstar_f$, that is weaker depression at the burst onset.
-
-While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the free phase contains exactly $n$ spikes.
-As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n-n$ bursts exists only on certain parameter intervals of $\gbar$.
-In the last sub-section we will analyse the mechanisms that guide how the stable $n-n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\gbar$ where such solutions exist.
-
-% TODO: Need to find a better sub-section title that doesn't include 'period increment'
-\subsection{Period increment bifurcations with co-existent attractors}
-Let $\gbar_+(n)$ and $\gbar_-(n)$ denote the left and right parameter borders on $\gbar$ where stable $n-n$ solutions exist.
-That is, as $\gbar$ is increased stable $n-n$ solutions are created at $\gbar_+(n)$ and destroyed at $\gbar_-(n)$.
-When $\gbar$ is reduced beyond $\gbar_+(n)$, $n-n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\gbar$ is increased beyond $\gbar_-(n)$, $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
-Let us briefly recap our observations regarding $\gbar_+(n)$ and $\gbar_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
-For $n>1$ there are the following relations:
-\begin{align}
-  \gbar_+(n) &< \gbar_-(n)\label{eq:easy1},\\
-  \gbar_+(n) &< \gbar_+(n+1)\text{ and } \gbar_-(n)<\gbar_-(n+1)\label{eq:easy2},\\
-  \gbar_+(n+1) &< \gbar_-(n)\label{eq:coexistence},\\
-  \gbar_-(n+1) - \gbar_+(n+1) &< \gbar_-(n) - \gbar_-(n)\label{eq:robustness}.
-\end{align}
-\Cref{eq:easy1,eq:easy2} are self-explanatory.
-\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n-n$ and $(n+1)-(n+1)$ solutions.
-\Cref{eq:robustness} implies that the parameter interval on $\gbar$ of $n-n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
-All of the above relations are reminiscent of the period increment bifurcations with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
-see][]{gardini2012,tramontana2012,avrutin2011,gardini2012}.
-While our maps $\Pi_n$ are fully continuous, the above observation suggests that
-a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
-We will explore what such a map might look like in the discussion.
-
-Let us now find algebraic equations that will allow us to calculate the critical parameters $\gbar_+(n)$ and $\gbar_-(n)$ associated with the period increment bifurcations.
-% BUG: Maybe don't call it period-increment here?
-Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\gbar$:
-\begin{equation}
-  \dv{P_{n}}{\gbar}=2\dv{F_n(\phi_n(\gbar), \gbar)}{\gbar}>0,
-\end{equation}
-that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the quiet cell, and $\delt$ becomes larger.
-Once $\delt=T$, the free cell can produce another spike and the solution bifurcates into a $(n+1)-(n+1)$ solution.
-Note, however, that at $\gbar_+(n)$ the bifurcation into a $(n-1)-(n-1)$ does not occur when $\delt=0$.
-Here the mechanism is different: A sufficient reduction of $\gbar$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the quiet cell to be released one spike earlier.
-
-Using the above reasoning we can now formulate the conditions for both bifurcations at $\gbar_+(n)$ and $\gbar_-(n)$.
-As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $\dstar_f=\phi_n(\gbar)$ (\cref{eq:phi}).
-At the right bifurcation border $\gbar_-(n)$ we have $\delt=T$, and after substituting our $F_{n}$-map (\cref{eq:Fn-map}) this translates into
-\begin{equation}
-  F_n(\phi_n(\gbar), \gbar) = T,
-\end{equation}
-which lets us define a function
-\begin{equation}
-  \label{eq:R}
-  R_{n}(\gbar):=F_n(\phi_n(\gbar), \gbar)-T,
-\end{equation}
-whose root is the desired right bifurcation border $\gbar_-(n)$.
-In case of the left bifurcation border at $\gbar_+(n)$ the release condition is satisfied just before the free cell has produced its $n$th spike, and after the depression variable has been reset $n-1$ times, which gives the condition
-\begin{equation}
-  \gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} = \gstar,
-\end{equation}
-and can be rewritten as a function
-\begin{equation}
-  \label{eq:L}
-  L_{n}(\gbar):=\gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} -\gstar,
-\end{equation}
-whose root is $\gbar_+(n)$.
-Both $R_{n}$ and $L_{n}$ are increasing with respect to $\gbar$, which makes finding their roots numerically straightforward.
-
-\Cref{fig:final-bif} shows the period $P_n(\gbar)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\gbar \in [\gbar_+(n),\gbar_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
-Note that the width of $n-n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
-That is, bursts with more spikes occur on increasingly smaller intervals of $\gbar$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
-We also note the occurrence of bi-stability between pairs of $n-n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in \cref{eq:coexistence}.
-
-As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate for $n>1$.
-Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be $\gbar \approx 0.592\si{mS/cm^2}$ in \cref{fig:release-delay}.
-The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\gbar_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
-However, even for branches of large $n-n$ solutions there is a mismatch between the bifurcation borders.
-Presumably our assumptions on the time scales of $w$ and $s$ dynamics do not hold here, and can only be captured by more complex approximations.
-Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.
-
-\section{Discussion}
 % PROBLEM SUMMARY
@@
 
-\section*{Conflict of Interest Statement}
-The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
-
-\section*{Author Contributions}
-MO and CH contributed to conception and design of the study.
-MO performed numerical computation and analysis.
-All authors contributed to manuscript writing and revision.
-
-\section*{Funding}
-This work was supported by the Wellcome Trust Doctoral Training Programme in Neural Dynamics, Grant no. 099699/Z/12/Z.
-
-\section*{Acknowledgements}
-The first author thanks the Wellcome Trust for financial support of his Ph.D. study.
-We thank Alan Champneys for sharing his insights on non-continuous maps during the course of this research.
-We are also grateful to Alan Roberts and Stephen R. Soffe for their comments on earlier versions of the manuscript.
-
-\section*{Data Availability Statement}
-The datasets generated for this study are available on request to the corresponding author.
-
-% \bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities
-\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
-
-\bibliography{bibliography.bib}
-
-\section*{Figure captions}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/nullclines-uncoupled.pdf}
-  \caption{Periodic solution of relaxation-oscillator model neuron.
-$\bm{\mathrm{(A)}}$ Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue, $v_\infty$) and $w$-nullcline (orange, $w_\infty$).
-Unstable fixed point $p_{f}$ is indicated by an orange dot.
-$\bm{\mathrm{(B)}}$ Corresponding voltage trace $v(t)$ of an action potential.~\label{fig:nullclines}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/depression-traces.pdf}
-  \caption{Solution profiles of a $4-4$ burst.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange).
-$\bm{\mathrm{(B)}}$ Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell 1.~\label{fig:depression-traces}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/burst-sols.pdf}
-  \caption{Voltage traces of both cells of numerically stable solutions for increasing values of the coupling strength $\gbar$ (increasing top to bottom).~\label{fig:burst-sols}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/bif-diagram.pdf}
-  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for increasing coupling strength $\gbar$.
-$\bm{\mathrm{(A)}}$ Period of stable solutions.
-Dashed lines show the interval between the $5-5$ and the suppressed solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals of $\gbar$.
-$\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in $\mathrm{(A)}$.
-Long $ISI$s are associated with the quiet phase of a burst, short $ISI$s with the free phase.
-During the free phase, $ISI$s are of approximately constant duration $T$.\label{fig:bif-diagram}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/nullclines-coupled.pdf}
-  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar s$.
-For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange point).
-Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until $p_{f}$ changes stability (half orange,  half blue point) at some critical total conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
-  \caption{Numerically computed values of the release delay for varying $\gbar$.
-Each of the three branches (A, B, C) also shows the timecourse of the total synaptic conductance $\gbar s$ of a sample stable solution of both cells (blue and orange), as well as the release conductance $g^{\star}$ (dashed green line).
-$\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution.
-Here the quiet cell only spikes after a significant release delay.
-$\bm{\mathrm{(B)}}$ Branch with a long release delay associated with a subset of $2-2$ solutions.
-Here the release condition is briefly satisfied after the first spike of cell 1.
-This does not cause firing of cell 2, which only occurs after the second spike of cell 1.
-$\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is approximately zero and the release condition is sufficient for firing of cell 2.
-   ~\label{fig:release-delay}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/free-quiet.pdf}
-  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
-The grey patches depict inter-burst-intervals $\delt$.
-$\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$.
-$\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/delta-t.pdf}
-  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
-Each continuous branch is associated with a stable $n-n$ burst solution.
-Increasing $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx T$.~\label{fig:delta-t}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/FQ-map.pdf}
-  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$.
-Curves $F_n$ intersect at $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/Pn-map.pdf}
-  \caption{Map $\Pi_{n}:d^{\star}$.
-$\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$ at $\gbar=0.6$ $\si{mS/cm^{2}}$.
-$\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$.
-The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/folds.pdf}
-  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves) and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
-$\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the corresponding solution period from numerical integration of the system of ODEs (orange).~\label{fig:folds}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
-  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
-\end{figure}
-
 \end{document}

### 2022-02-04 tex/sections/introduction.tex
Split latex document into subfiles

--- 2022-01-26 tex/draft.tex
@@
-\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and
-\usepackage{graphicx}
-\usepackage{amssymb}
-\usepackage{siunitx}
-\usepackage{amsmath}
-\usepackage{soul}
-\usepackage{physics}
-\usepackage{bm}
-
-\usepackage{url,hyperref,microtype,subcaption}
-\usepackage[onehalfspacing]{setspace}
-\usepackage{cleveref}
-% \usepackage[font={bold,it}]{caption}
-
-% Define better ref abbreviations
-\usepackage[displaymath]{lineno}
-
-\renewcommand{\d}{\mathrm{d}}
-\renewcommand{\k}{\mathrm{K}}
-\newcommand{\ca}{\mathrm{Ca}}
-\newcommand{\na}{\mathrm{Na}}
-\newcommand{\leak}{\mathrm{L}}
-\newcommand{\dstar}{d^\star}
-\newcommand{\gstar}{g^\star}
-\newcommand{\gbar}{\bar g}
-\newcommand{\delt}{\Delta t}
-\newcommand{\taus}{\tau_s}
-\newcommand{\dn}{\delta_n}
-\newcommand{\taud}{\tau_d}
-
-\linenumbers
-
-\def\keyFont{\fontsize{8}{11}\helveticabold }
-\def\firstAuthorLast{Olenik {et~al.}} %use et al only if is more than 1 author
-\def\Authors{Mark Olenik\,$^{1,*}$, and Conor Houghton\,$^{2}$}
-% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
-% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
-\def\Address{$^{1}$School of Biological Sciences, Faculty of Life Sciences, University of Bristol, Bristol, United Kingdom \\
-$^{2}$School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, Faculty of Engineering, University of Bristol, Bristol, United Kingdom}
-% The Corresponding Author should be marked with an asterisk
-% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
-\def\corrAuthor{Mark Olenik}
-
-\def\corrEmail{m.olenik@bristol.ac.uk}
+\documentclass[../manuscript.tex]{subfiles}
+\graphicspath{{../figures/}}
 
 \begin{document}
-
-\onecolumn
-\firstpage{1}
-
-\title[Scalar Poincaré map for bursting]{A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression.}
-
-\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
-\address{} %This field will be automatically populated
-\correspondance{} %This field will be automatically populated
-
-\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
-%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
-
-\maketitle
-
-\begin{abstract}
-\section{}
-Short-term synaptic plasticity is found in many areas of the central
-nervous system.  In the inhibitory half-centre central pattern
-generators involved in locomotion, synaptic depression is believed to
-act as a burst termination mechanism, allowing networks to generate
-anti-phase bursting patterns of varying periods.  To better understand
-burst generation in these central patter generators, we study a
-minimal network of two neurons coupled through depressing synapses.
-Depending on the strength of the synaptic conductance between the two
-neurons, this network can produce symmetric $n-n$ anti-phase bursts,
-where neurons fire $n$ spikes in alternation, with the period of such
-solutions increasing with the strength of the synaptic conductance.
-Relying on the timescale disparity in the model, we reduce the
-eight-dimensional network equations to a fully-explicit scalar
-Poincaré burst map.  This map tracks the state of synaptic depression
-from one burst to the next and captures the complex bursting dynamics
-of the network.  Fixed points of this map are associated with stable
-burst solutions of the full network model, and are created through
-fold bifurcations of maps.  We derive conditions that describe
-period-increment bifurcations between stable $n-n$ and $(n+1)-(n+1)$
-bursts, producing a full bifurcation diagram of the burst cycle
-period.  Predictions of the Poincaré map fit excellently with
-numerical simulations of the full network model and allow the study of
-parameter sensitivity for rhythm generation.
-
-\tiny
- \keyFont{ \section{Keywords:} Synaptic depression, Poincaré map, Dynamical system, Neuronal bursting, Central pattern generator}
-
-\end{abstract}
-
-\section{Introduction}
 % DEPRESSION
-Short-term synaptic plasticity may have a role in burst activity in
-central pattern generators (CPGs).  Short-term synaptic depression is
-commonly found in neuronal networks involved in the generation of
-rhythmic movements, such as in the pyloric CPG of the spiny
-lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of
-the chick embryo~\citep{donovan1998}.  Synaptic depression modulates
-the strength of synapses in response to changes to the presynaptic
-firing frequency.  At a high neuronal firing frequency, depression
-weakens the strength of synapses and therefore reduces the magnitude
-of the postsynaptic response.  At low firing frequency, it allows
-sufficient time for the synapse to recover from depression between
-spikes, leading to a stronger postsynaptic response.  In reciprocal
-networks, synaptic depression has been shown to act as a ``switch'',
-giving rise to a wide range of network dynamics such as synchronous
-and multi-stable rhythms, as well as fine tuning the frequency of
-network oscillations~\citep{nadim2000, nadim1999, bose2011}.
+Short-term synaptic plasticity may have a role in burst activity in central pattern
+generators (CPGs).  Short-term synaptic depression is commonly found in neuronal networks
+involved in the generation of rhythmic movements, such as in the pyloric CPG of the spiny
+lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of the chick
+embryo~\citep{donovan1998}.  Synaptic depression modulates the strength of synapses in
+response to changes to the presynaptic firing frequency.  At a high neuronal firing
+frequency, depression weakens the strength of synapses and therefore reduces the magnitude
+of the postsynaptic response.  At low firing frequency, it allows sufficient time for the
+synapse to recover from depression between spikes, leading to a stronger postsynaptic
+response.  In reciprocal networks, synaptic depression has been shown to act as a
+``switch'', giving rise to a wide range of network dynamics such as synchronous and
+multi-stable rhythms, as well as fine tuning the frequency of network
+oscillations~\citep{nadim2000, nadim1999, bose2011}.
 
 % Brown
-~\citet{brown1911} pioneered the idea that synaptic depression acts as
-a burst termination mechanism in reciprocally inhibitory CPGs involved
-in rhythm generation of locomotion. When one side is firing during a
-burst the other, antagonistic side, is prevented from firing by
-synaptic inhibition. However, the weakening of inhibition as a result
-of synaptic depression eventually releases the antagonistic side so
-that it starts firing, terminating the burst on the side that had
-originally been firing.  This rhythmogenesis hypothesis has been
-considered one of a handful of standard mechanisms for generating
-locomotion rhythms in
-vertebrates~\citep{reiss1962,perkel1974,friesen1994}. It has been
-proposed as an explaination of the antiphase burst rhythm in
-struggling in \textit{Xenopus} tadpoles~\citep{li2007}.
+~\citet{brown1911} pioneered the idea that synaptic depression acts as a burst termination
+mechanism in reciprocally inhibitory CPGs involved in rhythm generation of locomotion.
+When one side is firing during a burst the other, antagonistic side, is prevented from
+firing by synaptic inhibition. However, the weakening of inhibition as a result of
+synaptic depression eventually releases the antagonistic side so that it starts firing,
+terminating the burst on the side that had originally been firing.  This rhythmogenesis
+hypothesis has been considered one of a handful of standard mechanisms for generating
+locomotion rhythms in vertebrates~\citep{reiss1962,perkel1974,friesen1994}. It has been
+proposed as an explaination of the antiphase burst rhythm in struggling in
+\textit{Xenopus} tadpoles~\citep{li2007}.
 
-~\citet{bose2011} investigated burst generation in a generic
-half-centre CPG that consists of two identical, tonically active
-Morris-Lecar~\citep{morris1981} neurons coupled through inhibitory
-depressing synapses.  Numerical simulations showed that when the
-reciprocal synaptic conductance between the two neurons is varied, the
-network produces symmetric $n-n$ anti-phase bursts, with stronger
-synaptic coupling leading to longer bursts.  They used methods from
-geometric singular perturbation theory to separate the timescales of
-the fast membrane, and the slow synaptic dynamics of the network to
-derive one-dimensional conditions necessary for the existence of
-stable $n-n$ solutions (for $n\leq 2$). According to these conditions
-the type of firing pattern largely depends on the slow depression
-dynamics of the synapses between the two neurons, and can therefore be
-predicted by knowing the strengths of the synaptic conductances of the
-two synapses.
-Thus, the scalar conditions derived in~\citet{bose2011} provide a
-method to numerically identify the type of stable $n-n$ pattern for
-any given value of the coupling strength.  However, they do not
-predict the exact period of such solutions.
-Furthermore, while they provide good arguments for the validity of
-their reduction assumptions and the resulting scalar conditions, they
-do not verify them numerically.
+~\citet{bose2011} investigated burst generation in a generic half-centre CPG that consists
+of two identical, tonically active Morris-Lecar~\citep{morris1981} neurons coupled through
+inhibitory depressing synapses.  Numerical simulations showed that when the reciprocal
+synaptic conductance between the two neurons is varied, the network produces symmetric
+$n-n$ anti-phase bursts, with stronger synaptic coupling leading to longer bursts.  They
+used methods from geometric singular perturbation theory to separate the timescales of the
+fast membrane, and the slow synaptic dynamics of the network to derive one-dimensional
+conditions necessary for the existence of stable $n-n$ solutions (for $n\leq 2$).
+According to these conditions the type of firing pattern largely depends on the slow
+depression dynamics of the synapses between the two neurons, and can therefore be
+predicted by knowing the strengths of the synaptic conductances of the two synapses.
+Thus, the scalar conditions derived in~\citet{bose2011} provide a method to numerically
+identify the type of stable $n-n$ pattern for any given value of the coupling strength.
+However, they do not predict the exact period of such solutions.  Furthermore, while they
+provide good arguments for the validity of their reduction assumptions and the resulting
+scalar conditions, they do not verify them numerically.
 
-Here we extend the previous analysis by providing a Poincaré map of
-the slow depression dynamics.  This allows us not only to predict the
-types of stable $n-n$ solutions the full network can produce, (for any
-$n$), but also to study how varying the coupling strength affects the
-period of such solutions.  To do this, we build on, and numerically
-test, the assumptions on the fast-slow timescale disparity made
-in~\cite{bose2011}.  We reduce the two-cell model to a scalar
-Poincaré map that tracks the evolution of the depression from the
-beginning of one burst to the beginning of the next burst.  Stable
-fixed points of our map are associated with stable $n-n$ burst
-solutions.  Our map construction is motivated by the burst length map
-of a T-type calcium current, utilised by~\citet{matveev2007}, which
-approximates the anti-phase bursting dynamics of a network of two
-coupled Morris-Lecar neurons.  In contrast to our model, the network
-described in the~\cite{matveev2007} paper does not contain short-term synaptic
-depression, and burst termination is instead accomplished through the
-dynamics of a slow T-type calcium current.
+Here we extend the previous analysis by providing a Poincaré map of the slow depression
+dynamics.  This allows us not only to predict the types of stable $n-n$ solutions the full
+network can produce, (for any $n$), but also to study how varying the coupling strength
+affects the period of such solutions.  To do this, we build on, and numerically test, the
+assumptions on the fast-slow timescale disparity made in~\cite{bose2011}.  We reduce the
+two-cell model to a scalar Poincaré map that tracks the evolution of the depression from
+the beginning of one burst to the beginning of the next burst.  Stable fixed points of our
+map are associated with stable $n-n$ burst solutions.  Our map construction is motivated
+by the burst length map of a T-type calcium current, utilised by~\citet{matveev2007},
+which approximates the anti-phase bursting dynamics of a network of two coupled
+Morris-Lecar neurons.  In contrast to our model, the network described in
+the~\cite{matveev2007} paper does not contain short-term synaptic depression, and burst
+termination is instead accomplished through the dynamics of a slow T-type calcium current.
 
 % MAIN RESULTS AND CONCLUSIONS
-The Poincaré map derived here replicates the results from numerical
-simulations of the full two-cell ODE system: Given the strength of
-maximum conductance between the two neurons, fixed points of our map
-predict the type and period of $n-n$ patterns, the switch between
-burst solutions of different periods, as well as the occurrence of
-co-existent solutions.  In addition to proving the existence and
-stability of fixed points, our map shows that fixed points are created
-via a fold bifurcation of maps.  We also derive algebraic conditions
-that predict the period increment bifurcations that allow the switch
-between $n-n$ and $(n+1)-(n+1)$ solutions.  Because our map is fully
-explicit, it lays the framework for studying the effects of other
-model parameter on network dynamics without the need to run expensive
-numerical integrations of the ODEs.
+The Poincaré map derived here replicates the results from numerical simulations of the
+full two-cell ODE system: Given the strength of maximum conductance between the two
+neurons, fixed points of our map predict the type and period of $n-n$ patterns, the switch
+between burst solutions of different periods, as well as the occurrence of co-existent
+solutions.  In addition to proving the existence and stability of fixed points, our map
+shows that fixed points are created via a fold bifurcation of maps.  We also derive
+algebraic conditions that predict the period increment bifurcations that allow the switch
+between $n-n$ and $(n+1)-(n+1)$ solutions.  Because our map is fully explicit, it lays the
+framework for studying the effects of other model parameter on network dynamics without
+the need to run expensive numerical integrations of the ODEs.
 
 % PAPER STRUCTURE.
-This paper is organised as follows.  First, we introduce the network
-of two neurons, and describe the properties of single cell and synapse
-dynamics.  We use numerical simulations of the network to provide an
-intuition for the range of possible burst dynamics the system can
-produce.  Next, we state and justify the simplifying assumptions that
-are necessary for the map construction.  Finally, we analytically
-derive the first return map of the depression variable as well as the
-conditions that are required for stable solutions to bifurcate between
-$n-n$ and $(n+1)-(n+1)$ solutions.  We end this work with a
-discussion.
-
-\section{Materials and Methods}
-We consider a pair of identical Morris-Lecar neurons~\citep{morris1981}, with parameters adapted from~\cite{bose2011}.
-The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
-The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
-The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
-\begin{align}
-    ~\label{eq:cell-modelA}
-     \dot v_{i}&= f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}),\\
-    ~\label{eq:cell-modelB}
-     \dot w_{i} &=h(v_i,w_i).
-   \end{align}
-Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.
-Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
-\begin{equation}
- ~\label{eq:memcur}
-  f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})-g_{\leak}(v_{i}-v_{\leak}) + I.
-\end{equation}
-The currents include a constant current $I$, and three ionic currents:
-an instantaneous calcium current, a potassium current, and a leak current, with respective reversal potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances $g_{\ca}$, $g_{\k}$, and $g_{\leak}$.
-The function $h(v_{i}, w_{i})$ models the kinetics of the potassium gating variable $w_{i}$, and is given by
-\begin{equation}
-  h(v_{i}, w_{i})=\frac{w_{\infty}(v_{i})-w_{i}}{\tau_{w}}~\label{eq:h}.
-\end{equation}
-The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the \textbf{Supplementary Material S1}.
-
-The dynamics of the synaptic interactions between the neurons are governed by a synaptic gating variable $s_{i}$ and a depression variable $d_{i}$:
-\begin{linenomath}
-  \begin{align}
-    \dot s_{i} &= -s_{i}/\tau_{s}~\label{eq:dot-s},\\
-    \dot d_{i} &= (1-d_{i})/\tau_{d}~\label{eq:dot-d}.
-  \end{align}
-\end{linenomath}
-Variable $d_{i}$ describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
-Our model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
-In between spikes $s_{i}$ decays with time constant $\tau_{s}$, while $d_{i}$ recovers with time constant $\tau_{d}$.
-Because synaptic depression occurs on a much slower timescale than synaptic inhibition, we assume $\tau_{d}\gg\tau_{s}$.
-At spike time when the voltage $v_{i}$ crosses a synaptic threshold $v_{\theta}$, the synaptic variable $s_{i}$ is reset to the current value of $d_{i}$, and $d_{i}$ is scaled down by the depression strength parameter $\lambda$, where $0<\lambda<1$.
-This results in the following discontinuous reset rule on spike time:
-\begin{linenomath}
-  \begin{align}
-    s_{i} &\leftarrow d_{i}~\label{eq:s-reset},\\
-    d_{i} &\leftarrow \lambda d_{i}~\label{eq:d-reset}.
-  \end{align}
-\end{linenomath}
-The equations for the depression model were adapted from the~\citet{bose2001} model.
-These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by~\citet{tsodyks1997}.
-The original equations in~\cite{bose2001} include an exponential decay of $d_{i}$ throughout the active phase of the action potential, that is $\dot d_{i}=-d_{i}/\tau_{\beta}$ for $v_{i}>v_{\theta}$.
-To simplify the mathematical analysis we have reduced these dynamics to a single-reset event at spike time according to \cref{eq:d-reset}.
-This simplification is natural given an approximately constant duration of the active phase of an action potential, and it will become evident from our results that this simplification does not qualitatively change the dynamics of the network compared to the original equations, where depression dynamics are described by an exponential decay.
-
-When the cells are uncoupled ($\gbar=0$), the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
-The two curves intersect along the middle branch of $v_{\infty}$, creating an unstable fixed point $p_{f}=(v_{f},w_{f})$ with a surrounding stable limit cycle of period $T$ (\cref{fig:nullclines}A).
-Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
-The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
-During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
-Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
-During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
-
-The two-cell network model is numerically integrated using an adaptive step-size integrator for stiff differential equations implemented with XPPAUT~\citep{ermentrout2002} and controlled through the Python packages SciPy~\citep{scipy2020} and PyXPP~\citep{pyxpp}.
-The following mathematical analysis is performed on the equations of a single cell.
-Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
-
-\section{Results}
-\subsection{Anti-phase burst solutions}
-Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism~\citep{brown1911} and is known to produce $n-n$ anti-phase burst solutions of varying period.
-Such $n-n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
-\Cref{fig:depression-traces}A shows the timecourse of a typical $4-4$ burst.
-While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
-Therefore, at any given moment one cell is spiking while the other is inhibited.
-Consistent with~\citet{bose2011} we will refer to the currently firing cell as ``free'' and we will call the inhibited cell ``quiet''.
-Additionally, we will distinguish between two phases of a $n-n$ solution:
-We will refer to the burst duration of a cell as the ``free phase'', which is the time between the first spike and the last spike in a burst.
-And we will call the remaining duration of a cycle, when a cell is not spiking, the ``quiet phase''.
-
-% TODO: Add mention of gstar. Once critical conductance is crossed, cell is released.
-With each action potential of the free cell, short-term depression leads to a step-wise decrease of $d$, and consequently of $s$ (\cref{fig:depression-traces}B).
-If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\gbar s$ will eventually become sufficiently small to allow for the quiet cell to be released and start firing, thus inhibiting the previously free cell.
-While a cell is quiet its depression variable can recover.
-Once the quiet cell becomes free again its synaptic inhibition will be sufficient to terminate the burst of the previously free cell and commence a new cycle.
-As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\gbar$ determines the type of $n-n$ solution.
-Increasing $\gbar$ produces higher $n-n$ burst solutions with more spikes per burst and a longer cycle period.
-\Cref{fig:burst-sols} shows numerically stable $n-n$ solutions for varying values of $\gbar$.
-For small values of $\gbar$ the network produces anti-phase spiking $1-1$ solutions.
-As $\gbar$ is increased the network generates solutions of increasing $n$, that is $2-2$, $3-3$, and $4-4$.
-When $\gbar$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
-Depending on the initial conditions either of the two cells can become the suppressed cell, which is why the suppressed solution is numerically bistable.
-
-Branches of numerically stable $n-n$ solutions and their associated limit cycle period for varying values of $\gbar$ are depicted in \cref{fig:bif-diagram}A (see  \textbf{Supplementary Material S2} for algorithm description).
-Not only do higher $n-n$ solutions branches require stronger coupling $\gbar$, but also within $n-n$ branches the period increases with $\gbar$.
-In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2-2$ and $3-3$ solution branches.
-Branches of higher $n-n$ burst solutions occur on increasingly smaller intervals of $\gbar$, for instance is the $\gbar$ interval of the $5-5$ branch shorter than that of the $4-4$ branch and so on.
-The interval between the $5-5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n-n$ solutions, such as $11-11$ bursts, but also other non-symmetric $n-m$ solutions as well irregular, non-periodic solutions.
-However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n-n$ solutions.
-
-\subsection{Mathematical analysis of two-cell network}
-~\label{sec:assumptions}
-% Summary of assumptions
-The goal of the following mathematical analysis is to reduce the complexity of the eight-dimensional system to some easily tractable quantity.
-As we will see later this quantity is the value of the depression variable $d$ of either of the two cells.
-We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the free phase, and then during the quiet phase.
-This construction will require two assumptions about the membrane and synaptic dynamics.
-The first assumption states that during a burst the free cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
-The second assumption states that once the inhibitory conductance acting on the quiet cell drops below a critical threshold, the cell is immediately released and fires.
-The second assumption is necessary to predict the release time of the quiet cell, which allows us to model the recovery of $d$ during the quiet phase.
-In other words, the second assumption requires that the release of the quiet cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the quiet cell.
-Both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
-Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n-n$ solutions.
-However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.
-
-% Assumption 1: Free phase
-Our first assumption about the model states that the free cell fires at its uncoupled period $T$, that is, during the free phase of a burst we have $ISI=T$.
-Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
-We can further numerically confirm this observation by capturing the $ISI$s of the stable solutions from the bifurcation diagram in \cref{fig:bif-diagram}A.
-In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the quiet phase of the burst.
-$IBI$s lie on multiple branches, each branch associated with a stable $n-n$ solution, and are monotonically increasing with $\gbar$.
-In contrast, $ISI$s are calculated from the spikes within the free phase and do not vary significantly with $\gbar$, but are approximately $ISI\approx T$, affirming our first assumption.
-Assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the free phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
-Assuming $ISI=T$ seems reasonable given that inhibition acting on the quiet cell decays exponentially to zero on a much shorter timescale than the duration of the $ISI$, and therefore, once the quiet cell is released its trajectory quickly approaches the spiking limit cycle.
-
-% Assumption 2: Release
-Our second assumption states that the quiet cell is released and spikes as soon as inhibition from the free cell drops below a constant threshold.
-We will now define such a ``release condition'' by exploiting the discrepancy in timescales between the fast membrane dynamics, and the slower synaptic dynamics.
-Let us first consider the dynamics of a single Morris-Lecar neuron.
-We fix the synaptic variable that acts on the cell by setting $s=1$, which also makes the applied synaptic conductance $\gbar s$ constant.
-Recall from \cref{fig:nullclines}A that in case of a single uncoupled cell ($\gbar s=0$), the $v$- and $w$-nullclines intersect at some unstable fixed point $p_{f}=(v_{f},w_{f})$, while trajectories revolve around a stable spiking limit cycle.
-Increasing $\gbar s$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point $p_{f}$ down the sigmoid $w_{\infty}$ in the $(v-w)$-plane (\cref{fig:nullclines-coupled}).
-When $\gbar s$ is large enough, the fixed point $p_{f}$ becomes stable, attracting all previously periodic trajectories.
-There exists a unique value $\gbar s=g^{\star}$ when $p_{f}$ changes stability and the stable limit cycle vanishes.
-Thus, when a constant inhibitory conductance is applied, $\gbar s<g^{\star}$ acts as a necessary condition for a cell to spike.
-In contrast, when $\gbar s>g^{\star}$ inhibition is strong enough to prevent a cell from spiking~\citep{bose2011}.
-
-% NOTE
-% In our parameter range the bifurcations occur via subcritical Hopf (bose2011 p.47)
-
-Now let us analyse the nullclines of the quiet cell when the two cells are coupled via synaptic inhibition with depression.
-Let $\gbar s$ here denote the total synaptic conductance which acts on the quiet cell and is produced by the free cell, and let $p_{f}$ be the fixed point associated with the quiet cell.
-At the start of the burst of the free cell we have $\gbar s > g^{\star}$ and $p_{f}$ is stable.
-When the free cell spikes, $\gbar s$ peaks (\cref{eq:s-reset}), and the $v$-nullcline with the ensuing stable $p_f$ move down the $w$-nullcline.
-Then in between spikes $\gbar s$ decays exponentially (\cref{eq:dot-s}) causing the $v$-nullcline and $p_{f}$ to move up the $w$-nullcline while attracting trajectories of the quiet cell.
-Once depression causes the synaptic conductance to become small enough to satisfy $\gbar s<g^{\star}$ and the quiet cell is released, fixed point $p_{f}$ becomes unstable allowing the quiet cell to fire.
-If the trajectory of the quiet cell remains sufficiently close to the stable $p_{f}$ at the time when it changes stability, then $\gbar s < g^{\star}$ acts as a release condition that is not only necessary, but also sufficient for firing of the quiet cell.
-In this case the release of the quiet cell occurs precisely when
-\begin{equation}
- ~\label{eq:release}
-  \gbar s=g^{\star}
-\end{equation}
-is satisfied.
-
-Whether the $(v,w)$-trajectory of the quiet cell can remain close enough to $p_{f}$ to make \cref{eq:release} sufficient for firing depends largely on the coupling strength $\gbar$ and the timescale disparity between membrane dynamics and synaptic dynamics~\citep{bose2011}.
-It is straightforward to test our assumption of a release condition by numerically integrating the full system of ODEs and calculating the time interval between the first spike of the quiet cell and the time when $\gbar s$ first crosses $g^{\star}$.
-We will call this time interval the ``release delay''.
-If our assumption holds, we would expect an approximately zero release delay.
-\Cref{fig:release-delay} shows the numerically computed graph of the release delay for varying $\gbar$.
-The graph shows three distinct branches, next to each branch we also plot the timecourse of a corresponding sample solution of the total synaptic conductance $\gbar s$ of both cells.
-For the rightmost branch where $\gbar>0.592$ $\si{mS/cm^{2}}$ the release delay is approximately zero.
-Here the first spike of the quiet cell can be accurately predicted by the release condition in \cref{eq:release}.
-The leftmost and middle branches for $\gbar<0.592$ $\si{mS/cm^{2}}$  show a release delay greater than zero, the quiet cell does not immediately fire when the release condition is first satisfied, and \cref{eq:release} does not accurately predict the release of the quiet cell.
-The leftmost and middle branches contain $1-1$ and $2-2$ solutions respectively.
-In both cases the coupling $\gbar$ is not sufficiently strong to allow trajectories of the quiet cell to be close enough to $p_{f}$ to guarantee spiking once $\gbar$ crosses $g^{\star}$.
-Note that in the middle branch $\gbar s $ crosses $g^{\star}$ twice, and only after the second crossing does the quiet cell fire.
-The following map construction relies on the assumption that the release condition in \cref{eq:release} can accurately predict the release time of the quiet cell.
-Given our model parameters this is only possible for sufficiently large $\gbar>0.592 $ $\si{mS/cm^{2}}$.
-For completeness, however, we will also consider values $\gbar < 0.592$ $\si{mS/cm^{2}}$ in the following analysis, bearing in mind that in this parameter range our map will not be accurate.
-
-In summary: For $\gbar>0.592$ $\si{mS/cm^{2}}$ the release condition is sufficient to predict when the quiet cell is released.
-Due to the symmetry of $n-n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
-The release time therefore uniquely determines the type of $n-n$ solution.
-Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the quiet cell.
-Instead, the solution of the synaptic variable $s$ of the free cell is sufficient to predict when $\gbar s=g^{*}$ is satisfied.
-Finally, $s$ is solely determined by the evolution of the depression variable $d$ of the free cell.
-Constructing a solution of $d$ during the free phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
-However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
-In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n-n$ solutions.
-
-\subsection{Construction of the scalar Poincaré map}
-In this section we construct the scalar Poincaré map $\Pi_{n}:d^{\star}\mapsto d^{\star}$.
-Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n-n$ burst.
-The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
-To simplify the map construction we will assume that a free cell fires exactly $n$ times before it becomes quiet.
-Later we will relax this assumption.
-We will construct $\Pi_{n}$ by evolving $d$ first during the free phase and then during the quiet phase of the $n-n$ limit cycle.
-First, let us give explicit definitions of the free and quiet phases.
-A schematic illustration of both phases is given in \cref{fig:free-quiet1}.
-
-Suppose that at $t=0$ cell 1 becomes free with some initial $d(0)$. 
-Cell 1 then fires $n$ spikes at the uncoupled period $T$.
-Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
-After $n$ spikes the total conductance $\gbar s(t)$ acting on the quiet cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}, that is at some time $t=(n-1)T+\delt$ we have $\gbar s(t)=g^{\star}$.
-Cell 2 is then released and prevents cell 1 from further spiking.
-Here $\delt$ is the \emph{inter-burst-interval}, or the time between the last spike of cell 1 and the first spike of cell 2~\citep{bose2011}.
-Once released, cell 2 also fires $n$ spikes until cell 1 becomes free once again at the cycle period.
-Let $P_n$ denote the full cycle period of a $n-n$ solution:
-\begin{equation}
- ~\label{eq:P}
-  P_n = 2(n-1)T + 2\delt.
-\end{equation}
-We can now define the free and quiet phases of cell 1 explicitly. The free phase is the time interval between the first and last spikes of the burst, that is for time $0<t<(n-1)T$.
-During the free phase of cell 1, the quiet cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\gbar s > g^{\star}$.
-The quiet phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T < t < 2(n-1)T + 2\delt$.
-
-Note that only the quiet phase depends on $\delt$, and $\delt$ will play a central role in the construction of $\Pi_{n}$.
-From \cref{eq:P} $\delt$ can be be computed as
-\begin{equation}
- ~\label{eq:delta-t-P}
-  \delt = \frac{1}{2}P_n - (n-1)T.
-\end{equation}
-\noindent
-We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n-n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\delt$ as a function of $\gbar$ (\cref{fig:delta-t}).
-Each continuous branch of $\delt$ is monotonically increasing and corresponds to a $n-n$ burst:
-Stronger coupling $\gbar$ increases the total synaptic conductance $\gbar s$ that acts on the quiet cell, thus delaying its release.
-It is easy to see that for any $n$-branch we have $\delt<T$:
-Once $\delt$ crosses $T$, the free cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1)-(n+1)$ burst.
-
-Distinguishing between the free and quiet phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
-As can be seen from \cref{fig:free-quiet1}C, during the free phase $d$ depresses at spike times and recovers in the $ISI$s.
-In contrast, during the quiet phase $d$ only recovers and does not depress.
-Given the initial $d^{\star}=d(0)$ at the beginning of the cycle and the number of spikes in the free phase $n$, we can now construct the burst map $\Pi_{n}$.
-The map
-\begin{equation}
-  \Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star}\big))
-\end{equation}
-\noindent
-is a composition of two maps.
-Map
-\begin{equation}
-  F_{n}:d^{\star}\mapsto \delt
-\end{equation}
-models the evolution of $d$ in the free phase.
-$F_{n}$ takes an initial value $d^{\star}$ and calculates the inter-burst-interval $\delt$.
-Map
-\begin{equation}
-  Q_{n}:\delt \mapsto d^{\star}
-\end{equation}
-models the recovery of $d$ in the quiet phase.
-Given some $\delt$ map $Q_n$ computes $\dstar$ at the start of the next cycle.
-
-Our aim in the following analysis is to elucidate the properties of $\Pi_{n}$ and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of $\Pi_{n}$ are created.
-To that effect it will be useful to include not only positive, but also negative values of $d^{\star}$ to the domain of $\Pi_{n}$.
-But it is important to add that values $d^{\star}<0$ are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
-Because $\Pi_{n}$ maps first from $d^{\star}$ to $\delt$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n-n$ solutions with partially overlapping bursts.
-As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n-n$ solutions of the full system of ODEs only exist for $\Delta t>0$.
-
-We start the construction of $\Pi_n$ by first considering the free phase and building the map $F_n$.
-At each spike time $t_{k}$, variable $d$ depresses with the reset $d(t_{k})\leftarrow \lambda d(t_{k}^{-})$ (\cref{eq:d-reset}).
-For the duration of the subsequent $ISI$, the recovery of $d$ is described by the solution to \cref{eq:dot-d}:
-\begin{equation}
-  d(t) = 1 - (1-\lambda d_{k})e^{-t/\tau_{d}}~\label{eq:d-sol},
-\end{equation}
-where the variable $d_{k}=d(t^{-}_{k})$ is the level of depression at spike time $t_{k}$.
-By substituting $t=T$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the free phase:
-\begin{equation}
-  d_{k+1} = \lambda\rho d_{k} + (1-\rho),~\label{eq:map-d}
-\end{equation}
-where to keep the notation simple we let $\rho=\exp(-T/\tau_{d})$.
-Since $0<\lambda, \rho<1$, the map~\eqref{eq:map-d} is increasing and contracting, with a fixed point at
-\begin{equation}
- ~\label{eq:dsup}
-  d_{s}=\frac{1-\rho}{1-\lambda\rho},
-\end{equation}
-where $0<d_{s}<1$.
-The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
-Using the release condition in \cref{eq:release} allows us to derive the value of the the minimum coupling strength that will produce the full suppressed solution, denoted as $\gbar_{s}$.
-Solving \cref{eq:dot-s} for $s(t)$ with $t=T$ and setting the initial value $s(0)=d_{s}$ gives
-\begin{equation}
-\gbar_{s} d_{s}e^{-T/\tau_{s}}=g^{\star}.
-\end{equation}
-By further substituting the definition of $d_{s}$ in~\eqref{eq:dsup} and rearranging, we can write $\gbar_{s}$ as a function of the depression strength $\lambda$:
-\begin{equation}
-  \label{eq:gs}
-  \gbar_{s}(\lambda) = g^{\star}e^{T/\tau_{s}}\frac{1-\lambda \rho}{1-\rho}.
-\end{equation}
-Note that the above dependence of $\gbar_{s}$ on $\lambda$ is linear and monotonically decreasing.
-Increasing $\lambda$ reduces the strength of the depression of the free cell.
-This in turn allows the free cell to fully suppress the quiet cell at smaller values of $\gbar$.
-
-Solving~\eqref{eq:map-d} gives us the linear map $\delta_{n}:d^{\star}\mapsto d_{n}$, that for some initial $d^{\star}$ computes the depression at the $n$th spike time, $d_{n}=d(t_{n}^{-})$:
-\begin{equation}
- ~\label{eq:delta-map}
-  \delta_{n}(d^{\star}) = (\lambda \rho)^{n-1} d^{\star} + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}.
-\end{equation}
-Since $\lambda < 1$, function $\delta_{n}$ is a linearly increasing function of $d^{\star}$ with a fixed point at $d_{s}$ for all $n$.
-Having identified $d$ after $n$ spikes, we can now use the release condition $\gbar s = g^{\star}$ (\cref{eq:release}) to find $\delt$.
-At the last spike of the free phase at time $t_{n}=(n-1)T$ the synapse variable $s$ is reset according to \cref{eq:s-reset}:
-\begin{equation}
-  s(t_{n})\leftarrow \dn(\dstar).
-\end{equation}
-After the last spike $s$ decays exponentially according to the solution of \cref{eq:dot-s}, where setting the initial condition $s(0)=\dn(\dstar)$ yields:
-\begin{equation}
-~\label{eq:s-sol}
-  s(\delt)=\dn(\dstar)e^{-\Delta t/\tau_{s}}.
-\end{equation}
-Substituting $s(\delt)$ into $s$ of the release condition (\cref{eq:release}) gives then
-\begin{equation}
- ~\label{eq:release2}
-  \gbar \dn(\dstar) e^{-\delt/\tau_{s}}=g^{\star}.
-\end{equation}
-Our assumption of the release condition guarantees that the quiet cell 2 spikes and becomes free when $\gbar s - g^{\star}$ crosses zero.
-Solving \cref{eq:release2} for $\delt$ allows us to compute the inter-spike-interval as a function of $\dstar$, which defines our map $F_n$:
-\begin{equation}
- ~\label{eq:Fn-map}
-  F_{n}(d^{\star}):=\tau_{s}\ln{\left(\frac{\gbar }{g^{\star}} \delta_{n}(d^{\star})\right)}= \delt.
-\end{equation}
-
-\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\gbar$.
-Larger values of $d^{\star}$ and $\gbar$, respectively, cause stronger inhibition of the quiet cell, and therefore prolong its release time and the associated $\delt$.
-Map $F_{n}$ is defined on $d^{\star}>d_{a}$, where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(\dstar)=0$ in \cref{eq:delta-map} for $\dstar$, which yields
-\begin{equation}
-  d_{a}(n)=-\frac{(1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}}{ (\lambda \rho)^{n-1} }\leq 0~\label{eq:da}.
-\end{equation}
-
-We now turn to the construction of map $Q_{n}$, which describes the recovery of the depression variable during the quiet phase.
-As we have identified earlier, the recovery in the quiet phase of a $n-n$ solution is of duration $2\delt +(n-1)T$.
-Substituting that into the solution for $d(t)$ (\cref{eq:d-sol}) with the initial condition $d(0)=\dn(\dstar)$ yields the map $Q_{n}$:
-\begin{equation}
- ~\label{eq:Qn-map}
-  Q_{n}(\delt):=1- (1- \lambda \dn(\dstar))e^{-(2\Delta t+(n-1)T)/\tau_{d}}.
-\end{equation}
-Given $\delt$, we can find $\dn(\dstar)$ by rearranging the release condition in \cref{eq:release2}:
-\begin{equation}
- ~\label{eq:dn}
-  \dn(\dstar) = \frac{g^{\star}}{\gbar} e^{\delt/\tau_{s}}.
-\end{equation}
-Map $Q_{n}$ is shown in \cref{fig:FQ-map}B for various values $n$.
-Note that $Q_{n}$ is monotonically increasing as larger values $\delt$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
-All curves $Q_{n}$ intersect at some $\delt = \tau_{s}\ln{\left[\gbar/(g^{\star}\lambda)\right]}$ where
-\begin{equation}
-     ~\label{eq:Qn-intersect}
-      Q_{n}\left[\tau_{s}\ln{\left(\frac{\gbar}{g^{\star}\lambda}\right)}\right]=1.
-    \end{equation}
-As we will show in the next section, all fixed points of the full map $\Pi_{n}$ occur for $d^{\star}<1$.
-We will therefore restrict the domain of $Q_{n}$ to $(-\infty, \ln{\left[\gbar/(g^{\star}\lambda)\right]}\tau_{s})$ and the codomain to $(-\infty, 1)$.
-Additionally, while values $\delt>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t=T$, and we will address this concern in the last part of our map analysis.
-
-Having found $F_{n}$ and $Q_{n}$, we can now construct the full map $\Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star})\big)$:
-\begin{equation}
- ~\label{eq:Pn-map}
-  \Pi_{n}(d^{\star})= 1-
-\frac{\rho^{n-1}{g^{\star}}^{\tau}}{{\gbar}^{\tau}}\delta_{n}^{-\tau}(d^{\star})\big(1-\lambda\delta_{n}(d^{\star})\big),
-\end{equation}
-where we substituted $\tau = 2\tau_{s}/\tau_{d}$.
-Since $d$ is the slowest variable of the system and $\tau_{d}\gg \tau_{s}$, we will also assume $\tau<1$.
-\Cref{fig:Pn-map}A depicts $\Pi_{n}$ for various $n$.
-Intersections of $\Pi_{n}$ with the diagonal are fixed points of the map.
-\Cref{fig:Pn-map}B shows $\Pi_{2}$ with $n=2$.
-Varying the synaptic strength $\gbar$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
-For $\gbar<0.03$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
-As $\gbar$ is increased to $\gbar \approx 0.03$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
-When $\gbar > 0.03$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
-
-From \cref{eq:Pn-map} it is evident that $\Pi_{n}$ is monotonically increasing with respect to $\gbar$ and also $\dstar$:
-\begin{align}
-  \label{eq:non-degen1}
-  \dv{\Pi_{n}}{\gbar}&>0,\\[0.5ex]
-  \label{eq:dPidd}
-  \dv{\Pi_{n}}{\dstar}&>0,
-\end{align}
-and in the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
-Just as $F_{n}$, curves $\Pi_{n}$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
-\begin{equation}
-  \lim_{\gbar \to \infty}\Pi_{n} = 1\text{ for all }n,
-\end{equation}
-fixed points of $\Pi_{n}$ lie in $(d_{a}, 1)$.
-
-% \subsection{Existence and stability of fixed points of $\mathit{\Pi_{n}}$}
-\subsection{Existence and stability of fixed points}
-We introduce the fixed point notation $\dstar_{f}$ with $\Pi_{n}(\dstar_{f})=\dstar_{f}$.
-The existence of fixed points $\dstar_{f}$ for $\gbar$ sufficiently large can be shown from the strict monotonicity of $\Pi_{n}$ with respect to $\gbar$ and $\dstar$ (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of $\Pi_{n}$ is monotonically decreasing,
-\begin{equation}
-  \label{eq:non-degen2}
-  \left(\frac{\mathrm{d}}{\mathrm{d}\dstar}\right)^2 \Pi_{n}<0.
-\end{equation}
-In the limit $\dstar \to d_{a}$ the value of $\Pi_n$ decreases without bound for any $\gbar>0$.
-In the limit $\gbar \to 0$, $\Pi_n$ also decreases without bound, but as $\gbar \to \infty$ values of $\Pi_n$ approach $1$.
-It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some $\gbar$ large enough $\Pi_n$ intersects the diagonal.
-Moreover, because $\Pi_n$ and its slope are monotonic with respect to $\dstar$, there exists some critical fixed point $(\dstar_b, \gbar_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
-\begin{align}
-  \Pi_{n}(\dstar_{b}; \gbar_{b}) &=\dstar_{b},\\
-  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b})&=1.
-\end{align}
-Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(\dstar_{b}, \gbar_{b})$ map $\Pi_{n}$ has the topological normal form described by the graph of
-\begin{equation}
-  \label{eq:normal-form}
-  x\mapsto \beta+x-x^{2},
-\end{equation}
-with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.
-
-\subsection{Fold bifurcations}
-Fixed points of $\Pi_n$ satisfy the fixed point equation
-\begin{equation}
-  \label{eq:Phi}
-  \Phi_n(\dstar; \gbar)=0,
-\end{equation}
-where
-\begin{equation}
- ~\label{eq:Phi-def}
-  \Phi_{n}(d^{\star}, \gbar):=\Pi_{n}(d^{\star}, \gbar)-d^{\star}.
-\end{equation}
-As we have already shown, for $\gbar > \gbar_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
-Solving \cref{eq:Phi} explicitly for $\dstar$ it not trivial, but solving for $\gbar$ is straightforward and given by $\gbar = G_n(\dstar)$, where
-\begin{equation}
- ~\label{eq:g}
-  G_{n}(d^{\star}) := g^{\star} \left(\frac{\rho^{n-1}\delta_{n}^{-\tau}(d^{\star})(1-\lambda\delta_{n}(d^{\star}))}{1-d^{\star}}\right)^{1/\tau}.
-\end{equation}
-Plotting $d^{\star}$ against $\gbar$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
-Note the typical quadratic shape of a fold bifurcation of maps.
-It is also evident that the fold bifurcations occur for increasingly smaller $\gbar$ as $n$ is increased.
-Moreover, we can observe that unstable fixed points have negative values of $d^{\star}$ for $n>1$.
-
-\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(\dstar_{b}(n), \gbar_{b}(n)\big)$, which is the global minimum of $G_{n}(\dstar_f)$:
-\begin{align}
-  \dstar_{b}(n) &= \operatorname{argmin} G_{n}(\dstar_{f}),\\
-  \gbar_{b}(n)  &= \min{G_{n}(\dstar_{f})}.
-\end{align}
-Function $G_{n}$ is strictly monotonic on the respective intervals of $\dstar_f$ that correspond to the stable and unstable fixed points, that is
-\begin{align}
-  \dv{G_n}{\dstar_f}& < 0, \text{ for } \dstar_f>\dstar_b(n) \text{ stable},\\[0.5ex]
-  \dv{G_n}{\dstar_f}& > 0, \text{ for } \dstar_f<\dstar_b(n) \text{ unstable},
-\end{align}
-which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $\dstar_f$.
-Because we are primarily interested in the stable fixed points, we define the stable fixed point function $\dstar_f=\phi_n(\gbar)$ as
-\begin{equation}
-  \label{eq:phi}
-  \phi_{n}(\gbar):= G_{n}^{-1}(\dstar_{f}) \text{ for } \dstar_{f}>\dstar_{b}(n).
-\end{equation}
-Function $\phi_n(\gbar)$ is also monotonic, and is therefore straightforward to compute numerically via root-finding.
-Here we use the Python package Pynverse~\citep{pynverse} for that purpose.
-
-Having found the stable fixed points $\dstar_f$ as a function of the coupling strength $\gbar$, we can now compute the associated cycle period.
-Recall that the period is given by \cref{eq:P}, which we can be written as a function of $\gbar$:
-\begin{equation}
-  \label{eq:period}
-  P_n(\gbar) = 2(n-1)T + 2F_n\big(\underbrace{\phi_n(\gbar)}_{\dstar_f}, \gbar\big),
-\end{equation}
-where map $F_n$ (\cref{eq:Fn-map}) calculates the inter-burst-interval $\delt$ given a stable fixed point $\dstar_f=\phi_n(\gbar)$.
-We plot the predicted period $P_n(\gbar)$ versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
-For $n>1$ our map $\Pi_n$ accurately predicts the period.
-When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for $n=1$ (see \cref{fig:release-delay}), since here $\gbar$ is not sufficiently strong to guarantee the validity of our release condition (\cref{eq:release}).
-
-It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\gbar$.
-This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\gbar), \gbar)=0$ in \cref{eq:Phi}.
-For $\dstar_f=\phi_n(\gbar)>d_b(n)$ we get:
-\begin{equation}
-  \label{eq:dstardg}
-  \dv{\phi_n}{\gbar} = -\frac{\pdv*{\Phi_n}{\gbar}}{\pdv*{\Phi_n}{\dstar}} =
-  \frac{\pdv*{\Pi_n}{\gbar}}{1-\pdv*{\Pi_n}{\dstar}}>0.
-\end{equation}
-The inequality follows from $\pdv*{\Pi_n}{\gbar}>0$ and the fact that $\pdv*{\Pi_n}{\dstar}<1$ for $\dstar>d_b(n)$.
-\Cref{eq:dstardg} allows us to explain why the period $P_n$ increases with $\gbar$, as seen in \cref{fig:folds}B.
-Differentiating $P_n$ gives:
-\begin{equation}
-  \label{eq:dPdg}
-  \dv{P_{n}}{\gbar} = 2\grad F_n(\dstar_f, \gbar) \cdot
-                      \begin{bmatrix}\pdv*{\phi_n}{\gbar}\\[0.5ex] 1\end{bmatrix}>0,
-\end{equation}
-where the partial derivatives of $F_n(\dstar_f, \gbar)$ are:
-\begin{align}
-  \pdv{F_n}{\dstar_f} &= \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar_f)}>0,\\[0.5ex]
-  \pdv{F_n}{\gbar}  &= \frac{\taus}{\gbar}>0.
-\end{align}
-\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation:
-Increasing the coupling strength between the neurons leads to overall stronger inhibition of the quiet cell, which delays its release and leads to a longer cycle period.
-The latter allows more time for the synapse to depress in the free phase and recover in the quiet phase, resulting in overall larger values of $\dstar_f$, that is weaker depression at the burst onset.
-
-While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the free phase contains exactly $n$ spikes.
-As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n-n$ bursts exists only on certain parameter intervals of $\gbar$.
-In the last sub-section we will analyse the mechanisms that guide how the stable $n-n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\gbar$ where such solutions exist.
-
-% TODO: Need to find a better sub-section title that doesn't include 'period increment'
-\subsection{Period increment bifurcations with co-existent attractors}
-Let $\gbar_+(n)$ and $\gbar_-(n)$ denote the left and right parameter borders on $\gbar$ where stable $n-n$ solutions exist.
-That is, as $\gbar$ is increased stable $n-n$ solutions are created at $\gbar_+(n)$ and destroyed at $\gbar_-(n)$.
-When $\gbar$ is reduced beyond $\gbar_+(n)$, $n-n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\gbar$ is increased beyond $\gbar_-(n)$, $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
-Let us briefly recap our observations regarding $\gbar_+(n)$ and $\gbar_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
-For $n>1$ there are the following relations:
-\begin{align}
-  \gbar_+(n) &< \gbar_-(n)\label{eq:easy1},\\
-  \gbar_+(n) &< \gbar_+(n+1)\text{ and } \gbar_-(n)<\gbar_-(n+1)\label{eq:easy2},\\
-  \gbar_+(n+1) &< \gbar_-(n)\label{eq:coexistence},\\
-  \gbar_-(n+1) - \gbar_+(n+1) &< \gbar_-(n) - \gbar_-(n)\label{eq:robustness}.
-\end{align}
-\Cref{eq:easy1,eq:easy2} are self-explanatory.
-\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n-n$ and $(n+1)-(n+1)$ solutions.
-\Cref{eq:robustness} implies that the parameter interval on $\gbar$ of $n-n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
-All of the above relations are reminiscent of the period increment bifurcations with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
-see][]{gardini2012,tramontana2012,avrutin2011,gardini2012}.
-While our maps $\Pi_n$ are fully continuous, the above observation suggests that
-a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
-We will explore what such a map might look like in the discussion.
-
-Let us now find algebraic equations that will allow us to calculate the critical parameters $\gbar_+(n)$ and $\gbar_-(n)$ associated with the period increment bifurcations.
-% BUG: Maybe don't call it period-increment here?
-Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\gbar$:
-\begin{equation}
-  \dv{P_{n}}{\gbar}=2\dv{F_n(\phi_n(\gbar), \gbar)}{\gbar}>0,
-\end{equation}
-that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the quiet cell, and $\delt$ becomes larger.
-Once $\delt=T$, the free cell can produce another spike and the solution bifurcates into a $(n+1)-(n+1)$ solution.
-Note, however, that at $\gbar_+(n)$ the bifurcation into a $(n-1)-(n-1)$ does not occur when $\delt=0$.
-Here the mechanism is different: A sufficient reduction of $\gbar$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the quiet cell to be released one spike earlier.
-
-Using the above reasoning we can now formulate the conditions for both bifurcations at $\gbar_+(n)$ and $\gbar_-(n)$.
-As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $\dstar_f=\phi_n(\gbar)$ (\cref{eq:phi}).
-At the right bifurcation border $\gbar_-(n)$ we have $\delt=T$, and after substituting our $F_{n}$-map (\cref{eq:Fn-map}) this translates into
-\begin{equation}
-  F_n(\phi_n(\gbar), \gbar) = T,
-\end{equation}
-which lets us define a function
-\begin{equation}
-  \label{eq:R}
-  R_{n}(\gbar):=F_n(\phi_n(\gbar), \gbar)-T,
-\end{equation}
-whose root is the desired right bifurcation border $\gbar_-(n)$.
-In case of the left bifurcation border at $\gbar_+(n)$ the release condition is satisfied just before the free cell has produced its $n$th spike, and after the depression variable has been reset $n-1$ times, which gives the condition
-\begin{equation}
-  \gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} = \gstar,
-\end{equation}
-and can be rewritten as a function
-\begin{equation}
-  \label{eq:L}
-  L_{n}(\gbar):=\gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} -\gstar,
-\end{equation}
-whose root is $\gbar_+(n)$.
-Both $R_{n}$ and $L_{n}$ are increasing with respect to $\gbar$, which makes finding their roots numerically straightforward.
-
-\Cref{fig:final-bif} shows the period $P_n(\gbar)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\gbar \in [\gbar_+(n),\gbar_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
-Note that the width of $n-n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
-That is, bursts with more spikes occur on increasingly smaller intervals of $\gbar$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
-We also note the occurrence of bi-stability between pairs of $n-n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in \cref{eq:coexistence}.
-
-As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate for $n>1$.
-Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be $\gbar \approx 0.592\si{mS/cm^2}$ in \cref{fig:release-delay}.
-The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\gbar_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
-However, even for branches of large $n-n$ solutions there is a mismatch between the bifurcation borders.
-Presumably our assumptions on the time scales of $w$ and $s$ dynamics do not hold here, and can only be captured by more complex approximations.
-Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.
-
-\section{Discussion}
-% PROBLEM SUMMARY
-Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming~\citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
-In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
-Mathematical modelling can shed light on the underlying mechanisms that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.
-
-% MAIN RESULTS
-To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression.
-When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n-n$ burst patterns.
-Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
-This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n-n$ solutions respectively.
-Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons.
-Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n-n$ burst solutions of the full two-cell system of ODEs.
-The results from our one-dimensional map match excellently with numerical simulation of the full network.
-Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.
-
-% FURTHER METHOD IDEAS
-We have studied $n-n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
-However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes.
-It is conceivable that our map construction can be extended to also capture such $m-n$ solutions.
-Remember, in the case of symmetrical coupling with $n-n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
-To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other.
-To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$.
-While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}.
-Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons.
-As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses.
-In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.
-
-In tadpoles, struggling is believed to be initiated by an increase in the firing frequency of reciprocally inhibitory commisural interneurons, which has been hypothesised to lead to stronger synaptic depression of inhibition and result in the iconic anti-phase bursting \citep{li2007}.
-It would therefore be interesting to study how varying the cell intrinsic firing period $T$ could affect the network rhythm.
-While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying $T$.
-Recall that $T$ is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters.
-This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult.
-A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting in this scenario.
-
-% LIMITATION: SPIKE MAP
-Our simulations of the network showed that $n-n$ solutions lose robustness as their period is increased.
-That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
-We were able to replicate this finding by numerically finding the respective left and right borders of stable $n-n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
-We have also noted the resemblance of our bifurcation diagram to one where such $n-n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
-It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}.
-Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
-The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
-In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations.
-It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
-In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.
-
-% FLOW SYSTEM BIFURCATION
-In addition to stable $n-n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n-n$ solutions.
-While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.
-However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
-SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
-% Should be possible to use averaging to reduce the system.
-
-% BIOLOGICAL IMPORTANCE OF DEPRESSION
-We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.
-This result is in line with the idea that one role of synaptic depression in the nervous system may be to allow a finite size neuronal network to participate in different tasks by producing a large number of rhythms~\citep{bose2011, jalil2004, li2007}.
-To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength, which can occur through the process of learning.
-Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.
-
-\section*{Conflict of Interest Statement}
-The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
-
-\section*{Author Contributions}
-MO and CH contributed to conception and design of the study.
-MO performed numerical computation and analysis.
-All authors contributed to manuscript writing and revision.
-
-\section*{Funding}
-This work was supported by the Wellcome Trust Doctoral Training Programme in Neural Dynamics, Grant no. 099699/Z/12/Z.
-
-\section*{Acknowledgements}
-The first author thanks the Wellcome Trust for financial support of his Ph.D. study.
-We thank Alan Champneys for sharing his insights on non-continuous maps during the course of this research.
-We are also grateful to Alan Roberts and Stephen R. Soffe for their comments on earlier versions of the manuscript.
-
-\section*{Data Availability Statement}
-The datasets generated for this study are available on request to the corresponding author.
-
-% \bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities
-\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
-
-\bibliography{bibliography.bib}
-
-\section*{Figure captions}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/nullclines-uncoupled.pdf}
-  \caption{Periodic solution of relaxation-oscillator model neuron.
-$\bm{\mathrm{(A)}}$ Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue, $v_\infty$) and $w$-nullcline (orange, $w_\infty$).
-Unstable fixed point $p_{f}$ is indicated by an orange dot.
-$\bm{\mathrm{(B)}}$ Corresponding voltage trace $v(t)$ of an action potential.~\label{fig:nullclines}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/depression-traces.pdf}
-  \caption{Solution profiles of a $4-4$ burst.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange).
-$\bm{\mathrm{(B)}}$ Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell 1.~\label{fig:depression-traces}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/burst-sols.pdf}
-  \caption{Voltage traces of both cells of numerically stable solutions for increasing values of the coupling strength $\gbar$ (increasing top to bottom).~\label{fig:burst-sols}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/bif-diagram.pdf}
-  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for increasing coupling strength $\gbar$.
-$\bm{\mathrm{(A)}}$ Period of stable solutions.
-Dashed lines show the interval between the $5-5$ and the suppressed solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals of $\gbar$.
-$\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in $\mathrm{(A)}$.
-Long $ISI$s are associated with the quiet phase of a burst, short $ISI$s with the free phase.
-During the free phase, $ISI$s are of approximately constant duration $T$.\label{fig:bif-diagram}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/nullclines-coupled.pdf}
-  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar s$.
-For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange point).
-Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until $p_{f}$ changes stability (half orange,  half blue point) at some critical total conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
-  \caption{Numerically computed values of the release delay for varying $\gbar$.
-Each of the three branches (A, B, C) also shows the timecourse of the total synaptic conductance $\gbar s$ of a sample stable solution of both cells (blue and orange), as well as the release conductance $g^{\star}$ (dashed green line).
-$\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution.
-Here the quiet cell only spikes after a significant release delay.
-$\bm{\mathrm{(B)}}$ Branch with a long release delay associated with a subset of $2-2$ solutions.
-Here the release condition is briefly satisfied after the first spike of cell 1.
-This does not cause firing of cell 2, which only occurs after the second spike of cell 1.
-$\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is approximately zero and the release condition is sufficient for firing of cell 2.
-   ~\label{fig:release-delay}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/free-quiet.pdf}
-  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
-The grey patches depict inter-burst-intervals $\delt$.
-$\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$.
-$\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/delta-t.pdf}
-  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
-Each continuous branch is associated with a stable $n-n$ burst solution.
-Increasing $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx T$.~\label{fig:delta-t}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/FQ-map.pdf}
-  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$.
-Curves $F_n$ intersect at $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/Pn-map.pdf}
-  \caption{Map $\Pi_{n}:d^{\star}$.
-$\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$ at $\gbar=0.6$ $\si{mS/cm^{2}}$.
-$\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$.
-The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/folds.pdf}
-  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves) and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
-$\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the corresponding solution period from numerical integration of the system of ODEs (orange).~\label{fig:folds}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
-  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
-\end{figure}
+This paper is organised as follows.  First, we introduce the network of two neurons, and
+describe the properties of single cell and synapse dynamics.  We use numerical simulations
+of the network to provide an intuition for the range of possible burst dynamics the system
+can produce.  Next, we state and justify the simplifying assumptions that are necessary
+for the map construction.  Finally, we analytically derive the first return map of the
+depression variable as well as the conditions that are required for stable solutions to
+bifurcate between $n-n$ and $(n+1)-(n+1)$ solutions.  We end this work with a discussion.
 

### 2022-02-04 tex/sections/methods.tex
Split latex document into subfiles

--- 2022-01-26 tex/draft.tex
@@
-\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and
-\usepackage{graphicx}
-\usepackage{amssymb}
-\usepackage{siunitx}
-\usepackage{amsmath}
-\usepackage{soul}
-\usepackage{physics}
-\usepackage{bm}
-
-\usepackage{url,hyperref,microtype,subcaption}
-\usepackage[onehalfspacing]{setspace}
-\usepackage{cleveref}
-% \usepackage[font={bold,it}]{caption}
-
-% Define better ref abbreviations
-\usepackage[displaymath]{lineno}
-
-\renewcommand{\d}{\mathrm{d}}
-\renewcommand{\k}{\mathrm{K}}
-\newcommand{\ca}{\mathrm{Ca}}
-\newcommand{\na}{\mathrm{Na}}
-\newcommand{\leak}{\mathrm{L}}
-\newcommand{\dstar}{d^\star}
-\newcommand{\gstar}{g^\star}
-\newcommand{\gbar}{\bar g}
-\newcommand{\delt}{\Delta t}
-\newcommand{\taus}{\tau_s}
-\newcommand{\dn}{\delta_n}
-\newcommand{\taud}{\tau_d}
-
-\linenumbers
-
-\def\keyFont{\fontsize{8}{11}\helveticabold }
-\def\firstAuthorLast{Olenik {et~al.}} %use et al only if is more than 1 author
-\def\Authors{Mark Olenik\,$^{1,*}$, and Conor Houghton\,$^{2}$}
-% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
-% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
-\def\Address{$^{1}$School of Biological Sciences, Faculty of Life Sciences, University of Bristol, Bristol, United Kingdom \\
-$^{2}$School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, Faculty of Engineering, University of Bristol, Bristol, United Kingdom}
-% The Corresponding Author should be marked with an asterisk
-% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
-\def\corrAuthor{Mark Olenik}
-
-\def\corrEmail{m.olenik@bristol.ac.uk}
+\documentclass[../manuscript.tex]{subfiles}
+\graphicspath{{../figures/}}
 
 \begin{document}
-
-\onecolumn
-\firstpage{1}
-
-\title[Scalar Poincaré map for bursting]{A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression.}
-
-\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
-\address{} %This field will be automatically populated
-\correspondance{} %This field will be automatically populated
-
-\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
-%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
-
-\maketitle
-
-\begin{abstract}
-\section{}
-Short-term synaptic plasticity is found in many areas of the central
-nervous system.  In the inhibitory half-centre central pattern
-generators involved in locomotion, synaptic depression is believed to
-act as a burst termination mechanism, allowing networks to generate
-anti-phase bursting patterns of varying periods.  To better understand
-burst generation in these central patter generators, we study a
-minimal network of two neurons coupled through depressing synapses.
-Depending on the strength of the synaptic conductance between the two
-neurons, this network can produce symmetric $n-n$ anti-phase bursts,
-where neurons fire $n$ spikes in alternation, with the period of such
-solutions increasing with the strength of the synaptic conductance.
-Relying on the timescale disparity in the model, we reduce the
-eight-dimensional network equations to a fully-explicit scalar
-Poincaré burst map.  This map tracks the state of synaptic depression
-from one burst to the next and captures the complex bursting dynamics
-of the network.  Fixed points of this map are associated with stable
-burst solutions of the full network model, and are created through
-fold bifurcations of maps.  We derive conditions that describe
-period-increment bifurcations between stable $n-n$ and $(n+1)-(n+1)$
-bursts, producing a full bifurcation diagram of the burst cycle
-period.  Predictions of the Poincaré map fit excellently with
-numerical simulations of the full network model and allow the study of
-parameter sensitivity for rhythm generation.
-
-\tiny
- \keyFont{ \section{Keywords:} Synaptic depression, Poincaré map, Dynamical system, Neuronal bursting, Central pattern generator}
-
-\end{abstract}
-
-\section{Introduction}
-% DEPRESSION
-Short-term synaptic plasticity may have a role in burst activity in
-central pattern generators (CPGs).  Short-term synaptic depression is
-commonly found in neuronal networks involved in the generation of
-rhythmic movements, such as in the pyloric CPG of the spiny
-lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of
-the chick embryo~\citep{donovan1998}.  Synaptic depression modulates
-the strength of synapses in response to changes to the presynaptic
-firing frequency.  At a high neuronal firing frequency, depression
-weakens the strength of synapses and therefore reduces the magnitude
-of the postsynaptic response.  At low firing frequency, it allows
-sufficient time for the synapse to recover from depression between
-spikes, leading to a stronger postsynaptic response.  In reciprocal
-networks, synaptic depression has been shown to act as a ``switch'',
-giving rise to a wide range of network dynamics such as synchronous
-and multi-stable rhythms, as well as fine tuning the frequency of
-network oscillations~\citep{nadim2000, nadim1999, bose2011}.
-
-% Brown
-~\citet{brown1911} pioneered the idea that synaptic depression acts as
-a burst termination mechanism in reciprocally inhibitory CPGs involved
-in rhythm generation of locomotion. When one side is firing during a
-burst the other, antagonistic side, is prevented from firing by
-synaptic inhibition. However, the weakening of inhibition as a result
-of synaptic depression eventually releases the antagonistic side so
-that it starts firing, terminating the burst on the side that had
-originally been firing.  This rhythmogenesis hypothesis has been
-considered one of a handful of standard mechanisms for generating
-locomotion rhythms in
-vertebrates~\citep{reiss1962,perkel1974,friesen1994}. It has been
-proposed as an explaination of the antiphase burst rhythm in
-struggling in \textit{Xenopus} tadpoles~\citep{li2007}.
-
-~\citet{bose2011} investigated burst generation in a generic
-half-centre CPG that consists of two identical, tonically active
-Morris-Lecar~\citep{morris1981} neurons coupled through inhibitory
-depressing synapses.  Numerical simulations showed that when the
-reciprocal synaptic conductance between the two neurons is varied, the
-network produces symmetric $n-n$ anti-phase bursts, with stronger
-synaptic coupling leading to longer bursts.  They used methods from
-geometric singular perturbation theory to separate the timescales of
-the fast membrane, and the slow synaptic dynamics of the network to
-derive one-dimensional conditions necessary for the existence of
-stable $n-n$ solutions (for $n\leq 2$). According to these conditions
-the type of firing pattern largely depends on the slow depression
-dynamics of the synapses between the two neurons, and can therefore be
-predicted by knowing the strengths of the synaptic conductances of the
-two synapses.
-Thus, the scalar conditions derived in~\citet{bose2011} provide a
-method to numerically identify the type of stable $n-n$ pattern for
-any given value of the coupling strength.  However, they do not
-predict the exact period of such solutions.
-Furthermore, while they provide good arguments for the validity of
-their reduction assumptions and the resulting scalar conditions, they
-do not verify them numerically.
-
-Here we extend the previous analysis by providing a Poincaré map of
-the slow depression dynamics.  This allows us not only to predict the
-types of stable $n-n$ solutions the full network can produce, (for any
-$n$), but also to study how varying the coupling strength affects the
-period of such solutions.  To do this, we build on, and numerically
-test, the assumptions on the fast-slow timescale disparity made
-in~\cite{bose2011}.  We reduce the two-cell model to a scalar
-Poincaré map that tracks the evolution of the depression from the
-beginning of one burst to the beginning of the next burst.  Stable
-fixed points of our map are associated with stable $n-n$ burst
-solutions.  Our map construction is motivated by the burst length map
-of a T-type calcium current, utilised by~\citet{matveev2007}, which
-approximates the anti-phase bursting dynamics of a network of two
-coupled Morris-Lecar neurons.  In contrast to our model, the network
-described in the~\cite{matveev2007} paper does not contain short-term synaptic
-depression, and burst termination is instead accomplished through the
-dynamics of a slow T-type calcium current.
-
-% MAIN RESULTS AND CONCLUSIONS
-The Poincaré map derived here replicates the results from numerical
-simulations of the full two-cell ODE system: Given the strength of
-maximum conductance between the two neurons, fixed points of our map
-predict the type and period of $n-n$ patterns, the switch between
-burst solutions of different periods, as well as the occurrence of
-co-existent solutions.  In addition to proving the existence and
-stability of fixed points, our map shows that fixed points are created
-via a fold bifurcation of maps.  We also derive algebraic conditions
-that predict the period increment bifurcations that allow the switch
-between $n-n$ and $(n+1)-(n+1)$ solutions.  Because our map is fully
-explicit, it lays the framework for studying the effects of other
-model parameter on network dynamics without the need to run expensive
-numerical integrations of the ODEs.
-
-% PAPER STRUCTURE.
-This paper is organised as follows.  First, we introduce the network
-of two neurons, and describe the properties of single cell and synapse
-dynamics.  We use numerical simulations of the network to provide an
-intuition for the range of possible burst dynamics the system can
-produce.  Next, we state and justify the simplifying assumptions that
-are necessary for the map construction.  Finally, we analytically
-derive the first return map of the depression variable as well as the
-conditions that are required for stable solutions to bifurcate between
-$n-n$ and $(n+1)-(n+1)$ solutions.  We end this work with a
-discussion.
-
-\section{Materials and Methods}
-We consider a pair of identical Morris-Lecar neurons~\citep{morris1981}, with parameters adapted from~\cite{bose2011}.
-The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
-The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
-The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
+We consider a pair of identical Morris-Lecar neurons~\citep{morris1981}, with parameters
+adapted from~\cite{bose2011}.  The Morris-Lecar model is a set of two first-order
+differential equations that describe the membrane dynamics of a spiking neuron.  The
+depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation
+by a slow potassium current and a leak current.  The membrane potential $v_{i}$ and
+potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
 \begin{align}
   ~\label{eq:cell-modelA}
-     \dot v_{i}&= f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}),\\
+  \dot v_{i} & = f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}), \\
   ~\label{eq:cell-modelB}
-     \dot w_{i} &=h(v_i,w_i).
+  \dot w_{i} & =h(v_i,w_i).
 \end{align}
-Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.
-Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
+Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal
+synaptic conductance and the synaptic gating, respectively, constituting the total
+inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.  Function $f(v_{i},
+w_{i})$ describes the membrane currents of a single cell:
 \begin{equation}
@@
 \end{equation}
-The currents include a constant current $I$, and three ionic currents:
-an instantaneous calcium current, a potassium current, and a leak current, with respective reversal potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances $g_{\ca}$, $g_{\k}$, and $g_{\leak}$.
-The function $h(v_{i}, w_{i})$ models the kinetics of the potassium gating variable $w_{i}$, and is given by
+The currents include a constant current $I$, and three ionic currents: an instantaneous
+calcium current, a potassium current, and a leak current, with respective reversal
+potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances
+$g_{\ca}$, $g_{\k}$, and $g_{\leak}$.  The function $h(v_{i}, w_{i})$ models the kinetics
+of the potassium gating variable $w_{i}$, and is given by
 \begin{equation}
@@
 \end{equation}
-The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the \textbf{Supplementary Material S1}.
+The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default
+model parameters are described in the \textbf{Supplementary Material S1}.
 
-The dynamics of the synaptic interactions between the neurons are governed by a synaptic gating variable $s_{i}$ and a depression variable $d_{i}$:
+The dynamics of the synaptic interactions between the neurons are governed by a synaptic
+gating variable $s_{i}$ and a depression variable $d_{i}$:
 \begin{linenomath}
   \begin{align}
-    \dot s_{i} &= -s_{i}/\tau_{s}~\label{eq:dot-s},\\
-    \dot d_{i} &= (1-d_{i})/\tau_{d}~\label{eq:dot-d}.
+    \dot d_{i} & =
+    \begin{cases}
+      (1-d_{i})/\tau_a\text{ if }v_i<v_\theta, \\
+      -d_{i}/\tau_b\text{ if }v_i>v_\theta,
+    \end{cases}\label{eq:dot-d} \\
+    \dot s_{i} & =
+    \begin{cases}
+      -s_i/\tau_\kappa\text{ if }v_i<v_\theta, \\
+      (d_i-s_i)/\tau_\gamma\text{ if }v_i>v_\theta.
+    \end{cases}\label{eq:dot-s}
   \end{align}
@@
 Variable $d_{i}$ describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
-Our model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
-In between spikes $s_{i}$ decays with time constant $\tau_{s}$, while $d_{i}$ recovers with time constant $\tau_{d}$.
-Because synaptic depression occurs on a much slower timescale than synaptic inhibition, we assume $\tau_{d}\gg\tau_{s}$.
-At spike time when the voltage $v_{i}$ crosses a synaptic threshold $v_{\theta}$, the synaptic variable $s_{i}$ is reset to the current value of $d_{i}$, and $d_{i}$ is scaled down by the depression strength parameter $\lambda$, where $0<\lambda<1$.
-This results in the following discontinuous reset rule on spike time:
-\begin{linenomath}
-  \begin{align}
-    s_{i} &\leftarrow d_{i}~\label{eq:s-reset},\\
-    d_{i} &\leftarrow \lambda d_{i}~\label{eq:d-reset}.
-  \end{align}
-\end{linenomath}
+The model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
+When the voltage is below firing threshold, depression variable $d_i$ recovers with time constant $\tau_a$, while synaptic variable $s_i$ decays with time constant $\tau_\kappa$.
+% TODO Maybe mention that this topic will be discussed in the appendix or later.
+Because synaptic depression occurs on a much slower timescale than synaptic inhibition, we assume $\tau_d\gg\tau_\kappa$.
+When the voltage is above firing threshold, variable $d_i$ decays to zero with $\tau_b$, while $s_i$ quickly approaches the respective value of $d_i$.
+Since $\tau_\gamma$ is the shortest time constant of the system with $\tau_\gamma \ll 1$, we can assume that whenever $v>v_\theta$ we can we have $s_i=d_i$.
 The equations for the depression model were adapted from the~\citet{bose2001} model.
 These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by~\citet{tsodyks1997}.
-The original equations in~\cite{bose2001} include an exponential decay of $d_{i}$ throughout the active phase of the action potential, that is $\dot d_{i}=-d_{i}/\tau_{\beta}$ for $v_{i}>v_{\theta}$.
-To simplify the mathematical analysis we have reduced these dynamics to a single-reset event at spike time according to \cref{eq:d-reset}.
-This simplification is natural given an approximately constant duration of the active phase of an action potential, and it will become evident from our results that this simplification does not qualitatively change the dynamics of the network compared to the original equations, where depression dynamics are described by an exponential decay.
 
 When the cells are uncoupled ($\gbar=0$), the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
-The two curves intersect along the middle branch of $v_{\infty}$, creating an unstable fixed point $p_{f}=(v_{f},w_{f})$ with a surrounding stable limit cycle of period $T$ (\cref{fig:nullclines}A).
+The two curves intersect along the middle branch of $v_{\infty}$, creating an unstable fixed point $p_{f}=(v_{f},w_{f})$ with a surrounding stable limit cycle of period $T=T_{act}+T_{inact}$ (\cref{fig:nullclines}A).
+Here $T_{act}$ is the amount of time the cell spends in the active state when $v>v_\theta$, while $T_{inact}$ is the time it spends in the silent state when $v<v_\theta$.
 Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
@@
 
-\section{Results}
-\subsection{Anti-phase burst solutions}
-Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism~\citep{brown1911} and is known to produce $n-n$ anti-phase burst solutions of varying period.
-Such $n-n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
-\Cref{fig:depression-traces}A shows the timecourse of a typical $4-4$ burst.
-While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
-Therefore, at any given moment one cell is spiking while the other is inhibited.
-Consistent with~\citet{bose2011} we will refer to the currently firing cell as ``free'' and we will call the inhibited cell ``quiet''.
-Additionally, we will distinguish between two phases of a $n-n$ solution:
-We will refer to the burst duration of a cell as the ``free phase'', which is the time between the first spike and the last spike in a burst.
-And we will call the remaining duration of a cycle, when a cell is not spiking, the ``quiet phase''.
-
-% TODO: Add mention of gstar. Once critical conductance is crossed, cell is released.
-With each action potential of the free cell, short-term depression leads to a step-wise decrease of $d$, and consequently of $s$ (\cref{fig:depression-traces}B).
-If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\gbar s$ will eventually become sufficiently small to allow for the quiet cell to be released and start firing, thus inhibiting the previously free cell.
-While a cell is quiet its depression variable can recover.
-Once the quiet cell becomes free again its synaptic inhibition will be sufficient to terminate the burst of the previously free cell and commence a new cycle.
-As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\gbar$ determines the type of $n-n$ solution.
-Increasing $\gbar$ produces higher $n-n$ burst solutions with more spikes per burst and a longer cycle period.
-\Cref{fig:burst-sols} shows numerically stable $n-n$ solutions for varying values of $\gbar$.
-For small values of $\gbar$ the network produces anti-phase spiking $1-1$ solutions.
-As $\gbar$ is increased the network generates solutions of increasing $n$, that is $2-2$, $3-3$, and $4-4$.
-When $\gbar$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
-Depending on the initial conditions either of the two cells can become the suppressed cell, which is why the suppressed solution is numerically bistable.
-
-Branches of numerically stable $n-n$ solutions and their associated limit cycle period for varying values of $\gbar$ are depicted in \cref{fig:bif-diagram}A (see  \textbf{Supplementary Material S2} for algorithm description).
-Not only do higher $n-n$ solutions branches require stronger coupling $\gbar$, but also within $n-n$ branches the period increases with $\gbar$.
-In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2-2$ and $3-3$ solution branches.
-Branches of higher $n-n$ burst solutions occur on increasingly smaller intervals of $\gbar$, for instance is the $\gbar$ interval of the $5-5$ branch shorter than that of the $4-4$ branch and so on.
-The interval between the $5-5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n-n$ solutions, such as $11-11$ bursts, but also other non-symmetric $n-m$ solutions as well irregular, non-periodic solutions.
-However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n-n$ solutions.
-
-\subsection{Mathematical analysis of two-cell network}
-~\label{sec:assumptions}
-% Summary of assumptions
-The goal of the following mathematical analysis is to reduce the complexity of the eight-dimensional system to some easily tractable quantity.
-As we will see later this quantity is the value of the depression variable $d$ of either of the two cells.
-We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the free phase, and then during the quiet phase.
-This construction will require two assumptions about the membrane and synaptic dynamics.
-The first assumption states that during a burst the free cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
-The second assumption states that once the inhibitory conductance acting on the quiet cell drops below a critical threshold, the cell is immediately released and fires.
-The second assumption is necessary to predict the release time of the quiet cell, which allows us to model the recovery of $d$ during the quiet phase.
-In other words, the second assumption requires that the release of the quiet cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the quiet cell.
-Both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
-Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n-n$ solutions.
-However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.
-
-% Assumption 1: Free phase
-Our first assumption about the model states that the free cell fires at its uncoupled period $T$, that is, during the free phase of a burst we have $ISI=T$.
-Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
-We can further numerically confirm this observation by capturing the $ISI$s of the stable solutions from the bifurcation diagram in \cref{fig:bif-diagram}A.
-In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the quiet phase of the burst.
-$IBI$s lie on multiple branches, each branch associated with a stable $n-n$ solution, and are monotonically increasing with $\gbar$.
-In contrast, $ISI$s are calculated from the spikes within the free phase and do not vary significantly with $\gbar$, but are approximately $ISI\approx T$, affirming our first assumption.
-Assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the free phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
-Assuming $ISI=T$ seems reasonable given that inhibition acting on the quiet cell decays exponentially to zero on a much shorter timescale than the duration of the $ISI$, and therefore, once the quiet cell is released its trajectory quickly approaches the spiking limit cycle.
-
-% Assumption 2: Release
-Our second assumption states that the quiet cell is released and spikes as soon as inhibition from the free cell drops below a constant threshold.
-We will now define such a ``release condition'' by exploiting the discrepancy in timescales between the fast membrane dynamics, and the slower synaptic dynamics.
-Let us first consider the dynamics of a single Morris-Lecar neuron.
-We fix the synaptic variable that acts on the cell by setting $s=1$, which also makes the applied synaptic conductance $\gbar s$ constant.
-Recall from \cref{fig:nullclines}A that in case of a single uncoupled cell ($\gbar s=0$), the $v$- and $w$-nullclines intersect at some unstable fixed point $p_{f}=(v_{f},w_{f})$, while trajectories revolve around a stable spiking limit cycle.
-Increasing $\gbar s$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point $p_{f}$ down the sigmoid $w_{\infty}$ in the $(v-w)$-plane (\cref{fig:nullclines-coupled}).
-When $\gbar s$ is large enough, the fixed point $p_{f}$ becomes stable, attracting all previously periodic trajectories.
-There exists a unique value $\gbar s=g^{\star}$ when $p_{f}$ changes stability and the stable limit cycle vanishes.
-Thus, when a constant inhibitory conductance is applied, $\gbar s<g^{\star}$ acts as a necessary condition for a cell to spike.
-In contrast, when $\gbar s>g^{\star}$ inhibition is strong enough to prevent a cell from spiking~\citep{bose2011}.
-
-% NOTE
-% In our parameter range the bifurcations occur via subcritical Hopf (bose2011 p.47)
-
-Now let us analyse the nullclines of the quiet cell when the two cells are coupled via synaptic inhibition with depression.
-Let $\gbar s$ here denote the total synaptic conductance which acts on the quiet cell and is produced by the free cell, and let $p_{f}$ be the fixed point associated with the quiet cell.
-At the start of the burst of the free cell we have $\gbar s > g^{\star}$ and $p_{f}$ is stable.
-When the free cell spikes, $\gbar s$ peaks (\cref{eq:s-reset}), and the $v$-nullcline with the ensuing stable $p_f$ move down the $w$-nullcline.
-Then in between spikes $\gbar s$ decays exponentially (\cref{eq:dot-s}) causing the $v$-nullcline and $p_{f}$ to move up the $w$-nullcline while attracting trajectories of the quiet cell.
-Once depression causes the synaptic conductance to become small enough to satisfy $\gbar s<g^{\star}$ and the quiet cell is released, fixed point $p_{f}$ becomes unstable allowing the quiet cell to fire.
-If the trajectory of the quiet cell remains sufficiently close to the stable $p_{f}$ at the time when it changes stability, then $\gbar s < g^{\star}$ acts as a release condition that is not only necessary, but also sufficient for firing of the quiet cell.
-In this case the release of the quiet cell occurs precisely when
-\begin{equation}
- ~\label{eq:release}
-  \gbar s=g^{\star}
-\end{equation}
-is satisfied.
-
-Whether the $(v,w)$-trajectory of the quiet cell can remain close enough to $p_{f}$ to make \cref{eq:release} sufficient for firing depends largely on the coupling strength $\gbar$ and the timescale disparity between membrane dynamics and synaptic dynamics~\citep{bose2011}.
-It is straightforward to test our assumption of a release condition by numerically integrating the full system of ODEs and calculating the time interval between the first spike of the quiet cell and the time when $\gbar s$ first crosses $g^{\star}$.
-We will call this time interval the ``release delay''.
-If our assumption holds, we would expect an approximately zero release delay.
-\Cref{fig:release-delay} shows the numerically computed graph of the release delay for varying $\gbar$.
-The graph shows three distinct branches, next to each branch we also plot the timecourse of a corresponding sample solution of the total synaptic conductance $\gbar s$ of both cells.
-For the rightmost branch where $\gbar>0.592$ $\si{mS/cm^{2}}$ the release delay is approximately zero.
-Here the first spike of the quiet cell can be accurately predicted by the release condition in \cref{eq:release}.
-The leftmost and middle branches for $\gbar<0.592$ $\si{mS/cm^{2}}$  show a release delay greater than zero, the quiet cell does not immediately fire when the release condition is first satisfied, and \cref{eq:release} does not accurately predict the release of the quiet cell.
-The leftmost and middle branches contain $1-1$ and $2-2$ solutions respectively.
-In both cases the coupling $\gbar$ is not sufficiently strong to allow trajectories of the quiet cell to be close enough to $p_{f}$ to guarantee spiking once $\gbar$ crosses $g^{\star}$.
-Note that in the middle branch $\gbar s $ crosses $g^{\star}$ twice, and only after the second crossing does the quiet cell fire.
-The following map construction relies on the assumption that the release condition in \cref{eq:release} can accurately predict the release time of the quiet cell.
-Given our model parameters this is only possible for sufficiently large $\gbar>0.592 $ $\si{mS/cm^{2}}$.
-For completeness, however, we will also consider values $\gbar < 0.592$ $\si{mS/cm^{2}}$ in the following analysis, bearing in mind that in this parameter range our map will not be accurate.
-
-In summary: For $\gbar>0.592$ $\si{mS/cm^{2}}$ the release condition is sufficient to predict when the quiet cell is released.
-Due to the symmetry of $n-n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
-The release time therefore uniquely determines the type of $n-n$ solution.
-Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the quiet cell.
-Instead, the solution of the synaptic variable $s$ of the free cell is sufficient to predict when $\gbar s=g^{*}$ is satisfied.
-Finally, $s$ is solely determined by the evolution of the depression variable $d$ of the free cell.
-Constructing a solution of $d$ during the free phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
-However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
-In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n-n$ solutions.
-
-\subsection{Construction of the scalar Poincaré map}
-In this section we construct the scalar Poincaré map $\Pi_{n}:d^{\star}\mapsto d^{\star}$.
-Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n-n$ burst.
-The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
-To simplify the map construction we will assume that a free cell fires exactly $n$ times before it becomes quiet.
-Later we will relax this assumption.
-We will construct $\Pi_{n}$ by evolving $d$ first during the free phase and then during the quiet phase of the $n-n$ limit cycle.
-First, let us give explicit definitions of the free and quiet phases.
-A schematic illustration of both phases is given in \cref{fig:free-quiet1}.
-
-Suppose that at $t=0$ cell 1 becomes free with some initial $d(0)$. 
-Cell 1 then fires $n$ spikes at the uncoupled period $T$.
-Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
-After $n$ spikes the total conductance $\gbar s(t)$ acting on the quiet cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}, that is at some time $t=(n-1)T+\delt$ we have $\gbar s(t)=g^{\star}$.
-Cell 2 is then released and prevents cell 1 from further spiking.
-Here $\delt$ is the \emph{inter-burst-interval}, or the time between the last spike of cell 1 and the first spike of cell 2~\citep{bose2011}.
-Once released, cell 2 also fires $n$ spikes until cell 1 becomes free once again at the cycle period.
-Let $P_n$ denote the full cycle period of a $n-n$ solution:
-\begin{equation}
- ~\label{eq:P}
-  P_n = 2(n-1)T + 2\delt.
-\end{equation}
-We can now define the free and quiet phases of cell 1 explicitly. The free phase is the time interval between the first and last spikes of the burst, that is for time $0<t<(n-1)T$.
-During the free phase of cell 1, the quiet cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\gbar s > g^{\star}$.
-The quiet phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T < t < 2(n-1)T + 2\delt$.
-
-Note that only the quiet phase depends on $\delt$, and $\delt$ will play a central role in the construction of $\Pi_{n}$.
-From \cref{eq:P} $\delt$ can be be computed as
-\begin{equation}
- ~\label{eq:delta-t-P}
-  \delt = \frac{1}{2}P_n - (n-1)T.
-\end{equation}
-\noindent
-We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n-n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\delt$ as a function of $\gbar$ (\cref{fig:delta-t}).
-Each continuous branch of $\delt$ is monotonically increasing and corresponds to a $n-n$ burst:
-Stronger coupling $\gbar$ increases the total synaptic conductance $\gbar s$ that acts on the quiet cell, thus delaying its release.
-It is easy to see that for any $n$-branch we have $\delt<T$:
-Once $\delt$ crosses $T$, the free cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1)-(n+1)$ burst.
-
-Distinguishing between the free and quiet phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
-As can be seen from \cref{fig:free-quiet1}C, during the free phase $d$ depresses at spike times and recovers in the $ISI$s.
-In contrast, during the quiet phase $d$ only recovers and does not depress.
-Given the initial $d^{\star}=d(0)$ at the beginning of the cycle and the number of spikes in the free phase $n$, we can now construct the burst map $\Pi_{n}$.
-The map
-\begin{equation}
-  \Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star}\big))
-\end{equation}
-\noindent
-is a composition of two maps.
-Map
-\begin{equation}
-  F_{n}:d^{\star}\mapsto \delt
-\end{equation}
-models the evolution of $d$ in the free phase.
-$F_{n}$ takes an initial value $d^{\star}$ and calculates the inter-burst-interval $\delt$.
-Map
-\begin{equation}
-  Q_{n}:\delt \mapsto d^{\star}
-\end{equation}
-models the recovery of $d$ in the quiet phase.
-Given some $\delt$ map $Q_n$ computes $\dstar$ at the start of the next cycle.
-
-Our aim in the following analysis is to elucidate the properties of $\Pi_{n}$ and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of $\Pi_{n}$ are created.
-To that effect it will be useful to include not only positive, but also negative values of $d^{\star}$ to the domain of $\Pi_{n}$.
-But it is important to add that values $d^{\star}<0$ are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
-Because $\Pi_{n}$ maps first from $d^{\star}$ to $\delt$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n-n$ solutions with partially overlapping bursts.
-As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n-n$ solutions of the full system of ODEs only exist for $\Delta t>0$.
-
-We start the construction of $\Pi_n$ by first considering the free phase and building the map $F_n$.
-At each spike time $t_{k}$, variable $d$ depresses with the reset $d(t_{k})\leftarrow \lambda d(t_{k}^{-})$ (\cref{eq:d-reset}).
-For the duration of the subsequent $ISI$, the recovery of $d$ is described by the solution to \cref{eq:dot-d}:
-\begin{equation}
-  d(t) = 1 - (1-\lambda d_{k})e^{-t/\tau_{d}}~\label{eq:d-sol},
-\end{equation}
-where the variable $d_{k}=d(t^{-}_{k})$ is the level of depression at spike time $t_{k}$.
-By substituting $t=T$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the free phase:
-\begin{equation}
-  d_{k+1} = \lambda\rho d_{k} + (1-\rho),~\label{eq:map-d}
-\end{equation}
-where to keep the notation simple we let $\rho=\exp(-T/\tau_{d})$.
-Since $0<\lambda, \rho<1$, the map~\eqref{eq:map-d} is increasing and contracting, with a fixed point at
-\begin{equation}
- ~\label{eq:dsup}
-  d_{s}=\frac{1-\rho}{1-\lambda\rho},
-\end{equation}
-where $0<d_{s}<1$.
-The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
-Using the release condition in \cref{eq:release} allows us to derive the value of the the minimum coupling strength that will produce the full suppressed solution, denoted as $\gbar_{s}$.
-Solving \cref{eq:dot-s} for $s(t)$ with $t=T$ and setting the initial value $s(0)=d_{s}$ gives
-\begin{equation}
-\gbar_{s} d_{s}e^{-T/\tau_{s}}=g^{\star}.
-\end{equation}
-By further substituting the definition of $d_{s}$ in~\eqref{eq:dsup} and rearranging, we can write $\gbar_{s}$ as a function of the depression strength $\lambda$:
-\begin{equation}
-  \label{eq:gs}
-  \gbar_{s}(\lambda) = g^{\star}e^{T/\tau_{s}}\frac{1-\lambda \rho}{1-\rho}.
-\end{equation}
-Note that the above dependence of $\gbar_{s}$ on $\lambda$ is linear and monotonically decreasing.
-Increasing $\lambda$ reduces the strength of the depression of the free cell.
-This in turn allows the free cell to fully suppress the quiet cell at smaller values of $\gbar$.
-
-Solving~\eqref{eq:map-d} gives us the linear map $\delta_{n}:d^{\star}\mapsto d_{n}$, that for some initial $d^{\star}$ computes the depression at the $n$th spike time, $d_{n}=d(t_{n}^{-})$:
-\begin{equation}
- ~\label{eq:delta-map}
-  \delta_{n}(d^{\star}) = (\lambda \rho)^{n-1} d^{\star} + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}.
-\end{equation}
-Since $\lambda < 1$, function $\delta_{n}$ is a linearly increasing function of $d^{\star}$ with a fixed point at $d_{s}$ for all $n$.
-Having identified $d$ after $n$ spikes, we can now use the release condition $\gbar s = g^{\star}$ (\cref{eq:release}) to find $\delt$.
-At the last spike of the free phase at time $t_{n}=(n-1)T$ the synapse variable $s$ is reset according to \cref{eq:s-reset}:
-\begin{equation}
-  s(t_{n})\leftarrow \dn(\dstar).
-\end{equation}
-After the last spike $s$ decays exponentially according to the solution of \cref{eq:dot-s}, where setting the initial condition $s(0)=\dn(\dstar)$ yields:
-\begin{equation}
-~\label{eq:s-sol}
-  s(\delt)=\dn(\dstar)e^{-\Delta t/\tau_{s}}.
-\end{equation}
-Substituting $s(\delt)$ into $s$ of the release condition (\cref{eq:release}) gives then
-\begin{equation}
- ~\label{eq:release2}
-  \gbar \dn(\dstar) e^{-\delt/\tau_{s}}=g^{\star}.
-\end{equation}
-Our assumption of the release condition guarantees that the quiet cell 2 spikes and becomes free when $\gbar s - g^{\star}$ crosses zero.
-Solving \cref{eq:release2} for $\delt$ allows us to compute the inter-spike-interval as a function of $\dstar$, which defines our map $F_n$:
-\begin{equation}
- ~\label{eq:Fn-map}
-  F_{n}(d^{\star}):=\tau_{s}\ln{\left(\frac{\gbar }{g^{\star}} \delta_{n}(d^{\star})\right)}= \delt.
-\end{equation}
-
-\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\gbar$.
-Larger values of $d^{\star}$ and $\gbar$, respectively, cause stronger inhibition of the quiet cell, and therefore prolong its release time and the associated $\delt$.
-Map $F_{n}$ is defined on $d^{\star}>d_{a}$, where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(\dstar)=0$ in \cref{eq:delta-map} for $\dstar$, which yields
-\begin{equation}
-  d_{a}(n)=-\frac{(1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}}{ (\lambda \rho)^{n-1} }\leq 0~\label{eq:da}.
-\end{equation}
-
-We now turn to the construction of map $Q_{n}$, which describes the recovery of the depression variable during the quiet phase.
-As we have identified earlier, the recovery in the quiet phase of a $n-n$ solution is of duration $2\delt +(n-1)T$.
-Substituting that into the solution for $d(t)$ (\cref{eq:d-sol}) with the initial condition $d(0)=\dn(\dstar)$ yields the map $Q_{n}$:
-\begin{equation}
- ~\label{eq:Qn-map}
-  Q_{n}(\delt):=1- (1- \lambda \dn(\dstar))e^{-(2\Delta t+(n-1)T)/\tau_{d}}.
-\end{equation}
-Given $\delt$, we can find $\dn(\dstar)$ by rearranging the release condition in \cref{eq:release2}:
-\begin{equation}
- ~\label{eq:dn}
-  \dn(\dstar) = \frac{g^{\star}}{\gbar} e^{\delt/\tau_{s}}.
-\end{equation}
-Map $Q_{n}$ is shown in \cref{fig:FQ-map}B for various values $n$.
-Note that $Q_{n}$ is monotonically increasing as larger values $\delt$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
-All curves $Q_{n}$ intersect at some $\delt = \tau_{s}\ln{\left[\gbar/(g^{\star}\lambda)\right]}$ where
-\begin{equation}
-     ~\label{eq:Qn-intersect}
-      Q_{n}\left[\tau_{s}\ln{\left(\frac{\gbar}{g^{\star}\lambda}\right)}\right]=1.
-    \end{equation}
-As we will show in the next section, all fixed points of the full map $\Pi_{n}$ occur for $d^{\star}<1$.
-We will therefore restrict the domain of $Q_{n}$ to $(-\infty, \ln{\left[\gbar/(g^{\star}\lambda)\right]}\tau_{s})$ and the codomain to $(-\infty, 1)$.
-Additionally, while values $\delt>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t=T$, and we will address this concern in the last part of our map analysis.
-
-Having found $F_{n}$ and $Q_{n}$, we can now construct the full map $\Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star})\big)$:
-\begin{equation}
- ~\label{eq:Pn-map}
-  \Pi_{n}(d^{\star})= 1-
-\frac{\rho^{n-1}{g^{\star}}^{\tau}}{{\gbar}^{\tau}}\delta_{n}^{-\tau}(d^{\star})\big(1-\lambda\delta_{n}(d^{\star})\big),
-\end{equation}
-where we substituted $\tau = 2\tau_{s}/\tau_{d}$.
-Since $d$ is the slowest variable of the system and $\tau_{d}\gg \tau_{s}$, we will also assume $\tau<1$.
-\Cref{fig:Pn-map}A depicts $\Pi_{n}$ for various $n$.
-Intersections of $\Pi_{n}$ with the diagonal are fixed points of the map.
-\Cref{fig:Pn-map}B shows $\Pi_{2}$ with $n=2$.
-Varying the synaptic strength $\gbar$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
-For $\gbar<0.03$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
-As $\gbar$ is increased to $\gbar \approx 0.03$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
-When $\gbar > 0.03$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
-
-From \cref{eq:Pn-map} it is evident that $\Pi_{n}$ is monotonically increasing with respect to $\gbar$ and also $\dstar$:
-\begin{align}
-  \label{eq:non-degen1}
-  \dv{\Pi_{n}}{\gbar}&>0,\\[0.5ex]
-  \label{eq:dPidd}
-  \dv{\Pi_{n}}{\dstar}&>0,
-\end{align}
-and in the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
-Just as $F_{n}$, curves $\Pi_{n}$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
-\begin{equation}
-  \lim_{\gbar \to \infty}\Pi_{n} = 1\text{ for all }n,
-\end{equation}
-fixed points of $\Pi_{n}$ lie in $(d_{a}, 1)$.
-
-% \subsection{Existence and stability of fixed points of $\mathit{\Pi_{n}}$}
-\subsection{Existence and stability of fixed points}
-We introduce the fixed point notation $\dstar_{f}$ with $\Pi_{n}(\dstar_{f})=\dstar_{f}$.
-The existence of fixed points $\dstar_{f}$ for $\gbar$ sufficiently large can be shown from the strict monotonicity of $\Pi_{n}$ with respect to $\gbar$ and $\dstar$ (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of $\Pi_{n}$ is monotonically decreasing,
-\begin{equation}
-  \label{eq:non-degen2}
-  \left(\frac{\mathrm{d}}{\mathrm{d}\dstar}\right)^2 \Pi_{n}<0.
-\end{equation}
-In the limit $\dstar \to d_{a}$ the value of $\Pi_n$ decreases without bound for any $\gbar>0$.
-In the limit $\gbar \to 0$, $\Pi_n$ also decreases without bound, but as $\gbar \to \infty$ values of $\Pi_n$ approach $1$.
-It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some $\gbar$ large enough $\Pi_n$ intersects the diagonal.
-Moreover, because $\Pi_n$ and its slope are monotonic with respect to $\dstar$, there exists some critical fixed point $(\dstar_b, \gbar_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
-\begin{align}
-  \Pi_{n}(\dstar_{b}; \gbar_{b}) &=\dstar_{b},\\
-  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b})&=1.
-\end{align}
-Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(\dstar_{b}, \gbar_{b})$ map $\Pi_{n}$ has the topological normal form described by the graph of
-\begin{equation}
-  \label{eq:normal-form}
-  x\mapsto \beta+x-x^{2},
-\end{equation}
-with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.
-
-\subsection{Fold bifurcations}
-Fixed points of $\Pi_n$ satisfy the fixed point equation
-\begin{equation}
-  \label{eq:Phi}
-  \Phi_n(\dstar; \gbar)=0,
-\end{equation}
-where
-\begin{equation}
- ~\label{eq:Phi-def}
-  \Phi_{n}(d^{\star}, \gbar):=\Pi_{n}(d^{\star}, \gbar)-d^{\star}.
-\end{equation}
-As we have already shown, for $\gbar > \gbar_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
-Solving \cref{eq:Phi} explicitly for $\dstar$ it not trivial, but solving for $\gbar$ is straightforward and given by $\gbar = G_n(\dstar)$, where
-\begin{equation}
- ~\label{eq:g}
-  G_{n}(d^{\star}) := g^{\star} \left(\frac{\rho^{n-1}\delta_{n}^{-\tau}(d^{\star})(1-\lambda\delta_{n}(d^{\star}))}{1-d^{\star}}\right)^{1/\tau}.
-\end{equation}
-Plotting $d^{\star}$ against $\gbar$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
-Note the typical quadratic shape of a fold bifurcation of maps.
-It is also evident that the fold bifurcations occur for increasingly smaller $\gbar$ as $n$ is increased.
-Moreover, we can observe that unstable fixed points have negative values of $d^{\star}$ for $n>1$.
-
-\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(\dstar_{b}(n), \gbar_{b}(n)\big)$, which is the global minimum of $G_{n}(\dstar_f)$:
-\begin{align}
-  \dstar_{b}(n) &= \operatorname{argmin} G_{n}(\dstar_{f}),\\
-  \gbar_{b}(n)  &= \min{G_{n}(\dstar_{f})}.
-\end{align}
-Function $G_{n}$ is strictly monotonic on the respective intervals of $\dstar_f$ that correspond to the stable and unstable fixed points, that is
-\begin{align}
-  \dv{G_n}{\dstar_f}& < 0, \text{ for } \dstar_f>\dstar_b(n) \text{ stable},\\[0.5ex]
-  \dv{G_n}{\dstar_f}& > 0, \text{ for } \dstar_f<\dstar_b(n) \text{ unstable},
-\end{align}
-which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $\dstar_f$.
-Because we are primarily interested in the stable fixed points, we define the stable fixed point function $\dstar_f=\phi_n(\gbar)$ as
-\begin{equation}
-  \label{eq:phi}
-  \phi_{n}(\gbar):= G_{n}^{-1}(\dstar_{f}) \text{ for } \dstar_{f}>\dstar_{b}(n).
-\end{equation}
-Function $\phi_n(\gbar)$ is also monotonic, and is therefore straightforward to compute numerically via root-finding.
-Here we use the Python package Pynverse~\citep{pynverse} for that purpose.
-
-Having found the stable fixed points $\dstar_f$ as a function of the coupling strength $\gbar$, we can now compute the associated cycle period.
-Recall that the period is given by \cref{eq:P}, which we can be written as a function of $\gbar$:
-\begin{equation}
-  \label{eq:period}
-  P_n(\gbar) = 2(n-1)T + 2F_n\big(\underbrace{\phi_n(\gbar)}_{\dstar_f}, \gbar\big),
-\end{equation}
-where map $F_n$ (\cref{eq:Fn-map}) calculates the inter-burst-interval $\delt$ given a stable fixed point $\dstar_f=\phi_n(\gbar)$.
-We plot the predicted period $P_n(\gbar)$ versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
-For $n>1$ our map $\Pi_n$ accurately predicts the period.
-When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for $n=1$ (see \cref{fig:release-delay}), since here $\gbar$ is not sufficiently strong to guarantee the validity of our release condition (\cref{eq:release}).
-
-It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\gbar$.
-This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\gbar), \gbar)=0$ in \cref{eq:Phi}.
-For $\dstar_f=\phi_n(\gbar)>d_b(n)$ we get:
-\begin{equation}
-  \label{eq:dstardg}
-  \dv{\phi_n}{\gbar} = -\frac{\pdv*{\Phi_n}{\gbar}}{\pdv*{\Phi_n}{\dstar}} =
-  \frac{\pdv*{\Pi_n}{\gbar}}{1-\pdv*{\Pi_n}{\dstar}}>0.
-\end{equation}
-The inequality follows from $\pdv*{\Pi_n}{\gbar}>0$ and the fact that $\pdv*{\Pi_n}{\dstar}<1$ for $\dstar>d_b(n)$.
-\Cref{eq:dstardg} allows us to explain why the period $P_n$ increases with $\gbar$, as seen in \cref{fig:folds}B.
-Differentiating $P_n$ gives:
-\begin{equation}
-  \label{eq:dPdg}
-  \dv{P_{n}}{\gbar} = 2\grad F_n(\dstar_f, \gbar) \cdot
-                      \begin{bmatrix}\pdv*{\phi_n}{\gbar}\\[0.5ex] 1\end{bmatrix}>0,
-\end{equation}
-where the partial derivatives of $F_n(\dstar_f, \gbar)$ are:
-\begin{align}
-  \pdv{F_n}{\dstar_f} &= \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar_f)}>0,\\[0.5ex]
-  \pdv{F_n}{\gbar}  &= \frac{\taus}{\gbar}>0.
-\end{align}
-\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation:
-Increasing the coupling strength between the neurons leads to overall stronger inhibition of the quiet cell, which delays its release and leads to a longer cycle period.
-The latter allows more time for the synapse to depress in the free phase and recover in the quiet phase, resulting in overall larger values of $\dstar_f$, that is weaker depression at the burst onset.
-
-While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the free phase contains exactly $n$ spikes.
-As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n-n$ bursts exists only on certain parameter intervals of $\gbar$.
-In the last sub-section we will analyse the mechanisms that guide how the stable $n-n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\gbar$ where such solutions exist.
-
-% TODO: Need to find a better sub-section title that doesn't include 'period increment'
-\subsection{Period increment bifurcations with co-existent attractors}
-Let $\gbar_+(n)$ and $\gbar_-(n)$ denote the left and right parameter borders on $\gbar$ where stable $n-n$ solutions exist.
-That is, as $\gbar$ is increased stable $n-n$ solutions are created at $\gbar_+(n)$ and destroyed at $\gbar_-(n)$.
-When $\gbar$ is reduced beyond $\gbar_+(n)$, $n-n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\gbar$ is increased beyond $\gbar_-(n)$, $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
-Let us briefly recap our observations regarding $\gbar_+(n)$ and $\gbar_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
-For $n>1$ there are the following relations:
-\begin{align}
-  \gbar_+(n) &< \gbar_-(n)\label{eq:easy1},\\
-  \gbar_+(n) &< \gbar_+(n+1)\text{ and } \gbar_-(n)<\gbar_-(n+1)\label{eq:easy2},\\
-  \gbar_+(n+1) &< \gbar_-(n)\label{eq:coexistence},\\
-  \gbar_-(n+1) - \gbar_+(n+1) &< \gbar_-(n) - \gbar_-(n)\label{eq:robustness}.
-\end{align}
-\Cref{eq:easy1,eq:easy2} are self-explanatory.
-\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n-n$ and $(n+1)-(n+1)$ solutions.
-\Cref{eq:robustness} implies that the parameter interval on $\gbar$ of $n-n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
-All of the above relations are reminiscent of the period increment bifurcations with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
-see][]{gardini2012,tramontana2012,avrutin2011,gardini2012}.
-While our maps $\Pi_n$ are fully continuous, the above observation suggests that
-a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
-We will explore what such a map might look like in the discussion.
-
-Let us now find algebraic equations that will allow us to calculate the critical parameters $\gbar_+(n)$ and $\gbar_-(n)$ associated with the period increment bifurcations.
-% BUG: Maybe don't call it period-increment here?
-Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\gbar$:
-\begin{equation}
-  \dv{P_{n}}{\gbar}=2\dv{F_n(\phi_n(\gbar), \gbar)}{\gbar}>0,
-\end{equation}
-that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the quiet cell, and $\delt$ becomes larger.
-Once $\delt=T$, the free cell can produce another spike and the solution bifurcates into a $(n+1)-(n+1)$ solution.
-Note, however, that at $\gbar_+(n)$ the bifurcation into a $(n-1)-(n-1)$ does not occur when $\delt=0$.
-Here the mechanism is different: A sufficient reduction of $\gbar$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the quiet cell to be released one spike earlier.
-
-Using the above reasoning we can now formulate the conditions for both bifurcations at $\gbar_+(n)$ and $\gbar_-(n)$.
-As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $\dstar_f=\phi_n(\gbar)$ (\cref{eq:phi}).
-At the right bifurcation border $\gbar_-(n)$ we have $\delt=T$, and after substituting our $F_{n}$-map (\cref{eq:Fn-map}) this translates into
-\begin{equation}
-  F_n(\phi_n(\gbar), \gbar) = T,
-\end{equation}
-which lets us define a function
-\begin{equation}
-  \label{eq:R}
-  R_{n}(\gbar):=F_n(\phi_n(\gbar), \gbar)-T,
-\end{equation}
-whose root is the desired right bifurcation border $\gbar_-(n)$.
-In case of the left bifurcation border at $\gbar_+(n)$ the release condition is satisfied just before the free cell has produced its $n$th spike, and after the depression variable has been reset $n-1$ times, which gives the condition
-\begin{equation}
-  \gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} = \gstar,
-\end{equation}
-and can be rewritten as a function
-\begin{equation}
-  \label{eq:L}
-  L_{n}(\gbar):=\gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} -\gstar,
-\end{equation}
-whose root is $\gbar_+(n)$.
-Both $R_{n}$ and $L_{n}$ are increasing with respect to $\gbar$, which makes finding their roots numerically straightforward.
-
-\Cref{fig:final-bif} shows the period $P_n(\gbar)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\gbar \in [\gbar_+(n),\gbar_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
-Note that the width of $n-n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
-That is, bursts with more spikes occur on increasingly smaller intervals of $\gbar$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
-We also note the occurrence of bi-stability between pairs of $n-n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in \cref{eq:coexistence}.
-
-As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate for $n>1$.
-Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be $\gbar \approx 0.592\si{mS/cm^2}$ in \cref{fig:release-delay}.
-The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\gbar_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
-However, even for branches of large $n-n$ solutions there is a mismatch between the bifurcation borders.
-Presumably our assumptions on the time scales of $w$ and $s$ dynamics do not hold here, and can only be captured by more complex approximations.
-Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.
-
-\section{Discussion}
-% PROBLEM SUMMARY
-Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming~\citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
-In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
-Mathematical modelling can shed light on the underlying mechanisms that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.
-
-% MAIN RESULTS
-To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression.
-When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n-n$ burst patterns.
-Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
-This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n-n$ solutions respectively.
-Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons.
-Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n-n$ burst solutions of the full two-cell system of ODEs.
-The results from our one-dimensional map match excellently with numerical simulation of the full network.
-Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.
-
-% FURTHER METHOD IDEAS
-We have studied $n-n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
-However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes.
-It is conceivable that our map construction can be extended to also capture such $m-n$ solutions.
-Remember, in the case of symmetrical coupling with $n-n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
-To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other.
-To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$.
-While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}.
-Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons.
-As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses.
-In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.
-
-In tadpoles, struggling is believed to be initiated by an increase in the firing frequency of reciprocally inhibitory commisural interneurons, which has been hypothesised to lead to stronger synaptic depression of inhibition and result in the iconic anti-phase bursting \citep{li2007}.
-It would therefore be interesting to study how varying the cell intrinsic firing period $T$ could affect the network rhythm.
-While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying $T$.
-Recall that $T$ is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters.
-This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult.
-A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting in this scenario.
-
-% LIMITATION: SPIKE MAP
-Our simulations of the network showed that $n-n$ solutions lose robustness as their period is increased.
-That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
-We were able to replicate this finding by numerically finding the respective left and right borders of stable $n-n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
-We have also noted the resemblance of our bifurcation diagram to one where such $n-n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
-It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}.
-Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
-The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
-In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations.
-It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
-In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.
-
-% FLOW SYSTEM BIFURCATION
-In addition to stable $n-n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n-n$ solutions.
-While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.
-However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
-SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
-% Should be possible to use averaging to reduce the system.
-
-% BIOLOGICAL IMPORTANCE OF DEPRESSION
-We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.
-This result is in line with the idea that one role of synaptic depression in the nervous system may be to allow a finite size neuronal network to participate in different tasks by producing a large number of rhythms~\citep{bose2011, jalil2004, li2007}.
-To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength, which can occur through the process of learning.
-Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.
-
-\section*{Conflict of Interest Statement}
-The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
-
-\section*{Author Contributions}
-MO and CH contributed to conception and design of the study.
-MO performed numerical computation and analysis.
-All authors contributed to manuscript writing and revision.
-
-\section*{Funding}
-This work was supported by the Wellcome Trust Doctoral Training Programme in Neural Dynamics, Grant no. 099699/Z/12/Z.
-
-\section*{Acknowledgements}
-The first author thanks the Wellcome Trust for financial support of his Ph.D. study.
-We thank Alan Champneys for sharing his insights on non-continuous maps during the course of this research.
-We are also grateful to Alan Roberts and Stephen R. Soffe for their comments on earlier versions of the manuscript.
-
-\section*{Data Availability Statement}
-The datasets generated for this study are available on request to the corresponding author.
-
-% \bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities
-\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
-
-\bibliography{bibliography.bib}
-
-\section*{Figure captions}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/nullclines-uncoupled.pdf}
-  \caption{Periodic solution of relaxation-oscillator model neuron.
-$\bm{\mathrm{(A)}}$ Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue, $v_\infty$) and $w$-nullcline (orange, $w_\infty$).
-Unstable fixed point $p_{f}$ is indicated by an orange dot.
-$\bm{\mathrm{(B)}}$ Corresponding voltage trace $v(t)$ of an action potential.~\label{fig:nullclines}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/depression-traces.pdf}
-  \caption{Solution profiles of a $4-4$ burst.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange).
-$\bm{\mathrm{(B)}}$ Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell 1.~\label{fig:depression-traces}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/burst-sols.pdf}
-  \caption{Voltage traces of both cells of numerically stable solutions for increasing values of the coupling strength $\gbar$ (increasing top to bottom).~\label{fig:burst-sols}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/bif-diagram.pdf}
-  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for increasing coupling strength $\gbar$.
-$\bm{\mathrm{(A)}}$ Period of stable solutions.
-Dashed lines show the interval between the $5-5$ and the suppressed solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals of $\gbar$.
-$\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in $\mathrm{(A)}$.
-Long $ISI$s are associated with the quiet phase of a burst, short $ISI$s with the free phase.
-During the free phase, $ISI$s are of approximately constant duration $T$.\label{fig:bif-diagram}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/nullclines-coupled.pdf}
-  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar s$.
-For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange point).
-Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until $p_{f}$ changes stability (half orange,  half blue point) at some critical total conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
-  \caption{Numerically computed values of the release delay for varying $\gbar$.
-Each of the three branches (A, B, C) also shows the timecourse of the total synaptic conductance $\gbar s$ of a sample stable solution of both cells (blue and orange), as well as the release conductance $g^{\star}$ (dashed green line).
-$\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution.
-Here the quiet cell only spikes after a significant release delay.
-$\bm{\mathrm{(B)}}$ Branch with a long release delay associated with a subset of $2-2$ solutions.
-Here the release condition is briefly satisfied after the first spike of cell 1.
-This does not cause firing of cell 2, which only occurs after the second spike of cell 1.
-$\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is approximately zero and the release condition is sufficient for firing of cell 2.
-   ~\label{fig:release-delay}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/free-quiet.pdf}
-  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
-The grey patches depict inter-burst-intervals $\delt$.
-$\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$.
-$\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/delta-t.pdf}
-  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
-Each continuous branch is associated with a stable $n-n$ burst solution.
-Increasing $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx T$.~\label{fig:delta-t}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/FQ-map.pdf}
-  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$.
-Curves $F_n$ intersect at $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/Pn-map.pdf}
-  \caption{Map $\Pi_{n}:d^{\star}$.
-$\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$ at $\gbar=0.6$ $\si{mS/cm^{2}}$.
-$\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$.
-The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/folds.pdf}
-  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves) and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
-$\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the corresponding solution period from numerical integration of the system of ODEs (orange).~\label{fig:folds}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
-  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
-\end{figure}
-
 \end{document}

### 2022-02-04 tex/sections/results.tex
Split latex document into subfiles

--- 2022-01-26 tex/draft.tex
@@
 
-\onecolumn
-\firstpage{1}
-
-\title[Scalar Poincaré map for bursting]{A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression.}
-
-\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
-\address{} %This field will be automatically populated
-\correspondance{} %This field will be automatically populated
-
-\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
-%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
-
-\maketitle
-
-\begin{abstract}
-\section{}
-Short-term synaptic plasticity is found in many areas of the central
-nervous system.  In the inhibitory half-centre central pattern
-generators involved in locomotion, synaptic depression is believed to
-act as a burst termination mechanism, allowing networks to generate
-anti-phase bursting patterns of varying periods.  To better understand
-burst generation in these central patter generators, we study a
-minimal network of two neurons coupled through depressing synapses.
-Depending on the strength of the synaptic conductance between the two
-neurons, this network can produce symmetric $n-n$ anti-phase bursts,
-where neurons fire $n$ spikes in alternation, with the period of such
-solutions increasing with the strength of the synaptic conductance.
-Relying on the timescale disparity in the model, we reduce the
-eight-dimensional network equations to a fully-explicit scalar
-Poincaré burst map.  This map tracks the state of synaptic depression
-from one burst to the next and captures the complex bursting dynamics
-of the network.  Fixed points of this map are associated with stable
-burst solutions of the full network model, and are created through
-fold bifurcations of maps.  We derive conditions that describe
-period-increment bifurcations between stable $n-n$ and $(n+1)-(n+1)$
-bursts, producing a full bifurcation diagram of the burst cycle
-period.  Predictions of the Poincaré map fit excellently with
-numerical simulations of the full network model and allow the study of
-parameter sensitivity for rhythm generation.
-
-\tiny
- \keyFont{ \section{Keywords:} Synaptic depression, Poincaré map, Dynamical system, Neuronal bursting, Central pattern generator}
-
-\end{abstract}
-
-\section{Introduction}
-% DEPRESSION
-Short-term synaptic plasticity may have a role in burst activity in
-central pattern generators (CPGs).  Short-term synaptic depression is
-commonly found in neuronal networks involved in the generation of
-rhythmic movements, such as in the pyloric CPG of the spiny
-lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of
-the chick embryo~\citep{donovan1998}.  Synaptic depression modulates
-the strength of synapses in response to changes to the presynaptic
-firing frequency.  At a high neuronal firing frequency, depression
-weakens the strength of synapses and therefore reduces the magnitude
-of the postsynaptic response.  At low firing frequency, it allows
-sufficient time for the synapse to recover from depression between
-spikes, leading to a stronger postsynaptic response.  In reciprocal
-networks, synaptic depression has been shown to act as a ``switch'',
-giving rise to a wide range of network dynamics such as synchronous
-and multi-stable rhythms, as well as fine tuning the frequency of
-network oscillations~\citep{nadim2000, nadim1999, bose2011}.
-
-% Brown
-~\citet{brown1911} pioneered the idea that synaptic depression acts as
-a burst termination mechanism in reciprocally inhibitory CPGs involved
-in rhythm generation of locomotion. When one side is firing during a
-burst the other, antagonistic side, is prevented from firing by
-synaptic inhibition. However, the weakening of inhibition as a result
-of synaptic depression eventually releases the antagonistic side so
-that it starts firing, terminating the burst on the side that had
-originally been firing.  This rhythmogenesis hypothesis has been
-considered one of a handful of standard mechanisms for generating
-locomotion rhythms in
-vertebrates~\citep{reiss1962,perkel1974,friesen1994}. It has been
-proposed as an explaination of the antiphase burst rhythm in
-struggling in \textit{Xenopus} tadpoles~\citep{li2007}.
-
-~\citet{bose2011} investigated burst generation in a generic
-half-centre CPG that consists of two identical, tonically active
-Morris-Lecar~\citep{morris1981} neurons coupled through inhibitory
-depressing synapses.  Numerical simulations showed that when the
-reciprocal synaptic conductance between the two neurons is varied, the
-network produces symmetric $n-n$ anti-phase bursts, with stronger
-synaptic coupling leading to longer bursts.  They used methods from
-geometric singular perturbation theory to separate the timescales of
-the fast membrane, and the slow synaptic dynamics of the network to
-derive one-dimensional conditions necessary for the existence of
-stable $n-n$ solutions (for $n\leq 2$). According to these conditions
-the type of firing pattern largely depends on the slow depression
-dynamics of the synapses between the two neurons, and can therefore be
-predicted by knowing the strengths of the synaptic conductances of the
-two synapses.
-Thus, the scalar conditions derived in~\citet{bose2011} provide a
-method to numerically identify the type of stable $n-n$ pattern for
-any given value of the coupling strength.  However, they do not
-predict the exact period of such solutions.
-Furthermore, while they provide good arguments for the validity of
-their reduction assumptions and the resulting scalar conditions, they
-do not verify them numerically.
-
-Here we extend the previous analysis by providing a Poincaré map of
-the slow depression dynamics.  This allows us not only to predict the
-types of stable $n-n$ solutions the full network can produce, (for any
-$n$), but also to study how varying the coupling strength affects the
-period of such solutions.  To do this, we build on, and numerically
-test, the assumptions on the fast-slow timescale disparity made
-in~\cite{bose2011}.  We reduce the two-cell model to a scalar
-Poincaré map that tracks the evolution of the depression from the
-beginning of one burst to the beginning of the next burst.  Stable
-fixed points of our map are associated with stable $n-n$ burst
-solutions.  Our map construction is motivated by the burst length map
-of a T-type calcium current, utilised by~\citet{matveev2007}, which
-approximates the anti-phase bursting dynamics of a network of two
-coupled Morris-Lecar neurons.  In contrast to our model, the network
-described in the~\cite{matveev2007} paper does not contain short-term synaptic
-depression, and burst termination is instead accomplished through the
-dynamics of a slow T-type calcium current.
-
-% MAIN RESULTS AND CONCLUSIONS
-The Poincaré map derived here replicates the results from numerical
-simulations of the full two-cell ODE system: Given the strength of
-maximum conductance between the two neurons, fixed points of our map
-predict the type and period of $n-n$ patterns, the switch between
-burst solutions of different periods, as well as the occurrence of
-co-existent solutions.  In addition to proving the existence and
-stability of fixed points, our map shows that fixed points are created
-via a fold bifurcation of maps.  We also derive algebraic conditions
-that predict the period increment bifurcations that allow the switch
-between $n-n$ and $(n+1)-(n+1)$ solutions.  Because our map is fully
-explicit, it lays the framework for studying the effects of other
-model parameter on network dynamics without the need to run expensive
-numerical integrations of the ODEs.
-
-% PAPER STRUCTURE.
-This paper is organised as follows.  First, we introduce the network
-of two neurons, and describe the properties of single cell and synapse
-dynamics.  We use numerical simulations of the network to provide an
-intuition for the range of possible burst dynamics the system can
-produce.  Next, we state and justify the simplifying assumptions that
-are necessary for the map construction.  Finally, we analytically
-derive the first return map of the depression variable as well as the
-conditions that are required for stable solutions to bifurcate between
-$n-n$ and $(n+1)-(n+1)$ solutions.  We end this work with a
-discussion.
-
-\section{Materials and Methods}
-We consider a pair of identical Morris-Lecar neurons~\citep{morris1981}, with parameters adapted from~\cite{bose2011}.
-The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
-The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
-The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
-\begin{align}
-    ~\label{eq:cell-modelA}
-     \dot v_{i}&= f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}),\\
-    ~\label{eq:cell-modelB}
-     \dot w_{i} &=h(v_i,w_i).
-   \end{align}
-Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.
-Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
-\begin{equation}
- ~\label{eq:memcur}
-  f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})-g_{\leak}(v_{i}-v_{\leak}) + I.
-\end{equation}
-The currents include a constant current $I$, and three ionic currents:
-an instantaneous calcium current, a potassium current, and a leak current, with respective reversal potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances $g_{\ca}$, $g_{\k}$, and $g_{\leak}$.
-The function $h(v_{i}, w_{i})$ models the kinetics of the potassium gating variable $w_{i}$, and is given by
-\begin{equation}
-  h(v_{i}, w_{i})=\frac{w_{\infty}(v_{i})-w_{i}}{\tau_{w}}~\label{eq:h}.
-\end{equation}
-The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the \textbf{Supplementary Material S1}.
-
-The dynamics of the synaptic interactions between the neurons are governed by a synaptic gating variable $s_{i}$ and a depression variable $d_{i}$:
-\begin{linenomath}
-  \begin{align}
-    \dot s_{i} &= -s_{i}/\tau_{s}~\label{eq:dot-s},\\
-    \dot d_{i} &= (1-d_{i})/\tau_{d}~\label{eq:dot-d}.
-  \end{align}
-\end{linenomath}
-Variable $d_{i}$ describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
-Our model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
-In between spikes $s_{i}$ decays with time constant $\tau_{s}$, while $d_{i}$ recovers with time constant $\tau_{d}$.
-Because synaptic depression occurs on a much slower timescale than synaptic inhibition, we assume $\tau_{d}\gg\tau_{s}$.
-At spike time when the voltage $v_{i}$ crosses a synaptic threshold $v_{\theta}$, the synaptic variable $s_{i}$ is reset to the current value of $d_{i}$, and $d_{i}$ is scaled down by the depression strength parameter $\lambda$, where $0<\lambda<1$.
-This results in the following discontinuous reset rule on spike time:
-\begin{linenomath}
-  \begin{align}
-    s_{i} &\leftarrow d_{i}~\label{eq:s-reset},\\
-    d_{i} &\leftarrow \lambda d_{i}~\label{eq:d-reset}.
-  \end{align}
-\end{linenomath}
-The equations for the depression model were adapted from the~\citet{bose2001} model.
-These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by~\citet{tsodyks1997}.
-The original equations in~\cite{bose2001} include an exponential decay of $d_{i}$ throughout the active phase of the action potential, that is $\dot d_{i}=-d_{i}/\tau_{\beta}$ for $v_{i}>v_{\theta}$.
-To simplify the mathematical analysis we have reduced these dynamics to a single-reset event at spike time according to \cref{eq:d-reset}.
-This simplification is natural given an approximately constant duration of the active phase of an action potential, and it will become evident from our results that this simplification does not qualitatively change the dynamics of the network compared to the original equations, where depression dynamics are described by an exponential decay.
-
-When the cells are uncoupled ($\gbar=0$), the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
-The two curves intersect along the middle branch of $v_{\infty}$, creating an unstable fixed point $p_{f}=(v_{f},w_{f})$ with a surrounding stable limit cycle of period $T$ (\cref{fig:nullclines}A).
-Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
-The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
-During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
-Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
-During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
-
-The two-cell network model is numerically integrated using an adaptive step-size integrator for stiff differential equations implemented with XPPAUT~\citep{ermentrout2002} and controlled through the Python packages SciPy~\citep{scipy2020} and PyXPP~\citep{pyxpp}.
-The following mathematical analysis is performed on the equations of a single cell.
-Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
-
-\section{Results}
 \subsection{Anti-phase burst solutions}
@@
 Suppose that at $t=0$ cell 1 becomes free with some initial $d(0)$.
-Cell 1 then fires $n$ spikes at the uncoupled period $T$.
+Cell 1 then fires $n$ spikes at the uncoupled period $T=T_{act}+T_{inact}$.
 Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
-After $n$ spikes the total conductance $\gbar s(t)$ acting on the quiet cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}, that is at some time $t=(n-1)T+\delt$ we have $\gbar s(t)=g^{\star}$.
+After $n$ spikes the total conductance $\gbar s(t)$ acting on the quiet cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}, that is at some time $t=(n-1)T + \delt$, where $\Delta t < T_{inact}$, we have $\gbar s(t)=g^{\star}$.
 Cell 2 is then released and prevents cell 1 from further spiking.
-Here $\delt$ is the \emph{inter-burst-interval}, or the time between the last spike of cell 1 and the first spike of cell 2~\citep{bose2011}.
+Here $\delt$ is the time between the last spike of cell 1 and the first spike of cell 2 ~\citep{bose2011}.
 Once released, cell 2 also fires $n$ spikes until cell 1 becomes free once again at the cycle period.
@@
 
-Note that only the quiet phase depends on $\delt$, and $\delt$ will play a central role in the construction of $\Pi_{n}$.
+Note that only the quiet phase depends on $\delt$ which will play a central role in the construction of $\Pi_{n}$.
 From \cref{eq:P} $\delt$ can be be computed as
@@
 
-Distinguishing between the free and quiet phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
-As can be seen from \cref{fig:free-quiet1}C, during the free phase $d$ depresses at spike times and recovers in the $ISI$s.
-In contrast, during the quiet phase $d$ only recovers and does not depress.
+Distinguishing between the active and silent phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
+As can be seen from \cref{fig:free-quiet1}C, during the active phase $d$ depresses during the active phase of spikes and recovers during the inactive phases of spikes.
+% TODO need to sort out terminology here, i.e. inactive vs quiet
+In contrast, during the silent phase $d$ only recovers and does not depress.
 Given the initial $d^{\star}=d(0)$ at the beginning of the cycle and the number of spikes in the free phase $n$, we can now construct the burst map $\Pi_{n}$.
@@
 
+% TODO: Edit par
 We start the construction of $\Pi_n$ by first considering the free phase and building the map $F_n$.
-At each spike time $t_{k}$, variable $d$ depresses with the reset $d(t_{k})\leftarrow \lambda d(t_{k}^{-})$ (\cref{eq:d-reset}).
-For the duration of the subsequent $ISI$, the recovery of $d$ is described by the solution to \cref{eq:dot-d}:
+At each spike time $t_{k}$ where $d(t_k) = d_k$, variable $d$ decays first for the duration of the active phase of the spike for $T_{act}$, as described by the solution to \cref{eq:dot-d}.
+At $t = t_k + T_{act}$ we have
 \begin{equation}
-  d(t) = 1 - (1-\lambda d_{k})e^{-t/\tau_{d}}~\label{eq:d-sol},
+  d(t_k + T_{act}) = d_k e^{-T_{act}/\tau_b}.
 \end{equation}
-where the variable $d_{k}=d(t^{-}_{k})$ is the level of depression at spike time $t_{k}$.
-By substituting $t=T$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the free phase:
+The depression variable then recovers during the inactive phase of the spike until $t_{k+1}$, where for $0<t<T_{inact}$ we get
+\begin{equation}
+  d(t_{k+1}) = 1 - (1 - d_k e^{-T_{act}/\tau_b} )e^{-t/\tau_a}.
+\end{equation}
+By substituting $t=T_{inact}$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the free phase:
 \begin{equation}
@@
 \end{equation}
-where to keep the notation simple we let $\rho=\exp(-T/\tau_{d})$.
-Since $0<\lambda, \rho<1$, the map~\eqref{eq:map-d} is increasing and contracting, with a fixed point at
+where to keep the notation simple we let
+\begin{align}
+  \lambda & = \exp(-T_{act}/\tau_b),    \\
+  \rho    & =\exp(-T_{inact}/\tau_{a}).
+\end{align}
+
+Given constant $T_{act}$ and $T_{inact}$, parameter $\lambda$ determines how much the synapses depresses during the active phase of the spike, while $\rho$ determines how much it recovers during the inactive phase.
+Since $0<\lambda, \rho<1$, map \cref{eq:map-d} is increasing and contracting, with a fixed point at
 \begin{equation}
@@
 Using the release condition in \cref{eq:release} allows us to derive the value of the the minimum coupling strength that will produce the full suppressed solution, denoted as $\gbar_{s}$.
+% TODO Explain why s(0) = ds
+% TODO See https://trello.com/c/AYqZIaXh: Would be good to elaborate on the idea that lambda and tau can be
+% viewed as the new time constants in the reduced system.
 Solving \cref{eq:dot-s} for $s(t)$ with $t=T$ and setting the initial value $s(0)=d_{s}$ gives
 \begin{equation}
-\gbar_{s} d_{s}e^{-T/\tau_{s}}=g^{\star}.
+  \gbar_{s} d_{s}e^{-T/\tau_\kappa}=g^{\star}.
 \end{equation}
-By further substituting the definition of $d_{s}$ in~\eqref{eq:dsup} and rearranging, we can write $\gbar_{s}$ as a function of the depression strength $\lambda$:
+By further substituting the definition of $d_{s}$ in~\eqref{eq:dsup} and rearranging, we can write $\gbar_{s}$ as a function of $\lambda$ and $\rho$:
 \begin{equation}
   \label{eq:gs}
-  \gbar_{s}(\lambda) = g^{\star}e^{T/\tau_{s}}\frac{1-\lambda \rho}{1-\rho}.
+  \gbar_{s}(\lambda, \rho) = g^{\star}e^{T/\tau_\kappa}\frac{1-\lambda \rho}{1-\rho}.
 \end{equation}
@@
 
-Solving~\eqref{eq:map-d} gives us the linear map $\delta_{n}:d^{\star}\mapsto d_{n}$, that for some initial $d^{\star}$ computes the depression at the $n$th spike time, $d_{n}=d(t_{n}^{-})$:
+Solving~\eqref{eq:map-d} gives us the linear map $\delta_{n}:d^{\star}\mapsto
+d_{n}$, that for some initial $d^{\star}$ computes the depression at the $n$th
+spike time, $d_{n}=d(t_{n}^{-})$:
 \begin{equation}
@@
 \end{equation}
-Since $\lambda < 1$, function $\delta_{n}$ is a linearly increasing function of $d^{\star}$ with a fixed point at $d_{s}$ for all $n$.
-Having identified $d$ after $n$ spikes, we can now use the release condition $\gbar s = g^{\star}$ (\cref{eq:release}) to find $\delt$.
-At the last spike of the free phase at time $t_{n}=(n-1)T$ the synapse variable $s$ is reset according to \cref{eq:s-reset}:
-\begin{equation}
-  s(t_{n})\leftarrow \dn(\dstar).
-\end{equation}
-After the last spike $s$ decays exponentially according to the solution of \cref{eq:dot-s}, where setting the initial condition $s(0)=\dn(\dstar)$ yields:
+Since $\lambda < 1$, function $\delta_{n}$ is a linearly increasing function of
+$d^{\star}$ with a fixed point at $d_{s}$ for all $n$.  Having identified $d$ after $n$
+spikes, we can now use the release condition $\gbar s = g^{\star}$ (\cref{eq:release}) to
+find $\delt$.
+% FIXME:
+After the last spike of the free phase at time $t_{n} = (n-1)T$ the synapse variable $s$
+has the value of $d$ for the duration of $T_{act}$, which is given by
+$\delta_n(\dstar)\lambda$. $s$ then decays exponentially for $\Delta t < T_{inact}$.
+Solving \cref{eq:dot-s} (case $v < v_\theta$) with initial condition
+$s(0)=\dn(\dstar)\lambda$ yields:
 \begin{equation}
   ~\label{eq:s-sol}
-  s(\delt)=\dn(\dstar)e^{-\Delta t/\tau_{s}}.
+  s(\delt)=\dn(\dstar)e^{-\Delta t/\tau_\kappa}.
 \end{equation}
-Substituting $s(\delt)$ into $s$ of the release condition (\cref{eq:release}) gives then
+Substituting $s(\delt)$ into $s$ of the release condition (\cref{eq:release})
+gives then
 \begin{equation}
   ~\label{eq:release2}
-  \gbar \dn(\dstar) e^{-\delt/\tau_{s}}=g^{\star}.
+  \gbar \dn(\dstar) e^{-\delt/\tau_\kappa}=g^{\star}.
 \end{equation}
-Our assumption of the release condition guarantees that the quiet cell 2 spikes and becomes free when $\gbar s - g^{\star}$ crosses zero.
-Solving \cref{eq:release2} for $\delt$ allows us to compute the inter-spike-interval as a function of $\dstar$, which defines our map $F_n$:
+Our assumption of the release condition guarantees that the quiet cell 2 spikes and
+becomes free when $\gbar s - g^{\star}$ crosses zero. Solving \cref{eq:release2} for
+$\delt$ allows us to compute the inter-spike-interval as a function of $\dstar$, which
+defines our map $F_n$:
 \begin{equation}
   ~\label{eq:Fn-map}
-  F_{n}(d^{\star}):=\tau_{s}\ln{\left(\frac{\gbar }{g^{\star}} \delta_{n}(d^{\star})\right)}= \delt.
+  F_{n}(d^{\star}):=\tau_\kappa \ln{\left(\frac{\gbar }{g^{\star}} \delta_{n}(d^{\star})\right)}= \delt.
 \end{equation}
 
-\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\gbar$.
-Larger values of $d^{\star}$ and $\gbar$, respectively, cause stronger inhibition of the quiet cell, and therefore prolong its release time and the associated $\delt$.
-Map $F_{n}$ is defined on $d^{\star}>d_{a}$, where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(\dstar)=0$ in \cref{eq:delta-map} for $\dstar$, which yields
+\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing
+function of $d^{\star}$ as well as $\gbar$.  Larger values of $d^{\star}$ and $\gbar$,
+respectively, cause stronger inhibition of the quiet cell, and therefore prolong its
+release time and the associated $\delt$.  Map $F_{n}$ is defined on $d^{\star}>d_{a}$,
+where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(\dstar)=0$ in
+\cref{eq:delta-map} for $\dstar$, which yields
 \begin{equation}
@@
   \label{eq:non-degen1}
-  \dv{\Pi_{n}}{\gbar}&>0,\\[0.5ex]
+  \dv{\Pi_{n}}{\gbar}  & >0, \\[0.5ex]
   \label{eq:dPidd}
-  \dv{\Pi_{n}}{\dstar}&>0,
+  \dv{\Pi_{n}}{\dstar} & >0,
 \end{align}
@@
 \begin{align}
-  \Pi_{n}(\dstar_{b}; \gbar_{b}) &=\dstar_{b},\\
-  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b})&=1.
+  \Pi_{n}(\dstar_{b}; \gbar_{b})                     & =\dstar_{b}, \\
+  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b}) & =1.
 \end{align}
@@
 \begin{align}
-  \dstar_{b}(n) &= \operatorname{argmin} G_{n}(\dstar_{f}),\\
-  \gbar_{b}(n)  &= \min{G_{n}(\dstar_{f})}.
+  \dstar_{b}(n) & = \operatorname{argmin} G_{n}(\dstar_{f}), \\
+  \gbar_{b}(n)  & = \min{G_{n}(\dstar_{f})}.
 \end{align}
@@
 \begin{align}
-  \dv{G_n}{\dstar_f}& < 0, \text{ for } \dstar_f>\dstar_b(n) \text{ stable},\\[0.5ex]
-  \dv{G_n}{\dstar_f}& > 0, \text{ for } \dstar_f<\dstar_b(n) \text{ unstable},
+  \dv{G_n}{\dstar_f} & < 0, \text{ for } \dstar_f>\dstar_b(n) \text{ stable},   \\[0.5ex]
+  \dv{G_n}{\dstar_f} & > 0, \text{ for } \dstar_f<\dstar_b(n) \text{ unstable},
 \end{align}
@@
 \begin{align}
-  \pdv{F_n}{\dstar_f} &= \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar_f)}>0,\\[0.5ex]
-  \pdv{F_n}{\gbar}  &= \frac{\taus}{\gbar}>0.
+  \pdv{F_n}{\dstar_f} & = \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar_f)}>0, \\[0.5ex]
+  \pdv{F_n}{\gbar}    & = \frac{\taus}{\gbar}>0.
 \end{align}
@@
 \begin{align}
-  \gbar_+(n) &< \gbar_-(n)\label{eq:easy1},\\
-  \gbar_+(n) &< \gbar_+(n+1)\text{ and } \gbar_-(n)<\gbar_-(n+1)\label{eq:easy2},\\
-  \gbar_+(n+1) &< \gbar_-(n)\label{eq:coexistence},\\
-  \gbar_-(n+1) - \gbar_+(n+1) &< \gbar_-(n) - \gbar_-(n)\label{eq:robustness}.
+  \gbar_+(n)                  & < \gbar_-(n)\label{eq:easy1},                                       \\
+  \gbar_+(n)                  & < \gbar_+(n+1)\text{ and } \gbar_-(n)<\gbar_-(n+1)\label{eq:easy2}, \\
+  \gbar_+(n+1)                & < \gbar_-(n)\label{eq:coexistence},                                 \\
+  \gbar_-(n+1) - \gbar_+(n+1) & < \gbar_-(n) - \gbar_-(n)\label{eq:robustness}.
 \end{align}
@@
 
-\section{Discussion}
-% PROBLEM SUMMARY
-Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming~\citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
-In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
-Mathematical modelling can shed light on the underlying mechanisms that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.
-
-% MAIN RESULTS
-To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression.
-When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n-n$ burst patterns.
-Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
-This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n-n$ solutions respectively.
-Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons.
-Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n-n$ burst solutions of the full two-cell system of ODEs.
-The results from our one-dimensional map match excellently with numerical simulation of the full network.
-Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.
-
-% FURTHER METHOD IDEAS
-We have studied $n-n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
-However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes.
-It is conceivable that our map construction can be extended to also capture such $m-n$ solutions.
-Remember, in the case of symmetrical coupling with $n-n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
-To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other.
-To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$.
-While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}.
-Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons.
-As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses.
-In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.
-
-In tadpoles, struggling is believed to be initiated by an increase in the firing frequency of reciprocally inhibitory commisural interneurons, which has been hypothesised to lead to stronger synaptic depression of inhibition and result in the iconic anti-phase bursting \citep{li2007}.
-It would therefore be interesting to study how varying the cell intrinsic firing period $T$ could affect the network rhythm.
-While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying $T$.
-Recall that $T$ is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters.
-This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult.
-A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting in this scenario.
-
-% LIMITATION: SPIKE MAP
-Our simulations of the network showed that $n-n$ solutions lose robustness as their period is increased.
-That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
-We were able to replicate this finding by numerically finding the respective left and right borders of stable $n-n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
-We have also noted the resemblance of our bifurcation diagram to one where such $n-n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
-It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}.
-Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
-The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
-In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations.
-It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
-In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.
-
-% FLOW SYSTEM BIFURCATION
-In addition to stable $n-n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n-n$ solutions.
-While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.
-However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
-SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
-% Should be possible to use averaging to reduce the system.
-
-% BIOLOGICAL IMPORTANCE OF DEPRESSION
-We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.
-This result is in line with the idea that one role of synaptic depression in the nervous system may be to allow a finite size neuronal network to participate in different tasks by producing a large number of rhythms~\citep{bose2011, jalil2004, li2007}.
-To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength, which can occur through the process of learning.
-Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.
-
-\section*{Conflict of Interest Statement}
-The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
-
-\section*{Author Contributions}
-MO and CH contributed to conception and design of the study.
-MO performed numerical computation and analysis.
-All authors contributed to manuscript writing and revision.
-
-\section*{Funding}
-This work was supported by the Wellcome Trust Doctoral Training Programme in Neural Dynamics, Grant no. 099699/Z/12/Z.
-
-\section*{Acknowledgements}
-The first author thanks the Wellcome Trust for financial support of his Ph.D. study.
-We thank Alan Champneys for sharing his insights on non-continuous maps during the course of this research.
-We are also grateful to Alan Roberts and Stephen R. Soffe for their comments on earlier versions of the manuscript.
-
-\section*{Data Availability Statement}
-The datasets generated for this study are available on request to the corresponding author.
-
-% \bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities
-\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
-
-\bibliography{bibliography.bib}
-
-\section*{Figure captions}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/nullclines-uncoupled.pdf}
-  \caption{Periodic solution of relaxation-oscillator model neuron.
-$\bm{\mathrm{(A)}}$ Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue, $v_\infty$) and $w$-nullcline (orange, $w_\infty$).
-Unstable fixed point $p_{f}$ is indicated by an orange dot.
-$\bm{\mathrm{(B)}}$ Corresponding voltage trace $v(t)$ of an action potential.~\label{fig:nullclines}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/depression-traces.pdf}
-  \caption{Solution profiles of a $4-4$ burst.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange).
-$\bm{\mathrm{(B)}}$ Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell 1.~\label{fig:depression-traces}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/burst-sols.pdf}
-  \caption{Voltage traces of both cells of numerically stable solutions for increasing values of the coupling strength $\gbar$ (increasing top to bottom).~\label{fig:burst-sols}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/bif-diagram.pdf}
-  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for increasing coupling strength $\gbar$.
-$\bm{\mathrm{(A)}}$ Period of stable solutions.
-Dashed lines show the interval between the $5-5$ and the suppressed solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals of $\gbar$.
-$\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in $\mathrm{(A)}$.
-Long $ISI$s are associated with the quiet phase of a burst, short $ISI$s with the free phase.
-During the free phase, $ISI$s are of approximately constant duration $T$.\label{fig:bif-diagram}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/nullclines-coupled.pdf}
-  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar s$.
-For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange point).
-Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until $p_{f}$ changes stability (half orange,  half blue point) at some critical total conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
-  \caption{Numerically computed values of the release delay for varying $\gbar$.
-Each of the three branches (A, B, C) also shows the timecourse of the total synaptic conductance $\gbar s$ of a sample stable solution of both cells (blue and orange), as well as the release conductance $g^{\star}$ (dashed green line).
-$\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution.
-Here the quiet cell only spikes after a significant release delay.
-$\bm{\mathrm{(B)}}$ Branch with a long release delay associated with a subset of $2-2$ solutions.
-Here the release condition is briefly satisfied after the first spike of cell 1.
-This does not cause firing of cell 2, which only occurs after the second spike of cell 1.
-$\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is approximately zero and the release condition is sufficient for firing of cell 2.
-   ~\label{fig:release-delay}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/free-quiet.pdf}
-  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
-The grey patches depict inter-burst-intervals $\delt$.
-$\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$.
-$\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/delta-t.pdf}
-  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
-Each continuous branch is associated with a stable $n-n$ burst solution.
-Increasing $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx T$.~\label{fig:delta-t}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/FQ-map.pdf}
-  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$.
-Curves $F_n$ intersect at $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/Pn-map.pdf}
-  \caption{Map $\Pi_{n}:d^{\star}$.
-$\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$ at $\gbar=0.6$ $\si{mS/cm^{2}}$.
-$\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$.
-The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/folds.pdf}
-  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves) and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
-$\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the corresponding solution period from numerical integration of the system of ODEs (orange).~\label{fig:folds}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
-  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
-\end{figure}
-
 \end{document}

### 2022-02-04 tex/supplemental.tex
Split latex document into subfiles

@@
               & \\
-    $g_{\leak}$ & 0.15 \si{mS/cm^2}\\
-    $g_{\ca}$ & 0.3 \si{mS/cm^2}\\
-    $g_{\k}$ & 0.6 \si{mS/cm^2}\\
-    $v_{\leak}$ & -50 mV\\
-    $v_{\ca}$ & 100 mV\\
-    $v_{\k}$ & -70 mV\\
-    $v_{A}$ & 1 mV\\
-    $v_{B}$ & 14.5 mV\\
-    $v_{C}$ & 4 mV\\
-    $v_{D}$ & 15 mV\\
-    $I$ & 6 \si{\mu A/cm^2}\\
-    $\tau$$_{w}$ & 100 ms\\
-    $\tau$$_{d}$ & 1000 ms\\
-    $\tau$$_{s}$ & 100 ms\\
-    $v_{\theta}$ & 0 mV\\
-    $v_{s}$ & -80 mV\\
-    $\lambda$ & 0.5\\
-    $T$ & 217 ms\\
-    $\gstar$ & 0.03804 \si{mS/cm^2}\\
+    $g_{\leak}$ & $0.15$ \si{mS/cm^2}\\
+    $g_{\ca}$ & $0.3$ \si{mS/cm^2}\\
+    $g_{\k}$ & $0.6$ \si{mS/cm^2}\\
+    $v_{\leak}$ & $-50$ \si{mV}\\
+    $v_{\ca}$ & $100$ \si{mV}\\
+    $v_{\k}$ & $-70$ \si{mV}\\
+    $v_{A}$ & $1$ \si{mV}\\
+    $v_{B}$ & $14.5$ \si{mV}\\
+    $v_{C}$ & $4$ \si{mV}\\
+    $v_{D}$ & $15$ \si{mV}\\
+    $I$ & $3.8$ \si{\mu A/cm^2}\\
+    $\tau_w$ & $100$ \si{ms}\\
+    $\tau_a$ & $1000$ \si{ms}\\
+    $\tau_b$ & $100$ \si{ms}\\
+    $\tau_\kappa$ & $100$ \si{ms}\\
+    $\tau_\gamma$ & $0.0001$ \si{ms}\\
+    $v_{\theta}$ & $0$ \si{mV}\\
+    $v_{s}$ & $-80$ \si{mV}\\
+    $T$ & $376$ \si{ms}\\
+    $T_{act}$ & $49$ \si{ms}\\
+    $T_{inact}$ & $327$ \si{ms}\\
+    $\gstar$ & $0.0036$ \si{mS/cm^2}\\
+    $\lambda:=\exp(-T_{act}/\tau_b)$ & $0.612$\\
+    $\rho:=\exp(-T_{inact}/\tau_a)$ & $0.721$\\
   \end{tabular}

### 2022-03-05 scripts/compute_bifdat.py
Refactor ode implementation

@@ -1,45 +1,0 @@
-"""Script to numerically compute bifurcation diagram."""
-
-import argparse
-import pickle
-
-import pandas as pd
-
-from poincare_map import ode
-
-
-def compute_bif_diagram(xppfile: str, echo: bool = True) -> pd.DataFrame:
-    nsteps = 100
-    p0s = [0.3, 0.4, 0.5, 0.52, 0.56]
-    parsteps = [0.01, 0.01, 0.005, 0.001, 0.001]
-    totals = [5000, 8000, 10000, 15000, 15000]
-    curves = []
-    for p0, step, total in zip(p0s, parsteps, totals):
-        if echo:
-            print(f"Initialising parameter at {p0}")
-        left = ode.cont(
-            xppfile, g=p0, parstep=-step, nsteps=nsteps, total=total
-        )
-        right = ode.cont(
-            xppfile, g=p0, parstep=step, nsteps=nsteps, total=total
-        )
-        if (left is not None) and (right is not None):
-            curve = (
-                left.iloc[::-1].append(right.iloc[1:]).reset_index(drop=True)
-            )
-            curves.append(curve)
-        else:
-            curves.append(None)
-    return pd.concat(curves)
-
-
-if __name__ == "__main__":
-    parser = argparse.ArgumentParser()
-    parser.add_argument("--output", help="Output file", type=str)
-    parser.add_argument(
-        "--xppfile", help="XPP ODE file", default="mlml.ode", type=str
-    )
-    args = parser.parse_args()
-
-    dat = compute_bif_diagram(args.xppfile)
-    pickle.dump(dat, open(args.output, "wb"))

### 2022-03-05 scripts/makefig.py

@@ -1,3 +1,4 @@
+# %% Initialise
 import itertools
 import multiprocessing
 import os
@@ -7,12 +8,13 @@ import warnings
 from os import path
 
 import matplotlib
+matplotlib.use('pgf')
+
 import pandas as pd
 import pyxpp.pyxpp as xpp
 import scipy as sp
 from matplotlib import patches
 from matplotlib import pyplot as plt
-from matplotlib.backends.backend_pgf import FigureCanvasPgf
 from matplotlib.gridspec import GridSpec
 from matplotlib.lines import Line2D
 from pandas import DataFrame
@@ -22,27 +24,19 @@ from pathlib import Path
 from poincare_map import helpers
 from poincare_map import model
 from poincare_map import ode
+from poincare_map import paths
 
 import numpy as np
+
+plt.ioff()
 
 warnings.filterwarnings("ignore", category=DeprecationWarning)
 # Ignore devide by zero
 np.seterr(divide='ignore')
 np.seterr(all='ignore')
 
-rcp = matplotlib.rcParamsDefault
-plt.ioff()
-matplotlib.use('pgf')
 
-
-DATDIR = Path('data')
-FIGDIR = Path('figures/')
-if not os.path.isdir(DATDIR):
-    os.mkdir(DATDIR)
-if not os.path.isdir(FIGDIR):
-    os.mkdir(DATDIR)
-
-XPPFILE = 'mlml.ode'
+xppfile = str(paths.odes / "mlml.ode")
 CENTER_TITLE_SIZE = 11
 FIGWIDTH = 3.85
 FIGSIZE = (FIGWIDTH, FIGWIDTH)
@@ -50,6 +44,7 @@ FIG2by1 = (FIGWIDTH*1.4, (FIGWIDTH*1.4)/2)
 
 EQSIZE = 15                     # Font size of equaitons.
 
+rcp = matplotlib.rcParamsDefault
 rcp['figure.max_open_warning'] = 0
 rcp['axes.unicode_minus'] = False
 rcp['text.usetex'] = True
@@ -66,12 +61,10 @@ rcp['pgf.preamble'] = r'\usepackage{amsmath} \usepackage{siunitx}'
 
[…]

### 2022-03-05 src/poincare_map/helpers.py

@@ -1,92 +1,148 @@
+from __future__ import annotations
+from logging import debug
+
+import pandas as pd
 import numpy as np
-from typing import List, Optional, Tuple
+from numpy.typing import ArrayLike
+from typing import Dict, List, Optional, Tuple
 from matplotlib import pyplot as plt
 import matplotlib.lines as mlines
 import matplotlib.patches as mpatches
 
 
-def roots(x: np.ndarray) -> np.ndarray:
+def roots(x: np.ndarray, up: int = 0) -> np.ndarray:
     """Find roots using sign changes."""
     signs = np.sign(x)
-    roots = np.where(signs + np.roll(signs, -1) == 0)[0]
-    return roots
+    # root_mask = (signs + np.roll(signs, -1)) == 0
+    # NOTE: Careful here, not sure if this introduces others bugs...
+    root_mask = np.append(np.diff(signs) != 0, False)
+    # Consider direction of sign changes.
+    if up == 1:  # Return positive change roots.
+        return np.where(root_mask & (signs < 0))[0]
+    elif up == -1:  # Return negative change roots.
+        return np.where(root_mask & (signs > 0))[0]
+    else:  # Return all roots.
+        return np.where(root_mask)[0]
 
 
-def spikes(x: np.ndarray) -> np.ndarray:
-    """Find spike indices using roots with positive slope."""
+def spike_times(sol: pd.Series) -> pd.Index:
+    """Find spike times of a voltage trace using upward zero crossings."""
+    ids = roots(sol.to_numpy(), up=1)
+    return sol.index[ids]
 
-    id1 = roots(x)
-    if len(id1) > 0:
-        grad1 = np.gradient(x)
-        return id1[grad1[id1]>0]
+
+# def events(x: np.ndarray, down: bool = True) -> np.ndarray:
+#     """Find indices of events where the slope of array changes its sign."""
+#     grad = np.gradient(x)
+#     signs = np.sign(grad)
+#     direction = signs > 0 if down else signs < 0
+#     sign_changes = np.where((signs + np.roll(signs, -1) == 0) & direction)[0]
+#     return sign_changes
+
+
+# def find_limit_cycle(
+#     sol: pd.DataFrame,
+#     thresh: float = 1e-3,
+#     norm: bool = True,
+# ) -> pd.DataFrame:
+#     """Try to find limit cycle in solution using a voltage section."""
+#     tks = spike_times(sol["v1"])
+#     # Case 1: No spiking - return fixed point.
[…]

### 2022-03-05 src/poincare_map/model.py

@@ -1,473 +1,0 @@
-"""Poincare map definition with methods.
-
-Module containing the most important model parameters and derived
-quantities and functions.
-"""
-
-from typing import NamedTuple, Sequence, Optional, Tuple
-
-import numpy as np
-from scipy import optimize
-from pandas import DataFrame
-from pynverse import inversefunc
-
-
-class Pars(NamedTuple):
-    """Map parameters."""
-
-    g: float = 0
-    gstar: float = 0.0036
-    period: float = 375  # Spiking period.
-    tauk: float = 100
-
-
-    @property
-    def rho(self):
-        return np.exp(-self.period / self.taud)
-
-    @property
-    def d_sup(self):
-        return (1 - self.rho) / (1 - self.Lambda * self.rho)
-
-    @property
-    def g_sup(self):
-        return self.gstar * np.exp(self.period / self.taus) / self.d_sup
-
-    @property
-    def tau(self):
-        return 2 * self.taus / self.taud
-
-
-## Convenience functions
-
-
-def alpha(pars: Pars, n: int) -> float:
-    return pow(pars.Lambda * pars.rho, n - 1)
-
-
-def beta(pars: Pars, n: int) -> float:
-    return (1 - pars.rho) * sum(
-        [pow(pars.Lambda * pars.rho, k) for k in range(int(n - 1))]
-    )
-
-
-def L2delt(pars: Pars, L: float) -> float:
-    """Get delta-t from burst length L."""
-    if L < 0:
-        return L
-    else:
-        return L % pars.period
-
-
-def L2n(pars: Pars, L: float) -> int:
-    """Get number of spikes in burst of length L."""
-    if L < 0:
-        return 0
-    else:
-        return int(L // pars.period + 1)
-
-
-def d2n(pars: Pars, d: float) -> int:
-    """Just a convenience function to find n from d."""
-    L = F_map(pars, d)
-    return L2n(pars, L)
-
-
-def d_n(pars: Pars, delt: float) -> float:
-    """Value of d at last (nth) spike time."""
-    return pars.gstar / pars.g * np.exp(delt / pars.taus)
-
-
-def d_a(pars: Pars, n: int) -> float:
-    """Leftmost bound of Pn-map domain."""
-    return -beta(pars, n) / alpha(pars, n)
-
-
[…]

### 2022-03-05 src/poincare_map/ode.py

@@ -1,206 +1,265 @@
 """Utilities for numerical integration of XPPAUT ODEs."""
+from __future__ import annotations
 
-import pandas as pd
-from typing import List, Optional, Tuple, Dict
 import multiprocessing
+from abc import ABC, abstractmethod
 from functools import partial
+import typing as tp
+
 import numpy as np
+import pandas as pd
 import pyxpp.pyxpp as xpp
+from scipy import optimize
+
 from poincare_map import helpers
 
 
-def run(xppfile: str, **kwargs) -> pd.DataFrame:
-    """Run XPP ODEs and wrap result in a Pandas dataframe."""
+class ODE(ABC):
+    ode_file: str
+    # State variables.
+    state_vars: tp.List[str]
+    # Model parameters.
+    pars: tp.Dict[str, float]
+    # Initial conditions.
+    ics: pd.DataFrame
+    # Numerical options.
+    numerics: tp.Dict[str, float]
 
-    dat = xpp.run(xppfile, **kwargs)
-    allvars = np.append("t", xpp.read_vars(xppfile))
-    return pd.DataFrame(dat, columns=allvars)
+    def __init__(self, ode_file: str) -> None:
+        """Initialise class from ode file."""
+        self.ode_file = ode_file
+        self.state_vars = list(xpp.read_vars(ode_file))
+        self.pars = dict(xpp.read_pars(ode_file))
+        self.ics = pd.DataFrame(
+            [xpp.read_ics(ode_file)], columns=self.state_vars
+        )
+        self.numerics = dict(xpp.read_opts(ode_file))
 
+    def run(
+        self,
+        ics: pd.DataFrame | tp.Iterable | None = None,
+        **kwargs,
+    ) -> pd.DataFrame:
+        """Run XPP ODEs and wrap result in a Pandas dataframe."""
+        # Convert ics to vector format.
+        if ics is not None:
+            ics_vector = np.array(ics)
+        else:
+            ics_vector = ics
+        sol = xpp.run(self.ode_file, ics=ics_vector, **kwargs)
+        index = pd.Index(data=sol[:, 0], name="time")
+        return pd.DataFrame(sol[:, 1:], columns=self.state_vars, index=index)
 
-def par_run(xppfile: str, nrand: int = 5, **kwargs) -> List[pd.DataFrame]:
-    """Randomise ICs and integrate system multiple times."""
[…]

### 2022-03-05 src/poincare_map/paths.py

@@ -1,0 +1,14 @@
+from pathlib import Path
+
+# Directories
+data = Path("data")
+figures = Path("figures")
+odes = Path("odes")
+
+data.mkdir(exist_ok=True)
+figures.mkdir(exist_ok=True)
+odes.mkdir(exist_ok=True)
+
+# Data files
+numeric_bif_diagram = data / "numeric-bif-diagram.parquet"
+analytic_bif_diagram = data / "analytic-bif-diagram.parquet"

### 2022-03-05 src/poincare_map/plots.py

@@ -1,0 +1,261 @@
+"""Functions to build figures."""
+
+#%% Initialise
+import os
+import pickle
+import pandas as pd
+
+import matplotlib
+# NOTE: Maybe plot directly as pgf and import?
+# matplotlib.use('pgf')
+from matplotlib import patches
+from matplotlib.figure import Figure
+from matplotlib import pyplot as plt
+from matplotlib.gridspec import GridSpec
+from matplotlib.lines import Line2D
+
+import string
+import numpy as np
+
+import pyxpp.pyxpp as xpp
+from poincare_map.poincare_map import PoincareMap
+from poincare_map import ode
+from poincare_map import paths
+
+# plt.ioff()
+
+xppfile = "odes/mlml.ode"
+model = PoincareMap.from_ode(xppfile)
+
+
+FIGWIDTH = 3.85
+FIGSIZE = (FIGWIDTH, FIGWIDTH)
+FIG2by1 = (FIGWIDTH*1.4, (FIGWIDTH*1.4)/2)
+
+#%% Plotting
+
+# TODO: Add patches
+def free_quiet() -> Figure:
+    """Illustration of free and quiet phases  with voltage and synpase 
+    variables."""
+    # Compute 3-3 solution.
+    TRANSIENT = 3000
+    TOTAL = 12000
+    G = 0.5
+    N = 2
+    sol = ode.run(xppfile, transient=3000, total=10000, g=G)
+    lc = ode.find_lc(sol, norm=True)
+
+    period = lc.t.iloc[-1]
+    idxs, _ = ode.spikes(lc)
+    # Append last point to first to make it look nice.
+    idxs = np.concatenate((idxs, [-1]))
+
+    fig, axs = plt.subplots(nrows=3, tight_layout=True, sharex=True,
+                            figsize=(FIGWIDTH, FIGWIDTH*1.7))
+
+    # A: Plot voltage trace.
+    ax = axs[0]
+    ax.plot(lc.t, lc.v1)
+    ax.plot(lc.t, lc.v2)
+    ax.set_ylim((-80, 140))
+    ax.set_ylabel(r'$v_{1,2}$')
+
+    # # Add arrows between ds.
+    # OFFSET = 16
+    # v0 = max(lc.v1)
+    # for idx0, idx1 in zip(idxs, idxs[1:]):
+    #     t0 = lc.t.iloc[idx0]
+    #     t1 = lc.t.iloc[idx1]
[…]

### 2022-03-05 src/poincare_map/poincare_map.py

@@ -1,0 +1,209 @@
+"""Poincare map definition with methods.
+
+Module containing the most important model parameters and derived
+quantities and functions.
+"""
+from __future__ import annotations
+
+from typing import NamedTuple, Tuple
+
+import numpy as np
+import pandas as pd
+from pynverse import inversefunc
+from scipy import optimize
+
+# Ignore divide-by-zero errors that can occur for minisation for extreme values.
+# np.seterr(divide='ignore')
+
+
+class PoincareMap(NamedTuple):
+    """Model for map computation."""
+
+    n: int
+
+    # These parameters should be read from ODE file.
+    tauk: float = 100
+    taua: float = 1000
+    taub: float = 100
+
+    # These are derived.
+    gstar: float = 0.0068
+    T: float = 376  # Spiking period.
+    Tact: float = 49
+    Tinact: float = 327
+
+    @property
+    def Lambda(self):
+        """Depression speed."""
+        return np.exp(-self.Tact / self.taub)
+
+    @property
+    def Rho(self):
+        """Depression recovery speed."""
+        return np.exp(-self.Tinact / self.taua)
+
+    @property
+    def dsup(self):
+        """Value of d for suppressed solution."""
+        return (1 - self.Rho) / (1 - self.Lambda * self.Rho)
+
+    @property
+    def gsup(self):
+        """Minimum value of g for suppressed solution."""
+        return (self.gstar / self.Lambda) * (
+            np.exp(self.Tinact / self.tauk) / self.dsup
+        )
+
+    @property
+    def tau(self):
+        """Overall time constant."""
+        return 2 * self.tauk / self.taua
+
+    @property
+    def alpha(self) -> float:
+        return pow(self.Lambda * self.Rho, self.n - 1)
+
+    @property
+    def beta(self) -> float:
+        return (1 - self.Rho) * sum(
+            [pow(self.Lambda * self.Rho, k) for k in range(int(self.n - 1))]
+        )
+
+    def delta(self, d: float) -> float:
+        """Solution to d-map after n spikes, which is the value of depression
+        variable at nth spike time."""
+        return self.alpha * d + self.beta
+
+    def d_asymptote(self) -> float:
+        """Leftmost bound of P-map domain."""
+        return -self.beta / self.alpha
+
+    def F_map(self, d: float, g: float) -> float:
+        """Free phase map F."""
+        return self.tauk * np.log(
[…]

### 2022-03-05 tex/manuscript.tex
Edit introdu nullcline description

@@
 \usepackage{physics}
+\usepackage{cases}
 \usepackage{bm}
-\usepackage{subfiles}
+% This should make nicer typesetting and lead to feaver underfull/overfull box errors
+\usepackage{microtype}
 
@@
 \usepackage{lineno}
+
+% Define terms for "free"/"quiet"
+\newcommand{\free}{free}
+\newcommand{\quiet}{suppressed}
 
@@
 \def\firstAuthorLast{Olenik {et~al.}} %use et al only if is more than 1 author
-\def\Authors{Mark Olenik\,$^{1,*}$, and Conor Houghton\,$^{2}$}
-% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
-% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
-\def\Address{$^{1}$School of Biological Sciences, Faculty of Life Sciences, University of Bristol, Bristol, United Kingdom \\
-$^{2}$School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, Faculty of Engineering, University of Bristol, Bristol, United Kingdom}
-% The Corresponding Author should be marked with an asterisk
-% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
+\def\Authors{Mark Olenik\,\(^{1,*}\), and Conor Houghton\,\(^{2}\)}
+\def\Address{\(^{1}\)School of Biological Sciences, Faculty of Life Sciences, University of Bristol, Bristol, United Kingdom \\
+\(^{2}\)School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, Faculty of Engineering, University of Bristol, Bristol, United Kingdom}
 \def\corrAuthor{Mark Olenik}
@@
 \extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
-%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
 
@@
   \section{}
-  Short-term synaptic plasticity is found in many areas of the central nervous system.  In
-  the inhibitory half-centre central pattern generators involved in locomotion, synaptic
-  depression is believed to act as a burst termination mechanism, allowing networks to
-  generate anti-phase bursting patterns of varying periods.  To better understand burst
-  generation in these central patter generators, we study a minimal network of two neurons
-  coupled through depressing synapses.  Depending on the strength of the synaptic
-  conductance between the two neurons, this network can produce symmetric $n-n$ anti-phase
-  bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions
-  increasing with the strength of the synaptic conductance.  Relying on the timescale
-  disparity in the model, we reduce the eight-dimensional network equations to a
-  fully-explicit scalar Poincaré burst map.  This map tracks the state of synaptic
-  depression from one burst to the next and captures the complex bursting dynamics of the
-  network.  Fixed points of this map are associated with stable burst solutions of the
-  full network model, and are created through fold bifurcations of maps.  We derive
-  conditions that describe period-increment bifurcations between stable $n-n$ and
-  $(n+1)-(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
-  Predictions of the Poincaré map fit excellently with numerical simulations of the full
-  network model and allow the study of parameter sensitivity for rhythm generation.
+  Short-term synaptic plasticity is found in many areas of the central nervous system.
+  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
+  To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
+  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric \(n-n\) anti-phase bursts, where neurons fire \(n\) spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
+  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
+  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
+  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
+  We derive conditions that describe period-increment bifurcations between stable \(n-n\) and \((n+1)-(n+1)\) bursts, producing a full bifurcation diagram of the burst cycle period.
+  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.
 
@@
 
-\section{Introduction}
-\section{Materials and Methods}
-\subfile{sections/methods.tex}
-
-\section{Results}
-\subfile{sections/results.tex}
-
-\section{Discussion}
-\subfile{sections/discussion.tex}
+\input{sections/introduction}
+\input{sections/methods}
+\input{sections/results}
+\input{sections/discussion}
 
 \section*{Conflict of Interest Statement}
-The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
+The authors declare that the research was conducted in the absence of any commercial or
+financial relationships that could be construed as a potential conflict of interest.
 
@@
 \section*{Funding}
-This work was supported by the Wellcome Trust Doctoral Training Programme in Neural Dynamics, Grant no. 099699/Z/12/Z.
+This work was supported by the Wellcome Trust Doctoral Training Programme in Neural
+Dynamics, Grant no. 099699/Z/12/Z.
 
@@
   \includegraphics{fig/nullclines-uncoupled.pdf}
-  \caption{Periodic solution of relaxation-oscillator model neuron.
-$\bm{\mathrm{(A)}}$ Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue, $v_\infty$) and $w$-nullcline (orange, $w_\infty$).
-Unstable fixed point $p_{f}$ is indicated by an orange dot.
-$\bm{\mathrm{(B)}}$ Corresponding voltage trace $v(t)$ of an action potential.~\label{fig:nullclines}}
+  \caption{Periodic solution of relaxation-oscillator model neuron. \(\bm{\mathrm{(A)}}\)
+    Projection of limit cycle onto (\(v,w\))-phase plane with \(v\)-nullcline (blue,
+    \(v_\infty\)) and \(w\)-nullcline (orange, \(w_\infty\)). Unstable fixed point \(p_{f}\)
+    is indicated by an orange dot. \(\bm{\mathrm{(B)}}\) Corresponding voltage trace
+    \(v(t)\) of an action potential.~\label{fig:nullclines}}
 \end{figure}
@@
   \includegraphics{fig/depression-traces.pdf}
-  \caption{Solution profiles of a $4-4$ burst.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange).
-$\bm{\mathrm{(B)}}$ Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell 1.~\label{fig:depression-traces}}
+  \caption{Solution profiles of a \(4-4\) burst. \(\bm{\mathrm{(A)}}\) Membrane potentials
+    of cell 1 (\(v_{1}\), blue), and cell 2 (\(v_{2}\), orange). \(\bm{\mathrm{(B)}}\)
+    Synaptic variables \(d_{1}\) (blue) and \(s_{1}\) (grey) of cell
+    1.~\label{fig:depression-traces}}
 \end{figure}
@@
   \includegraphics{fig/burst-sols.pdf}
-  \caption{Voltage traces of both cells of numerically stable solutions for increasing values of the coupling strength $\gbar$ (increasing top to bottom).~\label{fig:burst-sols}}
+  \caption{Voltage traces of both cells of numerically stable solutions for increasing
+    values of the coupling strength \(\gbar\) (increasing top to
+    bottom).~\label{fig:burst-sols}}
 \end{figure}
@@
   \includegraphics{fig/bif-diagram.pdf}
-  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for increasing coupling strength $\gbar$.
-$\bm{\mathrm{(A)}}$ Period of stable solutions.
-Dashed lines show the interval between the $5-5$ and the suppressed solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals of $\gbar$.
-$\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in $\mathrm{(A)}$.
-Long $ISI$s are associated with the quiet phase of a burst, short $ISI$s with the free phase.
-During the free phase, $ISI$s are of approximately constant duration $T$.\label{fig:bif-diagram}}
+  \caption{Numerically computed bifurcation diagrams of stable \(n-n\) solutions for
+    increasing coupling strength \(\gbar\). \(\bm{\mathrm{(A)}}\) Period of stable
+    solutions. Dashed lines show the interval between the \(5-5\) and the suppressed
+    solutions, where higher period \(n-n\) solutions occur on increasingly smaller intervals
+    of \(\gbar\). \(\bm{\mathrm{(B)}}\) \(ISI\)s corresponding to \(n-n\) solutions in
+    \(\mathrm{(A)}\). Long \(ISI\)s are associated with the quiet phase of a burst, short
+    \(ISI\)s with the free phase. During the free phase, \(ISI\)s are of approximately
+    constant duration \(T\).\label{fig:bif-diagram}}
 \end{figure}
@@
   \includegraphics{fig/nullclines-coupled.pdf}
-  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar s$.
-For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange point).
-Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until $p_{f}$ changes stability (half orange,  half blue point) at some critical total conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
+  \caption{Nullclines \(v_{\infty}\) (blue) and \(w_{\infty}\) (orange) in the
+  \((v,w\))-phase plane for different values of the total synaptic conductance \(\gbar
+  s\). For small \(\gbar s < g^{\star}\), fixed point \(p_{f}\) is unstable (orange
+  point). Larger values \(\gbar s\) move \(v_{\infty}\) down in the \((v,w)\)-plane until
+  \(p_{f}\) changes stability (half orange,  half blue point) at some critical total
+  conductance value \(\gbar s = g^{\star}\), and becomes stable (blue point) for
+  \(\gbar>g^{\star}\).~\label{fig:nullclines-coupled}}
 \end{figure}
@@
   \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
-  \caption{Numerically computed values of the release delay for varying $\gbar$.
-Each of the three branches (A, B, C) also shows the timecourse of the total synaptic conductance $\gbar s$ of a sample stable solution of both cells (blue and orange), as well as the release conductance $g^{\star}$ (dashed green line).
-$\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution.
-Here the quiet cell only spikes after a significant release delay.
-$\bm{\mathrm{(B)}}$ Branch with a long release delay associated with a subset of $2-2$ solutions.
-Here the release condition is briefly satisfied after the first spike of cell 1.
-This does not cause firing of cell 2, which only occurs after the second spike of cell 1.
-$\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is approximately zero and the release condition is sufficient for firing of cell 2.
+  \caption{Numerically computed values of the release delay for varying \(\gbar\). Each of
+    the three branches (A, B, C) also shows the timecourse of the total synaptic
+    conductance \(\gbar s\) of a sample stable solution of both cells (blue and orange),
+    as well as the release conductance \(g^{\star}\) (dashed green line).
+    \(\bm{\mathrm{(A)}}\) Branch corresponding to the \(1-1\) solution. Here the quiet
+    cell only spikes after a significant release delay. \(\bm{\mathrm{(B)}}\) Branch with
+    a long release delay associated with a subset of \(2-2\) solutions. Here the release
+    condition is briefly satisfied after the first spike of cell 1. This does not cause
+    firing of cell 2, which only occurs after the second spike of cell 1.
+    \(\bm{\mathrm{(C)}}\) Branch with \(n-n\) solutions  where release delay is
+    approximately zero and the release condition is sufficient for firing of cell 2.
     ~\label{fig:release-delay}}
@@
   \includegraphics{fig/free-quiet.pdf}
-  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
-The grey patches depict inter-burst-intervals $\delt$.
-$\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$.
-$\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
+  \caption{Schematic diagram of the free and quiet phases for a \(3-3\) solution.
+    \(\bm{\mathrm{(A)}}\) Membrane potentials of cell 1 (\(v_{1}\)) and cell 2 (\(v_{2}\)).
+    The grey patches depict inter-burst-intervals \(\delt\). \(\bm{\mathrm{(B)}}\) Total
+    synaptic conductance of cell 1 (\(\gbar s_1\)) as it crosses the release conductance
+    \(g^{\star}\). \(\bm{\mathrm{(C)}}\) Solution \(d_1(t)\) of depression variable of cell
+    1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
 \end{figure}
@@
   \includegraphics{fig/delta-t.pdf}
-  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
-Each continuous branch is associated with a stable $n-n$ burst solution.
-Increasing $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx T$.~\label{fig:delta-t}}
+  \caption{Numerically computed bifurcation diagram of \(\delt\) for varying \(\gbar\).
+    Each continuous branch is associated with a stable \(n-n\) burst solution. Increasing
+    \(\gbar\) increases \(\Delta t\) until the solutions bifurcate at \(\Delta t\approx
+    T\).~\label{fig:delta-t}}
 \end{figure}
@@
   \includegraphics{fig/FQ-map.pdf}
-  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$.
-Curves $F_n$ intersect at $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
+  \caption{Maps \(F_n\) \(\bm{\mathrm{(A)}}\) and \(Q_n\) \(\bm{\mathrm{(B)}}\) for
+  \(\gbar=0.6\) \(\si{mS/cm^{2}}\) and \(n=1,2,3,4\). Curves \(F_n\) intersect at
+  \(d_{s}\) which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
 \end{figure}
@@
   \includegraphics{fig/Pn-map.pdf}
-  \caption{Map $\Pi_{n}:d^{\star}$.
-$\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$ at $\gbar=0.6$ $\si{mS/cm^{2}}$.
-$\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$.
-The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
+  \caption{Map \(\Pi_{n}:d^{\star}\). \(\bm{\mathrm{(A)}}\) \(\Pi_{n}\) for \(n=1,2,3,4\)
+  at \(\gbar=0.6\) \(\si{mS/cm^{2}}\). \(\bm{\mathrm{(B)}}\) \(\Pi_{2}\) with \(n=2\) for
+  varying \(\gbar \approx 0.01, 0.034, 0.3\) \(\si{mS/cm^{2}}\). The identity function is
+  illustrated by a diagonal line.~\label{fig:Pn-map}}
 \end{figure}
@@
   \includegraphics{fig/folds.pdf}
-  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves) and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
-$\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the corresponding solution period from numerical integration of the system of ODEs (orange).~\label{fig:folds}}
+  \caption{\(\bm{\mathrm{(A)}}\) Fold bifurcation diagrams of stable (continuous curves)
+    and unstable (dotted curves) fixed points of \(\Pi_{n}\) for varying \(n\).
+    \(\bm{\mathrm{(B)}}\) Cycle periods computed from stable fixed points (blue), and the
+    corresponding solution period from numerical integration of the system of ODEs
+    (orange).~\label{fig:folds}}
 \end{figure}
@@
   \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
-  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
+  \caption{Bifurcation diagrams of stable \(n-n\) solutions computed analytically from
+    fixed points of \(\Pi_n\) and plotted on the respective intervals of \(\gbar\in
+    \big[\gbar_+(n),\gbar_-(n)\big]\) (blue), and computed from numerical integrations of
+    the ODEs (orange).~\label{fig:final-bif}}
 \end{figure}
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2022-03-05 tex/sections/discussion.tex
Edit introdu nullcline description

@@
-\documentclass[../manuscript.tex]{subfiles}
-\graphicspath{{../figures/}}
-
-\begin{document}
-
+\section{Discussion}
 % PROBLEM SUMMARY
-Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming~\citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
+Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming \citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
 In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
@@
 To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression.
-When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n-n$ burst patterns.
-Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
-This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n-n$ solutions respectively.
-Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons.
-Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n-n$ burst solutions of the full two-cell system of ODEs.
+When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different \(n-n\) burst patterns.
+Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map \(\Pi_n\) of the slow depression variable \(d\).
+This map \(\Pi_n\) is a composition of two maps, \(F_n\) and \(Q_n\), that model the evolution of the depression during the free and quiet phases of \(n-n\) solutions respectively.
+Both \(F_n\) and \(Q_n\) maps are constructed by using the dynamics of single uncoupled neurons.
+Fixed points of \(\Pi_n\) are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable \(n-n\) burst solutions of the full two-cell system of ODEs.
 The results from our one-dimensional map match excellently with numerical simulation of the full network.
@@
 % FURTHER METHOD IDEAS
-We have studied $n-n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
-However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes.
-It is conceivable that our map construction can be extended to also capture such $m-n$ solutions.
-Remember, in the case of symmetrical coupling with $n-n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
-To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other.
-To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$.
+We have studied \(n-n\) solutions assuming that the synaptic coupling \(\gbar \) between the two cells is symmetrical.
+However,~\citet{bose2011} have shown that asymmetrical coupling \((\gbar_1, \gbar_2)\) can result in network solutions of type \(m-n\), where one cell fires \(m\) spikes, while the other \(n\) spikes.
+It is conceivable that our map construction can be extended to also capture such \(m-n\) solutions.
+Remember, in the case of symmetrical coupling with \(n-n\) solutions, the timecourse of the depression variables \(d_{1}\) and \(d_{2}\) were in anti-phase, and it was therefore sufficient to track only one of the two variables.
+To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type \(m-n\), where the solutions of the depression variables \(d_1\) and \(d_2\) are not simply time-shifted versions of each other.
+To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map \(\Pi(d_1,d_2)\).
 While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}.
@@
 As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses.
-In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.
+In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g.
+see][]{kuehn2015}.
 
 In tadpoles, struggling is believed to be initiated by an increase in the firing frequency of reciprocally inhibitory commisural interneurons, which has been hypothesised to lead to stronger synaptic depression of inhibition and result in the iconic anti-phase bursting \citep{li2007}.
-It would therefore be interesting to study how varying the cell intrinsic firing period $T$ could affect the network rhythm.
-While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying $T$.
-Recall that $T$ is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters.
+It would therefore be interesting to study how varying the cell intrinsic firing period \(T\) could affect the network rhythm.
+While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying \(T\).
+Recall that \(T\) is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters.
 This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult.
-A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting in this scenario.
+A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying \(T\) independently of other model parameters, and could be more fitting in this scenario.
 
 % LIMITATION: SPIKE MAP
-Our simulations of the network showed that $n-n$ solutions lose robustness as their period is increased.
+Our simulations of the network showed that \(n-n\) solutions lose robustness as their period is increased.
 That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
-We were able to replicate this finding by numerically finding the respective left and right borders of stable $n-n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
-We have also noted the resemblance of our bifurcation diagram to one where such $n-n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
+We were able to replicate this finding by numerically finding the respective left and right borders of stable \(n-n\) branches of fixed points of \(\Pi_n\), and showing that the distance between these borders shrinks with \(n\).
+We have also noted the resemblance of our bifurcation diagram to one where such \(n-n\) branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
 It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}.
@@
 The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
-In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations.
+In contrast, we rely on \(n\) different maps \(\Pi_n\) to describe the burst dynamics without explicitly capturing the period increment bifurcations.
 It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
@@
 % FLOW SYSTEM BIFURCATION
-In addition to stable $n-n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n-n$ solutions.
+In addition to stable \(n-n\) solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable \(n-n\) solutions.
 While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.
@@
 Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.
-
-\end{document}

### 2022-03-05 tex/sections/introduction.tex
Edit introdu nullcline description

@@
-\documentclass[../manuscript.tex]{subfiles}
-\graphicspath{{../figures/}}
-
-\begin{document}
+\section{Introduction}
 % DEPRESSION
@@
 synaptic conductance between the two neurons is varied, the network produces symmetric
-$n-n$ anti-phase bursts, with stronger synaptic coupling leading to longer bursts.  They
+\(n-n\) anti-phase bursts, with stronger synaptic coupling leading to longer bursts.  They
 used methods from geometric singular perturbation theory to separate the timescales of the
 fast membrane, and the slow synaptic dynamics of the network to derive one-dimensional
-conditions necessary for the existence of stable $n-n$ solutions (for $n\leq 2$).
+conditions necessary for the existence of stable \(n-n\) solutions (for \(n\leq 2\)).
 According to these conditions the type of firing pattern largely depends on the slow
@@
 Thus, the scalar conditions derived in~\citet{bose2011} provide a method to numerically
-identify the type of stable $n-n$ pattern for any given value of the coupling strength.
+identify the type of stable \(n-n\) pattern for any given value of the coupling strength.
 However, they do not predict the exact period of such solutions.  Furthermore, while they
@@
 Here we extend the previous analysis by providing a Poincaré map of the slow depression
-dynamics.  This allows us not only to predict the types of stable $n-n$ solutions the full
-network can produce, (for any $n$), but also to study how varying the coupling strength
+dynamics.  This allows us not only to predict the types of stable \(n-n\) solutions the full
+network can produce, (for any \(n\)), but also to study how varying the coupling strength
 affects the period of such solutions.  To do this, we build on, and numerically test, the
@@
 the beginning of one burst to the beginning of the next burst.  Stable fixed points of our
-map are associated with stable $n-n$ burst solutions.  Our map construction is motivated
+map are associated with stable \(n-n\) burst solutions.  Our map construction is motivated
 by the burst length map of a T-type calcium current, utilised by~\citet{matveev2007},
@@
 full two-cell ODE system: Given the strength of maximum conductance between the two
-neurons, fixed points of our map predict the type and period of $n-n$ patterns, the switch
+neurons, fixed points of our map predict the type and period of \(n-n\) patterns, the switch
 between burst solutions of different periods, as well as the occurrence of co-existent
@@
 algebraic conditions that predict the period increment bifurcations that allow the switch
-between $n-n$ and $(n+1)-(n+1)$ solutions.  Because our map is fully explicit, it lays the
+between \(n-n\) and \((n+1)-(n+1)\) solutions.  Because our map is fully explicit, it lays the
 framework for studying the effects of other model parameter on network dynamics without
@@
 depression variable as well as the conditions that are required for stable solutions to
-bifurcate between $n-n$ and $(n+1)-(n+1)$ solutions.  We end this work with a discussion.
-
-\end{document}
+bifurcate between \(n-n\) and \((n+1)-(n+1)\) solutions.  We end this work with a discussion.

### 2022-03-05 tex/sections/methods.tex
Edit introdu nullcline description

@@
-\documentclass[../manuscript.tex]{subfiles}
-\graphicspath{{../figures/}}
-
-\begin{document}
-We consider a pair of identical Morris-Lecar neurons~\citep{morris1981}, with parameters
-adapted from~\cite{bose2011}.  The Morris-Lecar model is a set of two first-order
-differential equations that describe the membrane dynamics of a spiking neuron.  The
-depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation
-by a slow potassium current and a leak current.  The membrane potential $v_{i}$ and
-potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
-\begin{align}
-  ~\label{eq:cell-modelA}
+\section{Materials and Methods}
+We consider a pair of identical Morris-Lecar neurons \citep{morris1981}, with parameters adapted from \cite{bose2011}.
+The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
+The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
+The membrane potential \(v_{i}\) and potassium activation \(w_{i}\) of neuron \(i\) (\(i, j=1,2\)) is described by: \begin{align}
+	\label{eq:cell-modelA}
 	\dot v_{i} & = f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}), \\
-  ~\label{eq:cell-modelB}
+	\label{eq:cell-modelB}
 	\dot w_{i} & =h(v_i,w_i).
 \end{align}
-Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal
-synaptic conductance and the synaptic gating, respectively, constituting the total
-inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.  Function $f(v_{i},
-w_{i})$ describes the membrane currents of a single cell:
+Here \(v_{s}\) is the inhibitory reversal potential, and \(\gbar\) and \(s_{j}\) are the
+maximal synaptic conductance and the synaptic gating, respectively, constituting the total
+inhibitory conductance \(\gbar s_{j}\) from neuron \(j\) to neuron \(i\).  Function
+\(f(v_{i}, w_{i})\) describes the membrane currents of a single cell:
 \begin{equation}
-  ~\label{eq:memcur}
-  f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})-g_{\leak}(v_{i}-v_{\leak}) + I.
+	\label{eq:memcur}
+	f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})
+	-g_{\leak}(v_{i}-v_{\leak}) + I.
 \end{equation}
-The currents include a constant current $I$, and three ionic currents: an instantaneous
+The currents include a constant current \(I\), and three ionic currents: an instantaneous
 calcium current, a potassium current, and a leak current, with respective reversal
-potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances
-$g_{\ca}$, $g_{\k}$, and $g_{\leak}$.  The function $h(v_{i}, w_{i})$ models the kinetics
-of the potassium gating variable $w_{i}$, and is given by
+potentials \(v_{\ca}\), \(v_{\k}\), and \(v_{\leak}\), as well as maximum conductances
+\(g_{\ca}\), \(g_{\k}\), and \(g_{\leak}\).  The function \(h(v_{i}, w_{i})\) models the
+kinetics of the potassium gating variable \(w_{i}\), and is given by
 \begin{equation}
@@
 \end{equation}
-The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default
+The steady-state activation functions \(m_{\infty}\) and \(w_{\infty}\) as well as the default
 model parameters are described in the \textbf{Supplementary Material S1}.
@@
 The dynamics of the synaptic interactions between the neurons are governed by a synaptic
-gating variable $s_{i}$ and a depression variable $d_{i}$:
-\begin{linenomath}
-  \begin{align}
-    \dot d_{i} & =
-    \begin{cases}
-      (1-d_{i})/\tau_a\text{ if }v_i<v_\theta, \\
-      -d_{i}/\tau_b\text{ if }v_i>v_\theta,
-    \end{cases}\label{eq:dot-d} \\
-    \dot s_{i} & =
-    \begin{cases}
-      -s_i/\tau_\kappa\text{ if }v_i<v_\theta, \\
-      (d_i-s_i)/\tau_\gamma\text{ if }v_i>v_\theta.
-    \end{cases}\label{eq:dot-s}
-  \end{align}
-\end{linenomath}
-Variable $d_{i}$ describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
+gating variable \(s_{i}\) and a depression variable \(d_{i}\):
+\begin{numcases}{\dot d_{i} = }
+	(1-d_{i})/\tau_{a} & \text{ if }v_{i}<v_{\theta},\label{eq:dot-d-up}
+	\\
+	-d_{i}/\tau_{b}    & \text{ if }v_{i}>v_{\theta},\label{eq:dot-d-down}
+\end{numcases}
+
+\begin{numcases}{\dot s_{i} = }
+	-s_{i} / \tau_\kappa & \text{ if }v_{i}<v_{\theta},\label{eq:dot-s-down}
+	\\
+	0                & \text{ if }v_{i}>v_{\theta.}\label{eq:dot-s-up}
+\end{numcases}
+
+% TODO: Needs EDITING
+Variable \(d_{i}\) describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
 The model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
-When the voltage is below firing threshold, depression variable $d_i$ recovers with time constant $\tau_a$, while synaptic variable $s_i$ decays with time constant $\tau_\kappa$.
-% TODO Maybe mention that this topic will be discussed in the appendix or later.
-Because synaptic depression occurs on a much slower timescale than synaptic inhibition, we assume $\tau_d\gg\tau_\kappa$.
-When the voltage is above firing threshold, variable $d_i$ decays to zero with $\tau_b$, while $s_i$ quickly approaches the respective value of $d_i$.
-Since $\tau_\gamma$ is the shortest time constant of the system with $\tau_\gamma \ll 1$, we can assume that whenever $v>v_\theta$ we can we have $s_i=d_i$.
-The equations for the depression model were adapted from the~\citet{bose2001} model.
-These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by~\citet{tsodyks1997}.
+When the voltage of cell \(i\) is above firing threshold (\(v_i>v_\theta\)), variable \(d_i\) decays with time constant \(\tau_b\), and recovers with time constant \(\tau_a\) when voltage is below firing threshold (\(v_i < v_\theta\)).
+Since the synaptic inhibition occurs on a much faster timescale than synaptic depression, we assume that \(s_i\) is instantaneously reset to \(d_i\) whenever \(v_i\) increases above \(v_\theta\), where it remains throughout \(v_i > v_\theta\).
+Whenever \(v_i < v_\theta\), the synaptic variable decays exponentially with time constant \(\tau_\kappa\).
+The equations for the depression model were adapted from the \citet{bose2001} model.
+These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by \citet{tsodyks1997}.
 
-When the cells are uncoupled ($\gbar=0$), the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
-The two curves intersect along the middle branch of $v_{\infty}$, creating an unstable fixed point $p_{f}=(v_{f},w_{f})$ with a surrounding stable limit cycle of period $T=T_{act}+T_{inact}$ (\cref{fig:nullclines}A).
-Here $T_{act}$ is the amount of time the cell spends in the active state when $v>v_\theta$, while $T_{inact}$ is the time it spends in the silent state when $v<v_\theta$.
+When the cells are uncoupled (\(\gbar=0\)), the membrane dynamics are determined by the cubic \(v\)-nullcline \(v_{\infty}(v_i)\) and the sigmoid \(w\)-nullcline \(w_{\infty}(v_{i})\), satisfying \(\dot v_{i}=0\) and \(\dot w_{i}=0\), respectively.
+The two curves intersect along the middle branch of \(v_{\infty}\), creating an unstable fixed point with a surrounding stable limit cycle of period \(T=T_{act}+T_{inact}\) (\cref{fig:nullclines}A).
+Here \(T_{act}\) is the amount of time the cell spends in the active state when \(v>v_\theta\), while \(T_{inact}\) is the time it spends in the silent state when \(v<v_\theta\).
 Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
 The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
-During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
-Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
+During the silent phase the trajectory evolves along the left branch (\(v_{i}<v_{\theta}\)) of the cubic \(v\)-nullcline.
+Once the trajectory reaches the local minimum of \(v_{\infty}\), it ``jumps up'' to the right branch (\(v_{i}>v_{\theta}\)), crossing the firing threshold \(v_{\theta}\).
 During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
@@
 The following mathematical analysis is performed on the equations of a single cell.
-Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
-
-\end{document}
+Unless required for clarity, we will therefore omit the subscripts \(i,j\) from here on.

### 2022-03-05 tex/sections/results.tex
Edit introdu nullcline description

@@
-\documentclass[../manuscript.tex]{subfiles}
-\graphicspath{{../figures/}}
-
-\begin{document}
-
+\section{Results}
 \subsection{Anti-phase burst solutions}
-Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism~\citep{brown1911} and is known to produce $n-n$ anti-phase burst solutions of varying period.
-Such $n-n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
-\Cref{fig:depression-traces}A shows the timecourse of a typical $4-4$ burst.
+Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism \citep{brown1911} and is known to produce \(n-n\) anti-phase burst solutions of varying period.
+Such \(n-n\) solutions consist of cells firing bursts of \(n\) spikes in alternation.
+\Cref{fig:depression-traces}A shows the timecourse of a typical \(4-4\) burst.
 While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
+% FIXME: This isn't consistent with Bose, that needs to be mentioned
 Therefore, at any given moment one cell is spiking while the other is inhibited.
-Consistent with~\citet{bose2011} we will refer to the currently firing cell as ``free'' and we will call the inhibited cell ``quiet''.
-Additionally, we will distinguish between two phases of a $n-n$ solution:
-We will refer to the burst duration of a cell as the ``free phase'', which is the time between the first spike and the last spike in a burst.
-And we will call the remaining duration of a cycle, when a cell is not spiking, the ``quiet phase''.
+Consistent with \citet{bose2011} we will refer to the currently firing cell as ``\free{}'' and we will call the inhibited cell ``\quiet{}''.
+Additionally, we will distinguish between two phases of a \(n-n\) solution:
+We will refer to the time interval when a cell is firing as the ``\free{} phase'', and we will call the remaining duration of a cycle, when a cell is not firing, the ``\quiet{}  phase''.
 
 % TODO: Add mention of gstar. Once critical conductance is crossed, cell is released.
-With each action potential of the free cell, short-term depression leads to a step-wise decrease of $d$, and consequently of $s$ (\cref{fig:depression-traces}B).
-If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\gbar s$ will eventually become sufficiently small to allow for the quiet cell to be released and start firing, thus inhibiting the previously free cell.
-While a cell is quiet its depression variable can recover.
-Once the quiet cell becomes free again its synaptic inhibition will be sufficient to terminate the burst of the previously free cell and commence a new cycle.
-As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\gbar$ determines the type of $n-n$ solution.
-Increasing $\gbar$ produces higher $n-n$ burst solutions with more spikes per burst and a longer cycle period.
-\Cref{fig:burst-sols} shows numerically stable $n-n$ solutions for varying values of $\gbar$.
-For small values of $\gbar$ the network produces anti-phase spiking $1-1$ solutions.
-As $\gbar$ is increased the network generates solutions of increasing $n$, that is $2-2$, $3-3$, and $4-4$.
-When $\gbar$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
+With each action potential of the \free{} cell, short-term depression leads to a step-wise decrease of \(d\), and consequently of \(s\) (\cref{fig:depression-traces}B).
+If \(d\) depresses faster at spike time than it can recover in the inter-spike-intervals (\(ISI\)s), the total synaptic conductance \(\bar g s\) will eventually become sufficiently small to allow for the \quiet{} cell to be released and start firing, thus inhibiting the previously \free{} cell.
+While a cell is \quiet{} its depression variable can recover.
+Once the \quiet{} cell becomes \free{} again its synaptic inhibition will be sufficient to terminate the burst of the previously \free{} cell and commence a new cycle.
+% BUG: This is not 100% true, gbar AND the initial conditions uniquely determine the type of n-n pattern.
+As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength \(\bar g\) determines the type of \(n-n\) solution.
+Increasing \(\bar g\) produces higher \(n-n\) burst solutions with more spikes per burst and a longer cycle period.
+\Cref{fig:burst-sols} shows numerically stable \(n-n\) solutions for varying values of \(\bar g\).
+For small values of \(\bar g\) the network produces anti-phase spiking \(1-1\) solutions.
+As \(\bar g\) is increased the network generates solutions of increasing \(n\), that is \(2-2\), \(3-3\), and \(4-4\).
+When \(\bar g\) is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period \(T\) while the other cell remains fully suppressed.
 Depending on the initial conditions either of the two cells can become the suppressed cell, which is why the suppressed solution is numerically bistable.
 
-Branches of numerically stable $n-n$ solutions and their associated limit cycle period for varying values of $\gbar$ are depicted in \cref{fig:bif-diagram}A (see  \textbf{Supplementary Material S2} for algorithm description).
-Not only do higher $n-n$ solutions branches require stronger coupling $\gbar$, but also within $n-n$ branches the period increases with $\gbar$.
-In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2-2$ and $3-3$ solution branches.
-Branches of higher $n-n$ burst solutions occur on increasingly smaller intervals of $\gbar$, for instance is the $\gbar$ interval of the $5-5$ branch shorter than that of the $4-4$ branch and so on.
-The interval between the $5-5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n-n$ solutions, such as $11-11$ bursts, but also other non-symmetric $n-m$ solutions as well irregular, non-periodic solutions.
-However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n-n$ solutions.
+Branches of numerically stable \(n-n\) solutions and their associated limit cycle period for varying values of \(\bar g\) are depicted in \cref{fig:bif-diagram}A (see \textbf{Supplementary Material S2} for algorithm description).
+Not only do higher \(n-n\) solutions branches require stronger coupling \(\bar g\), but also within \(n-n\) branches the period increases with \(\bar g\).
+In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the \(2-2\) and \(3-3\) solution branches.
+Branches of higher \(n-n\) burst solutions occur on increasingly smaller intervals of \(\bar g\), for instance is the \(\bar g\) interval of the \(5-5\) branch shorter than that of the \(4-4\) branch and so on.
+The interval between the \(5-5\) branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable \(n-n\) solutions, such as \(11-11\) bursts, but also other non-symmetric \(n-m\) solutions as well irregular, non-periodic solutions.
+However, the analysis in the following sections will only be concerned with the numerically stable and symmetric \(n-n\) solutions.
 
 \subsection{Mathematical analysis of two-cell network}
-~\label{sec:assumptions}
+\label{sec:assumptions}
 % Summary of assumptions
-The goal of the following mathematical analysis is to reduce the complexity of the eight-dimensional system to some easily tractable quantity.
-As we will see later this quantity is the value of the depression variable $d$ of either of the two cells.
-We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the free phase, and then during the quiet phase.
+The goal of the following mathematical analysis is to reduce the complexity of the
+eight-dimensional system to some easily tractable quantity.
+As we will see later this quantity is the value of the depression variable \(d\) of either of the two cells.
+We will construct the solution of \(d\) in a piecewise manner from one spike to the next, first during the \free{} phase, and then during the \quiet{} phase.
 This construction will require two assumptions about the membrane and synaptic dynamics.
-The first assumption states that during a burst the free cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
-The second assumption states that once the inhibitory conductance acting on the quiet cell drops below a critical threshold, the cell is immediately released and fires.
-The second assumption is necessary to predict the release time of the quiet cell, which allows us to model the recovery of $d$ during the quiet phase.
-In other words, the second assumption requires that the release of the quiet cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the quiet cell.
+The first assumption states that during a burst the \free{} cell fires at its uncoupled period \(T\), which simplifies the construction of the solution of \(d\).
+The second assumption states that once the inhibitory conductance acting on the \quiet{} cell drops below a critical threshold, the cell is immediately released and fires.
+The second assumption is necessary to predict the release time of the \quiet{} cell, which allows us to model the recovery of \(d\) during the \quiet{} phase.
+In other words, the second assumption requires that the release of the \quiet{} cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the \quiet{} cell.
 Both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
-Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n-n$ solutions.
-However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.
+Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different \(n-n\) solutions.
+However here we will use these assumptions to construct a Poincaré map of \(d\), which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.
 
 % Assumption 1: Free phase
-Our first assumption about the model states that the free cell fires at its uncoupled period $T$, that is, during the free phase of a burst we have $ISI=T$.
-Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
-We can further numerically confirm this observation by capturing the $ISI$s of the stable solutions from the bifurcation diagram in \cref{fig:bif-diagram}A.
-In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the quiet phase of the burst.
-$IBI$s lie on multiple branches, each branch associated with a stable $n-n$ solution, and are monotonically increasing with $\gbar$.
-In contrast, $ISI$s are calculated from the spikes within the free phase and do not vary significantly with $\gbar$, but are approximately $ISI\approx T$, affirming our first assumption.
-Assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the free phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
-Assuming $ISI=T$ seems reasonable given that inhibition acting on the quiet cell decays exponentially to zero on a much shorter timescale than the duration of the $ISI$, and therefore, once the quiet cell is released its trajectory quickly approaches the spiking limit cycle.
+% FIXME: Probably good idea to remove IBI reference here (and in figure).
+Our first assumption about the model states that the \free{} cell fires at its uncoupled period \(T\), that is, during the \free{} phase of a burst we have \(ISI=T\).
+Solution profiles in \cref{fig:burst-sols} suggest that the \(ISI\)s are indeed approximately constant.
+We can further numerically confirm this observation by capturing the \(ISI\)s of the stable solutions from the bifurcation diagram in \cref{fig:bif-diagram}A.
+In addition to \(ISI\)s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals (\(IBI\)s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the \quiet{} phase of the burst.
+\(IBI\)s lie on multiple branches, each branch associated with a stable \(n-n\) solution, and are monotonically increasing with \(\bar g\).
+In contrast, \(ISI\)s are calculated from the spikes within the \free{} phase and do not vary significantly with \(\bar g\), but are approximately \(ISI\approx T\), affirming our first assumption.
+Assuming \(ISI=T\) allows us to ignore the non-linear membrane dynamics during the \free{} phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
+Assuming \(ISI=T\) seems reasonable given that inhibition acting on the \quiet{} cell decays exponentially to zero on a much shorter timescale than the duration of the \(ISI\), and therefore, once the \quiet{} cell is released its trajectory quickly approaches the spiking limit cycle.
 
 % Assumption 2: Release
-Our second assumption states that the quiet cell is released and spikes as soon as inhibition from the free cell drops below a constant threshold.
+Our second assumption states that the \quiet{} cell is released and spikes as soon as the total inhibitory conductance from the \free{} cell drops below a constant threshold.
 We will now define such a ``release condition'' by exploiting the discrepancy in timescales between the fast membrane dynamics, and the slower synaptic dynamics.
 Let us first consider the dynamics of a single Morris-Lecar neuron.
-We fix the synaptic variable that acts on the cell by setting $s=1$, which also makes the applied synaptic conductance $\gbar s$ constant.
-Recall from \cref{fig:nullclines}A that in case of a single uncoupled cell ($\gbar s=0$), the $v$- and $w$-nullclines intersect at some unstable fixed point $p_{f}=(v_{f},w_{f})$, while trajectories revolve around a stable spiking limit cycle.
-Increasing $\gbar s$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point $p_{f}$ down the sigmoid $w_{\infty}$ in the $(v-w)$-plane (\cref{fig:nullclines-coupled}).
-When $\gbar s$ is large enough, the fixed point $p_{f}$ becomes stable, attracting all previously periodic trajectories.
-There exists a unique value $\gbar s=g^{\star}$ when $p_{f}$ changes stability and the stable limit cycle vanishes.
-Thus, when a constant inhibitory conductance is applied, $\gbar s<g^{\star}$ acts as a necessary condition for a cell to spike.
-In contrast, when $\gbar s>g^{\star}$ inhibition is strong enough to prevent a cell from spiking~\citep{bose2011}.
+We fix the synaptic variable that acts on the cell by setting \(s=1\), which also makes the applied synaptic conductance \(\bar g s\) constant.
+Recall from \cref{fig:nullclines}A that in case of a single uncoupled cell (\(\bar g s=0\)), the \(v\)- and \(w\)-nullclines intersect at some unstable fixed point \(p_{f}=(v_{f},w_{f})\), while trajectories revolve around a stable spiking limit cycle.
+Increasing \(\bar g s\) moves the cubic \(v_{\infty}\) with the ensuing unstable fixed point \(p_{f}\) down the sigmoid \(w_{\infty}\) in the \((v-w)\)-plane (\cref{fig:nullclines-coupled}).
+When \(\bar g s\) is large enough, the fixed point \(p_{f}\) becomes stable, attracting all previously periodic trajectories.
+There exists a unique value \(\bar g s=g^{\star}\) when \(p_{f}\) changes stability and the stable limit cycle vanishes.
+Thus, when a constant inhibitory conductance is applied, \(\bar g s<g^{\star}\) acts as a necessary condition for a cell to spike.
+In contrast, when \(\bar g s>g^{\star}\) inhibition is strong enough to prevent a cell from spiking~\citep{bose2011}.
 
@@
 
-Now let us analyse the nullclines of the quiet cell when the two cells are coupled via synaptic inhibition with depression.
-Let $\gbar s$ here denote the total synaptic conductance which acts on the quiet cell and is produced by the free cell, and let $p_{f}$ be the fixed point associated with the quiet cell.
-At the start of the burst of the free cell we have $\gbar s > g^{\star}$ and $p_{f}$ is stable.
-When the free cell spikes, $\gbar s$ peaks (\cref{eq:s-reset}), and the $v$-nullcline with the ensuing stable $p_f$ move down the $w$-nullcline.
-Then in between spikes $\gbar s$ decays exponentially (\cref{eq:dot-s}) causing the $v$-nullcline and $p_{f}$ to move up the $w$-nullcline while attracting trajectories of the quiet cell.
-Once depression causes the synaptic conductance to become small enough to satisfy $\gbar s<g^{\star}$ and the quiet cell is released, fixed point $p_{f}$ becomes unstable allowing the quiet cell to fire.
-If the trajectory of the quiet cell remains sufficiently close to the stable $p_{f}$ at the time when it changes stability, then $\gbar s < g^{\star}$ acts as a release condition that is not only necessary, but also sufficient for firing of the quiet cell.
-In this case the release of the quiet cell occurs precisely when
+Now let us analyse the nullclines of the \quiet{} cell when the two cells are coupled via synaptic inhibition with depression.
+Let \(\bar g s\) here denote the total synaptic conductance which acts on the \quiet{} cell and is produced by the \free{} cell, and let \(p_{f}\) be the fixed point associated with the \quiet{} cell.
+At the start of the burst of the \free{} cell we have \(\bar g s > g^{\star}\) and \(p_{f}\) is stable.
+When the \free{} cell spikes, \(\bar g s\) peaks (\cref{eq:s-reset}), and the \(v\)-nullcline with the ensuing stable \(p_f\) move down the \(w\)-nullcline.
+Then in between spikes \(\bar g s\) decays exponentially (\cref{eq:dot-s}) causing the \(v\)-nullcline and \(p_{f}\) to move up the \(w\)-nullcline while attracting trajectories of the \quiet{} cell.
+Once depression causes the synaptic conductance to become small enough to satisfy \(\bar g s<g^{\star}\) and the \quiet{} cell is released, fixed point \(p_{f}\) becomes unstable allowing the \quiet{} cell to fire.
+If the trajectory of the \quiet{} cell remains sufficiently close to the stable \(p_{f}\) at the time when it changes stability, then \(\bar g s < g^{\star}\) acts as a release condition that is not only necessary, but also sufficient for firing of the \quiet{} cell.
+In this case the release of the \quiet{} cell occurs precisely when
 \begin{equation}
 	~\label{eq:release}
-  \gbar s=g^{\star}
+	\bar g s=g^{\star}
 \end{equation}
@@
 
-Whether the $(v,w)$-trajectory of the quiet cell can remain close enough to $p_{f}$ to make \cref{eq:release} sufficient for firing depends largely on the coupling strength $\gbar$ and the timescale disparity between membrane dynamics and synaptic dynamics~\citep{bose2011}.
-It is straightforward to test our assumption of a release condition by numerically integrating the full system of ODEs and calculating the time interval between the first spike of the quiet cell and the time when $\gbar s$ first crosses $g^{\star}$.
+Whether the \((v,w)\)-trajectory of the \quiet{} cell can remain close enough to \(p_{f}\) to make \cref{eq:release} sufficient for firing depends largely on the coupling strength \(\bar g\) and the timescale disparity between membrane dynamics and synaptic dynamics~\citep{bose2011}.
+It is straightforward to test our assumption of a release condition by numerically integrating the full system of ODEs and calculating the time interval between the first spike of the \quiet{} cell and the time when \(\bar g s\) first crosses \(g^{\star}\).
 We will call this time interval the ``release delay''.
 If our assumption holds, we would expect an approximately zero release delay.
-\Cref{fig:release-delay} shows the numerically computed graph of the release delay for varying $\gbar$.
-The graph shows three distinct branches, next to each branch we also plot the timecourse of a corresponding sample solution of the total synaptic conductance $\gbar s$ of both cells.
-For the rightmost branch where $\gbar>0.592$ $\si{mS/cm^{2}}$ the release delay is approximately zero.
-Here the first spike of the quiet cell can be accurately predicted by the release condition in \cref{eq:release}.
-The leftmost and middle branches for $\gbar<0.592$ $\si{mS/cm^{2}}$  show a release delay greater than zero, the quiet cell does not immediately fire when the release condition is first satisfied, and \cref{eq:release} does not accurately predict the release of the quiet cell.
-The leftmost and middle branches contain $1-1$ and $2-2$ solutions respectively.
-In both cases the coupling $\gbar$ is not sufficiently strong to allow trajectories of the quiet cell to be close enough to $p_{f}$ to guarantee spiking once $\gbar$ crosses $g^{\star}$.
-Note that in the middle branch $\gbar s $ crosses $g^{\star}$ twice, and only after the second crossing does the quiet cell fire.
-The following map construction relies on the assumption that the release condition in \cref{eq:release} can accurately predict the release time of the quiet cell.
-Given our model parameters this is only possible for sufficiently large $\gbar>0.592 $ $\si{mS/cm^{2}}$.
-For completeness, however, we will also consider values $\gbar < 0.592$ $\si{mS/cm^{2}}$ in the following analysis, bearing in mind that in this parameter range our map will not be accurate.
+\Cref{fig:release-delay} shows the numerically computed graph of the release delay for varying \(\bar g\).
+The graph shows three distinct branches, next to each branch we also plot the timecourse of a corresponding sample solution of the total synaptic conductance \(\bar g s\) of both cells.
+For the rightmost branch where \(\bar g>0.592\) \(\si{mS/cm^{2}}\) the release delay is approximately zero.
+Here the first spike of the \quiet{} cell can be accurately predicted by the release condition in \cref{eq:release}.
+The leftmost and middle branches for \(\bar g<0.592\) \(\si{mS/cm^{2}}\)  show a release delay greater than zero, the \quiet{} cell does not immediately fire when the release condition is first satisfied, and \cref{eq:release} does not accurately predict the release of the \quiet{} cell.
+The leftmost and middle branches contain \(1-1\) and \(2-2\) solutions respectively.
+In both cases the coupling \(\bar g\) is not sufficiently strong to allow trajectories of the \quiet{} cell to be close enough to \(p_{f}\) to guarantee spiking once \(\bar g\) crosses \(g^{\star}\).
+Note that in the middle branch \(\bar g s \) crosses \(g^{\star}\) twice, and only after the second crossing does the \quiet{} cell fire.
+The following map construction relies on the assumption that the release condition in \cref{eq:release} can accurately predict the release time of the \quiet{} cell.
+Given our model parameters this is only possible for sufficiently large \(\bar g>0.592 \) \(\si{mS/cm^{2}}\).
+For completeness, however, we will also consider values \(\bar g < 0.592\) \(\si{mS/cm^{2}}\) in the following analysis, bearing in mind that in this parameter range our map will not be accurate.
 
-In summary: For $\gbar>0.592$ $\si{mS/cm^{2}}$ the release condition is sufficient to predict when the quiet cell is released.
-Due to the symmetry of $n-n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
-The release time therefore uniquely determines the type of $n-n$ solution.
-Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the quiet cell.
-Instead, the solution of the synaptic variable $s$ of the free cell is sufficient to predict when $\gbar s=g^{*}$ is satisfied.
-Finally, $s$ is solely determined by the evolution of the depression variable $d$ of the free cell.
-Constructing a solution of $d$ during the free phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
-However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
-In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n-n$ solutions.
+In summary: For \(\bar g>0.592\) \(\si{mS/cm^{2}}\) the release condition is sufficient to predict when the \quiet{} cell is released.
+Due to the symmetry of \(n-n\) solutions the release occurs at exactly half the period of the full cycle, that is at \(P/2\).
+The release time therefore uniquely determines the type of \(n-n\) solution.
+Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the \quiet{} cell.
+Instead, the solution of the synaptic variable \(s\) of the \free{} cell is sufficient to predict when \(\bar g s=g^{*}\) is satisfied.
+Finally, \(s\) is solely determined by the evolution of the depression variable \(d\) of the \free{} cell.
+Constructing a solution of \(d\) during the \free{} phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
+However, finding the solution \(d\) requires us to know the initial value \(d(0)\) at the start of a cycle at \(t=0\).
+In the next section we will construct a scalar return map that tracks these initial values \(d(0)\) from cycle to cycle of stable \(n-n\) solutions.
 
 \subsection{Construction of the scalar Poincaré map}
-In this section we construct the scalar Poincaré map $\Pi_{n}:d^{\star}\mapsto d^{\star}$.
-Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n-n$ burst.
-The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
-To simplify the map construction we will assume that a free cell fires exactly $n$ times before it becomes quiet.
-Later we will relax this assumption.
-We will construct $\Pi_{n}$ by evolving $d$ first during the free phase and then during the quiet phase of the $n-n$ limit cycle.
-First, let us give explicit definitions of the free and quiet phases.
+In this section we construct the scalar Poincaré map \(\Pi_n:d^{\star}\mapsto d^{\star}\).
+Here the discrete variable \(d^{\star}\) tracks the values of the continuous depression variable \(d\) at the beginning of each \(n-n\) burst.
+The map \(\Pi_n\) therefore describes the evolution of \(d\), of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
+To simplify the map construction we will assume that a \free{} cell fires exactly \(n\) times before it becomes \quiet{}.
+We will construct \(\Pi_n\) by evolving \(d\) first during the \free{} phase and then during the \quiet{} phase of the \(n-n\) limit cycle.
+First, let us give explicit definitions of the \free{} and \quiet{} phases.
 A schematic illustration of both phases is given in \cref{fig:free-quiet1}.
 
-Suppose that at $t=0$ cell 1 becomes free with some initial $d(0)$.
-Cell 1 then fires $n$ spikes at the uncoupled period $T=T_{act}+T_{inact}$.
-Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
-After $n$ spikes the total conductance $\gbar s(t)$ acting on the quiet cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}, that is at some time $t=(n-1)T + \delt$, where $\Delta t < T_{inact}$, we have $\gbar s(t)=g^{\star}$.
+Suppose that at \(t=0\) cell 1 starts \free{} with some initial \(d(0)\). Cell 1 then fires \(n\) spikes at the uncoupled period \(T=T_{act}+T_{inact}\).
+Let \(s(t)\) and \(d(t)\) be the corresponding solutions of the synaptic and depression variables of cell 1.
+After \(n\) spikes the total conductance \(\bar g s(t)\) acting on the \quiet{} cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}.
+That is at some time \(t=(n-1)T + T_{act} + \Delta t\), where \(\Delta t < T_{inact}\), we have \(\bar g s(t)=g^{\star}\).
 Cell 2 is then released and prevents cell 1 from further spiking.
-Here $\delt$ is the time between the last spike of cell 1 and the first spike of cell 2 ~\citep{bose2011}.
-Once released, cell 2 also fires $n$ spikes until cell 1 becomes free once again at the cycle period.
-Let $P_n$ denote the full cycle period of a $n-n$ solution:
+Here \(\Delta t\) is the time between the last spike of cell 1 and the first spike of cell 2 ~\citep{bose2011}.
+Once released, cell 2 also fires \(n\) spikes until cell 1 becomes \free{} once again.
+Let \(P_n\) denote the full cycle period of a \(n-n\) solution:
 \begin{equation}
 	~\label{eq:P}
-  P_n = 2(n-1)T + 2\delt.
+	P_n = 2\Big( (n-1)T + T_{act} + \Delta t \Big).
 \end{equation}
-We can now define the free and quiet phases of cell 1 explicitly. The free phase is the time interval between the first and last spikes of the burst, that is for time $0<t<(n-1)T$.
-During the free phase of cell 1, the quiet cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\gbar s > g^{\star}$.
-The quiet phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T < t < 2(n-1)T + 2\delt$.
+We can now define the \free{} and \quiet{} phases of cell 1 explicitly.
+The \free{} phase is the interval that lasts from the first spike time up until the beginning of the inactive phase of the last spike, last spikes of the burst, that is for time \(0<t<(n-1)T + T_{act}\).
+During the \free{} phase of cell 1, the \quiet{} cell 2 is inhibited sufficiently strong to prevent it from firing, hence \(\bar g s > g^{\star}\).
+The \quiet{} phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for \((n-1)T + T_{act} < t < P_n\).
+Hence the \quiet{} phase lasts for \((n-1)T + T_{act} + 2\Delta t\).
 
-Note that only the quiet phase depends on $\delt$ which will play a central role in the construction of $\Pi_{n}$.
-From \cref{eq:P} $\delt$ can be be computed as
+Note that only the \quiet{} phase depends on \(\Delta t\), which will play a central role in the construction of \(\Pi_n\).
+From \cref{eq:P} \(\Delta t\) can be computed as
 \begin{equation}
-  ~\label{eq:delta-t-P}
-  \delt = \frac{1}{2}P_n - (n-1)T.
+	\label{eq:delta-t-P}
+	\Delta t = \frac{1}{2}P_n - (n-1)T - T_{act}.
+\end{equation}
+We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable \(n-n\) solutions in \cref{fig:bif-diagram}A to obtain the graph of \(\Delta t\) as a function of \(\bar g\) (\cref{fig:delta-t}).
+Each continuous branch of \(\Delta t\) is monotonically increasing and corresponds to a \(n-n\) burst:
+Stronger coupling \(\bar g\) increases the total synaptic conductance \(\bar g s\) that acts on the \quiet{} cell, thus delaying its release.
+It is easy to see that for any \(n\)-branch we have \(\Delta t < T_{inact}\):
+Once \(\Delta t\) crosses \(T_{inact}\), the \free{} cell can ``squeeze in" an additional spike and the solutions bifurcate into a \((n+1)-(n+1)\) burst.
+
+Distinguishing between the \free{} and \quiet{} phases of a cycle allows us to describe the dynamics of the depression variable \(d\) explicitly for each phase.
+As can be seen from \cref{fig:free-quiet1}C, during the \free{} phase \(d\) depresses when $v > v_\theta$ and recovers when $v < v_\theta$.
+In contrast, during the \quiet{} phase \(d\) only recovers and does not depress.
+Given the initial \(d^{\star} = d(0)\) at the beginning of the cycle and the number of spikes in the \free{} phase \(n\), we can now construct the burst map \(\Pi_n\).
+The map
+\begin{equation}
+	\Pi_n(d^\star)=Q_n\big(F_n(d^\star\big))
 \end{equation}
 \noindent
-We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n-n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\delt$ as a function of $\gbar$ (\cref{fig:delta-t}).
-Each continuous branch of $\delt$ is monotonically increasing and corresponds to a $n-n$ burst:
-Stronger coupling $\gbar$ increases the total synaptic conductance $\gbar s$ that acts on the quiet cell, thus delaying its release.
-It is easy to see that for any $n$-branch we have $\delt<T$:
-Once $\delt$ crosses $T$, the free cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1)-(n+1)$ burst.
-
-Distinguishing between the active and silent phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
-As can be seen from \cref{fig:free-quiet1}C, during the active phase $d$ depresses during the active phase of spikes and recovers during the inactive phases of spikes.
-% TODO need to sort out terminology here, i.e. inactive vs quiet
-In contrast, during the silent phase $d$ only recovers and does not depress.
-Given the initial $d^{\star}=d(0)$ at the beginning of the cycle and the number of spikes in the free phase $n$, we can now construct the burst map $\Pi_{n}$.
-The map
+is a composition of two maps. Map
 \begin{equation}
-  \Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star}\big))
+	F_n:d^\star\mapsto \Delta t
 \end{equation}
-\noindent
-is a composition of two maps.
+models the evolution of \(d\) in the \free{} phase.
+\(F_n\) takes an initial value \(d^{\star}\) and calculates \(\Delta t\).
 Map
 \begin{equation}
-  F_{n}:d^{\star}\mapsto \delt
+	Q_n:\Delta t \mapsto d^{\star}
 \end{equation}
-models the evolution of $d$ in the free phase.
-$F_{n}$ takes an initial value $d^{\star}$ and calculates the inter-burst-interval $\delt$.
-Map
-\begin{equation}
-  Q_{n}:\delt \mapsto d^{\star}
-\end{equation}
-models the recovery of $d$ in the quiet phase.
-Given some $\delt$ map $Q_n$ computes $\dstar$ at the start of the next cycle.
+models the recovery of \(d\) in the \quiet{} phase.
+Given some \(\Delta t\) map \(Q_n\) computes \(d^\star\) at the start of the next cycle.
 
-Our aim in the following analysis is to elucidate the properties of $\Pi_{n}$ and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of $\Pi_{n}$ are created.
-To that effect it will be useful to include not only positive, but also negative values of $d^{\star}$ to the domain of $\Pi_{n}$.
-But it is important to add that values $d^{\star}<0$ are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
-Because $\Pi_{n}$ maps first from $d^{\star}$ to $\delt$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n-n$ solutions with partially overlapping bursts.
-As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n-n$ solutions of the full system of ODEs only exist for $\Delta t>0$.
+Our aim in the following analysis is to elucidate the properties of \(\Pi_n\) and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of \(\Pi_{n}\) are created.
+To that effect it will be useful to include not only positive, but also negative values of \(d^{\star}\) to the domain of \(\Pi_{n}\).
+But it is important to add that values \(d^{\star}<0\) are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
+Because \(\Pi_{n}\) maps first from \(d^{\star}\) to \(\Delta t\), and then back to \(d^{\star}\), we will also consider negative values of \(\Delta t\), interpreting them as \(n-n\) solutions with partially overlapping bursts.
+As will become evident, \(\delt<0\) is only a formal violation of the biological realism of the map \(\Pi_{n}\), as numerically stable \(n-n\) solutions of the full system of ODEs only exist for \(\Delta t>0\).
 
 % TODO: Edit par
-We start the construction of $\Pi_n$ by first considering the free phase and building the map $F_n$.
-At each spike time $t_{k}$ where $d(t_k) = d_k$, variable $d$ decays first for the duration of the active phase of the spike for $T_{act}$, as described by the solution to \cref{eq:dot-d}.
-At $t = t_k + T_{act}$ we have
+We start the construction of \(\Pi_n\) by first considering the \free{} phase and building the map \(F_n\).
+At each spike time \(t_{k}\) where \(d(t_k) = d_k\), variable \(d\) decays first for the duration of the active phase of the spike for \(T_{act}\), as described by the solution to \cref{eq:dot-d}.
+At \(t = t_k + T_{act}\) we have
 \begin{equation}
@@
 \end{equation}
-The depression variable then recovers during the inactive phase of the spike until $t_{k+1}$, where for $0<t<T_{inact}$ we get
+The depression variable then recovers during the inactive phase of the spike until \(t_{k+1}\), where for \(0<t<T_{inact}\):
 \begin{equation}
@@
 \end{equation}
-By substituting $t=T_{inact}$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the free phase:
+By substituting \(t=T_{inact}\) we can build a linear map that models the depression of \(d\) from spike time \(t_{k}\) to the subsequent spike time \(t_{k+1}\) during the \free{} phase:
 \begin{equation}
@@
 \begin{align}
-  \lambda & = \exp(-T_{act}/\tau_b),    \\
-  \rho    & =\exp(-T_{inact}/\tau_{a}).
+	\lambda & := \exp(-T_{act}/\tau_b), \label{eq:lambda} \\
+	\rho    & :=\exp(-T_{inact}/\tau_{a}). \label{eq:rho}
 \end{align}
 
-Given constant $T_{act}$ and $T_{inact}$, parameter $\lambda$ determines how much the synapses depresses during the active phase of the spike, while $\rho$ determines how much it recovers during the inactive phase.
-Since $0<\lambda, \rho<1$, map \cref{eq:map-d} is increasing and contracting, with a fixed point at
+Given constant \(T_{act}\) and \(T_{inact}\), parameter \(\lambda\) determines how much the synapses depresses during the active phase of the spike, while \(\rho\) determines how much it recovers during the inactive phase.
+Since \(0<\lambda, \rho<1\), map \cref{eq:map-d} is increasing and contracting, with a fixed point at
 \begin{equation}
@@
 \end{equation}
-where $0<d_{s}<1$.
-The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
-Using the release condition in \cref{eq:release} allows us to derive the value of the the minimum coupling strength that will produce the full suppressed solution, denoted as $\gbar_{s}$.
-% TODO Explain why s(0) = ds
-% TODO See https://trello.com/c/AYqZIaXh: Would be good to elaborate on the idea that lambda and tau can be
-% viewed as the new time constants in the reduced system.
-Solving \cref{eq:dot-s} for $s(t)$ with $t=T$ and setting the initial value $s(0)=d_{s}$ gives
-\begin{equation}
-  \gbar_{s} d_{s}e^{-T/\tau_\kappa}=g^{\star}.
+where \(0<d_{s}<1\).
+The value \(d_{s}\) is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period \(T\) (see \cref{fig:burst-sols}E).
+Using the release condition in \cref{eq:release} allows us to derive the value of the minimum coupling strength that will produce the full suppressed solution, denoted as \(\bar g_{s}\).
+% TODO  Would be good to elaborate on the idea that lambda and tau can be viewed as the new time constants in the reduced system.
+Solving \cref{eq:dot-s} for \(s(t)\) with \(t=T_{inact}\) and setting the initial value \(s(0)=d_s\lambda\) gives \begin{equation}
+	\bar g_s d_s\lambda e^{-T_{inact}/\tau_\kappa}=g^{\star}.
 \end{equation}
-By further substituting the definition of $d_{s}$ in~\eqref{eq:dsup} and rearranging, we can write $\gbar_{s}$ as a function of $\lambda$ and $\rho$:
+By further substituting the definition of \(d_s\) in~\eqref{eq:dsup} and rearranging, we can write \(\bar g_s\) as a function of \(\lambda\) and \(\rho\):
 \begin{equation}
 	\label{eq:gs}
-  \gbar_{s}(\lambda, \rho) = g^{\star}e^{T/\tau_\kappa}\frac{1-\lambda \rho}{1-\rho}.
+	\bar g_s(\lambda, \rho) = \frac{1/\lambda-\rho}{1-\rho} e^{T_{inact}/\tau_\kappa}g^\star.
 \end{equation}
-Note that the above dependence of $\gbar_{s}$ on $\lambda$ is linear and monotonically decreasing.
-Increasing $\lambda$ reduces the strength of the depression of the free cell.
-This in turn allows the free cell to fully suppress the quiet cell at smaller values of $\gbar$.
+Note that the above dependence of \(\bar g_{s}\) on \(\lambda\) is linear and monotonically decreasing.
+Increasing \(\lambda\) reduces the strength of the depression of the \free{} cell.
+This in turn allows the \free{} cell to fully suppress the \quiet{} cell at smaller values of \(\bar g\).
 
-Solving~\eqref{eq:map-d} gives us the linear map $\delta_{n}:d^{\star}\mapsto
-d_{n}$, that for some initial $d^{\star}$ computes the depression at the $n$th
-spike time, $d_{n}=d(t_{n}^{-})$:
+Solving \cref{eq:map-d} gives us the linear map \(\delta_n:d^{\star}\mapsto d_n\), that for some initial \(d^\star\) computes the depression at the \(n\)th spike time, \(d_n=d(t_n)\):
 \begin{equation}
-  ~\label{eq:delta-map}
-  \delta_{n}(d^{\star}) = (\lambda \rho)^{n-1} d^{\star} + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}.
+	\label{eq:delta-map}
+	\delta_n(d^\star) = (\lambda \rho)^{n-1} d^\star + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^i.
 \end{equation}
-Since $\lambda < 1$, function $\delta_{n}$ is a linearly increasing function of
-$d^{\star}$ with a fixed point at $d_{s}$ for all $n$.  Having identified $d$ after $n$
-spikes, we can now use the release condition $\gbar s = g^{\star}$ (\cref{eq:release}) to
-find $\delt$.
-% FIXME:
-After the last spike of the free phase at time $t_{n} = (n-1)T$ the synapse variable $s$
-has the value of $d$ for the duration of $T_{act}$, which is given by
-$\delta_n(\dstar)\lambda$. $s$ then decays exponentially for $\Delta t < T_{inact}$.
-Solving \cref{eq:dot-s} (case $v < v_\theta$) with initial condition
-$s(0)=\dn(\dstar)\lambda$ yields:
+Since \(\lambda < 1\), function \(\delta_n\) is a linearly increasing function of \(d^\star\) with a fixed point at \(d_s\) for all \(n\).
+Having identified \(d\) after \(n\) spikes, we can now use the release condition \(\bar g s = g^{\star}\) (\cref{eq:release}) to find \(\Delta t\).
+At the last (\(n\)th) spike of the \free{} phase at time \(t_n = (n-1)T\) the synapse variable \(s\) is set to the respective value of \(d(t_n) = \delta_n(d^\star)\), and mirrors the value of \(d\) for the duration of \(T_{act}\).
+at the end of the active phase at time \(t_n + T_{act}\) variable \(d\) has decayed to $\delta_n(d^\star) \lambda$ \cref{eq:lambda}, therefore
+\begin{equation}
+	s(t_n + T_{act})=\delta_n(d^\star)\lambda.
+\end{equation}
+Finally \(s\) decays exponentially for \(\Delta t < T_{inact}\).
+Solving \cref{eq:dot-s} (case \(v < v_\theta\)) with initial condition \(s(0)=\dn(d^\star)\lambda\) yields:
 \begin{equation}
 	~\label{eq:s-sol}
-  s(\delt)=\dn(\dstar)e^{-\Delta t/\tau_\kappa}.
+	s(\Delta t)=\dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}.
 \end{equation}
-Substituting $s(\delt)$ into $s$ of the release condition (\cref{eq:release})
-gives then
+Substituting \(s(\Delta t)\) into \(s\) of the release condition (\cref{eq:release}) gives then
 \begin{equation}
 	~\label{eq:release2}
-  \gbar \dn(\dstar) e^{-\delt/\tau_\kappa}=g^{\star}.
+	\bar g \dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}=g^{\star}.
 \end{equation}
-Our assumption of the release condition guarantees that the quiet cell 2 spikes and
-becomes free when $\gbar s - g^{\star}$ crosses zero. Solving \cref{eq:release2} for
-$\delt$ allows us to compute the inter-spike-interval as a function of $\dstar$, which
-defines our map $F_n$:
+Our assumption of the release condition guarantees that the \quiet{} cell 2 spikes and becomes \free{} when \(\bar g s - g^{\star}\) crosses zero.
+Solving \cref{eq:release2} for \(\Delta t\) allows us to compute it a function of \(d^\star\), which defines our map \(F_n\):
 \begin{equation}
-  ~\label{eq:Fn-map}
-  F_{n}(d^{\star}):=\tau_\kappa \ln{\left(\frac{\gbar }{g^{\star}} \delta_{n}(d^{\star})\right)}= \delt.
+	\label{eq:Fn-map}
+	F_n(d^\star):=\tau_\kappa \ln{\left(\frac{\bar g }{g^\star} \lambda \delta_{n}(d^\star)\right)}= \Delta t.
 \end{equation}
 
-\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing
-function of $d^{\star}$ as well as $\gbar$.  Larger values of $d^{\star}$ and $\gbar$,
-respectively, cause stronger inhibition of the quiet cell, and therefore prolong its
-release time and the associated $\delt$.  Map $F_{n}$ is defined on $d^{\star}>d_{a}$,
-where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(\dstar)=0$ in
-\cref{eq:delta-map} for $\dstar$, which yields
+\Cref{fig:FQ-map}A shows \(F_n\) for various \(n\), which is a strict monotonically increasing function of \(d^{\star}\) as well as \(\bar g\).
+Larger values of \(d^{\star}\) and \(\bar g\), respectively, cause stronger inhibition of the \quiet{} cell, and therefore prolong its release time and the associated \(\Delta t\).
+Map \(F_n\) is defined on \(d^{\star}>d_{a}\), where \(d_{a}\) is a vertical asymptote found by solving \(\delta_{n}(d^\star)=0\) in \cref{eq:delta-map} for \(d^\star\), which yields
 \begin{equation}
@@
 
-We now turn to the construction of map $Q_{n}$, which describes the recovery of the depression variable during the quiet phase.
-As we have identified earlier, the recovery in the quiet phase of a $n-n$ solution is of duration $2\delt +(n-1)T$.
-Substituting that into the solution for $d(t)$ (\cref{eq:d-sol}) with the initial condition $d(0)=\dn(\dstar)$ yields the map $Q_{n}$:
+We now turn to the construction of map \(Q_n\), which describes the recovery of the depression variable during the \quiet{} phase.
+As we have identified earlier, the recovery in the \quiet{} phase of a \(n-n\) solution is of duration \((n-1)T + T_{act} + 2\Delta t\).
+Substituting that into the solution of \(d\) (\cref{eq:dot-d}) with the initial condition \(d(0)=\dn(d^\star) \lambda\) yields the map \(Q_{n}\):
 \begin{equation}
-  ~\label{eq:Qn-map}
-  Q_{n}(\delt):=1- (1- \lambda \dn(\dstar))e^{-(2\Delta t+(n-1)T)/\tau_{d}}.
+	\label{eq:Qn-map}
+	Q_n(\Delta t) := 1- (1- \dn(d^\star) \lambda)e^{-((n-1)T + T_{act} + 2\Delta t)/\tau_a}.
 \end{equation}
-Given $\delt$, we can find $\dn(\dstar)$ by rearranging the release condition in \cref{eq:release2}:
+Given \(\Delta t\), we can find \(\dn(d^\star)\) by rearranging the release condition in \cref{eq:release2}:
 \begin{equation}
-  ~\label{eq:dn}
-  \dn(\dstar) = \frac{g^{\star}}{\gbar} e^{\delt/\tau_{s}}.
+	\label{eq:dn}
+	\delta_n(d^\star) = \frac{1}{\bar g \lambda} g^\star e^{\Delta t/\tau_\kappa}.
 \end{equation}
-Map $Q_{n}$ is shown in \cref{fig:FQ-map}B for various values $n$.
-Note that $Q_{n}$ is monotonically increasing as larger values $\delt$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
-All curves $Q_{n}$ intersect at some $\delt = \tau_{s}\ln{\left[\gbar/(g^{\star}\lambda)\right]}$ where
+Map \(Q_n\) is shown in \cref{fig:FQ-map}B for various values \(n\).
+Note that \(Q_n\) is monotonically increasing as larger values \(\Delta t\) imply a longer recovery time, and hence \(Q_{n}\) grows without bound.
+All curves \(Q_{n}\) intersect at some \(\Delta t = \tau_\kappa\ln{\left[\bar g/g^\star\right]}\) where
 \begin{equation}
-  ~\label{eq:Qn-intersect}
-  Q_{n}\left[\tau_{s}\ln{\left(\frac{\gbar}{g^{\star}\lambda}\right)}\right]=1.
+	\label{eq:Qn-intersect}
+	Q_n\left[\tau_\kappa\ln{\left(\frac{\bar g}{g^\star}\right)}\right]=1.
 \end{equation}
-As we will show in the next section, all fixed points of the full map $\Pi_{n}$ occur for $d^{\star}<1$.
-We will therefore restrict the domain of $Q_{n}$ to $(-\infty, \ln{\left[\gbar/(g^{\star}\lambda)\right]}\tau_{s})$ and the codomain to $(-\infty, 1)$.
-Additionally, while values $\delt>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t=T$, and we will address this concern in the last part of our map analysis.
+As we will show in the next section, all fixed points of the full map \(\Pi_n\) occur for \(d^\star<1\).
+We will therefore restrict the domain of \(Q_n\) to \((-\infty, \tau_\kappa\ln{\left[\bar g/(g^\star)\right]})\) and the codomain to \((-\infty, 1)\).
+Additionally, while values \(\Delta t>T\) will be helpful in exploring the geometry of \(\Pi_{n}\), recall from \cref{fig:delta-t} that in the flow system all \(n-n\) solutions bifurcate into \((n+1)-(n+1)\) solutions exactly when \(\Delta t = T_{inact}\), and we will address this concern in the last part of our map analysis.
 
-Having found $F_{n}$ and $Q_{n}$, we can now construct the full map $\Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star})\big)$:
+Having found \(F_n\) and \(Q_n\), we can now construct the full map \(\Pi_n(d^\star)=Q_n\big(F_n(d^\star)\big)\):
 \begin{equation}
-  ~\label{eq:Pn-map}
-  \Pi_{n}(d^{\star})= 1-
-  \frac{\rho^{n-1}{g^{\star}}^{\tau}}{{\gbar}^{\tau}}\delta_{n}^{-\tau}(d^{\star})\big(1-\lambda\delta_{n}(d^{\star})\big),
+	\label{eq:Pn-map}
+	\Pi_n(d^\star) = 1 - \Big(1 - \delta_n(d^\star) \lambda \Big)
+	\Big(\frac{\bar g}{g^\star}\delta_n(d^\star) \lambda \Big)^{-\tau}
+	e^{-((n-1)T + T_{act})/\tau_a},
 \end{equation}
-where we substituted $\tau = 2\tau_{s}/\tau_{d}$.
-Since $d$ is the slowest variable of the system and $\tau_{d}\gg \tau_{s}$, we will also assume $\tau<1$.
-\Cref{fig:Pn-map}A depicts $\Pi_{n}$ for various $n$.
-Intersections of $\Pi_{n}$ with the diagonal are fixed points of the map.
-\Cref{fig:Pn-map}B shows $\Pi_{2}$ with $n=2$.
-Varying the synaptic strength $\gbar$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
-For $\gbar<0.03$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
-As $\gbar$ is increased to $\gbar \approx 0.03$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
-When $\gbar > 0.03$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
+where we substituted \(\tau = 2\tau_{k}/\tau_{a}\).
+Since \(d\) is the slowest variable of the system and \(\tau_a \gg \tau_\kappa\), we will also assume \(\tau<1\).
+\Cref{fig:Pn-map}A depicts \(\Pi_n\) for various \(n\).
+Intersections of \(\Pi_{n}\) with the diagonal are fixed points of the map.
+\Cref{fig:Pn-map}B shows \(\Pi_{2}\) with \(n=2\).
+Varying the synaptic strength \(\bar g\) moves the curves \(\Pi_{n}\) up and down the \((d^{\star}, \Pi_{n})\)-plane.
+For \(\bar g < 0.03\) \(\si{mS/cm^{2}}\) map \(\Pi_{2}\) has no fixed points.
+As \(\bar g\) is increased to \(\bar g \approx 0.03\) \(\si{mS/cm^{2}}\), curve \(\Pi_{2}\) coalesces with the diagonal tangentially.
+When \(\bar g > 0.03\) \(\si{mS/cm^{2}}\), a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
 
-From \cref{eq:Pn-map} it is evident that $\Pi_{n}$ is monotonically increasing with respect to $\gbar$ and also $\dstar$:
+From \cref{eq:Pn-map} it is evident that \(\Pi_n\) is monotonically increasing with respect to \(\bar g\) and also \(d^\star\):
 \begin{align}
 	\label{eq:non-degen1}
-  \dv{\Pi_{n}}{\gbar}  & >0, \\[0.5ex]
+	\dv{\Pi_n}{\bar g}  & >0, \\[0.5ex]
 	\label{eq:dPidd}
-  \dv{\Pi_{n}}{\dstar} & >0,
+	\dv{\Pi_n}{d^\star} & >0,
 \end{align}
-and in the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
-Just as $F_{n}$, curves $\Pi_{n}$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
+and in the following sections we will heavily rely on this monotonicity property of \(\Pi_n\).
+Just as \(F_n\), curves \(\Pi_n\) spawn at the asymptote \(d_{a}\) (\cref{eq:da}), and because
 \begin{equation}
-  \lim_{\gbar \to \infty}\Pi_{n} = 1\text{ for all }n,
+	\lim_{\bar g \to \infty}\Pi_n = 1\text{ for all }n,
 \end{equation}
-fixed points of $\Pi_{n}$ lie in $(d_{a}, 1)$.
+fixed points of \(\Pi_n\) lie in \((d_{a}, 1)\).
 
-% \subsection{Existence and stability of fixed points of $\mathit{\Pi_{n}}$}
 \subsection{Existence and stability of fixed points}
-We introduce the fixed point notation $\dstar_{f}$ with $\Pi_{n}(\dstar_{f})=\dstar_{f}$.
-The existence of fixed points $\dstar_{f}$ for $\gbar$ sufficiently large can be shown from the strict monotonicity of $\Pi_{n}$ with respect to $\gbar$ and $\dstar$ (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of $\Pi_{n}$ is monotonically decreasing,
+We introduce the fixed point notation \(d^\star_{f}\) with \(\Pi_n(d^\star_{f})=d^\star_{f}\).
+The existence of fixed points \(d^\star_{f}\) for \(\bar g\) sufficiently large can be shown from the strict monotonicity of \(\Pi_{n}\) with respect to \(\bar g\) and \(d^\star\) (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of \(\Pi_{n}\) is monotonically decreasing,
 \begin{equation}
 	\label{eq:non-degen2}
-  \left(\frac{\mathrm{d}}{\mathrm{d}\dstar}\right)^2 \Pi_{n}<0.
+	\left(\frac{\mathrm{d}}{\mathrm{d}d^\star}\right)^2 \Pi_n<0.
 \end{equation}
-In the limit $\dstar \to d_{a}$ the value of $\Pi_n$ decreases without bound for any $\gbar>0$.
-In the limit $\gbar \to 0$, $\Pi_n$ also decreases without bound, but as $\gbar \to \infty$ values of $\Pi_n$ approach $1$.
-It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some $\gbar$ large enough $\Pi_n$ intersects the diagonal.
-Moreover, because $\Pi_n$ and its slope are monotonic with respect to $\dstar$, there exists some critical fixed point $(\dstar_b, \gbar_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
+In the limit \(d^\star \to d_{a}\) the value of \(\Pi_n\) decreases without bound for any \(\bar g>0\).
+In the limit \(\bar g\to 0\), \(\Pi_n\) also decreases without bound, but as \(\bar g\to \infty\) values of \(\Pi_n\) approach \(1\).
+It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some \(\bar g\) large enough \(\Pi_n\) intersects the diagonal.
+Moreover, because \(\Pi_n\) and its slope are monotonic with respect to \(d^\star\), there exists some critical fixed point \((d^\star_b, \bar g_b)\) where \(\Pi_n\) aligns with the diagonal tangentially with
+% TODO: Replace the dx/dt with the physics package stuff
 \begin{align}
-  \Pi_{n}(\dstar_{b}; \gbar_{b})                     & =\dstar_{b}, \\
-  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b}) & =1.
+	\Pi_n(d^\star_b, \bar g_b)                  & =d^\star_b, \\
+	\frac{d}{d^\star}\Pi_n(d^\star_b, \bar g_b) & =1.
 \end{align}
-Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(\dstar_{b}, \gbar_{b})$ map $\Pi_{n}$ has the topological normal form described by the graph of
+Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of \((d^\star_{b}, \bar g_{b})\) map \(\Pi_n\) has the topological normal form described by the graph of
 \begin{equation}
@@
 \end{equation}
-with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.
+with a stable and unstable fixed point \(x=\pm\sqrt{\beta}\), and slopes \(\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}\), respectively.
 
-\subsection{Fold bifurcations}
-Fixed points of $\Pi_n$ satisfy the fixed point equation
+\subsection{Fold bifurcations of maps}
+Fixed points of \(\Pi_n\) satisfy the fixed point equation
 \begin{equation}
 	\label{eq:Phi}
-  \Phi_n(\dstar; \gbar)=0,
+	\Phi_n(d^\star, \bar g) := \Pi_n(d^\star, \bar g)-d^\star = 0.
 \end{equation}
-where
-\begin{equation}
-  ~\label{eq:Phi-def}
-  \Phi_{n}(d^{\star}, \gbar):=\Pi_{n}(d^{\star}, \gbar)-d^{\star}.
-\end{equation}
-As we have already shown, for $\gbar > \gbar_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
-Solving \cref{eq:Phi} explicitly for $\dstar$ it not trivial, but solving for $\gbar$ is straightforward and given by $\gbar = G_n(\dstar)$, where
+As we have already shown, for \(\bar g > \bar g_b(n)\) solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
+Solving \cref{eq:Phi} explicitly for \(d^\star\) it not trivial, but solving for \(\bar g\) is straightforward and given by \(\bar g= G_n(d^\star)\), where
 \begin{equation}
 	~\label{eq:g}
-  G_{n}(d^{\star}) := g^{\star} \left(\frac{\rho^{n-1}\delta_{n}^{-\tau}(d^{\star})(1-\lambda\delta_{n}(d^{\star}))}{1-d^{\star}}\right)^{1/\tau}.
+	G_{n}(d^{\star}) :=
+	\frac{g^{\star}}{\delta_n(d^\star)\lambda}
+	\Big(
+	\frac{(1-\lambda\delta_n(d^\star)) }{1-d^\star} e^{-((n-1)T + T_{act})/\tau_a}
+	\Big)^{1/\tau}.
 \end{equation}
-Plotting $d^{\star}$ against $\gbar$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
+Plotting \(d^\star\) against \(\bar g\) gives the fixed point curves, which are shown in \cref{fig:folds}A.
 Note the typical quadratic shape of a fold bifurcation of maps.
-It is also evident that the fold bifurcations occur for increasingly smaller $\gbar$ as $n$ is increased.
-Moreover, we can observe that unstable fixed points have negative values of $d^{\star}$ for $n>1$.
+It is also evident that the fold bifurcations occur for increasingly smaller \(\bar g\) as \(n\) is increased.
+Moreover, we can observe that unstable fixed points have negative values of \(d^\star\) for \(n>1\).
 
-\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(\dstar_{b}(n), \gbar_{b}(n)\big)$, which is the global minimum of $G_{n}(\dstar_f)$:
+\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely \(\big(d^\star_b(n), \bar g_b(n)\big)\), which is the global minimum
+of \(G_n(d^\star_f)\):
 \begin{align}
-  \dstar_{b}(n) & = \operatorname{argmin} G_{n}(\dstar_{f}), \\
-  \gbar_{b}(n)  & = \min{G_{n}(\dstar_{f})}.
+	d^\star_b(n) & = \operatorname{argmin} G_n(d^\star_f), \\
+	\bar g_b(n)  & = \min{G_n(d^\star_f)}.
 \end{align}
-Function $G_{n}$ is strictly monotonic on the respective intervals of $\dstar_f$ that correspond to the stable and unstable fixed points, that is
+Function \(G_n\) is strictly monotonic on the respective intervals of \(d^\star_f\) that correspond to the stable and unstable fixed points, that is
 \begin{align}
-  \dv{G_n}{\dstar_f} & < 0, \text{ for } \dstar_f>\dstar_b(n) \text{ stable},   \\[0.5ex]
-  \dv{G_n}{\dstar_f} & > 0, \text{ for } \dstar_f<\dstar_b(n) \text{ unstable},
+	\dv{G_n}{d^\star_f} & < 0, \text{ for } d^\star_f>d^\star_b(n) \text{ stable},   \\[0.5ex]
+	\dv{G_n}{d^\star_f} & > 0, \text{ for } d^\star_f<d^\star_b(n) \text{ unstable},
 \end{align}
-which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $\dstar_f$.
-Because we are primarily interested in the stable fixed points, we define the stable fixed point function $\dstar_f=\phi_n(\gbar)$ as
+which allows us to express the stable and unstable fixed points as the inverse of \(G_n\) on their respective intervals of \(d^\star_f\).
+Because we are primarily interested in the stable fixed points, we define the stable fixed point function \(d^\star_f = \phi_n(\bar g)\) as
 \begin{equation}
 	\label{eq:phi}
-  \phi_{n}(\gbar):= G_{n}^{-1}(\dstar_{f}) \text{ for } \dstar_{f}>\dstar_{b}(n).
+	\phi_n(\bar g):= G_n^{-1}(d^\star_f) \text{ for } d^\star_f>d^\star_b(n).
 \end{equation}
-Function $\phi_n(\gbar)$ is also monotonic, and is therefore straightforward to compute numerically via root-finding.
-Here we use the Python package Pynverse~\citep{pynverse} for that purpose.
+Function \(\phi_n(\bar g)\) is also monotonic, and is therefore straightforward to compute numerically.
+Here we use the Python package Pynverse \citep{pynverse} for that purpose.
 
-Having found the stable fixed points $\dstar_f$ as a function of the coupling strength $\gbar$, we can now compute the associated cycle period.
-Recall that the period is given by \cref{eq:P}, which we can be written as a function of $\gbar$:
+Having found the stable fixed points \(d^\star_f\) as a function of \(\bar g\), we can now compute the associated cycle period.
+Recall that the period is given by \cref{eq:P}, which we can be written as a function of \(\bar g\):
 \begin{equation}
 	\label{eq:period}
-  P_n(\gbar) = 2(n-1)T + 2F_n\big(\underbrace{\phi_n(\gbar)}_{\dstar_f}, \gbar\big),
+	P_n(\bar g) = 2 \Big(
+	(n-1)T + T_{act} + F_n\big(\underbrace{\phi_n(\bar g)}_{d^\star_f}, \bar g\big)
+	\Big),
 \end{equation}
-where map $F_n$ (\cref{eq:Fn-map}) calculates the inter-burst-interval $\delt$ given a stable fixed point $\dstar_f=\phi_n(\gbar)$.
-We plot the predicted period $P_n(\gbar)$ versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
-For $n>1$ our map $\Pi_n$ accurately predicts the period.
-When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for $n=1$ (see \cref{fig:release-delay}), since here $\gbar$ is not sufficiently strong to guarantee the validity of our release condition (\cref{eq:release}).
+where map \(F_n\) (\cref{eq:Fn-map}) calculates \(\Delta t\) given a stable fixed point \(d^\star_f=\phi_n(\bar g)\).
+We plot the predicted period \(P_n(\bar g)\) versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
+For \(n>1\) our map \(\Pi_n\) accurately predicts the period.
+When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for \(n=1\) (see \cref{fig:release-delay}), since here \(\bar g\) is not sufficiently strong to guarantee the validity of our release condition
+(\cref{eq:release}).
 
-It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\gbar$.
-This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\gbar), \gbar)=0$ in \cref{eq:Phi}.
-For $\dstar_f=\phi_n(\gbar)>d_b(n)$ we get:
+% TODO: Need to double-check this paragraph about implicit differentiation. It should still hold after the model change I believe.
+It is evident from \cref{fig:folds}A that \(\phi_n\) is strictly increasing with \(\bar g\).
+This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation \(\Phi_n(\phi_n(\bar g), \bar g)=0\) in \cref{eq:Phi}.
+For \(d^\star_f=\phi_n(\bar g)>d_b(n)\) we get:
 \begin{equation}
-  \label{eq:dstardg}
-  \dv{\phi_n}{\gbar} = -\frac{\pdv*{\Phi_n}{\gbar}}{\pdv*{\Phi_n}{\dstar}} =
-  \frac{\pdv*{\Pi_n}{\gbar}}{1-\pdv*{\Pi_n}{\dstar}}>0.
+	\label{dstardg:eq}
+	\dv{\phi_n}{\bar g} = -\frac{\pdv*{\Phi_n}{\bar g}}{\pdv*{\Phi_n}{d^\star}} =
+	\frac{\pdv*{\Pi_n}{\bar g}}{1-\pdv*{\Pi_n}{d^\star}}>0.
 \end{equation}
-The inequality follows from $\pdv*{\Pi_n}{\gbar}>0$ and the fact that $\pdv*{\Pi_n}{\dstar}<1$ for $\dstar>d_b(n)$.
-\Cref{eq:dstardg} allows us to explain why the period $P_n$ increases with $\gbar$, as seen in \cref{fig:folds}B.
-Differentiating $P_n$ gives:
+The inequality follows from \(\pdv*{\Pi_n}{\bar g}>0\) and the fact that \(\pdv*{\Pi_n}{d^\star}<1\) for \(d^\star>d_b(n)\).
+\Cref{eq:dstardg} allows us to explain why the period \(P_n\) increases with \(\bar g\), as seen in \cref{fig:folds}B.
+Differentiating \(P_n\) gives:
 \begin{equation}
 	\label{eq:dPdg}
-  \dv{P_{n}}{\gbar} = 2\grad F_n(\dstar_f, \gbar) \cdot
-  \begin{bmatrix}\pdv*{\phi_n}{\gbar}\\[0.5ex] 1\end{bmatrix}>0,
+	\dv{P_{n}}{\bar g} = 2\grad F_n(d^\star_f, \bar g) \cdot
+	\begin{bmatrix}\pdv*{\phi_n}{\bar g}\\[0.5ex] 1\end{bmatrix}>0,
 \end{equation}
-where the partial derivatives of $F_n(\dstar_f, \gbar)$ are:
+where the partial derivatives of \(F_n(d^\star_f, \bar g)\) are:
 \begin{align}
-  \pdv{F_n}{\dstar_f} & = \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar_f)}>0, \\[0.5ex]
-  \pdv{F_n}{\gbar}    & = \frac{\taus}{\gbar}>0.
+	\pdv{F_n}{d^\star_f} & = \taus \frac{(\lambda\rho)^{n-1}}{\dn(d^\star_f)}>0, \\[0.5ex]
+	\pdv{F_n}{\bar g}    & = \frac{\tau_s}{\bar g}>0.
 \end{align}
-\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation:
-Increasing the coupling strength between the neurons leads to overall stronger inhibition of the quiet cell, which delays its release and leads to a longer cycle period.
-The latter allows more time for the synapse to depress in the free phase and recover in the quiet phase, resulting in overall larger values of $\dstar_f$, that is weaker depression at the burst onset.
+\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation: Increasing the coupling strength between the neurons leads to overall stronger inhibition of the \quiet{} cell, which delays its release and leads to a longer cycle period.
+The latter allows more time for the synapse to depress in the \free{} phase and recover in the \quiet{} phase, resulting in overall larger values of \(d^\star_f\), that is weaker depression at the burst onset.
 
-While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the free phase contains exactly $n$ spikes.
-As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n-n$ bursts exists only on certain parameter intervals of $\gbar$.
-In the last sub-section we will analyse the mechanisms that guide how the stable $n-n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\gbar$ where such solutions exist.
+While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the \free{} phase contains exactly \(n\) spikes.
+As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable \(n-n\) bursts exists only on certain parameter intervals of \(\bar g\).
+In the last sub-section we will analyse the mechanisms that guide how the stable \(n-n\) are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of \(\bar g\) where such solutions exist.
 
@@
 \subsection{Period increment bifurcations with co-existent attractors}
-Let $\gbar_+(n)$ and $\gbar_-(n)$ denote the left and right parameter borders on $\gbar$ where stable $n-n$ solutions exist.
-That is, as $\gbar$ is increased stable $n-n$ solutions are created at $\gbar_+(n)$ and destroyed at $\gbar_-(n)$.
-When $\gbar$ is reduced beyond $\gbar_+(n)$, $n-n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\gbar$ is increased beyond $\gbar_-(n)$, $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
-Let us briefly recap our observations regarding $\gbar_+(n)$ and $\gbar_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
-For $n>1$ there are the following relations:
+Let \(\bar g_+(n)\) and \(\bar g_-(n)\) denote the left and right parameter borders on \(\bar g\) where stable \(n-n\) solutions exist.
+That is, as \(\bar g\) is increased stable \(n-n\) solutions are created at \(\bar g_+(n)\) and destroyed at \(\bar g_-(n)\).
+When \(\bar g\) is reduced beyond \(\bar g_+(n)\), \(n-n\) solutions bifurcate into \((n-1)-(n-1)\) solutions, while when \(\bar g\) is increased beyond \(\bar g_-(n)\), \(n-n\) solutions bifurcate into \((n+1)-(n+1)\) solutions.
+Let us briefly recap our observations regarding \(\bar g_+(n)\) and \(\bar g_-(n)\) from the numerical bifurcation diagram in \cref{fig:folds}B.
+For \(n>1\) there are the following relations:
 \begin{align}
-  \gbar_+(n)                  & < \gbar_-(n)\label{eq:easy1},                                       \\
-  \gbar_+(n)                  & < \gbar_+(n+1)\text{ and } \gbar_-(n)<\gbar_-(n+1)\label{eq:easy2}, \\
-  \gbar_+(n+1)                & < \gbar_-(n)\label{eq:coexistence},                                 \\
-  \gbar_-(n+1) - \gbar_+(n+1) & < \gbar_-(n) - \gbar_-(n)\label{eq:robustness}.
+	\bar g_+(n)                   & < \bar g_-(n)\label{eq:easy1},                                         \\
+	\bar g_+(n)                   & < \bar g_+(n+1)\text{ and } \bar g_-(n)<\bar g_-(n+1)\label{eq:easy2}, \\
+	\bar g_+(n+1)                 & < \bar g_-(n)\label{eq:coexistence},                                   \\
+	\bar g_-(n+1) - \bar g_+(n+1) & < \bar g_-(n) - \bar g_-(n)\label{eq:robustness}.
 \end{align}
 \Cref{eq:easy1,eq:easy2} are self-explanatory.
-\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n-n$ and $(n+1)-(n+1)$ solutions.
-\Cref{eq:robustness} implies that the parameter interval on $\gbar$ of $n-n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
+\Cref{eq:coexistence} formally describes occurrence of co-existence between stable \(n-n\) and \((n+1)-(n+1)\) solutions.
+\Cref{eq:robustness} implies that the parameter interval on \(\bar g\) of \(n-n\) solutions decreases with \(n\), in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
 All of the above relations are reminiscent of the period increment bifurcations with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
 	see][]{gardini2012,tramontana2012,avrutin2011,gardini2012}.
-While our maps $\Pi_n$ are fully continuous, the above observation suggests that
-a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
+While our maps \(\Pi_n\) are fully continuous, the above observation suggests that a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
 We will explore what such a map might look like in the discussion.
 
-Let us now find algebraic equations that will allow us to calculate the critical parameters $\gbar_+(n)$ and $\gbar_-(n)$ associated with the period increment bifurcations.
+Let us now find algebraic equations that will allow us to calculate the critical parameters \(\bar g_+(n)\) and \(\bar g_-(n)\) associated with the period increment bifurcations.
 % BUG: Maybe don't call it period-increment here?
-Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\gbar$:
+Recall that the period \(P_n\) derived from the fixed points of \(\Pi_n\) is an increasing function of \(\bar g\):
 \begin{equation}
-  \dv{P_{n}}{\gbar}=2\dv{F_n(\phi_n(\gbar), \gbar)}{\gbar}>0,
+	\dv{P_{n}}{\bar g}=2\dv{F_n(\phi_n(\bar g), \bar g)}{\bar g}>0,
 \end{equation}
-that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the quiet cell, and $\delt$ becomes larger.
-Once $\delt=T$, the free cell can produce another spike and the solution bifurcates into a $(n+1)-(n+1)$ solution.
-Note, however, that at $\gbar_+(n)$ the bifurcation into a $(n-1)-(n-1)$ does not occur when $\delt=0$.
-Here the mechanism is different: A sufficient reduction of $\gbar$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the quiet cell to be released one spike earlier.
+that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the \quiet{} cell, and \(\Delta t\) becomes larger.
+When \(\Delta t > T_{inact}\), the \free{} cell can produce another spike and the solution bifurcates into a \((n+1)-(n+1)\) solution.
+Note, however, that at \(\bar g_+(n)\) the bifurcation into a \((n-1)-(n-1)\) does not occur at \(\Delta t = 0\).
+Here the mechanism is different: A sufficient reduction of \(\bar g\) causes the total synaptic conductance to drop below the release conductance in the \emph{previous} \(ISI\), which allows the \quiet{} cell to be released one spike earlier.
 
-Using the above reasoning we can now formulate the conditions for both bifurcations at $\gbar_+(n)$ and $\gbar_-(n)$.
-As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $\dstar_f=\phi_n(\gbar)$ (\cref{eq:phi}).
-At the right bifurcation border $\gbar_-(n)$ we have $\delt=T$, and after substituting our $F_{n}$-map (\cref{eq:Fn-map}) this translates into
+Using the above reasoning we can now formulate the conditions for both bifurcations at \(\bar g_+(n)\) and \(\bar g_-(n)\).
+As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by \(d^\star_f=\phi_n(\bar g)\) (\cref{eq:phi}).
+At the right bifurcation border \(\bar g_-(n)\) we have \(\Delta t=T_{inact}\), and after substituting our \(F_n\) map (\cref{eq:Fn-map}) this translates into
 \begin{equation}
-  F_n(\phi_n(\gbar), \gbar) = T,
+	F_n(\phi_n(\bar g), \bar g) = T_{inact},
 \end{equation}
@@
 	\label{eq:R}
-  R_{n}(\gbar):=F_n(\phi_n(\gbar), \gbar)-T,
+	\mathcal{R}_{n}(\bar g):=F_n(\phi_n(\bar g), \bar g)-T_{inact},
 \end{equation}
-whose root is the desired right bifurcation border $\gbar_-(n)$.
-In case of the left bifurcation border at $\gbar_+(n)$ the release condition is satisfied just before the free cell has produced its $n$th spike, and after the depression variable has been reset $n-1$ times, which gives the condition
+whose root is the desired right bifurcation border \(\bar g_-(n)\).
+% NOTE: @CONOR: After changing the model I'm not sure anymore whether the next equation is clear from my explanation or I need another sentence.
+In case of the left bifurcation border at \(\bar g_+(n)\), the release condition is satisfied just before the \free{} cell has produced its \(n\)th spike, where total synaptic conductance is given by
 \begin{equation}
-  \gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} = \gstar,
+	\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{inact}/\tau_\kappa} = g^\star,
 \end{equation}
-and can be rewritten as a function
+which can be rewritten as a function
 \begin{equation}
 	\label{eq:L}
-  L_{n}(\gbar):=\gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} -\gstar,
+	\mathcal{L}_n(\bar g):=\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{inact}/\tau_\kappa} -g^\star,
 \end{equation}
-whose root is $\gbar_+(n)$.
-Both $R_{n}$ and $L_{n}$ are increasing with respect to $\gbar$, which makes finding their roots numerically straightforward.
+whose root is \(\bar g_+(n)\).
+Both \(\mathcal{R}_n\) and \(\mathcal{L}_n\) are increasing with respect to \(\bar g\), which makes finding their roots numerically straightforward.
 
-\Cref{fig:final-bif} shows the period $P_n(\gbar)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\gbar \in [\gbar_+(n),\gbar_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
-Note that the width of $n-n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
-That is, bursts with more spikes occur on increasingly smaller intervals of $\gbar$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
-We also note the occurrence of bi-stability between pairs of $n-n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in \cref{eq:coexistence}.
+\Cref{fig:final-bif} shows the period \(P_n(\bar g)\) as predicted by the fixed points of \(\Pi_n\) (\cref{eq:period}) plotted on their respective intervals \(\bar g \in [\bar g_+(n),\bar g_-(n)]\) (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
+Note that the width of \(n-n\) branches decreases with \(n\), which confirms the inequality in \cref{eq:robustness}.
+That is, bursts with more spikes occur on increasingly smaller intervals of \(\bar g\), which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
+We also note the occurrence of bi-stability between pairs of \(n-n\) and \((n+1)-(n+1)\) branches, which also confirms our initial observation in
+\cref{eq:coexistence}.
 
-As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate for $n>1$.
-Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be $\gbar \approx 0.592\si{mS/cm^2}$ in \cref{fig:release-delay}.
-The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\gbar_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
-However, even for branches of large $n-n$ solutions there is a mismatch between the bifurcation borders.
-Presumably our assumptions on the time scales of $w$ and $s$ dynamics do not hold here, and can only be captured by more complex approximations.
+As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate for \(n>1\).
+Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be \(\bar g \approx 0.592\si{mS/cm^2}\) in \cref{fig:release-delay}.
+The mismatch in period for \(1-1\) solutions, but also the mismatch in the left bifurcation border \(\bar g_-(n=2)\) of the \(2-2\) solution can be attributed to the violation of that assumption.
+However, even for branches of large \(n-n\) solutions there is a mismatch between the bifurcation borders.
+Presumably our assumptions on the time scales of \(w\) and \(s\) dynamics do not hold here, and can only be captured by more complex approximations.
 Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.
-
-\end{document}

### 2022-03-07 tex/response.tex
Refactor a bunch of plots

\documentclass[utf8]{frontiers_suppmat} % for all articles
\usepackage{url,hyperref,lineno,microtype}
\usepackage[onehalfspacing]{setspace}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{xr}
\graphicspath{{../figures/}}
\externaldocument{draft}

\renewcommand{\d}{\mathrm{d}}
\renewcommand{\k}{\mathrm{K}}
\newcommand{\ca}{\mathrm{Ca}}
\newcommand{\na}{\mathrm{Na}}
\newcommand{\leak}{\mathrm{L}}
\newcommand{\dstar}{d^\star}
\newcommand{\gstar}{g^\star}
\newcommand{\gbar}{\bar g}
\newcommand{\delt}{\Delta t}
\newcommand{\taus}{\tau_s}
\newcommand{\dn}{\delta_n}
\newcommand{\taud}{\tau_d}

% Leave a blank line between paragraphs instead of using \\

\begin{document}
\onecolumn
\firstpage{1}

\title[Response]{{\helveticaitalic{Response}}}
\maketitle

% TODO: Add line numbers everywhere.
\section{Minor changes}
\subsection{Changes to the nullclines plot}
In order to reduce the number of figures we have merged figures 1 and 5, and adjusted added a paragraph describing the non-zero constant synaptic conductance case at the end of the methods part.

\section{Release delay}
Due to the changes to the single cell model parameters, i.e. reducing the applied current from $I=6 \si{\mu A/cm^{2}}$ to $I=3.8\si{\mu A/cm^{2}}$, the $v$-nullcline moved down along the $w$-nullcline.
% I've checked that old HB value manually, should be correct.
This made the system become more excitable, that is the subcritical Andronov-Hopf bifurcation point where the fixed point changes stability moved from $\bar g=0.038$ to $\bar g=0.0038$.
As a consequence, the release delay seen previously is now negligible for all $n:n$ solutions, see figure \cref{fig:release-delay}.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\textwidth]{release-delay.pdf}
  \caption{Numerically computed graph of the release delay as a function of $\bar g$~\label{fig:release-delay}}
\end{figure}

\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
\bibliography{bibliography.bib}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2022-03-07 tex/manuscript.tex
Refactor a bunch of plots

--- 2022-02-04 tex/manuscript.tex
@@
 \usepackage{lineno}
+
+% Define terms for "free"/"quiet"
+\newcommand{\free}{free}
+\newcommand{\suppressed}{suppressed}
 
@@
 \def\Authors{Mark Olenik\,$^{1,*}$, and Conor Houghton\,$^{2}$}
-% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
-% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
 \def\Address{$^{1}$School of Biological Sciences, Faculty of Life Sciences, University of Bristol, Bristol, United Kingdom \\
 $^{2}$School of Computer Science, Electrical and Electronic Engineering, and Engineering Mathematics, Faculty of Engineering, University of Bristol, Bristol, United Kingdom}
-% The Corresponding Author should be marked with an asterisk
-% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
 \def\corrAuthor{Mark Olenik}
@@
   \section{}
-  Short-term synaptic plasticity is found in many areas of the central nervous system.  In
-  the inhibitory half-centre central pattern generators involved in locomotion, synaptic
-  depression is believed to act as a burst termination mechanism, allowing networks to
-  generate anti-phase bursting patterns of varying periods.  To better understand burst
-  generation in these central patter generators, we study a minimal network of two neurons
-  coupled through depressing synapses.  Depending on the strength of the synaptic
-  conductance between the two neurons, this network can produce symmetric $n-n$ anti-phase
-  bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions
-  increasing with the strength of the synaptic conductance.  Relying on the timescale
-  disparity in the model, we reduce the eight-dimensional network equations to a
-  fully-explicit scalar Poincaré burst map.  This map tracks the state of synaptic
-  depression from one burst to the next and captures the complex bursting dynamics of the
-  network.  Fixed points of this map are associated with stable burst solutions of the
-  full network model, and are created through fold bifurcations of maps.  We derive
-  conditions that describe period-increment bifurcations between stable $n-n$ and
-  $(n+1)-(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
-  Predictions of the Poincaré map fit excellently with numerical simulations of the full
-  network model and allow the study of parameter sensitivity for rhythm generation.
+  Short-term synaptic plasticity is found in many areas of the central nervous system.
+  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
+  To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
+  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n-n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
+  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
+  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
+  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
+  We derive conditions that describe period-increment bifurcations between stable $n-n$ and $(n+1)-(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
+  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.
 
@@
   \includegraphics{fig/nullclines-uncoupled.pdf}
-  \caption{Periodic solution of relaxation-oscillator model neuron.
-$\bm{\mathrm{(A)}}$ Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue, $v_\infty$) and $w$-nullcline (orange, $w_\infty$).
-Unstable fixed point $p_{f}$ is indicated by an orange dot.
-$\bm{\mathrm{(B)}}$ Corresponding voltage trace $v(t)$ of an action potential.~\label{fig:nullclines}}
+  \caption{Periodic solution of relaxation-oscillator model neuron. $\bm{\mathrm{(A)}}$
+    Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue,
+    $v_\infty$) and $w$-nullcline (orange, $w_\infty$). Unstable fixed point $p_{f}$
+    is indicated by an orange dot. $\bm{\mathrm{(B)}}$ Corresponding voltage trace
+    $v(t)$ of an action potential.~\label{fig:nullclines}}
 \end{figure}
@@
   \includegraphics{fig/depression-traces.pdf}
-  \caption{Solution profiles of a $4-4$ burst.
-$\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange).
-$\bm{\mathrm{(B)}}$ Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell 1.~\label{fig:depression-traces}}
+  \caption{Solution profiles of a $4-4$ burst. $\bm{\mathrm{(A)}}$ Membrane potentials
+    of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange). $\bm{\mathrm{(B)}}$
+    Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell
+    1.~\label{fig:depression-traces}}
 \end{figure}
@@
   \includegraphics{fig/burst-sols.pdf}
-  \caption{Voltage traces of both cells of numerically stable solutions for increasing values of the coupling strength $\gbar$ (increasing top to bottom).~\label{fig:burst-sols}}
+  \caption{Voltage traces of both cells of numerically stable solutions for increasing
+    values of the coupling strength $\gbar$ (increasing top to
+    bottom).~\label{fig:burst-sols}}
 \end{figure}
@@
   \includegraphics{fig/bif-diagram.pdf}
-  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for increasing coupling strength $\gbar$.
-$\bm{\mathrm{(A)}}$ Period of stable solutions.
-Dashed lines show the interval between the $5-5$ and the suppressed solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals of $\gbar$.
-$\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in $\mathrm{(A)}$.
-Long $ISI$s are associated with the quiet phase of a burst, short $ISI$s with the free phase.
-During the free phase, $ISI$s are of approximately constant duration $T$.\label{fig:bif-diagram}}
+  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for
+    increasing coupling strength $\gbar$. $\bm{\mathrm{(A)}}$ Period of stable
+    solutions. Dashed lines show the interval between the $5-5$ and the suppressed
+    solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals
+    of $\gbar$. $\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in
+    $\mathrm{(A)}$. Long $ISI$s are associated with the quiet phase of a burst, short
+    $ISI$s with the free phase. During the free phase, $ISI$s are of approximately
+    constant duration $T$.\label{fig:bif-diagram}}
 \end{figure}
@@
   \includegraphics{fig/nullclines-coupled.pdf}
-  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar s$.
-For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange point).
-Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until $p_{f}$ changes stability (half orange,  half blue point) at some critical total conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
+  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the
+  $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar
+  s$. For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange
+  point). Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until
+  $p_{f}$ changes stability (half orange,  half blue point) at some critical total
+  conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for
+  $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
 \end{figure}
@@
   \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
-  \caption{Numerically computed values of the release delay for varying $\gbar$.
-Each of the three branches (A, B, C) also shows the timecourse of the total synaptic conductance $\gbar s$ of a sample stable solution of both cells (blue and orange), as well as the release conductance $g^{\star}$ (dashed green line).
-$\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution.
-Here the quiet cell only spikes after a significant release delay.
-$\bm{\mathrm{(B)}}$ Branch with a long release delay associated with a subset of $2-2$ solutions.
-Here the release condition is briefly satisfied after the first spike of cell 1.
-This does not cause firing of cell 2, which only occurs after the second spike of cell 1.
-$\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is approximately zero and the release condition is sufficient for firing of cell 2.
+  \caption{Numerically computed values of the release delay for varying $\gbar$. Each of
+    the three branches (A, B, C) also shows the timecourse of the total synaptic
+    conductance $\gbar s$ of a sample stable solution of both cells (blue and orange),
+    as well as the release conductance $g^{\star}$ (dashed green line).
+    $\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution. Here the quiet
+    cell only spikes after a significant release delay. $\bm{\mathrm{(B)}}$ Branch with
+    a long release delay associated with a subset of $2-2$ solutions. Here the release
+    condition is briefly satisfied after the first spike of cell 1. This does not cause
+    firing of cell 2, which only occurs after the second spike of cell 1.
+    $\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is
+    approximately zero and the release condition is sufficient for firing of cell 2.
     ~\label{fig:release-delay}}
@@
     $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
-The grey patches depict inter-burst-intervals $\delt$.
-$\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$.
-$\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
+    The grey patches depict inter-burst-intervals $\delt$. $\bm{\mathrm{(B)}}$ Total
+    synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance
+    $g^{\star}$. $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell
+    1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
 \end{figure}
@@
   \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
-Each continuous branch is associated with a stable $n-n$ burst solution.
-Increasing $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx T$.~\label{fig:delta-t}}
+    Each continuous branch is associated with a stable $n-n$ burst solution. Increasing
+    $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
+    T$.~\label{fig:delta-t}}
 \end{figure}
@@
   \includegraphics{fig/FQ-map.pdf}
-  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$.
-Curves $F_n$ intersect at $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
+  \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for
+  $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at
+  $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
 \end{figure}
@@
   \includegraphics{fig/Pn-map.pdf}
-  \caption{Map $\Pi_{n}:d^{\star}$.
-$\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$ at $\gbar=0.6$ $\si{mS/cm^{2}}$.
-$\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$.
-The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
+  \caption{Map $\Pi_{n}:d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$
+  at $\gbar=0.6$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
+  varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$. The identity function is
+  illustrated by a diagonal line.~\label{fig:Pn-map}}
 \end{figure}
@@
   \includegraphics{fig/folds.pdf}
-  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves) and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
-$\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the corresponding solution period from numerical integration of the system of ODEs (orange).~\label{fig:folds}}
+  \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves)
+    and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
+    $\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the
+    corresponding solution period from numerical integration of the system of ODEs
+    (orange).~\label{fig:folds}}
 \end{figure}
@@
   \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
-  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
+  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from
+    fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in
+    \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of
+    the ODEs (orange).~\label{fig:final-bif}}
 \end{figure}

### 2022-03-07 tex/sections/discussion.tex
Refactor a bunch of plots

--- 2022-02-04 tex/sections/discussion.tex
@@
 As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses.
-In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.
+In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g.
+see][]{kuehn2015}.
 

### 2022-03-07 tex/sections/methods.tex
Refactor a bunch of plots

--- 2022-02-04 tex/sections/methods.tex
@@
-\documentclass[../manuscript.tex]{subfiles}
-\graphicspath{{../figures/}}
-
-\begin{document}
-We consider a pair of identical Morris-Lecar neurons~\citep{morris1981}, with parameters
-adapted from~\cite{bose2011}.  The Morris-Lecar model is a set of two first-order
-differential equations that describe the membrane dynamics of a spiking neuron.  The
-depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation
-by a slow potassium current and a leak current.  The membrane potential $v_{i}$ and
-potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
-\begin{align}
-  ~\label{eq:cell-modelA}
+\section{Materials and Methods}
+We consider a pair of identical Morris-Lecar neurons \citep{morris1981}, with parameters adapted from \cite{bose2011}.
+The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
+The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
+The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by: \begin{align}
+	\label{eq:cell-modelA}
 	\dot v_{i} & = f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}), \\
-  ~\label{eq:cell-modelB}
+	\label{eq:cell-modelB}
 	\dot w_{i} & =h(v_i,w_i).
 \end{align}
-Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal
-synaptic conductance and the synaptic gating, respectively, constituting the total
-inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.  Function $f(v_{i},
-w_{i})$ describes the membrane currents of a single cell:
+Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.
+Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
 \begin{equation}
-  ~\label{eq:memcur}
-  f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})-g_{\leak}(v_{i}-v_{\leak}) + I.
+	\label{eq:memcur}
+	f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})
+	-g_{\leak}(v_{i}-v_{\leak}) + I.
 \end{equation}
-The currents include a constant current $I$, and three ionic currents: an instantaneous
-calcium current, a potassium current, and a leak current, with respective reversal
+The currents include a constant current $I$, and three ionic currents: an instantaneous calcium current, a potassium current, and a leak current, with respective reversal
 potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances
-$g_{\ca}$, $g_{\k}$, and $g_{\leak}$.  The function $h(v_{i}, w_{i})$ models the kinetics
-of the potassium gating variable $w_{i}$, and is given by
+$g_{\ca}$, $g_{\k}$, and $g_{\leak}$.  The function $h(v_{i}, w_{i})$ models the
+kinetics of the potassium gating variable $w_{i}$, and is given by
 \begin{equation}
@@
 \end{equation}
-The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default
-model parameters are described in the \textbf{Supplementary Material S1}.
+The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the \textbf{Supplementary Material S1}.
 
-The dynamics of the synaptic interactions between the neurons are governed by a synaptic
-gating variable $s_{i}$ and a depression variable $d_{i}$:
-\begin{linenomath}
-  \begin{align}
-    \dot d_{i} & =
-    \begin{cases}
-      (1-d_{i})/\tau_a\text{ if }v_i<v_\theta, \\
-      -d_{i}/\tau_b\text{ if }v_i>v_\theta,
-    \end{cases}\label{eq:dot-d} \\
-    \dot s_{i} & =
-    \begin{cases}
-      -s_i/\tau_\kappa\text{ if }v_i<v_\theta, \\
-      (d_i-s_i)/\tau_\gamma\text{ if }v_i>v_\theta.
-    \end{cases}\label{eq:dot-s}
-  \end{align}
-\end{linenomath}
+The dynamics of the synaptic interactions between the neurons are governed by a synaptic gating variable $s_{i}$ and a depression variable $d_{i}$:
+\begin{numcases}{\dot d_{i} = }
+	(1-d_{i})/\tau_{a} &  if $v_{i}<v_{\theta}$,\label{eq:dot-d-up}
+	\\
+	-d_{i}/\tau_{b}    &  if $v_{i}>v_{\theta}$,\label{eq:dot-d-down}
+\end{numcases}
+
+\begin{numcases}{\dot s_{i} = }
+	-s_{i} / \tau_{\kappa} & if $v_{i}<v_{\theta}$,\label{eq:dot-s-down}
+	\\
+	0                & if $v_{i}>v_{\theta}$.\label{eq:dot-s-up}
+\end{numcases}
+
+% TOD: Needs EDITING
 Variable $d_{i}$ describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
 The model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
-When the voltage is below firing threshold, depression variable $d_i$ recovers with time constant $\tau_a$, while synaptic variable $s_i$ decays with time constant $\tau_\kappa$.
-% TODO Maybe mention that this topic will be discussed in the appendix or later.
-Because synaptic depression occurs on a much slower timescale than synaptic inhibition, we assume $\tau_d\gg\tau_\kappa$.
-When the voltage is above firing threshold, variable $d_i$ decays to zero with $\tau_b$, while $s_i$ quickly approaches the respective value of $d_i$.
-Since $\tau_\gamma$ is the shortest time constant of the system with $\tau_\gamma \ll 1$, we can assume that whenever $v>v_\theta$ we can we have $s_i=d_i$.
-The equations for the depression model were adapted from the~\citet{bose2001} model.
-These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by~\citet{tsodyks1997}.
+When the voltage of cell $i$ is above firing threshold ($v_i>v_\theta$), variable $d_i$ decays with time constant $\tau_b$, and recovers with time constant $\tau_a$ when voltage is below firing threshold ($v_i < v_\theta$).
+Since the synaptic inhibition occurs on a much faster timescale than synaptic depression, we assume that $s_i$ is instantaneously reset to $d_i$ whenever $v_i$ increases above $v_\theta$, where it remains throughout $v_i > v_\theta$.
+Whenever $v_i < v_\theta$, the synaptic variable decays exponentially with time constant $\tau_\kappa$.
+The equations for the depression model were adapted from the \citet{bose2001} model.
+These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by \citet{tsodyks1997}.
 
-When the cells are uncoupled ($\gbar=0$), the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
-The two curves intersect along the middle branch of $v_{\infty}$, creating an unstable fixed point $p_{f}=(v_{f},w_{f})$ with a surrounding stable limit cycle of period $T=T_{act}+T_{inact}$ (\cref{fig:nullclines}A).
+When the total inhibitory conductance $g = \bar g s$ is constant, the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
+In case of no inhibition ($g=0$), the two curves intersect near the local minimum of $v_{\infty}$ to the left of $v_{\theta}$ (commonly referred to as ``left knee'' of $v_{\infty}$), creating an unstable fixed point with a surrounding stable limit cycle of period $T=T_{act}+T_{inact}$ (\cref{fig:nullclines}A).
 Here $T_{act}$ is the amount of time the cell spends in the active state when $v>v_\theta$, while $T_{inact}$ is the time it spends in the silent state when $v<v_\theta$.
@@
 During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
+In the case of a non-zero inhibition ($g>0$) the location of $v_{\infty}$ depends on the exact value of $g$.
+Increasing $g$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point down $w_{\infty}$ in the $(v-w)$ -plane.
+When $g$ is large enough, the fixed point moves past the left knee and becomes stable via a subcritical Andoronov-Hopf bifurcation, attracting all previously periodic trajectories.
+In the following section we will refer to the value of the total conductance at the bifurcation as $g_{HB}$.
 
@@
 Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
-
-\end{document}

### 2022-03-07 tex/sections/results.tex
Refactor a bunch of plots

--- 2022-02-04 tex/sections/results.tex
@@
-\documentclass[../manuscript.tex]{subfiles}
-\graphicspath{{../figures/}}
-
-\begin{document}
-
+\section{Results}
 \subsection{Anti-phase burst solutions}
-Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism~\citep{brown1911} and is known to produce $n-n$ anti-phase burst solutions of varying period.
+Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism \citep{brown1911} and is known to produce $n-n$ anti-phase burst solutions of varying period.
 Such $n-n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
@@
 While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
+% FIXME: This isn't consistent with Bose, that needs to be mentioned
 Therefore, at any given moment one cell is spiking while the other is inhibited.
-Consistent with~\citet{bose2011} we will refer to the currently firing cell as ``free'' and we will call the inhibited cell ``quiet''.
+Consistent with \citet{bose2011} we will refer to the currently firing cell as ``\free{}'' and we will call the inhibited cell ``\suppressed{}''.
 Additionally, we will distinguish between two phases of a $n-n$ solution:
-We will refer to the burst duration of a cell as the ``free phase'', which is the time between the first spike and the last spike in a burst.
-And we will call the remaining duration of a cycle, when a cell is not spiking, the ``quiet phase''.
+We will refer to the time interval when a cell is firing as the ``\free{} phase'', and we will call the remaining duration of a cycle, when a cell is not firing, the ``\suppressed{}  phase''.
 
 % TODO: Add mention of gstar. Once critical conductance is crossed, cell is released.
-With each action potential of the free cell, short-term depression leads to a step-wise decrease of $d$, and consequently of $s$ (\cref{fig:depression-traces}B).
-If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\gbar s$ will eventually become sufficiently small to allow for the quiet cell to be released and start firing, thus inhibiting the previously free cell.
-While a cell is quiet its depression variable can recover.
-Once the quiet cell becomes free again its synaptic inhibition will be sufficient to terminate the burst of the previously free cell and commence a new cycle.
-As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\gbar$ determines the type of $n-n$ solution.
-Increasing $\gbar$ produces higher $n-n$ burst solutions with more spikes per burst and a longer cycle period.
-\Cref{fig:burst-sols} shows numerically stable $n-n$ solutions for varying values of $\gbar$.
-For small values of $\gbar$ the network produces anti-phase spiking $1-1$ solutions.
-As $\gbar$ is increased the network generates solutions of increasing $n$, that is $2-2$, $3-3$, and $4-4$.
-When $\gbar$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
+With each action potential of the \free{} cell, short-term depression leads to a step-wise decrease of $d$, and consequently of $s$ (\cref{fig:depression-traces}B).
+If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\bar g s$ will eventually become sufficiently small to allow for the \suppressed{} cell to be released and start firing, thus inhibiting the previously \free{} cell.
+While a cell is \suppressed{} its depression variable can recover.
+Once the \suppressed{} cell becomes \free{} again its synaptic inhibition will be sufficient to terminate the burst of the previously \free{} cell and commence a new cycle.
+% BUG: This is not 100% true, gbar AND the initial conditions uniquely determine the type of n-n pattern.
+As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\bar g$ determines the type of $n-n$ solution.
+Increasing $\bar g$ produces higher $n-n$ burst solutions with more spikes per burst and a longer cycle period.
+\Cref{fig:burst-sols} shows numerically stable $n-n$ solutions for varying values of $\bar g$.
+For small values of $\bar g$ the network produces anti-phase spiking $1-1$ solutions.
+As $\bar g$ is increased the network generates solutions of increasing $n$, that is $2-2$, $3-3$, and $4-4$.
+When $\bar g$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
 Depending on the initial conditions either of the two cells can become the suppressed cell, which is why the suppressed solution is numerically bistable.
 
-Branches of numerically stable $n-n$ solutions and their associated limit cycle period for varying values of $\gbar$ are depicted in \cref{fig:bif-diagram}A (see  \textbf{Supplementary Material S2} for algorithm description).
-Not only do higher $n-n$ solutions branches require stronger coupling $\gbar$, but also within $n-n$ branches the period increases with $\gbar$.
+Branches of numerically stable $n-n$ solutions and their associated limit cycle period for varying values of $\bar g$ are depicted in \cref{fig:bif-diagram}A (see \textbf{Supplementary Material S2} for algorithm description).
+Not only do higher $n-n$ solutions branches require stronger coupling $\bar g$, but also within $n-n$ branches the period increases with $\bar g$.
 In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2-2$ and $3-3$ solution branches.
-Branches of higher $n-n$ burst solutions occur on increasingly smaller intervals of $\gbar$, for instance is the $\gbar$ interval of the $5-5$ branch shorter than that of the $4-4$ branch and so on.
+Branches of higher $n-n$ burst solutions occur on increasingly smaller intervals of $\bar g$, for instance is the $\bar g$ interval of the $5-5$ branch shorter than that of the $4-4$ branch and so on.
 The interval between the $5-5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n-n$ solutions, such as $11-11$ bursts, but also other non-symmetric $n-m$ solutions as well irregular, non-periodic solutions.
@@
 \subsection{Mathematical analysis of two-cell network}
-~\label{sec:assumptions}
+\label{sec:assumptions}
 % Summary of assumptions
-The goal of the following mathematical analysis is to reduce the complexity of the eight-dimensional system to some easily tractable quantity.
+The goal of the following mathematical analysis is to reduce the complexity of the
+eight-dimensional system to some easily tractable quantity.
 As we will see later this quantity is the value of the depression variable $d$ of either of the two cells.
-We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the free phase, and then during the quiet phase.
+We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the \free{} phase, and then during the \suppressed{} phase.
 This construction will require two assumptions about the membrane and synaptic dynamics.
-The first assumption states that during a burst the free cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
-The second assumption states that once the inhibitory conductance acting on the quiet cell drops below a critical threshold, the cell is immediately released and fires.
-The second assumption is necessary to predict the release time of the quiet cell, which allows us to model the recovery of $d$ during the quiet phase.
-In other words, the second assumption requires that the release of the quiet cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the quiet cell.
+The first assumption states that during a burst the \free{} cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
+The second assumption states that once the inhibitory conductance acting on the \suppressed{} cell drops below a critical threshold, the cell is immediately released and fires.
+The second assumption is necessary to predict the release time of the \suppressed{} cell, which allows us to model the recovery of $d$ during the \suppressed{} phase.
+In other words, the second assumption requires that the release of the \suppressed{} cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the \suppressed{} cell.
 Both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
@@
 % Assumption 1: Free phase
-Our first assumption about the model states that the free cell fires at its uncoupled period $T$, that is, during the free phase of a burst we have $ISI=T$.
+% FIXME: Probably good idea to remove IBI reference here (and in figure).
+Our first assumption about the model states that the \free{} cell fires at its uncoupled period $T$, that is, during the \free{} phase of a burst we have $ISI=T$.
 Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
 We can further numerically confirm this observation by capturing the $ISI$s of the stable solutions from the bifurcation diagram in \cref{fig:bif-diagram}A.
-In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the quiet phase of the burst.
-$IBI$s lie on multiple branches, each branch associated with a stable $n-n$ solution, and are monotonically increasing with $\gbar$.
-In contrast, $ISI$s are calculated from the spikes within the free phase and do not vary significantly with $\gbar$, but are approximately $ISI\approx T$, affirming our first assumption.
-Assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the free phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
-Assuming $ISI=T$ seems reasonable given that inhibition acting on the quiet cell decays exponentially to zero on a much shorter timescale than the duration of the $ISI$, and therefore, once the quiet cell is released its trajectory quickly approaches the spiking limit cycle.
+In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the \suppressed{} phase of the burst.
+$IBI$s lie on multiple branches, each branch associated with a stable $n-n$ solution, and are monotonically increasing with $\bar g$.
+In contrast, $ISI$s are calculated from the spikes within the \free{} phase and do not vary significantly with $\bar g$, but are approximately $ISI\approx T$, affirming our first assumption.
+Assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the \free{} phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
+Assuming $ISI=T$ seems reasonable given that inhibition acting on the \suppressed{} cell decays exponentially to zero on a much shorter timescale than the duration of the $ISI$, and therefore, once the \suppressed{} cell is released its trajectory quickly approaches the spiking limit cycle.
 
 % Assumption 2: Release
-Our second assumption states that the quiet cell is released and spikes as soon as inhibition from the free cell drops below a constant threshold.
-We will now define such a ``release condition'' by exploiting the discrepancy in timescales between the fast membrane dynamics, and the slower synaptic dynamics.
-Let us first consider the dynamics of a single Morris-Lecar neuron.
-We fix the synaptic variable that acts on the cell by setting $s=1$, which also makes the applied synaptic conductance $\gbar s$ constant.
-Recall from \cref{fig:nullclines}A that in case of a single uncoupled cell ($\gbar s=0$), the $v$- and $w$-nullclines intersect at some unstable fixed point $p_{f}=(v_{f},w_{f})$, while trajectories revolve around a stable spiking limit cycle.
-Increasing $\gbar s$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point $p_{f}$ down the sigmoid $w_{\infty}$ in the $(v-w)$-plane (\cref{fig:nullclines-coupled}).
-When $\gbar s$ is large enough, the fixed point $p_{f}$ becomes stable, attracting all previously periodic trajectories.
-There exists a unique value $\gbar s=g^{\star}$ when $p_{f}$ changes stability and the stable limit cycle vanishes.
-Thus, when a constant inhibitory conductance is applied, $\gbar s<g^{\star}$ acts as a necessary condition for a cell to spike.
-In contrast, when $\gbar s>g^{\star}$ inhibition is strong enough to prevent a cell from spiking~\citep{bose2011}.
-
-% NOTE
-% In our parameter range the bifurcations occur via subcritical Hopf (bose2011 p.47)
-
-Now let us analyse the nullclines of the quiet cell when the two cells are coupled via synaptic inhibition with depression.
-Let $\gbar s$ here denote the total synaptic conductance which acts on the quiet cell and is produced by the free cell, and let $p_{f}$ be the fixed point associated with the quiet cell.
-At the start of the burst of the free cell we have $\gbar s > g^{\star}$ and $p_{f}$ is stable.
-When the free cell spikes, $\gbar s$ peaks (\cref{eq:s-reset}), and the $v$-nullcline with the ensuing stable $p_f$ move down the $w$-nullcline.
-Then in between spikes $\gbar s$ decays exponentially (\cref{eq:dot-s}) causing the $v$-nullcline and $p_{f}$ to move up the $w$-nullcline while attracting trajectories of the quiet cell.
-Once depression causes the synaptic conductance to become small enough to satisfy $\gbar s<g^{\star}$ and the quiet cell is released, fixed point $p_{f}$ becomes unstable allowing the quiet cell to fire.
-If the trajectory of the quiet cell remains sufficiently close to the stable $p_{f}$ at the time when it changes stability, then $\gbar s < g^{\star}$ acts as a release condition that is not only necessary, but also sufficient for firing of the quiet cell.
-In this case the release of the quiet cell occurs precisely when
+% TODO: Mention that we will derive the exact value of
+% I don't think we should introduce the g_min notation, instead call g* the minimum value.
+Our second assumption states that the suppressed cell is released and spikes as soon as the total inhibitory conductance $g = \bar g s$ acting on it drops below a constant threshold.
+We call this critical threshold value the ``release conductance'', denoted by $g^\star$, and define it as the value of $g$ at the time when the voltage of the suppressed cell first crosses the firing threshold $v_{\theta}$, that is when that cell is released and fires its first spike.
+Recall from figure ... that when a cell is suppressed its fixed point is stable and $g > g_{HB}$.
+A sufficient condition for the suppressed cell to be released is therefore $g > g_{HB}$ .
+However, depending on the topology of the stable manifold, the trajectory of the suppressed cell can escape the stable fixed point and allow the cell to produce a spike for $g < g_{HB}$.
+This spike will inhibit the previously firing cell and allow cell 2 to take over the role of the firing cell.
+Moreover, there exists a minimal conductance value $g_{min}$ and a condition $g_{tot} > g_{min}$ that is necessary for the trajectory to pass the fixed point and the cell to spike.
+We will derive the exact value of such a $g_{min}$ in the following section, and to simplify the derivation our map assume that $g_{min}$ is a good approximation for the release conductance, therefore setting $g^\star = g_{min}$ .
+This assumption allows us to predict that timing of the release of the suppressed cell, that is precisely when
 \begin{equation}
 	~\label{eq:release}
-  \gbar s=g^{\star}
+	\bar g s=g^{\star}
 \end{equation}
@@
 
-Whether the $(v,w)$-trajectory of the quiet cell can remain close enough to $p_{f}$ to make \cref{eq:release} sufficient for firing depends largely on the coupling strength $\gbar$ and the timescale disparity between membrane dynamics and synaptic dynamics~\citep{bose2011}.
-It is straightforward to test our assumption of a release condition by numerically integrating the full system of ODEs and calculating the time interval between the first spike of the quiet cell and the time when $\gbar s$ first crosses $g^{\star}$.
-We will call this time interval the ``release delay''.
-If our assumption holds, we would expect an approximately zero release delay.
-\Cref{fig:release-delay} shows the numerically computed graph of the release delay for varying $\gbar$.
-The graph shows three distinct branches, next to each branch we also plot the timecourse of a corresponding sample solution of the total synaptic conductance $\gbar s$ of both cells.
-For the rightmost branch where $\gbar>0.592$ $\si{mS/cm^{2}}$ the release delay is approximately zero.
-Here the first spike of the quiet cell can be accurately predicted by the release condition in \cref{eq:release}.
-The leftmost and middle branches for $\gbar<0.592$ $\si{mS/cm^{2}}$  show a release delay greater than zero, the quiet cell does not immediately fire when the release condition is first satisfied, and \cref{eq:release} does not accurately predict the release of the quiet cell.
-The leftmost and middle branches contain $1-1$ and $2-2$ solutions respectively.
-In both cases the coupling $\gbar$ is not sufficiently strong to allow trajectories of the quiet cell to be close enough to $p_{f}$ to guarantee spiking once $\gbar$ crosses $g^{\star}$.
-Note that in the middle branch $\gbar s $ crosses $g^{\star}$ twice, and only after the second crossing does the quiet cell fire.
-The following map construction relies on the assumption that the release condition in \cref{eq:release} can accurately predict the release time of the quiet cell.
-Given our model parameters this is only possible for sufficiently large $\gbar>0.592 $ $\si{mS/cm^{2}}$.
-For completeness, however, we will also consider values $\gbar < 0.592$ $\si{mS/cm^{2}}$ in the following analysis, bearing in mind that in this parameter range our map will not be accurate.
-
-In summary: For $\gbar>0.592$ $\si{mS/cm^{2}}$ the release condition is sufficient to predict when the quiet cell is released.
+% NOTE: Perhaps mention the first assumption here as well.
+In summary: We assume that the release condition is sufficient to predict when the \suppressed{} cell is released.
 Due to the symmetry of $n-n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
 The release time therefore uniquely determines the type of $n-n$ solution.
-Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the quiet cell.
-Instead, the solution of the synaptic variable $s$ of the free cell is sufficient to predict when $\gbar s=g^{*}$ is satisfied.
-Finally, $s$ is solely determined by the evolution of the depression variable $d$ of the free cell.
-Constructing a solution of $d$ during the free phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
+Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the \suppressed{} cell.
+Instead, the solution of the synaptic variable $s$ of the \free{} cell is sufficient to predict when $g=g^{*}$ is satisfied.
+Finally, $s$ is solely determined by the evolution of the depression variable $d$ of the \free{} cell.
+Constructing a solution of $d$ during the \free{} phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
 However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
@@
 \subsection{Construction of the scalar Poincaré map}
-In this section we construct the scalar Poincaré map $\Pi_{n}:d^{\star}\mapsto d^{\star}$.
+In this section we construct the scalar Poincaré map $\Pi_n:d^{\star}\mapsto d^{\star}$.
 Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n-n$ burst.
-The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
-To simplify the map construction we will assume that a free cell fires exactly $n$ times before it becomes quiet.
-Later we will relax this assumption.
-We will construct $\Pi_{n}$ by evolving $d$ first during the free phase and then during the quiet phase of the $n-n$ limit cycle.
-First, let us give explicit definitions of the free and quiet phases.
+The map $\Pi_n$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
+To simplify the map construction we will assume that a \free{} cell fires exactly $n$ times before it becomes \suppressed{}.
+We will construct $\Pi_n$ by evolving $d$ first during the \free{} phase and then during the \suppressed{} phase of the $n-n$ limit cycle.
+First, let us give explicit definitions of the \free{} and \suppressed{} phases.
 A schematic illustration of both phases is given in \cref{fig:free-quiet1}.
 
-Suppose that at $t=0$ cell 1 becomes free with some initial $d(0)$.
-Cell 1 then fires $n$ spikes at the uncoupled period $T=T_{act}+T_{inact}$.
+Suppose that at $t=0$ cell 1 starts \free{} with some initial $d(0)$. Cell 1 then fires $n$ spikes at the uncoupled period $T=T_{act}+T_{inact}$.
 Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
-After $n$ spikes the total conductance $\gbar s(t)$ acting on the quiet cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}, that is at some time $t=(n-1)T + \delt$, where $\Delta t < T_{inact}$, we have $\gbar s(t)=g^{\star}$.
+After $n$ spikes the total conductance $\bar g s(t)$ acting on the \suppressed{} cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}.
+That is at some time $t=(n-1)T + T_{act} + \Delta t$, where $\Delta t < T_{inact}$, we have $\bar g s(t)=g^{\star}$.
 Cell 2 is then released and prevents cell 1 from further spiking.
-Here $\delt$ is the time between the last spike of cell 1 and the first spike of cell 2 ~\citep{bose2011}.
-Once released, cell 2 also fires $n$ spikes until cell 1 becomes free once again at the cycle period.
+Here $\Delta t$ is the time between the last spike of cell 1 and the first spike of cell 2 ~\citep{bose2011}.
+Once released, cell 2 also fires $n$ spikes until cell 1 becomes \free{} once again.
 Let $P_n$ denote the full cycle period of a $n-n$ solution:
@@
 	~\label{eq:P}
-  P_n = 2(n-1)T + 2\delt.
+	P_n = 2\Big( (n-1)T + T_{act} + \Delta t \Big).
 \end{equation}
-We can now define the free and quiet phases of cell 1 explicitly. The free phase is the time interval between the first and last spikes of the burst, that is for time $0<t<(n-1)T$.
-During the free phase of cell 1, the quiet cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\gbar s > g^{\star}$.
-The quiet phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T < t < 2(n-1)T + 2\delt$.
+We can now define the \free{} and \suppressed{} phases of cell 1 explicitly.
+The \free{} phase is the interval that lasts from the first spike time up until the beginning of the inactive phase of the last spike, last spikes of the burst, that is for time $0<t<(n-1)T + T_{act}$.
+During the \free{} phase of cell 1, the \suppressed{} cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\bar g s > g^{\star}$.
+The \suppressed{} phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T + T_{act} < t < P_n$.
+Hence the \suppressed{} phase lasts for $(n-1)T + T_{act} + 2\Delta t$.
 
-Note that only the quiet phase depends on $\delt$ which will play a central role in the construction of $\Pi_{n}$.
-From \cref{eq:P} $\delt$ can be be computed as
+Note that only the \suppressed{} phase depends on $\Delta t$, which will play a central role in the construction of $\Pi_n$.
+From \cref{eq:P} $\Delta t$ can be computed as
 \begin{equation}
-  ~\label{eq:delta-t-P}
-  \delt = \frac{1}{2}P_n - (n-1)T.
+	\label{eq:delta-t-P}
+	\Delta t = \frac{1}{2}P_n - (n-1)T - T_{act}.
+\end{equation}
+We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n-n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\Delta t$ as a function of $\bar g$ (\cref{fig:delta-t}).
+Each continuous branch of $\Delta t$ is monotonically increasing and corresponds to a $n-n$ burst:
+Stronger coupling $\bar g$ increases the total synaptic conductance $\bar g s$ that acts on the \suppressed{} cell, thus delaying its release.
+It is easy to see that for any $n$-branch we have $\Delta t < T_{inact}$:
+Once $\Delta t$ crosses $T_{inact}$, the \free{} cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1)-(n+1)$ burst.
+
+Distinguishing between the \free{} and \suppressed{} phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
+As can be seen from \cref{fig:free-quiet1}C, during the \free{} phase $d$ depresses when $v > v_\theta$ and recovers when $v < v_\theta$.
+In contrast, during the \suppressed{} phase $d$ only recovers and does not depress.
+Given the initial $d^{\star} = d(0)$ at the beginning of the cycle and the number of spikes in the \free{} phase $n$, we can now construct the burst map $\Pi_n$.
+The map
+\begin{equation}
+	\Pi_n(d^\star)=Q_n\big(F_n(d^\star\big))
 \end{equation}
 \noindent
-We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n-n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\delt$ as a function of $\gbar$ (\cref{fig:delta-t}).
-Each continuous branch of $\delt$ is monotonically increasing and corresponds to a $n-n$ burst:
-Stronger coupling $\gbar$ increases the total synaptic conductance $\gbar s$ that acts on the quiet cell, thus delaying its release.
-It is easy to see that for any $n$-branch we have $\delt<T$:
-Once $\delt$ crosses $T$, the free cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1)-(n+1)$ burst.
-
-Distinguishing between the active and silent phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
-As can be seen from \cref{fig:free-quiet1}C, during the active phase $d$ depresses during the active phase of spikes and recovers during the inactive phases of spikes.
-% TODO need to sort out terminology here, i.e. inactive vs quiet
-In contrast, during the silent phase $d$ only recovers and does not depress.
-Given the initial $d^{\star}=d(0)$ at the beginning of the cycle and the number of spikes in the free phase $n$, we can now construct the burst map $\Pi_{n}$.
-The map
+is a composition of two maps. Map
 \begin{equation}
-  \Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star}\big))
+	F_n:d^\star\mapsto \Delta t
 \end{equation}
-\noindent
-is a composition of two maps.
+models the evolution of $d$ in the \free{} phase.
+$F_n$ takes an initial value $d^{\star}$ and calculates $\Delta t$.
 Map
 \begin{equation}
-  F_{n}:d^{\star}\mapsto \delt
+	Q_n:\Delta t \mapsto d^{\star}
 \end{equation}
-models the evolution of $d$ in the free phase.
-$F_{n}$ takes an initial value $d^{\star}$ and calculates the inter-burst-interval $\delt$.
-Map
-\begin{equation}
-  Q_{n}:\delt \mapsto d^{\star}
-\end{equation}
-models the recovery of $d$ in the quiet phase.
-Given some $\delt$ map $Q_n$ computes $\dstar$ at the start of the next cycle.
+models the recovery of $d$ in the \suppressed{} phase.
+Given some $\Delta t$ map $Q_n$ computes $d^\star$ at the start of the next cycle.
 
-Our aim in the following analysis is to elucidate the properties of $\Pi_{n}$ and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of $\Pi_{n}$ are created.
+Our aim in the following analysis is to elucidate the properties of $\Pi_n$ and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of $\Pi_{n}$ are created.
 To that effect it will be useful to include not only positive, but also negative values of $d^{\star}$ to the domain of $\Pi_{n}$.
 But it is important to add that values $d^{\star}<0$ are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
-Because $\Pi_{n}$ maps first from $d^{\star}$ to $\delt$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n-n$ solutions with partially overlapping bursts.
+Because $\Pi_{n}$ maps first from $d^{\star}$ to $\Delta t$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n-n$ solutions with partially overlapping bursts.
 As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n-n$ solutions of the full system of ODEs only exist for $\Delta t>0$.
@@
 % TODO: Edit par
-We start the construction of $\Pi_n$ by first considering the free phase and building the map $F_n$.
-At each spike time $t_{k}$ where $d(t_k) = d_k$, variable $d$ decays first for the duration of the active phase of the spike for $T_{act}$, as described by the solution to \cref{eq:dot-d}.
+We start the construction of $\Pi_n$ by first considering the \free{} phase and building the map $F_n$.
+At each spike time $t_{k}$ where $d(t_k) = d_k$, variable $d$ decays first for the duration of the active phase of the spike for $T_{act}$, as described by the solution to \cref{eq:dot-d-down}.
 At $t = t_k + T_{act}$ we have
@@
 \end{equation}
-The depression variable then recovers during the inactive phase of the spike until $t_{k+1}$, where for $0<t<T_{inact}$ we get
+The depression variable then recovers during the inactive phase of the spike until $t_{k+1}$, where for $0<t<T_{inact}$:
 \begin{equation}
@@
 \end{equation}
-By substituting $t=T_{inact}$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the free phase:
+By substituting $t=T_{inact}$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the \free{} phase:
 \begin{equation}
@@
 \begin{align}
-  \lambda & = \exp(-T_{act}/\tau_b),    \\
-  \rho    & =\exp(-T_{inact}/\tau_{a}).
+	\lambda & := \exp(-T_{act}/\tau_b), \label{eq:lambda} \\
+	\rho    & :=\exp(-T_{inact}/\tau_{a}). \label{eq:rho}
 \end{align}
@@
 Given constant $T_{act}$ and $T_{inact}$, parameter $\lambda$ determines how much the synapses depresses during the active phase of the spike, while $\rho$ determines how much it recovers during the inactive phase.
-Since $0<\lambda, \rho<1$, map \cref{eq:map-d} is increasing and contracting, with a fixed point at
+Since $0<\lambda, \rho<1$, the map in \cref{eq:map-d} is increasing and contracting, with a fixed point at
 \begin{equation}
@@
 The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
-Using the release condition in \cref{eq:release} allows us to derive the value of the the minimum coupling strength that will produce the full suppressed solution, denoted as $\gbar_{s}$.
-% TODO Explain why s(0) = ds
-% TODO See https://trello.com/c/AYqZIaXh: Would be good to elaborate on the idea that lambda and tau can be
-% viewed as the new time constants in the reduced system.
-Solving \cref{eq:dot-s} for $s(t)$ with $t=T$ and setting the initial value $s(0)=d_{s}$ gives
-\begin{equation}
-  \gbar_{s} d_{s}e^{-T/\tau_\kappa}=g^{\star}.
+Using the release condition in \cref{eq:release} allows us to derive the value of the minimum coupling strength that will produce the full suppressed solution, denoted as $\bar g_{s}$.
+% TODO  Would be good to elaborate on the idea that lambda and tau can be viewed as the new time constants in the reduced system.
+Solving \cref{eq:dot-s-down} for $s(t)$ with $t=T_{inact}$ and setting the initial value $s(0)=d_s\lambda$ gives \begin{equation}
+	\bar g_s d_s\lambda e^{-T_{inact}/\tau_\kappa}=g^{\star}.
 \end{equation}
-By further substituting the definition of $d_{s}$ in~\eqref{eq:dsup} and rearranging, we can write $\gbar_{s}$ as a function of $\lambda$ and $\rho$:
+By further substituting the definition of $d_s$ in~\eqref{eq:dsup} and rearranging, we can write $\bar g_s$ as a function of $\lambda$ and $\rho$:
 \begin{equation}
 	\label{eq:gs}
-  \gbar_{s}(\lambda, \rho) = g^{\star}e^{T/\tau_\kappa}\frac{1-\lambda \rho}{1-\rho}.
+	\bar g_s(\lambda, \rho) = \frac{1/\lambda-\rho}{1-\rho} e^{T_{inact}/\tau_\kappa}g^\star.
 \end{equation}
-Note that the above dependence of $\gbar_{s}$ on $\lambda$ is linear and monotonically decreasing.
-Increasing $\lambda$ reduces the strength of the depression of the free cell.
-This in turn allows the free cell to fully suppress the quiet cell at smaller values of $\gbar$.
+Note that the above dependence of $\bar g_{s}$ on $\lambda$ is linear and monotonically decreasing.
+Increasing $\lambda$ reduces the strength of the depression of the \free{} cell.
+This in turn allows the \free{} cell to fully suppress the \suppressed{} cell at smaller values of $\bar g$.
 
-Solving~\eqref{eq:map-d} gives us the linear map $\delta_{n}:d^{\star}\mapsto
-d_{n}$, that for some initial $d^{\star}$ computes the depression at the $n$th
-spike time, $d_{n}=d(t_{n}^{-})$:
+Solving \cref{eq:map-d} gives us the linear map $\delta_n:d^{\star}\mapsto d_n$, that for some initial $d^\star$ computes the depression at the $n$th spike time, $d_n=d(t_n)$:
 \begin{equation}
-  ~\label{eq:delta-map}
-  \delta_{n}(d^{\star}) = (\lambda \rho)^{n-1} d^{\star} + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}.
+	\label{eq:delta-map}
+	\delta_n(d^\star) = (\lambda \rho)^{n-1} d^\star + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^i.
 \end{equation}
-Since $\lambda < 1$, function $\delta_{n}$ is a linearly increasing function of
-$d^{\star}$ with a fixed point at $d_{s}$ for all $n$.  Having identified $d$ after $n$
-spikes, we can now use the release condition $\gbar s = g^{\star}$ (\cref{eq:release}) to
-find $\delt$.
-% FIXME:
-After the last spike of the free phase at time $t_{n} = (n-1)T$ the synapse variable $s$
-has the value of $d$ for the duration of $T_{act}$, which is given by
-$\delta_n(\dstar)\lambda$. $s$ then decays exponentially for $\Delta t < T_{inact}$.
-Solving \cref{eq:dot-s} (case $v < v_\theta$) with initial condition
-$s(0)=\dn(\dstar)\lambda$ yields:
+Since $\lambda < 1$, function $\delta_n$ is a linearly increasing function of $d^\star$ with a fixed point at $d_s$ for all $n$.
+Having identified $d$ after $n$ spikes, we can now use the release condition $\bar g s = g^{\star}$ (\cref{eq:release}) to find $\Delta t$.
+At the last ($n$th) spike of the \free{} phase at time $t_n = (n-1)T$ the synapse variable $s$ is set to the respective value of $d(t_n) = \delta_n(d^\star)$, and mirrors the value of $d$ for the duration of $T_{act}$.
+at the end of the active phase at time $t_n + T_{act}$ variable $d$ has decayed to $\delta_n(d^\star) \lambda$ \cref{eq:lambda}, therefore
+\begin{equation}
+	s(t_n + T_{act})=\delta_n(d^\star)\lambda.
+\end{equation}
+Finally $s$ decays exponentially for $\Delta t < T_{inact}$.
+Solving \cref{eq:dot-s} (case $v < v_\theta$) with initial condition $s(0)=\dn(d^\star)\lambda$ yields:
 \begin{equation}
 	~\label{eq:s-sol}
-  s(\delt)=\dn(\dstar)e^{-\Delta t/\tau_\kappa}.
+	s(\Delta t)=\dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}.
 \end{equation}
-Substituting $s(\delt)$ into $s$ of the release condition (\cref{eq:release})
-gives then
+Substituting $s(\Delta t)$ into $s$ of the release condition (\cref{eq:release}) gives then
 \begin{equation}
 	~\label{eq:release2}
-  \gbar \dn(\dstar) e^{-\delt/\tau_\kappa}=g^{\star}.
+	\bar g \dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}=g^{\star}.
 \end{equation}
-Our assumption of the release condition guarantees that the quiet cell 2 spikes and
-becomes free when $\gbar s - g^{\star}$ crosses zero. Solving \cref{eq:release2} for
-$\delt$ allows us to compute the inter-spike-interval as a function of $\dstar$, which
-defines our map $F_n$:
+Our assumption of the release condition guarantees that the \suppressed{} cell 2 spikes and becomes \free{} when $\bar g s - g^{\star}$ crosses zero.
+Solving \cref{eq:release2} for $\Delta t$ allows us to compute it a function of $d^\star$, which defines our map $F_n$:
 \begin{equation}
-  ~\label{eq:Fn-map}
-  F_{n}(d^{\star}):=\tau_\kappa \ln{\left(\frac{\gbar }{g^{\star}} \delta_{n}(d^{\star})\right)}= \delt.
+	\label{eq:Fn-map}
+	F_n(d^\star):=\tau_\kappa \ln{\left(\frac{\bar g }{g^\star} \lambda \delta_{n}(d^\star)\right)}= \Delta t.
 \end{equation}
 
-\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing
-function of $d^{\star}$ as well as $\gbar$.  Larger values of $d^{\star}$ and $\gbar$,
-respectively, cause stronger inhibition of the quiet cell, and therefore prolong its
-release time and the associated $\delt$.  Map $F_{n}$ is defined on $d^{\star}>d_{a}$,
-where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(\dstar)=0$ in
-\cref{eq:delta-map} for $\dstar$, which yields
+\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\bar g$.
+Larger values of $d^{\star}$ and $\bar g$, respectively, cause stronger inhibition of the \suppressed{} cell, and therefore prolong its release time and the associated $\Delta t$.
+Map $F_n$ is defined on $d^{\star}>d_{a}$, where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(d^\star)=0$ in \cref{eq:delta-map} for $d^\star$, which yields
 \begin{equation}
@@
 
-We now turn to the construction of map $Q_{n}$, which describes the recovery of the depression variable during the quiet phase.
-As we have identified earlier, the recovery in the quiet phase of a $n-n$ solution is of duration $2\delt +(n-1)T$.
-Substituting that into the solution for $d(t)$ (\cref{eq:d-sol}) with the initial condition $d(0)=\dn(\dstar)$ yields the map $Q_{n}$:
+We now turn to the construction of map $Q_n$, which describes the recovery of the depression variable during the \suppressed{} phase.
+As we have identified earlier, the recovery in the \suppressed{} phase of a $n-n$ solution is of duration $(n-1)T + T_{act} + 2\Delta t$.
+Substituting that into the solution of $d$ (\cref{eq:dot-d}) with the initial condition $d(0)=\dn(d^\star) \lambda$ yields the map $Q_{n}$:
 \begin{equation}
-  ~\label{eq:Qn-map}
-  Q_{n}(\delt):=1- (1- \lambda \dn(\dstar))e^{-(2\Delta t+(n-1)T)/\tau_{d}}.
+	\label{eq:Qn-map}
+	Q_n(\Delta t) := 1- (1- \dn(d^\star) \lambda)e^{-((n-1)T + T_{act} + 2\Delta t)/\tau_a}.
 \end{equation}
-Given $\delt$, we can find $\dn(\dstar)$ by rearranging the release condition in \cref{eq:release2}:
+Given $\Delta t$, we can find $\dn(d^\star)$ by rearranging the release condition in \cref{eq:release2}:
 \begin{equation}
-  ~\label{eq:dn}
-  \dn(\dstar) = \frac{g^{\star}}{\gbar} e^{\delt/\tau_{s}}.
+	\label{eq:dn}
+	\delta_n(d^\star) = \frac{1}{\bar g \lambda} g^\star e^{\Delta t/\tau_\kappa}.
 \end{equation}
-Map $Q_{n}$ is shown in \cref{fig:FQ-map}B for various values $n$.
-Note that $Q_{n}$ is monotonically increasing as larger values $\delt$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
-All curves $Q_{n}$ intersect at some $\delt = \tau_{s}\ln{\left[\gbar/(g^{\star}\lambda)\right]}$ where
+Map $Q_n$ is shown in \cref{fig:FQ-map}B for various values $n$.
+Note that $Q_n$ is monotonically increasing as larger values $\Delta t$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
+All curves $Q_{n}$ intersect at some $\Delta t = \tau_\kappa\ln{\left[\bar g/g^\star\right]}$ where
 \begin{equation}
-  ~\label{eq:Qn-intersect}
-  Q_{n}\left[\tau_{s}\ln{\left(\frac{\gbar}{g^{\star}\lambda}\right)}\right]=1.
+	\label{eq:Qn-intersect}
+	Q_n\left[\tau_\kappa\ln{\left(\frac{\bar g}{g^\star}\right)}\right]=1.
 \end{equation}
-As we will show in the next section, all fixed points of the full map $\Pi_{n}$ occur for $d^{\star}<1$.
-We will therefore restrict the domain of $Q_{n}$ to $(-\infty, \ln{\left[\gbar/(g^{\star}\lambda)\right]}\tau_{s})$ and the codomain to $(-\infty, 1)$.
-Additionally, while values $\delt>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t=T$, and we will address this concern in the last part of our map analysis.
+As we will show in the next section, all fixed points of the full map $\Pi_n$ occur for $d^\star<1$.
+We will therefore restrict the domain of $Q_n$ to $(-\infty, \tau_\kappa\ln{\left[\bar g/(g^\star)\right]})$ and the codomain to $(-\infty, 1)$.
+Additionally, while values $\Delta t>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t = T_{inact}$, and we will address this concern in the last part of our map analysis.
 
-Having found $F_{n}$ and $Q_{n}$, we can now construct the full map $\Pi_{n}(d^{\star})=Q_{n}\big(F_{n}(d^{\star})\big)$:
+Having found $F_n$ and $Q_n$, we can now construct the full map $\Pi_n(d^\star)=Q_n\big(F_n(d^\star)\big)$:
 \begin{equation}
-  ~\label{eq:Pn-map}
-  \Pi_{n}(d^{\star})= 1-
-  \frac{\rho^{n-1}{g^{\star}}^{\tau}}{{\gbar}^{\tau}}\delta_{n}^{-\tau}(d^{\star})\big(1-\lambda\delta_{n}(d^{\star})\big),
+	\label{eq:Pn-map}
+	\Pi_n(d^\star) = 1 - \Big(1 - \delta_n(d^\star) \lambda \Big)
+	\Big(\frac{\bar g}{g^\star}\delta_n(d^\star) \lambda \Big)^{-\tau}
+	e^{-((n-1)T + T_{act})/\tau_a},
 \end{equation}
-where we substituted $\tau = 2\tau_{s}/\tau_{d}$.
-Since $d$ is the slowest variable of the system and $\tau_{d}\gg \tau_{s}$, we will also assume $\tau<1$.
-\Cref{fig:Pn-map}A depicts $\Pi_{n}$ for various $n$.
+where we substituted $\tau = 2\tau_{k}/\tau_{a}$.
+Since $d$ is the slowest variable of the system and $\tau_a \gg \tau_\kappa$, we will also assume $\tau<1$.
+\Cref{fig:Pn-map}A depicts $\Pi_n$ for various $n$.
 Intersections of $\Pi_{n}$ with the diagonal are fixed points of the map.
 \Cref{fig:Pn-map}B shows $\Pi_{2}$ with $n=2$.
-Varying the synaptic strength $\gbar$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
-For $\gbar<0.03$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
-As $\gbar$ is increased to $\gbar \approx 0.03$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
-When $\gbar > 0.03$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
+Varying the synaptic strength $\bar g$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
+For $\bar g < 0.03$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
+As $\bar g$ is increased to $\bar g \approx 0.03$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
+When $\bar g > 0.03$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
 
-From \cref{eq:Pn-map} it is evident that $\Pi_{n}$ is monotonically increasing with respect to $\gbar$ and also $\dstar$:
+From \cref{eq:Pn-map} it is evident that $\Pi_n$ is monotonically increasing with respect to $\bar g$ and also $d^\star$:
 \begin{align}
 	\label{eq:non-degen1}
-  \dv{\Pi_{n}}{\gbar}  & >0, \\[0.5ex]
+	\dv{\Pi_n}{\bar g}  & >0, \\[0.5ex]
 	\label{eq:dPidd}
-  \dv{\Pi_{n}}{\dstar} & >0,
+	\dv{\Pi_n}{d^\star} & >0,
 \end{align}
 and in the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
-Just as $F_{n}$, curves $\Pi_{n}$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
+Just as $F_n$, curves $\Pi_n$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
 \begin{equation}
-  \lim_{\gbar \to \infty}\Pi_{n} = 1\text{ for all }n,
+	\lim_{\bar g \to \infty}\Pi_n = 1\text{ for all }n,
 \end{equation}
-fixed points of $\Pi_{n}$ lie in $(d_{a}, 1)$.
+fixed points of $\Pi_n$ lie in $(d_{a}, 1)$.
 
-% \subsection{Existence and stability of fixed points of $\mathit{\Pi_{n}}$}
 \subsection{Existence and stability of fixed points}
-We introduce the fixed point notation $\dstar_{f}$ with $\Pi_{n}(\dstar_{f})=\dstar_{f}$.
-The existence of fixed points $\dstar_{f}$ for $\gbar$ sufficiently large can be shown from the strict monotonicity of $\Pi_{n}$ with respect to $\gbar$ and $\dstar$ (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of $\Pi_{n}$ is monotonically decreasing,
+We introduce the fixed point notation $d^\star_{f}$ with $\Pi_n(d^\star_{f})=d^\star_{f}$.
+The existence of fixed points $d^\star_{f}$ for $\bar g$ sufficiently large can be shown from the strict monotonicity of $\Pi_{n}$ with respect to $\bar g$ and $d^\star$ (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of $\Pi_{n}$ is monotonically decreasing,
 \begin{equation}
 	\label{eq:non-degen2}
-  \left(\frac{\mathrm{d}}{\mathrm{d}\dstar}\right)^2 \Pi_{n}<0.
+	\left(\frac{\mathrm{d}}{\mathrm{d}d^\star}\right)^2 \Pi_n<0.
 \end{equation}
-In the limit $\dstar \to d_{a}$ the value of $\Pi_n$ decreases without bound for any $\gbar>0$.
-In the limit $\gbar \to 0$, $\Pi_n$ also decreases without bound, but as $\gbar \to \infty$ values of $\Pi_n$ approach $1$.
-It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some $\gbar$ large enough $\Pi_n$ intersects the diagonal.
-Moreover, because $\Pi_n$ and its slope are monotonic with respect to $\dstar$, there exists some critical fixed point $(\dstar_b, \gbar_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
+In the limit $d^\star \to d_{a}$ the value of $\Pi_n$ decreases without bound for any $\bar g>0$.
+In the limit $\bar g\to 0$, $\Pi_n$ also decreases without bound, but as $\bar g\to \infty$ values of $\Pi_n$ approach $1$.
+It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some $\bar g$ large enough $\Pi_n$ intersects the diagonal.
+Moreover, because $\Pi_n$ and its slope are monotonic with respect to $d^\star$, there exists some critical fixed point $(d^\star_b, \bar g_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
+% TODO: Replace the dx/dt with the physics package stuff
 \begin{align}
-  \Pi_{n}(\dstar_{b}; \gbar_{b})                     & =\dstar_{b}, \\
-  \frac{\d}{\d \dstar}\Pi_{n}(\dstar_{b}; \gbar_{b}) & =1.
+	\Pi_n(d^\star_b, \bar g_b)                  & =d^\star_b, \\
+	\frac{d}{d^\star}\Pi_n(d^\star_b, \bar g_b) & =1.
 \end{align}
-Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(\dstar_{b}, \gbar_{b})$ map $\Pi_{n}$ has the topological normal form described by the graph of
+Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(d^\star_{b}, \bar g_{b})$ map $\Pi_n$ has the topological normal form described by the graph of
 \begin{equation}
@@
 
-\subsection{Fold bifurcations}
+\subsection{Fold bifurcations of maps}
 Fixed points of $\Pi_n$ satisfy the fixed point equation
@@
 	\label{eq:Phi}
-  \Phi_n(\dstar; \gbar)=0,
+	\Phi_n(d^\star, \bar g) := \Pi_n(d^\star, \bar g)-d^\star = 0.
 \end{equation}
-where
-\begin{equation}
-  ~\label{eq:Phi-def}
-  \Phi_{n}(d^{\star}, \gbar):=\Pi_{n}(d^{\star}, \gbar)-d^{\star}.
-\end{equation}
-As we have already shown, for $\gbar > \gbar_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
-Solving \cref{eq:Phi} explicitly for $\dstar$ it not trivial, but solving for $\gbar$ is straightforward and given by $\gbar = G_n(\dstar)$, where
+As we have already shown, for $\bar g > \bar g_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
+Solving \cref{eq:Phi} explicitly for $d^\star$ it not trivial, but solving for $\bar g$ is straightforward and given by $\bar g= G_n(d^\star)$, where
 \begin{equation}
 	~\label{eq:g}
-  G_{n}(d^{\star}) := g^{\star} \left(\frac{\rho^{n-1}\delta_{n}^{-\tau}(d^{\star})(1-\lambda\delta_{n}(d^{\star}))}{1-d^{\star}}\right)^{1/\tau}.
+	G_{n}(d^{\star}) :=
+	\frac{g^{\star}}{\delta_n(d^\star)\lambda}
+	\Big(
+	\frac{(1-\lambda\delta_n(d^\star)) }{1-d^\star} e^{-((n-1)T + T_{act})/\tau_a}
+	\Big)^{1/\tau}.
 \end{equation}
-Plotting $d^{\star}$ against $\gbar$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
+Plotting $d^\star$ against $\bar g$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
 Note the typical quadratic shape of a fold bifurcation of maps.
-It is also evident that the fold bifurcations occur for increasingly smaller $\gbar$ as $n$ is increased.
-Moreover, we can observe that unstable fixed points have negative values of $d^{\star}$ for $n>1$.
+It is also evident that the fold bifurcations occur for increasingly smaller $\bar g$ as $n$ is increased.
+Moreover, we can observe that unstable fixed points have negative values of $d^\star$ for $n>1$.
 
-\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(\dstar_{b}(n), \gbar_{b}(n)\big)$, which is the global minimum of $G_{n}(\dstar_f)$:
+\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(d^\star_b(n), \bar g_b(n)\big)$, which is the global minimum
+of $G_n(d^\star_f)$:
 \begin{align}
-  \dstar_{b}(n) & = \operatorname{argmin} G_{n}(\dstar_{f}), \\
-  \gbar_{b}(n)  & = \min{G_{n}(\dstar_{f})}.
+	d^\star_b(n) & = \operatorname{argmin} G_n(d^\star_f), \\
+	\bar g_b(n)  & = \min{G_n(d^\star_f)}.
 \end{align}
-Function $G_{n}$ is strictly monotonic on the respective intervals of $\dstar_f$ that correspond to the stable and unstable fixed points, that is
+Function $G_n$ is strictly monotonic on the respective intervals of $d^\star_f$ that correspond to the stable and unstable fixed points, that is
 \begin{align}
-  \dv{G_n}{\dstar_f} & < 0, \text{ for } \dstar_f>\dstar_b(n) \text{ stable},   \\[0.5ex]
-  \dv{G_n}{\dstar_f} & > 0, \text{ for } \dstar_f<\dstar_b(n) \text{ unstable},
+	\dv{G_n}{d^\star_f} & < 0, \text{ for } d^\star_f>d^\star_b(n) \text{ stable},   \\[0.5ex]
+	\dv{G_n}{d^\star_f} & > 0, \text{ for } d^\star_f<d^\star_b(n) \text{ unstable},
 \end{align}
-which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $\dstar_f$.
-Because we are primarily interested in the stable fixed points, we define the stable fixed point function $\dstar_f=\phi_n(\gbar)$ as
+which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $d^\star_f$.
+Because we are primarily interested in the stable fixed points, we define the stable fixed point function $d^\star_f = \phi_n(\bar g)$ as
 \begin{equation}
 	\label{eq:phi}
-  \phi_{n}(\gbar):= G_{n}^{-1}(\dstar_{f}) \text{ for } \dstar_{f}>\dstar_{b}(n).
+	\phi_n(\bar g):= G_n^{-1}(d^\star_f) \text{ for } d^\star_f>d^\star_b(n).
 \end{equation}
-Function $\phi_n(\gbar)$ is also monotonic, and is therefore straightforward to compute numerically via root-finding.
-Here we use the Python package Pynverse~\citep{pynverse} for that purpose.
+Function $\phi_n(\bar g)$ is also monotonic, and is therefore straightforward to compute numerically.
+Here we use the Python package Pynverse \citep{pynverse} for that purpose.
 
-Having found the stable fixed points $\dstar_f$ as a function of the coupling strength $\gbar$, we can now compute the associated cycle period.
-Recall that the period is given by \cref{eq:P}, which we can be written as a function of $\gbar$:
+Having found the stable fixed points $d^\star_f$ as a function of $\bar g$, we can now compute the associated cycle period.
+Recall that the period is given by \cref{eq:P}, which we can be written as a function of $\bar g$:
 \begin{equation}
 	\label{eq:period}
-  P_n(\gbar) = 2(n-1)T + 2F_n\big(\underbrace{\phi_n(\gbar)}_{\dstar_f}, \gbar\big),
+	P_n(\bar g) = 2 \Big(
+	(n-1)T + T_{act} + F_n\big(\underbrace{\phi_n(\bar g)}_{d^\star_f}, \bar g\big)
+	\Big),
 \end{equation}
-where map $F_n$ (\cref{eq:Fn-map}) calculates the inter-burst-interval $\delt$ given a stable fixed point $\dstar_f=\phi_n(\gbar)$.
-We plot the predicted period $P_n(\gbar)$ versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
+where map $F_n$ (\cref{eq:Fn-map}) calculates $\Delta t$ given a stable fixed point $d^\star_f=\phi_n(\bar g)$.
+We plot the predicted period $P_n(\bar g)$ versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
 For $n>1$ our map $\Pi_n$ accurately predicts the period.
-When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for $n=1$ (see \cref{fig:release-delay}), since here $\gbar$ is not sufficiently strong to guarantee the validity of our release condition (\cref{eq:release}).
+When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for $n=1$ (see \cref{fig:release-delay}), since here $\bar g$ is not sufficiently strong to guarantee the validity of our release condition
+(\cref{eq:release}).
 
-It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\gbar$.
-This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\gbar), \gbar)=0$ in \cref{eq:Phi}.
-For $\dstar_f=\phi_n(\gbar)>d_b(n)$ we get:
+% TODO: Need to double-check this paragraph about implicit differentiation. It should still hold after the model change I believe.
+It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\bar g$.
+This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\bar g), \bar g)=0$ in \cref{eq:Phi}.
+For $d^\star_f=\phi_n(\bar g)>d_b(n)$ we get:
 \begin{equation}
-  \label{eq:dstardg}
-  \dv{\phi_n}{\gbar} = -\frac{\pdv*{\Phi_n}{\gbar}}{\pdv*{\Phi_n}{\dstar}} =
-  \frac{\pdv*{\Pi_n}{\gbar}}{1-\pdv*{\Pi_n}{\dstar}}>0.
+	\label{dstardg:eq}
+	\dv{\phi_n}{\bar g} = -\frac{\pdv*{\Phi_n}{\bar g}}{\pdv*{\Phi_n}{d^\star}} =
+	\frac{\pdv*{\Pi_n}{\bar g}}{1-\pdv*{\Pi_n}{d^\star}}>0.
 \end{equation}
-The inequality follows from $\pdv*{\Pi_n}{\gbar}>0$ and the fact that $\pdv*{\Pi_n}{\dstar}<1$ for $\dstar>d_b(n)$.
-\Cref{eq:dstardg} allows us to explain why the period $P_n$ increases with $\gbar$, as seen in \cref{fig:folds}B.
+The inequality follows from $\pdv*{\Pi_n}{\bar g}>0$ and the fact that $\pdv*{\Pi_n}{d^\star}<1$ for $d^\star>d_b(n)$.
+\Cref{eq:dstardg} allows us to explain why the period $P_n$ increases with $\bar g$, as seen in \cref{fig:folds}B.
 Differentiating $P_n$ gives:
@@
 	\label{eq:dPdg}
-  \dv{P_{n}}{\gbar} = 2\grad F_n(\dstar_f, \gbar) \cdot
-  \begin{bmatrix}\pdv*{\phi_n}{\gbar}\\[0.5ex] 1\end{bmatrix}>0,
+	\dv{P_{n}}{\bar g} = 2\grad F_n(d^\star_f, \bar g) \cdot
+	\begin{bmatrix}\pdv*{\phi_n}{\bar g}\\[0.5ex] 1\end{bmatrix}>0,
 \end{equation}
-where the partial derivatives of $F_n(\dstar_f, \gbar)$ are:
+where the partial derivatives of $F_n(d^\star_f, \bar g)$ are:
 \begin{align}
-  \pdv{F_n}{\dstar_f} & = \taus \frac{(\lambda\rho)^{n-1}}{\dn(\dstar_f)}>0, \\[0.5ex]
-  \pdv{F_n}{\gbar}    & = \frac{\taus}{\gbar}>0.
+	\pdv{F_n}{d^\star_f} & = \taus \frac{(\lambda\rho)^{n-1}}{\dn(d^\star_f)}>0, \\[0.5ex]
+	\pdv{F_n}{\bar g}    & = \frac{\tau_s}{\bar g}>0.
 \end{align}
-\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation:
-Increasing the coupling strength between the neurons leads to overall stronger inhibition of the quiet cell, which delays its release and leads to a longer cycle period.
-The latter allows more time for the synapse to depress in the free phase and recover in the quiet phase, resulting in overall larger values of $\dstar_f$, that is weaker depression at the burst onset.
+\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation: Increasing the coupling strength between the neurons leads to overall stronger inhibition of the \suppressed{} cell, which delays its release and leads to a longer cycle period.
+The latter allows more time for the synapse to depress in the \free{} phase and recover in the \suppressed{} phase, resulting in overall larger values of $d^\star_f$, that is weaker depression at the burst onset.
 
-While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the free phase contains exactly $n$ spikes.
-As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n-n$ bursts exists only on certain parameter intervals of $\gbar$.
-In the last sub-section we will analyse the mechanisms that guide how the stable $n-n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\gbar$ where such solutions exist.
+While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the \free{} phase contains exactly $n$ spikes.
+As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n-n$ bursts exists only on certain parameter intervals of $\bar g$.
+In the last sub-section we will analyse the mechanisms that guide how the stable $n-n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\bar g$ where such solutions exist.
 
@@
 \subsection{Period increment bifurcations with co-existent attractors}
-Let $\gbar_+(n)$ and $\gbar_-(n)$ denote the left and right parameter borders on $\gbar$ where stable $n-n$ solutions exist.
-That is, as $\gbar$ is increased stable $n-n$ solutions are created at $\gbar_+(n)$ and destroyed at $\gbar_-(n)$.
-When $\gbar$ is reduced beyond $\gbar_+(n)$, $n-n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\gbar$ is increased beyond $\gbar_-(n)$, $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
-Let us briefly recap our observations regarding $\gbar_+(n)$ and $\gbar_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
+Let $\bar g_+(n)$ and $\bar g_-(n)$ denote the left and right parameter borders on $\bar g$ where stable $n-n$ solutions exist.
+That is, as $\bar g$ is increased stable $n-n$ solutions are created at $\bar g_+(n)$ and destroyed at $\bar g_-(n)$.
+When $\bar g$ is reduced beyond $\bar g_+(n)$, $n-n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\bar g$ is increased beyond $\bar g_-(n)$, $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
+Let us briefly recap our observations regarding $\bar g_+(n)$ and $\bar g_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
 For $n>1$ there are the following relations:
 \begin{align}
-  \gbar_+(n)                  & < \gbar_-(n)\label{eq:easy1},                                       \\
-  \gbar_+(n)                  & < \gbar_+(n+1)\text{ and } \gbar_-(n)<\gbar_-(n+1)\label{eq:easy2}, \\
-  \gbar_+(n+1)                & < \gbar_-(n)\label{eq:coexistence},                                 \\
-  \gbar_-(n+1) - \gbar_+(n+1) & < \gbar_-(n) - \gbar_-(n)\label{eq:robustness}.
+	\bar g_+(n)                   & < \bar g_-(n)\label{eq:easy1},                                         \\
+	\bar g_+(n)                   & < \bar g_+(n+1)\text{ and } \bar g_-(n)<\bar g_-(n+1)\label{eq:easy2}, \\
+	\bar g_+(n+1)                 & < \bar g_-(n)\label{eq:coexistence},                                   \\
+	\bar g_-(n+1) - \bar g_+(n+1) & < \bar g_-(n) - \bar g_-(n)\label{eq:robustness}.
 \end{align}
@@
 \Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n-n$ and $(n+1)-(n+1)$ solutions.
-\Cref{eq:robustness} implies that the parameter interval on $\gbar$ of $n-n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
+\Cref{eq:robustness} implies that the parameter interval on $\bar g$ of $n-n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
 All of the above relations are reminiscent of the period increment bifurcations with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
 	see][]{gardini2012,tramontana2012,avrutin2011,gardini2012}.
-While our maps $\Pi_n$ are fully continuous, the above observation suggests that
-a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
+While our maps $\Pi_n$ are fully continuous, the above observation suggests that a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
 We will explore what such a map might look like in the discussion.
 
-Let us now find algebraic equations that will allow us to calculate the critical parameters $\gbar_+(n)$ and $\gbar_-(n)$ associated with the period increment bifurcations.
+Let us now find algebraic equations that will allow us to calculate the critical parameters $\bar g_+(n)$ and $\bar g_-(n)$ associated with the period increment bifurcations.
 % BUG: Maybe don't call it period-increment here?
-Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\gbar$:
+Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\bar g$:
 \begin{equation}
-  \dv{P_{n}}{\gbar}=2\dv{F_n(\phi_n(\gbar), \gbar)}{\gbar}>0,
+	\dv{P_{n}}{\bar g}=2\dv{F_n(\phi_n(\bar g), \bar g)}{\bar g}>0,
 \end{equation}
-that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the quiet cell, and $\delt$ becomes larger.
-Once $\delt=T$, the free cell can produce another spike and the solution bifurcates into a $(n+1)-(n+1)$ solution.
-Note, however, that at $\gbar_+(n)$ the bifurcation into a $(n-1)-(n-1)$ does not occur when $\delt=0$.
-Here the mechanism is different: A sufficient reduction of $\gbar$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the quiet cell to be released one spike earlier.
+that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the \suppressed{} cell, and $\Delta t$ becomes larger.
+When $\Delta t > T_{inact}$, the \free{} cell can produce another spike and the solution bifurcates into a $(n+1)-(n+1)$ solution.
+Note, however, that at $\bar g_+(n)$ the bifurcation into a $(n-1)-(n-1)$ does not occur at $\Delta t = 0$.
+Here the mechanism is different: A sufficient reduction of $\bar g$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the \suppressed{} cell to be released one spike earlier.
 
-Using the above reasoning we can now formulate the conditions for both bifurcations at $\gbar_+(n)$ and $\gbar_-(n)$.
-As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $\dstar_f=\phi_n(\gbar)$ (\cref{eq:phi}).
-At the right bifurcation border $\gbar_-(n)$ we have $\delt=T$, and after substituting our $F_{n}$-map (\cref{eq:Fn-map}) this translates into
+Using the above reasoning we can now formulate the conditions for both bifurcations at $\bar g_+(n)$ and $\bar g_-(n)$.
+As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $d^\star_f=\phi_n(\bar g)$ (\cref{eq:phi}).
+At the right bifurcation border $\bar g_-(n)$ we have $\Delta t=T_{inact}$, and after substituting our $F_n$ map (\cref{eq:Fn-map}) this translates into
 \begin{equation}
-  F_n(\phi_n(\gbar), \gbar) = T,
+	F_n(\phi_n(\bar g), \bar g) = T_{inact},
 \end{equation}
@@
 	\label{eq:R}
-  R_{n}(\gbar):=F_n(\phi_n(\gbar), \gbar)-T,
+	\mathcal{R}_{n}(\bar g):=F_n(\phi_n(\bar g), \bar g)-T_{inact},
 \end{equation}
-whose root is the desired right bifurcation border $\gbar_-(n)$.
-In case of the left bifurcation border at $\gbar_+(n)$ the release condition is satisfied just before the free cell has produced its $n$th spike, and after the depression variable has been reset $n-1$ times, which gives the condition
+whose root is the desired right bifurcation border $\bar g_-(n)$.
+% NOTE: @CONOR: After changing the model I'm not sure anymore whether the next equation is clear from my explanation or I need another sentence.
+In case of the left bifurcation border at $\bar g_+(n)$, the release condition is satisfied just before the \free{} cell has produced its $n$th spike, where total synaptic conductance is given by
 \begin{equation}
-  \gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} = \gstar,
+	\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{inact}/\tau_\kappa} = g^\star,
 \end{equation}
-and can be rewritten as a function
+which can be rewritten as a function
 \begin{equation}
 	\label{eq:L}
-  L_{n}(\gbar):=\gbar \delta_{n-1}\big(\phi_{n}(\gbar)\big)e^{-T/\taus} -\gstar,
+	\mathcal{L}_n(\bar g):=\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{inact}/\tau_\kappa} -g^\star,
 \end{equation}
-whose root is $\gbar_+(n)$.
-Both $R_{n}$ and $L_{n}$ are increasing with respect to $\gbar$, which makes finding their roots numerically straightforward.
+whose root is $\bar g_+(n)$.
+Both $\mathcal{R}_n$ and $\mathcal{L}_n$ are increasing with respect to $\bar g$, which makes finding their roots numerically straightforward.
 
-\Cref{fig:final-bif} shows the period $P_n(\gbar)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\gbar \in [\gbar_+(n),\gbar_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
+\Cref{fig:final-bif} shows the period $P_n(\bar g)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\bar g \in [\bar g_+(n),\bar g_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
 Note that the width of $n-n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
-That is, bursts with more spikes occur on increasingly smaller intervals of $\gbar$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
-We also note the occurrence of bi-stability between pairs of $n-n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in \cref{eq:coexistence}.
+That is, bursts with more spikes occur on increasingly smaller intervals of $\bar g$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
+We also note the occurrence of bi-stability between pairs of $n-n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in
+\cref{eq:coexistence}.
 
 As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate for $n>1$.
-Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be $\gbar \approx 0.592\si{mS/cm^2}$ in \cref{fig:release-delay}.
-The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\gbar_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
+Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be $\bar g \approx 0.592\si{mS/cm^2}$ in \cref{fig:release-delay}.
+The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\bar g_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
 However, even for branches of large $n-n$ solutions there is a mismatch between the bifurcation borders.
@@
 Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.
-
-\end{document}

### 2022-03-07 tex/supplementary.tex
Refactor a bunch of plots

--- 2022-01-26 tex/supplemental.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This is just an example/guide for you to refer to when producing your supplementary material for your Frontiers article.                                 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% Version 2.5 Generated 2018/06/15 %%%
-%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
-%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
-%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%
-
 \documentclass[utf8]{frontiers_suppmat} % for all articles
@@
 \section{Model equations and parameters}
-The asymptotic functions $m_{\infty}$ and $w_{\infty}$ for the calcium and potassium conductances, respectively, are given by
+The asymptotic function for the calcium conductance $m_{\infty}$ is given by
+\begin{equation}
+	m_{\infty}(v) = \frac{1}{2}\left(1+\tanh{\left((v-v_{A})/v_{B}\right)}\right).
+\end{equation}
+The voltage and potassium nullclines, \(v_{\infty}(v)\) and \(w_{\infty}(v)\), are
 \begin{align}
-  m_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{A})/v_{B}\right)}\right),\\
-  w_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{C})/v_{D}\right)}\right).
+	v_{\infty}(v) & = \frac{-g_{l}(v-v_{l}) - g_{ca}m_{\infty}(v)(v-v_{ca}) + I - \bar g s(v-v_{s})}{g_{k}(v-v_{k})},
+	\\
+	w_{\infty}(v) & = \frac{1}{2}\left(1+\tanh{\left((v-v_{C})/v_{D}\right)}\right).
 \end{align}
@@
 	\begin{tabular}{ll}
-    Parameter & value\\
+		Parameter                        & value                 \\
 		\hline
 		                                 &                       \\
-    $g_{\leak}$ & 0.15 \si{mS/cm^2}\\
-    $g_{\ca}$ & 0.3 \si{mS/cm^2}\\
-    $g_{\k}$ & 0.6 \si{mS/cm^2}\\
-    $v_{\leak}$ & -50 mV\\
-    $v_{\ca}$ & 100 mV\\
-    $v_{\k}$ & -70 mV\\
-    $v_{A}$ & 1 mV\\
-    $v_{B}$ & 14.5 mV\\
-    $v_{C}$ & 4 mV\\
-    $v_{D}$ & 15 mV\\
-    $I$ & 6 \si{\mu A/cm^2}\\
-    $\tau$$_{w}$ & 100 ms\\
-    $\tau$$_{d}$ & 1000 ms\\
-    $\tau$$_{s}$ & 100 ms\\
-    $v_{\theta}$ & 0 mV\\
-    $v_{s}$ & -80 mV\\
-    $\lambda$ & 0.5\\
-    $T$ & 217 ms\\
-    $\gstar$ & 0.03804 \si{mS/cm^2}\\
+		$g_{\leak}$                      & $0.15$ \si{mS/cm^2}   \\
+		$g_{\ca}$                        & $0.3$ \si{mS/cm^2}    \\
+		$g_{\k}$                         & $0.6$ \si{mS/cm^2}    \\
+		$v_{\leak}$                      & $-50$ \si{mV}         \\
+		$v_{\ca}$                        & $100$ \si{mV}         \\
+		$v_{\k}$                         & $-70$ \si{mV}         \\
+		$v_{A}$                          & $1$ \si{mV}           \\
+		$v_{B}$                          & $14.5$ \si{mV}        \\
+		$v_{C}$                          & $4$ \si{mV}           \\
+		$v_{D}$                          & $15$ \si{mV}          \\
+		$I$                              & $3.8$ \si{\mu A/cm^2} \\
+		$\tau_w$                         & $100$ \si{ms}         \\
+		$\tau_a$                         & $1000$ \si{ms}        \\
+		$\tau_b$                         & $100$ \si{ms}         \\
+		$\tau_\kappa$                    & $100$ \si{ms}         \\
+		$\tau_\gamma$                    & $0.0001$ \si{ms}      \\
+		$v_{\theta}$                     & $0$ \si{mV}           \\
+		$v_{s}$                          & $-80$ \si{mV}         \\
+		$T$                              & $376$ \si{ms}         \\
+		$T_{act}$                        & $49$ \si{ms}          \\
+		$T_{inact}$                      & $327$ \si{ms}         \\
+		$\gstar$                         & $0.0036$ \si{mS/cm^2} \\
+		$\lambda:=\exp(-T_{act}/\tau_b)$ & $0.612$               \\
+		$\rho:=\exp(-T_{inact}/\tau_a)$  & $0.721$               \\
 	\end{tabular}
@@
 
-% \bibliographystyle{frontiersinSCNS_ENG_HUMS} %  for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
 \bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles

### 2022-03-07 scripts/compute.py

@@ -1,0 +1,80 @@
+"""Script to compute numeric and analytic bifurcation diagrams."""
+
+from __future__ import annotations
+
+import time
+import argparse
+import multiprocessing
+
+import pandas as pd
+
+from poincare_map import ode, paths, poincare_map
+
+
+def compute_numeric_bif_diagram() -> pd.DataFrame:
+    """Compute bifurcation diagram numerically for n=1,2,3,4,5."""
+    mlml = ode.MLML("odes/mlml.ode")
+    nsteps = 100
+
+    gmin = 0.3
+    ns = [1, 2, 3, 4, 5]
+    g0s = [0.3, 0.4, 0.5, 0.52, 0.56]
+    gsteps = [0.002, 0.002, 0.002, 0.001, 0.001]
+    totals = [5000, 8000, 10000, 15000, 15000]
+
+    curves = []
+    for n, g0, step, total in zip(ns, g0s, gsteps, totals):
+        print(f"Starting branch at g={g0}")
+        left = mlml.continuate(
+            n=n, step=-step, nsteps=nsteps, g=g0, total=total, gmin=gmin
+        )
+        right = mlml.continuate(
+            n=n, step=step, nsteps=nsteps, g=g0, total=total, gmin=gmin
+        )
+        if (left is not None) and (right is not None):
+            curve = pd.concat([left.iloc[::-1], right]).reset_index(
+                drop=True
+            )
+            curves.append(curve)
+    return pd.concat(curves, axis=0)  # type: ignore
+
+
+def compute_analytic_bif_diagram() -> pd.DataFrame:
+    """Compute bifurcation diagram analytically."""
+    ns = list(range(10))[1:]
+    with multiprocessing.get_context("fork").Pool() as pool:
+        futures = []
+        for n in ns:
+            poincare = poincare_map.PoincareMap(n)
+            future = pool.apply_async(poincare.compute_stable_branch)
+            futures.append(future)
+        branches = [future.get() for future in futures]
+        return pd.concat(branches)  # type: ignore
+
+
+
+
+parser = argparse.ArgumentParser()
+parser.add_argument(
+    "--recompute", help="Whether to recompute diagrams", action="store_true"
+)
+
+if __name__ == "__main__":
+
+    args = parser.parse_args()
+
+    t0 = time.time()
+    if (not paths.numeric_bif_diagram.exists()) or args.recompute:
+        print(
+            "Computing numeric bifurcation diagram. This might take a while ..."
[…]

### 2022-03-07 scripts/makefig.py

@@ -1,1301 +1,433 @@
-# %% Initialise
-import itertools
-import multiprocessing
 import os
+from functools import partial
 import pickle
-import string
-import warnings
-from os import path
+import pandas as pd
 
 import matplotlib
-matplotlib.use('pgf')
 
-import pandas as pd
-import pyxpp.pyxpp as xpp
-import scipy as sp
+# NOTE: Maybe plot directly as pgf and import?
+matplotlib.use("pgf")
+import matplotlib
 from matplotlib import patches
+from matplotlib.figure import Figure
 from matplotlib import pyplot as plt
 from matplotlib.gridspec import GridSpec
 from matplotlib.lines import Line2D
-from pandas import DataFrame
-from scipy.misc import derivative
-from pathlib import Path
 
-from poincare_map import helpers
-from poincare_map import model
+import string
+import numpy as np
+
 from poincare_map import ode
 from poincare_map import paths
 
-import numpy as np
+from poincare_map.poincare_map import PoincareMap
+from poincare_map import ode, paths, helpers
+
 
 plt.ioff()
-
-warnings.filterwarnings("ignore", category=DeprecationWarning)
-# Ignore devide by zero
-np.seterr(divide='ignore')
-np.seterr(all='ignore')
-
-
-xppfile = str(paths.odes / "mlml.ode")
-CENTER_TITLE_SIZE = 11
-FIGWIDTH = 3.85
-FIGSIZE = (FIGWIDTH, FIGWIDTH)
-FIG2by1 = (FIGWIDTH*1.4, (FIGWIDTH*1.4)/2)
-
-EQSIZE = 15                     # Font size of equaitons.
-
 rcp = matplotlib.rcParamsDefault
-rcp['figure.max_open_warning'] = 0
-rcp['axes.unicode_minus'] = False
-rcp['text.usetex'] = True
-rcp['pgf.rcfonts'] = False
-rcp['pgf.texsystem'] = 'pdflatex'
-rcp['xtick.labelsize'] = 'small'
-rcp['ytick.labelsize'] = 'small'
[…]

### 2022-03-07 src/poincare_map/helpers.py

@@ -1,13 +1,11 @@
 from __future__ import annotations
-from logging import debug
 
-import pandas as pd
-import numpy as np
-from numpy.typing import ArrayLike
-from typing import Dict, List, Optional, Tuple
-from matplotlib import pyplot as plt
+from typing import Dict
+
 import matplotlib.lines as mlines
 import matplotlib.patches as mpatches
+import numpy as np
+import pandas as pd
 
 
 def roots(x: np.ndarray, up: int = 0) -> np.ndarray:
@@ -138,6 +136,13 @@ def limit_cycle_info(lc: pd.DataFrame) -> Dict:
     dmin = lc["d1"].min()
     info = {"n": n, "period": period, "dmax": dmax, "dmin": dmin}
     return info
+
+
+def calc_delta_t(lc: pd.DataFrame, Tact: float = 49) -> float:
+    """Calculate numerical Delta-t from limit cycle solution."""
+    spikes1 = spike_times(lc["v1"])
+    spikes2 = spike_times(lc["v2"])
+    return spikes2[0] - (spikes1[-1] + Tact)
 
 
 def sigmoid(x: float, A, B) -> float:

### 2022-03-07 src/poincare_map/ode.py

@@ -2,9 +2,10 @@
 from __future__ import annotations
 
 import multiprocessing
+import typing as tp
 from abc import ABC, abstractmethod
 from functools import partial
-import typing as tp
+from pathlib import Path
 
 import numpy as np
 import pandas as pd
@@ -25,9 +26,9 @@ class ODE(ABC):
     # Numerical options.
     numerics: tp.Dict[str, float]
 
-    def __init__(self, ode_file: str) -> None:
+    def __init__(self, ode_file: str | Path) -> None:
         """Initialise class from ode file."""
-        self.ode_file = ode_file
+        self.ode_file = str(ode_file)
         self.state_vars = list(xpp.read_vars(ode_file))
         self.pars = dict(xpp.read_pars(ode_file))
         self.ics = pd.DataFrame(
@@ -50,7 +51,9 @@ class ODE(ABC):
         index = pd.Index(data=sol[:, 0], name="time")
         return pd.DataFrame(sol[:, 1:], columns=self.state_vars, index=index)
 
-    def parallel_run(self, nrand: int = 5, **kwargs) -> tp.List[pd.DataFrame]:
+    def parallel_rand_run(
+        self, nrand: int = 5, **kwargs
+    ) -> tp.List[pd.DataFrame]:
         """Randomise ICs and integrate system multiple times."""
 
         with multiprocessing.get_context("fork").Pool() as pool:
@@ -186,7 +189,7 @@ class MLML(ODE):
             time = np.linspace(0, period, len(lc))
             return lc_normed.set_index(pd.Index(time, name=lc.index.name))
 
-        solutions = self.parallel_run(nrand=nrand, **kwargs)
+        solutions = self.parallel_rand_run(nrand=nrand, **kwargs)
         for sol in solutions:
             spikes = helpers.spike_times(sol["v1"])
             lc_index = helpers.limit_cycle_index(
@@ -232,8 +235,6 @@ class MLML(ODE):
 
         # Run continuation in some direction
         for _ in range(nsteps):
-            # Update ICs and parameter.
-            g = g + step
             # import pdb; pdb.set_trace()
             if gmin < g < gmax:
                 # Try finding a n-limit cycle
@@ -248,6 +249,7 @@ class MLML(ODE):
                                 **lc_info,
                                 **{
                                     "g": g,
+                                    "lc": lc
                                 },
                             }
                         )
@@ -260,6 +262,8 @@ class MLML(ODE):
                     return pd.DataFrame(results)
             else:
[…]

### 2022-03-07 src/poincare_map/paths.py

@@ -10,5 +10,9 @@ figures.mkdir(exist_ok=True)
 odes.mkdir(exist_ok=True)
 
 # Data files
-numeric_bif_diagram = data / "numeric-bif-diagram.parquet"
-analytic_bif_diagram = data / "analytic-bif-diagram.parquet"
+numeric_bif_diagram = data / "numeric-bif-diagram.pkl"
+analytic_bif_diagram = data / "analytic-bif-diagram.pkl"
+
+# ODE files
+ml_file = odes / "ml.ode"
+mlml_file = odes / "mlml.ode"

### 2022-03-07 src/poincare_map/poincare_map.py

@@ -19,9 +19,9 @@ from scipy import optimize
 class PoincareMap(NamedTuple):
     """Model for map computation."""
 
-    n: int
+    n: int = 2
 
-    # These parameters should be read from ODE file.
+    # These parameters should match the ODE file.
     tauk: float = 100
     taua: float = 1000
     taub: float = 100

### 2022-03-08 scripts/makefig.py
Fix some plots

@@ -44,8 +44,8 @@ rcp["pgf.preamble"] = r"\usepackage{amsmath} \usepackage{siunitx}"
 
 matplotlib.rcParams.update(rcp)
 
-np.seterr(divide='ignore')
-np.seterr(all='ignore')
+np.seterr(divide="ignore")
+np.seterr(all="ignore")
 
 FIGWIDTH = 3.85
 FIGSIZE = (FIGWIDTH, FIGWIDTH)
@@ -56,6 +56,7 @@ mlml = ode.ML(paths.mlml_file)
 pmap = PoincareMap()
 
 df = pd.read_pickle(paths.numeric_bif_diagram)
+df_ana = pd.read_pickle(paths.analytic_bif_diagram)
 
 #%% Nullclines uncoupled
 vs = np.linspace(-65, 60, 100)
@@ -371,6 +372,7 @@ ns = np.arange(1, 5, 1)
 
 fig, axs = plt.subplots(figsize=FIG2by1, tight_layout=True, ncols=2)
 
+# A: F-map
 ax = axs[0]
 for n in ns:
     pmap_n = PoincareMap(n)
@@ -393,22 +395,23 @@ ax.text(1.01, 325, r"$3$")
 ax.text(1.01, 305, r"$4$")
 
 ax.axvline(pmap.dsup, c="grey", ls="--")
-ax.text(pmap.dsup+0.04, 0, r'$d_s$')
+ax.text(pmap.dsup + 0.04, 0, r"$d_s$")
 
 ax.set(
-    xlabel=r'$d^\star$',
-    ylabel=r'$\Delta t=F_n(d^\star)$',
+    xlabel=r"$d^\star$",
+    ylabel=r"$\Delta t=F_n(d^\star)$",
     xlim=(-1, 1),
-    ylim=(-20, 400)
+    ylim=(-20, 400),
 )
 
+# B: Q-map
 ax = axs[1]
 delts = np.linspace(-200, 500, 10000)
 
 for n in ns:
     pmap_n = PoincareMap(n)
     ys = np.array([pmap_n.Q_map(delt, g=g) for delt in delts])
-    ax.plot(delts, ys, c='C0')
+    ax.plot(delts, ys, c="C0")
 
 # Add n numbers
 ax.text(500, 1.38, r"$1$")
@@ -417,17 +420,184 @@ ax.text(500, 1.14, r"$3$")
 ax.text(500, 1.05, r"$4$")
 
 
[…]

### 2022-03-08 src/poincare_map/poincare_map.py

@@ -106,12 +106,17 @@ class PoincareMap(NamedTuple):
     #     C = np.exp(-((n - 1) * self.T + self.Tact) / self.taua)
     #     return 1 - A * B * C
 
-    def G(self, d: float) -> float:
+    def G(self, d: float) -> float | None:
         """Fixed point function maps d to the corresponding fixed point value gbar."""
         delta = self.delta(d)
-        A = (1 - delta * self.Lambda) / (1 - d)
-        B = np.exp(-((self.n - 1) * self.T + self.Tact) / self.taua)
-        return (self.gstar / (delta * self.Lambda)) * pow(A * B, 1 / self.tau)
+        if (delta < 0) and (d < 1):  # G is only defined here.
+            return None
+        else:
+            A = (1 - delta * self.Lambda) / (1 - d)
+            B = np.exp(-((self.n - 1) * self.T + self.Tact) / self.taua)
+            return (self.gstar / (delta * self.Lambda)) * pow(
+                A * B, 1 / self.tau
+            )
 
     def period(self, g: float) -> float | None:
         """Compute n-n period (eq. 45)."""
@@ -120,7 +125,7 @@ class PoincareMap(NamedTuple):
             delta_t = self.F_map(df, g)
             return 2 * ((self.n - 1) * self.T + self.Tact + delta_t)
 
-    def critical_fp(self, x0: float = 0.5) -> Tuple:
+    def critical_fp(self, x0: float = 0.5) -> Tuple[float, float]:
         """Compute critical fixed point (db, gb) at fold bifurcation
         (equations 41 and 42).
         """

### 2022-03-08 tex/manuscript.tex
Change notation from n-n to n:n
This is what reviewer 1 suggested.

@@
   To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
-  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n-n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
+  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n:n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
   Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
@@
   Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
-  We derive conditions that describe period-increment bifurcations between stable $n-n$ and $(n+1)-(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
+  We derive conditions that describe period-increment bifurcations between stable $n:n$ and $(n+1):(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
   Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.
@@
   \includegraphics{fig/bif-diagram.pdf}
-  \caption{Numerically computed bifurcation diagrams of stable $n-n$ solutions for
+  \caption{Numerically computed bifurcation diagrams of stable $n:n$ solutions for
     increasing coupling strength $\gbar$. $\bm{\mathrm{(A)}}$ Period of stable
     solutions. Dashed lines show the interval between the $5-5$ and the suppressed
-    solutions, where higher period $n-n$ solutions occur on increasingly smaller intervals
-    of $\gbar$. $\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n-n$ solutions in
+    solutions, where higher period $n:n$ solutions occur on increasingly smaller intervals
+    of $\gbar$. $\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n:n$ solutions in
     $\mathrm{(A)}$. Long $ISI$s are associated with the quiet phase of a burst, short
@@
     firing of cell 2, which only occurs after the second spike of cell 1.
-    $\bm{\mathrm{(C)}}$ Branch with $n-n$ solutions  where release delay is
+    $\bm{\mathrm{(C)}}$ Branch with $n:n$ solutions  where release delay is
     approximately zero and the release condition is sufficient for firing of cell 2.
@@
   \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
-    Each continuous branch is associated with a stable $n-n$ burst solution. Increasing
+    Each continuous branch is associated with a stable $n:n$ burst solution. Increasing
     $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
@@
   \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
-  \caption{Bifurcation diagrams of stable $n-n$ solutions computed analytically from
+  \caption{Bifurcation diagrams of stable $n:n$ solutions computed analytically from
     fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in

### 2022-03-08 tex/sections/discussion.tex
Change notation from n-n to n:n
This is what reviewer 1 suggested.

@@
 To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression.
-When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n-n$ burst patterns.
+When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n:n$ burst patterns.
 Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
-This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n-n$ solutions respectively.
+This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n:n$ solutions respectively.
 Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons.
-Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n-n$ burst solutions of the full two-cell system of ODEs.
+Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n:n$ burst solutions of the full two-cell system of ODEs.
 The results from our one-dimensional map match excellently with numerical simulation of the full network.
@@
 % FURTHER METHOD IDEAS
-We have studied $n-n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
+We have studied $n:n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
 However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes.
 It is conceivable that our map construction can be extended to also capture such $m-n$ solutions.
-Remember, in the case of symmetrical coupling with $n-n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
+Remember, in the case of symmetrical coupling with $n:n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
 To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other.
@@
 % LIMITATION: SPIKE MAP
-Our simulations of the network showed that $n-n$ solutions lose robustness as their period is increased.
+Our simulations of the network showed that $n:n$ solutions lose robustness as their period is increased.
 That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
-We were able to replicate this finding by numerically finding the respective left and right borders of stable $n-n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
-We have also noted the resemblance of our bifurcation diagram to one where such $n-n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
+We were able to replicate this finding by numerically finding the respective left and right borders of stable $n:n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
+We have also noted the resemblance of our bifurcation diagram to one where such $n:n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
 It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}.
@@
 % FLOW SYSTEM BIFURCATION
-In addition to stable $n-n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n-n$ solutions.
+In addition to stable $n:n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n:n$ solutions.
 While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.

### 2022-03-08 tex/sections/introduction.tex
Refactor a bunch of plots
Change notation from n-n to n:n
This is what reviewer 1 suggested.

@@
 Short-term synaptic plasticity may have a role in burst activity in central pattern
-generators (CPGs).  Short-term synaptic depression is commonly found in neuronal networks
-involved in the generation of rhythmic movements, such as in the pyloric CPG of the spiny
-lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of the chick
-embryo~\citep{donovan1998}.  Synaptic depression modulates the strength of synapses in
-response to changes to the presynaptic firing frequency.  At a high neuronal firing
-frequency, depression weakens the strength of synapses and therefore reduces the magnitude
-of the postsynaptic response.  At low firing frequency, it allows sufficient time for the
-synapse to recover from depression between spikes, leading to a stronger postsynaptic
-response.  In reciprocal networks, synaptic depression has been shown to act as a
-``switch'', giving rise to a wide range of network dynamics such as synchronous and
-multi-stable rhythms, as well as fine tuning the frequency of network
-oscillations~\citep{nadim2000, nadim1999, bose2011}.
+generators (CPGs).
+Short-term synaptic depression is commonly found in neuronal networks involved in the generation of rhythmic movements, such as in the pyloric CPG of the spiny lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of the chick embryo~\citep{donovan1998}.
+Synaptic depression modulates the strength of synapses in response to changes to the presynaptic firing frequency.
+At a high neuronal firing frequency, depression weakens the strength of synapses and therefore reduces the magnitude of the postsynaptic response.
+At low firing frequency, it allows sufficient time for the synapse to recover from depression between spikes, leading to a stronger postsynaptic response.
+In reciprocal networks, synaptic depression has been shown to act as a ``switch'', giving rise to a wide range of network dynamics such as synchronous and multi-stable rhythms, as well as fine tuning the frequency of network oscillations~\citep{nadim2000, nadim1999, bose2011}.
 
@@
 When one side is firing during a burst the other, antagonistic side, is prevented from
-firing by synaptic inhibition. However, the weakening of inhibition as a result of
-synaptic depression eventually releases the antagonistic side so that it starts firing,
-terminating the burst on the side that had originally been firing.  This rhythmogenesis
-hypothesis has been considered one of a handful of standard mechanisms for generating
-locomotion rhythms in vertebrates~\citep{reiss1962,perkel1974,friesen1994}. It has been
-proposed as an explaination of the antiphase burst rhythm in struggling in
-\textit{Xenopus} tadpoles~\citep{li2007}.
+firing by synaptic inhibition.
+However, the weakening of inhibition as a result of synaptic depression eventually releases the antagonistic side so that it starts firing, terminating the burst on the side that had originally been firing.
+This rhythmogenesis hypothesis has been considered one of a handful of standard mechanisms for generating locomotion rhythms in vertebrates~\citep{reiss1962,perkel1974,friesen1994}.
+It has been proposed as an explaination of the antiphase burst rhythm in struggling in \textit{Xenopus} tadpoles~\citep{li2007}.
 
@@
 of two identical, tonically active Morris-Lecar~\citep{morris1981} neurons coupled through
-inhibitory depressing synapses.  Numerical simulations showed that when the reciprocal
-synaptic conductance between the two neurons is varied, the network produces symmetric
-\(n-n\) anti-phase bursts, with stronger synaptic coupling leading to longer bursts.  They
-used methods from geometric singular perturbation theory to separate the timescales of the
-fast membrane, and the slow synaptic dynamics of the network to derive one-dimensional
-conditions necessary for the existence of stable \(n-n\) solutions (for \(n\leq 2\)).
+inhibitory depressing synapses.
+Numerical simulations showed that when the reciprocal synaptic conductance between the two neurons is varied, the network produces symmetric $n:n$ anti-phase bursts, with stronger synaptic coupling leading to longer bursts.
+They used methods from geometric singular perturbation theory to separate the timescales of the fast membrane, and the slow synaptic dynamics of the network to derive one-dimensional conditions necessary for the existence of stable $n:n$ solutions (for $n\leq 2$).
 According to these conditions the type of firing pattern largely depends on the slow
@@
 Thus, the scalar conditions derived in~\citet{bose2011} provide a method to numerically
-identify the type of stable \(n-n\) pattern for any given value of the coupling strength.
-However, they do not predict the exact period of such solutions.  Furthermore, while they
-provide good arguments for the validity of their reduction assumptions and the resulting
-scalar conditions, they do not verify them numerically.
+identify the type of stable $n:n$ pattern for any given value of the coupling strength.
+However, they do not predict the exact period of such solutions.
+Furthermore, while they provide good arguments for the validity of their reduction assumptions and the resulting scalar conditions, they do not verify them numerically.
 
 Here we extend the previous analysis by providing a Poincaré map of the slow depression
-dynamics.  This allows us not only to predict the types of stable \(n-n\) solutions the full
-network can produce, (for any \(n\)), but also to study how varying the coupling strength
-affects the period of such solutions.  To do this, we build on, and numerically test, the
-assumptions on the fast-slow timescale disparity made in~\cite{bose2011}.  We reduce the
-two-cell model to a scalar Poincaré map that tracks the evolution of the depression from
-the beginning of one burst to the beginning of the next burst.  Stable fixed points of our
-map are associated with stable \(n-n\) burst solutions.  Our map construction is motivated
-by the burst length map of a T-type calcium current, utilised by~\citet{matveev2007},
-which approximates the anti-phase bursting dynamics of a network of two coupled
-Morris-Lecar neurons.  In contrast to our model, the network described in
-the~\cite{matveev2007} paper does not contain short-term synaptic depression, and burst
-termination is instead accomplished through the dynamics of a slow T-type calcium current.
+dynamics.
+This allows us not only to predict the types of stable $n:n$ solutions the full
+network can produce, (for any $n$), but also to study how varying the coupling strength
+affects the period of such solutions.
+To do this, we build on, and numerically test, the
+assumptions on the fast-slow timescale disparity made in~\cite{bose2011}.
+We reduce the two-cell model to a scalar Poincaré map that tracks the evolution of the depression from the beginning of one burst to the beginning of the next burst.
+Stable fixed points of our map are associated with stable $n:n$ burst solutions.
+Our map construction is motivated by the burst length map of a T-type calcium current, utilised by~\citet{matveev2007}, which approximates the anti-phase bursting dynamics of a network of two coupled Morris-Lecar neurons.
+In contrast to our model, the network described in the~\cite{matveev2007} paper does not contain short-term synaptic depression, and burst termination is instead accomplished through the dynamics of a slow T-type calcium current.
 
@@
 full two-cell ODE system: Given the strength of maximum conductance between the two
-neurons, fixed points of our map predict the type and period of \(n-n\) patterns, the switch
+neurons, fixed points of our map predict the type and period of $n:n$ patterns, the switch
 between burst solutions of different periods, as well as the occurrence of co-existent
-solutions.  In addition to proving the existence and stability of fixed points, our map
-shows that fixed points are created via a fold bifurcation of maps.  We also derive
-algebraic conditions that predict the period increment bifurcations that allow the switch
-between \(n-n\) and \((n+1)-(n+1)\) solutions.  Because our map is fully explicit, it lays the
-framework for studying the effects of other model parameter on network dynamics without
-the need to run expensive numerical integrations of the ODEs.
+solutions.
+In addition to proving the existence and stability of fixed points, our map shows that fixed points are created via a fold bifurcation of maps.
+We also derive algebraic conditions that predict the period increment bifurcations that allow the switch between $n:n$ and $(n+1):(n+1)$ solutions.
+Because our map is fully explicit, it lays the framework for studying the effects of other model parameter on network dynamics without the need to run expensive numerical integrations of the ODEs.
 
 % PAPER STRUCTURE.
-This paper is organised as follows.  First, we introduce the network of two neurons, and
-describe the properties of single cell and synapse dynamics.  We use numerical simulations
-of the network to provide an intuition for the range of possible burst dynamics the system
-can produce.  Next, we state and justify the simplifying assumptions that are necessary
-for the map construction.  Finally, we analytically derive the first return map of the
-depression variable as well as the conditions that are required for stable solutions to
-bifurcate between \(n-n\) and \((n+1)-(n+1)\) solutions.  We end this work with a discussion.
+This paper is organised as follows.
+First, we introduce the network of two neurons, and describe the properties of single cell and synapse dynamics.
+We use numerical simulations of the network to provide an intuition for the range of possible burst dynamics the system can produce.
+Next, we state and justify the simplifying assumptions that are necessary for the map construction.
+Finally, we analytically derive the first return map of the depression variable as well as the conditions that are required for stable solutions to bifurcate between $n:n$ and $(n+1):(n+1)$ solutions.
+We end this work with a discussion.

### 2022-03-08 tex/sections/methods.tex
Change notation from n-n to n:n
This is what reviewer 1 suggested.

@@
 When $g$ is large enough, the fixed point moves past the left knee and becomes stable via a subcritical Andoronov-Hopf bifurcation, attracting all previously periodic trajectories.
-In the following section we will refer to the value of the total conductance at the bifurcation as $g_{HB}$.
+In the following section we will refer to the value of the total conductance at the bifurcation as $g_{bif}$.
 
@@
 Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
+% TODO: Edit this later
+It should be noted that \citep{bose2011} used $n-n$ to denote the stable bursts with $n$ spikes, however, here we use the $n:n$ notation for more clarity.

### 2022-03-08 tex/sections/results.tex
Change notation from n-n to n:n
This is what reviewer 1 suggested.

@@
 \subsection{Anti-phase burst solutions}
-Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism \citep{brown1911} and is known to produce $n-n$ anti-phase burst solutions of varying period.
-Such $n-n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
-\Cref{fig:depression-traces}A shows the timecourse of a typical $4-4$ burst.
+Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism \citep{brown1911} and is known to produce $n:n$ anti-phase burst solutions of varying period.
+Such $n:n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
+\Cref{fig:depression-traces}A shows the timecourse of a typical $4:4$ burst.
 While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
@@
 Consistent with \citet{bose2011} we will refer to the currently firing cell as ``\free{}'' and we will call the inhibited cell ``\suppressed{}''.
-Additionally, we will distinguish between two phases of a $n-n$ solution:
+Additionally, we will distinguish between two phases of a $n:n$ solution:
 We will refer to the time interval when a cell is firing as the ``\free{} phase'', and we will call the remaining duration of a cycle, when a cell is not firing, the ``\suppressed{}  phase''.
@@
 Once the \suppressed{} cell becomes \free{} again its synaptic inhibition will be sufficient to terminate the burst of the previously \free{} cell and commence a new cycle.
-% BUG: This is not 100% true, gbar AND the initial conditions uniquely determine the type of n-n pattern.
-As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\bar g$ determines the type of $n-n$ solution.
-Increasing $\bar g$ produces higher $n-n$ burst solutions with more spikes per burst and a longer cycle period.
-\Cref{fig:burst-sols} shows numerically stable $n-n$ solutions for varying values of $\bar g$.
-For small values of $\bar g$ the network produces anti-phase spiking $1-1$ solutions.
-As $\bar g$ is increased the network generates solutions of increasing $n$, that is $2-2$, $3-3$, and $4-4$.
+% BUG: This is not 100% true, gbar AND the initial conditions uniquely determine the type of n:n pattern.
+As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\bar g$ determines the type of $n:n$ solution.
+Increasing $\bar g$ produces higher $n:n$ burst solutions with more spikes per burst and a longer cycle period.
+\Cref{fig:burst-sols} shows numerically stable $n:n$ solutions for varying values of $\bar g$.
+For small values of $\bar g$ the network produces anti-phase spiking $1:1$ solutions.
+As $\bar g$ is increased the network generates solutions of increasing $n$, that is $2:2$, $3:3$, and $4:4$.
 When $\bar g$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
@@
 
-Branches of numerically stable $n-n$ solutions and their associated limit cycle period for varying values of $\bar g$ are depicted in \cref{fig:bif-diagram}A (see \textbf{Supplementary Material S2} for algorithm description).
-Not only do higher $n-n$ solutions branches require stronger coupling $\bar g$, but also within $n-n$ branches the period increases with $\bar g$.
-In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2-2$ and $3-3$ solution branches.
-Branches of higher $n-n$ burst solutions occur on increasingly smaller intervals of $\bar g$, for instance is the $\bar g$ interval of the $5-5$ branch shorter than that of the $4-4$ branch and so on.
-The interval between the $5-5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n-n$ solutions, such as $11-11$ bursts, but also other non-symmetric $n-m$ solutions as well irregular, non-periodic solutions.
-However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n-n$ solutions.
+Branches of numerically stable $n:n$ solutions and their associated limit cycle period for varying values of $\bar g$ are depicted in \cref{fig:bif-diagram}A (see \textbf{Supplementary Material S2} for algorithm description).
+Not only do higher $n:n$ solutions branches require stronger coupling $\bar g$, but also within $n:n$ branches the period increases with $\bar g$.
+In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2:2$ and $3:3$ solution branches.
+Branches of higher $n:n$ burst solutions occur on increasingly smaller intervals of $\bar g$, for instance is the $\bar g$ interval of the $5:5$ branch shorter than that of the $4:4$ branch and so on.
+The interval between the $5:5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n:n$ solutions, such as $11:11$ bursts, but also other non-symmetric $n:m$ solutions as well irregular, non-periodic solutions.
+However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n:n$ solutions.
 
@@
 Both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
-Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n-n$ solutions.
+Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n:n$ solutions.
 However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.
@@
 In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the \suppressed{} phase of the burst.
-$IBI$s lie on multiple branches, each branch associated with a stable $n-n$ solution, and are monotonically increasing with $\bar g$.
+$IBI$s lie on multiple branches, each branch associated with a stable $n:n$ solution, and are monotonically increasing with $\bar g$.
 In contrast, $ISI$s are calculated from the spikes within the \free{} phase and do not vary significantly with $\bar g$, but are approximately $ISI\approx T$, affirming our first assumption.
@@
 We call this critical threshold value the ``release conductance'', denoted by $g^\star$, and define it as the value of $g$ at the time when the voltage of the suppressed cell first crosses the firing threshold $v_{\theta}$, that is when that cell is released and fires its first spike.
-Recall from figure ... that when a cell is suppressed its fixed point is stable and $g > g_{HB}$.
-A sufficient condition for the suppressed cell to be released is therefore $g > g_{HB}$ .
-However, depending on the topology of the stable manifold, the trajectory of the suppressed cell can escape the stable fixed point and allow the cell to produce a spike for $g < g_{HB}$.
-This spike will inhibit the previously firing cell and allow cell 2 to take over the role of the firing cell.
-Moreover, there exists a minimal conductance value $g_{min}$ and a condition $g_{tot} > g_{min}$ that is necessary for the trajectory to pass the fixed point and the cell to spike.
+Recall from figure ... that when a cell is suppressed its $v$- and $w$-nullclines intersect at a stable fixed point and $g > g_{bif}$.
+A sufficient condition for the suppressed cell to be released is therefore $g > g_{bif}$ .
+However, depending on the topology of the stable manifold, the trajectory of the suppressed cell can escape the stable fixed point and allow the cell to produce a spike for $g < g_{bif}$.
+This spike will inhibit the firing cell and allow the previously suppressed cell to start firing.
+Moreover, there exists a conductance value $g^{\star}$ and a condition $g > g^{\star}$ that is necessary for the suppressed cell to be release at all.
+In other words, only when $g > g^{\star}$ is satisfied can the network produce stable $n:n$ solutions, and produces the suppressed solution otherwise.
+The true value of the release conductance will depend on the type of $n:n$ solution and the coupling strength $\bar g$, and will lie in the interval $(g_{bif}, g^{\star})$.
+As we will show in the following section, it turns out that $g^{\star}$ is a good approximation
+
+trajectory to pass the fixed point and the cell to spike.
 We will derive the exact value of such a $g_{min}$ in the following section, and to simplify the derivation our map assume that $g_{min}$ is a good approximation for the release conductance, therefore setting $g^\star = g_{min}$ .
@@
 In summary: We assume that the release condition is sufficient to predict when the \suppressed{} cell is released.
-Due to the symmetry of $n-n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
-The release time therefore uniquely determines the type of $n-n$ solution.
+Due to the symmetry of $n:n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
+The release time therefore uniquely determines the type of $n:n$ solution.
 Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the \suppressed{} cell.
@@
 However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
-In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n-n$ solutions.
+In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n:n$ solutions.
 
@@
 In this section we construct the scalar Poincaré map $\Pi_n:d^{\star}\mapsto d^{\star}$.
-Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n-n$ burst.
+Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n:n$ burst.
 The map $\Pi_n$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
 To simplify the map construction we will assume that a \free{} cell fires exactly $n$ times before it becomes \suppressed{}.
-We will construct $\Pi_n$ by evolving $d$ first during the \free{} phase and then during the \suppressed{} phase of the $n-n$ limit cycle.
+We will construct $\Pi_n$ by evolving $d$ first during the \free{} phase and then during the \suppressed{} phase of the $n:n$ limit cycle.
 First, let us give explicit definitions of the \free{} and \suppressed{} phases.
@@
 Once released, cell 2 also fires $n$ spikes until cell 1 becomes \free{} once again.
-Let $P_n$ denote the full cycle period of a $n-n$ solution:
+Let $P_n$ denote the full cycle period of a $n:n$ solution:
 \begin{equation}
@@
 \end{equation}
-We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n-n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\Delta t$ as a function of $\bar g$ (\cref{fig:delta-t}).
-Each continuous branch of $\Delta t$ is monotonically increasing and corresponds to a $n-n$ burst:
+We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n:n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\Delta t$ as a function of $\bar g$ (\cref{fig:delta-t}).
+Each continuous branch of $\Delta t$ is monotonically increasing and corresponds to a $n:n$ burst:
 Stronger coupling $\bar g$ increases the total synaptic conductance $\bar g s$ that acts on the \suppressed{} cell, thus delaying its release.
@@
 But it is important to add that values $d^{\star}<0$ are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
-Because $\Pi_{n}$ maps first from $d^{\star}$ to $\Delta t$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n-n$ solutions with partially overlapping bursts.
-As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n-n$ solutions of the full system of ODEs only exist for $\Delta t>0$.
+Because $\Pi_{n}$ maps first from $d^{\star}$ to $\Delta t$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n:n$ solutions with partially overlapping bursts.
+As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n:n$ solutions of the full system of ODEs only exist for $\Delta t>0$.
 
@@
 We now turn to the construction of map $Q_n$, which describes the recovery of the depression variable during the \suppressed{} phase.
-As we have identified earlier, the recovery in the \suppressed{} phase of a $n-n$ solution is of duration $(n-1)T + T_{act} + 2\Delta t$.
+As we have identified earlier, the recovery in the \suppressed{} phase of a $n:n$ solution is of duration $(n-1)T + T_{act} + 2\Delta t$.
 Substituting that into the solution of $d$ (\cref{eq:dot-d}) with the initial condition $d(0)=\dn(d^\star) \lambda$ yields the map $Q_{n}$:
@@
 We will therefore restrict the domain of $Q_n$ to $(-\infty, \tau_\kappa\ln{\left[\bar g/(g^\star)\right]})$ and the codomain to $(-\infty, 1)$.
-Additionally, while values $\Delta t>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t = T_{inact}$, and we will address this concern in the last part of our map analysis.
+Additionally, while values $\Delta t>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n:n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t = T_{inact}$, and we will address this concern in the last part of our map analysis.
 
@@
 	\frac{(1-\lambda\delta_n(d^\star)) }{1-d^\star} e^{-((n-1)T + T_{act})/\tau_a}
-	\Big)^{1/\tau}.
+	\Big)^{1/\tau}
 \end{equation}
+is defined for $d^{\star}<1$ and $\delta_{n}(d^{\star})>0$.
 Plotting $d^\star$ against $\bar g$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
@@
 While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the \free{} phase contains exactly $n$ spikes.
-As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n-n$ bursts exists only on certain parameter intervals of $\bar g$.
-In the last sub-section we will analyse the mechanisms that guide how the stable $n-n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\bar g$ where such solutions exist.
+As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n:n$ bursts exists only on certain parameter intervals of $\bar g$.
+In the last sub-section we will analyse the mechanisms that guide how the stable $n:n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\bar g$ where such solutions exist.
 
@@
 \subsection{Period increment bifurcations with co-existent attractors}
-Let $\bar g_+(n)$ and $\bar g_-(n)$ denote the left and right parameter borders on $\bar g$ where stable $n-n$ solutions exist.
-That is, as $\bar g$ is increased stable $n-n$ solutions are created at $\bar g_+(n)$ and destroyed at $\bar g_-(n)$.
-When $\bar g$ is reduced beyond $\bar g_+(n)$, $n-n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\bar g$ is increased beyond $\bar g_-(n)$, $n-n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
+Let $\bar g_+(n)$ and $\bar g_-(n)$ denote the left and right parameter borders on $\bar g$ where stable $n:n$ solutions exist.
+That is, as $\bar g$ is increased stable $n:n$ solutions are created at $\bar g_+(n)$ and destroyed at $\bar g_-(n)$.
+When $\bar g$ is reduced beyond $\bar g_+(n)$, $n:n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\bar g$ is increased beyond $\bar g_-(n)$, $n:n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
 Let us briefly recap our observations regarding $\bar g_+(n)$ and $\bar g_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
@@
 \Cref{eq:easy1,eq:easy2} are self-explanatory.
-\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n-n$ and $(n+1)-(n+1)$ solutions.
-\Cref{eq:robustness} implies that the parameter interval on $\bar g$ of $n-n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
+\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n:n$ and $(n+1)-(n+1)$ solutions.
+\Cref{eq:robustness} implies that the parameter interval on $\bar g$ of $n:n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
 All of the above relations are reminiscent of the period increment bifurcations with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
@@
 \Cref{fig:final-bif} shows the period $P_n(\bar g)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\bar g \in [\bar g_+(n),\bar g_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
-Note that the width of $n-n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
+Note that the width of $n:n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
 That is, bursts with more spikes occur on increasingly smaller intervals of $\bar g$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
-We also note the occurrence of bi-stability between pairs of $n-n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in
+We also note the occurrence of bi-stability between pairs of $n:n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in
 \cref{eq:coexistence}.
@@
 The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\bar g_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
-However, even for branches of large $n-n$ solutions there is a mismatch between the bifurcation borders.
+However, even for branches of large $n:n$ solutions there is a mismatch between the bifurcation borders.
 Presumably our assumptions on the time scales of $w$ and $s$ dynamics do not hold here, and can only be captured by more complex approximations.

### 2022-03-08 tex/supplementary.tex
Change notation from n-n to n:n
This is what reviewer 1 suggested.

@@
 		$T_{inact}$                      & $327$ \si{ms}         \\
-		$\gstar$                         & $0.0036$ \si{mS/cm^2} \\
+		$g^{\star}$                         & $0.0068$ \si{mS/cm^2} \\
+		$g_{bif}$                         & $0.0038$ \si{mS/cm^2} \\
 		$\lambda:=\exp(-T_{act}/\tau_b)$ & $0.612$               \\

### 2022-03-30 tex/response.tex
Change notation from n-n to n:n
This is what reviewer 1 suggested.
Update a bunch of tex files

@@
-\documentclass[utf8]{frontiers_suppmat} % for all articles
+\documentclass[utf8]{article}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
+
+\usepackage{natbib}
+
+% import Eq and Section references from the main manuscript where needed
+\usepackage{xr}
+\externaldocument{manuscript}
+% \externaldocument{methods}
+\externaldocument{supplementary}
+
+\newcommand{\linerange}[2]{%
+\ifthenelse{\equal{\getrefnumber{#1}}{\getrefnumber{#2}}}{%
+line \ref{#1}%
+}{%
+lines \ref{#1}--\ref{#2}%
+}%
+}
+% package needed for optional arguments
+\usepackage{xifthen}
+\renewcommand{\thefigure}{R\arabic{figure}}
+
 \usepackage{url,hyperref,lineno,microtype}
+
 \usepackage[onehalfspacing]{setspace}
+\usepackage{graphicx}
+\usepackage{amsmath}
 \usepackage{cleveref}
@@
 \usepackage{xr}
+\usepackage{bm}
+\usepackage{cases}
+
 \graphicspath{{../figures/}}
-\externaldocument{draft}
 
-\renewcommand{\d}{\mathrm{d}}
-\renewcommand{\k}{\mathrm{K}}
-\newcommand{\ca}{\mathrm{Ca}}
-\newcommand{\na}{\mathrm{Na}}
-\newcommand{\leak}{\mathrm{L}}
-\newcommand{\dstar}{d^\star}
-\newcommand{\gstar}{g^\star}
-\newcommand{\gbar}{\bar g}
-\newcommand{\delt}{\Delta t}
-\newcommand{\taus}{\tau_s}
-\newcommand{\dn}{\delta_n}
-\newcommand{\taud}{\tau_d}
+\setcounter{section}{0}
+\newcounter{point}[section]
+\setcounter{point}{0}
 
-% Leave a blank line between paragraphs instead of using \\
+% command declarations for reviewer points and our responses
+
+\newenvironment{point}
+{\refstepcounter{point} \bigskip \noindent {\textbf{Point~P\thesubsection.\arabic{point}} } ---\ }
+{\par }
+
+\newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent
+	{\textbf{Point~P\thesubsection.\arabic{point}} } ---~#1\par }
+
+\newenvironment{reply}
+{\medskip \noindent Reply:\  }
+		{\medskip}
+
+\newcommand{\shortreply}[2][]{\medskip \noindent Reply:\  #2
+		\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
+		\medskip}
 
 \begin{document}
-\onecolumn
-\firstpage{1}
+% \onecolumn
+% \firstpage{1}
 
-\title[Response]{{\helveticaitalic{Response}}}
-\maketitle
+\begin{center}
+	\Large Response to the reviewers
+\end{center}
+We thank the reviewers for their critical assessment of our work.
+The biggest changes in the revised manuscript came as a result of points \hyperref[p:biol]{P2.1.1} and \hyperref[p:gstar]{P2.3.8}, which led us to revert our model to the original equations and parameter values used in \cite{bose2011}.
+The motivation behind a slightly different model in our original manuscript, as well as the consequence of the latest changes in the revised manuscript are given in \cref{sec:model}.
+Both reviewers also pointed out that some of our notation and terminology is unclear.
+As a result we renamed many of the terms, an overview of the most important terms is given in \cref{sec:terminology}.
 
-% TODO: Add line numbers everywhere.
-\section{Minor changes}
-\subsection{Changes to the nullclines plot}
-In order to reduce the number of figures we have merged figures 1 and 5, and adjusted added a paragraph describing the non-zero constant synaptic conductance case at the end of the methods part.
+We will refer to the first version of the manuscript that was submitted to the journal as ``original manuscript'' (M0), and we will call the latest submitted version the ``revised manuscript'' (M1).
+If not otherwise stated, the equations numbers, figures, and line numbers refer to the revised manuscript.
+This response is structured as follows:
+\Cref{sec:sum} contains the terminology as well as summarises the main model changes in the revised manuscript.
+In \cref{sec:r1} we address the concerns raised by reviewer 1, and in \cref{sec:r1} the concerns raised by reviewer 2.
 
-\section{Release delay}
-Due to the changes to the single cell model parameters, i.e.
-reducing the applied current from $I=6 \si{\mu A/cm^{2}}$ to $I=3.8\si{\mu A/cm^{2}}$, the $v$-nullcline moved down along the $w$-nullcline.
-% I've checked that old HB value manually, should be correct.
-This made the system become more excitable, that is the subcritical Andronov-Hopf bifurcation point where the fixed point changes stability moved from $\bar g=0.038$ to $\bar g=0.0038$.
-As a consequence, the release delay seen previously is now negligible for all $n:n$ solutions, see figure \cref{fig:release-delay}.
+\section{Summary of changes}
+\label{sec:sum}
+
+\subsection{Terminology and notation}
+\label{sec:terminology}
+To increase clarity we have changed some of the terminology.
+Below we briefly define the controversial terms.
+In the context of a spiking limit cycle of an uncoupled Morris-Lecar (ML) cell we have:
+\begin{itemize}
+	\item $T_{a}$: The time interval when the voltage is above firing threshold, i.e. when $v>v_{\theta}$.
+	\item $T_{s}$: The time interval when the voltage is below firing threshold, i.e. when $v<v_{\theta}$.
+\end{itemize}
+In the context of a stable $n:n$ solution we have:
+\begin{itemize}
+	\item \textbf{Active cell}: Cell that is currently firing.
+	\item \textbf{Silent cell}: Cell that is currently suppressed and does not fire.
+	\item \textbf{Active phase}: Time interval between the start of the limit cycle and the time when the voltage of the active cell falls below firing threshold after the $n$th spike, i.e.
+for $t \in \left[0, (n-1)T + T_{a}\right]$.
+	\item \textbf{Silent phase}: Time interval after the end of the active phase and the cycle period, i.e. for $t \in \left[(n-1)T + T_{a}, P\right]$.
+	\item \textbf{Active phase map}: Map $F_{n}$ that models the evolution of $d$ during the active phase.
+	\item \textbf{Recovery phase map}: Map $Q_{n}$ that models the evolution of $d$ during the silent phase.
+	\item \textbf{Left and right branch borders}: The left and right branch borders of stable $n:n$ solutions are denoted by $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$, respectively.
+\end{itemize}
+
+\subsection{Model changes}
+\label{sec:model}
+% Overview
+In this section we first explain the model differences between the \cite{bose2011} paper and our original manuscript.
+We will then outline a short motivation for these changes.
+Finally the model of the revised manuscript is discussed.
+There are two main differences in the model equations and parameters between the original manuscript and \cite{bose2011}:
+First, the value of the applied current $I$ is different: In \cite{bose2011} they have $I=3.8$ $\si{\mu A/cm^2}$, in the original manuscript we had $I=3.8$ $\si{\mu A/cm^2}$.
+Second, the original manuscript used step-wise resets of $d$ and $s$ to simplify the dynamics of the active state of the spike (when $v > v_{\theta}$).
 
@@
 	\centering
-  \includegraphics[width=0.8\textwidth]{release-delay.pdf}
-  \caption{Numerically computed graph of the release delay as a function of $\bar g$~\label{fig:release-delay}}
+	\includegraphics[width=0.9\textwidth]{model-changes}
+	\caption{Nullclines of the \cite{bose2011} ML model with $I=3.8$ $\si{\mu A/cm^2}$ (left), and the model from our original manuscript with $I=6$ $\si{\mu A/cm^2}$ (right).
+The solid blue lines are the $v$-nullclines when $\bar g s=0$.
+The dashed blue lines are the $v$-nullclines when $\bar g s$ is near the respective bifurcation point where the fixed point changes stability.\label{fig:nullclines}}
 \end{figure}
 
-\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
+The main motivation for increasing $I$ in the original manuscript had to do with the excitability of a silent ML cell, and was to simplify the explanation of the concept of the ``release conductance''.
+\Cref{fig:nullclines} shows the $v$- and $w$-nullclines for $I=3.8$ $\si{\mu A/cm^2}$ (left) and for $I=6$ $\si{\mu A/cm^2}$ (right) when no inhibition is applied and $g = 0$ (let $g:= \bar g s$).
+The dashed lines indicate the $v$-nullcline at the bifurcation point when the total synaptic conductance $g$ is at the respective bifurcation value, $g=g_{bif}$.
+In case of $I=3.8$ $\si{\mu A/cm^2}$ we have $g_{bif}\approx 0.007$ $\si{\mu A/cm^2}$, whereas for $I=6$ $\si{\mu A/cm^2}$ we have $g_{bif}\approx 0.03804$ $\si{\mu A/cm^2}$.
+Hence for $I=3.8$ $\si{\mu A/cm^2}$ and $g=0$, the unstable fixed point is ``closer'' in phase space to the stable fixed point at bifurcation when $g=g_{bif}$, than in case of $I=6$ $\si{\mu A/cm^2}$.
+In other words, a silent cell with $I=3.8$ $\si{\mu A/cm^2}$ is ``easier to excite'' than a silent cell with $I=6$ $\si{\mu A/cm^2}$.
+
+In contrast to the $I=6$ $\si{\mu A/cm^2}$ scenario, when $I=3.8$ $\si{\mu A/cm^2}$ the bifurcation at $g=g_{bif}$ is not sufficient to accurately predict the release time of the silent cell, as the silent cell can produce a first spike despite $g > g_{bif}$.
+Why this happens is interesting but not trivial, and we believe that at this stage it is not important.
+However, when $I=6$ $\si{\mu A/cm^2}$ the condition $g>g_{bif}$ becomes sufficient to accurately predict the release time of the silent cell, that is assuming $n>1$ and with the exception of the $2:2$ outliers in fig.
+6 (original manuscript).
+When $g>g_{bif}$ is sufficient for predicting the release time, the definition of the release conductance $g^\star$ becomes straightforward, that is $g^\star=g_{bif}$.
+Moreoever, the value of $g^\star$ can be computed numerically, for example using AUTO.
+The downside of using $I=6$ $\si{\mu A/cm^2}$ is that finding $g^\star$ analytically becomes difficult.
+Because reviewer 1 asked for an analytic derivation of $g^\star$ in point \hyperref[p:gstar]{P2.3.8}, and to avoid more confusion by using a different model than \cite{bose2011}, we decided to use $I=3.8$ $\si{\mu A/cm^2}$ in the revised manuscript.
+As explained above, however, this comlicates the definition and explanation of $g^\star$:
+Now the actual value of the release conductance (as defined by the value of $g$ at the first spike time of the silent cell) depends on both $n$ and $\bar g$, as we illustrate in \cref{fig:gstar-diag}A.
+But as the graph also shows, the dashed line appears to be a good approximation for the numerically computed release conductances.
+This line marks the value of $g$ of a suppressed and $\bar g= \bar g_s$, at the end of a cycle.
+Here that $\bar g_s$ is smallest value of $\bar g$ that produces the suppressed solution.
+And this values is easy to express analytically:
+\begin{equation}
+	\bar g_s d_s\lambda e^{-T_{s}/\tau_\kappa}=g^{\star} \approx 0.0068\, \si{mS/cm^2}.
+\end{equation}
+Another advantage of using $I=3.8$ $\si{\mu A/cm^2}$ is that all release delays are on the millisecond scale, and there are no more outliers such the branch B in fig. 6 (M0).
+
+The main motivation for changing the synapse model was mathematical convenience, as it made the $\Pi_{n}$-map formulation more readable.
+This change does not appear to affect the overall picture, i.e. the period bifurcation diagram has a similar shape even after our change, e.g. compare fig. 4A (M0) to \cref{fig:bif-diagram} (M1).
+However, the biological realism of the step-wise resets of $s$ and $d$ in the original manuscript were correctly questioned by reviewer 1 in \hyperref[p:biol]{P2.1.1}.
+We hope that reverting to the original equations used in \cite{bose2011} solves this concern.
+
+To sum up the model changes:
+The revised manuscript has $I=3.8$ $\si{\mu A/cm^2}$, and synaptic dynamics are modelled by
+
+\begin{align*}
+	\dot d & =
+	\begin{cases}
+		(1-d)/\tau_{a} & \text{ if }\, v<v_{\theta}, \\
+		-d/\tau_{b}    & \text{ if }\, v>v_{\theta},
+	\end{cases}
+\end{align*}
+
+\begin{align*}
+	\dot s & =
+	\begin{cases}
+		-s/\tau_{\kappa} & \text{ if }\, v<v_{\theta}, \\
+		0                & \text{ if }\, v>v_{\theta},
+	\end{cases}
+\end{align*}
+and we set $s=d$ while $v>v_{\theta}$.
+All equations and derivation in the process of the construction of $\Pi_n$ were modified accordingly.
+It is important not note that $\lambda$ is a \textit{derived} parameter in the revised manuscript:
+\begin{equation}
+\lambda := \exp(-T_s/\tau_a).
+\end{equation}
+Naturally all the data for all figures was recomputed with the new model.
+Fig. 5 (M0) was removed.
+Because $g^\star$ is not defined by the Hopf-bifurcation in the revised manuscript, an illustration of the nullclines as $\bar g s$ is varied seems to be of minor importance.
+Fig. 6 (M0) was also removed, since the new definition of $g^\star$ does not produce a significant release delay.
+
+\subsection{Other minor changes}
+
+\begin{itemize}
+	\item In Fig.
+1 (M0) we removed the four phases of a spike (``active'', ``silent'', ``jump up'', ``jump down'').
+We did this to reduce the terminology confusion regarding ``free''/``quite'' vs ``active''/``silent'', pointed out by reviewer 1 in P2.2.1.
+As suggested by the reviewer, in the revised manuscript we use ``active''/``silent'' to refer to the two phases of burst only.
+	\item Fig. 4B (M0) was removed, as $IBI$ is not clearly defined and is confusing.
+	\item $T_{act}$ and $T_{inact}$ were renamed to $T_a$ and $T_s$, respectively.
+	\item $\bar g_{+}$ and $\bar g_{-}$ were renamed to $\bar g_{\mathcal{L}}$ and $\bar g_{\mathcal{R}}$, as a response to point P2.3.19 raised by reviewer 1.
+\end{itemize}
+
+\section{Reviewer 1}
+\label{sec:r1}
+\subsection{Major Comments}
+\setcounter{point}{0}
+
+\begin{point}
+\label{p:biol}
+I don't see the justification for assuming $\dot d=(1-d)/\tau_{d}$ when a neuron is ACTIVE (see below for ``active'' meaning).
+Can the authors provide some biological justification that the available synaptic resources actually increase during a spike?
+If not, it seems critical that they give some other justification that this assumption is OK.
+\end{point}
+\begin{reply}
+We agree with the reviewer's criticism.
+Beyond mathematical convenience there was no biological justification for making the assumption that the depression variable recovers when $v>v_{\theta}$.
+In the original model from \cite{bose2011} $d$ decays when $v>v_{\theta}$:
+\begin{align*}
+  \dot d_{i} &= \begin{cases}
+  (1-d_{i})/\tau_{a} &  \text{ if } v_{i}<v_{\theta},
+  \\
+  -d_{i}/\tau_{b}    &  \text{ if } v_{i}>v_{\theta},
+  \end{cases}
+\end{align*}
+which is now also used in the revised manuscript, see eq. (\ref{eq:dot-d-up}) and (\ref{eq:dot-d-down}).
+\end{reply}
+
+\shortpoint{The authors assume that each spike has duration $T$.
+But that can only be true exactly if the $s$ variable from the silent neuron is 0, which is never the case.
+The authors should compute how fast $s$ has to decay to make period=T a reasonable approximation even in the first spike of a burst, and some commentary about this should be given.}
+\begin{reply}
+We agree that $\tau_{\kappa}$ is important for the $ISI=T$ assumption.
+The paragraph outlining the is assumption in \cref{sec:assumptions} of the main text has been edited to highlight the importance of $\tau_{\kappa}$ for the validity of that assumption.
+We have also added \cref{sec:tauk} to the Supplementary Material where we numerically explore how changing the value of $\tau_{\kappa}$ affects the first, second, and third $ISI$.
+There we come to the conclusion that for $\tau_{\kappa} \leq 100$ $\si{ms}$ the effect of a non-zero $s$ at the start of the active phase is negligible for the first, and naturally the subsequent, $ISI$s.
+\end{reply}
+
+\subsection{Terminology}
+\setcounter{point}{0}
+
+\begin{point}
+	First, the authors refer to the neurons as ``free'' or ``quiet'' and refer to the ``free phase'' and ``quiet phase''.
+	They say that they follow Bose and Booth in doing so.
+	But I have read (and written) MANY papers on bursting\slash CPGs\slash multi-phase solutions, and they always refer to ``active'' and ``silent'' rather than ``free'' and ``quiet''.
+	The authors should switch their word use as well to avoid confusing the field.
+\end{point}
+\begin{reply}
+	We agree that the ``free''\slash``quiet'' terminology is uncommon in the field.
+	When referring to a cell in the context of $n:n$ limit cycles, apart from being consistent with \citet{bose2011}, our original intent was to use the ``free''\slash``quiet'' terms to distinguish them from the phases of the action potential, where we used the more common ``active''\slash ``silent'' terms.
+	However, as reviewer 1 has pointed out, using ``active''\slash``silent'' to refer to both the phases of a spiking limit cycle \cite[e.g.~p.~250]{ermentrout2010}, and the bursting limit cycle \cite[e.g.~p.~103]{ermentrout2010} (at least in the context of ``bursty'' single cells) appears to be more common in the field.
+	For the construction of $\Pi_{n}$ only the distinction between the active ($v>v_{\theta}$) and quiet ($v<v_{\theta}$) states of an action potential, and the associated times intervals $T_{a}$ and $T_{s}$, are essential.
+	To reduce confusion we have therefore removed the mention of the ``four phases of a spike'' (lines 112-118 in M0), such that in the new version of the manuscript ``active'' and ``silent'' refer exclusively to the phases of a $n:n$ solution.
+	We hope that this clarification is sufficient to be consistent with the field, but if this is still confusing we are open for further naming suggestions.
+\end{reply}
+
+\shortpoint{Second, the authors use $ISI$ and $IBI$ incorrectly.
+The $ISI$ is the inter-spike interval.
+This is the period BETWEEN spikes, NOT the entire period T of a spiking event (see e.g., line 181).
+The $IBI$ is the inter-burst interval.
+In this paper, that would be the silent phase duration for one neuron.
+It is NOT the entire period of a bursting event, nor is it the delay from the end of one neuron’s active phase to the start of the other neuron’s active phase (e.g., line 266).
+These need to be corrected throughout the paper.}
+\begin{reply}
+We agree with the reviewer that the $IBI$ notation is misleading, and it has been completely removed from the manuscript.
+For the inter-spike-interval $ISI$ we have used what we believe is the standard definition \cite[e.g. see][]{ermentrout1998,bose2011,matveev2007}:
+The $ISI$ is the time interval between successive spike times, where a spike time is the time when the voltage crosses the firing threshold upwards, i.e.
+the time when $v$ changes from being below the firing threshold to being above it.
+In the case of an uncoupled ML cell we have $ISI=T$.
+If this definition of the $ISI$ is not common in the field, then we kindly ask the reviewer to point us to references where a different, more common definition is used.
+\end{reply}
+
+\shortpoint{Third, in the Results, the authors state the signs of various derivatives without proof.
+Some are obvious (e.g., eqn.
+(30)) but others, such as eqn.
+(31), are not.
+Some brief justification is needed.}
+\begin{reply}
+Agreed. We have added a brief explanation regarding the monotonicity of $\Pi_{n}$ w.r.t. $d^{\star}$ (line \ref{line:mono}), which follows from the monotonicity of both $Q_{n}$ and $F_{n}$.
+Showing $\dv*{Q_{n}}{\Delta t} > 0$ and $\dv*{F_{n}}{d^{\star}} > 0$ for our model parameters is uncomplicated.
+\end{reply}
+
+\shortpoint{Fourth, Fig.
+11A seems to contrast with Fig.
+4A.
+Fig.
+11A seems to show massive multistability of solutions for different $n$, whereas Fig.
+4A only has bistability.
+Some clarification is needed}
+\shortreply{Figure 11A (M0) shows stable fixed points of $\Pi_{n}$ for different $n$.
+Figure 4A (M0) shows the period of stable $n:n$ solutions for the flow system.
+The map $\Pi_{n}$ relies on the assumption that the active phase contains exactly $n$ spikes.
+This assumption is only valid on certain intervals of $\bar g$, namely those defined by $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$.
+We have added some additional clarification in line \ref{line:ll}.}
+
+\shortpoint{And fifth, the notation $n-n$ is non-ideal, as it looks like $n$ minus $n$. In my opinion, $n:n$ is more standard and clearer.}
+\shortreply{Thank you for this suggestion, as it especially makes the $(n+1):(n+1)$ easier to read. As suggested, we have replaced the $n-n$ notation with $n:n$ everywhere in the revised manuscript.}
+
+\subsection{Minor Comments}
+\setcounter{point}{0}
+
+\shortpoint{Line 31: It’s a CPG composed of reciprocally inhibitory neurons; referring to a ``reciprocally inhibitory CPG'' is misleading.}
+\shortreply{Agreed. We changed ``reciprocally inhibitory CPG'' to ``CPGs composed of reciprocally inhibitory neurons'' in line \ref{line:A}.}
+
+\shortpoint{The par.
+starting on line 38 is unclear: The $1-d$ conditions for $n:n$ solutions in [6] are stated to be for $n\leq 2$ (line 43); the authors should clarify if $n:n$ in line 48 also refers to $n \leq 2$ or not.}
+\shortreply{Agreed. We added a clarification that the scalar conditions are valid only for $n\leq 2$ (line \ref{line:B}).}
+
+\shortpoint{Results line 130: It is important to note that both neurons inhibit each other at all times. $s$ may get small but it's nonzero. Thus, ``inhibited'' cell is not really well-defined.}
+\shortreply{Agreed. We changed ``inhibited cell'' to ``suppressed cell'', and added a short explanation, see \linerange{line:C1}{line:C2}.}
+
+\shortpoint{Line 137: Wang \& Rinzel, 1992 (and perhaps Skinner et al. from 1993 or 1994) should be cited in reference to release.}
+\shortreply{Added the \cite{wang1992} and \cite{skinner1994} references when ``release'' is mentioned in line \ref{line:D}.}
+
+\shortpoint{I don’t understand Fig.
+4B.
+The ISI is less than the IBI, so how can their ratio be bigger than 1?
+Or perhaps the axis label ``ISI/IBI'' does not refer to ISI divided by IBI?
+Clarification is needed.}
+\shortreply{The $IBI$ notation was indeed unclear, and did not help in explaining our model assumptions, thank you for pointing this out.
+All mentions of $IBI$, as well as Fig.
+4B (M0), have been removed from the revised manuscript.
+Instead, we provide a more straightforward numerical argument for the $ISI=T$ assumption in \linerange{line:E1}{line:E2}: For every stable $n:n$ solution in the period bifurcation diagram (\cref{fig:bif-diagram} in the revised manuscript), we compute all $ISI$s and find that they all fall within the interval $\left[376, 377\right]$ $\si{ms}$.}
+
+\shortpoint{Line 200: “revolve” should be replaced by “evolve”.}
+\shortreply{The whole paragraph formerly starting at line 194 (M0) has been rewritten.}
+
+\shortpoint{Line 213 is incorrect: It’s not the decay of $d$ that matters but the decay of $s$ before the next spike occurs.
+Correction needed - except now I realize that lines 207-219 can be cut, as they add nothing relative to the previous paragraph.}
+\shortreply{Definition of $g^{\star}$ was changed due to the change in equations, consequently the paragraph formerly starting in line 207 (M0) was removed.}
+
+\begin{point}
+\label{p:gstar}
+It seems like the authors should be able to analytically compute or at least approximate $g^{\star}$ and should give some explanation for the delay in Fig.
+6A, left branch.
+This must relate to the silent cell spending too short of a time in the silent phase.
+Fig.
+4 is certainly relevant.\label{p:release-delay}
+\end{point}
+\shortreply{Thank you for this remark. Due to the aforementioned model changes and redefinition of $g^{\star}$ we can now express $g^{\star}$ explicitly in \cref{eq:gstar}.}
+
+\shortpoint{Lines 246-7: The authors should revise because $s$ is determined by $d$ and by $\tau_{s}$.}
+\shortreply{Agreed.
+In line \ref{line:E} we clarify that the value of $s$ ``at each spike time'' of the active cell depends only on $d$.
+This is because in the revised synapse model (eq.
+(\ref{eq:dot-s-up})) $s$ is set to the value $d$ when $v>v_{\theta}$.}
+
+\shortpoint{Line 270: It seems like the active phase ends at time $(n-1)T+\Delta t$, yet the authors say it ends at $(n-1)T$.
+This may be more convenient for their analysis but it’s not correct usage of the phase terminology, so clarification is needed.}
+\begin{reply}
+It is indeed misleading when we let the active phase end at $(n-1)T$, since this time is the beginning of the last spike of the active cell.
+The change of the model to \citet{bose2011} original equations, where $T=T_{a}+T_{s}$, and the according redefinition of the active phase hopefully clarifies this issue.
+In the revised manuscript the active phase ends at $(n-1)T + T_{a}$, which is also the time when the previously active cell becomes silent.
+\end{reply}
+
+\shortpoint{It’s disorienting to see $\delta_n(d*)$ in eqn. (20) when just above (line 320) the same quantity is called $d_n = d(t_n^{-})$. The authors should pick one notation for both places.}
+\shortreply{Agreed. We have removed the $d_{n}$ notation completely.}
+
+\shortpoint{Cut line 339 and equation (27). These add a bit of confusion and nothing else.}
+\shortreply{We believe that line 339 (M0) and eqn.
+(27) (M0) (\cref{eq:dn} in M1) are central to understanding the derivation of map $Q_{n}$.
+Eqn.
+(27) (M0) implies that if we know $\Delta t$, then we can predict the value of the depression variable of the active cell after $n$ spikes.
+This statement is not trivial because when computing $Q_{n}$ we have no knowledge of the initial $d^{\star}$.
+We have added some additional explanation in line \ref{line:abc} and would suggest to leave eqn.
+(27) (M0) as it is.}
+
+\shortpoint{Fig. 9 caption: mention where the $Q_n$ curves intersect.}
+\shortreply{Added intersection to caption in \cref{fig:FQ-maps}.}
+
+\shortpoint{Eqn. (29): remind the reader that $\delta_n(d^{\star})$ comes from eqn. (20) and that $g^{\star}$ is obtained numerically.}
+\shortreply{Added reminder in line \ref{line:remind}.}
+
+\shortpoint{Lines 364-6 including eqn. (36) should be cut – they are neither new nor helpful here.}
+\shortreply{Agreed. Lines have been removed as suggested.}
+
+\shortpoint{Eqns. (37),(38) can and should be combined.}
+\shortreply{Combined as suggested.}
+
+\shortpoint{Eqn. (44) is confusing: here the authors want $d_f^\star = \phi_h(\bar{g})$, so it’s strange to express it as a function of $d_f^\star$ again.}
+\shortreply{The $d_{f}^{\star}$ in eqn. (44) (M0) was a typo, thank you for pointing this out. It should be
+  \begin{equation}
+  \phi_{n}(\bar g) := G^{-1}(\bar g).
+  \end{equation}
+  Corrected accordingly in \cref{eq:phi}.
+}
+
+\shortpoint{Fig. 11B needs more explanation, such as a reminder that the orange curves are only computed over small intervals of $\bar{g}$ where the solution branch is stable.}
+\shortreply{Agreed. Added reminder in the \cref{fig:final-bif} caption that the orange curves are computed from stable $n:n$ solutions that come from numerical integration of the system.}
+
+\shortpoint{The notation $\bar{g}_{+}(n) < \bar{g}_{-}(n)$ seems strange – seems like these should be reversed (the math is fine, I’m questioning the choice of notation).}
+\shortreply{We changed the $\bar{g}_{+}(n) < \bar{g}_{-}(n)$ notation to $\bar{g}_{\mathcal{L}}(n) < \bar{g}_{\mathcal{R}}(n)$, where the $\mathcal{L}$ and $\mathcal{R}$ subscripts stand for ``left'' and ``right'' branch borders.}
+
+\shortpoint{Line 415: [21] is cited twice.}
+\shortreply{Corrected.}
+
+\shortpoint{Rather than stating eqn. (54), it would be clearer just to reference eqn. (47) there.}
+\shortreply{Agreed. We removed eqn. (54) (M0) and referenced eqn. (47) (M0), see line \ref{line:bbb}.}
+
+\shortpoint{A better explanation of what is shown in Fig. 12 is needed. Is this $\bar{g}_{+}(n)$ and $\bar{g}_{-}(n)$ for various n, computed numerically from (56) and (58)?}
+\shortreply{Agreed. A short clarification was added in the text and captions to \cref{fig:final-bif}.}
+
+\shortpoint{Discussion lines 459-462: Please explain what such “light” has been shed here.
+If none, as it appears, that’s OK for this math paper, but then this comment doesn’t really belong in the discussion.}
+\shortreply{Agreed, our formulation was indeed misleading.
+This paper does not provide much insight on the underlying biological mechanisms in anti-phase burst generation.
+Instead, by ``underlying mechanisms'' we were referring to the ``mathematical principles'', e.g.
+importance of model parameters for the rhythm etc.
+A clarification was added in the text, line \ref{line:principle}.}
+
+\shortpoint{I’m confused about lines 534-6. I have never heard of learning in a CPG. Please clarify what is meant.}
+\shortreply{An elaborate explanation of learning in CPGs seems to be beyond the scope of this paper, and we have removed the learning reference.
+If the reviewer is interested the topic ``learning in CPGs'', please consider \citet{lukowiak1999}, where the authors experimentally study learning through operant conditioning in the respiratory CPG of the Lymnaea stagnalis snail, which consists of three inter-neurons.
+Interestingly, they show that in this CPG learning seems to occurs on both the synaptic level (change in connection strength), and cell-intrinsic level (changes in membrane properties).}
+
+% % Begin a new reviewer section
+% \reviewersection
+
+% \begin{point}
+% 	This is the first point of Reviewer \thereviewer. With some more words foo
+% 	bar foo bar ...
+% \end{point}
+
+% \begin{reply}
+% 	Our reply to it with reference to one of our points above using the \LaTeX's
+% 	label/ref system (see also \ref{pt:foo}).
+% \end{reply}
+
+\section{Reviewer 2}
+\label{sec:r2}
+\subsection{Major Comments}
+\textbf{Note on terminology and notation for reviewer 2:} In our replies to reviewer 2 we used the same terminology as used in the original manuscript.
+This is because the majority of the terminology changes were suggested by reviewer 1.
+In the following replies we wanted to focus on the content of the points raised by reviewer 2, instead of burdening them with new terminology.
+\setcounter{point}{0}
+
+\begin{point}
+My major concern is about a few inaccuracies in the terminology.
+The authors several times repeat that $n - n$ solution ``bifurcates'' to $(n + 1) - (n + 1)$ one (page 3, line 78; page 8, line 281; page 11, line 346; page 14, lines 3-4 of Sec.
+3.6; page 14, line 423).
+I cannot fully agree with such a formulation, since (as follows, e.
+g., from Eqs.
+(51) and (52)) there are ranges of the bifurcation parameter (coupling strength) $\bar g$ where two subsequent solutions coexist.
+When one says that solution A ``bifurcates'' to solution B, it usually means that before the bifurcation only solution A exists and after the bifurcation only solution B exists, which is not the current case.
+The authors should revise this point to avoid confusion.
+\end{point}
+
+\begin{reply}
+We agree with the reviewer's formulation of ``bifurcation'', i.e.
+before the bifurcation point only solution A exists and after only solution B, and that bistability between $n-n$ and $(n+1)-(n+1)$ solutions should not be referred to as ``bifurcation''.
+However, doesn't the loss of stability at the left and right branch borders qualify for the reviewer's definition of bifurcation?
+That is, near the right border $\bar g_{-}(n)$ of a $n-n$ branch, as $\bar g$ is increased beyond $\bar g_{-}(n)$ the $n-n$ solution ``bifurcates'' into a $(n+1)-(n+1)$ solution when the $n-n$ solution loses stability (similarly near the left branch border as $\bar g$ is decreased).
+This use of the term ``bifurcates'' is consistent with \cite{bose2011}, e.g.
+see p.
+48: ``\dots, we will analytically explain why the bifurcation from a $n-n$ solution occurs at periods of $2nT$'' or p.
+49: ``Further, the condition also implies that a $1-1$ solution bifurcates to another solution when \dots''.
+The lines in the original manuscript that were pointed out by the reviewer use the term ``bifurcates'' to refer to these branch borders.
+Unless we are misunderstanding the reviewer, we would suggest to leave these lines unchanged.
+However, we are open for an alternative terminology that more accurately describes what is happening at the branch borders.
+\end{reply}
+
+\begin{point}
+By the same reason, I suggest the authors to avoid the term ``period increment bifurcation'' (page 1, line 15; page 2, line 69; page 14, lines 408, 413, 416 and 419; page 17, lines 509 and 516), and moreover, such term does not exist.
+The confusion could have been appeared because of the title of Ref.[23].
+The authors of that reference meant a particular type of the big bang bifurcation, where the latter is a codim-2 bifurcation, an organizing center.
+On the other hand, one can refer to the period increment bifurcation structure (or scenario), which consists of the parameter regions corresponding to periodic dynamics (periodicity regions) that are organized in the parameter space according to a particular principle.
+However, the bifurcations defining the boundaries of these periodicity regions may be different.
+For instance, in works by Avrutin et al. the boundaries of such regions were associated with boundary collision bifurcations, since the map there considered was discontinuous.
+In the current work, it is not clear which bifurcation is responsible for appearance/disappearance of the $n-n$ solution.
+It is not a trivial question and certainly requires deeper analysis, but it is incorrect to call it ``period increment bifurcation''.
+\end{point}
+\begin{reply}
+This comment is very helpful, thank you.
+The reviewer is correct, the term ``period increment bifurcation'' does not exist, Avrutin and colleagues indeed only use the terms ``period increment scenario'' or ``structure''.
+Throughout the revised manuscript we have replaced the term ``period increment bifurcation'' by one of the  following: ``period increment scenario'', ``period increment dynamics'', or simply ``bifurcation''.
+The changed lines in the revised manuscript are: line \ref{line:abstract}, line \ref{line:branchA}, line \ref{line:branchB}, and \linerange{line:disc-pincA}{line:disc-pincB}.
+The \cref{sec:borders} title was changed to ``Stable solution branch borders''.
+\end{reply}
+
+\subsection{Minor Comments}
+\setcounter{point}{0}
+
+\shortpoint{Page 2, line 36: change “explaination” to “explanation”.}
+\shortreply{Corrected.}
+
+\shortpoint{Page 5, line 158: insert “as” between “well” and “irregular”.}
+\shortreply{Corrected.}
+
+\shortpoint{Page 5, line 158: It is claimed that in the certain range of the parameter $\bar g$ (marked in fig.
+4A), there exist non-symmetric $n-m$ and even irregular solutions.
+Non-symmetric solutions are mentioned once more in Sec.
+4 in connection with an asymmetric coupling.
+Can such solutions indeed appear in the symmetric version of the system?
+If yes, could the authors provide an example?
+Or alternatively, the respective sentence in line 158 can be developed a bit concerning this point.}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.7\textwidth]{irregular}
+\caption{Voltage traces of an ``irregular'' solution with $\bar g=0.581$ $(\si{mS/cm^{2}})$. \label{fig:irregular}}
+\end{figure}
+
+\begin{reply}
+\Cref{fig:irregular} shows an example of the aforementioned ``irregular'' solutions.
+The figure was produced with strong symmetric coupling $\bar g=0.581$ $(\si{mS/cm^{2}})$, which is close to the $\bar g_{s}$ associated with the left border of the branch of suppressed solutions.
+An integration time step of $dt=0.5$ $\si{ms}$ was used.
+To get rid of transients the system was integrated for $500,000$ $\si{ms}$, and \cref{fig:irregular} shows the last $20,000$ $\si{ms}$.
+It would be interesting to explore how chaotic the system is for large $\bar g$, but this would likely distract from the main story of the paper, which is also the main reason why we have not included this graph in the paper.
+\end{reply}
+
+\shortpoint{Page 6, line 183: The authors probably meant “fig. 4B” instead of “fig. 4A”, as the latter does not show ISI (only for the suppressed solution when it is equal to the period).}
+\shortreply{Fig. 4 (M0) was removed from the paper.}
+
+\shortpoint{Page 7, line 235: Did the authors mean ``$\bar g s$ crosses $g^{\star}$''?}
+\shortreply{Corrected.}
+
+\shortpoint{Page 7, line 246: It should be “$g^\star$” instead of “$g^*$” like throughout the manuscript.}
+\shortreply{Corrected.}
+
+\shortpoint{Page 12, line 371: It should be “is not trivial”.}
+\shortreply{Corrected.}
+
+\shortpoint{In Eq. (44) the function $G^{-1}_{n}$ cannot depend on $d^{\star}$, please revise.}
+\shortreply{Indeed, thank you for spotting this. $G^{-1}_{n}$ depends on $\bar g$. Changed accordingly.}
+
+\shortpoint{Page 13, line 383: Please remove the word “we”.}
+\shortreply{Corrected.}
+
+\shortpoint{Page 14, line 415: Ref. [21] is written twice.}
+\shortreply{Corrected.}
+
+\shortpoint{Page 17, line 511: In “Avrutin et al. and colleagues” either “et al.” or “and colleagues” should be removed.}
+\shortreply{Corrected.}
+
+\shortpoint{Fig. 1A: Marking the threshold $v_{\theta}$ would be helpful.}
+\shortreply{Added $v_{\theta}$ indicators. to \cref{fig:nullclines}.}
+
+\shortpoint{Fig.
+4: The regions of overlapping (bistability) are obviously distinguishable.
+However, it would be helpful if they are highlighted, for instance, by vertical lines or colored vertical stripes, so that one can easier guess the approximate critical values of $\bar g$.}
+\shortreply{Good idea. This will be done in the next iteration of the review process (if there is one).}
+
+\shortpoint{Caption of Fig.10: It should be $\Pi_{n}: d^{\star}\mapsto d^{\star}$.}
+\shortreply{Corrected.}
+
+\bibliographystyle{apalike} % for Health, Physics and Mathematics articles
 \bibliography{bibliography.bib}
@@
 \end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2022-03-30 tex/manuscript.tex
Update a bunch of tex files

@@
-\documentclass[utf8, draft]{frontiersFPHY} % for Physics and Applied Maths
-% \documentclass[utf8]{frontiersFPHY} % for Physics and Applied Maths
+\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Maths
 \usepackage{graphicx}
@@
 
-\graphicspath{{../figures/}}
+\graphicspath{{../figures}}
 
@@
 
+\usepackage{xr}
+\externaldocument{supplementary}
+
 % Define terms for "free"/"quiet"
-\newcommand{\free}{free}
-\newcommand{\suppressed}{suppressed}
+\newcommand{\free}{active}
+\newcommand{\suppressed}{silent}
 
@@
 
-\begin{abstract}
-  \section{}
-  Short-term synaptic plasticity is found in many areas of the central nervous system.
-  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
-  To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
-  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n:n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
-  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
-  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
-  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
-  We derive conditions that describe period-increment bifurcations between stable $n:n$ and $(n+1):(n+1)$ bursts, producing a full bifurcation diagram of the burst cycle period.
-  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.
-
-  \tiny
-  \keyFont{ \section{Keywords:} Synaptic depression, Poincaré map, Dynamical system, Neuronal bursting, Central pattern generator}
-
-\end{abstract}
-
 \input{sections/introduction}
@@
 \section*{Data Availability Statement}
-The datasets generated for this study are available on request to the corresponding author.
+The data sets generated for this study are available on request to the corresponding author.
 
@@
   \centering
-  \includegraphics{fig/nullclines-uncoupled.pdf}
+  \includegraphics{nullclines}
   \caption{Periodic solution of relaxation-oscillator model neuron. $\bm{\mathrm{(A)}}$
@@
   \centering
-  \includegraphics{fig/depression-traces.pdf}
-  \caption{Solution profiles of a $4-4$ burst. $\bm{\mathrm{(A)}}$ Membrane potentials
-    of cell 1 ($v_{1}$, blue), and cell 2 ($v_{2}$, orange). $\bm{\mathrm{(B)}}$
-    Synaptic variables $d_{1}$ (blue) and $s_{1}$ (grey) of cell
-    1.~\label{fig:depression-traces}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/burst-sols.pdf}
+  \includegraphics{burst-sols}
   \caption{Voltage traces of both cells of numerically stable solutions for increasing
@@
   \centering
-  \includegraphics{fig/bif-diagram.pdf}
-  \caption{Numerically computed bifurcation diagrams of stable $n:n$ solutions for
-    increasing coupling strength $\gbar$. $\bm{\mathrm{(A)}}$ Period of stable
-    solutions. Dashed lines show the interval between the $5-5$ and the suppressed
-    solutions, where higher period $n:n$ solutions occur on increasingly smaller intervals
-    of $\gbar$. $\bm{\mathrm{(B)}}$ $ISI$s corresponding to $n:n$ solutions in
-    $\mathrm{(A)}$. Long $ISI$s are associated with the quiet phase of a burst, short
-    $ISI$s with the free phase. During the free phase, $ISI$s are of approximately
-    constant duration $T$.\label{fig:bif-diagram}}
+  \includegraphics{bif-diagram}
+  \caption{Numerically computed bifurcation diagram of the cycle period of stable $n:n$ solutions for increasing coupling strength $\gbar$.
+Dashed lines show the interval between the $5-5$ and the suppressed solution, where higher period $n:n$ solutions occur on increasingly smaller intervals of $\gbar$.\label{fig:bif-diagram}}
+\end{figure}
+
+% \begin{figure}[h!]
+%   \centering
+%   \includegraphics{nullclines-coupled}
+%   \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the
+%   $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar
+%   s$. For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange
+%   point). Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until
+%   $p_{f}$ changes stability (half orange,  half blue point) at some critical total
+%   conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for
+%   $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
+% \end{figure}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics{gstar-diag}
+  \caption{Numerically computed values of the release conductance ($\tilde g^{\star}$) for various $n:n$ solutions.
+The dashed line indicates the analytical approximation of the release conductance by $g^{\star}$.\label{fig:gstar-diag}}
 \end{figure}
@@
   \centering
-  \includegraphics{fig/nullclines-coupled.pdf}
-  \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the
-  $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar
-  s$. For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange
-  point). Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until
-  $p_{f}$ changes stability (half orange,  half blue point) at some critical total
-  conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for
-  $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.8\textwidth]{fig/release-delay.pdf}
-  \caption{Numerically computed values of the release delay for varying $\gbar$. Each of
-    the three branches (A, B, C) also shows the timecourse of the total synaptic
-    conductance $\gbar s$ of a sample stable solution of both cells (blue and orange),
-    as well as the release conductance $g^{\star}$ (dashed green line).
-    $\bm{\mathrm{(A)}}$ Branch corresponding to the $1-1$ solution. Here the quiet
-    cell only spikes after a significant release delay. $\bm{\mathrm{(B)}}$ Branch with
-    a long release delay associated with a subset of $2-2$ solutions. Here the release
-    condition is briefly satisfied after the first spike of cell 1. This does not cause
-    firing of cell 2, which only occurs after the second spike of cell 1.
-    $\bm{\mathrm{(C)}}$ Branch with $n:n$ solutions  where release delay is
-    approximately zero and the release condition is sufficient for firing of cell 2.
-    ~\label{fig:release-delay}}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics{fig/free-quiet.pdf}
+  \includegraphics{free-quiet}
   \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution.
@@
     $g^{\star}$. $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell
-    1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet1}}
+    1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet}}
 \end{figure}
@@
   \centering
-  \includegraphics{fig/delta-t.pdf}
+  \includegraphics{delta-t}
   \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
@@
   \centering
-  \includegraphics{fig/FQ-map.pdf}
+  \includegraphics{FQ-maps}
   \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for
-  $\gbar=0.6$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at
-  $d_{s}$ which is indicated by a dashed vertical line.~\label{fig:FQ-map}}
+  $\gbar=0.5$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at
+  $d^{\star}=d_{s}$ which is indicated by a dashed vertical line. Curves $Q_n$ intersect at $\Delta t = \tau_{\kappa}\ln\Big(\bar g / g^{\star}\Big)$. \label{fig:FQ-maps}}
 \end{figure}
@@
   \centering
-  \includegraphics{fig/Pn-map.pdf}
-  \caption{Map $\Pi_{n}:d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$
+  \includegraphics{Pn-map}
+  \caption{Map $\Pi_{n}:d^{\star}\mapsto d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$
   at $\gbar=0.6$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
@@
   \centering
-  \includegraphics{fig/folds.pdf}
+  \includegraphics{folds}
   \caption{$\bm{\mathrm{(A)}}$ Fold bifurcation diagrams of stable (continuous curves)
     and unstable (dotted curves) fixed points of $\Pi_{n}$ for varying $n$.
-    $\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points (blue), and the
-    corresponding solution period from numerical integration of the system of ODEs
+    $\bm{\mathrm{(B)}}$ Cycle periods computed from stable fixed points of $\Pi_{n}$ (blue), and the corresponding periods from stable $n:n$ solutions acquired via numerical integration of the system of ODEs
     (orange).~\label{fig:folds}}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{fig/final-bif.pdf}
+  \includegraphics[width=0.8\textwidth]{final-bif}
   \caption{Bifurcation diagrams of stable $n:n$ solutions computed analytically from
     fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in
-    \big[\gbar_+(n),\gbar_-(n)\big]$ (blue), and computed from numerical integrations of
-    the ODEs (orange).~\label{fig:final-bif}}
+    \big[\gbar_{\mathcal{L}}(n),\gbar_{\mathcal{R}}(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
 \end{figure}

### 2022-03-30 tex/sections/discussion.tex
Update a bunch of tex files

@@
 In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
-Mathematical modelling can shed light on the underlying mechanisms that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.
+\linelabel{line:principle}
+Modelling can shed light on the underlying mathematical principles that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.
 
@@
 Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
-This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the free and quiet phases of $n:n$ solutions respectively.
-Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of single uncoupled neurons.
+This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the active and silent phases of $n:n$ solutions respectively.
+Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of a single uncoupled neuron.
 Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n:n$ burst solutions of the full two-cell system of ODEs.
 The results from our one-dimensional map match excellently with numerical simulation of the full network.
-Our results are in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.
+Our results are also in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.
 
@@
 As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses.
-In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g.
-see][]{kuehn2015}.
+In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.
 
@@
 This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult.
-A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting in this scenario.
+A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting for such an investigation.
 
@@
 We were able to replicate this finding by numerically finding the respective left and right borders of stable $n:n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
-We have also noted the resemblance of our bifurcation diagram to one where such $n:n$ branches are created via a period-increment bifurcation with co-existent attractors of scalar linear maps with a discontinuity~\citep{avrutin2012,avrutin2011}.
-It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} and colleagues result from a ``reinjection'' mechanism, first described by~\citet{perez1985}.
+\linelabel{line:disc-pincA}
+We have also noted the resemblance of our bifurcation diagram to one where such $n:n$ branches are created via the bifurcation scenario of type period-increment with co-existent attractors, first described for scalar linear maps with a discontinuity \citep{avrutin2012,avrutin2011}.
+It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} result from a ``reinjection'' mechanism \cite{perez1985}.
 Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
 The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
-In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment bifurcations.
+In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment dynamics.
 It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
+\linelabel{line:disc-pincB}
 In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.
@@
 While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.
-However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariance circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
+However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariant circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
 SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
@@
 % BIOLOGICAL IMPORTANCE OF DEPRESSION
+% TODO: Perhaps mention learning after all?
 We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.
 This result is in line with the idea that one role of synaptic depression in the nervous system may be to allow a finite size neuronal network to participate in different tasks by producing a large number of rhythms~\citep{bose2011, jalil2004, li2007}.
-To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength, which can occur through the process of learning.
+To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength.
 Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.

### 2022-03-30 tex/sections/introduction.tex
Update a bunch of tex files

@@
+\begin{abstract}
+  \section{}
+  Short-term synaptic plasticity is found in many areas of the central nervous system.
+  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
+  To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
+  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n:n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
+  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
+  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
+  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
+  \linelabel{line:abstract}
+  We derive conditions that predict the bifurcations between $n:n$ and $(n+1):(n+1)$ solutions, producing a full bifurcation diagram of the burst cycle period.
+  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.
+
+  \tiny
+  \keyFont{ \section{Keywords:} Synaptic depression, Poincaré map, Dynamical system, Neuronal bursting, Central pattern generator}
+
+\end{abstract}
+
 \section{Introduction}
@@
 % Brown
+\linelabel{line:A}
 ~\citet{brown1911} pioneered the idea that synaptic depression acts as a burst termination
-mechanism in reciprocally inhibitory CPGs involved in rhythm generation of locomotion.
+mechanism in CPGs composed of reciprocally inhibitory neurons and involved in rhythm generation of locomotion.
 When one side is firing during a burst the other, antagonistic side, is prevented from
@@
 This rhythmogenesis hypothesis has been considered one of a handful of standard mechanisms for generating locomotion rhythms in vertebrates~\citep{reiss1962,perkel1974,friesen1994}.
-It has been proposed as an explaination of the antiphase burst rhythm in struggling in \textit{Xenopus} tadpoles~\citep{li2007}.
+It has been proposed as an explanation of the antiphase burst rhythm in struggling in \textit{Xenopus} tadpoles~\citep{li2007}.
 
@@
 predicted by knowing the strengths of the synaptic conductances of the two synapses.
-Thus, the scalar conditions derived in~\citet{bose2011} provide a method to numerically
-identify the type of stable $n:n$ pattern for any given value of the coupling strength.
+\linelabel{line:B}
+Thus, the scalar conditions derived in \citet{bose2011} provide a method to numerically
+identify the type of stable $n:n$ pattern for any given value of the coupling strength and $n\leq 2$.
 However, they do not predict the exact period of such solutions.
@@
 In addition to proving the existence and stability of fixed points, our map shows that fixed points are created via a fold bifurcation of maps.
-We also derive algebraic conditions that predict the period increment bifurcations that allow the switch between $n:n$ and $(n+1):(n+1)$ solutions.
+Finally, we use our map to derive algebraic conditions that allow us to predict parameter values of the maximum conductance at which $n:n$ solutions bifurcate to $(n+1):(n+1)$ solutions, and vice versa.
 Because our map is fully explicit, it lays the framework for studying the effects of other model parameter on network dynamics without the need to run expensive numerical integrations of the ODEs.
@@
 Next, we state and justify the simplifying assumptions that are necessary for the map construction.
-Finally, we analytically derive the first return map of the depression variable as well as the conditions that are required for stable solutions to bifurcate between $n:n$ and $(n+1):(n+1)$ solutions.
+Finally, we analytically derive the first return map of the depression variable as well as the conditions that are required for stable $n:n$ solutions.
 We end this work with a discussion.

### 2022-03-30 tex/sections/methods.tex
Update a bunch of tex files

@@
 The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
-The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by: \begin{align}
+The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
+\begin{align}
 	\label{eq:cell-modelA}
-	\dot v_{i} & = f(v_{i}, w_{i}) -\gbar s_j(v_i-v_{s}), \\
+	\dot v_{i} & = f(v_{i}, w_{i}) -\bar g s_j(v_i-v_{s}), \\
 	\label{eq:cell-modelB}
@@
 \end{align}
-Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\gbar s_{j}$ from neuron $j$ to neuron $i$.
+Here $v_{-}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\bar g s_{j}$ from neuron $j$ to neuron $i$.
 Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
 \begin{equation}
-	\label{eq:memcur}
+	\label{eq:f}
 	f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})
@@
 \begin{equation}
-	h(v_{i}, w_{i})=\frac{w_{\infty}(v_{i})-w_{i}}{\tau_{w}}~\label{eq:h}.
+	\label{eq:h}
+	h(v_{i}, w_{i})=\frac{w_{\infty}(v_{i})-w_{i}}{\tau_{w}}.
 \end{equation}
-The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the \textbf{Supplementary Material S1}.
+The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the Supplementary Material S1.
 
@@
 \begin{numcases}{\dot d_{i} = }
-	(1-d_{i})/\tau_{a} &  if $v_{i}<v_{\theta}$,\label{eq:dot-d-up}
+	(1-d_{i})/\tau_{a} &  if $v_{i}<v_{\theta}$, \label{eq:dot-d-up}
 	\\
-	-d_{i}/\tau_{b}    &  if $v_{i}>v_{\theta}$,\label{eq:dot-d-down}
+	-d_{i}/\tau_{b}    &  if $v_{i}>v_{\theta}$, \label{eq:dot-d-down}
 \end{numcases}
@@
 
-When the total inhibitory conductance $g = \bar g s$ is constant, the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
-In case of no inhibition ($g=0$), the two curves intersect near the local minimum of $v_{\infty}$ to the left of $v_{\theta}$ (commonly referred to as ``left knee'' of $v_{\infty}$), creating an unstable fixed point with a surrounding stable limit cycle of period $T=T_{act}+T_{inact}$ (\cref{fig:nullclines}A).
-Here $T_{act}$ is the amount of time the cell spends in the active state when $v>v_\theta$, while $T_{inact}$ is the time it spends in the silent state when $v<v_\theta$.
+When the total inhibitory conductance $\bar g s$ is constant, the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
+In case of no inhibition ($\bar g=0$), the two curves intersect near the local minimum of $v_{\infty}$ to the left of $v_{\theta}$ (commonly referred to as ``left knee'' of $v_{\infty}$), creating an unstable fixed point $p_{f}$ with a surrounding stable limit cycle of period $T=T_{a}+T_{s}$ (\cref{fig:nullclines}A).
+Here $T_{a}$ is the amount of time the membrane potential spends above firing threshold ($v>v_\theta$), while $T_{s}$ is the time it spends below firing threshold ($v<v_\theta$).
 Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
-The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
-During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
-Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
-During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
-In the case of a non-zero inhibition ($g>0$) the location of $v_{\infty}$ depends on the exact value of $g$.
-Increasing $g$ moves the cubic $v_{\infty}$ with the ensuing unstable fixed point down $w_{\infty}$ in the $(v-w)$ -plane.
-When $g$ is large enough, the fixed point moves past the left knee and becomes stable via a subcritical Andoronov-Hopf bifurcation, attracting all previously periodic trajectories.
-In the following section we will refer to the value of the total conductance at the bifurcation as $g_{bif}$.
+% The trajectory of an action potential can be dissected into four phases: (1) a silent phase, (2) a jump up, (3) an active phase, and (4) a jump down~\citep[see e.g.][]{ermentrout2010}.
+% During the silent phase the trajectory evolves along the left branch ($v_{i}<v_{\theta}$) of the cubic $v$-nullcline.
+% Once the trajectory reaches the local minimum of $v_{\infty}$, it ``jumps up'' to the right branch ($v_{i}>v_{\theta}$), crossing the firing threshold $v_{\theta}$.
+% During the active phase the trajectory then evolves along the right branch of the cubic until it arrives at the local maximum, where it ``jumps down'' to the left branch commencing a new cycle.
+% In the case of a non-zero inhibition ($g_{j}>0$) the location of $v_{\infty}$ depends on the exact value of $g_{j}$.
+Applying a constant nonzero inhibition, e.g. by setting $s=1$ and $\bar g > 0$, moves the cubic $v_{\infty}$ with the ensuing unstable fixed point down $w_{\infty}$ in the $(v-w)$ -plane.
+When $\bar g$ is large enough, the fixed point moves past the left knee and becomes stable via a subcritical Andoronov-Hopf bifurcation, attracting all previously periodic trajectories.
+In the following section we will refer to the value of the total conductance $\bar g s$ at the bifurcation point as $g_{bif}$.
 

### 2022-03-30 tex/sections/results.tex
Update a bunch of tex files

@@
 Such $n:n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
-\Cref{fig:depression-traces}A shows the timecourse of a typical $4:4$ burst.
+\Cref{fig:burst-sols}A shows the timecourse of a typical $4:4$ burst.
 While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
-% FIXME: This isn't consistent with Bose, that needs to be mentioned
-Therefore, at any given moment one cell is spiking while the other is inhibited.
-Consistent with \citet{bose2011} we will refer to the currently firing cell as ``\free{}'' and we will call the inhibited cell ``\suppressed{}''.
+\linelabel{line:C1}
+Therefore, at any given moment one cell is spiking while the other is suppressed and does not spike.
+We will refer to the currently firing cell as ``active'' and we will call the suppressed cell ``silent''.
 Additionally, we will distinguish between two phases of a $n:n$ solution:
-We will refer to the time interval when a cell is firing as the ``\free{} phase'', and we will call the remaining duration of a cycle, when a cell is not firing, the ``\suppressed{}  phase''.
+\linelabel{line:C2}
+We will refer to the time interval when a cell is firing as the ``active phase'', and we will call the remaining duration of a cycle, when a cell is not firing, the ``silent  phase''.
 
-% TODO: Add mention of gstar. Once critical conductance is crossed, cell is released.
-With each action potential of the \free{} cell, short-term depression leads to a step-wise decrease of $d$, and consequently of $s$ (\cref{fig:depression-traces}B).
-If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\bar g s$ will eventually become sufficiently small to allow for the \suppressed{} cell to be released and start firing, thus inhibiting the previously \free{} cell.
-While a cell is \suppressed{} its depression variable can recover.
-Once the \suppressed{} cell becomes \free{} again its synaptic inhibition will be sufficient to terminate the burst of the previously \free{} cell and commence a new cycle.
+With each action potential of the active cell, short-term depression leads to a decrease of $d$, and consequently of $s$ (\cref{fig:burst-sols}B).
+\linelabel{line:D}
+If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\bar g s$ will eventually become sufficiently small to allow for the silent cell to be released \citep{wang1992,skinner1994} and start firing, thus inhibiting the previously active cell.
+While a cell is silent its depression variable can recover.
+Once the silent cell becomes active again its synaptic inhibition will be sufficient to terminate the burst of the previously active cell and commence a new cycle.
 % BUG: This is not 100% true, gbar AND the initial conditions uniquely determine the type of n:n pattern.
@@
 
-Branches of numerically stable $n:n$ solutions and their associated limit cycle period for varying values of $\bar g$ are depicted in \cref{fig:bif-diagram}A (see \textbf{Supplementary Material S2} for algorithm description).
+Branches of numerically stable $n:n$ solutions and their associated limit cycle period for varying values of $\bar g$ are depicted in \cref{fig:bif-diagram}A (see Supplementary Material S2 for algorithm description).
 Not only do higher $n:n$ solutions branches require stronger coupling $\bar g$, but also within $n:n$ branches the period increases with $\bar g$.
@@
 Branches of higher $n:n$ burst solutions occur on increasingly smaller intervals of $\bar g$, for instance is the $\bar g$ interval of the $5:5$ branch shorter than that of the $4:4$ branch and so on.
-The interval between the $5:5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n:n$ solutions, such as $11:11$ bursts, but also other non-symmetric $n:m$ solutions as well irregular, non-periodic solutions.
+The interval between the $5:5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n:n$ solutions, such as $11:11$ bursts, but also other non-symmetric $n:m$ solutions as well as irregular, non-periodic solutions.
 However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n:n$ solutions.
@@
 The goal of the following mathematical analysis is to reduce the complexity of the
-eight-dimensional system to some easily tractable quantity.
-As we will see later this quantity is the value of the depression variable $d$ of either of the two cells.
-We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the \free{} phase, and then during the \suppressed{} phase.
+eight-dimensional system to a more tractable problem.
+As we will explain, we do this by approximating the full dynamics by a reduced system describing the dynamics of the depression variable $d$ of either of the two cells.
+We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the active phase, and then during the silent phase.
 This construction will require two assumptions about the membrane and synaptic dynamics.
-The first assumption states that during a burst the \free{} cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
-The second assumption states that once the inhibitory conductance acting on the \suppressed{} cell drops below a critical threshold, the cell is immediately released and fires.
-The second assumption is necessary to predict the release time of the \suppressed{} cell, which allows us to model the recovery of $d$ during the \suppressed{} phase.
-In other words, the second assumption requires that the release of the \suppressed{} cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the \suppressed{} cell.
-Both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
-Both assumptions were first explored in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n:n$ solutions.
+The first assumption states that during a burst the active cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
+The second assumption states that once the inhibitory conductance acting on the silent cell drops below a critical threshold, the cell is immediately released and fires.
+The second assumption is necessary to predict the release time of the silent cell, which allows us to model the recovery of $d$ during the silent phase.
+In other words, the second assumption requires that the release of the silent cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the silent cell.
+The approximate validity of both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
+Both assumptions were first used in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n:n$ solutions.
 However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.
 
-% Assumption 1: Free phase
-% FIXME: Probably good idea to remove IBI reference here (and in figure).
-Our first assumption about the model states that the \free{} cell fires at its uncoupled period $T$, that is, during the \free{} phase of a burst we have $ISI=T$.
+% Assumption 1: active phase
+\linelabel{line:E1}
+Our first assumption about the model states that the active cell fires at its uncoupled period $T$, that is, during the active phase of a burst we have $ISI=T$.
 Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
-We can further numerically confirm this observation by capturing the $ISI$s of the stable solutions from the bifurcation diagram in \cref{fig:bif-diagram}A.
-In addition to $ISI$s, \Cref{fig:bif-diagram}B also shows inter-\textit{burst} intervals ($IBI$s), which correspond to the time interval between the last spike of the burst and the full cycle period, and which lie in the \suppressed{} phase of the burst.
-$IBI$s lie on multiple branches, each branch associated with a stable $n:n$ solution, and are monotonically increasing with $\bar g$.
-In contrast, $ISI$s are calculated from the spikes within the \free{} phase and do not vary significantly with $\bar g$, but are approximately $ISI\approx T$, affirming our first assumption.
-Assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the \free{} phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
-Assuming $ISI=T$ seems reasonable given that inhibition acting on the \suppressed{} cell decays exponentially to zero on a much shorter timescale than the duration of the $ISI$, and therefore, once the \suppressed{} cell is released its trajectory quickly approaches the spiking limit cycle.
+Numerically computing $ISI$s for all stable $n:n$ solutions in \cref{fig:bif-diagram} reveals that $ISI$s differ by at most $1\, \si{ms}$ from the intrinsic firing period $T\approx 376\, \si{ms}$.
+Assuming $ISI=T$ seems reasonable given that inhibition acting on the silent cell decays exponentially on a much shorter timescale $\tau_{\kappa}$ than the duration of the $ISI$.
+Therefore once the silent cell is released its trajectory quickly approaches the spiking limit cycle.
+Naturally the above assumption requires a sufficiently small $\tau_{\kappa}$, and fails when $\tau_{\kappa}$ is large.
+In the Supplementary Material \cref{sec:tauk} we numerically explore how different values of $\tau_{\kappa}$ affect the $ISIs$ of the active cell.
+Finally, assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the active phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
+\linelabel{line:E2}
 
 % Assumption 2: Release
-% TODO: Mention that we will derive the exact value of
-% I don't think we should introduce the g_min notation, instead call g* the minimum value.
-Our second assumption states that the suppressed cell is released and spikes as soon as the total inhibitory conductance $g = \bar g s$ acting on it drops below a constant threshold.
-We call this critical threshold value the ``release conductance'', denoted by $g^\star$, and define it as the value of $g$ at the time when the voltage of the suppressed cell first crosses the firing threshold $v_{\theta}$, that is when that cell is released and fires its first spike.
-Recall from figure ... that when a cell is suppressed its $v$- and $w$-nullclines intersect at a stable fixed point and $g > g_{bif}$.
-A sufficient condition for the suppressed cell to be released is therefore $g > g_{bif}$ .
-However, depending on the topology of the stable manifold, the trajectory of the suppressed cell can escape the stable fixed point and allow the cell to produce a spike for $g < g_{bif}$.
-This spike will inhibit the firing cell and allow the previously suppressed cell to start firing.
-Moreover, there exists a conductance value $g^{\star}$ and a condition $g > g^{\star}$ that is necessary for the suppressed cell to be release at all.
-In other words, only when $g > g^{\star}$ is satisfied can the network produce stable $n:n$ solutions, and produces the suppressed solution otherwise.
-The true value of the release conductance will depend on the type of $n:n$ solution and the coupling strength $\bar g$, and will lie in the interval $(g_{bif}, g^{\star})$.
-As we will show in the following section, it turns out that $g^{\star}$ is a good approximation
+\linelabel{line:release1}
+Our second assumption states that the silent cell is released and spikes as soon as the total inhibitory conductance $\bar g s$ acting on it drops below some threshold value.
+We call this critical threshold value the ``release conductance'', and define it as the value of $\bar g s$ at the time when the voltage of the quiet cell first crosses the firing threshold $v_{\theta}$, that is when that cell is released and fires its first spike.
+Recall that when a cell is quiet its $v$- and $w$-nullclines intersect at a stable fixed point and $\bar g s > g_{bif}$.
+% The following does not necessarily imply that it fires instantly on release.
+A sufficient condition for the quiet cell to be released is therefore $\bar g s < g_{bif}$.
+However, depending on the topology of the stable manifold, the $(v,w)$-trajectory of the silent cell can escape the stable fixed point and allow the cell to produce a spike for $\bar g s > g_{bif}$.
+In this case the value of the release conductance depends on the type of $n:n$ solution and the coupling strength $\bar g$.
+For any stable $n:n$ solution in \cref{fig:bif-diagram} we can compute an associated release conductance numerically by recording the value of $\bar g s$ at the time of the first spike of the silent cell.
+% ''Converges'' is probably the wrong word here...
+Such values of the release conductance are shown in \cref{fig:gstar-diag}A, and the graph suggests that as $n$ increases, the value of the release conductance converges to some constant conductance value $g^{\star} \approx 0.0068\, \si{mS/cm^2}$.
+Here $g^{\star}$ is the value of $\bar g s$ at the end of a cycle of a suppressed solution, just before the active cell spikes.
+Using $g^{\star}$ as a constant approximation for the release conductance will allow us to formulate a scalar condition that predicts the release time of the silent cell.
+Moreover, using $g^{\star}$ is convenient because its exact value can be derived explicitly, as will be shown in the following section.
 
-trajectory to pass the fixed point and the cell to spike.
-We will derive the exact value of such a $g_{min}$ in the following section, and to simplify the derivation our map assume that $g_{min}$ is a good approximation for the release conductance, therefore setting $g^\star = g_{min}$ .
-This assumption allows us to predict that timing of the release of the suppressed cell, that is precisely when
+Assuming a constant release conductance for all $n:n$ solutions will naturally introduce some error in the prediction of the release time of the silent cell.
+We can compute that error for any associated solution in \cref{fig:gstar-diag}A by calculating the time interval between the first spike of the silent cell and the time when $\bar g s$ first crosses $g^{\star}$.
+We will call this time interval the ``release delay''.
+\Cref{fig:gstar-diag}B shows the numerically computed graph of such release delays.
+For $n>1$ the absolute delays are smaller than $2\, \si{ms}$.
+Therefore, using
 \begin{equation}
@@
 \end{equation}
-is satisfied.
+as a constant release condition for all $n:n$ solutions allows us to accurately predict the timing of the release of the quiet cell.
+And to simplify the terminology, from now on we will refer to \cref{eq:release} simply as the ``release condition''.
+\linelabel{line:release2}
 
 % NOTE: Perhaps mention the first assumption here as well.
-In summary: We assume that the release condition is sufficient to predict when the \suppressed{} cell is released.
+In summary: We assume that the release condition is sufficient to predict when the silent cell is released.
 Due to the symmetry of $n:n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
 The release time therefore uniquely determines the type of $n:n$ solution.
-Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the \suppressed{} cell.
-Instead, the solution of the synaptic variable $s$ of the \free{} cell is sufficient to predict when $g=g^{*}$ is satisfied.
-Finally, $s$ is solely determined by the evolution of the depression variable $d$ of the \free{} cell.
-Constructing a solution of $d$ during the \free{} phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
+Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the silent cell.
+Instead, the solution of the synaptic variable $s$ of the active cell is sufficient to predict when $\bar g s =g^{\star}$ is satisfied.
+\linelabel{line:F}
+Finally, the value of $s$ at each spike time is determined by the evolution of the depression variable $d$ of the active cell.
+Constructing a solution of $d$ during the active phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
 However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
@@
 Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n:n$ burst.
-The map $\Pi_n$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
-To simplify the map construction we will assume that a \free{} cell fires exactly $n$ times before it becomes \suppressed{}.
-We will construct $\Pi_n$ by evolving $d$ first during the \free{} phase and then during the \suppressed{} phase of the $n:n$ limit cycle.
-First, let us give explicit definitions of the \free{} and \suppressed{} phases.
-A schematic illustration of both phases is given in \cref{fig:free-quiet1}.
+The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
+To simplify the map construction we will assume that an active cell fires exactly $n$ times before it becomes silent.
+We will construct $\Pi_n$ by evolving $d$ first during the active phase and then during the silent phase of the $n:n$ limit cycle.
+The terms ``active'' and ``silent'' phases will be defined in terms of the state of the depression variable.
+Hence, during the active phase the depression variable of the active cell will both decay and recover, while during the silent phase it will only recover.
+First, let us give explicit definitions of the active and silent phases of a burst.
+A schematic illustration of both phases is given in \cref{fig:free-quiet}.
 
-Suppose that at $t=0$ cell 1 starts \free{} with some initial $d(0)$. Cell 1 then fires $n$ spikes at the uncoupled period $T=T_{act}+T_{inact}$.
+Suppose that at $t=0$ cell 1 becomes active with some initial $d(0)$. Cell 1 then fires $n$ spikes at the uncoupled period $T=T_{a}+T_{s}$.
 Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
-After $n$ spikes the total conductance $\bar g s(t)$ acting on the \suppressed{} cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}.
-That is at some time $t=(n-1)T + T_{act} + \Delta t$, where $\Delta t < T_{inact}$, we have $\bar g s(t)=g^{\star}$.
+After $n$ spikes the total conductance $\bar g s(t)$ acting on the silent cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}.
+That is at some time $t=(n-1)T + T_{a} + \Delta t$, where $\Delta t < T_{s}$ will be determined below, we have $\bar g s(t)=g^{\star}$ \citep{bose2011}.
 Cell 2 is then released and prevents cell 1 from further spiking.
-Here $\Delta t$ is the time between the last spike of cell 1 and the first spike of cell 2 ~\citep{bose2011}.
-Once released, cell 2 also fires $n$ spikes until cell 1 becomes \free{} once again.
+Once released, cell 2 also fires $n$ spikes until cell 1 becomes active once again.
 Let $P_n$ denote the full cycle period of a $n:n$ solution:
@@
 	~\label{eq:P}
-	P_n = 2\Big( (n-1)T + T_{act} + \Delta t \Big).
+	P_n = 2\Big( (n-1)T + T_{a} + \Delta t \Big).
 \end{equation}
-We can now define the \free{} and \suppressed{} phases of cell 1 explicitly.
-The \free{} phase is the interval that lasts from the first spike time up until the beginning of the inactive phase of the last spike, last spikes of the burst, that is for time $0<t<(n-1)T + T_{act}$.
-During the \free{} phase of cell 1, the \suppressed{} cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\bar g s > g^{\star}$.
-The \suppressed{} phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T + T_{act} < t < P_n$.
-Hence the \suppressed{} phase lasts for $(n-1)T + T_{act} + 2\Delta t$.
+We can now define the active and silent phases of cell 1 explicitly.
+The active phase of a burst is the interval that lasts from the first spike time up until the beginning of the silent phase of the last spike, that is for time $0<t<(n-1)T + T_{a}$.
+During the active phase of cell 1, the silent cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\bar g s > g^{\star}$.
+The silent phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T + T_{a} < t < P_n$.
+Hence the silent phase lasts for $(n-1)T + T_{a} + 2\Delta t$.
 
-Note that only the \suppressed{} phase depends on $\Delta t$, which will play a central role in the construction of $\Pi_n$.
+Note that only the silent phase depends on $\Delta t$, which will play a central role in the construction of $\Pi_n$.
 From \cref{eq:P} $\Delta t$ can be computed as
@@
 	\label{eq:delta-t-P}
-	\Delta t = \frac{1}{2}P_n - (n-1)T - T_{act}.
+	\Delta t = \frac{1}{2}P_n - (n-1)T - T_{a}.
 \end{equation}
@@
 Each continuous branch of $\Delta t$ is monotonically increasing and corresponds to a $n:n$ burst:
-Stronger coupling $\bar g$ increases the total synaptic conductance $\bar g s$ that acts on the \suppressed{} cell, thus delaying its release.
-It is easy to see that for any $n$-branch we have $\Delta t < T_{inact}$:
-Once $\Delta t$ crosses $T_{inact}$, the \free{} cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1)-(n+1)$ burst.
+Stronger coupling $\bar g$ increases the total synaptic conductance $\bar g s$ that acts on the silent cell, thus delaying its release.
+It is easy to see that for any $n$-branch we have $\Delta t < T_{s}$:
+Once $\Delta t$ crosses $T_{s}$, the active cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1):(n+1)$ burst.
 
-Distinguishing between the \free{} and \suppressed{} phases of a cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
-As can be seen from \cref{fig:free-quiet1}C, during the \free{} phase $d$ depresses when $v > v_\theta$ and recovers when $v < v_\theta$.
-In contrast, during the \suppressed{} phase $d$ only recovers and does not depress.
-Given the initial $d^{\star} = d(0)$ at the beginning of the cycle and the number of spikes in the \free{} phase $n$, we can now construct the burst map $\Pi_n$.
+Distinguishing between the active and silent phases of a $n:n$ cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
+As can be seen from \cref{fig:free-quiet}C, during the active phase $d$ depresses when $v > v_\theta$ and recovers when $v < v_\theta$.
+In contrast, during the silent phase $d$ only recovers and does not depress.
+Given the initial $d^{\star} = d(0)$ at the beginning of the cycle and the number of spikes in the active phase $n$, we can now construct the burst map $\Pi_n$.
 The map
@@
 \end{equation}
-models the evolution of $d$ in the \free{} phase.
+models the evolution of $d$ in the active phase.
 $F_n$ takes an initial value $d^{\star}$ and calculates $\Delta t$.
@@
 \end{equation}
-models the recovery of $d$ in the \suppressed{} phase.
+models the recovery of $d$ in the silent phase.
 Given some $\Delta t$ map $Q_n$ computes $d^\star$ at the start of the next cycle.
@@
 
-% TODO: Edit par
-We start the construction of $\Pi_n$ by first considering the \free{} phase and building the map $F_n$.
-At each spike time $t_{k}$ where $d(t_k) = d_k$, variable $d$ decays first for the duration of the active phase of the spike for $T_{act}$, as described by the solution to \cref{eq:dot-d-down}.
-At $t = t_k + T_{act}$ we have
+We start the construction of $\Pi_n$ by first considering the active phase and building the map $F_n$.
+At each spike time $t_{k}$ where $d(t_k) = d_k$, variable $d$ decays first for the duration of $T_{a}$, as described by the solution to eq.
+(\ref{eq:dot-d-down}).
+% cref doesn't work with cases package
+At $t = t_k + T_{a}$ we have
 \begin{equation}
-	d(t_k + T_{act}) = d_k e^{-T_{act}/\tau_b}.
+	d(t_k + T_{a}) = d_k e^{-T_{a}/\tau_b}.
 \end{equation}
-The depression variable then recovers during the inactive phase of the spike until $t_{k+1}$, where for $0<t<T_{inact}$:
+The depression variable then recovers for $T_{s}$ until $t_{k+1}$, where for $0<t<T_{s}$:
 \begin{equation}
-	d(t_{k+1}) = 1 - (1 - d_k e^{-T_{act}/\tau_b} )e^{-t/\tau_a}.
+	d(t_{k+1}) = 1 - (1 - d_k e^{-T_{a}/\tau_b} )e^{-t/\tau_a}.
 \end{equation}
-By substituting $t=T_{inact}$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the \free{} phase:
+By substituting $t=T_{s}$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the active phase:
 \begin{equation}
@@
 \begin{align}
-	\lambda & := \exp(-T_{act}/\tau_b), \label{eq:lambda} \\
-	\rho    & :=\exp(-T_{inact}/\tau_{a}). \label{eq:rho}
+	\lambda & := \exp(-T_{a}/\tau_b), \label{eq:lambda} \\
+	\rho    & :=\exp(-T_{s}/\tau_{a}). \label{eq:rho}
 \end{align}
 
-Given constant $T_{act}$ and $T_{inact}$, parameter $\lambda$ determines how much the synapses depresses during the active phase of the spike, while $\rho$ determines how much it recovers during the inactive phase.
+Given constant $T_{a}$ and $T_{s}$, parameter $\lambda$ determines how much the synapses depresses during the active phase of the spike, while $\rho$ determines how much it recovers during the silent phase.
 Since $0<\lambda, \rho<1$, the map in \cref{eq:map-d} is increasing and contracting, with a fixed point at
@@
 % TODO  Would be good to elaborate on the idea that lambda and tau can be viewed as the new time constants in the reduced system.
-Solving \cref{eq:dot-s-down} for $s(t)$ with $t=T_{inact}$ and setting the initial value $s(0)=d_s\lambda$ gives \begin{equation}
-	\bar g_s d_s\lambda e^{-T_{inact}/\tau_\kappa}=g^{\star}.
+Solving \cref{eq:dot-s-down} for $s(t)$ with $t=T_{s}$ and setting the initial value $s(0)=d_s\lambda$ then gives us the aforementioned approximation of the release conductance $g^{\star}$:
+\begin{equation}
+	\label{eq:gstar}
+	\bar g_s d_s\lambda e^{-T_{s}/\tau_\kappa}=g^{\star} \approx 0.0068\, \si{mS/cm^2}.
 \end{equation}
-By further substituting the definition of $d_s$ in~\eqref{eq:dsup} and rearranging, we can write $\bar g_s$ as a function of $\lambda$ and $\rho$:
+By substituting the definition of $d_{s}$ in \eqref{eq:dsup} and rearranging, we can also write $\bar g_s$ as a function of $\lambda$ and $\rho$:
 \begin{equation}
 	\label{eq:gs}
-	\bar g_s(\lambda, \rho) = \frac{1/\lambda-\rho}{1-\rho} e^{T_{inact}/\tau_\kappa}g^\star.
+	\bar g_s(\lambda, \rho) = \frac{1/\lambda-\rho}{1-\rho} e^{T_{s}/\tau_\kappa}g^\star.
 \end{equation}
 Note that the above dependence of $\bar g_{s}$ on $\lambda$ is linear and monotonically decreasing.
-Increasing $\lambda$ reduces the strength of the depression of the \free{} cell.
-This in turn allows the \free{} cell to fully suppress the \suppressed{} cell at smaller values of $\bar g$.
+Increasing $\lambda$ reduces the strength of the depression of the active cell.
+This in turn allows the active cell to fully suppress the silent cell at smaller values of $\bar g$.
 
-Solving \cref{eq:map-d} gives us the linear map $\delta_n:d^{\star}\mapsto d_n$, that for some initial $d^\star$ computes the depression at the $n$th spike time, $d_n=d(t_n)$:
+Solving \cref{eq:map-d} gives us the linear map $\delta_n$, that for some initial $d^\star$ computes the depression at the $n$th spike time, that is $d(t_n)$:
 \begin{equation}
@@
 Having identified $d$ after $n$ spikes, we can now use the release condition $\bar g s = g^{\star}$ (\cref{eq:release}) to find $\Delta t$.
-At the last ($n$th) spike of the \free{} phase at time $t_n = (n-1)T$ the synapse variable $s$ is set to the respective value of $d(t_n) = \delta_n(d^\star)$, and mirrors the value of $d$ for the duration of $T_{act}$.
-at the end of the active phase at time $t_n + T_{act}$ variable $d$ has decayed to $\delta_n(d^\star) \lambda$ \cref{eq:lambda}, therefore
+At the last ($n$th) spike of the active phase at time $t_n = (n-1)T$ the synapse variable $s$ is set to the respective value of $d(t_n) = \delta_n(d^\star)$, and mirrors the value of $d$ for the duration of $T_{a}$.
+At the end of the active phase at time $t_n + T_{a}$ variable $d$ has decayed to $\delta_n(d^\star) \lambda$, therefore
 \begin{equation}
-	s(t_n + T_{act})=\delta_n(d^\star)\lambda.
+	s(t_n + T_{a})=\delta_n(d^\star)\lambda.
 \end{equation}
-Finally $s$ decays exponentially for $\Delta t < T_{inact}$.
-Solving \cref{eq:dot-s} (case $v < v_\theta$) with initial condition $s(0)=\dn(d^\star)\lambda$ yields:
+Finally $s$ decays exponentially for $\Delta t < T_{s}$.
+Solving \cref{eq:dot-s-down} with initial condition $s(0)=\dn(d^\star)\lambda$ yields:
 \begin{equation}
@@
 \end{equation}
-Our assumption of the release condition guarantees that the \suppressed{} cell 2 spikes and becomes \free{} when $\bar g s - g^{\star}$ crosses zero.
-Solving \cref{eq:release2} for $\Delta t$ allows us to compute it a function of $d^\star$, which defines our map $F_n$:
+Our assumption of the release condition guarantees that the silent cell 2 spikes and becomes active when $\bar g s - g^{\star}$ crosses zero.
+Solving \cref{eq:release2} for $\Delta t$ allows us to compute $\Delta t$ as a function of $d^{\star}$, which defines our map $F_{n}$:
 \begin{equation}
@@
 
-\Cref{fig:FQ-map}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\bar g$.
-Larger values of $d^{\star}$ and $\bar g$, respectively, cause stronger inhibition of the \suppressed{} cell, and therefore prolong its release time and the associated $\Delta t$.
+\Cref{fig:FQ-maps}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\bar g$.
+Larger values of $d^{\star}$ and $\bar g$, respectively, cause stronger inhibition of the silent cell, and therefore prolong its release time and the associated $\Delta t$.
 Map $F_n$ is defined on $d^{\star}>d_{a}$, where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(d^\star)=0$ in \cref{eq:delta-map} for $d^\star$, which yields
@@
 
-We now turn to the construction of map $Q_n$, which describes the recovery of the depression variable during the \suppressed{} phase.
-As we have identified earlier, the recovery in the \suppressed{} phase of a $n:n$ solution is of duration $(n-1)T + T_{act} + 2\Delta t$.
-Substituting that into the solution of $d$ (\cref{eq:dot-d}) with the initial condition $d(0)=\dn(d^\star) \lambda$ yields the map $Q_{n}$:
+We now turn to the construction of map $Q_n$, which describes the recovery of the depression variable during the silent phase.
+As we have identified earlier, the recovery of $d$ in the silent phase of a $n:n$ solution starts at time $t_{n} + T_{a}$ and lasts for the duration of $(n-1)T + T_{a} + 2\Delta t$.
+Substituting that duration into the solution of $d$ (\cref{eq:dot-d-up}) with the initial condition $d(0)=\dn(d^\star) \lambda$ yields the map $Q_{n}$:
 \begin{equation}
 	\label{eq:Qn-map}
-	Q_n(\Delta t) := 1- (1- \dn(d^\star) \lambda)e^{-((n-1)T + T_{act} + 2\Delta t)/\tau_a}.
+	Q_n(\Delta t) := 1- (1- \dn(d^\star) \lambda)e^{-((n-1)T + T_{a} + 2\Delta t)/\tau_a}.
 \end{equation}
-Given $\Delta t$, we can find $\dn(d^\star)$ by rearranging the release condition in \cref{eq:release2}:
+\noindent
+\linelabel{line:abc}
+We can find $\delta_{n}(d^{\star})$, i.e. the value of $d$ at the $n$th spike time, by rearranging the release condition in \cref{eq:release2}:
 \begin{equation}
 	\label{eq:dn}
-	\delta_n(d^\star) = \frac{1}{\bar g \lambda} g^\star e^{\Delta t/\tau_\kappa}.
+	\delta_{n}(d^{\star}) = \frac{1}{\bar g \lambda} g^\star e^{\Delta t/\tau_\kappa}.
 \end{equation}
-Map $Q_n$ is shown in \cref{fig:FQ-map}B for various values $n$.
+Map $Q_n$ is shown in \cref{fig:FQ-maps}B for various values $n$.
 Note that $Q_n$ is monotonically increasing as larger values $\Delta t$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
@@
 We will therefore restrict the domain of $Q_n$ to $(-\infty, \tau_\kappa\ln{\left[\bar g/(g^\star)\right]})$ and the codomain to $(-\infty, 1)$.
-Additionally, while values $\Delta t>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system all $n:n$ solutions bifurcate into $(n+1)-(n+1)$ solutions exactly when $\Delta t = T_{inact}$, and we will address this concern in the last part of our map analysis.
+Additionally, while values $\Delta t>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system $n:n$ solutions bifurcate into $(n+1):(n+1)$ solutions exactly when $\Delta t = T_{s}$, and we will address this concern in the last part of our map analysis.
 
@@
 	\Big(\frac{\bar g}{g^\star}\delta_n(d^\star) \lambda \Big)^{-\tau}
-	e^{-((n-1)T + T_{act})/\tau_a},
+	e^{-((n-1)T + T_{a})/\tau_a},
 \end{equation}
 where we substituted $\tau = 2\tau_{k}/\tau_{a}$.
+\linelabel{line:remind}
+Recall that $\delta_{n}(d^{\star})$ and $g^{\star}$ are obtained from \cref{eq:delta-map} and \cref{eq:gstar}, respectively.
 Since $d$ is the slowest variable of the system and $\tau_a \gg \tau_\kappa$, we will also assume $\tau<1$.
@@
 Varying the synaptic strength $\bar g$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
-For $\bar g < 0.03$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
-As $\bar g$ is increased to $\bar g \approx 0.03$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
-When $\bar g > 0.03$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
+For $\bar g < 0.0015$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
+As $\bar g$ is increased to $\bar g \approx 0.0015$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
+When $\bar g > 0.0015$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
 
-From \cref{eq:Pn-map} it is evident that $\Pi_n$ is monotonically increasing with respect to $\bar g$ and also $d^\star$:
+$\Pi_n$ is monotonically increasing with respect to $\bar g$ and also $d^\star$:
 \begin{align}
@@
 	\label{eq:dPidd}
-	\dv{\Pi_n}{d^\star} & >0,
+	\dv{\Pi_n}{d^\star} & >0.
 \end{align}
-and in the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
+\noindent
+\linelabel{line:mono}
+The monotonicity of $\Pi_{n}$ w.r.t. $\bar g$ is evident from \Cref{eq:non-degen1}, while the monotonicity w.r.t. $d^{\star}$ follows from the monotonicity of both $Q_{n}$ and $F_{n}$.
+In the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
 Just as $F_n$, curves $\Pi_n$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
@@
 Moreover, because $\Pi_n$ and its slope are monotonic with respect to $d^\star$, there exists some critical fixed point $(d^\star_b, \bar g_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
-% TODO: Replace the dx/dt with the physics package stuff
 \begin{align}
@@
 \end{align}
-Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(d^\star_{b}, \bar g_{b})$ map $\Pi_n$ has the topological normal form described by the graph of
-\begin{equation}
-	\label{eq:normal-form}
-	x\mapsto \beta+x-x^{2},
-\end{equation}
-with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.
+% Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(d^\star_{b}, \bar g_{b})$ map $\Pi_n$ has the topological normal form described by the graph of
+% \begin{equation}
+% 	\label{eq:normal-form}
+% 	x\mapsto \beta+x-x^{2},
+% \end{equation}
+% with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.
 
@@
 	\label{eq:Phi}
-	\Phi_n(d^\star, \bar g) := \Pi_n(d^\star, \bar g)-d^\star = 0.
+	\Phi_{n}(d^{\star}, \bar g) := \Pi_{n}(d^{\star}, \bar g)-d^{\star} = 0.
 \end{equation}
 As we have already shown, for $\bar g > \bar g_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
-Solving \cref{eq:Phi} explicitly for $d^\star$ it not trivial, but solving for $\bar g$ is straightforward and given by $\bar g= G_n(d^\star)$, where
+Solving \cref{eq:Phi} explicitly for $d^{\star}$ is not trivial, but solving for $\bar g$ is straightforward and given by $\bar g= G_n(d^\star)$, where
 \begin{equation}
@@
 	\Big(
-	\frac{(1-\lambda\delta_n(d^\star)) }{1-d^\star} e^{-((n-1)T + T_{act})/\tau_a}
+	\frac{(1-\lambda\delta_n(d^\star)) }{1-d^\star} e^{-((n-1)T + T_{a})/\tau_a}
 	\Big)^{1/\tau}
@@
 It is also evident that the fold bifurcations occur for increasingly smaller $\bar g$ as $n$ is increased.
-Moreover, we can observe that unstable fixed points have negative values of $d^\star$ for $n>1$.
+Moreover, the graph suggests that for $n>1$ unstable fixed points have negative values of $d^\star$.
 
@@
 which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $d^\star_f$.
-Because we are primarily interested in the stable fixed points, we define the stable fixed point function $d^\star_f = \phi_n(\bar g)$ as
+Because we are primarily interested in the stable fixed points $d^\star_f>d^\star_b(n)$, we define the stable fixed point function $d^\star_f = \phi_n(\bar g)$ as
 \begin{equation}
 	\label{eq:phi}
-	\phi_n(\bar g):= G_n^{-1}(d^\star_f) \text{ for } d^\star_f>d^\star_b(n).
+	\phi_n(\bar g):= G_n^{-1}(\bar g).
 \end{equation}
@@
 Having found the stable fixed points $d^\star_f$ as a function of $\bar g$, we can now compute the associated cycle period.
-Recall that the period is given by \cref{eq:P}, which we can be written as a function of $\bar g$:
+Recall that the period is given by \cref{eq:P}, which can be written as a function of $\bar g$:
 \begin{equation}
@@
 	P_n(\bar g) = 2 \Big(
-	(n-1)T + T_{act} + F_n\big(\underbrace{\phi_n(\bar g)}_{d^\star_f}, \bar g\big)
+	(n-1)T + T_{a} + F_n\big(\underbrace{\phi_n(\bar g)}_{d^\star_f}, \bar g\big)
 	\Big),
@@
 where map $F_n$ (\cref{eq:Fn-map}) calculates $\Delta t$ given a stable fixed point $d^\star_f=\phi_n(\bar g)$.
-We plot the predicted period $P_n(\bar g)$ versus the cycle period that was computed from numerically integrating the full system of ODEs in \cref{fig:folds}B.
-For $n>1$ our map $\Pi_n$ accurately predicts the period.
-When laying out our assumptions in \cref{sec:assumptions}, we have already predicted an inaccuracy for $n=1$ (see \cref{fig:release-delay}), since here $\bar g$ is not sufficiently strong to guarantee the validity of our release condition
-(\cref{eq:release}).
+\Cref{fig:folds}B shows the period $P_{n}(\bar g)$ computed from \cref{eq:period} versus the cycle period of stable $n:n$ solutions, computed from numerically integrating the full system of ODEs.
+The overlap between blue and orange curves suggests that stable fixed points of $\Pi_{n}$ accurately predict the cycle period of stable solutions of the flow system.
 
@@
 It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\bar g$.
-This property follows directly from the normal form of the fold bifurcation (\cref{eq:normal-form}), but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\bar g), \bar g)=0$ in \cref{eq:Phi}.
+This property follows directly from the quadratic normal form of the fold bifurcation, but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\bar g), \bar g)=0$ in \cref{eq:Phi}.
 For $d^\star_f=\phi_n(\bar g)>d_b(n)$ we get:
 \begin{equation}
-	\label{dstardg:eq}
+	\label{eq:dstardg}
 	\dv{\phi_n}{\bar g} = -\frac{\pdv*{\Phi_n}{\bar g}}{\pdv*{\Phi_n}{d^\star}} =
@@
 \begin{align}
-	\pdv{F_n}{d^\star_f} & = \taus \frac{(\lambda\rho)^{n-1}}{\dn(d^\star_f)}>0, \\[0.5ex]
-	\pdv{F_n}{\bar g}    & = \frac{\tau_s}{\bar g}>0.
+	\pdv{F_n}{d^\star_f} & = \tau_{\kappa} \frac{(\lambda\rho)^{n-1}}{\dn(d^\star_f)}>0, \\[0.5ex]
+	\pdv{F_n}{\bar g}    & = \frac{\tau_{\kappa}}{\bar g}>0.
 \end{align}
-\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation: Increasing the coupling strength between the neurons leads to overall stronger inhibition of the \suppressed{} cell, which delays its release and leads to a longer cycle period.
-The latter allows more time for the synapse to depress in the \free{} phase and recover in the \suppressed{} phase, resulting in overall larger values of $d^\star_f$, that is weaker depression at the burst onset.
+\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation: Increasing the coupling strength between the neurons leads to overall stronger inhibition of the silent cell, which delays its release and leads to a longer cycle period.
+The latter allows more time for the synapse to depress in the active phase and recover in the silent phase, resulting in overall larger values of $d^\star_f$, that is weaker depression at the burst onset.
 
-While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the \free{} phase contains exactly $n$ spikes.
+While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the active phase contains exactly $n$ spikes.
 As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n:n$ bursts exists only on certain parameter intervals of $\bar g$.
+% TODO: Edit this sentence.
+\linelabel{line:ll}
+The multi-stability of fixed points of maps $\Pi_{n}$ in \cref{fig:folds}B does therefore not imply a similar multi-stability of the flow system.
 In the last sub-section we will analyse the mechanisms that guide how the stable $n:n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\bar g$ where such solutions exist.
 
-% TODO: Need to find a better sub-section title that doesn't include 'period increment'
-\subsection{Period increment bifurcations with co-existent attractors}
-Let $\bar g_+(n)$ and $\bar g_-(n)$ denote the left and right parameter borders on $\bar g$ where stable $n:n$ solutions exist.
-That is, as $\bar g$ is increased stable $n:n$ solutions are created at $\bar g_+(n)$ and destroyed at $\bar g_-(n)$.
-When $\bar g$ is reduced beyond $\bar g_+(n)$, $n:n$ solutions bifurcate into $(n-1)-(n-1)$ solutions, while when $\bar g$ is increased beyond $\bar g_-(n)$, $n:n$ solutions bifurcate into $(n+1)-(n+1)$ solutions.
-Let us briefly recap our observations regarding $\bar g_+(n)$ and $\bar g_-(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
+\subsection{Stable solution branch borders}
+~\label{sec:borders}
+Let $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ denote the left and right parameter borders on $\bar g$ where stable $n:n$ solutions exist.
+That is, as $\bar g$ is increased stable $n:n$ solutions are created at $\bar g_{\mathcal{L}}(n)$ and destroyed at $\bar g_{\mathcal{R}}(n)$.
+When $\bar g$ is reduced beyond $\bar g_{\mathcal{L}}(n)$, $n:n$ solutions bifurcate into $(n-1):(n-1)$ solutions, while when $\bar g$ is increased beyond $\bar g_{\mathcal{R}}(n)$, $n:n$ solutions bifurcate into $(n+1):(n+1)$ solutions.
+Let us briefly recap our observations regarding $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
 For $n>1$ there are the following relations:
 \begin{align}
-	\bar g_+(n)                   & < \bar g_-(n)\label{eq:easy1},                                         \\
-	\bar g_+(n)                   & < \bar g_+(n+1)\text{ and } \bar g_-(n)<\bar g_-(n+1)\label{eq:easy2}, \\
-	\bar g_+(n+1)                 & < \bar g_-(n)\label{eq:coexistence},                                   \\
-	\bar g_-(n+1) - \bar g_+(n+1) & < \bar g_-(n) - \bar g_-(n)\label{eq:robustness}.
+	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{R}}(n)\label{eq:easy1},                                                                 \\
+	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{R}}(n+1)\text{ and } \bar g_{\mathcal{R}}(n)<\bar g_{\mathcal{L}}(n+1)\label{eq:easy2}, \\
+	\bar g_{\mathcal{R}}(n+1)                             & < \bar g_{\mathcal{R}}(n)\label{eq:coexistence},                                                           \\
+	\bar g_{\mathcal{L}}(n+1) - \bar g_{\mathcal{R}}(n+1) & < \bar g_{\mathcal{R}}(n) - \bar g_{\mathcal{R}}(n)\label{eq:robustness}.
 \end{align}
 \Cref{eq:easy1,eq:easy2} are self-explanatory.
-\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n:n$ and $(n+1)-(n+1)$ solutions.
+\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n:n$ and $(n+1):(n+1)$ solutions.
 \Cref{eq:robustness} implies that the parameter interval on $\bar g$ of $n:n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
-All of the above relations are reminiscent of the period increment bifurcations with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
-	see][]{gardini2012,tramontana2012,avrutin2011,gardini2012}.
+\linelabel{line:branchA}
+All of the above relations are reminiscent of the bifurcation scenario of type period increment with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
+	see][]{gardini2012,tramontana2012,avrutin2011}.
 While our maps $\Pi_n$ are fully continuous, the above observation suggests that a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
@@
 
-Let us now find algebraic equations that will allow us to calculate the critical parameters $\bar g_+(n)$ and $\bar g_-(n)$ associated with the period increment bifurcations.
-% BUG: Maybe don't call it period-increment here?
-Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\bar g$:
+\linelabel{line:branchB}
+Let us now find algebraic equations that will allow us to calculate the critical parameters $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ associated with the left and right $n:n$ branch borders.
+\linelabel{line:bbb}
+Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\bar g$ (\cref{eq:dPdg}).
+That is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the silent cell, and $\Delta t$ becomes larger.
+When $\Delta t > T_{s}$, the active cell can produce another spike and the solution bifurcates into a $(n+1):(n+1)$ solution.
+Note, however, that at $\bar g_{\mathcal{L}}(n)$ the bifurcation into a $(n-1):(n-1)$ does not occur at $\Delta t = 0$.
+Here the mechanism is different: A sufficient reduction of $\bar g$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the silent cell to be released one spike earlier.
+
+Using the above reasoning we can now formulate the conditions for both bifurcations at $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$.
+As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $d^\star_f=\phi_n(\bar g)$ (\cref{eq:phi}).
+At the right bifurcation border $\bar g_{\mathcal{R}}(n)$ we have $\Delta t=T_{s}$, and after substituting our $F_n$ map (\cref{eq:Fn-map}) this translates into
 \begin{equation}
-	\dv{P_{n}}{\bar g}=2\dv{F_n(\phi_n(\bar g), \bar g)}{\bar g}>0,
-\end{equation}
-that is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the \suppressed{} cell, and $\Delta t$ becomes larger.
-When $\Delta t > T_{inact}$, the \free{} cell can produce another spike and the solution bifurcates into a $(n+1)-(n+1)$ solution.
-Note, however, that at $\bar g_+(n)$ the bifurcation into a $(n-1)-(n-1)$ does not occur at $\Delta t = 0$.
-Here the mechanism is different: A sufficient reduction of $\bar g$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the \suppressed{} cell to be released one spike earlier.
-
-Using the above reasoning we can now formulate the conditions for both bifurcations at $\bar g_+(n)$ and $\bar g_-(n)$.
-As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $d^\star_f=\phi_n(\bar g)$ (\cref{eq:phi}).
-At the right bifurcation border $\bar g_-(n)$ we have $\Delta t=T_{inact}$, and after substituting our $F_n$ map (\cref{eq:Fn-map}) this translates into
-\begin{equation}
-	F_n(\phi_n(\bar g), \bar g) = T_{inact},
+	F_n(\phi_n(\bar g), \bar g) = T_{s},
 \end{equation}
@@
 	\label{eq:R}
-	\mathcal{R}_{n}(\bar g):=F_n(\phi_n(\bar g), \bar g)-T_{inact},
+	\mathcal{R}_{n}(\bar g):=F_n(\phi_n(\bar g), \bar g)-T_{s},
 \end{equation}
-whose root is the desired right bifurcation border $\bar g_-(n)$.
+whose root is the desired right bifurcation border $\bar g_{\mathcal{R}}(n)$.
 % NOTE: @CONOR: After changing the model I'm not sure anymore whether the next equation is clear from my explanation or I need another sentence.
-In case of the left bifurcation border at $\bar g_+(n)$, the release condition is satisfied just before the \free{} cell has produced its $n$th spike, where total synaptic conductance is given by
+In case of the left bifurcation border at $\bar g_{\mathcal{L}}(n)$, the release condition is satisfied just before the active cell has produced its $n$th spike, where total synaptic conductance is given by
 \begin{equation}
-	\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{inact}/\tau_\kappa} = g^\star,
+	\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{s}/\tau_\kappa} = g^\star,
 \end{equation}
@@
 	\label{eq:L}
-	\mathcal{L}_n(\bar g):=\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{inact}/\tau_\kappa} -g^\star,
+	\mathcal{L}_n(\bar g):=\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{s}/\tau_\kappa} -g^\star,
 \end{equation}
-whose root is $\bar g_+(n)$.
+whose root is $\bar g_{\mathcal{L}}(n)$.
 Both $\mathcal{R}_n$ and $\mathcal{L}_n$ are increasing with respect to $\bar g$, which makes finding their roots numerically straightforward.
 
-\Cref{fig:final-bif} shows the period $P_n(\bar g)$ as predicted by the fixed points of $\Pi_n$ (\cref{eq:period}) plotted on their respective intervals $\bar g \in [\bar g_+(n),\bar g_-(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
+% TODO: Edit a bit more
+\Cref{fig:final-bif} shows the period $P_{n}(\bar g)$ as predicted by the fixed points of $\Pi_{n}$ (\cref{eq:period}) plotted on their respective intervals $\bar g \in [\bar g_{\mathcal{L}}(n),\bar g_{\mathcal{R}}(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
+Here $g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ were computed from \cref{eq:L,eq:R}, respectively.
 Note that the width of $n:n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
 That is, bursts with more spikes occur on increasingly smaller intervals of $\bar g$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
-We also note the occurrence of bi-stability between pairs of $n:n$ and $(n+1)-(n+1)$ branches, which also confirms our initial observation in
+We also note the occurrence of bistability between pairs of $n:n$ and $(n+1):(n+1)$ branches, which also confirms our initial observation in
 \cref{eq:coexistence}.
-
-As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate for $n>1$.
-Recall that our reduction assumptions required a sufficiently large coupling strength, which we numerically estimated to be $\bar g \approx 0.592\si{mS/cm^2}$ in \cref{fig:release-delay}.
-The mismatch in period for $1-1$ solutions, but also the mismatch in the left bifurcation border $\bar g_-(n=2)$ of the $2-2$ solution can be attributed to the violation of that assumption.
-However, even for branches of large $n:n$ solutions there is a mismatch between the bifurcation borders.
-Presumably our assumptions on the time scales of $w$ and $s$ dynamics do not hold here, and can only be captured by more complex approximations.
+As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate.
+However, the mismatch in the left and right branch borders is significant.
+This mismatch might be due to the millisecond release delay error (\cref{fig:gstar-diag}B) induced by our assumption of a constant release conductance for all $n:n$ solutions (see \cref{eq:release}).
+Another explanation for the border mismatch could be that our assumptions on the time scales of $w$ and $s$ dynamics do not hold near the stability borders, and that they can only be captured by more complex approximations.
 Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.

### 2022-03-30 tex/supplementary.tex
Update a bunch of tex files

@@
 \usepackage{cleveref}
+\usepackage{graphicx}
 \usepackage{physics}
 \usepackage{siunitx}
+\usepackage{interval}
+\intervalconfig{soft open fences}
 \usepackage{xr}
-\externaldocument{draft}
+\externaldocument{manuscript}
 
@@
 \newcommand{\taud}{\tau_d}
+
+\graphicspath{{../figures}}
 
@@
 
-Note that applying conventional methods of numerical continuation is not straightforward for our model, as the discontinuous resets in \cref{eq:s-reset} and~\eqref{eq:d-reset} make the root finding challenging~\citep[e.g.
-see][ for continuation methods]{kuznetsov2004}.
+\section{Numerical validation of constant ISI assumption}
+\label{sec:tauk}
+% TODO Double-check that you've addressed all of the reviewers concerns here.
+% TODO Write caption
+To study the effect of the synaptic time constant $\tau_\kappa$ on consecutive $ISI$s of the active cell we consider a single cell that is inhibited by an exponentially decaying synaptic conductance $g$:
+\begin{align}
+	\label{eq:dotv}
+	\dot v & = f(v, w) - g(v - v_{s}), \\
+	\label{eq:dotw}
+	\dot w & =h(v, w),                 \\
+	\label{eq:dotg}
+	\dot g & = -g/\tau_{\kappa},
+\end{align}
+where functions $f$ and $h$ come from \cref{eq:f,eq:h}.
+We assume that the cell is released and fires its first spike at time $t=0$.
+We therefore initialise $v$ at the firing threshold $v_{\theta}$, $w$ at its nullcline, and
+the $g$ at the release conductance $g^{\star}$, respectively:
+\begin{align}
+	v(0) & = v_{\theta}, \\
+	w(0) & = v(0),       \\
+	g(0) & = g^{\star}.
+\end{align}
+We vary $\tau_{\kappa}$ and integrate the system numerically to record consecutive $ISI$s.
+
+\Cref{fig:tauk-vs-ISI} shows the curves for the first ($ISI_{1}$), second ($ISI_{2}$), and third ($ISI_{3}$) inter-spike-intervals for values $\tau_{\kappa} \in \interval[open left]{0}{800}$.
+These results suggest that for $\tau_\kappa \leq 100$ we have $ISI_i \approx T$, that is, inhibition $g$ decays sufficiently fast for its effect on the spiking period to be negligible.
+For $\tau_\kappa > 100$ the first $ISI_{1}$ becomes increasingly longer with $\tau_{\kappa}$, moreover the effect of the inhibition propagates to the subsequent $ISI_{2}$ and $ISI_{3}$, suggesting that for a too slow synaptic time constant the assumption $ISI \approx T$ is not suitable.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{tauk-vs-ISI}
+	\caption{Voltage traces of both cells of numerically stable solutions for increasing
+		values of the coupling strength $\gbar$ (increasing top to
+		bottom).~\label{fig:tauk-vs-ISI}}
+\end{figure}
+
+% TODO
+% **Note of caution**: Our ICs might be inaccurate for very large $\tau_\kappa$ , since then $w(0) \approx w_\infty(g^\star)$ will be likely violated.
+
+% \section{Irregular solutions}
+% Even
 

### 2022-03-30 tex/response.tex
Pre-submission

@@
 
+\usepackage{interval}
+\intervalconfig{soft open fences}
 \usepackage{natbib}
-
+\usepackage{lineno}
+\linenumbers
 % import Eq and Section references from the main manuscript where needed
@@
 \end{center}
-We thank the reviewers for their critical assessment of our work.
+We are very grateful to the reviews for their comments.
+We are, of course, very pleased that Reviewer 2 was so supportive of our manuscript and that they have endorsed publication.
+We were equally pleased that Reviewer 1 has engaged so fully with our work, that they saw value in our results and have provided such thoughtful and valuable suggestions.
+We are sorry it has taken a long time to reply; we wanted to give careful consideration to these suggestions and have made a number of substantial extensions to the work which we believe has made it stronger; we are very grateful for the help the referee comments provided in this.
+
 The biggest changes in the revised manuscript came as a result of points \hyperref[p:biol]{P2.1.1} and \hyperref[p:gstar]{P2.3.8}, which led us to revert our model to the original equations and parameter values used in \cite{bose2011}.
-The motivation behind a slightly different model in our original manuscript, as well as the consequence of the latest changes in the revised manuscript are given in \cref{sec:model}.
+The motivation behind a slightly different model in our original manuscript, as well as the consequence of the latest changes in the revised manuscript, are explained in \cref{sec:model}.
 Both reviewers also pointed out that some of our notation and terminology is unclear.
 As a result we renamed many of the terms, an overview of the most important terms is given in \cref{sec:terminology}.
-
-We will refer to the first version of the manuscript that was submitted to the journal as ``original manuscript'' (M0), and we will call the latest submitted version the ``revised manuscript'' (M1).
+We will refer to the first version of the manuscript that was submitted to the journal as the ``original manuscript'' (M0), and we will call the latest submitted version the ``revised manuscript'' (M1).
 If not otherwise stated, the equations numbers, figures, and line numbers refer to the revised manuscript.
@@
 \Cref{sec:sum} contains the terminology as well as summarises the main model changes in the revised manuscript.
-In \cref{sec:r1} we address the concerns raised by reviewer 1, and in \cref{sec:r1} the concerns raised by reviewer 2.
+In \cref{sec:r1} we address the concerns raised by Reviewer 1, and in \cref{sec:r2} the concerns raised by Reviewer 2.
 
@@
 \label{sec:terminology}
-To increase clarity we have changed some of the terminology.
+Notation and terminology in this field is surprisingly controversial; different authors use different terms for the same thing and the same terms for things that are different, sometimes subtly different.
+We have tried to follow the referees suggestions as much as possible, but would be grateful for any further guidance.
 Below we briefly define the controversial terms.
@@
 for $t \in \left[0, (n-1)T + T_{a}\right]$.
-	\item \textbf{Silent phase}: Time interval after the end of the active phase and the cycle period, i.e. for $t \in \left[(n-1)T + T_{a}, P\right]$.
+\item \textbf{Silent phase}: Time interval after the end of the active phase and the cycle period, i.e. for $t \in \interval[open left]{(n-1)T+T_{a}}{P}$
 \item \textbf{Active phase map}: Map $F_{n}$ that models the evolution of $d$ during the active phase.
@@
 There are two main differences in the model equations and parameters between the original manuscript and \cite{bose2011}:
-First, the value of the applied current $I$ is different: In \cite{bose2011} they have $I=3.8$ $\si{\mu A/cm^2}$, in the original manuscript we had $I=3.8$ $\si{\mu A/cm^2}$.
-Second, the original manuscript used step-wise resets of $d$ and $s$ to simplify the dynamics of the active state of the spike (when $v > v_{\theta}$).
+First, the value of the applied current $I$ is different: In \cite{bose2011} they have $I=3.8$ $\si{\mu A/cm^2}$, in the original manuscript we had $I=6$ $\si{\mu A/cm^2}$.
+Second, the original manuscript uses step-wise resets of $d$ and $s$ to simplify the dynamics of the active state of the spike (when $v > v_{\theta}$).
 
@@
 
-The main motivation for increasing $I$ in the original manuscript had to do with the excitability of a silent ML cell, and was to simplify the explanation of the concept of the ``release conductance''.
+The main motivation for increasing $I$ in the original manuscript had to do with the ``excitability'' of a silent ML cell, and was to simplify the explanation of the concept of the ``release conductance''.
 \Cref{fig:nullclines} shows the $v$- and $w$-nullclines for $I=3.8$ $\si{\mu A/cm^2}$ (left) and for $I=6$ $\si{\mu A/cm^2}$ (right) when no inhibition is applied and $g = 0$ (let $g:= \bar g s$).
@@
 However, when $I=6$ $\si{\mu A/cm^2}$ the condition $g>g_{bif}$ becomes sufficient to accurately predict the release time of the silent cell, that is assuming $n>1$ and with the exception of the $2:2$ outliers in fig.
-6 (original manuscript).
+6 (M0).
 When $g>g_{bif}$ is sufficient for predicting the release time, the definition of the release conductance $g^\star$ becomes straightforward, that is $g^\star=g_{bif}$.
-Moreoever, the value of $g^\star$ can be computed numerically, for example using AUTO.
+Moreover, the value of $g^\star$ can be computed numerically, for example using AUTO.
 The downside of using $I=6$ $\si{\mu A/cm^2}$ is that finding $g^\star$ analytically becomes difficult.
-Because reviewer 1 asked for an analytic derivation of $g^\star$ in point \hyperref[p:gstar]{P2.3.8}, and to avoid more confusion by using a different model than \cite{bose2011}, we decided to use $I=3.8$ $\si{\mu A/cm^2}$ in the revised manuscript.
-As explained above, however, this comlicates the definition and explanation of $g^\star$:
+Because Reviewer 1 asked for an analytic derivation of $g^\star$ in point \hyperref[p:gstar]{P2.3.8}, and to avoid more confusion by using a different model than \cite{bose2011},
+we have followed the referee's suggestion and moved the model to $I=3.8$ $\si{\mu A/cm^2}$ in the revised manuscript; all the analysis and numerical computation has been redone with this revised value.
+As explained above, however, this complicates the definition and explanation of $g^\star$:
 Now the actual value of the release conductance (as defined by the value of $g$ at the first spike time of the silent cell) depends on both $n$ and $\bar g$, as we illustrate in \cref{fig:gstar-diag}A.
 But as the graph also shows, the dashed line appears to be a good approximation for the numerically computed release conductances.
-This line marks the value of $g$ of a suppressed and $\bar g= \bar g_s$, at the end of a cycle.
-Here that $\bar g_s$ is smallest value of $\bar g$ that produces the suppressed solution.
+This line marks the value of $g$ of a suppressed and $\bar g= \bar g_s$, at the end of a cycle; recall that $\bar g_{s}$ is the minimum coupling strength that will produce the full suppressed solution.
 And this values is easy to express analytically:
-\begin{equation}
+\begin{equation*}
 	\bar g_s d_s\lambda e^{-T_{s}/\tau_\kappa}=g^{\star} \approx 0.0068\, \si{mS/cm^2}.
-\end{equation}
-Another advantage of using $I=3.8$ $\si{\mu A/cm^2}$ is that all release delays are on the millisecond scale, and there are no more outliers such the branch B in fig. 6 (M0).
+\end{equation*}
+Another advantage of using $I=3.8$ $\si{\mu A/cm^2}$ is that all release delays are on the millisecond scale, and there are no more outliers such the branch B in fig.
+6 (M0); or at least none that we could find numerically.
+We had not anticipated this advantage and are pleased that Reviewer 1 prompted us to use this new value of $I$.
 
@@
 This change does not appear to affect the overall picture, i.e. the period bifurcation diagram has a similar shape even after our change, e.g. compare fig. 4A (M0) to \cref{fig:bif-diagram} (M1).
-However, the biological realism of the step-wise resets of $s$ and $d$ in the original manuscript were correctly questioned by reviewer 1 in \hyperref[p:biol]{P2.1.1}.
-We hope that reverting to the original equations used in \cite{bose2011} solves this concern.
+However, the biological realism of the step-wise resets of $s$ and $d$ in the original manuscript were correctly questioned by Reviewer 1 in \hyperref[p:biol]{P2.1.1}.
+We trust that reverting to the original equations used in \cite{bose2011} solves this concern.
 
@@
 Naturally all the data for all figures was recomputed with the new model.
-Fig. 5 (M0) was removed.
-Because $g^\star$ is not defined by the Hopf-bifurcation in the revised manuscript, an illustration of the nullclines as $\bar g s$ is varied seems to be of minor importance.
-Fig. 6 (M0) was also removed, since the new definition of $g^\star$ does not produce a significant release delay.
+Fig. 5 (M0) that showed the nullclines for various $\bar g s$ was removed;
+because $g^\star$ is not defined by the Hopf-bifurcation in the revised manuscript, an illustration of the nullclines as $\bar g s$ is varied seems to be of minor importance.
+The ``release delay'' fig. 6 (M0) was replaced by \cref{fig:gstar-diag}A and B (M1).
 
@@
 1 (M0) we removed the four phases of a spike (``active'', ``silent'', ``jump up'', ``jump down'').
-We did this to reduce the terminology confusion regarding ``free''/``quite'' vs ``active''/``silent'', pointed out by reviewer 1 in P2.2.1.
+We did this to reduce the terminology confusion regarding ``free''/``quite'' vs ``active''/``silent'', pointed out by Reviewer 1 in P2.2.1.
 As suggested by the reviewer, in the revised manuscript we use ``active''/``silent'' to refer to the two phases of burst only.
@@
 \item $T_{act}$ and $T_{inact}$ were renamed to $T_a$ and $T_s$, respectively.
-	\item $\bar g_{+}$ and $\bar g_{-}$ were renamed to $\bar g_{\mathcal{L}}$ and $\bar g_{\mathcal{R}}$, as a response to point P2.3.19 raised by reviewer 1.
+\item $\bar g_{+}$ and $\bar g_{-}$ were renamed to $\bar g_{\mathcal{L}}$ and $\bar g_{\mathcal{R}}$, as a response to point P2.3.19 raised by Reviewer 1.
+\item Synaptic time constant $\tau_{s}$ was renamed to $\tau_{\kappa}$, the original notation used in \cite{bose2011}.
 \end{itemize}
@@
 	When referring to a cell in the context of $n:n$ limit cycles, apart from being consistent with \citet{bose2011}, our original intent was to use the ``free''\slash``quiet'' terms to distinguish them from the phases of the action potential, where we used the more common ``active''\slash ``silent'' terms.
-	However, as reviewer 1 has pointed out, using ``active''\slash``silent'' to refer to both the phases of a spiking limit cycle \cite[e.g.~p.~250]{ermentrout2010}, and the bursting limit cycle \cite[e.g.~p.~103]{ermentrout2010} (at least in the context of ``bursty'' single cells) appears to be more common in the field.
+	However, as Reviewer 1 has pointed out, using ``active''\slash``silent'' to refer to both the phases of a spiking limit cycle \cite[e.g.~p.~250]{ermentrout2010}, and the bursting limit cycle \cite[e.g.~p.~103]{ermentrout2010} (at least in the context of ``bursty'' single cells) appears to be more common in the field.
 	For the construction of $\Pi_{n}$ only the distinction between the active ($v>v_{\theta}$) and quiet ($v<v_{\theta}$) states of an action potential, and the associated times intervals $T_{a}$ and $T_{s}$, are essential.
@@
 In the case of an uncoupled ML cell we have $ISI=T$.
-If this definition of the $ISI$ is not common in the field, then we kindly ask the reviewer to point us to references where a different, more common definition is used.
 \end{reply}
@@
 \shortreply{Agreed.
-In line \ref{line:E} we clarify that the value of $s$ ``at each spike time'' of the active cell depends only on $d$.
+In line \ref{line:F} we clarify that the value of $s$ ``at each spike time'' of the active cell depends only on $d$.
 This is because in the revised synapse model (eq.
@@
 \subsection{Major Comments}
-\textbf{Note on terminology and notation for reviewer 2:} In our replies to reviewer 2 we used the same terminology as used in the original manuscript.
-This is because the majority of the terminology changes were suggested by reviewer 1.
-In the following replies we wanted to focus on the content of the points raised by reviewer 2, instead of burdening them with new terminology.
+\textbf{Note on terminology and notation for Reviewer 2:} In our replies to Reviewer 2 we used the same terminology as used in the original manuscript.
+This is because the majority of the terminology changes were suggested by Reviewer 1.
+In the following replies we wanted to focus on the content of the points raised by Reviewer 2, instead of burdening them with new terminology.
 \setcounter{point}{0}

### 2022-03-30 tex/manuscript.tex
Pre-submission

@@
   \includegraphics{nullclines}
-  \caption{Periodic solution of relaxation-oscillator model neuron. $\bm{\mathrm{(A)}}$
+  \caption{Periodic solution of ML model neuron.
+    $\bm{\mathrm{(A)}}$
     Projection of limit cycle onto ($v,w$)-phase plane with $v$-nullcline (blue,
     $v_\infty$) and $w$-nullcline (orange, $w_\infty$). Unstable fixed point $p_{f}$
-    is indicated by an orange dot. $\bm{\mathrm{(B)}}$ Corresponding voltage trace
-    $v(t)$ of an action potential.~\label{fig:nullclines}}
+    is indicated by an orange dot; firing threshold $v_{\theta}$ is denoted by a dashed line.
+    $\bm{\mathrm{(B)}}$ Corresponding voltage trace $v(t)$ of an action potential.~\label{fig:nullclines}}
 \end{figure}
@@
 
-% \begin{figure}[h!]
-%   \centering
-%   \includegraphics{nullclines-coupled}
-%   \caption{Nullclines $v_{\infty}$ (blue) and $w_{\infty}$ (orange) in the
-%   $(v,w$)-phase plane for different values of the total synaptic conductance $\gbar
-%   s$. For small $\gbar s < g^{\star}$, fixed point $p_{f}$ is unstable (orange
-%   point). Larger values $\gbar s$ move $v_{\infty}$ down in the $(v,w)$-plane until
-%   $p_{f}$ changes stability (half orange,  half blue point) at some critical total
-%   conductance value $\gbar s = g^{\star}$, and becomes stable (blue point) for
-%   $\gbar>g^{\star}$.~\label{fig:nullclines-coupled}}
-% \end{figure}
-
 \begin{figure}[h!]
@@
   \includegraphics{gstar-diag}
-  \caption{Numerically computed values of the release conductance ($\tilde g^{\star}$) for various $n:n$ solutions.
+  \caption{
+    Numerically computed values of the release conductance $\bm{\mathrm{(A)}}$ and release delay ($\bm{\mathrm{B}}$) for various $n:n$ solutions and values $\bar g$.
 The dashed line indicates the analytical approximation of the release conductance by $g^{\star}$.\label{fig:gstar-diag}}
@@
   \includegraphics{free-quiet}
-  \caption{Schematic diagram of the free and quiet phases for a $3-3$ solution.
+  \caption{Schematic diagram of the active and silent phases for a $3:3$ solution.
     $\bm{\mathrm{(A)}}$ Membrane potentials of cell 1 ($v_{1}$) and cell 2 ($v_{2}$).
-    The grey patches depict inter-burst-intervals $\delt$. $\bm{\mathrm{(B)}}$ Total
-    synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance
-    $g^{\star}$. $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell
-    1, during free (blue) and quiet phases (orange).~\label{fig:free-quiet}}
+    Grey patches depict $\delt$ intervals.
+    $\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$.
+    $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during active (blue) and silent phases (orange).~\label{fig:free-quiet}}
 \end{figure}
@@
     $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
-    T$.~\label{fig:delta-t}}
+    T_{s}$.~\label{fig:delta-t}}
 \end{figure}
@@
   \caption{Map $\Pi_{n}:d^{\star}\mapsto d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$
-  at $\gbar=0.6$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
-  varying $\gbar \approx 0.01, 0.034, 0.3$ $\si{mS/cm^{2}}$. The identity function is
-  illustrated by a diagonal line.~\label{fig:Pn-map}}
+  at $\gbar=0.5$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
+  various $\gbar$. The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
 \end{figure}
@@
   \includegraphics[width=0.8\textwidth]{final-bif}
-  \caption{Bifurcation diagrams of stable $n:n$ solutions computed analytically from
-    fixed points of $\Pi_n$ and plotted on the respective intervals of $\gbar\in
-    \big[\gbar_{\mathcal{L}}(n),\gbar_{\mathcal{R}}(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
+  \caption{Bifurcation diagram of the period of stable $n:n$ solutions computed analytically from fixed points of $\Pi_n$, plotted on the respective intervals of $\gbar\in \big[\gbar_{\mathcal{L}}(n),\gbar_{\mathcal{R}}(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
 \end{figure}

### 2022-03-30 tex/sections/methods.tex
Pre-submission

@@
 \section{Materials and Methods}
-We consider a pair of identical Morris-Lecar neurons \citep{morris1981}, with parameters adapted from \cite{bose2011}.
+We consider a pair of identical Morris-Lecar neurons \citep{morris1981}, with parameters from \cite{bose2011}.
 The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
@@
 \end{align}
-Here $v_{-}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\bar g s_{j}$ from neuron $j$ to neuron $i$.
+Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\bar g s_{j}$ from neuron $j$ to neuron $i$.
 Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
@@
 Whenever $v_i < v_\theta$, the synaptic variable decays exponentially with time constant $\tau_\kappa$.
-The equations for the depression model were adapted from the \citet{bose2001} model.
+The equations for the depression model are identical to the \citet{bose2001} model.
 These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by \citet{tsodyks1997}.
 
-When the total inhibitory conductance $\bar g s$ is constant, the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
+When the total inhibitory conductance $\bar g s_{j}$ is constant, the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
 In case of no inhibition ($\bar g=0$), the two curves intersect near the local minimum of $v_{\infty}$ to the left of $v_{\theta}$ (commonly referred to as ``left knee'' of $v_{\infty}$), creating an unstable fixed point $p_{f}$ with a surrounding stable limit cycle of period $T=T_{a}+T_{s}$ (\cref{fig:nullclines}A).
-Here $T_{a}$ is the amount of time the membrane potential spends above firing threshold ($v>v_\theta$), while $T_{s}$ is the time it spends below firing threshold ($v<v_\theta$).
+Here $T_{a}$ is the amount of time the membrane potential spends above firing threshold ($v_{i}>v_\theta$), while $T_{s}$ is the time it spends below firing threshold ($v_{i}<v_\theta$).
 Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
@@
 % In the case of a non-zero inhibition ($g_{j}>0$) the location of $v_{\infty}$ depends on the exact value of $g_{j}$.
-Applying a constant nonzero inhibition, e.g. by setting $s=1$ and $\bar g > 0$, moves the cubic $v_{\infty}$ with the ensuing unstable fixed point down $w_{\infty}$ in the $(v-w)$ -plane.
+Applying a constant nonzero inhibition, e.g. by letting $s_{j}=1$ and $\bar g > 0$, moves the cubic $v_{\infty}$ with the ensuing unstable fixed point down $w_{\infty}$ in the $(v_{i}, w_{i})$ -plane.
 When $\bar g$ is large enough, the fixed point moves past the left knee and becomes stable via a subcritical Andoronov-Hopf bifurcation, attracting all previously periodic trajectories.
-In the following section we will refer to the value of the total conductance $\bar g s$ at the bifurcation point as $g_{bif}$.
+In the following section we will refer to the value of the total conductance $\bar g s_{j}$ at the bifurcation point as $g_{bif}$.
 
@@
 Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
-% TODO: Edit this later
-It should be noted that \citep{bose2011} used $n-n$ to denote the stable bursts with $n$ spikes, however, here we use the $n:n$ notation for more clarity.
+% % TODO: Edit this later
+% It should be noted that \citep{bose2011} used $n-n$ to denote the stable bursts with $n$ spikes, however, here we use the $n:n$ notation for more clarity.

### 2022-03-30 tex/sections/results.tex
Pre-submission

@@
 eight-dimensional system to a more tractable problem.
-As we will explain, we do this by approximating the full dynamics by a reduced system describing the dynamics of the depression variable $d$ of either of the two cells.
+As we will explain, we do this by approximating the full dynamics by a reduced system that describes the evolution of the depression variable $d$ of either of the two cells.
 We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the active phase, and then during the silent phase.
@@
 Assuming $ISI=T$ seems reasonable given that inhibition acting on the silent cell decays exponentially on a much shorter timescale $\tau_{\kappa}$ than the duration of the $ISI$.
-Therefore once the silent cell is released its trajectory quickly approaches the spiking limit cycle.
+Therefore, once the silent cell is released its trajectory quickly approaches the spiking limit cycle.
 Naturally the above assumption requires a sufficiently small $\tau_{\kappa}$, and fails when $\tau_{\kappa}$ is large.
@@
 Our second assumption states that the silent cell is released and spikes as soon as the total inhibitory conductance $\bar g s$ acting on it drops below some threshold value.
-We call this critical threshold value the ``release conductance'', and define it as the value of $\bar g s$ at the time when the voltage of the quiet cell first crosses the firing threshold $v_{\theta}$, that is when that cell is released and fires its first spike.
-Recall that when a cell is quiet its $v$- and $w$-nullclines intersect at a stable fixed point and $\bar g s > g_{bif}$.
+We call this critical threshold value the ``release conductance'', and define it as the value of $\bar g s$ at the time when the voltage of the silent cell first crosses the firing threshold $v_{\theta}$, that is when that cell is released and fires its first spike.
+Recall that when a cell is silent its $v$- and $w$-nullclines intersect at a stable fixed point and $\bar g s > g_{bif}$.
 % The following does not necessarily imply that it fires instantly on release.
-A sufficient condition for the quiet cell to be released is therefore $\bar g s < g_{bif}$.
+A sufficient condition for the silent cell to be released is therefore $\bar g s < g_{bif}$.
 However, depending on the topology of the stable manifold, the $(v,w)$-trajectory of the silent cell can escape the stable fixed point and allow the cell to produce a spike for $\bar g s > g_{bif}$.
@@
 \end{equation}
-as a constant release condition for all $n:n$ solutions allows us to accurately predict the timing of the release of the quiet cell.
+as a constant release condition for all $n:n$ solutions allows us to accurately predict the timing of the release of the silent cell.
 And to simplify the terminology, from now on we will refer to \cref{eq:release} simply as the ``release condition''.
@@
 
-% NOTE: Perhaps mention the first assumption here as well.
 In summary: We assume that the release condition is sufficient to predict when the silent cell is released.
-Due to the symmetry of $n:n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
+Due to the symmetry of $n:n$ solutions the release occurs at exactly half the period of the full cycle.
 The release time therefore uniquely determines the type of $n:n$ solution.
@@
 The terms ``active'' and ``silent'' phases will be defined in terms of the state of the depression variable.
-Hence, during the active phase the depression variable of the active cell will both decay and recover, while during the silent phase it will only recover.
+During the active phase the depression variable of the active cell both decays and recovers, while during the silent phase it only recovers.
 First, let us give explicit definitions of the active and silent phases of a burst.
@@
 We can now define the active and silent phases of cell 1 explicitly.
+% TODO: This NEEDS editing. Silent phase term here confusing.
 The active phase of a burst is the interval that lasts from the first spike time up until the beginning of the silent phase of the last spike, that is for time $0<t<(n-1)T + T_{a}$.
@@
 The silent phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T + T_{a} < t < P_n$.
-Hence the silent phase lasts for $(n-1)T + T_{a} + 2\Delta t$.
+The silent phase lasts for $(n-1)T + T_{a} + 2\Delta t$.
 
@@
 
-Given constant $T_{a}$ and $T_{s}$, parameter $\lambda$ determines how much the synapses depresses during the active phase of the spike, while $\rho$ determines how much it recovers during the silent phase.
+Given constant $T_{a}$ and $T_{s}$, the derived parameter $\lambda$ determines how much the synapses depresses when $v>v_{\theta}$, while $\rho$ determines how much it recovers when $v<v_{\theta}$.
 Since $0<\lambda, \rho<1$, the map in \cref{eq:map-d} is increasing and contracting, with a fixed point at
@@
 Using the release condition in \cref{eq:release} allows us to derive the value of the minimum coupling strength that will produce the full suppressed solution, denoted as $\bar g_{s}$.
-% TODO  Would be good to elaborate on the idea that lambda and tau can be viewed as the new time constants in the reduced system.
 Solving \cref{eq:dot-s-down} for $s(t)$ with $t=T_{s}$ and setting the initial value $s(0)=d_s\lambda$ then gives us the aforementioned approximation of the release conductance $g^{\star}$:
@@
 Our assumption of the release condition guarantees that the silent cell 2 spikes and becomes active when $\bar g s - g^{\star}$ crosses zero.
-Solving \cref{eq:release2} for $\Delta t$ allows us to compute $\Delta t$ as a function of $d^{\star}$, which defines our map $F_{n}$:
+Solving \cref{eq:release2} for $\Delta t$ allows us to compute $\Delta t$ as a function of $d^{\star}$, which defines the map $F_{n}$:
 \begin{equation}
@@
 Function $\phi_n(\bar g)$ is also monotonic, and is therefore straightforward to compute numerically.
-Here we use the Python package Pynverse \citep{pynverse} for that purpose.
+We use the Python package Pynverse \citep{pynverse} for that purpose.
 
@@
 This mismatch might be due to the millisecond release delay error (\cref{fig:gstar-diag}B) induced by our assumption of a constant release conductance for all $n:n$ solutions (see \cref{eq:release}).
-Another explanation for the border mismatch could be that our assumptions on the time scales of $w$ and $s$ dynamics do not hold near the stability borders, and that they can only be captured by more complex approximations.
+Another explanation for the border mismatch could be that our assumptions on the time scales of $(v,w)$ vs $s$- and $d$-dynamics do not hold near the stability borders, and that they can only be captured by more complex approximations.
 Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.

### 2022-03-30 tex/supplementary.tex
Pre-submission

@@
 		$\tau_\kappa$                    & $100$ \si{ms}         \\
-		$\tau_\gamma$                    & $0.0001$ \si{ms}      \\
 		$v_{\theta}$                     & $0$ \si{mV}           \\
@@
 		$T$                              & $376$ \si{ms}         \\
-		$T_{act}$                        & $49$ \si{ms}          \\
-		$T_{inact}$                      & $327$ \si{ms}         \\
+		$T_{a}$                        & $49$ \si{ms}          \\
+		$T_{s}$                      & $327$ \si{ms}         \\
 		$g^{\star}$                      & $0.0068$ \si{mS/cm^2} \\
 		$g_{bif}$                        & $0.0038$ \si{mS/cm^2} \\
-		$\lambda:=\exp(-T_{act}/\tau_b)$ & $0.612$               \\
-		$\rho:=\exp(-T_{inact}/\tau_a)$  & $0.721$               \\
+		$\lambda:=\exp(-T_{a}/\tau_b)$ & $0.612$               \\
+		$\rho:=\exp(-T_{s}/\tau_a)$  & $0.721$               \\
 	\end{tabular}
@@
 The bifurcation diagram of stable $n-n$ solutions of the two-cell network in \cref{fig:bif-diagram} is obtained numerically as follows:
-We initialise the coupling strength at parameter values associated with one type of $n-n$ solution, that is we choose the values $\bar g = 0.4, 0.7, 0.8, 0.9, 0.98$ for the $1-1$, $2-2$, $3-3$, $4-4$, and $5-5$ solutions respectively.
+We initialise the coupling strength at parameter values associated with one type of $n-n$ solution, that is we choose the values $\bar g = 0.35, 0.4, 0.5, 0.52, 0.56$ for the $1-1$, $2-2$, $3-3$, $4-4$, and $5-5$ solutions respectively.
 For each $\bar g$ the system is then numerically integrated sufficiently long for any transients to fully subside.

### 2022-03-30 scripts/check_slopes.py

@@ -1,0 +1,11 @@
+"""Check if dQ/dd is positive."""
+
+ds = np.linspace(0.0001, 300, 100)
+
+fig, ax = plt.subplots()
+# ax.plot(ds, [PoincareMap(3).Q_map_slope(d, 0.5) for d in ds])
+# ax.plot(ds, [PoincareMap(3).Q_map_slope_num(d, 0.5) for d in ds])
+
+ax.plot(ds, [PoincareMap(4).Q_map_slope(d, 0.5) for d in ds])
+ax.plot(ds, [PoincareMap(4).Q_map_slope_num(d, 0.5) for d in ds])
+fig.savefig('tmp/tmp.pdf')

### 2022-03-30 scripts/compute.py

@@ -11,14 +11,14 @@ import pandas as pd
 from poincare_map import ode, paths, poincare_map
 
 
-def compute_numeric_bif_diagram() -> pd.DataFrame:
+def compute_numeric_bif_diagram(dt: float=0.5) -> pd.DataFrame:
     """Compute bifurcation diagram numerically for n=1,2,3,4,5."""
     mlml = ode.MLML("odes/mlml.ode")
     nsteps = 100
 
-    gmin = 0.3
+    gmin = 0.01
     ns = [1, 2, 3, 4, 5]
-    g0s = [0.3, 0.4, 0.5, 0.52, 0.56]
+    g0s = [0.35, 0.4, 0.5, 0.52, 0.56]
     gsteps = [0.002, 0.002, 0.002, 0.001, 0.001]
     totals = [5000, 8000, 10000, 15000, 15000]
 
@@ -26,10 +26,10 @@ def compute_numeric_bif_diagram() -> pd.DataFrame:
     for n, g0, step, total in zip(ns, g0s, gsteps, totals):
         print(f"Starting branch at g={g0}")
         left = mlml.continuate(
-            n=n, step=-step, nsteps=nsteps, g=g0, total=total, gmin=gmin
+            n=n, step=-step, nsteps=nsteps, g=g0, total=total, gmin=gmin, dt=dt
         )
         right = mlml.continuate(
-            n=n, step=step, nsteps=nsteps, g=g0, total=total, gmin=gmin
+            n=n, step=step, nsteps=nsteps, g=g0, total=total, gmin=gmin, dt=dt
         )
         if (left is not None) and (right is not None):
             curve = pd.concat([left.iloc[::-1], right]).reset_index(
@@ -71,10 +71,10 @@ if __name__ == "__main__":
         numeric_diagram = compute_numeric_bif_diagram()
         numeric_diagram.to_pickle(paths.numeric_bif_diagram)
 
-    if (not paths.analytic_bif_diagram.exists()) or args.recompute:
-        print("Computing analytic bifurcation diagram.")
-        analytic_diagram = compute_analytic_bif_diagram()
-        analytic_diagram.to_pickle(paths.analytic_bif_diagram)
+    # if (not paths.analytic_bif_diagram.exists()) or args.recompute:
+    #     print("Computing analytic bifurcation diagram.")
+    #     analytic_diagram = compute_analytic_bif_diagram()
[…]

### 2022-03-30 scripts/find_gstar.py

@@ -1,0 +1,200 @@
+"""Find gstar numerically."""
+
+
+from poincare_map import ode
+from poincare_map import helpers
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+from matplotlib.figure import Figure
+import intersect
+import tqdm
+from typing import Tuple
+import pandas as pd
+from poincare_map.model import PoincareMap
+
+plt.ioff()
+
+rcp = matplotlib.rcParamsDefault
+rcp["axes.spines.right"] = False
+rcp["axes.spines.top"] = False
+matplotlib.rcParams.update(rcp)
+
+VTHETA = 0
+GSTAR = 0.0068
+T = 376
+
+xppfile = "odes/ml.ode"
+
+
+def roots(x, y) -> np.ndarray:
+    return intersect.intersection(x, y, x, np.zeros(len(x)))[0]
+
+
+def calc(
+    xppfile: str = "odes/ml.ode",
+    g: float = 0.5,
+    tauk: float = 100,
+    total: float = 400,  # big enough even for large g?
+    **kwargs,
+) -> pd.DataFrame:
+    """Compute solution given initial conditions."""
+    vnull, wnull = ode.nullclines(xppfile, gtot=GSTAR)
+    v_fp, w_fp = intersect.intersection(
+        vnull[:, 0], vnull[:, 1], wnull[:, 0], wnull[:, 1]
+    )
+    v0 = v_fp[0]
+    w0 = w_fp[0]
+    s0 = 1
+    ics = np.array([v0, w0, s0])
+    sol = ode.run(xppfile, ics=ics, g=g, tauk=tauk, total=total, **kwargs)
+    return sol
+
+
+def calc_sol(
+    xppfile: str = "odes/ml.ode",
+    g0: float = 0.1,
+    total: float = 800,  # big enough even for large g?
+    **kwargs,
+) -> pd.DataFrame:
+    """Compute solution given initial conditions."""
+    vnull, wnull = ode.nullclines(xppfile, gtot=g0)
+    v_fp, w_fp = intersect.intersection(
+        vnull[:, 0], vnull[:, 1], wnull[:, 0], wnull[:, 1]
+    )
+    v0 = v_fp[0]
+    w0 = w_fp[0]
+    ics = np.array([v0, w0, g0])
[…]

### 2022-03-30 scripts/main.py

@@ -1,0 +1,29 @@
+# %% Init stuff
+import matplotlib.pyplot as plt
+import numpy as np
+from poincare_map.poincare_map import PoincareMap
+from poincare_map.bif import compute_analytic
+
+xppfile = "odes/mlml.ode"
+
+#%% Plot G
+
+fig, ax = plt.subplots()
+for n in [1, 2, 3, 4, 5, 6]:
+    poincare = PoincareMap(n=n)
+    branch = poincare.stable_branch()
+    if branch is not None:
+        ax.plot(branch['g'], branch['period'])
+
+fig.savefig('tmp/ana-bif.pdf')
+
+#%% phi stable
+
+gs = np.linspace(0, 1, 100)
+fig, ax = plt.subplots()
+ax.plot(gs, [PoincareMap(n=1).phi_stable(g) for g in gs])
+fig.savefig('tmp/phi_stable.pdf')
+
+
+#%% Plot diagram
+PoincareMap(n=2).phi_stable(0.01)

### 2022-03-30 scripts/makefig.py

@@ -1,4 +1,5 @@
 import os
+import tqdm
 from functools import partial
 import pickle
 import pandas as pd
@@ -58,80 +59,176 @@ pmap = PoincareMap()
 df = pd.read_pickle(paths.numeric_bif_diagram)
 df_ana = pd.read_pickle(paths.analytic_bif_diagram)
 
-#%% Nullclines uncoupled
-vs = np.linspace(-65, 60, 100)
-vnull = [ml.vinf(v, gtot=0) for v in vs]
-wnull = [ml.winf(v) for v in vs]
-lc = ml.find_equilibrium(total=3000)
 
-# loop = lc.append(lc.iloc[0])    # Close the loop.
-loop = lc
+#%% Nullclines
 
-#%%
+# Compute spiking solution.
+lc = ml.find_limit_cycle()
+
 # Plot.
 fig, axs = plt.subplots(ncols=2, tight_layout=True, figsize=FIG2by1)
 
-# Nullclines.
+# A: Nullclines.
+vs = np.linspace(-69, 60, 100)
+vinf = np.vectorize(ml.vinf)
+winf = np.vectorize(ml.winf)
+
 ax = axs[0]
-ax.plot(vs, vnull, color="C0")
-ax.plot(vs, wnull, color="C1")
-(line,) = ax.plot(loop["v"], loop["w"], color="black")
-fp_stable = [-5.53, 0.219]
-ax.plot(fp_stable[0], fp_stable[1], c="C1", marker="o", markeredgecolor="k")
-ax.text(fp_stable[0] + 4, fp_stable[1] - 0.01, r"$p_f$")
+ax.plot(vs, vinf(vs), color="C0")
+ax.plot(vs, winf(vs), color="C1")
+ax.axvline(ml.pars["vtheta"], c="k", ls="--", lw=0.7)
+(line,) = ax.plot(lc["v"], lc["w"], color="black")
+vfp = ml.fixed_point()
+wfp = ml.winf(vfp)  # type: ignore
+if vfp:
+    ax.plot(vfp, wfp, c="C1", marker="o", markeredgecolor="k")
+    ax.text(vfp - 6, wfp + 0.03, r"$p_f$")
 
 helpers.add_arrow_to_line2D(
     ax, line, arrow_locs=[0.05, 0.35, 0.6, 0.8], arrowstyle="->"
 )
+ax.text(ml.pars["vtheta"] - 10, 0.48, r"$v_\theta$")
 
-ax.text(-45, 0.442, "Jump Down")
[…]

### 2022-03-30 scripts/makefig_bak.py

@@ -1,0 +1,1301 @@
+# %% Initialise
+import itertools
+import multiprocessing
+import os
+import pickle
+import string
+import warnings
+from os import path
+
+import matplotlib
+matplotlib.use('pgf')
+
+import pandas as pd
+import pyxpp.pyxpp as xpp
+import scipy as sp
+from matplotlib import patches
+from matplotlib import pyplot as plt
+from matplotlib.gridspec import GridSpec
+from matplotlib.lines import Line2D
+from pandas import DataFrame
+from scipy.misc import derivative
+from pathlib import Path
+
+from poincare_map import helpers
+from poincare_map import model
+from poincare_map import ode
+from poincare_map import paths
+
+import numpy as np
+
+plt.ioff()
+
+warnings.filterwarnings("ignore", category=DeprecationWarning)
+# Ignore devide by zero
+np.seterr(divide='ignore')
+np.seterr(all='ignore')
+
+
+xppfile = str(paths.odes / "mlml.ode")
+CENTER_TITLE_SIZE = 11
+FIGWIDTH = 3.85
+FIGSIZE = (FIGWIDTH, FIGWIDTH)
+FIG2by1 = (FIGWIDTH*1.4, (FIGWIDTH*1.4)/2)
+
+EQSIZE = 15                     # Font size of equaitons.
+
+rcp = matplotlib.rcParamsDefault
+rcp['figure.max_open_warning'] = 0
+rcp['axes.unicode_minus'] = False
+rcp['text.usetex'] = True
+rcp['pgf.rcfonts'] = False
+rcp['pgf.texsystem'] = 'pdflatex'
+rcp['xtick.labelsize'] = 'small'
+rcp['ytick.labelsize'] = 'small'
+rcp['axes.labelsize'] = 'x-large'
+rcp['axes.titlesize'] = 'xx-large'
+rcp['figure.titlesize'] = 'large'
+rcp['font.size'] = 9
+# Use latex preamble.
+rcp['pgf.preamble'] = r'\usepackage{amsmath} \usepackage{siunitx}'
+
+matplotlib.rcParams.update(rcp)
+
+p = xpp.read_pars(xppfile)
+
[…]

### 2022-03-30 scripts/plot_tauk.py

@@ -1,203 +1,0 @@
-from poincare_map import ode
-from poincare_map import helpers
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib
-from matplotlib.figure import Figure
-import intersect
-import tqdm
-from typing import Tuple
-import pandas as pd
-
-plt.ioff()
-
-rcp = matplotlib.rcParamsDefault
-rcp["axes.spines.right"] = False
-rcp["axes.spines.top"] = False
-matplotlib.rcParams.update(rcp)
-
-GSTAR = 0.0036
-T = 375
-
-xppfile = "odes/ml.ode"
-vnull, wnull = ode.nullclines(xppfile, gtot=GSTAR)
-v_fp, w_fp = intersect.intersection(vnull[:, 0], vnull[:, 1], wnull[:, 0], wnull[:, 1])
-v_fp = v_fp[0]
-w_fp = w_fp[0]
-
-
-def roots(x, y) -> np.ndarray:
-    return intersect.intersection(x, y, x, np.zeros(len(x)))[0]
-
-
-def calc(
-    xppfile: str,
-    v0: float = v_fp,
-    w0: float = w_fp,
-    gstar: float = GSTAR,
-    g: float = 0.5,
-    tauk: float = 100,
-    total: float = 400,  # big enough even for large g?
-    **kwargs,
-) -> pd.DataFrame:
-    """Compute solution given initial conditiosn"""
-    s0 = gstar / g
-    ics = np.array([v0, w0, s0])
-    sol = ode.run(xppfile, ics=ics, g=g, tauk=tauk, total=total, **kwargs)
-    return sol
-
-
-
-def nth_ISI(sol: pd.DataFrame, n: int = 0) -> float:
-    """Compute nth ISI."""
-    x0s = roots(sol.t, sol.v)
-    spikes = x0s[::2]
-    ISIs = np.diff(spikes)
-    return ISIs[n]
-
-
-#* spikes
-
-signs = np.sign(sol.v)
-roots = np.where(signs + np.roll(signs, 1) == 0)[0]
-
-id1 = helpers.spikes(sol.v)
-
-
-
-fig, ax = plt.subplots()
-ax.plot(sol.t, sol.v)
[…]

### 2022-03-30 scripts/plot_tauk_bak.py

@@ -1,0 +1,112 @@
+import intersect
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import tqdm
+
+from poincare_map import helpers, ode, paths
+from poincare_map.poincare_map import PoincareMap
+
+plt.ioff()
+
+rcp = matplotlib.rcParamsDefault
+rcp["axes.spines.right"] = False
+rcp["axes.spines.top"] = False
+matplotlib.rcParams.update(rcp)
+
+ml = ode.ML(paths.ml_file)
+pmap = PoincareMap()
+
+
+def calc_ISIs(sol: pd.DataFrame) -> np.ndarray:
+    """Compute nth ISI."""
+    spike_times = helpers.spike_times(sol["v"])
+    ISIs = np.diff(spike_times)
+    return ISIs
+
+
+def calc_release_delay(sol: pd.DataFrame, gstar: float) -> float:
+    """Compute the release time, that is when gs=g*."""
+    spike_times = helpers.spike_times(sol["v"])
+    if len(spike_times) > 0:
+        # Get rid of transient
+        _sol = sol.loc[sol.index > 5]
+        # Release time as defined by the release condition
+        release_condition_satisfied = _sol.loc[_sol["gtot"] < gstar].index[0]
+        return release_condition_satisfied - spike_times[0]
+
+
+gbif = 0.00379
+# Make ICs and integrate
+gstar = pmap.gstar
+# TODO: Repeat with gbif
+vfp = ml.fixed_point(gtot=gstar)
+wfp = ml.winf(vfp)  # type: ignore
+
+sols_tauk = []
+sols_delay = []
+tauks = np.linspace(10, 800, 50)
+for tauk in tqdm.tqdm(tauks):
+    # tauk
+    gtot0 = gstar
+    v0 = ml.pars["vtheta"] - 1  # Subtract 1 to have a root at t=0.
+    w0 = wfp
+    ics = np.array([v0, w0, gtot0])
+    sol = ml.run(total=2000, ics=ics, tauk=tauk, dt=0.1)
+    sols_tauk.append(sol)
+
+    # delay
+    gtot0 = 0.45
+    v0 = ml.fixed_point(gtot=gtot0)
[…]

### 2022-03-30 scripts/refactor.py

@@ -1,0 +1,114 @@
+## Copy of recursive maps and functions (in case I need that)
+
+
+def L2delt(self, L: float) -> float:
+    """Get delta-t from burst length L."""
+    if L < 0:
+        return L
+    else:
+        return L % self.T
+
+
+
+def L2n(self, L: float) -> int:
+    """Get number of spikes in burst of length L."""
+    if L < 0:
+        return 0
+    else:
+        return int(L // self.T + 1)
+
+
+def d2n(self, d: float) -> int:
+    """Just a convenience function to find n from d."""
+    L = self.F_map(d)
+    return self.L2n(L)
+
+def F_map(self: self, d: float) -> float:
+    """Recursive free phase map F."""
+    if s_sol(self, d) <= self.gstar:
+        return self.taus * np.log(self.g * d / self.gstar)
+    else:
+        dnew = d_sol(self, d)
+        return self.T + F_map(self, dnew)
+
+
+def Q_map(self: self, L: float) -> float:
+    """Recursive quiet phase map Q."""
+    delt = L2delt(self, L)
+    n = L2n(self, L)
+    return Qn_map(self, delt, n)
+
+
+def P_map(self: self, d: float) -> float:
+    """Recursive burst map."""
+    return Q_map(self, F_map(self, d))
+
+
+def P_map_fps(
+    self: self, nsteps: int = 10000, con_thresh: float = 0.005
+) -> [float, float]:
+    """
+    Compute fixed points of recursive P-map using brute force.
+
+    Since the input is 1D and the function only partially
+    continuous brute force is appropriate.
+
+    """
+
+    # Define grid.
+    xs = np.linspace(0, 1, nsteps)
+    ys = np.array([P_map(self, x) - x for x in xs])
+
+    # Find continuous intervals.
+    contints = np.hstack(([0], abs(np.diff(ys)) < con_thresh))
+    # Find zero crossing by sign change.
+    zerocros = np.hstack(([0], np.diff((ys > 0) * 1)))
+
+    # Roots
+    y0idxs = np.where(np.multiply(contints, zerocros))
+    roots = xs[y0idxs]
+
+    return roots
+
+
+def P_map_period(self: self, dstar: float) -> float:
+    """Estimate burst period from a fixed point of recursive P-map."""
+    L = F_map(self, dstar)
+    n = L2n(self, L)
+    delt = L2delt(self, L)
[…]

### 2022-03-30 scripts/refactor_model.py

@@ -1,0 +1,473 @@
+"""Script to test refactoring of maps in model.py"""
+import matplotlib.pyplot as plt
+import numpy as np
+from poincare_map.model import PoincareMap
+import pickle
+
+plt.ioff()
+
+xppfile = "odes/mlml.ode"
+model = PoincareMap.from_ode("odes/mlml.ode")
+
+#%%
+
+ds = np.linspace(-1, 1, 100)
+
+n = 3
+fig, ax = plt.subplots()
+Ps = [model.P_map(d, n) for d in ds]
+ax.plot(ds, Ps, label="comp")
+Ps = [model.P_map_direct(d, n) for d in ds]
+ax.plot(ds, Ps, ".", label="direct")
+ax.legend()
+fig.savefig("tmp/pimap.pdf")
+
+
+#%% Vary g
+gs = [0.1, 0.3, 0.6]
+
+fig, ax = plt.subplots()
+for g in gs:
+    Ps = [model._replace(g=g).P_map(d, n) for d in ds]
+    ax.plot(ds, Ps, label=f"g={str(g)}")
+ax.legend()
+fig.savefig("tmp/pimap_g.pdf")
+
+#%% inverse
+
+g = 0.55
+n = 4
+f = lambda d: model._replace(g=g).G(d, n)
+dmin, gmin = model.critical_fp(n)
+kk = inversefunc(f, g, domain=[dmin, 1])
+
+#%% Left border
+from scipy import optimize
+
+f = lambda g: model.L_fun(g, n=3)
+fp0 = optimize.newton(f, x0=1.0)
+
+#%% Test period
+
+# Load numericly computed diagram
+df = pickle.load(open("data/bif-diagram.pkl", "rb"))
+# ns = df.n.unique()
+ns = [2, 3, 4, 5]
+
+fig, ax = plt.subplots()
+for idx, n in enumerate(ns):
+    dfn = df[(df.n == n) & (df.g > 0.1)]
+    ax.plot(dfn.g, dfn.period, c=f"C{idx}")
+    # Compute analytic period
+    # Ps = [model.Period(g, n) for g in dfn.g]
+    # ax.plot(dfn.g, Ps, c='C1', linewidth=1)
+
+gg = 0.006788
+# Plot left/right borders
+for idx, n in enumerate(ns):
+    # NOTE: We're cheating here since T=376.3
+    left_border = model._replace(gstar=gg).left_branch_border(n)
[…]

### 2022-03-30 src/poincare_map/model_backup.py

@@ -1,0 +1,169 @@
+
+    # ----------------------------------------------------------
+    # TODO: Sort this out, what's still needed and what can be discarded
+
+    # def Pn_map_diff(self, d: float, n: int) -> float:
+    #     """Derivative of Pn for root finder."""
+
+    #     _delta = self.delta(self, d, n)
+    #     gr = self.g / self.gstar
+    #     tau = 2 * self.taus / self.taud
+    #     b = (self.taud - 2 * self.taus) / (self.taud * self.taus)
+    #     p1 = (
+    #         self.taus
+    #         * self.alpha(self, n)
+    #         * pow(self.Rho, n - 1)
+    #         * pow(gr, -tau)
+    #     )
+    #     p2 = 2 / self.taud * pow(_delta, -(tau + 1)) + b * self.Lambda * pow(
+    #         _delta, -tau
+    #     )
+    #     return p1 * p2
+
+    # def Pn_map_fps(self, n: int) -> Tuple[Optional[float], Optional[float]]:
+    #     """Compute fixed points of Pn-map using Newton."""
+
+    #     P = lambda d: self.P_map(d, n) - d
+    #     DP = lambda d: self.Pn_map_diff(d, n) - 1
+
+    #     # Unstable fixed point
+    #     EPSILON = 0.0001
+    #     x0 = self.d_a(n) + EPSILON
+    #     try:
+    #         fp0 = optimize.newton(P, x0, fprime=DP)
+    #         # fp0 = sp.optimize.brentq(P, x0, 1)
+    #     except:
+    #         fp0 = None
+
+    #     # Stable fixed point
+    #     x1 = 1
+    #     try:
+    #         fp1 = optimize.newton(P, x1, fprime=DP)
+    #     except:
+    #         fp1 = None
+
+    #     # There are either two or no fixed points.
+    #     if fp0 is None and fp1 is None:
+    #         return (None, None)
+    #     else:
+    #         return (fp0, fp1)
+
+    # def Phi(self, d, n):
+    #     """Fixed point equation."""
+    #     return self.P_map(d, n) - d
+
+    # def phi(self, n, x0=1.0):
+    #     """Numerically find stable fixed point."""
+    #     try:
+    #         fp = optimize.newton(partial(self.Phi, n=n), x0)
+    #         if np.isreal(fp):
+    #             return np.real(fp)
+    #         else:
+    #             return np.nan
+    #     except:
+    #         return np.nan
+
[…]

### 2022-03-30 src/poincare_map/ode.py

@@ -75,6 +75,11 @@ class ODE(ABC):
         """Numerically compute fixed point of nullclines."""
         pass
 
+    @abstractmethod
+    def find_limit_cycle(self, **kwargs) -> pd.DataFrame:
+        """Integrate and return either limit cycle solution or empty dataframe."""
+        pass
+
 
 class ML(ODE):
     def rand_ics(self, seed: int | None = None) -> pd.DataFrame:
@@ -87,23 +92,30 @@ class ML(ODE):
         )
         return pd.DataFrame([ics], columns=self.state_vars)
 
-    def find_equilibrium(self, thresh: float = 2, **kwargs) -> pd.DataFrame:
+    def find_limit_cycle(self, thresh: float = 2, **kwargs) -> pd.DataFrame:
         """Integrate and return either limit cycle or stable fixed point."""
         solution = self.run(**kwargs)
         if not solution.empty:
             spikes = helpers.spike_times(solution["v"])
             if spikes.empty:
-                # Return stable fixed point instead.
-                return solution.iloc[-1]
+                # If no limit can be found return empty DataFrame.
+                return pd.DataFrame(columns=solution.columns)
             else:
                 lc_index = helpers.limit_cycle_index(
                     solution["v"], spikes, thresh=thresh
                 )
                 lc = solution.loc[lc_index]
-                return lc
-        else:
-            # Return empty dataframe.
-            return solution
+                # Make lc cyclic
+                lc = pd.DataFrame(
+                    np.vstack([lc.values, lc.iloc[0].values]),
+                    columns=lc.columns,
+                )
+                # Reset time index
+                period = lc.index[-1] - lc.index[0]
+                time = np.linspace(0, period, len(lc))
+                return lc.set_index(pd.Index(time, name=lc.index.name))
+        # If no limit can be found return empty DataFrame.
+        return pd.DataFrame(columns=solution.columns)
 
     def minf(self, v: float) -> float:
         """Calcium asymptotic function."""
@@ -121,7 +133,7 @@ class ML(ODE):
         I_k = self.pars["gk"] * (v - self.pars["vk"])
         return (-I_leak - I_ca - I_syn + self.pars["iapp"]) / I_k
 
-    def fixed_point(self, gtot: float, x0: float = -69) -> float | None:
+    def fixed_point(self, gtot: float = 0.0, x0: float = -69) -> float | None:
         """Numerically compute fixed point of nullclines."""
[…]

### 2022-03-30 src/poincare_map/ode_debug.py

@@ -1,0 +1,131 @@
+import numpy as np
+from functools import partial
+import pandas as pd
+import matplotlib.pyplot as plt
+import typing as tp
+
+plt.ioff()
+
+from poincare_map import ode
+from poincare_map.poincare_map import PoincareMap
+from poincare_map import helpers
+from scipy import optimize
+
+ml = ode.ML("odes/ml.ode")
+mlml = ode.MLML("odes/mlml.ode")
+
+#%% Find HB.
+
+gstar = 0.0068
+g_hb = ml.find_HB(g0=0.007, total=3000)
+
+#%% Investigate how close cell trajectory is to fixed point trajectory.
+vs = np.linspace(-60, 60, 500)
+
+# Initialise system at fixed point.
+# gtots = np.linspace(0.3, tp.cast(float, g_hb), 100)
+gtot0 = 0.3
+vfp0 = tp.cast(float, ml.fixed_point(gtot0))
+
+# Integrate for single gtot for now
+sol = ml.run(ics=[vfp0, ml.winf(vfp0), gtot0])
+vfp = np.array([ml.fixed_point(gtot) for gtot in sol["gtot"]])
+wfp = [ml.winf(v) for v in vfp]
+unstable_mask = sol["gtot"]<g_hb
+v_LK = [
+    tp.cast(float, ml.find_left_knee(gtot)) for gtot in sol["gtot"]
+]
+w_LK = [ml.winf(v) for v in v_LK]
+
+
+#%% Plot nullclines
+fig, ax = plt.subplots()
+# Plot nullclines without inhibition
+ax.plot(vs, [ml.winf(v) for v in vs])
+ax.plot(vs, [ml.vinf(v, 0) for v in vs])
+ax.plot([vfp0], [ml.winf(vfp0)], "o", color="black")
+ax.plot(sol["v"], sol["w"], color="black")
+# ax.plot(vfp_trajectory, [ml.winf(v) for v in vfp_trajectory], color="red")
+ax.plot(
+    v_LK,
+    [ml.winf(v) for v in v_LK],
+    color="red",
+    linestyle="dotted",
+)
+ax.set(xlabel="v", ylabel="w", ylim=(-0.05, 0.4), xlim=(-62, 10))
+fig.savefig("tmp/LK/nullclines.pdf")
+
+fig, ax = plt.subplots()
+ax.plot(sol.index, sol["gtot"])
[…]

### 2022-03-30 src/poincare_map/plots.py

@@ -17,15 +17,13 @@ from matplotlib.lines import Line2D
 import string
 import numpy as np
 
-import pyxpp.pyxpp as xpp
 from poincare_map.poincare_map import PoincareMap
 from poincare_map import ode
 from poincare_map import paths
 
-# plt.ioff()
 
 xppfile = "odes/mlml.ode"
-model = PoincareMap.from_ode(xppfile)
+model = PoincareMap(xppfile)
 
 
 FIGWIDTH = 3.85
@@ -35,123 +33,6 @@ FIG2by1 = (FIGWIDTH*1.4, (FIGWIDTH*1.4)/2)
 #%% Plotting
 
 # TODO: Add patches
-def free_quiet() -> Figure:
-    """Illustration of free and quiet phases  with voltage and synpase 
-    variables."""
-    # Compute 3-3 solution.
-    TRANSIENT = 3000
-    TOTAL = 12000
-    G = 0.5
-    N = 2
-    sol = ode.run(xppfile, transient=3000, total=10000, g=G)
-    lc = ode.find_lc(sol, norm=True)
-
-    period = lc.t.iloc[-1]
-    idxs, _ = ode.spikes(lc)
-    # Append last point to first to make it look nice.
-    idxs = np.concatenate((idxs, [-1]))
-
-    fig, axs = plt.subplots(nrows=3, tight_layout=True, sharex=True,
-                            figsize=(FIGWIDTH, FIGWIDTH*1.7))
-
-    # A: Plot voltage trace.
-    ax = axs[0]
-    ax.plot(lc.t, lc.v1)
-    ax.plot(lc.t, lc.v2)
-    ax.set_ylim((-80, 140))
-    ax.set_ylabel(r'$v_{1,2}$')
-
-    # # Add arrows between ds.
-    # OFFSET = 16
-    # v0 = max(lc.v1)
-    # for idx0, idx1 in zip(idxs, idxs[1:]):
-    #     t0 = lc.t.iloc[idx0]
-    #     t1 = lc.t.iloc[idx1]
-    #     midpoint = t0 + (t1-t0)/2.
-    #     p = patches.FancyArrowPatch((t0, v0), (t1, v0),
-    #                                 connectionstyle='arc3, rad=-0.3',
-    #                                 arrowstyle='->', mutation_scale=8)
-    #     ax.add_patch(p)
-
-    #     # Put text on top of patch.
-    #     if idx1 == -1:
[…]

### 2022-03-30 src/poincare_map/poincare_map.py

@@ -28,19 +28,19 @@ class PoincareMap(NamedTuple):
 
     # These are derived.
     gstar: float = 0.0068
-    T: float = 376  # Spiking period.
-    Tact: float = 49
-    Tinact: float = 327
+    T: float = 376  # Spiking period. Or 376?
+    Ta: float = 49
+    Ts: float = 327
 
     @property
     def Lambda(self):
         """Depression speed."""
-        return np.exp(-self.Tact / self.taub)
+        return np.exp(-self.Ta / self.taub)
 
     @property
     def Rho(self):
         """Depression recovery speed."""
-        return np.exp(-self.Tinact / self.taua)
+        return np.exp(-self.Ts / self.taua)
 
     @property
     def dsup(self):
@@ -51,7 +51,7 @@ class PoincareMap(NamedTuple):
     def gsup(self):
         """Minimum value of g for suppressed solution."""
         return (self.gstar / self.Lambda) * (
-            np.exp(self.Tinact / self.tauk) / self.dsup
+            np.exp(self.Ts / self.tauk) / self.dsup
         )
 
     @property
@@ -89,10 +89,21 @@ class PoincareMap(NamedTuple):
         delta_n = (
             (1 / (g * self.Lambda)) * self.gstar * np.exp(delta_t / self.tauk)
         )
-        exponent = (
-            -((self.n - 1) * self.T + self.Tact + 2 * delta_t) / self.taua
-        )
+        exponent = -((self.n - 1) * self.T + self.Ta + 2 * delta_t) / self.taua
         return 1 - (1 - self.Lambda * delta_n) * np.exp(exponent)
+
+    def Q_map_slope_num(self, delta_t: float, g: float) -> float:
+        eps = 0.00001
+        return (self.Q_map(delta_t + eps, g) - self.Q_map(delta_t, g))/eps
+
+    def Q_map_slope(self, delta_t: float, g: float) -> float:
+        A = (self.n - 1) * self.T + self.Ta
+        E1 = np.exp(-2 * delta_t / self.taua)
+        E2 = np.exp(delta_t / self.tauk - 2 * delta_t / self.taua)
+        return np.exp(-A / self.taua) * (
+            (2 / self.taua) * E1
+            + self.gstar / g * (1 / self.tauk - 2 / self.taua) * E2
+        )
 
     def P_map(self, d: float, g: float) -> float:
         """Explicit burstmap."""
@@ -113,7 +124,7 @@ class PoincareMap(NamedTuple):
             return None
         else:
[…]

### 2022-05-03 tex/sections/results.tex
Add small edits

@@
 While a cell is silent its depression variable can recover.
-Once the silent cell becomes active again its synaptic inhibition will be sufficient to terminate the burst of the previously active cell and commence a new cycle.
-% BUG: This is not 100% true, gbar AND the initial conditions uniquely determine the type of n:n pattern.
-As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\bar g$ determines the type of $n:n$ solution.
+Once the silent cell becomes active again its synaptic inhibition will be sufficient to As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\bar g$ determines the type of $n:n$ solution.
 Increasing $\bar g$ produces higher $n:n$ burst solutions with more spikes per burst and a longer cycle period.
@@
 Recall that when a cell is silent its $v$- and $w$-nullclines intersect at a stable fixed point and $\bar g s > g_{bif}$.
-% The following does not necessarily imply that it fires instantly on release.
 A sufficient condition for the silent cell to be released is therefore $\bar g s < g_{bif}$.
@@
 For any stable $n:n$ solution in \cref{fig:bif-diagram} we can compute an associated release conductance numerically by recording the value of $\bar g s$ at the time of the first spike of the silent cell.
-% ''Converges'' is probably the wrong word here...
 Such values of the release conductance are shown in \cref{fig:gstar-diag}A, and the graph suggests that as $n$ increases, the value of the release conductance converges to some constant conductance value $g^{\star} \approx 0.0068\, \si{mS/cm^2}$.
@@
 We can now define the active and silent phases of cell 1 explicitly.
-% TODO: This NEEDS editing. Silent phase term here confusing.
 The active phase of a burst is the interval that lasts from the first spike time up until the beginning of the silent phase of the last spike, that is for time $0<t<(n-1)T + T_{a}$.
@@
 \noindent
-\linelabel{line:mono}
-The monotonicity of $\Pi_{n}$ w.r.t. $\bar g$ is evident from \Cref{eq:non-degen1}, while the monotonicity w.r.t. $d^{\star}$ follows from the monotonicity of both $Q_{n}$ and $F_{n}$.
+The monotonicity of $\Pi_{n}$ w.r.t. $\bar g$ is evident from \cref{eq:Pn-map}, while the monotonicity w.r.t. $d^{\star}$ follows from the monotonicity of both $Q_{n}$ and $F_{n}$.
 In the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
@@
 \end{align}
-% Equations~\eqref{eq:non-degen1} and~\eqref{eq:non-degen2} constitute the non-degeneracy conditions for a codimension-1 fold bifurcation of maps, indicating that in a neighbourhood of $(d^\star_{b}, \bar g_{b})$ map $\Pi_n$ has the topological normal form described by the graph of
-% \begin{equation}
-% 	\label{eq:normal-form}
-% 	x\mapsto \beta+x-x^{2},
-% \end{equation}
-% with a stable and unstable fixed point $x=\pm\sqrt{\beta}$, and slopes $\dv*{x}{\beta}=\mp {(2\sqrt{\beta})}^{-1}$, respectively.
 
@@
 
-% TODO: Need to double-check this paragraph about implicit differentiation. It should still hold after the model change I believe.
 It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\bar g$.
@@
 As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n:n$ bursts exists only on certain parameter intervals of $\bar g$.
-% TODO: Edit this sentence.
 \linelabel{line:ll}
@@
 whose root is the desired right bifurcation border $\bar g_{\mathcal{R}}(n)$.
-% NOTE: @CONOR: After changing the model I'm not sure anymore whether the next equation is clear from my explanation or I need another sentence.
 In case of the left bifurcation border at $\bar g_{\mathcal{L}}(n)$, the release condition is satisfied just before the active cell has produced its $n$th spike, where total synaptic conductance is given by
@@
 
-% TODO: Edit a bit more
 \Cref{fig:final-bif} shows the period $P_{n}(\bar g)$ as predicted by the fixed points of $\Pi_{n}$ (\cref{eq:period}) plotted on their respective intervals $\bar g \in [\bar g_{\mathcal{L}}(n),\bar g_{\mathcal{R}}(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).

### 2022-05-03 tex/sections/results.tex
Add small edits

@@
 	see][]{gardini2012,tramontana2012,avrutin2011}.
-While our maps $\Pi_n$ are fully continuous, the above observation suggests that a different piecewise-linear scalar map that captures the period increment bifurcations of the full system might exist.
+While our maps $\Pi_n$ are fully continuous, the above observation suggests that a different piecewise-linear scalar map that captures such period increment dynamics of the full system might exist.
 We will explore what such a map might look like in the discussion.

### 2022-05-03 tex/supplementary.tex
Add gsup value to supplementary materials

@@
 		$g_{bif}$                      & $0.0038$ \si{mS/cm^2} \\
+		$\bar g_{s}$                   & $0.584$ \si{mS/cm^2}  \\
 		$\lambda:=\exp(-T_{a}/\tau_b)$ & $0.612$               \\

### 2022-05-03 tex/manuscript.tex
Add vertical stripes in bif diagram to show bistability

@@
 \newcommand{\gstar}{g^\star}
-\newcommand{\gbar}{\bar g}
+\newcommand{\bar g}{\bar g}
 \newcommand{\delt}{\Delta t}
@@
   \caption{Voltage traces of both cells of numerically stable solutions for increasing
-    values of the coupling strength $\gbar$ (increasing top to
+    values of the coupling strength $\bar g$ (increasing top to
     bottom).~\label{fig:burst-sols}}
@@
   \includegraphics{bif-diagram}
-  \caption{Numerically computed bifurcation diagram of the cycle period of stable $n:n$ solutions for increasing coupling strength $\gbar$.
-Dashed lines show the interval between the $5-5$ and the suppressed solution, where higher period $n:n$ solutions occur on increasingly smaller intervals of $\gbar$.\label{fig:bif-diagram}}
+  \caption{Numerically computed bifurcation diagram of the cycle period of stable $n:n$ solutions for increasing coupling strength $\bar g$.
+Regions of bistability are indicated by light blue vertical stripes.
+Dashed lines show the interval between the $5:5$ and the suppressed solution, where higher period $n:n$ solutions occur on increasingly smaller intervals of $\bar g$.\label{fig:bif-diagram}}
 \end{figure}
@@
     Grey patches depict $\delt$ intervals.
-    $\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\gbar s_1$) as it crosses the release conductance $g^{\star}$.
+    $\bm{\mathrm{(B)}}$ Total synaptic conductance of cell 1 ($\bar g s_1$) as it crosses the release conductance $g^{\star}$.
     $\bm{\mathrm{(C)}}$ Solution $d_1(t)$ of depression variable of cell 1, during active (blue) and silent phases (orange).~\label{fig:free-quiet}}
@@
   \includegraphics{delta-t}
-  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\gbar$.
+  \caption{Numerically computed bifurcation diagram of $\delt$ for varying $\bar g$.
     Each continuous branch is associated with a stable $n:n$ burst solution. Increasing
-    $\gbar$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
+    $\bar g$ increases $\Delta t$ until the solutions bifurcate at $\Delta t\approx
     T_{s}$.~\label{fig:delta-t}}
@@
   \caption{Maps $F_n$ $\bm{\mathrm{(A)}}$ and $Q_n$ $\bm{\mathrm{(B)}}$ for
-  $\gbar=0.5$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at
+  $\bar g=0.5$ $\si{mS/cm^{2}}$ and $n=1,2,3,4$. Curves $F_n$ intersect at
   $d^{\star}=d_{s}$ which is indicated by a dashed vertical line. Curves $Q_n$ intersect at $\Delta t = \tau_{\kappa}\ln\Big(\bar g / g^{\star}\Big)$. \label{fig:FQ-maps}}
@@
   \caption{Map $\Pi_{n}:d^{\star}\mapsto d^{\star}$. $\bm{\mathrm{(A)}}$ $\Pi_{n}$ for $n=1,2,3,4$
-  at $\gbar=0.5$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
-  various $\gbar$. The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
+  at $\bar g=0.5$ $\si{mS/cm^{2}}$. $\bm{\mathrm{(B)}}$ $\Pi_{2}$ with $n=2$ for
+  various $\bar g$. The identity function is illustrated by a diagonal line.~\label{fig:Pn-map}}
 \end{figure}
@@
   \includegraphics[width=0.8\textwidth]{final-bif}
-  \caption{Bifurcation diagram of the period of stable $n:n$ solutions computed analytically from fixed points of $\Pi_n$, plotted on the respective intervals of $\gbar\in \big[\gbar_{\mathcal{L}}(n),\gbar_{\mathcal{R}}(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
+  \caption{Bifurcation diagram of the period of stable $n:n$ solutions computed analytically from fixed points of $\Pi_n$, plotted on the respective intervals of $\bar g\in \big[\bar g_{\mathcal{L}}(n),\bar g_{\mathcal{R}}(n)\big]$ (blue), and computed from numerical integrations of the ODEs (orange).~\label{fig:final-bif}}
 \end{figure}

### 2022-05-03 scripts/makefig.py

@@ -91,11 +91,6 @@ ax.text(ml.pars["vtheta"] - 10, 0.48, r"$v_\theta$")
 
 # Add inhibited vnullcline
 
-# ax.text(-45, 0.39, "Jump Down")
-# ax.text(-4.5, 0.003, "Jump Up")
-# ax.text(-65, 0.08, "Silent\nState")
-# ax.text(35, 0.2, "Active\nState")
-
 ax.text(-53, 0.53, r"$v_\infty$")
 ax.text(8, 0.53, r"$w_\infty$")
 
@@ -193,14 +188,20 @@ fig.savefig(paths.figures / "burst-sols.pdf")
 
 
 #%% Numeric bifurcation diagram
-ns = np.arange(1, 10)
+ns = df['n'].unique()
 
 fig, ax = plt.subplots(tight_layout=True)
 # Plot numeric diagram
-for n in df["n"].unique():
+for n in ns:
     dfn = df[df["n"] == n]
     ax.plot(dfn["g"], dfn["period"], c="C0", lw=2.5)
 
+
+# Highlight bi-stability regions.
+for n1, n2 in zip(ns, ns[1:]):
+    n1_right = df.loc[df['n']==n1]['g'].max()
+    n2_left = df.loc[df['n']==n2]['g'].min()
+    ax.axvspan(n1_right, n2_left, ymin=0, ymax=1, color="C0", alpha=0.2)
 
 # Add dotted lines with higher-order solutions.
 ax.axvline(df["g"].max(), c="grey", ls="--")

### 2022-05-03 scripts/makefig_bak.py

@@ -1,1301 +1,0 @@
-# %% Initialise
-import itertools
-import multiprocessing
-import os
-import pickle
-import string
-import warnings
-from os import path
-
-import matplotlib
-matplotlib.use('pgf')
-
-import pandas as pd
-import pyxpp.pyxpp as xpp
-import scipy as sp
-from matplotlib import patches
-from matplotlib import pyplot as plt
-from matplotlib.gridspec import GridSpec
-from matplotlib.lines import Line2D
-from pandas import DataFrame
-from scipy.misc import derivative
-from pathlib import Path
-
-from poincare_map import helpers
-from poincare_map import model
-from poincare_map import ode
-from poincare_map import paths
-
-import numpy as np
-
-plt.ioff()
-
-warnings.filterwarnings("ignore", category=DeprecationWarning)
-# Ignore devide by zero
-np.seterr(divide='ignore')
-np.seterr(all='ignore')
-
-
-xppfile = str(paths.odes / "mlml.ode")
-CENTER_TITLE_SIZE = 11
-FIGWIDTH = 3.85
-FIGSIZE = (FIGWIDTH, FIGWIDTH)
-FIG2by1 = (FIGWIDTH*1.4, (FIGWIDTH*1.4)/2)
-
-EQSIZE = 15                     # Font size of equaitons.
-
-rcp = matplotlib.rcParamsDefault
-rcp['figure.max_open_warning'] = 0
-rcp['axes.unicode_minus'] = False
-rcp['text.usetex'] = True
-rcp['pgf.rcfonts'] = False
-rcp['pgf.texsystem'] = 'pdflatex'
-rcp['xtick.labelsize'] = 'small'
-rcp['ytick.labelsize'] = 'small'
-rcp['axes.labelsize'] = 'x-large'
-rcp['axes.titlesize'] = 'xx-large'
-rcp['figure.titlesize'] = 'large'
-rcp['font.size'] = 9
-# Use latex preamble.
-rcp['pgf.preamble'] = r'\usepackage{amsmath} \usepackage{siunitx}'
-
-matplotlib.rcParams.update(rcp)
-
-p = xpp.read_pars(xppfile)
-
[…]

### 2022-06-08 tex/manuscript.tex
Add README

@@
 \newcommand{\gstar}{g^\star}
-\newcommand{\bar g}{\bar g}
+\newcommand{\gbar}{\bar g}
 \newcommand{\delt}{\Delta t}
@@
 This work was supported by the Wellcome Trust Doctoral Training Programme in Neural
-Dynamics, Grant no. 099699/Z/12/Z.
+Dynamics, Grant no. 102374/Z/13/Z.
 
@@
 	\includegraphics{burst-sols}
-  \caption{Voltage traces of both cells of numerically stable solutions for increasing
-    values of the coupling strength $\bar g$ (increasing top to
-    bottom).~\label{fig:burst-sols}}
+	\caption{Voltage traces of cell 1 (blue) and cell 2 (orange) of numerically stable solutions.
+$\bm{\mathrm{(A-D)}}$ $1:1$, $2:2$, $3:3$, and $4:4$ anti-phase solutions for increasing values of $\bar g$.
+$\bm{\mathrm{(E)}}$ Suppressed solution.~\label{fig:burst-sols}}
 \end{figure}

### 2022-06-08 tex/sections/introduction.tex
Add README

@@
   In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
-  To better understand burst generation in these central patter generators, we study a minimal network of two neurons coupled through depressing synapses.
+  To better understand burst generation in these central pattern generators, we study a minimal network of two neurons coupled through depressing synapses.
   Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n:n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.

### 2022-06-08 tex/sections/results.tex
Add README

@@
 While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
-\linelabel{line:C1}
 Therefore, at any given moment one cell is spiking while the other is suppressed and does not spike.
@@
 Additionally, we will distinguish between two phases of a $n:n$ solution:
-\linelabel{line:C2}
 We will refer to the time interval when a cell is firing as the ``active phase'', and we will call the remaining duration of a cycle, when a cell is not firing, the ``silent  phase''.
 
-With each action potential of the active cell, short-term depression leads to a decrease of $d$, and consequently of $s$ (\cref{fig:burst-sols}B).
-\linelabel{line:D}
+With each action potential of the active cell, short-term depression leads to a decrease of $d$, and consequently of $s$.
 If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\bar g s$ will eventually become sufficiently small to allow for the silent cell to be released \citep{wang1992,skinner1994} and start firing, thus inhibiting the previously active cell.
 While a cell is silent its depression variable can recover.
-Once the silent cell becomes active again its synaptic inhibition will be sufficient to As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\bar g$ determines the type of $n:n$ solution.
+Once the silent cell becomes active again its synaptic inhibition will be sufficient to terminate the burst of the previously active cell and commence a new cycle.
+As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\bar g$ determines the type of $n:n$ solution.
 Increasing $\bar g$ produces higher $n:n$ burst solutions with more spikes per burst and a longer cycle period.

### 2022-06-08 tex/supplementary.tex
Add README

@@
 \section{Computing bifurcation diagram numerically}\label{appendix2}
-The bifurcation diagram of stable $n-n$ solutions of the two-cell network in \cref{fig:bif-diagram} is obtained numerically as follows:
-We initialise the coupling strength at parameter values associated with one type of $n-n$ solution, that is we choose the values $\bar g = 0.35, 0.4, 0.5, 0.52, 0.56$ for the $1-1$, $2-2$, $3-3$, $4-4$, and $5-5$ solutions respectively.
+The bifurcation diagram of stable $n:n$ solutions of the two-cell network in \cref{fig:bif-diagram} is obtained numerically as follows:
+We initialise the coupling strength at parameter values associated with one type of $n:n$ solution, that is we choose the values $\bar g = 0.35, 0.4, 0.5, 0.52, 0.56$ for the $1:1$, $2:2$, $3:3$, $4:4$, and $5:5$ solutions respectively.
 For each $\bar g$ the system is then numerically integrated sufficiently long for any transients to fully subside.
@@
 That is, we choose some value $d_{k}$ at a spike time $t_{k}$, and by iterating from spike to spike find some subsequent value $d_{k+1}$ at spike time such that $|d_{k+1}-d_{k}|<\epsilon$.
-If a periodic solution of type $n-n$ is found in such way, $\bar g$ is step-wise increased/decreased, and the above algorithm is repeated.
+If a periodic solution of type $n:n$ is found in such way, $\bar g$ is step-wise increased/decreased, and the above algorithm is repeated.
 Otherwise, the set of all previously found solutions and the corresponding values $\bar g$ are returned.
@@
 	\includegraphics[width=0.8\textwidth]{tauk-vs-ISI}
-	\caption{Voltage traces of both cells of numerically stable solutions for increasing
-		values of the coupling strength $\gbar$ (increasing top to
-		bottom).~\label{fig:tauk-vs-ISI}}
+	\caption{Numerically computed values of the first ($ISI_{1}$), second ($ISI_{2}$), and third ($ISI_{3}$) inter-spike-intervals as a function of $\tau_{\kappa} \in \interval[open left]{0}{800}$.~\label{fig:tauk-vs-ISI}}
 \end{figure}
-
-% TODO
-% **Note of caution**: Our ICs might be inaccurate for very large $\tau_\kappa$ , since then $w(0) \approx w_\infty(g^\star)$ will be likely violated.
-
-% \section{Irregular solutions}
-% Even
 

### 2022-06-08 scripts/makefig.py

@@ -803,7 +803,7 @@ ax.plot(tauks, [ISIs[0] for ISIs in ISI_list], label=r"$ISI_1$")
 ax.plot(tauks, [ISIs[1] for ISIs in ISI_list], label=r"$ISI_2$")
 ax.plot(tauks, [ISIs[2] for ISIs in ISI_list], label=r"$ISI_3$")
 ax.plot(tauks, np.ones(len(tauks)) * pmap.T, "k--")
-ax.set(xlabel=r"$\tau_k$", ylabel=r"$ISI$", xlim=(0, 800), ylim=(350, 525))
+ax.set(xlabel=r"$\tau_k$ $(\si{ms})$", ylabel=r"$ISI$ $(\si{ms})$", xlim=(0, 800), ylim=(350, 525))
 ax.legend()
 
 # Add T
@@ -815,7 +815,7 @@ fig.savefig(paths.figures / "tauk-vs-ISI.pdf")
 #%% Response stuff
 # ================================================================================================
 
-#%% Irregular solution (for supplemenatary)
+# Irregular solution
 g = 0.581
 
 sol = mlml.run(g=g, transient=480000, total=500000)
@@ -828,7 +828,7 @@ ax.set(xlabel="time " + r"$(\si{ms})$", ylabel=r"$v_i$ " + r"$(\si{mV})$")
 ax.legend()
 fig.savefig(paths.figures / "irregular.pdf")
 
-#%% Comparison of Boses model to our update model (nullclines)
+# Comparison of Boses model to our update model (nullclines)
 
 # Plot.
 fig, axs = plt.subplots(ncols=2, tight_layout=True, figsize=FIG2by1)

### 2022-06-10 src/poincare_map/model_backup.py
Add published pdf

@@ -1,169 +1,0 @@
-
-    # ----------------------------------------------------------
-    # TODO: Sort this out, what's still needed and what can be discarded
-
-    # def Pn_map_diff(self, d: float, n: int) -> float:
-    #     """Derivative of Pn for root finder."""
-
-    #     _delta = self.delta(self, d, n)
-    #     gr = self.g / self.gstar
-    #     tau = 2 * self.taus / self.taud
-    #     b = (self.taud - 2 * self.taus) / (self.taud * self.taus)
-    #     p1 = (
-    #         self.taus
-    #         * self.alpha(self, n)
-    #         * pow(self.Rho, n - 1)
-    #         * pow(gr, -tau)
-    #     )
-    #     p2 = 2 / self.taud * pow(_delta, -(tau + 1)) + b * self.Lambda * pow(
-    #         _delta, -tau
-    #     )
-    #     return p1 * p2
-
-    # def Pn_map_fps(self, n: int) -> Tuple[Optional[float], Optional[float]]:
-    #     """Compute fixed points of Pn-map using Newton."""
-
-    #     P = lambda d: self.P_map(d, n) - d
-    #     DP = lambda d: self.Pn_map_diff(d, n) - 1
-
-    #     # Unstable fixed point
-    #     EPSILON = 0.0001
-    #     x0 = self.d_a(n) + EPSILON
-    #     try:
-    #         fp0 = optimize.newton(P, x0, fprime=DP)
-    #         # fp0 = sp.optimize.brentq(P, x0, 1)
-    #     except:
-    #         fp0 = None
-
-    #     # Stable fixed point
-    #     x1 = 1
-    #     try:
-    #         fp1 = optimize.newton(P, x1, fprime=DP)
-    #     except:
-    #         fp1 = None
-
-    #     # There are either two or no fixed points.
-    #     if fp0 is None and fp1 is None:
-    #         return (None, None)
-    #     else:
-    #         return (fp0, fp1)
-
-    # def Phi(self, d, n):
-    #     """Fixed point equation."""
-    #     return self.P_map(d, n) - d
-
-    # def phi(self, n, x0=1.0):
-    #     """Numerically find stable fixed point."""
-    #     try:
-    #         fp = optimize.newton(partial(self.Phi, n=n), x0)
-    #         if np.isreal(fp):
-    #             return np.real(fp)
-    #         else:
-    #             return np.nan
-    #     except:
-    #         return np.nan
-
[…]

### 2022-06-10 scripts/check_slopes.py
Refactoring and cleaning up

@@ -1,11 +1,0 @@
-"""Check if dQ/dd is positive."""
-
-ds = np.linspace(0.0001, 300, 100)
-
-fig, ax = plt.subplots()
-# ax.plot(ds, [PoincareMap(3).Q_map_slope(d, 0.5) for d in ds])
-# ax.plot(ds, [PoincareMap(3).Q_map_slope_num(d, 0.5) for d in ds])
-
-ax.plot(ds, [PoincareMap(4).Q_map_slope(d, 0.5) for d in ds])
-ax.plot(ds, [PoincareMap(4).Q_map_slope_num(d, 0.5) for d in ds])
-fig.savefig('tmp/tmp.pdf')

### 2022-06-10 scripts/find_gstar.py

@@ -1,200 +1,0 @@
-"""Find gstar numerically."""
-
-
-from poincare_map import ode
-from poincare_map import helpers
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib
-from matplotlib.figure import Figure
-import intersect
-import tqdm
-from typing import Tuple
-import pandas as pd
-from poincare_map.model import PoincareMap
-
-plt.ioff()
-
-rcp = matplotlib.rcParamsDefault
-rcp["axes.spines.right"] = False
-rcp["axes.spines.top"] = False
-matplotlib.rcParams.update(rcp)
-
-VTHETA = 0
-GSTAR = 0.0068
-T = 376
-
-xppfile = "odes/ml.ode"
-
-
-def roots(x, y) -> np.ndarray:
-    return intersect.intersection(x, y, x, np.zeros(len(x)))[0]
-
-
-def calc(
-    xppfile: str = "odes/ml.ode",
-    g: float = 0.5,
-    tauk: float = 100,
-    total: float = 400,  # big enough even for large g?
-    **kwargs,
-) -> pd.DataFrame:
-    """Compute solution given initial conditions."""
-    vnull, wnull = ode.nullclines(xppfile, gtot=GSTAR)
-    v_fp, w_fp = intersect.intersection(
-        vnull[:, 0], vnull[:, 1], wnull[:, 0], wnull[:, 1]
-    )
-    v0 = v_fp[0]
-    w0 = w_fp[0]
-    s0 = 1
-    ics = np.array([v0, w0, s0])
-    sol = ode.run(xppfile, ics=ics, g=g, tauk=tauk, total=total, **kwargs)
-    return sol
-
-
-def calc_sol(
-    xppfile: str = "odes/ml.ode",
-    g0: float = 0.1,
-    total: float = 800,  # big enough even for large g?
-    **kwargs,
-) -> pd.DataFrame:
-    """Compute solution given initial conditions."""
-    vnull, wnull = ode.nullclines(xppfile, gtot=g0)
-    v_fp, w_fp = intersect.intersection(
-        vnull[:, 0], vnull[:, 1], wnull[:, 0], wnull[:, 1]
-    )
-    v0 = v_fp[0]
-    w0 = w_fp[0]
-    ics = np.array([v0, w0, g0])
[…]

### 2022-06-10 scripts/main.py

@@ -1,29 +1,0 @@
-# %% Init stuff
-import matplotlib.pyplot as plt
-import numpy as np
-from poincare_map.poincare_map import PoincareMap
-from poincare_map.bif import compute_analytic
-
-xppfile = "odes/mlml.ode"
-
-#%% Plot G
-
-fig, ax = plt.subplots()
-for n in [1, 2, 3, 4, 5, 6]:
-    poincare = PoincareMap(n=n)
-    branch = poincare.stable_branch()
-    if branch is not None:
-        ax.plot(branch['g'], branch['period'])
-
-fig.savefig('tmp/ana-bif.pdf')
-
-#%% phi stable
-
-gs = np.linspace(0, 1, 100)
-fig, ax = plt.subplots()
-ax.plot(gs, [PoincareMap(n=1).phi_stable(g) for g in gs])
-fig.savefig('tmp/phi_stable.pdf')
-
-
-#%% Plot diagram
-PoincareMap(n=2).phi_stable(0.01)

### 2022-06-10 scripts/refactor.py

@@ -1,114 +1,0 @@
-## Copy of recursive maps and functions (in case I need that)
-
-
-def L2delt(self, L: float) -> float:
-    """Get delta-t from burst length L."""
-    if L < 0:
-        return L
-    else:
-        return L % self.T
-
-
-
-def L2n(self, L: float) -> int:
-    """Get number of spikes in burst of length L."""
-    if L < 0:
-        return 0
-    else:
-        return int(L // self.T + 1)
-
-
-def d2n(self, d: float) -> int:
-    """Just a convenience function to find n from d."""
-    L = self.F_map(d)
-    return self.L2n(L)
-
-def F_map(self: self, d: float) -> float:
-    """Recursive free phase map F."""
-    if s_sol(self, d) <= self.gstar:
-        return self.taus * np.log(self.g * d / self.gstar)
-    else:
-        dnew = d_sol(self, d)
-        return self.T + F_map(self, dnew)
-
-
-def Q_map(self: self, L: float) -> float:
-    """Recursive quiet phase map Q."""
-    delt = L2delt(self, L)
-    n = L2n(self, L)
-    return Qn_map(self, delt, n)
-
-
-def P_map(self: self, d: float) -> float:
-    """Recursive burst map."""
-    return Q_map(self, F_map(self, d))
-
-
-def P_map_fps(
-    self: self, nsteps: int = 10000, con_thresh: float = 0.005
-) -> [float, float]:
-    """
-    Compute fixed points of recursive P-map using brute force.
-
-    Since the input is 1D and the function only partially
-    continuous brute force is appropriate.
-
-    """
-
-    # Define grid.
-    xs = np.linspace(0, 1, nsteps)
-    ys = np.array([P_map(self, x) - x for x in xs])
-
-    # Find continuous intervals.
-    contints = np.hstack(([0], abs(np.diff(ys)) < con_thresh))
-    # Find zero crossing by sign change.
-    zerocros = np.hstack(([0], np.diff((ys > 0) * 1)))
-
-    # Roots
-    y0idxs = np.where(np.multiply(contints, zerocros))
-    roots = xs[y0idxs]
-
-    return roots
-
-
-def P_map_period(self: self, dstar: float) -> float:
-    """Estimate burst period from a fixed point of recursive P-map."""
-    L = F_map(self, dstar)
-    n = L2n(self, L)
-    delt = L2delt(self, L)
[…]

### 2022-06-10 scripts/refactor_model.py

@@ -1,473 +1,0 @@
-"""Script to test refactoring of maps in model.py"""
-import matplotlib.pyplot as plt
-import numpy as np
-from poincare_map.model import PoincareMap
-import pickle
-
-plt.ioff()
-
-xppfile = "odes/mlml.ode"
-model = PoincareMap.from_ode("odes/mlml.ode")
-
-#%%
-
-ds = np.linspace(-1, 1, 100)
-
-n = 3
-fig, ax = plt.subplots()
-Ps = [model.P_map(d, n) for d in ds]
-ax.plot(ds, Ps, label="comp")
-Ps = [model.P_map_direct(d, n) for d in ds]
-ax.plot(ds, Ps, ".", label="direct")
-ax.legend()
-fig.savefig("tmp/pimap.pdf")
-
-
-#%% Vary g
-gs = [0.1, 0.3, 0.6]
-
-fig, ax = plt.subplots()
-for g in gs:
-    Ps = [model._replace(g=g).P_map(d, n) for d in ds]
-    ax.plot(ds, Ps, label=f"g={str(g)}")
-ax.legend()
-fig.savefig("tmp/pimap_g.pdf")
-
-#%% inverse
-
-g = 0.55
-n = 4
-f = lambda d: model._replace(g=g).G(d, n)
-dmin, gmin = model.critical_fp(n)
-kk = inversefunc(f, g, domain=[dmin, 1])
-
-#%% Left border
-from scipy import optimize
-
-f = lambda g: model.L_fun(g, n=3)
-fp0 = optimize.newton(f, x0=1.0)
-
-#%% Test period
-
-# Load numericly computed diagram
-df = pickle.load(open("data/bif-diagram.pkl", "rb"))
-# ns = df.n.unique()
-ns = [2, 3, 4, 5]
-
-fig, ax = plt.subplots()
-for idx, n in enumerate(ns):
-    dfn = df[(df.n == n) & (df.g > 0.1)]
-    ax.plot(dfn.g, dfn.period, c=f"C{idx}")
-    # Compute analytic period
-    # Ps = [model.Period(g, n) for g in dfn.g]
-    # ax.plot(dfn.g, Ps, c='C1', linewidth=1)
-
-gg = 0.006788
-# Plot left/right borders
-for idx, n in enumerate(ns):
-    # NOTE: We're cheating here since T=376.3
-    left_border = model._replace(gstar=gg).left_branch_border(n)
[…]

### 2022-06-26 scripts/makefig.py
Fix colors in last figure

@@ -644,15 +644,16 @@ fig.savefig(paths.figures / "folds.pdf")
 ns = np.arange(1, 10)
 
 fig, ax = plt.subplots(tight_layout=True)
-# Plot numeric diagram
-for n in df["n"].unique():
-    dfn = df[df["n"] == n]
-    ax.plot(dfn["g"], dfn["period"], c="C0", lw=2.5)
 
 # Plot analytic diagram on top
 for n in df_ana["n"].unique():
     dfn_ana = df_ana[df_ana["n"] == n]
-    ax.plot(dfn_ana["g"], dfn_ana["period"], c="C1", lw=1.3)
+    ax.plot(dfn_ana["g"], dfn_ana["period"], c="C0", lw=2.5)
+
+# Plot numeric diagram
+for n in df["n"].unique():
+    dfn = df[df["n"] == n]
+    ax.plot(dfn["g"], dfn["period"], c="C1", lw=1.3)
 
 ax.set(
     xlim=(0.3, pmap.gsup),

### 2022-07-17 tex/sections/introduction.tex
fix typos

@@
 Finally, we use our map to derive algebraic conditions that allow us to predict parameter values of the maximum conductance at which $n:n$ solutions bifurcate to $(n+1):(n+1)$ solutions, and vice versa.
-Because our map is fully explicit, it lays the framework for studying the effects of other model parameter on network dynamics without the need to run expensive numerical integrations of the ODEs.
+Because our map is fully explicit, it lays the framework for studying the effects of other model parameters on network dynamics without the need to run expensive numerical integrations of the ODEs.
 

### 2022-07-17 scripts/makefig.py

@@ -233,7 +233,6 @@ fig.savefig(paths.figures / "bif-diagram.pdf")
 
 
 #%% Free-quiet
-# TODO: Replace gbar*s with ggot?
 
 n = 3
 mlml = ode.MLML(paths.mlml_file)
@@ -571,13 +570,11 @@ fig.savefig(paths.figures / "Pn-map.pdf")
 #%% Folds
 
 ns = [1, 2, 3, 4, 5]
-# gs = np.linspace(0, 0.6, 100)
 gs = np.geomspace(0.000001, 0.6, 100)
 ds = np.linspace(-1.5, 1, 5000)
 gmax = gs[-1]
 
 fig, axs = plt.subplots(figsize=FIG2by1, tight_layout=True, ncols=2)
-axs[0] = axs[0]
 
 # A: Compute analytic bifurcation curves of d.
 curves = []

### 2022-07-17 tex/sections/discussion.tex
Add small edits
remove line labels

@@
 In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
-\linelabel{line:principle}
 Modelling can shed light on the underlying mathematical principles that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.
@@
 We were able to replicate this finding by numerically finding the respective left and right borders of stable $n:n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
-\linelabel{line:disc-pincA}
 We have also noted the resemblance of our bifurcation diagram to one where such $n:n$ branches are created via the bifurcation scenario of type period-increment with co-existent attractors, first described for scalar linear maps with a discontinuity \citep{avrutin2012,avrutin2011}.
@@
 It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
-\linelabel{line:disc-pincB}
 In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.
@@
 % BIOLOGICAL IMPORTANCE OF DEPRESSION
-% TODO: Perhaps mention learning after all?
 We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.

### 2022-07-17 tex/sections/introduction.tex
remove line labels

@@
   Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
-  \linelabel{line:abstract}
   We derive conditions that predict the bifurcations between $n:n$ and $(n+1):(n+1)$ solutions, producing a full bifurcation diagram of the burst cycle period.
@@
 % Brown
-\linelabel{line:A}
 ~\citet{brown1911} pioneered the idea that synaptic depression acts as a burst termination
@@
 predicted by knowing the strengths of the synaptic conductances of the two synapses.
-\linelabel{line:B}
 Thus, the scalar conditions derived in \citet{bose2011} provide a method to numerically

### 2022-07-17 tex/sections/results.tex
Fix colors in last figure
fix typos
remove line labels

@@
 % Assumption 1: active phase
-\linelabel{line:E1}
 Our first assumption about the model states that the active cell fires at its uncoupled period $T$, that is, during the active phase of a burst we have $ISI=T$.
@@
 Finally, assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the active phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
-\linelabel{line:E2}
 
 % Assumption 2: Release
-\linelabel{line:release1}
 Our second assumption states that the silent cell is released and spikes as soon as the total inhibitory conductance $\bar g s$ acting on it drops below some threshold value.
@@
 And to simplify the terminology, from now on we will refer to \cref{eq:release} simply as the ``release condition''.
-\linelabel{line:release2}
 
@@
 Instead, the solution of the synaptic variable $s$ of the active cell is sufficient to predict when $\bar g s =g^{\star}$ is satisfied.
-\linelabel{line:F}
 Finally, the value of $s$ at each spike time is determined by the evolution of the depression variable $d$ of the active cell.
@@
 \noindent
-\linelabel{line:abc}
 We can find $\delta_{n}(d^{\star})$, i.e. the value of $d$ at the $n$th spike time, by rearranging the release condition in \cref{eq:release2}:
@@
 where we substituted $\tau = 2\tau_{k}/\tau_{a}$.
-\linelabel{line:remind}
 Recall that $\delta_{n}(d^{\star})$ and $g^{\star}$ are obtained from \cref{eq:delta-map} and \cref{eq:gstar}, respectively.
@@
 	\Pi_n(d^\star_b, \bar g_b)               & =d^\star_b, \\
-	\frac{d}{d^\star}\Pi_n(d^\star_b, \bar g_b) & =1.
+	\dv{}{d^\star}\Pi_n(d^\star_b, \bar g_b) & =1.
 \end{align}
@@
 \begin{align}
-	\dv{G_n}{d^\star_f} & < 0, \text{ for } d^\star_f>d^\star_b(n) \text{ stable},   \\[0.5ex]
-	\dv{G_n}{d^\star_f} & > 0, \text{ for } d^\star_f<d^\star_b(n) \text{ unstable},
+	\dv{G_n}{d^\star_f} & > 0, \text{ for } d^\star_f>d^\star_b(n) \text{ stable},   \\[0.5ex]
+	\dv{G_n}{d^\star_f} & < 0, \text{ for } d^\star_f<d^\star_b(n) \text{ unstable},
 \end{align}
@@
 As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n:n$ bursts exists only on certain parameter intervals of $\bar g$.
-\linelabel{line:ll}
 The multi-stability of fixed points of maps $\Pi_{n}$ in \cref{fig:folds}B does therefore not imply a similar multi-stability of the flow system.
@@
 	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{R}}(n)\label{eq:easy1},                                                                 \\
-	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{R}}(n+1)\text{ and } \bar g_{\mathcal{R}}(n)<\bar g_{\mathcal{L}}(n+1)\label{eq:easy2}, \\
-	\bar g_{\mathcal{R}}(n+1)                             & < \bar g_{\mathcal{R}}(n)\label{eq:coexistence},                                                           \\
-	\bar g_{\mathcal{L}}(n+1) - \bar g_{\mathcal{R}}(n+1) & < \bar g_{\mathcal{R}}(n) - \bar g_{\mathcal{R}}(n)\label{eq:robustness}.
+	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{L}}(n+1)\text{ and } \bar g_{\mathcal{R}}(n)<\bar g_{\mathcal{R}}(n+1)\label{eq:easy2}, \\
+	\bar g_{\mathcal{L}}(n+1)                             & < \bar g_{\mathcal{R}}(n)\label{eq:coexistence},                                                           \\
+	\bar g_{\mathcal{R}}(n+1) - \bar g_{\mathcal{L}}(n+1) & < \bar g_{\mathcal{R}}(n) - \bar g_{\mathcal{L}}(n)\label{eq:robustness}.
 \end{align}
@@
 \Cref{eq:robustness} implies that the parameter interval on $\bar g$ of $n:n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
-\linelabel{line:branchA}
 All of the above relations are reminiscent of the bifurcation scenario of type period increment with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
@@
 
-\linelabel{line:branchB}
 Let us now find algebraic equations that will allow us to calculate the critical parameters $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ associated with the left and right $n:n$ branch borders.
-\linelabel{line:bbb}
 Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\bar g$ (\cref{eq:dPdg}).
@@
 \Cref{fig:final-bif} shows the period $P_{n}(\bar g)$ as predicted by the fixed points of $\Pi_{n}$ (\cref{eq:period}) plotted on their respective intervals $\bar g \in [\bar g_{\mathcal{L}}(n),\bar g_{\mathcal{R}}(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
-Here $g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ were computed from \cref{eq:L,eq:R}, respectively.
+Here $g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ were computed from eqs. \ref{eq:L} and \ref{eq:R}, respectively.
 Note that the width of $n:n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.

### 2022-09-17 tex/sections/results.tex
Add Zenodo link etc

@@
 We start the construction of $\Pi_n$ by first considering the active phase and building the map $F_n$.
-At each spike time $t_{k}$ where $d(t_k) = d_k$, variable $d$ decays first for the duration of $T_{a}$, as described by the solution to eq.
-(\ref{eq:dot-d-down}).
-% cref doesn't work with cases package
+At each spike time $t_{k}$ where $d(t_k) = d_k$, variable $d$ decays first for the duration of $T_{a}$, as described by the solution to eq. (\ref{eq:dot-d}).  % cref doesn't work with cases package
 At $t = t_k + T_{a}$ we have
@@
 Using the release condition in \cref{eq:release} allows us to derive the value of the minimum coupling strength that will produce the full suppressed solution, denoted as $\bar g_{s}$.
-Solving \cref{eq:dot-s-down} for $s(t)$ with $t=T_{s}$ and setting the initial value $s(0)=d_s\lambda$ then gives us the aforementioned approximation of the release conductance $g^{\star}$:
+Solving \cref{eq:dot-s} for $s(t)$ with $t=T_{s}$ and setting the initial value $s(0)=d_s\lambda$ then gives us the aforementioned approximation of the release conductance $g^{\star}$:
 \begin{equation}
@@
 Finally $s$ decays exponentially for $\Delta t < T_{s}$.
-Solving \cref{eq:dot-s-down} with initial condition $s(0)=\dn(d^\star)\lambda$ yields:
+Solving \cref{eq:dot-s} with initial condition $s(0)=\dn(d^\star)\lambda$ yields:
 \begin{equation}
@@
 As we have identified earlier, the recovery of $d$ in the silent phase of a $n:n$ solution starts at time $t_{n} + T_{a}$ and lasts for the duration of $(n-1)T + T_{a} + 2\Delta t$.
-Substituting that duration into the solution of $d$ (\cref{eq:dot-d-up}) with the initial condition $d(0)=\dn(d^\star) \lambda$ yields the map $Q_{n}$:
+Substituting that duration into the solution of $d$ (\cref{eq:dot-d}) with the initial condition $d(0)=\dn(d^\star) \lambda$ yields the map $Q_{n}$:
 \begin{equation}

### 2024-09-18 scripts/compute.py
update env

@@ -71,10 +71,10 @@ if __name__ == "__main__":
         numeric_diagram = compute_numeric_bif_diagram()
         numeric_diagram.to_pickle(paths.numeric_bif_diagram)
 
-    # if (not paths.analytic_bif_diagram.exists()) or args.recompute:
-    #     print("Computing analytic bifurcation diagram.")
-    #     analytic_diagram = compute_analytic_bif_diagram()
-    #     analytic_diagram.to_pickle(paths.analytic_bif_diagram)
+    if (not paths.analytic_bif_diagram.exists()) or args.recompute:
+        print("Computing analytic bifurcation diagram.")
+        analytic_diagram = compute_analytic_bif_diagram()
+        analytic_diagram.to_pickle(paths.analytic_bif_diagram)
 
     print("Done!")
     print(f"Computation took {time.time() - t0} seconds.")

### 2024-09-18 scripts/makefig.py

@@ -1,3 +1,4 @@
+#%%
 import os
 import tqdm
 from functools import partial
@@ -742,25 +743,25 @@ for idx, ax in enumerate(axs):
 
 fig.savefig(paths.figures / "gstar-diag.pdf")
 
-#%% ISI stats
-def calc_ISI(sol):
-    """Return list of ISIs."""
-    isis1 = np.diff(helpers.spike_times(sol["v1"]).values)
-    isis2 = np.diff(helpers.spike_times(sol["v2"]).values)
-    return list(np.concatenate([isis1, isis2]))
+# #%% ISI stats
+# def calc_ISI(sol):
+#     """Return list of ISIs."""
+#     isis1 = np.diff(helpers.spike_times(sol["v1"]).values)
+#     isis2 = np.diff(helpers.spike_times(sol["v2"]).values)
+#     return list(np.concatenate([isis1, isis2]))
 
 
-all_isis = list(np.concatenate(df["lc"].apply(calc_ISI).values))
-mean = np.mean(all_isis)
-std = np.std(all_isis)
-interval = [min(all_isis), max(all_isis)]
-print(f"mean: {mean}")
-print(f"std: {std}")
-print(f"interval: [{interval[0]}, {interval[1]}]")
+# all_isis = list(np.concatenate(df["lc"].apply(calc_ISI).values))
+# mean = np.mean(all_isis)
+# std = np.std(all_isis)
+# interval = [min(all_isis), max(all_isis)]
+# print(f"mean: {mean}")
+# print(f"std: {std}")
+# print(f"interval: [{interval[0]}, {interval[1]}]")
 
-fig, ax = plt.subplots()
-ax.hist(all_isis, bins="auto")
-fig.savefig("tmp/ISI-hist.pdf")
+# fig, ax = plt.subplots()
+# ax.hist(all_isis, bins="auto")
+# fig.savefig("tmp/ISI-hist.pdf")
 
 
 #%% Exploring tauk

### 2024-09-18 tex/manuscript.tex
Add Zenodo link etc
Refactor tex and update figs

@@
 \usepackage{url,hyperref,microtype,subcaption}
-% \usepackage[onehalfspacing]{setspace}
 \usepackage{cleveref}
-% \usepackage[font={bold,it}]{caption}
 
@@
 
-\title[Scalar Poincaré map for bursting]{A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression.}
+\title[Scalar Poincaré map for bursting]{A scalar Poincaré map for anti-phase bursting in coupled inhibitory neurons with synaptic depression}
 
@@
 
-\input{sections/introduction}
-\input{sections/methods}
-\input{sections/results}
-\input{sections/discussion}
+\begin{abstract}
+  \section{}
+  Short-term synaptic plasticity is found in many areas of the central nervous system.
+  In the inhibitory half-centre central pattern generators involved in locomotion, synaptic depression is believed to act as a burst termination mechanism, allowing networks to generate anti-phase bursting patterns of varying periods.
+  To better understand burst generation in these central pattern generators, we study a minimal network of two neurons coupled through depressing synapses.
+  Depending on the strength of the synaptic conductance between the two neurons, this network can produce symmetric $n:n$ anti-phase bursts, where neurons fire $n$ spikes in alternation, with the period of such solutions increasing with the strength of the synaptic conductance.
+  Relying on the timescale disparity in the model, we reduce the eight-dimensional network equations to a fully-explicit scalar Poincaré burst map.
+  This map tracks the state of synaptic depression from one burst to the next and captures the complex bursting dynamics of the network.
+  Fixed points of this map are associated with stable burst solutions of the full network model, and are created through fold bifurcations of maps.
+  We derive conditions that predict the bifurcations between $n:n$ and $(n+1):(n+1)$ solutions, producing a full bifurcation diagram of the burst cycle period.
+  Predictions of the Poincaré map fit excellently with numerical simulations of the full network model and allow the study of parameter sensitivity for rhythm generation.
+
+  \tiny
+  \keyFont{ \section{Keywords:} Synaptic depression, Poincaré map, Dynamical system, Neuronal bursting, Central pattern generator}
+
+\end{abstract}
+
+\section{Introduction}
+% DEPRESSION
+Short-term synaptic plasticity may have a role in burst activity in central pattern
+generators (CPGs).
+Short-term synaptic depression is commonly found in neuronal networks involved in the generation of rhythmic movements, such as in the pyloric CPG of the spiny lobster~\citep{manor1997, rabbah2007}, or in the lumbosacral cord of the chick embryo~\citep{donovan1998}.
+Synaptic depression modulates the strength of synapses in response to changes to the presynaptic firing frequency.
+At a high neuronal firing frequency, depression weakens the strength of synapses and therefore reduces the magnitude of the postsynaptic response.
+At low firing frequency, it allows sufficient time for the synapse to recover from depression between spikes, leading to a stronger postsynaptic response.
+In reciprocal networks, synaptic depression has been shown to act as a ``switch'', giving rise to a wide range of network dynamics such as synchronous and multi-stable rhythms, as well as fine tuning the frequency of network oscillations~\citep{nadim2000, nadim1999, bose2011}.
+
+% Brown
+~\citet{brown1911} pioneered the idea that synaptic depression acts as a burst termination
+mechanism in CPGs composed of reciprocally inhibitory neurons and involved in rhythm generation of locomotion.
+When one side is firing during a burst the other, antagonistic side, is prevented from
+firing by synaptic inhibition.
+However, the weakening of inhibition as a result of synaptic depression eventually releases the antagonistic side so that it starts firing, terminating the burst on the side that had originally been firing.
+This rhythmogenesis hypothesis has been considered one of a handful of standard mechanisms for generating locomotion rhythms in vertebrates~\citep{reiss1962,perkel1974,friesen1994}.
+It has been proposed as an explanation of the antiphase burst rhythm in struggling in \textit{Xenopus} tadpoles~\citep{li2007}.
+
+~\citet{bose2011} investigated burst generation in a generic half-centre CPG that consists
+of two identical, tonically active Morris-Lecar~\citep{morris1981} neurons coupled through
+inhibitory depressing synapses.
+Numerical simulations showed that when the reciprocal synaptic conductance between the two neurons is varied, the network produces symmetric $n:n$ anti-phase bursts, with stronger synaptic coupling leading to longer bursts.
+They used methods from geometric singular perturbation theory to separate the timescales of the fast membrane, and the slow synaptic dynamics of the network to derive one-dimensional conditions necessary for the existence of stable $n:n$ solutions (for $n\leq 2$).
+According to these conditions the type of firing pattern largely depends on the slow
+depression dynamics of the synapses between the two neurons, and can therefore be
+predicted by knowing the strengths of the synaptic conductances of the two synapses.
+Thus, the scalar conditions derived in \citet{bose2011} provide a method to numerically
+identify the type of stable $n:n$ pattern for any given value of the coupling strength and $n\leq 2$.
+However, they do not predict the exact period of such solutions.
+Furthermore, while they provide good arguments for the validity of their reduction assumptions and the resulting scalar conditions, they do not verify them numerically.
+
+Here we extend the previous analysis by providing a Poincaré map of the slow depression
+dynamics.
+This allows us not only to predict the types of stable $n:n$ solutions the full
+network can produce, (for any $n$), but also to study how varying the coupling strength
+affects the period of such solutions.
+To do this, we build on, and numerically test, the
+assumptions on the fast-slow timescale disparity made in~\cite{bose2011}.
+We reduce the two-cell model to a scalar Poincaré map that tracks the evolution of the depression from the beginning of one burst to the beginning of the next burst.
+Stable fixed points of our map are associated with stable $n:n$ burst solutions.
+Our map construction is motivated by the burst length map of a T-type calcium current, utilised by~\citet{matveev2007}, which approximates the anti-phase bursting dynamics of a network of two coupled Morris-Lecar neurons.
+In contrast to our model, the network described in the~\cite{matveev2007} paper does not contain short-term synaptic depression, and burst termination is instead accomplished through the dynamics of a slow T-type calcium current.
+
+% MAIN RESULTS AND CONCLUSIONS
+The Poincaré map derived here replicates the results from numerical simulations of the
+full two-cell ODE system: Given the strength of maximum conductance between the two
+neurons, fixed points of our map predict the type and period of $n:n$ patterns, the switch
+between burst solutions of different periods, as well as the occurrence of co-existent
+solutions.
+In addition to proving the existence and stability of fixed points, our map shows that fixed points are created via a fold bifurcation of maps.
+Finally, we use our map to derive algebraic conditions that allow us to predict parameter values of the maximum conductance at which $n:n$ solutions bifurcate to $(n+1):(n+1)$ solutions, and vice versa.
+Because our map is fully explicit, it lays the framework for studying the effects of other model parameters on network dynamics without the need to run expensive numerical integrations of the ODEs.
+
+% PAPER STRUCTURE.
+This paper is organised as follows.
+First, we introduce the network of two neurons, and describe the properties of single cell and synapse dynamics.
+We use numerical simulations of the network to provide an intuition for the range of possible burst dynamics the system can produce.
+Next, we state and justify the simplifying assumptions that are necessary for the map construction.
+Finally, we analytically derive the first return map of the depression variable as well as the conditions that are required for stable $n:n$ solutions.
+We end this work with a discussion.
+
+\section{Materials and Methods}
+We consider a pair of identical Morris-Lecar neurons \citep{morris1981}, with parameters from \cite{bose2011}.
+The Morris-Lecar model is a set of two first-order differential equations that describe the membrane dynamics of a spiking neuron.
+The depolarisation is modelled by an instantaneous calcium current, and the hyperpolarisation by a slow potassium current and a leak current.
+The membrane potential $v_{i}$ and potassium activation $w_{i}$ of neuron $i$ ($i, j=1,2$) is described by:
+\begin{align}
+	\label{eq:cell-modelA}
+	\dot v_{i} & = f(v_{i}, w_{i}) -\bar g s_j(v_i-v_{s}), \\
+	\label{eq:cell-modelB}
+	\dot w_{i} & =h(v_i,w_i).
+\end{align}
+Here $v_{s}$ is the inhibitory reversal potential, and $\gbar$ and $s_{j}$ are the maximal synaptic conductance and the synaptic gating, respectively, constituting the total inhibitory conductance $\bar g s_{j}$ from neuron $j$ to neuron $i$.
+Function $f(v_{i}, w_{i})$ describes the membrane currents of a single cell:
+\begin{equation}
+	\label{eq:f}
+	f(v_{i}, w_{i}) = -g_{\ca}m_{\infty}(v_{i})(v_{i}-v_{\ca}) - g_{\k}w_{i}(v_{i}-v_{\k})
+	-g_{\leak}(v_{i}-v_{\leak}) + I.
+\end{equation}
+The currents include a constant current $I$, and three ionic currents: an instantaneous calcium current, a potassium current, and a leak current, with respective reversal
+potentials $v_{\ca}$, $v_{\k}$, and $v_{\leak}$, as well as maximum conductances
+$g_{\ca}$, $g_{\k}$, and $g_{\leak}$.  The function $h(v_{i}, w_{i})$ models the
+kinetics of the potassium gating variable $w_{i}$, and is given by
+\begin{equation}
+	\label{eq:h}
+	h(v_{i}, w_{i})=\frac{w_{\infty}(v_{i})-w_{i}}{\tau_{w}}.
+\end{equation}
+The steady-state activation functions $m_{\infty}$ and $w_{\infty}$ as well as the default model parameters are described in the Supplementary Material S1.
+
+The dynamics of the synaptic interactions between the neurons are governed by a synaptic gating variable $s_{i}$ and a depression variable $d_{i}$:
+\begin{equation}
+	\label{eq:dot-d}
+	\dot d_{i} = \begin{cases}
+		(1-d_{i})/\tau_{a} & \text{ if } v_{i}<v_{\theta}, \\
+		-d_{i}/\tau_{b}    & \text{ if } v_{i}>v_{\theta},
+	\end{cases}
+\end{equation}
+
+\begin{equation}
+	\label{eq:dot-s}
+	\dot s_{i} = \begin{cases}
+		-s_{i} / \tau_{\kappa} & \text{ if } v_{i}<v_{\theta}  \\
+		0                      & \text{ if } v_{i}>v_{\theta}.
+	\end{cases}
+\end{equation}
+
+Variable $d_{i}$ describes a firing rate dependent depletion mechanism that governs the amount of depression acting on the synapse.
+The model is agnostic with respect to the exact mechanism of this depletion, be it pre- or post-synaptic.
+When the voltage of cell $i$ is above firing threshold ($v_i>v_\theta$), variable $d_i$ decays with time constant $\tau_b$, and recovers with time constant $\tau_a$ when voltage is below firing threshold ($v_i < v_\theta$).
+Since the synaptic inhibition occurs on a much faster timescale than synaptic depression, we assume that $s_i$ is instantaneously reset to $d_i$ whenever $v_i$ increases above $v_\theta$, where it remains throughout $v_i > v_\theta$.
+Whenever $v_i < v_\theta$, the synaptic variable decays exponentially with time constant $\tau_\kappa$.
+The equations for the depression model are identical to the \citet{bose2001} model.
+These equations are a mathematically tractable simplification of the established phenomenological depression model previously described by \citet{tsodyks1997}.
+
+When the total inhibitory conductance $\bar g s_{j}$ is constant, the membrane dynamics are determined by the cubic $v$-nullcline $v_{\infty}(v_i)$ and the sigmoid $w$-nullcline $w_{\infty}(v_{i})$, satisfying $\dot v_{i}=0$ and $\dot w_{i}=0$, respectively.
+In case of no inhibition ($\bar g=0$), the two curves intersect near the local minimum of $v_{\infty}$ to the left of $v_{\theta}$ (commonly referred to as ``left knee'' of $v_{\infty}$), creating an unstable fixed point $p_{f}$ with a surrounding stable limit cycle of period $T=T_{a}+T_{s}$ (\cref{fig:nullclines}A).
+Here $T_{a}$ is the amount of time the membrane potential spends above firing threshold ($v_{i}>v_\theta$), while $T_{s}$ is the time it spends below firing threshold ($v_{i}<v_\theta$).
+Trajectories along that limit cycle have the familiar shape of the action potential (\cref{fig:nullclines}B).
+Applying a constant nonzero inhibition, e.g. by letting $s_{j}=1$ and $\bar g > 0$, moves the cubic $v_{\infty}$ with the ensuing unstable fixed point down $w_{\infty}$ in the $(v_{i}, w_{i})$ -plane.
+When $\bar g$ is large enough, the fixed point moves past the left knee and becomes stable via a subcritical Andoronov-Hopf bifurcation, attracting all previously periodic trajectories.
+In the following section we will refer to the value of the total conductance $\bar g s_{j}$ at the bifurcation point as $g_{bif}$.
+
+The two-cell network model is numerically integrated using an adaptive step-size integrator for stiff differential equations implemented with XPPAUT~\citep{ermentrout2002} and controlled through the Python packages SciPy~\citep{scipy2020} and PyXPP~\citep{pyxpp}.
+The following mathematical analysis is performed on the equations of a single cell.
+Unless required for clarity, we will therefore omit the subscripts $i,j$ from here on.
+
+\section{Results}
+\subsection{Anti-phase burst solutions}
+Short-term synaptic depression of inhibition in a half-centre oscillator acts as a \emph{burst termination} mechanism \citep{brown1911} and is known to produce $n:n$ anti-phase burst solutions of varying period.
+Such $n:n$ solutions consist of cells firing bursts of $n$ spikes in alternation.
+\Cref{fig:burst-sols}A shows the timecourse of a typical $4:4$ burst.
+While one cell is firing a burst it provides an inhibitory conductance to the other cell,  preventing it from firing.
+Therefore, at any given moment one cell is spiking while the other is suppressed and does not spike.
+We will refer to the currently firing cell as ``active'' and we will call the suppressed cell ``silent''.
+Additionally, we will distinguish between two phases of a $n:n$ solution:
+We will refer to the time interval when a cell is firing as the ``active phase'', and we will call the remaining duration of a cycle, when a cell is not firing, the ``silent  phase''.
+
+With each action potential of the active cell, short-term depression leads to a decrease of $d$, and consequently of $s$.
+If $d$ depresses faster at spike time than it can recover in the inter-spike-intervals ($ISI$s), the total synaptic conductance $\bar g s$ will eventually become sufficiently small to allow for the silent cell to be released \citep{wang1992,skinner1994} and start firing, thus inhibiting the previously active cell.
+While a cell is silent its depression variable can recover.
+Once the silent cell becomes active again its synaptic inhibition will be sufficient to terminate the burst of the previously active cell and commence a new cycle.
+As previously demonstrated by~\citet{bose2011}, in a two-cell reciprocally inhibitory network with synaptic depression the coupling strength $\bar g$ determines the type of $n:n$ solution.
+Increasing $\bar g$ produces higher $n:n$ burst solutions with more spikes per burst and a longer cycle period.
+\Cref{fig:burst-sols} shows numerically stable $n:n$ solutions for varying values of $\bar g$.
+For small values of $\bar g$ the network produces anti-phase spiking $1:1$ solutions.
+As $\bar g$ is increased the network generates solutions of increasing $n$, that is $2:2$, $3:3$, and $4:4$.
+When $\bar g$ is sufficiently large (bottom of \cref{fig:burst-sols}), one of the cells continuously spikes at its uncoupled period $T$ while the other cell remains fully suppressed.
+Depending on the initial conditions either of the two cells can become the suppressed cell, which is why the suppressed solution is numerically bistable.
+
+Branches of numerically stable $n:n$ solutions and their associated limit cycle period for varying values of $\bar g$ are depicted in \cref{fig:bif-diagram}A (see Supplementary Material S2 for algorithm description).
+Not only do higher $n:n$ solutions branches require stronger coupling $\bar g$, but also within $n:n$ branches the period increases with $\bar g$.
+In line with~\citet{bose2011} we find small overlaps between solution branches indicating numerical bistability, for example such as between the $2:2$ and $3:3$ solution branches.
+Branches of higher $n:n$ burst solutions occur on increasingly smaller intervals of $\bar g$, for instance is the $\bar g$ interval of the $5:5$ branch shorter than that of the $4:4$ branch and so on.
+The interval between the $5:5$ branch and the suppressed solution (region between dotted lines in \cref{fig:bif-diagram}A) not only contains even higher numerically stable $n:n$ solutions, such as $11:11$ bursts, but also other non-symmetric $n:m$ solutions as well as irregular, non-periodic solutions.
+However, the analysis in the following sections will only be concerned with the numerically stable and symmetric $n:n$ solutions.
+
+\subsection{Mathematical analysis of two-cell network}
+\label{sec:assumptions}
+% Summary of assumptions
+The goal of the following mathematical analysis is to reduce the complexity of the
+eight-dimensional system to a more tractable problem.
+As we will explain, we do this by approximating the full dynamics by a reduced system that describes the evolution of the depression variable $d$ of either of the two cells.
+We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the active phase, and then during the silent phase.
+This construction will require two assumptions about the membrane and synaptic dynamics.
+The first assumption states that during a burst the active cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
+The second assumption states that once the inhibitory conductance acting on the silent cell drops below a critical threshold, the cell is immediately released and fires.
+The second assumption is necessary to predict the release time of the silent cell, which allows us to model the recovery of $d$ during the silent phase.
+In other words, the second assumption requires that the release of the silent cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the silent cell.
+The approximate validity of both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
+Both assumptions were first used in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n:n$ solutions.
+However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.
+
+% Assumption 1: active phase
+Our first assumption about the model states that the active cell fires at its uncoupled period $T$, that is, during the active phase of a burst we have $ISI=T$.
+Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
+Numerically computing $ISI$s for all stable $n:n$ solutions in \cref{fig:bif-diagram} reveals that $ISI$s differ by at most $1\, \si{ms}$ from the intrinsic firing period $T\approx 376\, \si{ms}$.
+Assuming $ISI=T$ seems reasonable given that inhibition acting on the silent cell decays exponentially on a much shorter timescale $\tau_{\kappa}$ than the duration of the $ISI$.
+Therefore, once the silent cell is released its trajectory quickly approaches the spiking limit cycle.
+Naturally the above assumption requires a sufficiently small $\tau_{\kappa}$, and fails when $\tau_{\kappa}$ is large.
+In the Supplementary Material \cref{sec:tauk} we numerically explore how different values of $\tau_{\kappa}$ affect the $ISIs$ of the active cell.
+Finally, assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the active phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
+
+% Assumption 2: Release
+Our second assumption states that the silent cell is released and spikes as soon as the total inhibitory conductance $\bar g s$ acting on it drops below some threshold value.
+We call this critical threshold value the ``release conductance'', and define it as the value of $\bar g s$ at the time when the voltage of the silent cell first crosses the firing threshold $v_{\theta}$, that is when that cell is released and fires its first spike.
+Recall that when a cell is silent its $v$- and $w$-nullclines intersect at a stable fixed point and $\bar g s > g_{bif}$.
+A sufficient condition for the silent cell to be released is therefore $\bar g s < g_{bif}$.
+However, depending on the topology of the stable manifold, the $(v,w)$-trajectory of the silent cell can escape the stable fixed point and allow the cell to produce a spike for $\bar g s > g_{bif}$.
+In this case the value of the release conductance depends on the type of $n:n$ solution and the coupling strength $\bar g$.
+For any stable $n:n$ solution in \cref{fig:bif-diagram} we can compute an associated release conductance numerically by recording the value of $\bar g s$ at the time of the first spike of the silent cell.
+Such values of the release conductance are shown in \cref{fig:gstar-diag}A, and the graph suggests that as $n$ increases, the value of the release conductance converges to some constant conductance value $g^{\star} \approx 0.0068\, \si{mS/cm^2}$.
+Here $g^{\star}$ is the value of $\bar g s$ at the end of a cycle of a suppressed solution, just before the active cell spikes.
+Using $g^{\star}$ as a constant approximation for the release conductance will allow us to formulate a scalar condition that predicts the release time of the silent cell.
+Moreover, using $g^{\star}$ is convenient because its exact value can be derived explicitly, as will be shown in the following section.
+
+Assuming a constant release conductance for all $n:n$ solutions will naturally introduce some error in the prediction of the release time of the silent cell.
+We can compute that error for any associated solution in \cref{fig:gstar-diag}A by calculating the time interval between the first spike of the silent cell and the time when $\bar g s$ first crosses $g^{\star}$.
+We will call this time interval the ``release delay''.
+\Cref{fig:gstar-diag}B shows the numerically computed graph of such release delays.
+For $n>1$ the absolute delays are smaller than $2\, \si{ms}$.
+Therefore, using
+\begin{equation}
+	~\label{eq:release}
+	\bar g s=g^{\star}
+\end{equation}
+as a constant release condition for all $n:n$ solutions allows us to accurately predict the timing of the release of the silent cell.
+And to simplify the terminology, from now on we will refer to \cref{eq:release} simply as the ``release condition''.
+
+In summary: We assume that the release condition is sufficient to predict when the silent cell is released.
+Due to the symmetry of $n:n$ solutions the release occurs at exactly half the period of the full cycle.
+The release time therefore uniquely determines the type of $n:n$ solution.
+Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the silent cell.
+Instead, the solution of the synaptic variable $s$ of the active cell is sufficient to predict when $\bar g s =g^{\star}$ is satisfied.
+Finally, the value of $s$ at each spike time is determined by the evolution of the depression variable $d$ of the active cell.
+Constructing a solution of $d$ during the active phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
+However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
+In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n:n$ solutions.
+
+\subsection{Construction of the scalar Poincaré map}
+In this section we construct the scalar Poincaré map $\Pi_n:d^{\star}\mapsto d^{\star}$.
+Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n:n$ burst.
+The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
+To simplify the map construction we will assume that an active cell fires exactly $n$ times before it becomes silent.
+We will construct $\Pi_n$ by evolving $d$ first during the active phase and then during the silent phase of the $n:n$ limit cycle.
+The terms ``active'' and ``silent'' phases will be defined in terms of the state of the depression variable.
+During the active phase the depression variable of the active cell both decays and recovers, while during the silent phase it only recovers.
+First, let us give explicit definitions of the active and silent phases of a burst.
+A schematic illustration of both phases is given in \cref{fig:free-quiet}.
+
+Suppose that at $t=0$ cell 1 becomes active with some initial $d(0)$. Cell 1 then fires $n$ spikes at the uncoupled period $T=T_{a}+T_{s}$.
+Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
+After $n$ spikes the total conductance $\bar g s(t)$ acting on the silent cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}.
+That is at some time $t=(n-1)T + T_{a} + \Delta t$, where $\Delta t < T_{s}$ will be determined below, we have $\bar g s(t)=g^{\star}$ \citep{bose2011}.
+Cell 2 is then released and prevents cell 1 from further spiking.
+Once released, cell 2 also fires $n$ spikes until cell 1 becomes active once again.
+Let $P_n$ denote the full cycle period of a $n:n$ solution:
+\begin{equation}
+	~\label{eq:P}
+	P_n = 2\Big( (n-1)T + T_{a} + \Delta t \Big).
+\end{equation}
+We can now define the active and silent phases of cell 1 explicitly.
+The active phase of a burst is the interval that lasts from the first spike time up until the beginning of the silent phase of the last spike, that is for time $0<t<(n-1)T + T_{a}$.
+During the active phase of cell 1, the silent cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\bar g s > g^{\star}$.
+The silent phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T + T_{a} < t < P_n$.
+The silent phase lasts for $(n-1)T + T_{a} + 2\Delta t$.
+
+Note that only the silent phase depends on $\Delta t$, which will play a central role in the construction of $\Pi_n$.
+From \cref{eq:P} $\Delta t$ can be computed as
+\begin{equation}
+	\label{eq:delta-t-P}
+	\Delta t = \frac{1}{2}P_n - (n-1)T - T_{a}.
+\end{equation}
+We can use \cref{eq:delta-t-P} and the numerically computed bifurcation diagram of the period for stable $n:n$ solutions in \cref{fig:bif-diagram}A to obtain the graph of $\Delta t$ as a function of $\bar g$ (\cref{fig:delta-t}).
+Each continuous branch of $\Delta t$ is monotonically increasing and corresponds to a $n:n$ burst:
+Stronger coupling $\bar g$ increases the total synaptic conductance $\bar g s$ that acts on the silent cell, thus delaying its release.
+It is easy to see that for any $n$-branch we have $\Delta t < T_{s}$:
+Once $\Delta t$ crosses $T_{s}$, the active cell can ``squeeze in" an additional spike and the solutions bifurcate into a $(n+1):(n+1)$ burst.
+
+Distinguishing between the active and silent phases of a $n:n$ cycle allows us to describe the dynamics of the depression variable $d$ explicitly for each phase.
+As can be seen from \cref{fig:free-quiet}C, during the active phase $d$ depresses when $v > v_\theta$ and recovers when $v < v_\theta$.
+In contrast, during the silent phase $d$ only recovers and does not depress.
+Given the initial $d^{\star} = d(0)$ at the beginning of the cycle and the number of spikes in the active phase $n$, we can now construct the burst map $\Pi_n$.
+The map
+\begin{equation}
+	\Pi_n(d^\star)=Q_n\big(F_n(d^\star\big))
+\end{equation}
+\noindent
+is a composition of two maps. Map
+\begin{equation}
+	F_n:d^\star\mapsto \Delta t
+\end{equation}
+models the evolution of $d$ in the active phase.
+$F_n$ takes an initial value $d^{\star}$ and calculates $\Delta t$.
+Map
+\begin{equation}
+	Q_n:\Delta t \mapsto d^{\star}
+\end{equation}
+models the recovery of $d$ in the silent phase.
+Given some $\Delta t$ map $Q_n$ computes $d^\star$ at the start of the next cycle.
+
+Our aim in the following analysis is to elucidate the properties of $\Pi_n$ and to understand the structure of its parameter space by exploring how the stable and unstable fixed points of $\Pi_{n}$ are created.
+To that effect it will be useful to include not only positive, but also negative values of $d^{\star}$ to the domain of $\Pi_{n}$.
+But it is important to add that values $d^{\star}<0$ are biologically impossible as the depression variable models a finite pool of neurotransmitters, and therefore must be positive.
+Because $\Pi_{n}$ maps first from $d^{\star}$ to $\Delta t$, and then back to $d^{\star}$, we will also consider negative values of $\Delta t$, interpreting them as $n:n$ solutions with partially overlapping bursts.
+As will become evident, $\delt<0$ is only a formal violation of the biological realism of the map $\Pi_{n}$, as numerically stable $n:n$ solutions of the full system of ODEs only exist for $\Delta t>0$.
+
+We start the construction of $\Pi_n$ by first considering the active phase and building the map $F_n$.
+At each spike time $t_{k}$ where $d(t_k) = d_k$, variable $d$ decays first for the duration of $T_{a}$, as described by the solution to eq. (\ref{eq:dot-d}).  % cref doesn't work with cases package
+At $t = t_k + T_{a}$ we have
+\begin{equation}
+	d(t_k + T_{a}) = d_k e^{-T_{a}/\tau_b}.
+\end{equation}
+The depression variable then recovers for $T_{s}$ until $t_{k+1}$, where for $0<t<T_{s}$:
+\begin{equation}
+	d(t_{k+1}) = 1 - (1 - d_k e^{-T_{a}/\tau_b} )e^{-t/\tau_a}.
+\end{equation}
+By substituting $t=T_{s}$ we can build a linear map that models the depression of $d$ from spike time $t_{k}$ to the subsequent spike time $t_{k+1}$ during the active phase:
+\begin{equation}
+	d_{k+1} = \lambda\rho d_{k} + (1-\rho),~\label{eq:map-d}
+\end{equation}
+where to keep the notation simple we let
+\begin{align}
+	\lambda & := \exp(-T_{a}/\tau_b), \label{eq:lambda} \\
+	\rho    & :=\exp(-T_{s}/\tau_{a}). \label{eq:rho}
+\end{align}
+
+Given constant $T_{a}$ and $T_{s}$, the derived parameter $\lambda$ determines how much the synapses depresses when $v>v_{\theta}$, while $\rho$ determines how much it recovers when $v<v_{\theta}$.
+Since $0<\lambda, \rho<1$, the map in \cref{eq:map-d} is increasing and contracting, with a fixed point at
+\begin{equation}
+	~\label{eq:dsup}
+	d_{s}=\frac{1-\rho}{1-\lambda\rho},
+\end{equation}
+where $0<d_{s}<1$.
+The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
+Using the release condition in \cref{eq:release} allows us to derive the value of the minimum coupling strength that will produce the full suppressed solution, denoted as $\bar g_{s}$.
+Solving \cref{eq:dot-s} for $s(t)$ with $t=T_{s}$ and setting the initial value $s(0)=d_s\lambda$ then gives us the aforementioned approximation of the release conductance $g^{\star}$:
+\begin{equation}
+	\label{eq:gstar}
+	\bar g_s d_s\lambda e^{-T_{s}/\tau_\kappa}=g^{\star} \approx 0.0068\, \si{mS/cm^2}.
+\end{equation}
+By substituting the definition of $d_{s}$ in \eqref{eq:dsup} and rearranging, we can also write $\bar g_s$ as a function of $\lambda$ and $\rho$:
+\begin{equation}
+	\label{eq:gs}
+	\bar g_s(\lambda, \rho) = \frac{1/\lambda-\rho}{1-\rho} e^{T_{s}/\tau_\kappa}g^\star.
+\end{equation}
+Note that the above dependence of $\bar g_{s}$ on $\lambda$ is linear and monotonically decreasing.
+Increasing $\lambda$ reduces the strength of the depression of the active cell.
+This in turn allows the active cell to fully suppress the silent cell at smaller values of $\bar g$.
+
+Solving \cref{eq:map-d} gives us the linear map $\delta_n$, that for some initial $d^\star$ computes the depression at the $n$th spike time, that is $d(t_n)$:
+\begin{equation}
+	\label{eq:delta-map}
+	\delta_n(d^\star) = (\lambda \rho)^{n-1} d^\star + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^i.
+\end{equation}
+Since $\lambda < 1$, function $\delta_n$ is a linearly increasing function of $d^\star$ with a fixed point at $d_s$ for all $n$.
+Having identified $d$ after $n$ spikes, we can now use the release condition $\bar g s = g^{\star}$ (\cref{eq:release}) to find $\Delta t$.
+At the last ($n$th) spike of the active phase at time $t_n = (n-1)T$ the synapse variable $s$ is set to the respective value of $d(t_n) = \delta_n(d^\star)$, and mirrors the value of $d$ for the duration of $T_{a}$.
+At the end of the active phase at time $t_n + T_{a}$ variable $d$ has decayed to $\delta_n(d^\star) \lambda$, therefore
+\begin{equation}
+	s(t_n + T_{a})=\delta_n(d^\star)\lambda.
+\end{equation}
+Finally $s$ decays exponentially for $\Delta t < T_{s}$.
+Solving \cref{eq:dot-s} with initial condition $s(0)=\dn(d^\star)\lambda$ yields:
+\begin{equation}
+	~\label{eq:s-sol}
+	s(\Delta t)=\dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}.
+\end{equation}
+Substituting $s(\Delta t)$ into $s$ of the release condition (\cref{eq:release}) gives then
+\begin{equation}
+	~\label{eq:release2}
+	\bar g \dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}=g^{\star}.
+\end{equation}
+Our assumption of the release condition guarantees that the silent cell 2 spikes and becomes active when $\bar g s - g^{\star}$ crosses zero.
+Solving \cref{eq:release2} for $\Delta t$ allows us to compute $\Delta t$ as a function of $d^{\star}$, which defines the map $F_{n}$:
+\begin{equation}
+	\label{eq:Fn-map}
+	F_n(d^\star):=\tau_\kappa \ln{\left(\frac{\bar g }{g^\star} \lambda \delta_{n}(d^\star)\right)}= \Delta t.
+\end{equation}
+
+\Cref{fig:FQ-maps}A shows $F_n$ for various $n$, which is a strict monotonically increasing function of $d^{\star}$ as well as $\bar g$.
+Larger values of $d^{\star}$ and $\bar g$, respectively, cause stronger inhibition of the silent cell, and therefore prolong its release time and the associated $\Delta t$.
+Map $F_n$ is defined on $d^{\star}>d_{a}$, where $d_{a}$ is a vertical asymptote found by solving $\delta_{n}(d^\star)=0$ in \cref{eq:delta-map} for $d^\star$, which yields
+\begin{equation}
+	d_{a}(n)=-\frac{(1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^{i}}{ (\lambda \rho)^{n-1} }\leq 0~\label{eq:da}.
+\end{equation}
+
+We now turn to the construction of map $Q_n$, which describes the recovery of the depression variable during the silent phase.
+As we have identified earlier, the recovery of $d$ in the silent phase of a $n:n$ solution starts at time $t_{n} + T_{a}$ and lasts for the duration of $(n-1)T + T_{a} + 2\Delta t$.
+Substituting that duration into the solution of $d$ (\cref{eq:dot-d}) with the initial condition $d(0)=\dn(d^\star) \lambda$ yields the map $Q_{n}$:
+\begin{equation}
+	\label{eq:Qn-map}
+	Q_n(\Delta t) := 1- (1- \dn(d^\star) \lambda)e^{-((n-1)T + T_{a} + 2\Delta t)/\tau_a}.
+\end{equation}
+\noindent
+We can find $\delta_{n}(d^{\star})$, i.e. the value of $d$ at the $n$th spike time, by rearranging the release condition in \cref{eq:release2}:
+\begin{equation}
+	\label{eq:dn}
+	\delta_{n}(d^{\star}) = \frac{1}{\bar g \lambda} g^\star e^{\Delta t/\tau_\kappa}.
+\end{equation}
+Map $Q_n$ is shown in \cref{fig:FQ-maps}B for various values $n$.
+Note that $Q_n$ is monotonically increasing as larger values $\Delta t$ imply a longer recovery time, and hence $Q_{n}$ grows without bound.
+All curves $Q_{n}$ intersect at some $\Delta t = \tau_\kappa\ln{\left[\bar g/g^\star\right]}$ where
+\begin{equation}
+	\label{eq:Qn-intersect}
+	Q_n\left[\tau_\kappa\ln{\left(\frac{\bar g}{g^\star}\right)}\right]=1.
+\end{equation}
+As we will show in the next section, all fixed points of the full map $\Pi_n$ occur for $d^\star<1$.
+We will therefore restrict the domain of $Q_n$ to $(-\infty, \tau_\kappa\ln{\left[\bar g/(g^\star)\right]})$ and the codomain to $(-\infty, 1)$.
+Additionally, while values $\Delta t>T$ will be helpful in exploring the geometry of $\Pi_{n}$, recall from \cref{fig:delta-t} that in the flow system $n:n$ solutions bifurcate into $(n+1):(n+1)$ solutions exactly when $\Delta t = T_{s}$, and we will address this concern in the last part of our map analysis.
+
+Having found $F_n$ and $Q_n$, we can now construct the full map $\Pi_n(d^\star)=Q_n\big(F_n(d^\star)\big)$:
+\begin{equation}
+	\label{eq:Pn-map}
+	\Pi_n(d^\star) = 1 - \Big(1 - \delta_n(d^\star) \lambda \Big)
+	\Big(\frac{\bar g}{g^\star}\delta_n(d^\star) \lambda \Big)^{-\tau}
+	e^{-((n-1)T + T_{a})/\tau_a},
+\end{equation}
+where we substituted $\tau = 2\tau_{k}/\tau_{a}$.
+Recall that $\delta_{n}(d^{\star})$ and $g^{\star}$ are obtained from \cref{eq:delta-map} and \cref{eq:gstar}, respectively.
+Since $d$ is the slowest variable of the system and $\tau_a \gg \tau_\kappa$, we will also assume $\tau<1$.
+\Cref{fig:Pn-map}A depicts $\Pi_n$ for various $n$.
+Intersections of $\Pi_{n}$ with the diagonal are fixed points of the map.
+\Cref{fig:Pn-map}B shows $\Pi_{2}$ with $n=2$.
+Varying the synaptic strength $\bar g$ moves the curves $\Pi_{n}$ up and down the $(d^{\star}, \Pi_{n})$-plane.
+For $\bar g < 0.0015$ $\si{mS/cm^{2}}$ map $\Pi_{2}$ has no fixed points.
+As $\bar g$ is increased to $\bar g \approx 0.0015$ $\si{mS/cm^{2}}$, curve $\Pi_{2}$ coalesces with the diagonal tangentially.
+When $\bar g > 0.0015$ $\si{mS/cm^{2}}$, a pair of fixed points emerge, one stable and one unstable fixed point, indicating the occurrence of a fold bifurcation of maps.
+
+$\Pi_n$ is monotonically increasing with respect to $\bar g$ and also $d^\star$:
+\begin{align}
+	\label{eq:non-degen1}
+	\dv{\Pi_n}{\bar g}  & >0, \\[0.5ex]
+	\label{eq:dPidd}
+	\dv{\Pi_n}{d^\star} & >0.
+\end{align}
+\noindent
+The monotonicity of $\Pi_{n}$ w.r.t. $\bar g$ is evident from \cref{eq:Pn-map}, while the monotonicity w.r.t. $d^{\star}$ follows from the monotonicity of both $Q_{n}$ and $F_{n}$.
+In the following sections we will heavily rely on this monotonicity property of $\Pi_n$.
+Just as $F_n$, curves $\Pi_n$ spawn at the asymptote $d_{a}$ (\cref{eq:da}), and because
+\begin{equation}
+	\lim_{\bar g \to \infty}\Pi_n = 1\text{ for all }n,
+\end{equation}
+fixed points of $\Pi_n$ lie in $(d_{a}, 1)$.
+
+\subsection{Existence and stability of fixed points}
+We introduce the fixed point notation $d^\star_{f}$ with $\Pi_n(d^\star_{f})=d^\star_{f}$.
+The existence of fixed points $d^\star_{f}$ for $\bar g$ sufficiently large can be shown from the strict monotonicity of $\Pi_{n}$ with respect to $\bar g$ and $d^\star$ (\cref{eq:dPidd,eq:non-degen1}), as well as the fact that the slope of $\Pi_{n}$ is monotonically decreasing,
+\begin{equation}
+	\label{eq:non-degen2}
+	\left(\frac{\mathrm{d}}{\mathrm{d}d^\star}\right)^2 \Pi_n<0.
+\end{equation}
+In the limit $d^\star \to d_{a}$ the value of $\Pi_n$ decreases without bound for any $\bar g>0$.
+In the limit $\bar g\to 0$, $\Pi_n$ also decreases without bound, but as $\bar g\to \infty$ values of $\Pi_n$ approach $1$.
+It follows from \cref{eq:non-degen1} and the intermediate value theorem that for some $\bar g$ large enough $\Pi_n$ intersects the diagonal.
+Moreover, because $\Pi_n$ and its slope are monotonic with respect to $d^\star$, there exists some critical fixed point $(d^\star_b, \bar g_b)$ where $\Pi_n$ aligns with the diagonal tangentially with
+\begin{align}
+	\Pi_n(d^\star_b, \bar g_b)               & =d^\star_b, \\
+	\dv{}{d^\star}\Pi_n(d^\star_b, \bar g_b) & =1.
+\end{align}
+
+\subsection{Fold bifurcations of maps}
+Fixed points of $\Pi_n$ satisfy the fixed point equation
+\begin{equation}
+	\label{eq:Phi}
+	\Phi_{n}(d^{\star}, \bar g) := \Pi_{n}(d^{\star}, \bar g)-d^{\star} = 0.
+\end{equation}
+As we have already shown, for $\bar g > \bar g_b(n)$ solutions to \cref{eq:Phi} exist in pairs of stable and unstable fixed points.
+Solving \cref{eq:Phi} explicitly for $d^{\star}$ is not trivial, but solving for $\bar g$ is straightforward and given by $\bar g= G_n(d^\star)$, where
+\begin{equation}
+	~\label{eq:g}
+	G_{n}(d^{\star}) :=
+	\frac{g^{\star}}{\delta_n(d^\star)\lambda}
+	\Big(
+	\frac{(1-\lambda\delta_n(d^\star)) }{1-d^\star} e^{-((n-1)T + T_{a})/\tau_a}
+	\Big)^{1/\tau}
+\end{equation}
+is defined for $d^{\star}<1$ and $\delta_{n}(d^{\star})>0$.
+Plotting $d^\star$ against $\bar g$ gives the fixed point curves, which are shown in \cref{fig:folds}A.
+Note the typical quadratic shape of a fold bifurcation of maps.
+It is also evident that the fold bifurcations occur for increasingly smaller $\bar g$ as $n$ is increased.
+Moreover, the graph suggests that for $n>1$ unstable fixed points have negative values of $d^\star$.
+
+\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(d^\star_b(n), \bar g_b(n)\big)$, which is the global minimum
+of $G_n(d^\star_f)$:
+\begin{align}
+	d^\star_b(n) & = \operatorname{argmin} G_n(d^\star_f), \\
+	\bar g_b(n)  & = \min{G_n(d^\star_f)}.
+\end{align}
+Function $G_n$ is strictly monotonic on the respective intervals of $d^\star_f$ that correspond to the stable and unstable fixed points, that is
+\begin{align}
+	\dv{G_n}{d^\star_f} & > 0, \text{ for } d^\star_f>d^\star_b(n) \text{ stable},   \\[0.5ex]
+	\dv{G_n}{d^\star_f} & < 0, \text{ for } d^\star_f<d^\star_b(n) \text{ unstable},
+\end{align}
+which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $d^\star_f$.
+Because we are primarily interested in the stable fixed points $d^\star_f>d^\star_b(n)$, we define the stable fixed point function $d^\star_f = \phi_n(\bar g)$ as
+\begin{equation}
+	\label{eq:phi}
+	\phi_n(\bar g):= G_n^{-1}(\bar g).
+\end{equation}
+Function $\phi_n(\bar g)$ is also monotonic, and is therefore straightforward to compute numerically.
+We use the Python package Pynverse \citep{pynverse} for that purpose.
+
+Having found the stable fixed points $d^\star_f$ as a function of $\bar g$, we can now compute the associated cycle period.
+Recall that the period is given by \cref{eq:P}, which can be written as a function of $\bar g$:
+\begin{equation}
+	\label{eq:period}
+	P_n(\bar g) = 2 \Big(
+	(n-1)T + T_{a} + F_n\big(\underbrace{\phi_n(\bar g)}_{d^\star_f}, \bar g\big)
+	\Big),
+\end{equation}
+where map $F_n$ (\cref{eq:Fn-map}) calculates $\Delta t$ given a stable fixed point $d^\star_f=\phi_n(\bar g)$.
+\Cref{fig:folds}B shows the period $P_{n}(\bar g)$ computed from \cref{eq:period} versus the cycle period of stable $n:n$ solutions, computed from numerically integrating the full system of ODEs.
+The overlap between blue and orange curves suggests that stable fixed points of $\Pi_{n}$ accurately predict the cycle period of stable solutions of the flow system.
+
+It is evident from \cref{fig:folds}A that $\phi_n$ is strictly increasing with $\bar g$.
+This property follows directly from the quadratic normal form of the fold bifurcation, but can also be shown using implicit differentiation and the fixed point equation $\Phi_n(\phi_n(\bar g), \bar g)=0$ in \cref{eq:Phi}.
+For $d^\star_f=\phi_n(\bar g)>d_b(n)$ we get:
+\begin{equation}
+	\label{eq:dstardg}
+	\dv{\phi_n}{\bar g} = -\frac{\pdv*{\Phi_n}{\bar g}}{\pdv*{\Phi_n}{d^\star}} =
+	\frac{\pdv*{\Pi_n}{\bar g}}{1-\pdv*{\Pi_n}{d^\star}}>0.
+\end{equation}
+The inequality follows from $\pdv*{\Pi_n}{\bar g}>0$ and the fact that $\pdv*{\Pi_n}{d^\star}<1$ for $d^\star>d_b(n)$.
+\Cref{eq:dstardg} allows us to explain why the period $P_n$ increases with $\bar g$, as seen in \cref{fig:folds}B.
+Differentiating $P_n$ gives:
+\begin{equation}
+	\label{eq:dPdg}
+	\dv{P_{n}}{\bar g} = 2\grad F_n(d^\star_f, \bar g) \cdot
+	\begin{bmatrix}\pdv*{\phi_n}{\bar g}\\[0.5ex] 1\end{bmatrix}>0,
+\end{equation}
+where the partial derivatives of $F_n(d^\star_f, \bar g)$ are:
+\begin{align}
+	\pdv{F_n}{d^\star_f} & = \tau_{\kappa} \frac{(\lambda\rho)^{n-1}}{\dn(d^\star_f)}>0, \\[0.5ex]
+	\pdv{F_n}{\bar g}    & = \frac{\tau_{\kappa}}{\bar g}>0.
+\end{align}
+\Cref{eq:dstardg,eq:dPdg} have an intuitive biological interpretation: Increasing the coupling strength between the neurons leads to overall stronger inhibition of the silent cell, which delays its release and leads to a longer cycle period.
+The latter allows more time for the synapse to depress in the active phase and recover in the silent phase, resulting in overall larger values of $d^\star_f$, that is weaker depression at the burst onset.
+
+While fixed points of our Poincaré map predict the cycle period of the flow system excellently, its construction relies on the strong assumption that the active phase contains exactly $n$ spikes.
+As is evident from \cref{fig:folds}B this assumption is clearly violated in the flow system, as stable $n:n$ bursts exists only on certain parameter intervals of $\bar g$.
+The multi-stability of fixed points of maps $\Pi_{n}$ in \cref{fig:folds}B does therefore not imply a similar multi-stability of the flow system.
+In the last sub-section we will analyse the mechanisms that guide how the stable $n:n$ are created and destroyed, and use our previous analysis to derive the corresponding parameter intervals of $\bar g$ where such solutions exist.
+
+\subsection{Stable solution branch borders}
+~\label{sec:borders}
+Let $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ denote the left and right parameter borders on $\bar g$ where stable $n:n$ solutions exist.
+That is, as $\bar g$ is increased stable $n:n$ solutions are created at $\bar g_{\mathcal{L}}(n)$ and destroyed at $\bar g_{\mathcal{R}}(n)$.
+When $\bar g$ is reduced beyond $\bar g_{\mathcal{L}}(n)$, $n:n$ solutions bifurcate into $(n-1):(n-1)$ solutions, while when $\bar g$ is increased beyond $\bar g_{\mathcal{R}}(n)$, $n:n$ solutions bifurcate into $(n+1):(n+1)$ solutions.
+Let us briefly recap our observations regarding $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ from the numerical bifurcation diagram in \cref{fig:folds}B.
+For $n>1$ there are the following relations:
+\begin{align}
+	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{R}}(n)\label{eq:easy1},                                                                 \\
+	\bar g_{\mathcal{L}}(n)                               & < \bar g_{\mathcal{L}}(n+1)\text{ and } \bar g_{\mathcal{R}}(n)<\bar g_{\mathcal{R}}(n+1)\label{eq:easy2}, \\
+	\bar g_{\mathcal{L}}(n+1)                             & < \bar g_{\mathcal{R}}(n)\label{eq:coexistence},                                                           \\
+	\bar g_{\mathcal{R}}(n+1) - \bar g_{\mathcal{L}}(n+1) & < \bar g_{\mathcal{R}}(n) - \bar g_{\mathcal{L}}(n)\label{eq:robustness}.
+\end{align}
+\Cref{eq:easy1,eq:easy2} are self-explanatory.
+\Cref{eq:coexistence} formally describes occurrence of co-existence between stable $n:n$ and $(n+1):(n+1)$ solutions.
+\Cref{eq:robustness} implies that the parameter interval on $\bar g$ of $n:n$ solutions decreases with $n$, in other words, bursts with more spikes occur on increasingly smaller intervals of the coupling strength.
+All of the above relations are reminiscent of the bifurcation scenario of type period increment with co-existent attractors, first described for piecewise-linear scalar maps with a single discontinuity by Avrutin and colleagues~\cite[e.g.
+	see][]{gardini2012,tramontana2012,avrutin2011}.
+While our maps $\Pi_n$ are fully continuous, the above observation suggests that a different piecewise-linear scalar map that captures such period increment dynamics of the full system might exist.
+We will explore what such a map might look like in the discussion.
+
+Let us now find algebraic equations that will allow us to calculate the critical parameters $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ associated with the left and right $n:n$ branch borders.
+Recall that the period $P_n$ derived from the fixed points of $\Pi_n$ is an increasing function of $\bar g$ (\cref{eq:dPdg}).
+That is, as the coupling strength increases, it takes longer for the total synaptic conductance to fall below the value of the release conductance, which delays the release of the silent cell, and $\Delta t$ becomes larger.
+When $\Delta t > T_{s}$, the active cell can produce another spike and the solution bifurcates into a $(n+1):(n+1)$ solution.
+Note, however, that at $\bar g_{\mathcal{L}}(n)$ the bifurcation into a $(n-1):(n-1)$ does not occur at $\Delta t = 0$.
+Here the mechanism is different: A sufficient reduction of $\bar g$ causes the total synaptic conductance to drop below the release conductance in the \emph{previous} $ISI$, which allows the silent cell to be released one spike earlier.
+
+Using the above reasoning we can now formulate the conditions for both bifurcations at $\bar g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$.
+As in the previous sections, we will only restrict ourselves to the analysis of the stable fixed points given implicitly by $d^\star_f=\phi_n(\bar g)$ (\cref{eq:phi}).
+At the right bifurcation border $\bar g_{\mathcal{R}}(n)$ we have $\Delta t=T_{s}$, and after substituting our $F_n$ map (\cref{eq:Fn-map}) this translates into
+\begin{equation}
+	F_n(\phi_n(\bar g), \bar g) = T_{s},
+\end{equation}
+which lets us define a function
+\begin{equation}
+	\label{eq:R}
+	\mathcal{R}_{n}(\bar g):=F_n(\phi_n(\bar g), \bar g)-T_{s},
+\end{equation}
+whose root is the desired right bifurcation border $\bar g_{\mathcal{R}}(n)$.
+In case of the left bifurcation border at $\bar g_{\mathcal{L}}(n)$, the release condition is satisfied just before the active cell has produced its $n$th spike, where total synaptic conductance is given by
+\begin{equation}
+	\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{s}/\tau_\kappa} = g^\star,
+\end{equation}
+which can be rewritten as a function
+\begin{equation}
+	\label{eq:L}
+	\mathcal{L}_n(\bar g):=\bar g \delta_{n-1}\big(\phi_n(\bar g)\big)\lambda e^{-T_{s}/\tau_\kappa} -g^\star,
+\end{equation}
+whose root is $\bar g_{\mathcal{L}}(n)$.
+Both $\mathcal{R}_n$ and $\mathcal{L}_n$ are increasing with respect to $\bar g$, which makes finding their roots numerically straightforward.
+
+\Cref{fig:final-bif} shows the period $P_{n}(\bar g)$ as predicted by the fixed points of $\Pi_{n}$ (\cref{eq:period}) plotted on their respective intervals $\bar g \in [\bar g_{\mathcal{L}}(n),\bar g_{\mathcal{R}}(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
+Here $g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ were computed from eqs. \ref{eq:L} and \ref{eq:R}, respectively.
+Note that the width of $n:n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
+That is, bursts with more spikes occur on increasingly smaller intervals of $\bar g$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
+We also note the occurrence of bistability between pairs of $n:n$ and $(n+1):(n+1)$ branches, which also confirms our initial observation in
+\cref{eq:coexistence}.
+As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate.
+However, the mismatch in the left and right branch borders is significant.
+This mismatch might be due to the millisecond release delay error (\cref{fig:gstar-diag}B) induced by our assumption of a constant release conductance for all $n:n$ solutions (see \cref{eq:release}).
+Another explanation for the border mismatch could be that our assumptions on the time scales of $(v,w)$ vs $s$- and $d$-dynamics do not hold near the stability borders, and that they can only be captured by more complex approximations.
+Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.
+
+\section{Discussion}
+% PROBLEM SUMMARY
+Synaptic depression of inhibition is believed to play an important role in the generation of rhythmic activity involved in many motor rhythms such as in leech swimming \citep{mangan1994} and leech heart beat~\citep{calabrese1995}, and in the lobster pyloric system~\citep{manor1997, rabbah2007}.
+In inhibitory half-centre CPGs, such as believed to be found in the struggling network of \textit{Xenopus} tapdoles,  synaptic depression can act as a burst termination mechanism, enabling the alternation of bursting between the two sides of the CPG~\citep{li2007}.
+Modelling can shed light on the underlying mathematical principles that enable the generation of such anti-phase bursts, and help identify the components that control this rhythm allowing it to switch between different patterns.
+
+% MAIN RESULTS
+To study the mechanisms of burst generation in half-centre CPGs we have analysed a neuronal model network that consists of a pair of inhibitory neurons that undergo a frequency dependent synaptic depression.
+When the strength of synaptic inhibition between the neurons is varied, such a simple network can display a range of different $n:n$ burst patterns.
+Using the timescale disparity between neuronal and synaptic dynamics, we have reduced the network model of eight ODEs to a scalar first return map $\Pi_n$ of the slow depression variable $d$.
+This map $\Pi_n$ is a composition of two maps, $F_n$ and $Q_n$, that model the evolution of the depression during the active and silent phases of $n:n$ solutions respectively.
+Both $F_n$ and $Q_n$ maps are constructed by using the dynamics of a single uncoupled neuron.
+Fixed points of $\Pi_n$ are created in pairs through a fold bifurcation of maps, where the stable fixed point correspond to stable $n:n$ burst solutions of the full two-cell system of ODEs.
+The results from our one-dimensional map match excellently with numerical simulation of the full network.
+Our results are also in line with \citeauthor{brown1911}'s~\citeyear{brown1911} rhythmogenesis hypothesis, namely that synaptic depression of inhibition is a mechanism by which anti-phase bursting may arise.
+
+% FURTHER METHOD IDEAS
+We have studied $n:n$ solutions assuming that the synaptic coupling $\gbar $ between the two cells is symmetrical.
+However,~\citet{bose2011} have shown that asymmetrical coupling $(\gbar_1, \gbar_2)$ can result in network solutions of type $m-n$, where one cell fires $m$ spikes, while the other $n$ spikes.
+It is conceivable that our map construction can be extended to also capture such $m-n$ solutions.
+Remember, in the case of symmetrical coupling with $n:n$ solutions, the timecourse of the depression variables $d_{1}$ and $d_{2}$ were in anti-phase, and it was therefore sufficient to track only one of the two variables.
+To capture the full network dynamics in case of asymmetrical coupling one would also have to account for burst patterns of type $m-n$, where the solutions of the depression variables $d_1$ and $d_2$ are not simply time-shifted versions of each other.
+To do that, one could track the state of both variables by constructing a two-dimensional Poincaré map $\Pi(d_1,d_2)$.
+While geometrical interpretation of two-dimensional maps remains challenging, there exist a number of recent studies which have employed novel geometrical analysis methods to understand the dynamics of two-dimensional maps of small neuronal networks~\citep{akcay2014,akcay2018,liao2020}.
+Generally speaking, our map construction approach is applicable to any small network, even with more than two neurons.
+As long as the network dynamics occur on separable timescales the main challenges to the map construction lie in identifying the slowest variables, and finding an appropriate, simplified description of their respective timecourses.
+In theory, the reduction approach can be also applied to neuronal systems with more than two timescales~\citep[e.g. see][]{kuehn2015}.
+
+In tadpoles, struggling is believed to be initiated by an increase in the firing frequency of reciprocally inhibitory commisural interneurons, which has been hypothesised to lead to stronger synaptic depression of inhibition and result in the iconic anti-phase bursting \citep{li2007}.
+It would therefore be interesting to study how varying the cell intrinsic firing period $T$ could affect the network rhythm.
+While we have laid out the framework to perform such an investigation, due to the choice of neural model we have avoided varying $T$.
+Recall that $T$ is a derived parameter in the~\citet{morris1981} model, and can therefore not be varied in isolation of other model parameters.
+This makes verifying any analytical results from our map analysis via numerical integration of the ODEs difficult.
+A more abstract model such as the quadratic integrate-and-fire model \citep{izhikevich2004} allows varying $T$ independently of other model parameters, and could be more fitting for such an investigation.
+
+% LIMITATION: SPIKE MAP
+Our simulations of the network showed that $n:n$ solutions lose robustness as their period is increased.
+That is, solutions with a larger cycle period occur on increasingly smaller intervals of the coupling strength.
+We were able to replicate this finding by numerically finding the respective left and right borders of stable $n:n$ branches of fixed points of $\Pi_n$, and showing that the distance between these borders shrinks with $n$.
+We have also noted the resemblance of our bifurcation diagram to one where such $n:n$ branches are created via the bifurcation scenario of type period-increment with co-existent attractors, first described for scalar linear maps with a discontinuity \citep{avrutin2012,avrutin2011}.
+It is worthwhile noting that the bifurcations of piecewise linear maps studied by~\citeauthor{avrutin2012} result from a ``reinjection'' mechanism \cite{perez1985}.
+Here the orbit of a map performs multiple iterations on one side of the discontinuity, before jumping to the other side and being \textit{reinjected} back into the initial side of the discontinuity.
+The stark difference of such a map to our map is that reinjection allows a \emph{single} scalar map to produce periodic solutions of varying periods.
+In contrast, we rely on $n$ different maps $\Pi_n$ to describe the burst dynamics without explicitly capturing the period increment dynamics.
+It is therefore conceivable that despite the complexity and non-linearity of the dynamics of our two-cell network, a single piecewise-linear map might be already sufficient to capture the mechanisms that shape the parameter space of the full system.
+In their discussion,~\citet{bose2011} briefly outline ideas about how such a linear map could be constructed.
+
+% FLOW SYSTEM BIFURCATION
+In addition to stable $n:n$ solutions, the numerical continuation by~\citet{bose2011} also revealed branches of unstable $n:n$ solutions.
+While we have identified fold bifurcations of our burst map, we have not found corresponding bifurcations of the flow ODE system, and have generally ignored the significance of unstable map fixed points.
+However, the quadratic nature of the period bifurcation curve is reminiscent of a saddle-node on an invariant circle (SNIC) bifurcation, where the oscillation period lengthens and finally becomes infinite as a limit cycle coalesces with a saddle point.
+SNIC bifurcations have been studied in great detail~\cite[e.g.][]{ermentrout1986}, and a next step would be to provide a rigorous explanation of not only the map dynamics, but also of the flow dynamics of the ODE system.
+% Should be possible to use averaging to reduce the system.
+
+% BIOLOGICAL IMPORTANCE OF DEPRESSION
+We have shown that when the strength of the maximum synaptic conductance is varied, synaptic depression of inhibition can enable our two-cell network to produce burst solutions of different periods.
+This result is in line with the idea that one role of synaptic depression in the nervous system may be to allow a finite size neuronal network to participate in different tasks by producing a large number of rhythms~\citep{bose2011, jalil2004, li2007}.
+To change from one rhythm to another would only require a reconfiguration of the network through changes in synaptic coupling strength.
+Thus short-term synaptic depression of inhibition may provide means for a network to adapt to environmental challenges without changing its topology, that is without the introduction or removal of neurons.
 

### 2024-09-18 scripts/compute.py

@@ -14,11 +14,11 @@ from poincare_map import ode, paths, poincare_map
 def compute_numeric_bif_diagram(dt: float=0.5) -> pd.DataFrame:
     """Compute bifurcation diagram numerically for n=1,2,3,4,5."""
     mlml = ode.MLML("odes/mlml.ode")
-    nsteps = 100
+    nsteps = 90
 
     gmin = 0.01
     ns = [1, 2, 3, 4, 5]
-    g0s = [0.35, 0.4, 0.5, 0.52, 0.56]
+    g0s = [0.35, 0.41, 0.51, 0.52, 0.56]
     gsteps = [0.002, 0.002, 0.002, 0.001, 0.001]
     totals = [5000, 8000, 10000, 15000, 15000]
 
@@ -68,7 +68,7 @@ if __name__ == "__main__":
         print(
             "Computing numeric bifurcation diagram. This might take a while ..."
         )
-        numeric_diagram = compute_numeric_bif_diagram()
+        numeric_diagram = compute_numeric_bif_diagram(dt=0.05)
         numeric_diagram.to_pickle(paths.numeric_bif_diagram)
 
     if (not paths.analytic_bif_diagram.exists()) or args.recompute:

### 2024-09-18 scripts/makefig.py

@@ -7,9 +7,7 @@ import pandas as pd
 
 import matplotlib
 
-# NOTE: Maybe plot directly as pgf and import?
 matplotlib.use("pgf")
-import matplotlib
 from matplotlib import patches
 from matplotlib.figure import Figure
 from matplotlib import pyplot as plt
@@ -33,8 +31,6 @@ rcp["axes.spines.top"] = False
 rcp["axes.spines.right"] = False
 rcp["axes.unicode_minus"] = False
 rcp["text.usetex"] = True
-rcp["pgf.rcfonts"] = False
-rcp["pgf.texsystem"] = "pdflatex"
 rcp["xtick.labelsize"] = "small"
 rcp["ytick.labelsize"] = "small"
 rcp["axes.labelsize"] = "x-large"
@@ -42,7 +38,14 @@ rcp["axes.titlesize"] = "xx-large"
 rcp["figure.titlesize"] = "large"
 rcp["font.size"] = 9
 # Use latex preamble.
-rcp["pgf.preamble"] = r"\usepackage{amsmath} \usepackage{siunitx}"
+rcp["pgf.rcfonts"] = False
+rcp["pgf.texsystem"] = "pdflatex"
+rcp["pgf.preamble"]= "\n".join([  # plots will use this preamble
+        r"\usepackage[utf8]{inputenc}",
+        r"\usepackage[T1]{fontenc}",
+        r"\usepackage[detect-all,locale=UK]{siunitx}",
+        r"\usepackage{amssymb}",
+    ])
 
 matplotlib.rcParams.update(rcp)
 
@@ -609,16 +612,16 @@ patch_unstable = Line2D([], [], linestyle=":", linewidth=1, label="unstable")
 axs[0].legend(handles=[patch_stable, patch_unstable], loc=(0.5, 0.9))
 
 # B: Compute period curves.
-axs[0] = axs[1]
+ax = axs[1]
 for n in ns:
     pmap_n = PoincareMap(n)
     dfn = df[df["n"] == n]
     # analytic
-    axs[0].plot(gs, [pmap_n.period(g) for g in gs], color="C0")
+    ax.plot(gs, [pmap_n.period(g) for g in gs], color="C0")
     # numeric
-    axs[0].plot(dfn["g"], dfn["period"], color="C1")
+    ax.plot(dfn["g"], dfn["period"], color="C1")
 
[…]
